### 2018-01-12 Main.Rmd
first commit

Libraries
```{r}
  library(purrr)
  library(readr)
  library(ggplot2)
  library(langcog)
  library(boot)
#  library(lazyeval)
  library(dplyr)
  library(tidyr)
  library(wordbankr)
  library(directlabels)
#  library(scales)
  library(stringr)
  library(lmtest)
  library(rwebppl)
  library(jsonlite)
  library(nlme)
  library(feather)
  library(broom)
  library(HDInterval)
  library(BBmisc)
```

Writings

Import functions

```{r}
source(paste(getwd(),"/helper_functions/all_helper.r",sep = ""), chdir = T)
```

Make a data set that combines all predictores

```{r, message=FALSE, warning=FALSE}

languages = c("Croatian","Danish","English (American)", "Italian", "Norwegian", "Russian","Spanish","Turkish")

#This command create combined data (all predcitores) and save them in the out_files folder (under: lang_name_combo.csv)

#create_combo(languages = languages)

#Now to save time, we will load already saved files 
Cro_combo <- read.csv("out_files/Croatian_combo.csv")
Dan_combo <- read.csv("out_files/Danish_combo.csv")
Eng_combo <- read.csv("out_files/English (American)_combo.csv")
Ita_combo <- read.csv("out_files/Italian_combo.csv")
Nor_combo <- read.csv("out_files/Norwegian_combo.csv")
Rus_combo <- read.csv("out_files/Russian_combo.csv")
Spa_combo <- read.csv("out_files/Spanish_combo.csv")
Tur_combo <- read.csv("out_files/Turkish_combo.csv")

language_dict = data.frame(language=c(1,2,3,4,5,6,7,8),
                           language_name=c("Croatian","Danish","English", "Italian", "Norwegian", "Russian","Spanish","Turkish"))
```

Select data for first month 
```{r}

data_original <- list(Cro_combo, Dan_combo, Eng_combo, Ita_combo, Nor_combo, Rus_combo, Spa_combo, Tur_combo)

data_first_month <- data.frame()

for (i in 1:length(data_original)) {

   #get first month
  first_month <- (data_original[[i]] %>%
    distinct(age))$age[1]

  #select the intersction of all predictors
  data_lang <- data_original[[i]] %>%
    filter(age == first_month) %>%
    mutate(language = i) %>%
    select(-age)

  data_first_month <- bind_rows(data_first_month, data_lang)

}

data_first_month <- data_first_month %>%
  left_join(language_dict) %>%
  select(-language) %>%
  rename(language = language_name) %>%
  select(-PAT_assoc, -PAT_phono_t1, -PAT_phono_t2, -PAT_phono_nt)

```

Here do the statistics

```{r}

#Total nounds used
total_nouns <- data_first_month %>%
  group_by(language) %>%
  summarise(total=n())

#Nounns that have unilemma
total_unilemas <- data_first_month %>%
  filter(!is.na(uni_lemma)) %>%
  group_by(language) %>%
  summarise(translated=n())

#Nouns with unilemas that have entries in Nelson's association norms 
total_association <- data_first_month %>%
  filter(!is.na(PAC_assoc)) %>%
  group_by(language) %>%
  summarise(normed=n())

total_nouns <- total_nouns %>%
  left_join(total_unilemas) %>%
  left_join(total_association)

feather::write_feather(total_nouns, "saved_data/statistics.feather")
total_nouns <- feather::read_feather("saved_data/statistics.feather")

```

Prepare data for age of acqusition analysis (regressions)

```{r}
data_original <- list(Cro_combo, Dan_combo, Eng_combo, Ita_combo, Nor_combo, Rus_combo, Spa_combo, Tur_combo)

data_regression <- data.frame()

for (i in 1:length(data_original)) {

   #get first month
  first_month <- (data_original[[i]] %>%
    distinct(age))$age[1]

  #select the intersction of all predictors
  data_lang <- data_original[[i]] %>%
    filter(age == first_month) %>% #the first month contains all the data 
    filter (#!is.na(freq), 
            !is.na(length), 
            !is.na(PAC_assoc),
            !is.na(PAC_phono_t1),
            !is.na(PAC_phono_t2)) %>%
    mutate(language = i) %>%
    select(-age)
  # replace NA in PAT with O (NA is when the utility cannot be computed, e.g., a candidate word is not linked to any previousely learned word)

  data_regression <- bind_rows(data_regression, data_lang)

}

data_regression <- data_regression %>%
  left_join(language_dict) %>%
  select(-language) %>%
  rename(language = language_name) %>%
  select(-PAT_assoc, -PAT_phono_t1, -PAT_phono_t2, -PAT_phono_nt)

```

Derive the statistics from Barginsky et al. 2016, and add to our data

```{r}

uni_joined <- feather::read_feather("saved_data/uni_joined.feather")
summ <- feather::read_feather("saved_data/uni_model_data.feather")

counts_mika <- uni_joined %>%
  distinct(language, uni_lemma, frequency) %>%
  rename(freq_mika = frequency)

data_regression_all <- data_regression %>%
  left_join(counts_mika)

#Here I should count how much data we missed when using the mika_freq

wordn_byLang <- data_regression_all %>%
  group_by(language) %>%
  dplyr::summarise(total=n())

missing <- data_regression_all %>%
  filter(is.na(freq_mika)) %>%
  group_by(language)  %>%
  dplyr::summarise(missing=n()) %>%
  left_join(wordn_byLang) %>%
  mutate(prop = missing/total) %>%
  mutate(remain = total-missing )

#There are large missing data in English and Russian (about 30%). For English, I will use instead the Ping Li of Penn State frequnecy count (availabale from CHILDES online). The problem remains in Russian

freq_eng <- data_regression_all %>%
  filter(language=='English') %>%
  select(-freq_mika) %>%
  mutate(freq_mika = freq)

data_regression_all_bis <- data_regression_all %>%
  filter(language != 'English')

data_regression_all_bis <- bind_rows(data_regression_all_bis, freq_eng)

```

Compute AOA  (50% acquisition rate)

```{r}
make_aoa <- function(lang, lang_form = "WS", lex_class = "nouns") {
  item_data <- get_lang_item_data(lang = lang,
                                  lang_form = lang_form,
                                  lex_class = lex_class)
  admin_data <-
    get_lang_admin_data(lang = lang, lang_form = lang_form)
  instr_data <-
    get_lang_instr_data(lang = lang, lang_form = lang_form)
  word_aoa <-
    get_lang_aoa(item_data = item_data,
                 admin_data = admin_data,
                 instr_data = instr_data)

  return(word_aoa)
}

aoa = data.frame()

for (lang in languages) {
aoa_lang <- make_aoa(lang) %>%
  select(item, age) %>%
  mutate(language = lang)

aoa <- bind_rows(aoa, aoa_lang)

}

aoa <- aoa %>%
  rename(AoA = age)

aoa_all <- aoa
aoa_all$language[aoa_all$language == 'English (American)'] <- 'English'

#all data with AoA
data_all <- data_regression_all %>%
  left_join(aoa_all)

#Scale all the predictors here (Wait I should scale for each language separately)
data_all_scaled <- data_all %>%
  group_by(language) %>%
  mutate_at(c("length", "freq", "PAC_assoc", "PAC_phono_t1", "PAC_phono_t2", "PAC_phono_nt", "freq_mika"), funs(as.numeric(scale(.)))) %>%
  select(item, definition, uni_lemma, learned,   IPA,    length,        freq,   PAC_assoc, PAC_phono_t1, PAC_phono_t2, PAC_phono_nt, freq_mika, AoA, language)

#############
#all data with AoA
data_all_bis <- data_regression_all_bis %>%
  left_join(aoa_all)

#Scale all the predictors here
data_all_scaled_bis <- data_all_bis %>%
  group_by(language) %>%
  mutate_at(c("length", "freq", "PAC_assoc", "PAC_phono_t1", "PAC_phono_t2", "PAC_phono_nt", "freq_mika"), funs(as.numeric(scale(.)))) %>%
  select(item, definition, uni_lemma, learned,   IPA,    length,        freq,   PAC_assoc, PAC_phono_t1, PAC_phono_t2, PAC_phono_nt, freq_mika, AoA, language)
#############

#Save at this point

feather::write_feather(data_all_scaled, "saved_data/data_all_scaled.feather")
data_all_scaled <- feather::read_feather("saved_data/data_all_scaled.feather")

#With English frequency
feather::write_feather(data_all_scaled_bis, "saved_data/data_all_scaled_bis.feather")
data_all_scaled_bis <- feather::read_feather("saved_data/data_all_scaled_bis.feather")
```

Plot data for all languages
```{r fig.width=4, fig.height=2}
#tidy data
data_long <- data_all_scaled %>%
  gather(predictor, value, length:freq_mika)

data_long %>%
  #filter(predictor %in% c("PAC_assoc", "PAC_phono_t2", "freq_mika", "length")) %>%
  filter(predictor %in% c("PAC_assoc", "PAC_phono_t2")) %>%
ggplot(aes(x=value, y=AoA))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  #scale_x_continuous(limits=c(-2,5))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") 
```

Regression Analysis 
```{r}

#apply lm for each langauge 
models <- data_all_scaled_bis %>%
  group_by(language) %>%
  do (fit_aoa = lm(AoA ~  freq_mika + length + PAC_assoc+ PAC_phono_t2, data=.) )
stat_estim <- tidy(models, fit_aoa)

models_confint <- data_all_scaled_bis %>%
  group_by(language) %>%
  do (fit_ci = confint(lm(AoA ~  freq_mika + length + PAC_assoc+ PAC_phono_t2, data=.) )) 
stat_conf <- tidy(models_confint, fit_ci) %>%
  rename(term = .rownames)

stat_all <- stat_estim %>%
  left_join(stat_conf) %>%
  filter(term != '(Intercept)') %>%
  rename(predictor = term)

stat_all$predictor <- mapValues(stat_all$predictor, 
                                 from = c("freq_mika", "length","PAC_assoc","PAC_phono_t2"), 
                                 to = c("frequency", "length", "semPAC", "phonoPAC"))

stat_all$predictor <- factor(stat_all$predictor, levels = c("frequency", "length", "semPAC", "phonoPAC"))

feather::write_feather(stat_all, "saved_data/regressions_bis.feather")
stat_all <- feather::read_feather("saved_data/regressions_bis.feather")

#General regression with language as a random variable (with length and frequency as covariate)
general <- lme(AoA ~  freq_mika + length + PAC_assoc+ PAC_phono_t2 , random=~1|language,  data=data_all_scaled_bis, na.action=na.omit)
general_ci <- data.frame(intervals(general)$fixed) 
general_ci$term <- rownames(general_ci)
general_ci <- general_ci %>%
  filter(term != '(Intercept)') %>%
  rename(predictor = term,
         estimate = est.)

general_ci$predictor <- mapValues(general_ci$predictor, 
                                 from = c("freq_mika", "length","PAC_assoc","PAC_phono_t2"), 
                                 to = c("frequency", "length", "semPAC", "phonoPAC"))

general_ci$predictor <- factor(general_ci$predictor, levels = c("frequency", "length", "semPAC", "phonoPAC"))

feather::write_feather(general_ci, "saved_data/regression_all_bis.feather")
general_ci <- feather::read_feather("saved_data/regression_all_bis.feather")

#General regression with language as a random variable (without the length and frequency as covariate)
general_noCov <- lme(AoA ~ PAC_assoc+ PAC_phono_t2 , random=~1|language,  data=data_all_scaled_bis, na.action=na.omit)
general_ci_noCov <- data.frame(intervals(general_noCov)$fixed) 
general_ci_noCov$term <- rownames(general_ci_noCov)
general_ci_noCov <- general_ci_noCov %>%
  filter(term != '(Intercept)') %>%
  rename(predictor = term,
         estimate = est.)

general_ci_noCov$predictor <- mapValues(general_ci_noCov$predictor, 
                                 from = c("PAC_assoc","PAC_phono_t2"), 
                                 to = c("semPAC", "phonoPAC"))

general_ci_noCov$predictor <- factor(general_ci_noCov$predictor, levels = c("frequency", "length", "semPAC", "phonoPAC"))

feather::write_feather(general_ci_noCov, "saved_data/regression_all_bis_noCov.feather")
general_ci_noCov <- feather::read_feather("saved_data/regression_all_bis_noCov.feather")

```

Plot coefficients

```{r fig.width=4, fig.height=3}
ggplot(stat_all, aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor))+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~language, ncol=4)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

ggplot(general_ci, aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = lower, ymax = upper, col = predictor))+
  geom_pointrange(data= general_ci_noCov, aes(ymin = lower, ymax = upper, col = predictor), linetype=2)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

ggplot(general_ci_noCov, aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = lower, ymax = upper, col = predictor))+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

```
Pre-process data for network growth models

```{r}

data_original <- list(Cro_combo, Dan_combo, Eng_combo, Ita_combo, Nor_combo, Rus_combo, Spa_combo, Tur_combo)

data <- vector("list", length = length(data_original))

for (i in 1:length(data_original)) {

  #get first month
  first_month <- (data_original[[i]] %>%
    distinct(age))$age[1]

  #select the intersction of all predictors
  data_lang <- data_original[[i]] %>%
    filter (#!is.na(freq), 
            !is.na(length), 
            !is.na(PAC_assoc),
            !is.na(PAC_phono_t1),
            !is.na(PAC_phono_t2)) %>%
   #Restrict data to up to 26 months in order to avoid overfitting to final months (which have small datapoints). In this we followed Hills et al. 2009.
  #Remove first month (16) in order to compare PAT to PAC (PAT utility can only be computed based on words learned in a previous months)
    filter (age < 27, 
            age > first_month) %>%
    mutate(language = i) %>%
    left_join(language_dict) %>%
    select(-language) %>%
    rename(language = language_name) %>%
    left_join(counts_mika) %>% #(but I am not using frequency at this stage, so this is not necessary)
    select(-language) #%>%
    #filter(!is.na(freq_mika))

  # replace NA in PAT with O (NA is when the utility cannot be computed, e.g., a candidate word is not linked to any previousely learned word)
  data_lang$PAT_assoc[is.na(data_lang$PAT_assoc)] <- 0
  data_lang$PAT_phono_t1[is.na(data_lang$PAT_phono_t1)] <- 0
  data_lang$PAT_phono_t2[is.na(data_lang$PAT_phono_t2)] <- 0

  data[[i]] <- data_lang

}

```

Compute z-score and test network growth

```{r}

zscores <- data.frame(matrix(ncol = 7, nrow = 0))
x <- c("mean", "parameter", "p.value", "lower","upper", "model", "language")
colnames(zscores) <- x

for (j in 1:length(data)) {

  age_list <- (data[[j]] %>% 
                 distinct(age))$age

  data_z <- data.frame()

  for (i in age_list) {
    data_age <- data[[j]] %>%
      filter(age==i)  %>%
      mutate(PAC_assoc_z=scale(PAC_assoc),
             PAT_assoc_z=scale(PAT_assoc),

             PAC_phono_t1_z=scale(PAC_phono_t1),
             PAT_phono_t1_z=scale(PAT_phono_t1),

             PAC_phono_t2_z=scale(PAC_phono_t2),
             PAT_phono_t2_z=scale(PAT_phono_t2)) %>%

      select(age, item, learned, PAC_assoc_z, PAT_assoc_z, PAC_phono_t1_z, PAT_phono_t1_z, PAC_phono_t2_z, PAT_phono_t2_z)

    data_z <- bind_rows(data_z, data_age) 
  }

  #Replace NA z-zcore with 0 (this happens when variance is 0, i.e., all data is a constant)
  data_z$PAT_assoc_z[is.na(data_z$PAT_assoc_z)] <- 0
  data_z$PAT_phono_t1_z[is.na(data_z$PAT_phono_t1_z)] <- 0
  data_z$PAT_phono_t2_z[is.na(data_z$PAT_phono_t2_z)] <- 0

  data_z <- data_z %>%
    filter(learned == 1)

  #Make table for z-score statistsics

  test <- t.test(data_z$PAC_assoc_z, mu=0)
  x1 <- data.frame(as.numeric(test$estimate), as.numeric(test$parameter), as.numeric(test$p.value), as.numeric(test$conf.int[1]), as.numeric(test$conf.int[2]),  'PAC_assoc', j)
  colnames(x1) <- x

  test <- t.test(data_z$PAT_assoc_z, mu=0)
  x2 <- data.frame(as.numeric(test$estimate), as.numeric(test$parameter), as.numeric(test$p.value), as.numeric(test$conf.int[1]), as.numeric(test$conf.int[2]), 'PAT_assoc', j)
  colnames(x2) <- x

  test <- t.test(data_z$PAC_phono_t1_z, mu=0)
  x3 <- data.frame(as.numeric(test$estimate), as.numeric(test$parameter), as.numeric(test$p.value), as.numeric(test$conf.int[1]), as.numeric(test$conf.int[2]), 'PAC_phono_t1', j)
  colnames(x3) <- x

  test <- t.test(data_z$PAT_phono_t1_z, mu=0)
  x4 <- data.frame(as.numeric(test$estimate), as.numeric(test$parameter), as.numeric(test$p.value), as.numeric(test$conf.int[1]),as.numeric(test$conf.int[2]), 'PAT_phono_t1', j)
  colnames(x4) <- x

  test <- t.test(data_z$PAC_phono_t2_z, mu=0)
  x5 <- data.frame(as.numeric(test$estimate), as.numeric(test$parameter), as.numeric(test$p.value), as.numeric(test$conf.int[1]), as.numeric(test$conf.int[2]), 'PAC_phono_t2', j)
  colnames(x5) <- x

  test<- t.test(data_z$PAT_phono_t2_z, mu=0)
  x6 <- data.frame(as.numeric(test$estimate), as.numeric(test$parameter), as.numeric(test$p.value), as.numeric(test$conf.int[1]), as.numeric(test$conf.int[2]), 'PAT_phono_t2', j)
  colnames(x6) <- x

 zscores <- bind_rows(zscores, x1, x2, x3, x4, x5, x6)

}

zscores <- zscores %>%
  left_join(language_dict) %>% 
  select(-language) %>% 
  rename(language = language_name) %>%
  #Since only phono t2 works, I filter out phono t1
  filter(model != 'PAC_phono_t1',
         model != 'PAT_phono_t1')

```

Plot z-score data

```{r}
ggplot(zscores, aes(x = model, y = mean)) +
  geom_pointrange(aes(ymin = lower, ymax = upper, y = mean, col = model))+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap(~language, ncol=4)  +
  theme(aspect.ratio = 0.7)

```

This section is about combining predictors in a network growth model.

Import models

```{r}
source(paste(getwd(),"/models/all_models.r",sep = ""), chdir = T)
```

Scale data before input to the model
```{r}

data_scaled <- vector("list", length = length(data))

for (i in 1:length(data)) {

   data_lang <- data[[i]] %>%
     mutate_at(vars(length:freq_mika), funs(as.numeric(scale(.))))

   data_scaled[[i]] <- data_lang
}

```

Combine all data in one data frame (which we will input to the model)
```{r}
data_combined <- data.frame()
#x <- c("mean", "parameter", "p.value", "lower","upper", "model", "language")
#colnames(zscores) <- x

for (i in 1:length(data_scaled)) {

   data_lang <- data_scaled[[i]] %>%
     mutate (language = i)

   data_combined <- bind_rows(data_combined, data_lang)
}

```

Make models

```{r}
#Isolateed predictors
model_semPAT <-  paste(helper, sem_PAT, optimize, sep = '\n')
model_semPAC <-  paste(helper, sem_PAC, optimize, sep = '\n')
model_phonoPAT <-  paste(helper, phono_PAT, optimize, sep = '\n')
model_phonoPAC <-  paste(helper, phono_PAC, optimize, sep = '\n')

#Combined predictors
model_semPAC_semPAT <-  paste(helper, semPAC_semPAT, optimize, sep = '\n')
model_phonoPAC_phonoPAT <-  paste(helper, phonoPAC_phonoPAT, optimize, sep = '\n')
model_semPAC_phonoPAC <-  paste(helper, semPAC_phonoPAC, optimize, sep = '\n')
model_semPAT_phonoPAT <-  paste(helper, semPAT_phonoPAT, optimize, sep = '\n')
model_semPAT_phonoPAC <-  paste(helper, semPAT_phonoPAC, optimize, sep = '\n')
model_semPAC_phonoPAT <-  paste(helper, semPAC_phonoPAT, optimize, sep = '\n')

model_semPAC_phonoPAC_semPAT_phonoPAT <-  paste(helper, semPAC_phonoPAC_semPAT_phonoPAT, optimize, sep = '\n')

model_freq_len_model_semPAC_phonoPAC_semPAT_phonoPAT <- paste(helper, freq_len_semPAC_phonoPAC_semPAT_phonoPAT, optimize, sep = '\n')

#Make a list of theses models
model_list = list(model_semPAT, model_semPAC, model_phonoPAT, model_phonoPAC,
                  model_semPAC_phonoPAC_semPAT_phonoPAT,
                  model_freq_len_model_semPAC_phonoPAC_semPAT_phonoPAT
                  #model_semPAC_semPAT, 
                  #model_phonoPAC_phonoPAT,
                  #model_semPAC_phonoPAC,
                  #model_semPAT_phonoPAT,
                  #model_semPAT_phonoPAC,
                  #model_semPAC_phonoPAT
                  )

model_dict = data.frame(model_index=seq(1, length(model_list)),
                           model_name=c('semPAT', 'semPAC', 'phonoPAT', 'phonoPAC',
                                        'model_semPAC_phonoPAC_semPAT_phonoPAT',
                                        'model_freq_len_semPAC_phonoPAC_semPAT_phonoPAT'
                                        #'model_semPAC_semPAT', 
                                        #'model_phonoPAC_phonoPAT',
                                        #'model_semPAC_phonoPAC',
                                        #'model_semPAT_phonoPAT',
                                        #'model_semPAT_phonoPAC',
                                        #'model_semPAC_phonoPAT'
                                        ))

```

Compute the posterior (looping over languages and models)

```{r}

posteriors_all <- vector("list", length = length(data_scaled))

for (j in 1:length(data_scaled)) {

  posteriors_lang <- vector("list", length = length(model_list))

  for (i in 1:length(model_list)) {

    posterior_model <- NULL

    while (typeof(posterior_model)=="NULL") {
      posterior_model <- webppl(model_list[[i]],
                                data = data_scaled[[j]],
                                data_var = "data",
                                inference_opts = list(
                                  method = "MCMC",
                                  samples = 200, 
                                  burn = 50),
                                model_var = "AOA",
                                output_format = "webppl")
    }

    posteriors_lang[[i]] <- posterior_model
  }

  posteriors_all[[j]] <- posteriors_lang

}

#feather::write_feather(posteriors_all, "saved_data/posterior.feather")
```

Model for all data combined
```{r}

posteriors_combined <- vector("list", length = length(model_list))

for (i in 1:length(model_list)) {

    posterior_model <- NULL

    while (typeof(posterior_model)=="NULL") {

      posterior_model <- webppl(model_list[[i]],
                                data = data_combined,
                                data_var = "data",
                                inference_opts = list(
                                  method = "MCMC",
                                  samples = 2000, 
                                  burn = 500),
                                model_var = "AOA",
                                output_format = "webppl")
    }

    posteriors_combined[[i]] <- posterior_model

}

#feather::write_feather(posteriors_all, "saved_data/posterior.feather")
```

Process parameters

```{r}

parameters_all = data.frame()

for (j in 1:length(posteriors_all)) {

  parameters_lang = data.frame()

  for (i in 1:length(posteriors_all[[j]])) {

    param <- posteriors_all[[j]][[i]] %>%

      select(starts_with("value.parameters")) %>%
      gather(alpha, value, value.parameters.alpha1:value.parameters.alpha4) %>%
      mutate(alpha = gsub("value.parameters.", "", alpha)) %>%
      mutate(model_index = i) #%>%
      #left_join(model_dict)

    parameters_lang <- bind_rows(parameters_lang, param)
  }

   parameters_lang <- parameters_lang %>%
     mutate(language = j )

  parameters_all <- bind_rows(parameters_all, parameters_lang)

}

parameters_all <- parameters_all %>%
  left_join(model_dict) %>%
  left_join(language_dict) %>%
  select(-model_index, -language) %>%
  rename(language = language_name,
         model = model_name)

feather::write_feather(parameters_all, "saved_data/parameters_all.feather")
parameters_all <- feather::read_feather("saved_data/parameters_all.feather")
```

Compute parameters for data combined:

```{r}
parameters_combined = data.frame()

  for (i in 1:length(posteriors_combined)) {

    param <- posteriors_combined[[i]] %>%

      select(starts_with("value.parameters")) %>%
      gather(alpha, value, value.parameters.alpha1:value.parameters.alpha4) %>%
      mutate(alpha = gsub("value.parameters.", "", alpha)) %>%
      mutate(model_index = i) #%>%
      #left_join(model_dict)

    parameters_combined <- bind_rows(parameters_combined, param)
}

parameters_combined <- parameters_combined %>%
  left_join(model_dict) %>%
  rename(model= model_name)
```

Compute point estimate and credible intervals
```{r}

parameters_sum <- parameters_all %>%
  group_by(language, model, alpha) %>%
  summarise(mean = mean(value),
            median = median(value),
            quantile_lower = quantile(value, c(0.025, 0.975))["2.5%"],
            quantile_upper = quantile(value, c(0.025, 0.975))["97.5%"],
            hdi_lower = hdi(value)['lower'],
            hdi_upper = hdi(value)['upper']
  )

post_combined <- parameters_sum %>%
  filter(model == "model_semPAC_phonoPAC_semPAT_phonoPAT") %>%
  ungroup() %>%
  select(-model,  -median, -quantile_lower, -quantile_upper) %>%
  rename(model = alpha)

post_combined$model <- mapValues(post_combined$model, 
                                 from = c("alpha1", "alpha2","alpha3","alpha4"), 
                                 to = c("semPAC", "phonoPAC", "semPAT", "phonoPAT"))

post_combined$model <- factor(post_combined$model, levels = c("phonoPAC", "phonoPAT", "semPAC", "semPAT"))

feather::write_feather(post_combined, "saved_data/combined_net.feather")
post_combined <- feather::read_feather("saved_data/combined_net.feather")

post_individual <- parameters_sum %>%
  filter(model != "model_semPAC_phonoPAC_semPAT_phonoPAT",
         alpha == "alpha1")

post_individual$model <- factor(post_individual$model, levels = c("semPAC", "phonoPAC","semPAT", "phonoPAT"))

##Prepare plot: join posterior on individual predictors and t-test in one data.frame
post_individual_toJoin <- post_individual %>%
  select(-alpha, -median, -quantile_lower, -quantile_upper) %>%
  rename(lower = hdi_lower,
         upper = hdi_upper) %>%
  mutate(Evaluation = 'Fit')

zscores_toJoin <- zscores
zscores_toJoin$model <- mapValues(zscores_toJoin$model, 
                                 from = c("PAC_assoc", "PAC_phono_t2", "PAT_assoc", "PAT_phono_t2"), 
                                 to = c("semPAC", "phonoPAC", "semPAT", "phonoPAT"))

zscores_toJoin <- zscores_toJoin %>%
  select(-parameter, -p.value) %>%
  mutate(Evaluation = 't-test')

individual_both <- bind_rows(post_individual_toJoin, zscores_toJoin)

feather::write_feather(individual_both, "saved_data/individual_both.feather")
individual_both <- feather::read_feather("saved_data/individual_both.feather")

######

ggplot(individual_both, aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = lower, ymax = upper, col = model, linetype=Evaluation),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap(~language, ncol=4)  +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

ggplot(post_combined, aes(x = alpha, y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, y = mean, col = alpha))+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap(~language, ncol=4)  +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

```

### 2018-01-12 cogsci/cogsci.Rmd
first commit

---
title: "The Role of Early Semantic and Phonological Networks in Noun Learning: a Cross-linguistic Analysis"

bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Yuan Bian} \\ \texttt{ybian.uiuc@gmail.com} \\ Department of Psychology \\ University of Illinois
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

abstract: 
    "Children tend to learn first the words that have a high density neighborhood in the lexical network (i.e., words that are connected to a variety of other words). However, the reason why connectivity influences learning is still not very well understood. Previous studies suggested this effect could be the consequence of the underlying learning mechanism. However, these studies focused on semantic networks and English data only, thus severely limiting the generality of the findings. Here we provide a systematic analysis of network growth models in both the phonological and the the semantic domains, and across 8 languages. We replicate the results obtained by Hills et al. (2009) with English semantic networks, show that the same  mechanism drives the growth of both semantic and phonological networks, and demonstrate that these effects hold cross-linguistically."

keywords:
    "keywords: semantic network, phonological network, word learning, semantic "

output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())

#knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
#                      echo=F, warning=F, cache=F, message=F, sanitize = T)

knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)

```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
options(xtable.comment = FALSE)
library(purrr)
library(readr)
library(ggplot2)
library(langcog)
library(boot)
#library(lazyeval)
library(dplyr)
library(tidyr)
library(wordbankr)
library(directlabels)
#library(scales)
library(stringr)
library(lmtest)
library(rwebppl)
library(jsonlite)
library(nlme)
library(feather)
library(broom)
library(HDInterval)
library(BBmisc)
```

# Introduction

A crucial question in language development is to understand why children learn some words at an earlier age than others. Previous studies documented various word properties that influence the age of acquisition. For example, it was shown that, within a lexical category, words that are more frequent in child-directed speech are acquired earlier [@goodman2008]. Other predictors include word length, the mean length of utterances in which the word occurs, and how concrete the word is [see @braginsky2016]. Besides these word-level properties, researchers found that the lexical structure (that is, the network that specifies how words relate to each other) also influences the learning process. For instance, children tend to produce first the words that have higher neighborhood density (i.g., high connectivity in the network) both at the phonological and the semantic level [@stokes2010; @storkel2009]. However, it is still not very well understood *why* connectivity in the lexical structure influences learning. @steyvers2005 suggested that this effect is nothing but the consequence of how these structures get constructed in the child's mind. According to this explanation (known as Preferential Attachment), highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario. Nonetheless, @hills2009 found that what biases the learning is not the connectivity in the child's internal lexicon but the connectivity in the learning environment.

These analyses, however, focused on growth in semantic networks only. A recent study by @stella2017 analysed both semantic and phonological connectivity, but assumed only one growth model (preferential acquisition). More importantly, almost all available studies are limited in their generality because they focus almost exlusively on English data. The novely of this study is that it investigtes, for the first time, whether phonological networks grow by preferential attachement or preferential acquisition. It also provides a systematic comparision between network growth scenarios in both the phonological and the semantic domains and assess their relative contribution to the learning process. Moreover, it tests the generality of the findings across eight languages.

The paper is organized as follows. First, we describe the dataset we used, the procedure we followed to construct both semantic and phonological networks, and the network growth scenarios we tested. Next, we show the results of the various analyses we conducted comparing network growth scenarios across languages. Then we compare the overall contribution of the networks in the learning process relative to other known predictors of age of acquisition (frequency and length). Finally we discuss the major results in relation to known experimental facts in language development.

```{r }

#Import data from saved
data_all_scaled <- feather::read_feather("../saved_data/data_all_scaled.feather")

#tidy data
data_long <- data_all_scaled %>%
  gather(predictor, value, length:freq_mika)

data_long <- data_long %>%
  #filter(predictor %in% c("PAC_assoc", "PAC_phono_t2", "freq_mika", "length")) %>%
  filter(predictor %in% c("PAC_assoc", "PAC_phono_t2"))

data_long$predictor <- mapValues(data_long$predictor, 
                                 from = c("PAC_assoc", "PAC_phono_t2"), 
                                 to = c("Sem.", "Phono."))

plot_data_all <- ggplot(data_long, aes(x=value, y=AoA))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  coord_cartesian(xlim=c(-2,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  xlab("degree z-score") +ylab("AoA")

ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)

```

```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the end-state network as predicted by the degree in this network. Results are shown in each language for the phonological network (top) and the semantic network (bottom). Each point is a word, with lines indicating linear model fits."}
plot_data_all
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

```

# Networks

## Data

We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI). The latter consists of parent report vocabulary checklists. We used the *Words and Sentence* version which contains the productive vocabulary of toddlers (age varied between 16 to 35 months). We included words that were produced by at least 50% of children, and we considered that these words were learned at the month when this percentage was reached [@goodman2008]. Moreover, following previous studies [e.g., @storkel2009; @hills2009], we restricted the analysis to the category of nouns, since there are known discrepancies between the learning of nouns, predicates, and function words [e.g., @braginsky2016]. 
We obtained these nouns in eight languages: Croatian, Danish, English, Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of nouns that had entries in the Florida Association Norms (see below). Since these norms are available only in English, we mapped words onto translation equivalents across CDI forms. This allowed us to use the English association norms across languages. Table \ref{tab:stats} gives an overview of the data used. The translation of non-English words is still an ongoing process. Note, however, that all languages have at least 60% of nouns translated.

```{r stats, results="asis", echo=FALSE}

statistics <- feather::read_feather("../saved_data/statistics.feather")
rownames(statistics) <- NULL

tab <- xtable::xtable(statistics,
                      caption = "\\label{tab:stats}Total number of productive nouns in the CDI (left). We used a subset of these nouns that have available English translations (middle), as well as entries in the Free Association Norms (right).")

print(tab, type="latex", comment = F, table.placement = "H")

#print(statistics, type="latex", comment = F, table.placement = "H")
```

With this data, we constructed both semantic and phonological networks.

## Semantic networks

We used as index of semantic relatedness the Florida Free Association Norms [@nelson1998]. This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target). For example, when given the word "ball", they might answer with the word "game". A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms. Each node was characterized by its "indegree", which represents the number of links for which the word was the target. Following @hills2009, we used as a proxy for the learning environment, the network constructed using the full CDI data in each language (e.g., in English this corresponds to the network by 30 months).

```{r }

#Import data from saved
individual_both <- feather::read_feather("../saved_data/individual_both.feather")

pred_ind <- ggplot(individual_both, aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = lower, ymax = upper, col = model, linetype=Evaluation),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap(~language, ncol=4)  +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

ggsave("figs/pred_ind.png", plot = pred_ind, width = 8, height = 4)

```

```{r pred_ind_img, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3.5, fig.align = "center", fig.cap = "\\label{fig:pred_ind}Evaluation of individual network growth models using both  one-sample t-test over the z-score distribution of learned words (dotted), and model fitting (solid). Each dot represents, in the first case, the mean of the z-score distribution of the learned words with ranges representing 95\\% confidence interval, and in the second case, the mean of the posterior distribution of the model's parameter, with ranges reppresenting 95\\% credible intervals (computed using the highest density intervals)."}

pred_ind

#img <- png::readPNG("figs/pred_ind.png")
#grid::grid.raster(img)
```

## Phonological networks

We used as a measure of phonological relatedness between two nodes the Levenshtein (edit) distance between their phonological forms. The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.  We generated approximate IPA forms from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).**. In previous studies, two nodes were linked if they had an edit distance of 1 [@stokes2010; @storkel2009]. However, in these previous studies the network was built using an adult vocabulary. Here, similar to the approximation we made for the semantic network, we used the full set of nouns in the CDI data as a proxy for phonological connectivity in the learning environment. However, since the children's vocabulary contains very few word pairs with an edit distance of 1, the resulting network was too sparse and uninformative. Thus, we increased the threshold from 1 to 2, that is, two node were related if their edit distance was equal to 1 or 2. Each node was characterized with its degree, i.e., the number of links it shares with other words.

## Network growth

We tested two network growth scenarios discussed in @hills2009. The first one was *Preferential Attachment* (PAT). According to this mechanism, the network structure of known words predicts what words will be learned next. A word is more likely to be learned if it is linked to one of the highly connected nodes in this internal network. The second mechanism was *Preferential Acquisition* (PAC). In this model, what predicts what word will enter the lexicon is not connectivity in the internal network, but connectivity in the learning environment.  Figure \ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network. For PAT, each candidate node was characterized with the average degree of the existing nodes that it would attach to. Thus, according to PAT, the node N1 is more likely to enter the lexicon first. For PAC, each candidate node was characterized with its degree in the entire network. According th PAC, the node N3 is more likely to enter the lexicon first.

```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Illustration of the two growth models with the same network. Filled circles (A to D) represent known words, and empty circles (N1 to N3) represent words that have not been learned yet. Back lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant (from Hills et al. 2009)."}

img <- png::readPNG("figs/growth.png")
grid::grid.raster(img)

```

# Analysis

## Connectivity vs. Age of acquisition

Preferential attachment and preferential acquisition provide different generative scenarios for the same end-state. The latter is defined here as the network corresponding to the oldest age for which we have CDI data. However in both cases, it is predicted that nodes with the higher degrees in this end-state are learned earlier than nodes with the lower degrees. Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network) in the end-state network. In order to compare this correlation across languages, the predictor (i.e., the degree) was centered and scaled. The plot shows a negative correlation between the month of acquisition and the degree (with the exception of the Russian semantic network), indicating that nouns with higher degrees are generally learned earlier.

```{r }

#Import data from saved
post_combined <- feather::read_feather("../saved_data/combined_net.feather")

pred_comb <- ggplot(post_combined, aes(x = model, y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, y = mean, col = model), size=0.3)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap(~language, ncol=4)  +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

ggsave("figs/pred_comb.png", plot = pred_comb, width = 8, height = 4)
```

```{r pred_comb_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:pred_comb_img}Estimates of the growth models' parameters in each language. Dots represent the means of the posteriori distribution of the parameters, and ranges represent 95\\% credible intervals (computed using the highest density intervals). "}
pred_comb
#img <- png::readPNG("figs/pred_comb.png")
#grid::grid.raster(img)
```

## Network growth models

Following @hills2009, we evaluated the growth models in two separate ways. The first evaluation consists in determining, in each month, the model-dependent growth value distribution of all words that could possibly be learned at this month, and then computing the z-score of each learned word with respect to this distribution.  For each model, we tested if the distribution constituted by the z-scores of all learned words was different from zero, using a one-sample t-test. The results are shown in Figure \ref{fig:pred_ind}.

The second evaluation consists in fitting an explicit model to the data. The purpose of this second evaluation is, first, to validate the findings obtained with the one-sample t-test, and second, to determine (in a next step) the relative contribution of each network growth scenario (PAT vs. PAC) across domains (phonological vs. semantic).

We proceeded as follows. We calculated the probability that a word $w_i$, with a growth value $d_i$ would enter the lexicon at a given month, using a softmax function: 
\begin{equation}
 p(w_i)= \frac{e^{\beta d_i}}{\sum_j e^{\beta d_j} }
\end{equation}

Where $\beta$ is the fitting parameter. A positive value of $\beta$ means that words with higher groth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first. The normalization included words that were not yet learned at the month the word at hand was acquired.  We estimated the parameter $\beta$ using a Bayesian approach. We started with a uniform distribution, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been actually learned at that month (using formula 1). We ended up with a posterior distribution of $\beta$, which we summarized in Figure \ref{fig:pred_ind}.

The results from both evaluations were very similar and lead essentially to the same conclusions. For the semantic networks, the results replicate Hills et al.'s finding in English, which was that the semantic network grows by PAC, not by PAT. Moreover, it generalizes this finding to all other languages (with the exception of Russian). For the phonological network, the results show that, generally speaking, PAC fits the developmental trajectory better than PAT in all languages. We note however that PAT, though weaker, fares  better for the phonological networks than it does for the semantic networks. In the former, it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian. In the latter, it is rather universally unpredictive.

Above we evaluated the network growth scenarios individually. As a next step, we analysed their relative contribution to the learning process. This was done through adding more fitting parameters to the model, that is, by substituting $\beta d_i$ in equation (1) with: $$\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}$$ where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and PhonoPAC. Using the same fitting technique, we obtained the values shown in Figure \ref{fig:pred_comb_img}. In term of growth scenarios, we found that PAC dominates the learning. In particular, though we found previously that phonological PAT predicted part of the learning in some languages when tested individually, here PAT appears to lose its predictive power when pitted against phonological PAC. In terms of domain (phonological vs. semantic), both phonological and semantic networks appear to contribute to learning, although the phonological network appears to be stronger and more reliable across languages. In summary, the findings show that both semantic and phonological networks grow primarily through preferential acquisition, and that, generally speaking, semantic and phonological networks both contribute to the learning process.

```{r }

#Import data from saved
regressions <- feather::read_feather("../saved_data/regressions_bis.feather")

pred_regressions <- ggplot(regressions, aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor), size=0.3)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~language, ncol=4)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

ggsave("figs/pred_regressions.png", plot = pred_regressions, width = 8, height = 4)
```

```{r regressions_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:regressions_img}Estimates of predictor coefficients by language. Values above 0 indicate a positive relationship (e.g. longer words tend to have a higher AoA), while values below 0 indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA). Ranges indicate 95\\% confidence intervals."}

pred_regressions

#img <- png::readPNG("figs/pred_regressions.png")
#grid::grid.raster(img)
```

## The big picture: comparison to other known predictors of age of acquisition

We saw that the way semantic and phonological information is structured in the learning environment (i.e., PAC) contribute to noun learning across languages. However, we know that other factors influence learning as well [e.g., @braginsky2016]. In what follows, we will investigate how semantic and phonological connectivity interact with two other factors. The first one is word frequency, a well studied factor shown to predict the age of acquisition in a reliable fashion [e.g. @goodman2008]. The second factor is word length because it correlates with phonological connectivity [@pisoni1985].

Since PAT was uninformative, we dropped it from this analysis. Thus, we no longer needed to to fit the growth model month-by-month as in the previous section. In fact, word utilities in the case of PAC are fixed, they do not depend on previously learned words. A more direct way to assess and compare the contribution of PAC in relation to other factors is through conducting linear regressions, where connectivity in the learning environment (at both the phonological and semantic level), frequency and length predict the age of acquisition.

We used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language. For each word, counts included words that shared the same stem  (e.g., cats counts as cat), or words that were synonymous (e.g. father counts as daddy). For word length, we used our generated IPA transcription. This allowed us to get a more accurate estimate of word length across languages than the number of characters in the orthographic transcription.

```{r }

#Import data from saved
regression_all <- feather::read_feather("../saved_data/regression_all_bis.feather")
regression_all_noCov <- feather::read_feather("../saved_data/regression_all_bis_noCov.feather")

pred_regression_all <- ggplot(regression_all, aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = lower, ymax = upper, col = predictor), size=0.3)+
  geom_pointrange(data=regression_all_noCov,
                  aes(ymin = lower, ymax = upper, col = predictor),
                  position = position_dodge(width = .3),
                  linetype=1,
                  size = 0.7,
                  fatten = 1.5,
                  alpha = 0.3)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

ggsave("figs/pred_regression_all.png", plot = pred_regression_all, width = 4, height = 2)
```

```{r regressions_all_img, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, fig.cap = "\\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined model. Ranges indicate 95\\% confidence intervals. Fade color indicates estimates of PAC predictors in a model that does not include frequency and length as covariates."}

pred_regression_all

#img <- png::readPNG("figs/pred_regression_all.png")
#grid::grid.raster(img)
```

We conducted two analyses. On the one had, we fit a linear regression for each language, and on the other hand, we fit a linear mixed-effect to all the data pooled across languages, with language as a random effect. Figure \ref{fig:regressions_img} shows the coefficient estimate for each predictor in each language, and figure \ref{fig:regressions_all_img} shows the coefficient estimates for all languages combined (all predictors were centered and scaled). The findings were as follows. Overall, frequency is the most reliable predictor of age of acquisition.  Word length predicts part of learning in some languages such as Croatian and Norwegian, but not in others (including English). It remains, however, a significant predictor in the global model. As for the factors of interest, i.e., semantic and phonological connectivities, we also found cross-linguistic differences. The phonological connectivity contributes to learning in languages such as Croatian, English and Russian, whereas semantic connectivity contributes to learning in Turkish, Spanish and to some extent in Croatian, but interestingly not in English\footnote{Semantic connectivity does not explain variance in English data beyond that explained by frequency and length. This contrasts with the original finding in Hills et al. 2009. However, in this previous studiy, semantic connectivity was not tested in a model that included both frequency and length as covariates. Morever, our sample size is bigger.}. Despite this cross-linguistic variation, both phonological and semantic connectivity remain significant predictors in the global model.

# Discussion

The present study provided a comprehensive analysis of how lexical connectivity influences the age of acquisition of nouns in toddlers. We compared two network growth scenarios and assessed the relative contribution of phonological and semantic information in 8 languages. Part of the findings largely replicate the results obtained in @hills2009, i.e., semantic networks (based on free associations) grow by preferential acquisition, not by preferential attachment. Another finding was that phonological networks also grow primarily by preferential acquisition, especially when both scenarios (PAT and PAC) were pitted against each other in the same model. These findings generalize well across languages. Moreoever, both semantic and phonological connectivity in the learning environment (i.e., PAC) predict growth in a consistent way across many languages. However, when pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting part of learning in some languages, but not in others. Despite this coross-lingusitic variation, both phonological and semantic connectivity contribute to the overall learning (when data is pooled across languages).

A major results of the study is that children start by learning words that have high phonological and semantic similarity with a variety of other words in the learning environment, not in the available lexicon.  This suggests that children are sensitive to connectivity even without having first acquired the connected words! How can children indirectly detect highly connected words, and why would such words be more readily learned? In the semantic case, free association can be predicted through the patterns of word co-occurrence [@griffiths07], meaning that highly connected words tend to be the words that co-occur with many other words in various contexts. One possibility, suggested by @hills2010, is that the referents of such words are more easily disambiguated as demonstrated, for instance, by cross-situational learning experiments [@smith2008].
In the phonological case, connectivity is inherently correlated with phonotactic probability [@vitevitch1999]. That is, highly connected words tend to be made of frequent sound sequences. We know even infant (whose vocabulary is still very rudimentary) develop a sensitivity for high frequency sound sequences in the ambient native language [@jusczyk1994]. Interestingly, it was shown that phonotactic probability facilitates learning and recognition of novel words in toddlers and preschoolers [@storkel2001;  @higgins2014]. Thus, children's ability to keep track of co-occurrence statistics (both at the semantic and phonological level) might explain their sensitivity and preference for highly connected words in the learning envirnoment.

Finally, this study shares a number of limitations with previous studies using similar datasets. For instance, we used normative age of acquisition. However, individual children may not follow a unique learning trajectory. The use of longitudinal data would allow us to assess how the aggregate behavior relates to individual trajectories [e.g., typical vs. late talkers, @beckage2011]. Moreover, the results obtained in this study provide correlational but not causal evidence. Thus, conclusion drawn from our network analysis would require parallel evidence, especially through controlled behavioral experiments.

# Acknowledgements

This work was supported by a post-doctoral grant from the Fyssen Foundation.

# References

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent

### 2018-01-12 cogsci/cogsci.tex
first commit

--- 2018-01-12 cogsci/cogsci.Rmd
@@
----
-title: "The Role of Early Semantic and Phonological Networks in Noun Learning: a Cross-linguistic Analysis"
+% Template for Cogsci submission with R Markdown
 
-bibliography: library.bib
-csl: apa6.csl
-document-params: "10pt, letterpaper"
+% Stuff changed from original Markdown PLOS Template
+\documentclass[10pt, letterpaper]{article}
 
-author-information: > 
-    \author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University
-    \And {\large \bf Yuan Bian} \\ \texttt{ybian.uiuc@gmail.com} \\ Department of Psychology \\ University of Illinois
-    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
+\usepackage{cogsci}
+\usepackage{pslatex}
+\usepackage{float}
+\usepackage{caption}
 
-abstract: 
-    "Children tend to learn first the words that have a high density neighborhood in the lexical network (i.e., words that are connected to a variety of other words).
-However, the reason why connectivity influences learning is still not very well understood.
-Previous studies suggested this effect could be the consequence of the underlying learning mechanism.
-However, these studies focused on semantic networks and English data only, thus severely limiting the generality of the findings.
-Here we provide a systematic analysis of network growth models in both the phonological and the the semantic domains, and across 8 languages.
-We replicate the results obtained by Hills et al.
-(2009) with English semantic networks, show that the same  mechanism drives the growth of both semantic and phonological networks, and demonstrate that these effects hold cross-linguistically."
+% amsmath package, useful for mathematical formulas
+\usepackage{amsmath}
 
-keywords:
-    "keywords: semantic network, phonological network, word learning, semantic "
+% amssymb package, useful for mathematical symbols
+\usepackage{amssymb}
 
-output: cogsci2016::cogsci_paper
----
+% hyperref package, useful for hyperlinks
+\usepackage{hyperref}
 
-```{r global_options, include=FALSE}
-rm(list=ls())
+% graphicx package, useful for including eps and pdf graphics
+% include graphics with the command \includegraphics
+\usepackage{graphicx}
 
-#knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
-#                      echo=F, warning=F, cache=F, message=F, sanitize = T)
+% Sweave(-like)
+\usepackage{fancyvrb}
+\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
+\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
+\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
+\newenvironment{Schunk}{}{}
+\DefineVerbatimEnvironment{Code}{Verbatim}{}
+\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
+\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
+\newenvironment{CodeChunk}{}{}
 
-knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=F, message=F, sanitize = T)
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
 
-```
+\usepackage{color}
 
-```{r, libraries}
-library(png)
-library(grid)
-library(ggplot2)
-library(xtable)
-options(xtable.comment = FALSE)
-library(purrr)
-library(readr)
-library(ggplot2)
-library(langcog)
-library(boot)
-#library(lazyeval)
-library(dplyr)
-library(tidyr)
-library(wordbankr)
-library(directlabels)
-#library(scales)
-library(stringr)
-library(lmtest)
-library(rwebppl)
-library(jsonlite)
-library(nlme)
-library(feather)
-library(broom)
-library(HDInterval)
-library(BBmisc)
-```
+% Use doublespacing - comment out for single spacing
+%\usepackage{setspace}
+%\doublespacing
 
-# Introduction
+% % Text layout
+% \topmargin 0.0cm
+% \oddsidemargin 0.5cm
+% \evensidemargin 0.5cm
+% \textwidth 16cm
+% \textheight 21cm
 
-A crucial question in language development is to understand why children learn some words at an earlier age than others.
-Previous studies documented various word properties that influence the age of acquisition.
-For example, it was shown that, within a lexical category, words that are more frequent in child-directed speech are acquired earlier [@goodman2008].
-Other predictors include word length, the mean length of utterances in which the word occurs, and how concrete the word is [see @braginsky2016].
-Besides these word-level properties, researchers found that the lexical structure (that is, the network that specifies how words relate to each other) also influences the learning process.
-For instance, children tend to produce first the words that have higher neighborhood density (i.g., high connectivity in the network) both at the phonological and the semantic level [@stokes2010; @storkel2009].
-However, it is still not very well understood *why* connectivity in the lexical structure influences learning.
-@steyvers2005 suggested that this effect is nothing but the consequence of how these structures get constructed in the child's mind.
-According to this explanation (known as Preferential Attachment), highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario.
-Nonetheless, @hills2009 found that what biases the learning is not the connectivity in the child's internal lexicon but the connectivity in the learning environment.
+\title{The Role of Early Semantic and Phonological Networks in Noun Learning: a
+Cross-linguistic Analysis}
 
-These analyses, however, focused on growth in semantic networks only.
-A recent study by @stella2017 analysed both semantic and phonological connectivity, but assumed only one growth model (preferential acquisition).
-More importantly, almost all available studies are limited in their generality because they focus almost exlusively on English data.
-The novely of this study is that it investigtes, for the first time, whether phonological networks grow by preferential attachement or preferential acquisition.
-It also provides a systematic comparision between network growth scenarios in both the phonological and the semantic domains and assess their relative contribution to the learning process.
-Moreover, it tests the generality of the findings across eight languages.
+\author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Yuan Bian} \\ \texttt{ybian.uiuc@gmail.com} \\ Department of Psychology \\ University of Illinois \And {\large \bf Michael C.
+Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
 
-The paper is organized as follows.
-First, we describe the dataset we used, the procedure we followed to construct both semantic and phonological networks, and the network growth scenarios we tested.
-Next, we show the results of the various analyses we conducted comparing network growth scenarios across languages.
-Then we compare the overall contribution of the networks in the learning process relative to other known predictors of age of acquisition (frequency and length).
-Finally we discuss the major results in relation to known experimental facts in language development.
+\begin{document}
 
-```{r }
+\maketitle
 
-#Import data from saved
-data_all_scaled <- feather::read_feather("../saved_data/data_all_scaled.feather")
+\begin{abstract}
+Children tend to learn first the words that have a high density
+neighborhood in the lexical network (i.e., words that are connected to a
+variety of other words). However, the reason why connectivity influences
+learning is still not very well understood. Previous studies suggested
+this effect could be the consequence of the underlying learning
+mechanism. However, these studies focused on semantic networks and
+English data only, thus severely limiting the generality of the
+findings. Here we provide a systematic analysis of network growth models
+in both the phonological and the the semantic domains, and across 8
+languages. We replicate the results obtained by Hills et al. (2009) with
+English semantic networks, show that the same mechanism drives the
+growth of both semantic and phonological networks, and demonstrate that
+these effects hold cross-linguistically.
 
-#tidy data
-data_long <- data_all_scaled %>%
-  gather(predictor, value, length:freq_mika)
+\textbf{Keywords:}
+keywords: semantic network, phonological network, word learning,
+semantic
+\end{abstract}
 
-data_long <- data_long %>%
-  #filter(predictor %in% c("PAC_assoc", "PAC_phono_t2", "freq_mika", "length")) %>%
-  filter(predictor %in% c("PAC_assoc", "PAC_phono_t2"))
+\section{Introduction}\label{introduction}
 
-data_long$predictor <- mapValues(data_long$predictor, 
-                                 from = c("PAC_assoc", "PAC_phono_t2"), 
-                                 to = c("Sem.", "Phono."))
+A crucial question in language development is to understand why children
+learn some words at an earlier age than others. Previous studies
+documented various word properties that influence the age of
+acquisition. For example, it was shown that, within a lexical category,
+words that are more frequent in child-directed speech are acquired
+earlier (Goodman, Dale, \& Li, 2008). Other predictors include word
+length, the mean length of utterances in which the word occurs, and how
+concrete the word is (see Braginsky, Yurovsky, Marchman, \& Frank,
+2016). Besides these word-level properties, researchers found that the
+lexical structure (that is, the network that specifies how words relate
+to each other) also influences the learning process. For instance,
+children tend to produce first the words that have higher neighborhood
+density (i.g., high connectivity in the network) both at the
+phonological and the semantic level (Stokes, 2010; Storkel, 2009).
+However, it is still not very well understood \emph{why} connectivity in
+the lexical structure influences learning. Steyvers \& Tenenbaum (2005)
+suggested that this effect is nothing but the consequence of how these
+structures get constructed in the child's mind. According to this
+explanation (known as Preferential Attachment), highly connected words
+in the child's lexicon tend to ``attract'' more words over time, in a
+rich-get-richer scenario. Nonetheless, Hills, Maouene, Maouene, Sheya,
+\& Smith (2009) found that what biases the learning is not the
+connectivity in the child's internal lexicon but the connectivity in the
+learning environment.
 
-plot_data_all <- ggplot(data_long, aes(x=value, y=AoA))+
-  facet_grid(predictor ~ language)+#, scales = "free") +
-  geom_jitter(#aes(colour = lexical_class),
-    colour = solarized_palette(1),
-    size = 0.5, alpha = 0.5) +
-  coord_cartesian(xlim=c(-2,5))+
-  #scale_x_continuous(limits=c(-2,5))+
-  scale_y_continuous(breaks =c(15,25,35))+
-  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
-  scale_colour_solarized(name = "") +
-  theme_bw()+
-  theme(aspect.ratio = 0.7, 
-        plot.margin=grid::unit(c(0,0,0,0), "mm")
-        )+
-  xlab("degree z-score") +ylab("AoA")
+These analyses, however, focused on growth in semantic networks only. A
+recent study by Stella, Beckage, \& Brede (2017) analysed both semantic
+and phonological connectivity, but assumed only one growth model
+(preferential acquisition). More importantly, almost all available
+studies are limited in their generality because they focus almost
+exlusively on English data. The novely of this study is that it
+investigtes, for the first time, whether phonological networks grow by
+preferential attachement or preferential acquisition. It also provides a
+systematic comparision between network growth scenarios in both the
+phonological and the semantic domains and assess their relative
+contribution to the learning process. Moreover, it tests the generality
+of the findings across eight languages.
 
-ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)
+The paper is organized as follows. First, we describe the dataset we
+used, the procedure we followed to construct both semantic and
+phonological networks, and the network growth scenarios we tested. Next,
+we show the results of the various analyses we conducted comparing
+network growth scenarios across languages. Then we compare the overall
+contribution of the networks in the learning process relative to other
+known predictors of age of acquisition (frequency and length). Finally
+we discuss the major results in relation to known experimental facts in
+language development.
 
-```
+\begin{CodeChunk}
+\begin{figure*}[h]
 
-```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the end-state network as predicted by the degree in this network.
+{\centering \includegraphics{figs/all_data-1}
+
+}
+
+\caption{\label{fig:data_all}Age of acquisition in the end-state network as predicted by the degree in this network.
 Results are shown in each language for the phonological network (top) and the semantic network (bottom).
-Each point is a word, with lines indicating linear model fits."}
-plot_data_all
-#img <- png::readPNG("figs/data_all.png")
-#grid::grid.raster(img)
+Each point is a word, with lines indicating linear model fits.}\label{fig:all_data}
+\end{figure*}
+\end{CodeChunk}
 
-```
+\section{Networks}\label{networks}
 
-# Networks
+\subsection{Data}\label{data}
 
-## Data
+We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
+2017), an open repository aggregating cross-linguistic language
+developmental data of the MacArthur-Bates Communicative Development
+Inventory (CDI). The latter consists of parent report vocabulary
+checklists. We used the \emph{Words and Sentence} version which contains
+the productive vocabulary of toddlers (age varied between 16 to 35
+months). We included words that were produced by at least 50\% of
+children, and we considered that these words were learned at the month
+when this percentage was reached (Goodman et al., 2008). Moreover,
+following previous studies (Hills et al., 2009; e.g., Storkel, 2009), we
+restricted the analysis to the category of nouns, since there are known
+discrepancies between the learning of nouns, predicates, and function
+words (e.g., Braginsky et al., 2016). We obtained these nouns in eight
+languages: Croatian, Danish, English, Italian, Norwegian, Russian,
+Spanish, and Turkish. We used the subset of nouns that had entries in
+the Florida Association Norms (see below). Since these norms are
+available only in English, we mapped words onto translation equivalents
+across CDI forms. This allowed us to use the English association norms
+across languages. Table \ref{tab:stats} gives an overview of the data
+used. The translation of non-English words is still an ongoing process.
+Note, however, that all languages have at least 60\% of nouns
+translated.
 
-We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI).
-The latter consists of parent report vocabulary checklists.
-We used the *Words and Sentence* version which contains the productive vocabulary of toddlers (age varied between 16 to 35 months).
-We included words that were produced by at least 50% of children, and we considered that these words were learned at the month when this percentage was reached [@goodman2008].
-Moreover, following previous studies [e.g., @storkel2009; @hills2009], we restricted the analysis to the category of nouns, since there are known discrepancies between the learning of nouns, predicates, and function words [e.g., @braginsky2016].
-We obtained these nouns in eight languages: Croatian, Danish, English, Italian, Norwegian, Russian, Spanish, and Turkish.
-We used the subset of nouns that had entries in the Florida Association Norms (see below).
-Since these norms are available only in English, we mapped words onto translation equivalents across CDI forms.
-This allowed us to use the English association norms across languages.
-Table \ref{tab:stats} gives an overview of the data used.
-The translation of non-English words is still an ongoing process.
-Note, however, that all languages have at least 60% of nouns translated.
-
-```{r stats, results="asis", echo=FALSE}
-
-statistics <- feather::read_feather("../saved_data/statistics.feather")
-rownames(statistics) <- NULL
-
-tab <- xtable::xtable(statistics,
-                      caption = "\\label{tab:stats}Total number of productive nouns in the CDI (left).
-We used a subset of these nouns that have available English translations (middle), as well as entries in the Free Association Norms (right).")
-
-print(tab, type="latex", comment = F, table.placement = "H")
-
-#print(statistics, type="latex", comment = F, table.placement = "H")
-```
+\begin{table}[H]
+\centering
+\begin{tabular}{rlrrr}
+  \hline
+ & language & total & translated & normed \\ 
+  \hline
+1 & Croatian & 253 & 177 & 170 \\ 
+  2 & Danish & 295 & 198 & 187 \\ 
+  3 & English & 296 & 296 & 274 \\ 
+  4 & Italian & 311 & 203 & 194 \\ 
+  5 & Norwegian & 305 & 193 & 186 \\ 
+  6 & Russian & 311 & 311 & 285 \\ 
+  7 & Spanish & 240 & 173 & 163 \\ 
+  8 & Turkish & 293 & 175 & 164 \\ 
+   \hline
+\end{tabular}
+\caption{\label{tab:stats}Total number of productive nouns in the CDI (left).
+We used a subset of these nouns that have available English translations (middle), as well as entries in the Free Association Norms (right).}
+\end{table}
 
@@
 
-## Semantic networks
+\subsection{Semantic networks}\label{semantic-networks}
 
-We used as index of semantic relatedness the Florida Free Association Norms [@nelson1998].
-This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target).
-For example, when given the word "ball", they might answer with the word "game".
-A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms.
-Each node was characterized by its "indegree", which represents the number of links for which the word was the target.
-Following @hills2009, we used as a proxy for the learning environment, the network constructed using the full CDI data in each language (e.g., in English this corresponds to the network by 30 months).
+We used as index of semantic relatedness the Florida Free Association
+Norms (Nelson, McEvoy, \& Schreiber, 1998). This dataset was collected
+by giving adult participants a word (the cue), and asking them to write
+the first word that comes to mind (the target). For example, when given
+the word ``ball'', they might answer with the word ``game''. A pair of
+nodes were connected by a directed link from the cue to the target if
+there was a cue-target relationship between these nodes in the
+association norms. Each node was characterized by its ``indegree'',
+which represents the number of links for which the word was the target.
+Following Hills et al. (2009), we used as a proxy for the learning
+environment, the network constructed using the full CDI data in each
+language (e.g., in English this corresponds to the network by 30
+months).
 
-```{r }
+\begin{CodeChunk}
+\begin{figure*}[h]
 
-#Import data from saved
-individual_both <- feather::read_feather("../saved_data/individual_both.feather")
+{\centering \includegraphics{figs/pred_ind_img-1}
 
-pred_ind <- ggplot(individual_both, aes(x = model , y = mean)) +
-  geom_pointrange(aes(ymin = lower, ymax = upper, col = model, linetype=Evaluation),
-                  position = position_dodge(width = .5),
-                  size = 0.5,
-                  fatten = 0.5)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  coord_flip() +
-  facet_wrap(~language, ncol=4)  +
-  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
-  scale_colour_solarized() +
-  theme_bw()+
-  theme(aspect.ratio = 0.7)
+}
 
-ggsave("figs/pred_ind.png", plot = pred_ind, width = 8, height = 4)
+\caption{\label{fig:pred_ind}Evaluation of individual network growth models using both  one-sample t-test over the z-score distribution of learned words (dotted), and model fitting (solid).
+Each dot represents, in the first case, the mean of the z-score distribution of the learned words with ranges representing 95\% confidence interval, and in the second case, the mean of the posterior distribution of the model's parameter, with ranges reppresenting 95\% credible intervals (computed using the highest density intervals).}\label{fig:pred_ind_img}
+\end{figure*}
+\end{CodeChunk}
 
-```
+\subsection{Phonological networks}\label{phonological-networks}
 
-```{r pred_ind_img, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3.5, fig.align = "center", fig.cap = "\\label{fig:pred_ind}Evaluation of individual network growth models using both  one-sample t-test over the z-score distribution of learned words (dotted), and model fitting (solid).
-Each dot represents, in the first case, the mean of the z-score distribution of the learned words with ranges representing 95\\% confidence interval, and in the second case, the mean of the posterior distribution of the model's parameter, with ranges reppresenting 95\\% credible intervals (computed using the highest density intervals)."}
+We used as a measure of phonological relatedness between two nodes the
+Levenshtein (edit) distance between their phonological forms. The
+measure counts the minimum number of operations (insertions, deletions,
+substitutions) required to change one string into another. We generated
+approximate IPA forms from the orthographic transcription, across
+languages, using the open source text-to-speech software
+\textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.}. In
+previous studies, two nodes were linked if they had an edit distance of
+1 (Stokes, 2010; Storkel, 2009). However, in these previous studies the
+network was built using an adult vocabulary. Here, similar to the
+approximation we made for the semantic network, we used the full set of
+nouns in the CDI data as a proxy for phonological connectivity in the
+learning environment. However, since the children's vocabulary contains
+very few word pairs with an edit distance of 1, the resulting network
+was too sparse and uninformative. Thus, we increased the threshold from
+1 to 2, that is, two node were related if their edit distance was equal
+to 1 or 2. Each node was characterized with its degree, i.e., the number
+of links it shares with other words.
 
-pred_ind
+\subsection{Network growth}\label{network-growth}
 
-#img <- png::readPNG("figs/pred_ind.png")
-#grid::grid.raster(img)
-```
+We tested two network growth scenarios discussed in Hills et al. (2009).
+The first one was \emph{Preferential Attachment} (PAT). According to
+this mechanism, the network structure of known words predicts what words
+will be learned next. A word is more likely to be learned if it is
+linked to one of the highly connected nodes in this internal network.
+The second mechanism was \emph{Preferential Acquisition} (PAC). In this
+model, what predicts what word will enter the lexicon is not
+connectivity in the internal network, but connectivity in the learning
+environment. Figure \ref{fig:growth} shows an illustration of both
+growth scenarios with the same simplified network. For PAT, each
+candidate node was characterized with the average degree of the existing
+nodes that it would attach to. Thus, according to PAT, the node N1 is
+more likely to enter the lexicon first. For PAC, each candidate node was
+characterized with its degree in the entire network. According th PAC,
+the node N3 is more likely to enter the lexicon first.
 
-## Phonological networks
+\begin{CodeChunk}
+\begin{figure}[H]
 
-We used as a measure of phonological relatedness between two nodes the Levenshtein (edit) distance between their phonological forms.
-The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.
-We generated approximate IPA forms from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).**.
-In previous studies, two nodes were linked if they had an edit distance of 1 [@stokes2010; @storkel2009].
-However, in these previous studies the network was built using an adult vocabulary.
-Here, similar to the approximation we made for the semantic network, we used the full set of nouns in the CDI data as a proxy for phonological connectivity in the learning environment.
-However, since the children's vocabulary contains very few word pairs with an edit distance of 1, the resulting network was too sparse and uninformative.
-Thus, we increased the threshold from 1 to 2, that is, two node were related if their edit distance was equal to 1 or 2.
-Each node was characterized with its degree, i.e., the number of links it shares with other words.
+{\centering \includegraphics{figs/growth-1}
 
-## Network growth
+}
 
-We tested two network growth scenarios discussed in @hills2009.
-The first one was *Preferential Attachment* (PAT).
-According to this mechanism, the network structure of known words predicts what words will be learned next.
-A word is more likely to be learned if it is linked to one of the highly connected nodes in this internal network.
-The second mechanism was *Preferential Acquisition* (PAC).
-In this model, what predicts what word will enter the lexicon is not connectivity in the internal network, but connectivity in the learning environment.
-Figure \ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network.
-For PAT, each candidate node was characterized with the average degree of the existing nodes that it would attach to.
-Thus, according to PAT, the node N1 is more likely to enter the lexicon first.
-For PAC, each candidate node was characterized with its degree in the entire network.
-According th PAC, the node N3 is more likely to enter the lexicon first.
-
-```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Illustration of the two growth models with the same network.
+\caption{\label{fig:growth}Illustration of the two growth models with the same network.
 Filled circles (A to D) represent known words, and empty circles (N1 to N3) represent words that have not been learned yet.
 Back lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant (from Hills et al.
-2009)."}
+2009).}\label{fig:growth}
+\end{figure}
+\end{CodeChunk}
 
-img <- png::readPNG("figs/growth.png")
-grid::grid.raster(img)
+\section{Analysis}\label{analysis}
 
-```
+\subsection{Connectivity vs.~Age of
+acquisition}\label{connectivity-vs.age-of-acquisition}
 
-# Analysis
+Preferential attachment and preferential acquisition provide different
+generative scenarios for the same end-state. The latter is defined here
+as the network corresponding to the oldest age for which we have CDI
+data. However in both cases, it is predicted that nodes with the higher
+degrees in this end-state are learned earlier than nodes with the lower
+degrees. Figure \ref{fig:data_all} shows how the age of acquisition for
+each word varies as a function of its degree (or indegree for the
+semantic network) in the end-state network. In order to compare this
+correlation across languages, the predictor (i.e., the degree) was
+centered and scaled. The plot shows a negative correlation between the
+month of acquisition and the degree (with the exception of the Russian
+semantic network), indicating that nouns with higher degrees are
+generally learned earlier.
 
-## Connectivity vs. Age of acquisition
+\begin{CodeChunk}
+\begin{figure*}[h]
 
-Preferential attachment and preferential acquisition provide different generative scenarios for the same end-state.
-The latter is defined here as the network corresponding to the oldest age for which we have CDI data.
-However in both cases, it is predicted that nodes with the higher degrees in this end-state are learned earlier than nodes with the lower degrees.
-Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network) in the end-state network.
-In order to compare this correlation across languages, the predictor (i.e., the degree) was centered and scaled.
-The plot shows a negative correlation between the month of acquisition and the degree (with the exception of the Russian semantic network), indicating that nouns with higher degrees are generally learned earlier.
+{\centering \includegraphics{figs/pred_comb_img-1}
 
-```{r }
+}
 
-#Import data from saved
-post_combined <- feather::read_feather("../saved_data/combined_net.feather")
+\caption{\label{fig:pred_comb_img}Estimates of the growth models' parameters in each language.
+Dots represent the means of the posteriori distribution of the parameters, and ranges represent 95\% credible intervals (computed using the highest density intervals).
+}\label{fig:pred_comb_img}
+\end{figure*}
+\end{CodeChunk}
 
-pred_comb <- ggplot(post_combined, aes(x = model, y = mean)) +
-  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, y = mean, col = model), size=0.3)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  coord_flip() +
-  facet_wrap(~language, ncol=4)  +
-  guides(colour=FALSE)+
-  scale_colour_solarized() +
-  theme_bw()+
-  theme(aspect.ratio = 0.7)
+\subsection{Network growth models}\label{network-growth-models}
 
-ggsave("figs/pred_comb.png", plot = pred_comb, width = 8, height = 4)
-```
-
-```{r pred_comb_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:pred_comb_img}Estimates of the growth models' parameters in each language.
-Dots represent the means of the posteriori distribution of the parameters, and ranges represent 95\\% credible intervals (computed using the highest density intervals).
-"}
-pred_comb
-#img <- png::readPNG("figs/pred_comb.png")
-#grid::grid.raster(img)
-```
-
-## Network growth models
-
-Following @hills2009, we evaluated the growth models in two separate ways.
-The first evaluation consists in determining, in each month, the model-dependent growth value distribution of all words that could possibly be learned at this month, and then computing the z-score of each learned word with respect to this distribution.
-For each model, we tested if the distribution constituted by the z-scores of all learned words was different from zero, using a one-sample t-test.
-The results are shown in Figure \ref{fig:pred_ind}.
+Following Hills et al. (2009), we evaluated the growth models in two
+separate ways. The first evaluation consists in determining, in each
+month, the model-dependent growth value distribution of all words that
+could possibly be learned at this month, and then computing the z-score
+of each learned word with respect to this distribution. For each model,
+we tested if the distribution constituted by the z-scores of all learned
+words was different from zero, using a one-sample t-test. The results
+are shown in Figure \ref{fig:pred_ind}.
 
 The second evaluation consists in fitting an explicit model to the data.
-The purpose of this second evaluation is, first, to validate the findings obtained with the one-sample t-test, and second, to determine (in a next step) the relative contribution of each network growth scenario (PAT vs.
-PAC) across domains (phonological vs.
-semantic).
+The purpose of this second evaluation is, first, to validate the
+findings obtained with the one-sample t-test, and second, to determine
+(in a next step) the relative contribution of each network growth
+scenario (PAT vs.~PAC) across domains (phonological vs.~semantic).
 
-We proceeded as follows. We calculated the probability that a word $w_i$, with a growth value $d_i$ would enter the lexicon at a given month, using a softmax function: 
+We proceeded as follows. We calculated the probability that a word
+\(w_i\), with a growth value \(d_i\) would enter the lexicon at a given
+month, using a softmax function:
+
 \begin{equation}
@@
 
-Where $\beta$ is the fitting parameter.
-A positive value of $\beta$ means that words with higher groth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first.
-The normalization included words that were not yet learned at the month the word at hand was acquired.
-We estimated the parameter $\beta$ using a Bayesian approach.
-We started with a uniform distribution, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been actually learned at that month (using formula 1).
-We ended up with a posterior distribution of $\beta$, which we summarized in Figure \ref{fig:pred_ind}.
+Where \(\beta\) is the fitting parameter. A positive value of \(\beta\)
+means that words with higher groth values \(d_i\) are acquired first,
+and a negative value means that words with lower growth values are
+acquired first. The normalization included words that were not yet
+learned at the month the word at hand was acquired. We estimated the
+parameter \(\beta\) using a Bayesian approach. We started with a uniform
+distribution, and at each month, we computed the likelihood function
+over words that could possibly enter the lexicon at that month, fit to
+the words that have been actually learned at that month (using formula
+1). We ended up with a posterior distribution of \(\beta\), which we
+summarized in Figure \ref{fig:pred_ind}.
 
-The results from both evaluations were very similar and lead essentially to the same conclusions.
-For the semantic networks, the results replicate Hills et al.'s finding in English, which was that the semantic network grows by PAC, not by PAT.
-Moreover, it generalizes this finding to all other languages (with the exception of Russian).
-For the phonological network, the results show that, generally speaking, PAC fits the developmental trajectory better than PAT in all languages.
-We note however that PAT, though weaker, fares  better for the phonological networks than it does for the semantic networks.
-In the former, it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian.
-In the latter, it is rather universally unpredictive.
+The results from both evaluations were very similar and lead essentially
+to the same conclusions. For the semantic networks, the results
+replicate Hills et al.'s finding in English, which was that the semantic
+network grows by PAC, not by PAT. Moreover, it generalizes this finding
+to all other languages (with the exception of Russian). For the
+phonological network, the results show that, generally speaking, PAC
+fits the developmental trajectory better than PAT in all languages. We
+note however that PAT, though weaker, fares better for the phonological
+networks than it does for the semantic networks. In the former, it
+predicts part of the growth process in some languages such as Croatian,
+English, Norwegian and Russian. In the latter, it is rather universally
+unpredictive.
 
-Above we evaluated the network growth scenarios individually.
-As a next step, we analysed their relative contribution to the learning process.
-This was done through adding more fitting parameters to the model, that is, by substituting $\beta d_i$ in equation (1) with: $$\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}$$ where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and PhonoPAC.
-Using the same fitting technique, we obtained the values shown in Figure \ref{fig:pred_comb_img}.
-In term of growth scenarios, we found that PAC dominates the learning.
-In particular, though we found previously that phonological PAT predicted part of the learning in some languages when tested individually, here PAT appears to lose its predictive power when pitted against phonological PAC.
-In terms of domain (phonological vs.
-semantic), both phonological and semantic networks appear to contribute to learning, although the phonological network appears to be stronger and more reliable across languages.
-In summary, the findings show that both semantic and phonological networks grow primarily through preferential acquisition, and that, generally speaking, semantic and phonological networks both contribute to the learning process.
+Above we evaluated the network growth scenarios individually. As a next
+step, we analysed their relative contribution to the learning process.
+This was done through adding more fitting parameters to the model, that
+is, by substituting \(\beta d_i\) in equation (1) with:
+\[\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}\]
+where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and
+PhonoPAC. Using the same fitting technique, we obtained the values shown
+in Figure \ref{fig:pred_comb_img}. In term of growth scenarios, we found
+that PAC dominates the learning. In particular, though we found
+previously that phonological PAT predicted part of the learning in some
+languages when tested individually, here PAT appears to lose its
+predictive power when pitted against phonological PAC. In terms of
+domain (phonological vs.~semantic), both phonological and semantic
+networks appear to contribute to learning, although the phonological
+network appears to be stronger and more reliable across languages. In
+summary, the findings show that both semantic and phonological networks
+grow primarily through preferential acquisition, and that, generally
+speaking, semantic and phonological networks both contribute to the
+learning process.
 
-```{r }
+\begin{CodeChunk}
+\begin{figure*}[h]
 
-#Import data from saved
-regressions <- feather::read_feather("../saved_data/regressions_bis.feather")
+{\centering \includegraphics{figs/regressions_img-1}
 
-pred_regressions <- ggplot(regressions, aes(x = predictor, y = estimate)) +
-  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor), size=0.3)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  facet_wrap(~language, ncol=4)  +
-  coord_flip() +
-  guides(colour=FALSE)+
-  scale_colour_solarized() +
-  theme_bw()+
-  theme(aspect.ratio = 0.7)
+}
 
-ggsave("figs/pred_regressions.png", plot = pred_regressions, width = 8, height = 4)
-```
-
-```{r regressions_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:regressions_img}Estimates of predictor coefficients by language.
+\caption{\label{fig:regressions_img}Estimates of predictor coefficients by language.
 Values above 0 indicate a positive relationship (e.g.
@@
 words with higher frequency tend to have a lower AoA).
-Ranges indicate 95\\% confidence intervals."}
+Ranges indicate 95\% confidence intervals.}\label{fig:regressions_img}
+\end{figure*}
+\end{CodeChunk}
 
-pred_regressions
+\subsection{The big picture: comparison to other known predictors of age
+of
+acquisition}\label{the-big-picture-comparison-to-other-known-predictors-of-age-of-acquisition}
 
-#img <- png::readPNG("figs/pred_regressions.png")
-#grid::grid.raster(img)
-```
+We saw that the way semantic and phonological information is structured
+in the learning environment (i.e., PAC) contribute to noun learning
+across languages. However, we know that other factors influence learning
+as well (e.g., Braginsky et al., 2016). In what follows, we will
+investigate how semantic and phonological connectivity interact with two
+other factors. The first one is word frequency, a well studied factor
+shown to predict the age of acquisition in a reliable fashion (e.g.
+Goodman et al., 2008). The second factor is word length because it
+correlates with phonological connectivity (Pisoni, Nusbaum, Luce, \&
+Slowiaczek, 1985).
 
-## The big picture: comparison to other known predictors of age of acquisition
+Since PAT was uninformative, we dropped it from this analysis. Thus, we
+no longer needed to to fit the growth model month-by-month as in the
+previous section. In fact, word utilities in the case of PAC are fixed,
+they do not depend on previously learned words. A more direct way to
+assess and compare the contribution of PAC in relation to other factors
+is through conducting linear regressions, where connectivity in the
+learning environment (at both the phonological and semantic level),
+frequency and length predict the age of acquisition.
 
-We saw that the way semantic and phonological information is structured in the learning environment (i.e., PAC) contribute to noun learning across languages.
-However, we know that other factors influence learning as well [e.g., @braginsky2016].
-In what follows, we will investigate how semantic and phonological connectivity interact with two other factors.
-The first one is word frequency, a well studied factor shown to predict the age of acquisition in a reliable fashion [e.g.
-@goodman2008].
-The second factor is word length because it correlates with phonological connectivity [@pisoni1985].
+We used the frequency estimates from Braginsky et al. (2016) where
+unigram counts were derived based on CHILDES corpora in each language.
+For each word, counts included words that shared the same stem (e.g.,
+cats counts as cat), or words that were synonymous (e.g.~father counts
+as daddy). For word length, we used our generated IPA transcription.
+This allowed us to get a more accurate estimate of word length across
+languages than the number of characters in the orthographic
+transcription.
 
-Since PAT was uninformative, we dropped it from this analysis.
-Thus, we no longer needed to to fit the growth model month-by-month as in the previous section.
-In fact, word utilities in the case of PAC are fixed, they do not depend on previously learned words.
-A more direct way to assess and compare the contribution of PAC in relation to other factors is through conducting linear regressions, where connectivity in the learning environment (at both the phonological and semantic level), frequency and length predict the age of acquisition.
+\begin{CodeChunk}
+\begin{figure}[H]
 
-We used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language.
-For each word, counts included words that shared the same stem  (e.g., cats counts as cat), or words that were synonymous (e.g.
-father counts as daddy).
-For word length, we used our generated IPA transcription.
-This allowed us to get a more accurate estimate of word length across languages than the number of characters in the orthographic transcription.
+{\centering \includegraphics{figs/regressions_all_img-1}
 
-```{r }
+}
 
-#Import data from saved
-regression_all <- feather::read_feather("../saved_data/regression_all_bis.feather")
-regression_all_noCov <- feather::read_feather("../saved_data/regression_all_bis_noCov.feather")
+\caption{\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined model.
+Ranges indicate 95\% confidence intervals.
+Fade color indicates estimates of PAC predictors in a model that does not include frequency and length as covariates.}\label{fig:regressions_all_img}
+\end{figure}
+\end{CodeChunk}
 
-pred_regression_all <- ggplot(regression_all, aes(x = predictor, y = estimate)) +
-  geom_pointrange(aes(ymin = lower, ymax = upper, col = predictor), size=0.3)+
-  geom_pointrange(data=regression_all_noCov,
-                  aes(ymin = lower, ymax = upper, col = predictor),
-                  position = position_dodge(width = .3),
-                  linetype=1,
-                  size = 0.7,
-                  fatten = 1.5,
-                  alpha = 0.3)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  coord_flip() +
-  guides(colour=FALSE)+
-  scale_colour_solarized() +
-  theme_bw()+
-  theme(aspect.ratio = 0.7)
-
-ggsave("figs/pred_regression_all.png", plot = pred_regression_all, width = 4, height = 2)
-```
-
-```{r regressions_all_img, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, fig.cap = "\\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined model.
-Ranges indicate 95\\% confidence intervals.
-Fade color indicates estimates of PAC predictors in a model that does not include frequency and length as covariates."}
-
-pred_regression_all
-
-#img <- png::readPNG("figs/pred_regression_all.png")
-#grid::grid.raster(img)
-```
-
-We conducted two analyses.
-On the one had, we fit a linear regression for each language, and on the other hand, we fit a linear mixed-effect to all the data pooled across languages, with language as a random effect.
-Figure \ref{fig:regressions_img} shows the coefficient estimate for each predictor in each language, and figure \ref{fig:regressions_all_img} shows the coefficient estimates for all languages combined (all predictors were centered and scaled).
-The findings were as follows.
-Overall, frequency is the most reliable predictor of age of acquisition.
-Word length predicts part of learning in some languages such as Croatian and Norwegian, but not in others (including English).
-It remains, however, a significant predictor in the global model.
-As for the factors of interest, i.e., semantic and phonological connectivities, we also found cross-linguistic differences.
-The phonological connectivity contributes to learning in languages such as Croatian, English and Russian, whereas semantic connectivity contributes to learning in Turkish, Spanish and to some extent in Croatian, but interestingly not in English\footnote{Semantic connectivity does not explain variance in English data beyond that explained by frequency and length.
+We conducted two analyses. On the one had, we fit a linear regression
+for each language, and on the other hand, we fit a linear mixed-effect
+to all the data pooled across languages, with language as a random
+effect. Figure \ref{fig:regressions_img} shows the coefficient estimate
+for each predictor in each language, and figure
+\ref{fig:regressions_all_img} shows the coefficient estimates for all
+languages combined (all predictors were centered and scaled). The
+findings were as follows. Overall, frequency is the most reliable
+predictor of age of acquisition. Word length predicts part of learning
+in some languages such as Croatian and Norwegian, but not in others
+(including English). It remains, however, a significant predictor in the
+global model. As for the factors of interest, i.e., semantic and
+phonological connectivities, we also found cross-linguistic differences.
+The phonological connectivity contributes to learning in languages such
+as Croatian, English and Russian, whereas semantic connectivity
+contributes to learning in Turkish, Spanish and to some extent in
+Croatian, but interestingly not in
+English\footnote{Semantic connectivity does not explain variance in English data beyond that explained by frequency and length.
 This contrasts with the original finding in Hills et al.
@@
 Morever, our sample size is bigger.}.
-Despite this cross-linguistic variation, both phonological and semantic connectivity remain significant predictors in the global model.
+Despite this cross-linguistic variation, both phonological and semantic
+connectivity remain significant predictors in the global model.
 
-# Discussion
+\section{Discussion}\label{discussion}
 
-The present study provided a comprehensive analysis of how lexical connectivity influences the age of acquisition of nouns in toddlers.
-We compared two network growth scenarios and assessed the relative contribution of phonological and semantic information in 8 languages.
-Part of the findings largely replicate the results obtained in @hills2009, i.e., semantic networks (based on free associations) grow by preferential acquisition, not by preferential attachment.
-Another finding was that phonological networks also grow primarily by preferential acquisition, especially when both scenarios (PAT and PAC) were pitted against each other in the same model.
-These findings generalize well across languages.
-Moreoever, both semantic and phonological connectivity in the learning environment (i.e., PAC) predict growth in a consistent way across many languages.
-However, when pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting part of learning in some languages, but not in others.
-Despite this coross-lingusitic variation, both phonological and semantic connectivity contribute to the overall learning (when data is pooled across languages).
+The present study provided a comprehensive analysis of how lexical
+connectivity influences the age of acquisition of nouns in toddlers. We
+compared two network growth scenarios and assessed the relative
+contribution of phonological and semantic information in 8 languages.
+Part of the findings largely replicate the results obtained in Hills et
+al. (2009), i.e., semantic networks (based on free associations) grow by
+preferential acquisition, not by preferential attachment. Another
+finding was that phonological networks also grow primarily by
+preferential acquisition, especially when both scenarios (PAT and PAC)
+were pitted against each other in the same model. These findings
+generalize well across languages. Moreoever, both semantic and
+phonological connectivity in the learning environment (i.e., PAC)
+predict growth in a consistent way across many languages. However, when
+pitted against other known predictors of age of acquisition (word
+frequency and length), the effect of word connectivity shows a
+cross-linguistic variation, predicting part of learning in some
+languages, but not in others. Despite this coross-lingusitic variation,
+both phonological and semantic connectivity contribute to the overall
+learning (when data is pooled across languages).
 
-A major results of the study is that children start by learning words that have high phonological and semantic similarity with a variety of other words in the learning environment, not in the available lexicon.
-This suggests that children are sensitive to connectivity even without having first acquired the connected words!
-How can children indirectly detect highly connected words, and why would such words be more readily learned?
-In the semantic case, free association can be predicted through the patterns of word co-occurrence [@griffiths07], meaning that highly connected words tend to be the words that co-occur with many other words in various contexts.
-One possibility, suggested by @hills2010, is that the referents of such words are more easily disambiguated as demonstrated, for instance, by cross-situational learning experiments [@smith2008].
-In the phonological case, connectivity is inherently correlated with phonotactic probability [@vitevitch1999].
-That is, highly connected words tend to be made of frequent sound sequences.
-We know even infant (whose vocabulary is still very rudimentary) develop a sensitivity for high frequency sound sequences in the ambient native language [@jusczyk1994].
-Interestingly, it was shown that phonotactic probability facilitates learning and recognition of novel words in toddlers and preschoolers [@storkel2001;  @higgins2014].
-Thus, children's ability to keep track of co-occurrence statistics (both at the semantic and phonological level) might explain their sensitivity and preference for highly connected words in the learning envirnoment.
+A major results of the study is that children start by learning words
+that have high phonological and semantic similarity with a variety of
+other words in the learning environment, not in the available lexicon.
+This suggests that children are sensitive to connectivity even without
+having first acquired the connected words! How can children indirectly
+detect highly connected words, and why would such words be more readily
+learned? In the semantic case, free association can be predicted through
+the patterns of word co-occurrence (Griffiths, Steyvers, \& Tenenbaum,
+2007), meaning that highly connected words tend to be the words that
+co-occur with many other words in various contexts. One possibility,
+suggested by Hills, Maouene, Riordan, \& Smith (2010), is that the
+referents of such words are more easily disambiguated as demonstrated,
+for instance, by cross-situational learning experiments (Smith \& Yu,
+2008). In the phonological case, connectivity is inherently correlated
+with phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999).
+That is, highly connected words tend to be made of frequent sound
+sequences, and vice versa. We know even infant (whose vocabulary is
+still very rudimentary) develop a sensitivity for high frequency sound
+sequences in the ambient native language (Jusczyk, Luce, \&
+Charles-Luce, 1994). Interestingly, it was shown that phonotactic
+probability facilitates learning and recognition of novel words in
+toddlers and preschoolers (MacRoy-Higgins, Shafer, Schwartz, \& Marton,
+2014; Storkel, 2001). Thus, children's ability to keep track of
+co-occurrence statistics (both at the semantic and phonological level)
+might explain their apparent sensitivity and preference for high
+connectivity in the lexical network.
 
-Finally, this study shares a number of limitations with previous studies using similar datasets.
-For instance, we used normative age of acquisition.
-However, individual children may not follow a unique learning trajectory.
-The use of longitudinal data would allow us to assess how the aggregate behavior relates to individual trajectories [e.g., typical vs.
-late talkers, @beckage2011].
-Moreover, the results obtained in this study provide correlational but not causal evidence.
-Thus, conclusion drawn from our network analysis would require parallel evidence, especially through controlled behavioral experiments.
+Finally, this study shares a number of limitations with previous studies
+using similar datasets. For instance, we used normative age of
+acquisition. However, individual children may not follow a unique
+learning trajectory. The use of longitudinal data would allow us to
+assess how the aggregate behavior relates to individual trajectories
+(e.g., typical vs.~late talkers, Beckage, Smith, \& Hills, 2011).
+Moreover, the results obtained in this study provide correlational but
+not causal evidence. Thus, conclusion drawn from our network analysis
+would require parallel evidence, especially through controlled
+behavioral experiments.
 
-# Acknowledgements
+\section{Acknowledgements}\label{acknowledgements}
 
-This work was supported by a post-doctoral grant from the Fyssen Foundation.
+This work was supported by a post-doctoral grant from the Fyssen
+Foundation.
 
-# References
+\section{References}\label{references}
 
-```{r}
-# References will be generated automatically by Pandoc and included here.
-# The following code is some latex to format the bibliography. Do not remove it.
-```
+\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent
 
-\setlength{\parindent}{-0.1in} 
-\setlength{\leftskip}{0.125in}
-\noindent
+\hypertarget{refs}{}
+\hypertarget{ref-beckage2011}{}
+Beckage, N. M., Smith, L., \& Hills, T. T. (2011). Small worlds and
+semantic network growth in typical and late talkers. \emph{PLOS ONE},
+\emph{6}(5), 1--6.
+
+\hypertarget{ref-braginsky2016}{}
+Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (2016).
+From uh-oh to tomorrow: Predicting age of acquisition for early words
+across languages. In \emph{Proceedings of the 38th Annual Conference of
+the Cognitive Science Society}.
+
+\hypertarget{ref-frank2017}{}
+Frank, M. C., Braginsky, M., Yurovsky, D., \& Marchman, V. A. (2017).
+Wordbank: An open repository for developmental vocabulary data.
+\emph{Journal of Child Language}, \emph{44}(3), 677--694.
+
+\hypertarget{ref-goodman2008}{}
+Goodman, J. C., Dale, P. S., \& Li, P. (2008). Does frequency count?
+Parental input and the acquisition of vocabulary. \emph{Journal of Child
+Language}, \emph{35}(3), 515--531.
+
+\hypertarget{ref-griffiths07}{}
+Griffiths, T. L., Steyvers, M., \& Tenenbaum, J. B. (2007). Topics in
+semantic representation. \emph{Psychological Review}, \emph{114}(2),
+2007.
+
+\hypertarget{ref-hills2010}{}
+Hills, T. T., Maouene, J., Riordan, B., \& Smith, L. B. (2010). The
+associative structure of language: Contextual diversity in early word
+learning. \emph{Journal of Memory and Language}, \emph{63}(3), 259--273.
+
+\hypertarget{ref-hills2009}{}
+Hills, T. T., Maouene, M., Maouene, J., Sheya, A., \& Smith, L. (2009).
+Longitudinal analysis of early semantic networks: Preferential
+attachment or preferential acquisition? \emph{Psychological Science},
+\emph{20}(6), 729--739.
+
+\hypertarget{ref-jusczyk1994}{}
+Jusczyk, P. W., Luce, P. A., \& Charles-Luce, J. (1994). Infant's
+sensitivity to phonotactic patterns in the native language.
+\emph{Journal of Memory and Language}, \emph{33}(5), 630--645.
+
+\hypertarget{ref-higgins2014}{}
+MacRoy-Higgins, M., Shafer, V. L., Schwartz, R. G., \& Marton, K.
+(2014). The influence of phonotactic probability on word recognition in
+toddlers. \emph{Child Language Teaching and Therapy}, \emph{30}(1),
+117--130.
+
+\hypertarget{ref-nelson1998}{}
+Nelson, D. L., McEvoy, C. L., \& Schreiber, T. A. (1998). The University
+of South Florida word association, rhyme, and word fragment norms.
+Retrieved from \url{http://w3.usf.edu/FreeAssociation/}
+
+\hypertarget{ref-pisoni1985}{}
+Pisoni, D. B., Nusbaum, H. C., Luce, P. A., \& Slowiaczek, L. M. (1985).
+Speech perception, word recognition and the structure of the lexicon.
+\emph{Speech Communication}, \emph{4}(1), 75--95.
+
+\hypertarget{ref-smith2008}{}
+Smith, L., \& Yu, C. (2008). Infants rapidly learn word-referent
+mappings via cross-situational statistics. \emph{Cognition},
+\emph{106}(3), 1558--1568.
+
+\hypertarget{ref-stella2017}{}
+Stella, M., Beckage, N. M., \& Brede, M. (2017). Multiplex lexical
+networks reveal patterns in early word acquisition in children.
+\emph{Scientific Reports}, \emph{7}.
+
+\hypertarget{ref-steyvers2005}{}
+Steyvers, M., \& Tenenbaum, J. B. (2005). The large-scale structure of
+semantic networks: Statistical analyses and a model of semantic growth.
+\emph{Cognitive Science}, \emph{29}(1), 41--78.
+
+\hypertarget{ref-stokes2010}{}
+Stokes, S. F. (2010). Neighborhood density and word frequency predict
+vocabulary size in toddlers. \emph{Journal of Speech, Language, and
+Hearing Research}, \emph{53}(3), 670--683.
+
+\hypertarget{ref-storkel2001}{}
+Storkel, H. L. (2001). Learning new words: Phonotactic probability in
+language development. \emph{Journal of Speech, Language, and Hearing
+Research}, \emph{44}(6), 1321--1337.
+
+\hypertarget{ref-storkel2009}{}
+Storkel, H. L. (2009). Developmental differences in the effects of
+phonological, lexical and semantic variables on word learning by
+infants. \emph{Journal of Child Language}, \emph{36}(2), 29--321.
+
+\hypertarget{ref-vitevitch1999}{}
+Vitevitch, M. S., Luce, P. A., Pisoni, D. B., \& Auer, E. T. (1999).
+Phonotactics, neighborhood activation, and lexical access for spoken
+words. \emph{Brain and Language}, \emph{68}(1), 306--311.
+
+\end{document}

### 2018-01-12 helper_functions/abandoned_functions.r

@@ -1,0 +1,131 @@
+
+
+# 
+# make_assoc_pairs <- function(lemma_list) {
+#   #Filter all the cues and targets that are not learnt after 30 months and are not normed
+#   cue_target <- read.csv(paste(getwd(), "/in_files/assoc_table.csv", sep = ""), as.is = T) %>%
+#     filter(cue %in% lemma_list$uni_lemma,
+#            target %in% lemma_list$uni_lemma)
+#   
+#   #make a association network dataframe with item number
+#   #rename stuffs so it could conform to the format PAT_generator needs
+#   #item corresponds to target ;  pair corresponds to cue
+#   assoc_link <- cue_target %>%
+#     rename(pair.definition = cue) %>%
+#     left_join(lemma_list, c("pair.definition" = "uni_lemma")) %>%
+#     rename(pair = item, item.definition = target) %>%
+#     left_join(lemma_list, c("item.definition" = "uni_lemma")) %>%
+#     select(item, item.definition, pair, pair.definition, link) %>%
+#     arrange(item, pair)
+#   
+#   return(assoc_link)
+# }
+
+#########################################################################################################
+
+# make_assoc_pairs <- function(lemma_list) {
+#   #Filter all the cues and targets that are not learnt after 30 months and are not normed
+#   cue_target <- read.csv(paste(getwd(), "/in_files/assoc_table.csv", sep = ""), as.is = T) %>%
+#     filter(cue %in% lemma_list$uni_lemma,
+#            target %in% lemma_list$uni_lemma)
+# 
+#   #make a association network dataframe with item number
+#   #rename stuffs so it could conform to the format PAT_generator needs
+#   #item corresponds to target ;  pair corresponds to cue
+#   assoc_link <- cue_target %>%
+#     select(cue, target) %>%
+#     rename(pair.definition = cue) %>%
+#     left_join(lemma_list, c("pair.definition" = "uni_lemma")) %>%
+#     rename(pair = item, item.definition = target) %>%
+#     left_join(lemma_list, c("item.definition" = "uni_lemma")) %>%
+#     select(item, item.definition, pair, pair.definition) %>%
+#     arrange(item, pair) %>%
+#     mutate(link = 1)
+#   
+#   return(assoc_link)
+# }
+
+# ######################################################################################################
[…]

### 2018-01-12 helper_functions/all_helper.r

@@ -1,0 +1,8 @@
+source("growth_helper.r")
+source("wb_helper.r")
+source("make_pairs_helper.r")
+source("optims.r")
+source("phono_helper.r")
+source("network_creator.r")
+source("network_tester.r")
+source("stemmer.R")

### 2018-01-12 helper_functions/clustering.R

@@ -1,0 +1,120 @@
+data_path <- "../../aoa_unified/saved_data"
+uni_prop_data <- feather::read_feather(
+  file.path(data_path, "uni_prop_data.feather")
+)
+
+eng <- uni_prop_data %>%
+  filter(language == "English")
+
+fit_aoa <- function(data) {
+  glm(cbind(num_true, num_false) ~ age, data, family = "binomial")
+}
+
+eng_coefs <- eng %>%
+  filter(!grepl(",", lexical_classes)) %>%
+  rename(lexical_class = lexical_classes) %>%
+  group_by(measure, lexical_class, uni_lemma) %>%
+  nest() %>%
+  mutate(model = map(data, fit_aoa),
+         intercept = map_dbl(model, ~coefficients(.x)[["(Intercept)"]]),
+         slope = map_dbl(model, ~coefficients(.x)[["age"]])) %>%
+  select(-data, -model)
+
+lang_coefs <- uni_prop_data %>%
+  filter(!grepl(",", lexical_classes)) %>%
+  rename(lexical_class = lexical_classes) %>%
+  group_by(language, measure, lexical_class, uni_lemma) %>%
+  nest() %>%
+  mutate(model = map(data, fit_aoa),
+         intercept = map_dbl(model, ~coefficients(.x)[["(Intercept)"]]),
+         slope = map_dbl(model, ~coefficients(.x)[["age"]])) %>%
+  select(-data, -model)
+
+lang_coefs <- lang_coefs %>%
+  mutate(aoa = -intercept / slope)
+
+# pair_aoa <- lang_coefs %>%
+#   filter(measure == "understands", aoa > 0, aoa < 40) %>%
+#   group_by(uni_lemma) %>%
+#   filter(n() == 10) %>%
+#   select(language, lexical_class, uni_lemma, aoa) %>%
+#   spread(language, aoa)
+#
+# ggcorplot(pair_aoa)
+
+aoas <- lang_coefs %>%
+  filter(measure == "understands", aoa > 0, aoa < 40) %>%
+  select(language, lexical_class, uni_lemma, aoa)
+
+feather::write_feather(aoas, "app/aoas.feather")
+
+pair_cor <- function(l1, l2) {
+  pair_aoas <- aoas %>%
+    filter(language == l1 | language == l2) %>%
+    spread(language, aoa)
+  cor(pair_aoas[[l1]], pair_aoas[[l2]], use = "complete.obs")
+}
+
+pair_aoas <- map_df(unique(aoas$language), function(l1) {
[…]

### 2018-01-12 helper_functions/croatian.py

@@ -1,0 +1,66 @@
+#-*-coding:utf-8-*-
+#
+#    Simple stemmer for Croatian v0.2
+#    Copyright 2012 Nikola Ljubešić and Ivan Pandžić
+#    Copyright 2015 Stefan Koch
+#
+#    This program is free software: you can redistribute it and/or modify
+#    it under the terms of the GNU Lesser General Public License as published
+#    by the Free Software Foundation, either version 3 of the License, or
+#    (at your option) any later version.
+#
+#    This program is distributed in the hope that it will be useful,
+#    but WITHOUT ANY WARRANTY; without even the implied warranty of
+#    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+#    GNU Lesser General Public License for more details.
+#
+#    You should have received a copy of the GNU Lesser General Public License
+#    along with this program.  If not, see <http://www.gnu.org/licenses/>.
+
+import re
+import sys
+stop=set(['biti','jesam','budem','sam','jesi','budeš','si','jesmo','budemo','smo','jeste','budete','ste','jesu','budu','su','bih','bijah','bjeh','bijaše','bi','bje','bješe','bijasmo','bismo','bjesmo','bijaste','biste','bjeste','bijahu','biste','bjeste','bijahu','bi','biše','bjehu','bješe','bio','bili','budimo','budite','bila','bilo','bile','ću','ćeš','će','ćemo','ćete','želim','želiš','želi','želimo','želite','žele','moram','moraš','mora','moramo','morate','moraju','trebam','trebaš','treba','trebamo','trebate','trebaju','mogu','možeš','može','možemo','možete'])
+
+
+class CroatianStemmer(object):
+    def __init__(self):
+        self.pravila=[re.compile(r'^('+osnova+')('+nastavak+r')$') for osnova, nastavak in [e.strip().split(' ') for e in open('croatian_rules.txt')]]
+        self.transformacije=[e.strip().split('\t') for e in open('croatian_transformations.txt')]
+
+    def stem(self, token):
+        if token.lower() in stop:
+            return token.lower()
+        else:
+            return self.korjenuj(self.transformiraj(token.lower()))
+
+    def istakniSlogotvornoR(self, niz):
+        return re.sub(r'(^|[^aeiou])r($|[^aeiou])',r'\1R\2',niz)
+
+    def imaSamoglasnik(self, niz):
+        if re.search(r'[aeiouR]', self.istakniSlogotvornoR(niz)) is None:
[…]

### 2018-01-12 helper_functions/growth_helper.r

@@ -1,0 +1,225 @@
+# PAT_generator
+# word_pairs argument should have the format below:
+# column name: 
+# item, item.definition, pair, pair.definition, link
+
+PAT_generator<-function(vocab_age, word_pairs){
+  vocab_age<-vocab_age %>%
+    filter(item %in% word_pairs$item) %>%
+    mutate(value=NA) %>%
+    arrange(age, item)
+  all_ages<- (vocab_age %>%
+    group_by(age) %>%
+    summarise(n=n()))$age
+  ages<- all_ages[2:length(all_ages)]
+  for (i in ages){
+    #current items in this age
+    curr_items<- (vocab_age %>%
+                    filter(age==i) %>%
+                    select(item))$item
+    #item learnt in previous ages
+    exist_words<-(vocab_age %>%
+                    filter(age<i,learned==1) %>%
+                    select(item))$item
+    #calculating the degree of nodes in the existing network
+    sem_acq<- word_pairs %>%
+      filter(item %in% exist_words, pair %in% exist_words) %>%
+      group_by(item) %>%
+      summarise(value=sum(link))
+
+    row_n<-which(vocab_age$age==i & vocab_age$item==curr_items[1])
+    for (j in curr_items){
+      #calculating d
+      link_to_exist<-(word_pairs %>% filter(pair==j, item %in% exist_words, link==1))$item
+      PAT_value<-sem_acq %>%
+        filter(item %in% link_to_exist)
+      vocab_age$value[row_n]<- mean(PAT_value$value)
+      row_n<-row_n+1
+    }
+  }
+  #filter first age since there are no PAT value
+  vocab_age<-vocab_age %>% filter(age!=(all_ages[1]))
+  return(vocab_age)
+}
+
+######################################################################################################################
+
+PAT_nt_generator<-function(vocab_age, word_pairs){
+  vocab_age<-vocab_age %>%
+    filter(item %in% word_pairs$item) %>%
+    mutate(value=NA) %>%
+    arrange(age, item)
+  all_ages<- (vocab_age %>%
+                group_by(age) %>%
+                summarise(n=n()))$age
+  ages<- all_ages[2:length(all_ages)]
+  for (i in ages){
+    #current items in this age
+    curr_items<- (vocab_age %>%
+                    filter(age==i) %>%
+                    select(item))$item
+    #item learnt in previous ages
+    exist_words<-(vocab_age %>%
+                    filter(age<i,learned==1) %>%
[…]

### 2018-01-12 helper_functions/make_pairs_helper.r

@@ -1,0 +1,182 @@
+# compute the semantic distance between pair of words
+
+make_McRae_pairs <- function(words_list) {
+  #Get the McRae features
+  features <-
+    read_delim(paste(getwd(), "/in_files/", "features.csv", sep = ""), delim = ",") %>%
+    select(Concept, Feature, WB_Label, BR_Label) %>%
+    rename(uni_lemma=Concept)
+  #Intersection of Wordbank with McRae concepts
+  
+  #List of word types in WordBank
+  wb <- words_list %>%
+    select(item, uni_lemma)
+  
+  # List of word bank with feature
+  #Here I should deal with words in parenthesis (homophones?), e.g., chiken (animal) vs. chiken (food), etc...
+  
+  item_feat <- wb %>%
+    left_join(features) %>%
+    rename(item.definition = uni_lemma,
+           item_feat = Feature) %>%
+    filter(!is.na(item_feat)) %>%
+    select(item, item.definition, item_feat)
+  
+  item_feat_list <- (wb %>%
+                       filter(item %in% item_feat$item) %>%
+                       select(item))$item
+  
+  # List these words pair-wise and compate the number of shared feature for each pair
+  
+  item_pair <- expand.grid(item = item_feat_list,
+                           pair = item_feat_list)
+  
+  pair_feat <- item_feat %>%
+    rename(pair = item,
+           pair_feat = item_feat,
+           pair.definition = item.definition)
+  
+  item_feat_pair <- left_join(item_feat, item_pair)
+  
+  item_pair_feat <- item_feat_pair %>%
+    left_join(pair_feat)
+  
+  item_pair_shared <- item_pair_feat %>%
+    group_by(item, item.definition, pair, pair.definition) %>%
+    summarise(sem_value = sum(pair_feat == item_feat)) %>%
+    filter(item!=pair)
+  
+  return(item_pair_shared)
+}
+
+
+##############################################################################################################################
+make_McRae_distinct_pairs<- function(words_list){
+  #Intersection of Wordbank with McRae concepts
+  features <-
+    read_delim(paste(getwd(), "/in_files/", "features.csv", sep = ""), delim = ",") %>%
+    select(Concept, Feature, WB_Label, BR_Label) %>%
+    filter(BR_Label=="visual-form_and_surface") %>%
+    rename(uni_lemma=Concept)
+  #List of word types in WordBank
+  wb <- words_list %>%
[…]

### 2018-01-12 helper_functions/network_creator.r

@@ -1,0 +1,248 @@
+create_combo <- function(languages){
+  suffix<<- "_p"
+  for (language in languages){
+    lang_name<<- language
+    # age of acquisition data frame
+    aoa_frame<- make_aoa_dataframe(lang = lang_name)
+    # list of lemmas of learnt words
+    first_age<- aoa_frame$age[1]
+    lemma_list<- aoa_frame %>%
+      trim_all_unilemma() %>%
+      filter(age==first_age) %>%
+      select(item, uni_lemma) 
+    # list of definitions of learnt words
+    def_list<- aoa_frame %>%
+      trim_all_definition() %>% 
+      filter(age==first_age) %>%
+      select(item, definition)
+    
+    # make pairs of words and show whether they have connection via associative norms
+    assoc_pairs<- make_assoc_pairs(lemma_list = lemma_list)
+    phono_pairs<- make_IPA_pairs(def_list = def_list, lang = lang_name)
+    
+    assoc_PAC<- PAC_generator(vocab_age = aoa_frame, word_pairs = assoc_pairs) %>% 
+      rename(PAC_assoc = value) %>% select(-definition, -uni_lemma)
+    assoc_PAT<- PAT_generator(vocab_age = aoa_frame, word_pairs = assoc_pairs) %>% 
+      rename(PAT_assoc = value) %>% select(-definition, -uni_lemma)
+    phono_PAC_t1<- PAC_generator(vocab_age = aoa_frame, word_pairs = phono_pairs %>% IPA_threshold(1)) %>% 
+      rename(PAC_phono_t1 = value) %>% select(-definition, -uni_lemma)
+    phono_PAT_t1<- PAT_generator(vocab_age = aoa_frame, word_pairs = phono_pairs %>% IPA_threshold(1)) %>% 
+      rename(PAT_phono_t1 = value) %>% select(-definition, -uni_lemma)
+    phono_PAC_t2<- PAC_generator(vocab_age = aoa_frame, word_pairs = phono_pairs %>% IPA_threshold(2)) %>% 
+      rename(PAC_phono_t2 = value) %>% select(-definition, -uni_lemma)
+    phono_PAT_t2<- PAT_generator(vocab_age = aoa_frame, word_pairs = phono_pairs %>% IPA_threshold(2)) %>% 
+      rename(PAT_phono_t2 = value) %>% select(-definition, -uni_lemma)
[…]

### 2018-01-12 helper_functions/network_tester.r

@@ -1,0 +1,158 @@
+test_network<- function(languages, features, r=3000){
+  analysis_df<- data.frame(matrix(ncol = 7, nrow = 500))
+  colnames(analysis_df)<-c("language", "type", "CI lower", "Optim Par", "CI upper", "Full Model nLLK","Random Model nLLK")
+  i=1
+  for (language in languages){
+    for (feature in features){
+      file_path<-paste(getwd(),"/out_files/", language, "_", feature, ".csv", sep = "")
+      if (file.exists(file_path)){
+        final_df <<- read.csv(file_path, as.is = T)
+        analysis_df[i,]<- get_confint(language = language, type = feature, r = r)
+        i=i+1
+      }
+    }
+  }
+  analysis_df <- analysis_df %>% filter(!is.na(language))
+  write.csv(analysis_df, file = "analysis_df.csv", row.names = F)
+  return(analysis_df)
+}
+
+
+######################################################################################################
+# test the significance of DEGREE, before and after controling frequency and length
+significance_testing<- function(lang, type){
+  file_name<-paste(lang,"_",type, sep = "")
+  
+  if (file.exists(paste(getwd(),"/out_files/", file_name,".csv", sep = ""))){
+    
+    parent_freq<- read.csv(paste(getwd(),"/in_files/log_freq.csv",sep = ""), as.is = T) 
+    df<- read.csv(paste(getwd(),"/out_files/", file_name,".csv", sep = ""), as.is = T) %>%
+      trim_all_definition() %>%
+      trim_all_unilemma() %>%
+      rowwise() %>%
+      mutate(IPA=Speak(lang = lang, word = definition)) %>%
+      trim_IPA_completely() %>%
+      mutate(value2=str_count(IPA)) %>%
+      ungroup() %>% 
+      filter(learned==1) %>% 
+      left_join(parent_freq) %>% 
+      mutate(freq=ifelse(is.na(freq),0,freq)) #if can't find the freq of word, set it to 0
+    
+    degree<- df$value
+    length<- df$value2
+    freq<- df$freq
+    age<- df$age
+    a_d<- lm(age ~ degree)
+    a_fl<- lm(age ~ freq+length)
+    a_dlf<- lm(age ~ length+freq+degree)
+    
+    degree_coef<- round(summary(a_d)$coefficients[2,1], digits = 3)
+    degree_coef_control<- round(summary(a_dlf)$coefficients[4,1], digits =3)
+    degree_sig<- significance_level(summary(a_d)$coefficients[2,4])
[…]

### 2018-01-12 helper_functions/optims.r

@@ -1,0 +1,275 @@
+get_confint<- function(language, type, r = 3000){
+  optim_par<- optim(0, loglike1)$par
+  full_model_nLLK<- optim(0, loglike1)$value
+  null_model_nLLK<- optim(0, loglike0)$value
+  dataset=final_df %>% mutate(n=row_number())
+  ci_value1 <- vector(mode = "numeric", length = r)
+  #ci_value2 <- vector(mode = "numeric", length = r)
+  n_sample <- length(dataset[, 1])
+  for (i in 1:r) {
+    cur_sample <- as.data.frame(dataset$n[sample(n_sample, n_sample, replace = T)])
+    colnames(cur_sample) <- "n"
+    final_df <<- cur_sample %>% left_join(dataset)
+    ci_value1[i] <- optim(0, loglike1)$par[1]
+    #ci_value2[i] <- optim(c(0,0), loglike2)$par[2]
+  }
+  ci_value1 <- sort(ci_value1, decreasing = F)
+  len <- length(ci_value1)
+  #ci_value2 <- sort(ci_value2, decreasing = F)
+  
+  new_row<-c(language, type,
+             ci_value1[as.integer(0.025 * len+1)],  optim_par,ci_value1[as.integer(0.975 * len)], 
+             full_model_nLLK, null_model_nLLK)
+  return(new_row)
+}
+
+
+# A bunch of optims
+######################################################################################################
+# Return the nLLK of each model
+optim_nllk <- function(par_n) {
+  if (par_n == 2) {
+    random_model <- optim(c(0, 0), loglike00)$value
+    two_par_model <- optim(c(0, 0), loglike11)$value
+    first_par_model <- optim(c(0, 0), loglike10)$value
+    second_par_model <- optim(c(0, 0), loglike01)$value
+    
+    return(data.frame(random_model,
+                      two_par_model,
+                      first_par_model,
+                      second_par_model, row.names = "nLLK"))
+  }
+  else {
+    random_model <- optim(0, loglike0)$value
+    model <- optim(0, loglike1)$value
+    return(data.frame(random_model, model, row.names = "nLLK"))
+  }
+}
+
+######################################################################################################
+# Return the optimized parameters
+optim_par <- function(par_n) {
+  if (par_n == 2) {
+    random_model <- optim(c(0, 0), loglike00)$par
+    two_par_model <- optim(c(0, 0), loglike11)$par
[…]

### 2018-01-12 helper_functions/phono_helper.r

@@ -1,0 +1,39 @@
+######################################################################################################
+# Espeak function
+Speak<- function(lang, word){
+  langs<- c("English (British)","English (American)", "Spanish", "Croatian", 
+            "Italian", "Danish", "Norwegian", "Turkish", "Slovak", "Swedish", "Russian", "German")
+  abbr <- c("en-rp", "en-us", "es", "hr", "it", "da", "no", "tr","sk", "sv","ru","de")
+  lang_abbr<- abbr[which(langs==lang)]
+  IPA<- system(paste("espeak -q -v ", lang_abbr, " --ipa ", "\"", word, "\"",sep=""), intern=T)
+  return(IPA)
+}
+
+######################################################################################################
+# trim IPA
+trim_IPA<- function(IPA_list){
+  IPA_list<- IPA_list %>%
+    mutate(IPA= gsub(" ","", IPA)) %>%
+    mutate(IPA= gsub("[[:punct:]]", "",IPA))
+  return(IPA_list)
+}
+
+######################################################################################################
+# trim IPA, more fiercely
+trim_IPA_completely<- function(IPA_list){
+  IPA_list<- IPA_list %>%
+    mutate(IPA= gsub(" ","", IPA)) %>%
+    mutate(IPA= gsub("ː","",IPA)) %>%
+    mutate(IPA= gsub("[[:punct:]]", "",IPA))
+  return(IPA_list)
+}
+
+######################################################################################################
+# set threshold for IPA distance
+IPA_threshold<- function(IPA_list, threshold){
+  IPA_list<- IPA_list %>%
+    mutate(link=as.numeric(dist<=threshold))
+  return(IPA_list)
+}
+
+######################################################################################################

### 2018-01-12 helper_functions/stemmer.R

@@ -1,0 +1,25 @@
+# Gets stems for a list of words in a given language.
+# Uses Snowball if it is available, otherwise uses a special case stemmer
+# So far: Croatian (uses Steven Koch's implementation of the Zagreb Stemer)
+#croatian_path <- file.path(getwd(), "croatian.py")
+
+stem <- function(words, language) {
+
+  language <- tolower(language)
+
+  if (language %in% SnowballC::getStemLanguages()) {
+    SnowballC::wordStem(words, language)
+
+  } else if (language == "croatian") {
+    chunk_size <- 1000
+    word_chunks <- split(words, ceiling(seq_along(words) / chunk_size))
+    purrr::map(word_chunks, function(word_chunk) {
+      system2("python", args = c("croatian.py", sprintf('"%s"', word_chunk)),
+              stdout = TRUE)
+    }) %>% unlist()
+
+  } else {
+    warning(sprintf("language %s not in list of stemmable languages", language))
+    words
+  }
+}

### 2018-01-12 helper_functions/wb_helper.r

@@ -1,0 +1,383 @@
+# This file contains functions used to get item data, admin data, etc. , and generate dataframes for analysis
+import_all_library<- function(){
+  library(tidyr)
+  library(purrr)
+  library(readr)
+  library(ggplot2)
+  library(langcog)
+  library(boot)
+  library(lazyeval)
+  library(dplyr)
+  library(wordbankr)
+  library(directlabels)
+  library(scales)
+  library(stringr)
+  library(lmtest)
+}
+######################################################################################################################
+get_lang_item_data <- function(lang, lang_form = "WS", lex_class = "nouns") {
+
+  item_data <- get_item_data(language = lang, form = lang_form) %>%
+    select(num_item_id, definition, type, lexical_class, uni_lemma) %>%
+    filter(type == "word", lexical_class == lex_class) %>%
+    rename(item = num_item_id)
+  
+  #Initialize every item as NA (NOT yet learnt)
+  lang_item <- item_data %>%
+    select(item, definition, uni_lemma) %>%
+    mutate(age = NA)
+  
+  return(lang_item)
+}
+
+######################################################################################################################
+# get only "useful" admin data (where production is not NA)
+get_lang_admin_data <- function(lang, lang_form = "WS") {
+  #get the kids' data_id from every age
+  admin_data <- get_administration_data() %>%
+    filter(form == lang_form, !is.na(production), language == lang) %>%
+    select(data_id, age) %>%
+    arrange(age)
+  
+  return(admin_data)
+}
+
+######################################################################################################################
+# See how many kids we have in every age
+get_kids_by_age <- function(admin_data) {
+  #get number of kids by age
+  nkids_by_age <- admin_data %>%
+    group_by(age) %>%
+    summarise(n = n())
+  return(nkids_by_age)
+}
+
+######################################################################################################################
+#get "produces" instrument data 
+get_lang_instr_data <- function(lang, lang_form = "WS") {
+  instr_data <- get_instrument_data(instrument_language = lang,
+                                    instrument_form = lang_form) %>%
+    filter(value == "produces") %>%
+    arrange(num_item_id) %>%
+    rename(item = num_item_id)
+  
+  return(instr_data)
+}
+
+######################################################################################################################
[…]

### 2018-01-12 models/all_models.R

@@ -1,0 +1,4 @@
+source("helpers.r")
+source("optimize.r")
+source("individual_pred.r")
+source("combined_pred.r")

### 2018-01-12 models/combined_pred.R

@@ -1,0 +1,286 @@
+freq_len <- '
+var model = cache(function(alpha1, alpha2, alpha3, alpha4, alpha5, alpha6,  month) {
+return Infer({method:"enumerate"}, function(){
+var wordlist = _.keys(learning[month]["isLearnt"])
+var word = uniformDraw(wordlist);
+var utility_freq = learning[month]["frequency"]
+var utility_len = learning[month]["length"]
+factor(alpha1 * utility_freq[word]
++ alpha2 * utility_len[word]
+);
+return word;
+});
+});
+
+'
+
+sem_phono <- '
+var model = cache(function(alpha1, alpha2, alpha3, alpha4, alpha5, alpha6,  month) {
+return Infer({method:"enumerate"}, function(){
+var wordlist = _.keys(learning[month]["isLearnt"])
+var word = uniformDraw(wordlist);
+var utility_sem= learning[month]["PAC_assoc"]
+var utility_phono= learning[month]["PAC_phono"]
+factor( alpha1 * utility_sem[word]
++ alpha2* utility_phono[word]
+);
+return word;
+});
+});
+'
+
+
+
+freq_sem <- '
+var model= cache(function(alpha1, alpha2, alpha3, alpha4, alpha5, alpha6,  month) {
+return Infer({method:"enumerate"}, function(){
+var wordlist = _.keys(learning[month]["isLearnt"])
+var word = uniformDraw(wordlist);
+var utility_freq = learning[month]["frequency"]
+var utility_sem= learning[month]["PAC_assoc"]
+factor(alpha1 * utility_freq[word]
++ alpha2 * utility_sem[word]
+);
+return word;
+});
+});
+'
+
+freq_phono <- '
+var model= cache(function(alpha1, alpha2, alpha3, alpha4, alpha5, alpha6,  month) {
+return Infer({method:"enumerate"}, function(){
+var wordlist = _.keys(learning[month]["isLearnt"])
+var word = uniformDraw(wordlist);
+var utility_freq = learning[month]["frequency"]
+var utility_phono= learning[month]["PAC_phono"]
+factor(alpha1 * utility_freq[word]
++ alpha2 * utility_phono[word]
+);
+return word;
+});
+});
+'
+
+
+freq_sem_phono<- '
+var model= cache(function(alpha1, alpha2, alpha3, alpha4, alpha5, alpha6,  month) {
[…]

### 2018-01-12 models/helpers.R

@@ -1,0 +1,90 @@
+helper <- '
+
+var levels = function(a, lvl){ return _.uniq(_.pluck(a, lvl)) }
+
+var months = levels(data, "age");
+
+var newData = map(function(month){
+
+//Select the data that correspond to each month
+var itemInfo = {age: month}
+var itemData = _.where(data, itemInfo)
+
+//prepare data for a dictionary with the utilies (freq, length, Sem_PAC, Phono_PAC)
+
+//frequency
+var value_freq  =  map(function(single){
+return _.object([single.definition], [single.freq_mika])
+}, itemData)
+
+//Length 
+var value_len  =  map(function(single){
+return _.object([single.definition], [single.length])
+}, itemData)
+
+//Sem PAC
+var value_PAC_assoc  =  map(function(single){
+return _.object([single.definition], [single.PAC_assoc])
+}, itemData)
+
+//Sem PAT
+var value_PAT_assoc  =  map(function(single){
+return _.object([single.definition], [single.PAT_assoc])
+}, itemData)
+
+//Phono PAC t2
+var value_PAC_phono  =  map(function(single){
+return _.object([single.definition], [single.PAC_phono_t2])
+}, itemData)
+
+//Phono PAT t2
+var value_PAT_phono  =  map(function(single){
+return _.object([single.definition], [single.PAT_phono_t2])
+}, itemData)
+
+//Also prepare data for a dictionary with "definitions" as keys and boolean "learned" as values
+var learned_pair = map(function(single){
+return _.object([single.definition], [single.learned])
+}, itemData)
+
+//now get the "defintions"
+var word = map(function(w){_.keys(w)[0]}, value_freq)
+
+//get the utilities scores
+var util_freq = map(function(w){w[_.keys(w)[0]]}, value_freq)
+var util_len = map(function(w){w[_.keys(w)[0]]}, value_len)
+var util_PAC_assoc = map(function(w){w[_.keys(w)[0]]}, value_PAC_assoc)
+var util_PAC_phono = map(function(w){w[_.keys(w)[0]]}, value_PAC_phono)
+var util_PAT_assoc = map(function(w){w[_.keys(w)[0]]}, value_PAT_assoc)
+var util_PAT_phono = map(function(w){w[_.keys(w)[0]]}, value_PAT_phono)
+
+//get "if learned" boolean score
[…]

### 2018-01-12 models/individual_pred.R

@@ -1,0 +1,82 @@
+freq <- '
+var model = cache(function(alpha1, alpha2, alpha3, alpha4, alpha5, alpha6,  month) {
+return Infer({method:"enumerate"}, function(){
+var wordlist = _.keys(learning[month]["isLearnt"])
+var word = uniformDraw(wordlist);
+var utility_freq = learning[month]["frequency"]
+factor(alpha1 * utility_freq[word])
+
+return word;
+});
+});
+'
+
+
+len <- '
+var model = cache(function(alpha1, alpha2, alpha3, alpha4, alpha5, alpha6,  month) {
+return Infer({method:"enumerate"}, function(){
+var wordlist = _.keys(learning[month]["isLearnt"])
+var word = uniformDraw(wordlist);
+var utility_len = learning[month]["length"]
+factor(alpha1 * utility_len[word])
+
+return word;
+});
+});
+
+'
+
+
+sem_PAC <- '
+var model = cache(function(alpha1, alpha2, alpha3, alpha4, alpha5, alpha6,  month) {
+return Infer({method:"enumerate"}, function(){
+var wordlist = _.keys(learning[month]["isLearnt"])
+var word = uniformDraw(wordlist);
+var utility_sem = learning[month]["PAC_assoc"]
+factor(alpha1 * utility_sem[word])
+
+return word;
+});
+});
+
+'
+
+sem_PAT <- '
+var model = cache(function(alpha1, alpha2, alpha3, alpha4, alpha5, alpha6,  month) {
+return Infer({method:"enumerate"}, function(){
+var wordlist = _.keys(learning[month]["isLearnt"])
+var word = uniformDraw(wordlist);
+var utility_sem = learning[month]["PAT_assoc"]
+factor(alpha1 * utility_sem[word])
+
+return word;
+});
+});
+
+'
+
+phono_PAC <- '
+var model = cache(function(alpha1, alpha2, alpha3, alpha4, alpha5, alpha6,  month) {
+return Infer({method:"enumerate"}, function(){
+var wordlist = _.keys(learning[month]["isLearnt"])
+var word = uniformDraw(wordlist);
+var utility_phono = learning[month]["PAC_phono"]
+factor(alpha1 * utility_phono[word])
+return word;
+});
+});
+
+'
+
+phono_PAT <- '
+var model = cache(function(alpha1, alpha2, alpha3, alpha4, alpha5, alpha6,  month) {
[…]

### 2018-01-12 models/optimize.R

@@ -1,0 +1,81 @@
+optimize <- '
+var AOA = function(){
+
+//_.range(-0.1,0.1, 0.005)
+
+var alpha1 = sample(Uniform({a: -0.5, b: 0.5}))
+var alpha2 = sample(Uniform({a: -0.5, b: 0.5}))
+var alpha3 = sample(Uniform({a: -0.5, b: 0.5}))
+var alpha4 = sample(Uniform({a: -0.5, b: 0.5}))
+var alpha5 = sample(Uniform({a: -0.5, b: 0.5}))
+var alpha6 = sample(Uniform({a: -0.5, b: 0.5}))
+
+var predictions = map(function(month){
+
+//List of all words that have not been learned yet
+var wordlist = _.keys(learning[month]["isLearnt"])
+
+//posterior dsitribution Dsitribution over these wrods (choose a model)
+var Posterior =  model(alpha1, alpha2, alpha3, alpha4, alpha5, alpha6,  month);
+
+//Select the words that have been learned that month 
+var isLearned = learning[month]["isLearnt"]
+var learned = filter(function(d){return isLearned[d]==1}, _.keys(isLearned))
+
+//Fit the distribution to the words that have been learned that month
+map(function(w){observe(Posterior, w)}, learned)
+
+//What are the words predicted by the model?
+//We select the highest probability words in our posterior distribution
+/////////////
+
+//map words to their scores in the distribution
+var scores = map(function(w){
+_.object(["word", "score"],[w, Posterior.score(w)])
+}, Posterior.supp)
+
+//Sort this list of objects based on the score property
+var scores_sorted = sort(scores, gt, function(x) { return x.score; })
+
+
+//Now select the highest score 
+var N_learned = learned.length
+var predicted_objects = scores_sorted.slice(0,N_learned)
+var predicted_words = map(function(obj){
+obj.word
+}, predicted_objects)
+
+//Random words selected from the words not yet learned
+var random_words = _.sample(wordlist, N_learned)
+
+//Compute the overlap between predicted and words learned in this month
+var intersection_model = _.intersection(predicted_words, learned)
+var intersection_random = _.intersection(random_words, learned)
+var accuracy_model = intersection_model.length/N_learned
+var accuracy_random = intersection_random.length/N_learned
+
+//Finally return the values of the accuracy for both the model and rando   
+
[…]

### 2018-01-23 cogsci/cogsci.Rmd
cogsci up-date and packrat

@@
 ---
-title: "The Role of Early Semantic and Phonological Networks in Noun Learning: a Cross-linguistic Analysis"
+title: "Word Learning as Network Growth: a Cross-linguistic Analysis"
 
@@
 abstract: 
-    "Children tend to learn first the words that have a high density neighborhood in the lexical network (i.e., words that are connected to a variety of other words).
-However, the reason why connectivity influences learning is still not very well understood.
-Previous studies suggested this effect could be the consequence of the underlying learning mechanism.
-However, these studies focused on semantic networks and English data only, thus severely limiting the generality of the findings.
-Here we provide a systematic analysis of network growth models in both the phonological and the the semantic domains, and across 8 languages.
-We replicate the results obtained by Hills et al.
-(2009) with English semantic networks, show that the same  mechanism drives the growth of both semantic and phonological networks, and demonstrate that these effects hold cross-linguistically."
+    "Children tend to learn first the words that are highly connected in the lexical network (i.e., words that are connected to a variety of other words).
+The process by which connectivity in both the phonological and semantic netwoks come to influence word learning is still not very well understood.
+One view suggests that learning is driven primarily by *internal* connectivity in the child's available lexicon.
+Another view suggests that *external* connectivity in the learning environment is what makes words salient and readily learned.
+The present study tests both scenarios systematically in both the phonological and the the semantic domains, and across 8 languages.
+We generate the results obtained by Hills et al.
+(2009) with English semantic networks, and show that external connectivity in the learning environment, rather than internal connectivity, drives growth of both semantic and phonological networks.
+Finally, we demonstrate that these effects hold cross-linguistically."
 
 keywords:
-    "keywords: semantic network, phonological network, word learning, semantic "
+    "semantic network, phonological network, word learning"
 
@@
 
-A crucial question in language development is to understand why children learn some words at an earlier age than others.
-Previous studies documented various word properties that influence the age of acquisition.
-For example, it was shown that, within a lexical category, words that are more frequent in child-directed speech are acquired earlier [@goodman2008].
-Other predictors include word length, the mean length of utterances in which the word occurs, and how concrete the word is [see @braginsky2016].
-Besides these word-level properties, researchers found that the lexical structure (that is, the network that specifies how words relate to each other) also influences the learning process.
-For instance, children tend to produce first the words that have higher neighborhood density (i.g., high connectivity in the network) both at the phonological and the semantic level [@stokes2010; @storkel2009].
-However, it is still not very well understood *why* connectivity in the lexical structure influences learning.
-@steyvers2005 suggested that this effect is nothing but the consequence of how these structures get constructed in the child's mind.
-According to this explanation (known as Preferential Attachment), highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario.
-Nonetheless, @hills2009 found that what biases the learning is not the connectivity in the child's internal lexicon but the connectivity in the learning environment.
+What factors shape vocabulary learning over the course of early childhood?
+To investigate this question, scientists have adopted multiple research strategies, from controlled laboratory experiments to corpus analysis.
+One strategy consists in documenting the timeline of words' acquisition, and studying the properies that make words easy or hard to learn.
+For example, within a lexical category, words that are more frequent in child-directed speech are acquired earlier [@goodman2008].
+Other factors include word length, the mean length of utterances in which the word occurs, and how concrete the word is [see @braginsky2016].
 
-These analyses, however, focused on growth in semantic networks only.
-A recent study by @stella2017 analysed both semantic and phonological connectivity, but assumed only one growth model (preferential acquisition).
-More importantly, almost all available studies are limited in their generality because they focus almost exlusively on English data.
-The novely of this study is that it investigtes, for the first time, whether phonological networks grow by preferential attachement or preferential acquisition.
-It also provides a systematic comparision between network growth scenarios in both the phonological and the semantic domains and assess their relative contribution to the learning process.
+Besides these word-level properties, researchers found that the lexical structure (that is, how words relate to each other) also influences the age of acquisition of words.
+The lexical structure is best characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words.
+Previous studies investigated early vocabulary networks based on different word relations such as shared semantic features, target-cue relationship in free association norms, co-occurrence in child directed speech, and phonological similarity.
+These studies found that children tend to produce earlier the words that have higher neighborhood density (i.g., high connectivity in the network) both at the phonological and the semantic level [@stokes2010; @storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017; @beckage2011].
+
+A crucial question that naturally emerges from these analyses is how does network connectivity influence word learning?
+@steyvers2005 suggested that the effect of connectivity is the consequence of how the lexical network gets constructed in the child's mind.
+According to this explanation, known as Preferential Attachment (PAT), highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99].
+In other words, what predicts word learning is *internal* connectivity in the child's early lexicon.
+In contrast, @hills2009 found that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment.
+They called this alternative explanation Preferential Acquisition (PAC).
+Figure \ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network.
+
+```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Illustration of the two growth models with the same network.
+Filled circles (I1-I4) represent known words (internal lexicon), and empty circles (E1 and E2) represent words that have not been learned yet (external lexicon).
+Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
+For PAT, each candidate node is characterized with the average degree (i.e., number of links) of the existing nodes that it would attach to.
+Thus, according to PAT, the node E1 is more likely to enter the lexicon first.
+For PAC, each candidate node is characterized with its degree in the entire network.
+According th PAC, the node E2 is more likely to enter the lexicon first."}
+
+img <- png::readPNG("figs/growth2.png")
+grid::grid.raster(img)
+
+```
+
+Studies that investigted lexical network growth focused on semantic networks using English data only [@steyvers2005; @hills2009; @hills2010].
+The novelty of the current study is that it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT.
+It also provides a systematic comparision of network growth scenarios in both the phonological and the semantic domains and assesses their relative contribution to the learning process.
 Moreover, it tests the generality of the findings across eight languages.
@@
 The paper is organized as follows.
-First, we describe the dataset we used, the procedure we followed to construct both semantic and phonological networks, and the network growth scenarios we tested.
+First, we describe the dataset we used, the procedure we followed to construct both semantic and phonological networks.
 Next, we show the results of the various analyses we conducted comparing network growth scenarios across languages.
-Then we compare the overall contribution of the networks in the learning process relative to other known predictors of age of acquisition (frequency and length).
+Then we test the overall contribution of the networks in the learning process relative to other known predictors of age of acquisition (frequency and length).
 Finally we discuss the major results in relation to known experimental facts in language development.
@@
 
+#Compute the correlations 
+correlations <-  data_long %>%
+  group_by(language, predictor) %>%
+  dplyr::summarise(cor = round(cor(AoA, value), 2))
+
 plot_data_all <- ggplot(data_long, aes(x=value, y=AoA))+
@@
     size = 0.5, alpha = 0.5) +
-  coord_cartesian(xlim=c(-2,5))+
+  coord_cartesian(xlim=c(-1,5))+
   #scale_x_continuous(limits=c(-2,5))+
@@
         )+
+  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
   xlab("degree z-score") +ylab("AoA")
@@
 
-We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI).
-The latter consists of parent report vocabulary checklists.
-We used the *Words and Sentence* version which contains the productive vocabulary of toddlers (age varied between 16 to 35 months).
-We included words that were produced by at least 50% of children, and we considered that these words were learned at the month when this percentage was reached [@goodman2008].
-Moreover, following previous studies [e.g., @storkel2009; @hills2009], we restricted the analysis to the category of nouns, since there are known discrepancies between the learning of nouns, predicates, and function words [e.g., @braginsky2016].
+We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist.
+We used the *Words and Sentence* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months).
+Following previous studies [e.g., @storkel2009; @hills2009], we restricted our analysis to the category of nouns, since there are known discrepancies between the learning of nouns, predicates, and function words [e.g., @braginsky2016].
+The age of acquisition was defined by the month at which a word was produced by at least 50% of children [@goodman2008].
+
 We obtained these nouns in eight languages: Croatian, Danish, English, Italian, Norwegian, Russian, Spanish, and Turkish.
 We used the subset of nouns that had entries in the Florida Association Norms (see below).
-Since these norms are available only in English, we mapped words onto translation equivalents across CDI forms.
+Since these norms are available only in English, we used the translation of non-English words provided by @braginsky2016.
 This allowed us to use the English association norms across languages.
@@
                       caption = "\\label{tab:stats}Total number of productive nouns in the CDI (left).
-We used a subset of these nouns that have available English translations (middle), as well as entries in the Free Association Norms (right).")
+We used a subset of these nouns that had available English translations (middle).
+The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).")
 
@@
 
-We used as index of semantic relatedness the Florida Free Association Norms [@nelson1998].
+We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998].
 This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target).
@@
 Each node was characterized by its "indegree", which represents the number of links for which the word was the target.
-Following @hills2009, we used as a proxy for the learning environment, the network constructed using the full CDI data in each language (e.g., in English this corresponds to the network by 30 months).
-
-```{r }
-
-#Import data from saved
-individual_both <- feather::read_feather("../saved_data/individual_both.feather")
-
-pred_ind <- ggplot(individual_both, aes(x = model , y = mean)) +
-  geom_pointrange(aes(ymin = lower, ymax = upper, col = model, linetype=Evaluation),
-                  position = position_dodge(width = .5),
-                  size = 0.5,
-                  fatten = 0.5)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  coord_flip() +
-  facet_wrap(~language, ncol=4)  +
-  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
-  scale_colour_solarized() +
-  theme_bw()+
-  theme(aspect.ratio = 0.7)
-
-ggsave("figs/pred_ind.png", plot = pred_ind, width = 8, height = 4)
-
-```
-
-```{r pred_ind_img, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3.5, fig.align = "center", fig.cap = "\\label{fig:pred_ind}Evaluation of individual network growth models using both  one-sample t-test over the z-score distribution of learned words (dotted), and model fitting (solid).
-Each dot represents, in the first case, the mean of the z-score distribution of the learned words with ranges representing 95\\% confidence interval, and in the second case, the mean of the posterior distribution of the model's parameter, with ranges reppresenting 95\\% credible intervals (computed using the highest density intervals)."}
-
-pred_ind
-
-#img <- png::readPNG("figs/pred_ind.png")
-#grid::grid.raster(img)
-```
+Following @hills2009, we used as a proxy for the learning environment, the network constructed using the full set of nouns in the CDI data in each language (e.g., in English this corresponds to the network by 30 months).
 
@@
 The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.
-We generated approximate IPA forms from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).**.
+We generated approximate International Phonetic Alphabet (IPA) trnascriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).**
+
 In previous studies, two nodes were linked if they had an edit distance of 1 [@stokes2010; @storkel2009].
@@
 
-## Network growth
+<!--## Network growth
 
@@
 
-```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Illustration of the two growth models with the same network.
-Filled circles (A to D) represent known words, and empty circles (N1 to N3) represent words that have not been learned yet.
-Back lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant (from Hills et al.
-2009)."}
-
-img <- png::readPNG("figs/growth.png")
-grid::grid.raster(img)
-
-```
+-->
 
@@
 
-## Connectivity vs. Age of acquisition
+We start by examining how connectivity in the global netowrk influences the age of acqusition.
+Regardless of the growth mechanism that might have given rise to this netowrk (i.e., PAC or PAT), we expect nodes with the higher degrees in this network to be learned earlier than nodes with the lower degrees.
+The network was constructed using nouns at the oldest age for which we have CDI data.
+Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network).
+For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages.
+The plots show, overall, a negative correlation between the month of acquisition and the degree, indicating that nouns with higher degrees are generally learned earlier.
 
-Preferential attachment and preferential acquisition provide different generative scenarios for the same end-state.
-The latter is defined here as the network corresponding to the oldest age for which we have CDI data.
-However in both cases, it is predicted that nodes with the higher degrees in this end-state are learned earlier than nodes with the lower degrees.
-Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network) in the end-state network.
-In order to compare this correlation across languages, the predictor (i.e., the degree) was centered and scaled.
-The plot shows a negative correlation between the month of acquisition and the degree (with the exception of the Russian semantic network), indicating that nouns with higher degrees are generally learned earlier.
-
+<!--
 ```{r }
@@
 ```
+-->
+
+```{r }
+
+#Import data from saved
+individual <- feather::read_feather("../saved_data/individual_both.feather") %>%
+  filter(Evaluation =='Fit') %>%
+  select(-Evaluation) %>%
+  mutate(Test = 'Individual')
+
+combined <- feather::read_feather("../saved_data/combined_net.feather") %>%
+  dplyr::rename(lower = hdi_lower,
+                upper = hdi_upper) %>%
+  mutate(Test = 'Combined')
+
+growth_all <- bind_rows(individual, combined)
+
+pred_ind <- ggplot(growth_all, aes(x = model , y = mean)) +
+  geom_pointrange(aes(ymin = lower, ymax = upper, col = model, linetype=Test),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  coord_flip() +
+  facet_wrap(~language, ncol=4)  +
+  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
+  scale_colour_solarized() +
+  theme_bw()+
+  theme(aspect.ratio = 0.7)
+
+ggsave("figs/pred_ind.png", plot = pred_ind, width = 8, height = 4)
+
+```
+
+```{r pred_ind_img, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3.5, fig.align = "center", fig.cap = "\\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid).
+Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\\% credible intervals (computed using the highest density intervals)."}
+
+pred_ind
+
+#img <- png::readPNG("figs/pred_ind.png")
+#grid::grid.raster(img)
+```
 
@@
 
-Following @hills2009, we evaluated the growth models in two separate ways.
-The first evaluation consists in determining, in each month, the model-dependent growth value distribution of all words that could possibly be learned at this month, and then computing the z-score of each learned word with respect to this distribution.
-For each model, we tested if the distribution constituted by the z-scores of all learned words was different from zero, using a one-sample t-test.
-The results are shown in Figure \ref{fig:pred_ind}.
+### How does each growth scenario predict noun development?
 
-The second evaluation consists in fitting an explicit model to the data.
-The purpose of this second evaluation is, first, to validate the findings obtained with the one-sample t-test, and second, to determine (in a next step) the relative contribution of each network growth scenario (PAT vs.
-PAC) across domains (phonological vs.
-semantic).
-
-We proceeded as follows. We calculated the probability that a word $w_i$, with a growth value $d_i$ would enter the lexicon at a given month, using a softmax function: 
+To test the network growth scenarios, we fit different growth models to the data.
+We proceeded as follows.
+We calculated the probability that a word $w_i$, with a growth value $d_i$ would enter the lexicon at a given month, using a softmax function:
 \begin{equation}
@@
 \end{equation}
+Where $\beta$ is the fitting parameter.
+A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first.
+As explained in Figure \ref{fig:growth}, each candidate word $w_i$ is characterized with a growth values $d_i$ that depends on the growth scenario tested.
+The normalization includes all words that could be learned at that month.
 
-Where $\beta$ is the fitting parameter.
-A positive value of $\beta$ means that words with higher groth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first.
-The normalization included words that were not yet learned at the month the word at hand was acquired.
 We estimated the parameter $\beta$ using a Bayesian approach.
+The inference was performed using the probabilisitic programming language  WebPPL [@dippl].
 We started with a uniform distribution, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been actually learned at that month (using formula 1).
@@
 
-The results from both evaluations were very similar and lead essentially to the same conclusions.
-For the semantic networks, the results replicate Hills et al.'s finding in English, which was that the semantic network grows by PAC, not by PAT.
+Besides fitting a growth model to the data, we conducted another evaluation.
+This second evaluation consists in determining, in each month, the model-dependent growth value distribution of all words that could possibly be learned at this month, and then computing the z-score of each learned word with respect to this distribution.
+For each model, we tested if the distribution constituted by the z-scores of all learned words was different from zero, using a one-sample t-test.
+
+The results from both evaluations were very similar and lead essentially to the same conclusions\footnote{we do not show here the resuts of the second evaluation because they were redundant with the results of the first evaluation}.
+For the semantic network, the results replicate Hills et al.'s finding in English, which was that the semantic network grows by PAC, not by PAT.
 Moreover, it generalizes this finding to all other languages (with the exception of Russian).
-For the phonological network, the results show that, generally speaking, PAC fits the developmental trajectory better than PAT in all languages.
-We note however that PAT, though weaker, fares  better for the phonological networks than it does for the semantic networks.
-In the former, it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian.
-In the latter, it is rather universally unpredictive.
+For the phonological network, the results show that, generally speaking, PAC again fits the developmental trajectory better than PAT.
+We note however that PAT, though weaker, fares  better for the phonological networks (where it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian) than it does for the semantic networks (where it is rather universally unpredictive).
+
+### What is the relative contribution of each growth model?
 
@@
 As a next step, we analysed their relative contribution to the learning process.
-This was done through adding more fitting parameters to the model, that is, by substituting $\beta d_i$ in equation (1) with: $$\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}$$ where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and PhonoPAC.
-Using the same fitting technique, we obtained the values shown in Figure \ref{fig:pred_comb_img}.
+This was done through adding more fitting parameters to the model, that is, by substituting $\beta d_i$ in formula (1) with: $$\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}$$ where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and PhonoPAC.
+Using the same fitting technique, we obtained the values shown in Figure \ref{fig:pred_ind}.
 In term of growth scenarios, we found that PAC dominates the learning.
 In particular, though we found previously that phonological PAT predicted part of the learning in some languages when tested individually, here PAT appears to lose its predictive power when pitted against phonological PAC.
-In terms of domain (phonological vs.
-semantic), both phonological and semantic networks appear to contribute to learning, although the phonological network appears to be stronger and more reliable across languages.
-In summary, the findings show that both semantic and phonological networks grow primarily through preferential acquisition, and that, generally speaking, semantic and phonological networks both contribute to the learning process.
+In terms of domain, both phonological and semantic networks appear to contribute to learning, although the phonological network appears to be stronger and more reliable across languages.
+In summary, the findings show that both semantic and phonological networks grow primarily by PAC, and that, generally speaking, semantic and phonological networks both contribute to the learning process.
 
@@
 
-## The big picture: comparison to other known predictors of age of acquisition
+## Comparison to other known predictors of age of acquisition
 
@@
 @goodman2008].
-The second factor is word length because it correlates with phonological connectivity [@pisoni1985].
+The second factor is word length, which correlates with phonological connectivity [@pisoni1985].
 
 Since PAT was uninformative, we dropped it from this analysis.
-Thus, we no longer needed to to fit the growth model month-by-month as in the previous section.
+Thus, we no longer needed to fit the growth model month-by-month as in the previous section.
 In fact, word utilities in the case of PAC are fixed, they do not depend on previously learned words.
@@
 For word length, we used our generated IPA transcription.
-This allowed us to get a more accurate estimate of word length across languages than the number of characters in the orthographic transcription.
+
+We conducted two analyses.
+We fit a linear regression for each language, and we fit a linear mixed-effect to all the data pooled across languages, with language as a random effect.
+Figure \ref{fig:regressions_img} shows the coefficient estimate for each predictor in each language, and figure \ref{fig:regressions_all_img} shows the coefficient estimates for all languages combined (all predictors were centered and scaled).
+The findings were as follows.
+Overall, frequency is the largest and most consistent predictor of age of acquisition.
+Word length predicts learning in some languages such as Croatian and Norwegian, but not in others (including English).
+It remains, however, a significant predictor in the global model.
+As for the factors of interest, i.e., semantic and phonological connectivity, we also found cross-linguistic differences.
+The phonological connectivity contributes to learning in languages such as Croatian, English and Russian, whereas semantic connectivity contributes to learning in Turkish, Spanish and to some extent in Croatian, but interestingly not in English\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
+This contrasts with the original finding in Hills et al.
+2009.
+However, in this previous study, semantic connectivity was not tested in a model that included both frequency and length as covariates.
+Another important difference is the number of words tested.
+Our study uses a larger set of nouns.}.
+Despite this cross-linguistic variation, both phonological and semantic connectivity remain significant predictors in the global model.
+
+# Discussion
+
+The present study provided a comprehensive analysis of how lexical connectivity influences the age of acquisition of nouns in toddlers.
+We compared two network growth scenarios and assessed the relative contribution of phonological and semantic information in 8 languages.
+Part of the findings largely replicate the results obtained in @hills2009, i.e., semantic networks (based on free associations) grow by preferential acquisition, not by preferential attachment.
+Another finding was that phonological networks also grow primarily by preferential acquisition, especially when both scenarios (PAT and PAC) were pitted against each other in the same model.
+These findings generalize well across languages.
+Moreoever, both semantic and phonological connectivity in the learning environment (i.e., PAC) predict growth in a consistent way across many languages.
+However, when pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting learning in some languages, but not in others.
+Despite this cross-lingusitic variation, both phonological and semantic connectivity contribute to the overall learning (when data is pooled across languages).
 
@@
 
-```{r regressions_all_img, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, fig.cap = "\\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined model.
+```{r regressions_all_img, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, fig.cap = "\\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined model pooling across languages .
 Ranges indicate 95\\% confidence intervals.
@@
 
-We conducted two analyses.
-On the one had, we fit a linear regression for each language, and on the other hand, we fit a linear mixed-effect to all the data pooled across languages, with language as a random effect.
-Figure \ref{fig:regressions_img} shows the coefficient estimate for each predictor in each language, and figure \ref{fig:regressions_all_img} shows the coefficient estimates for all languages combined (all predictors were centered and scaled).
-The findings were as follows.
-Overall, frequency is the most reliable predictor of age of acquisition.
-Word length predicts part of learning in some languages such as Croatian and Norwegian, but not in others (including English).
-It remains, however, a significant predictor in the global model.
-As for the factors of interest, i.e., semantic and phonological connectivities, we also found cross-linguistic differences.
-The phonological connectivity contributes to learning in languages such as Croatian, English and Russian, whereas semantic connectivity contributes to learning in Turkish, Spanish and to some extent in Croatian, but interestingly not in English\footnote{Semantic connectivity does not explain variance in English data beyond that explained by frequency and length.
-This contrasts with the original finding in Hills et al.
-2009.
-However, in this previous studiy, semantic connectivity was not tested in a model that included both frequency and length as covariates.
-Morever, our sample size is bigger.}.
-Despite this cross-linguistic variation, both phonological and semantic connectivity remain significant predictors in the global model.
-
-# Discussion
-
-The present study provided a comprehensive analysis of how lexical connectivity influences the age of acquisition of nouns in toddlers.
-We compared two network growth scenarios and assessed the relative contribution of phonological and semantic information in 8 languages.
-Part of the findings largely replicate the results obtained in @hills2009, i.e., semantic networks (based on free associations) grow by preferential acquisition, not by preferential attachment.
-Another finding was that phonological networks also grow primarily by preferential acquisition, especially when both scenarios (PAT and PAC) were pitted against each other in the same model.
-These findings generalize well across languages.
-Moreoever, both semantic and phonological connectivity in the learning environment (i.e., PAC) predict growth in a consistent way across many languages.
-However, when pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting part of learning in some languages, but not in others.
-Despite this coross-lingusitic variation, both phonological and semantic connectivity contribute to the overall learning (when data is pooled across languages).
-
-A major results of the study is that children start by learning words that have high phonological and semantic similarity with a variety of other words in the learning environment, not in the available lexicon.
-This suggests that children are sensitive to connectivity even without having first acquired the connected words!
+A major results of the study is that children start by learning words that have high phonological and semantic similarity with a variety of other words in the learning environment, not in the child's available lexicon.
+This suggests that children are sensitive to connectivity even without having first acquired the connected words.
 How can children indirectly detect highly connected words, and why would such words be more readily learned?
 In the semantic case, free association can be predicted through the patterns of word co-occurrence [@griffiths07], meaning that highly connected words tend to be the words that co-occur with many other words in various contexts.
-One possibility, suggested by @hills2010, is that the referents of such words are more easily disambiguated as demonstrated, for instance, by cross-situational learning experiments [@smith2008].
+One possibility, suggested by @hills2010, is that the referents of such words are more easily disambiguated from other potential referents.
+Such effect was demonstrated by cross-situational learning experiments [@smith2008].
 In the phonological case, connectivity is inherently correlated with phonotactic probability [@vitevitch1999].
 That is, highly connected words tend to be made of frequent sound sequences.
-We know even infant (whose vocabulary is still very rudimentary) develop a sensitivity for high frequency sound sequences in the ambient native language [@jusczyk1994].
+We know even infant (whose vocabulary is still very rudimentary) develop a sensitivity for high frequency sound sequences in the ambient language [@jusczyk1994].
 Interestingly, it was shown that phonotactic probability facilitates learning and recognition of novel words in toddlers and preschoolers [@storkel2001;  @higgins2014].
@@
 For instance, we used normative age of acquisition.
-However, individual children may not follow a unique learning trajectory.
-The use of longitudinal data would allow us to assess how the aggregate behavior relates to individual trajectories [e.g., typical vs.
+However, individual children may follow different learning trajectories.
+The use of longitudinal data would allow us to assess how the aggregate behavior relates to these individual trajectories [e.g., typical vs.
 late talkers, @beckage2011].
 Moreover, the results obtained in this study provide correlational but not causal evidence.
-Thus, conclusion drawn from our network analysis would require parallel evidence, especially through controlled behavioral experiments.
+Thus, conclusions drawn from our network analysis would require parallel evidence, especially from controlled behavioral experiments.
+
+\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}} \vspace{1em}
 

### 2018-01-23 cogsci/cogsci.tex
cogsci up-date and packrat

@@
 
-\title{The Role of Early Semantic and Phonological Networks in Noun Learning: a
-Cross-linguistic Analysis}
+\title{Word Learning as Network Growth: a Cross-linguistic Analysis}
 
@@
 \begin{abstract}
-Children tend to learn first the words that have a high density
-neighborhood in the lexical network (i.e., words that are connected to a
-variety of other words). However, the reason why connectivity influences
-learning is still not very well understood. Previous studies suggested
-this effect could be the consequence of the underlying learning
-mechanism. However, these studies focused on semantic networks and
-English data only, thus severely limiting the generality of the
-findings. Here we provide a systematic analysis of network growth models
-in both the phonological and the the semantic domains, and across 8
-languages. We replicate the results obtained by Hills et al. (2009) with
-English semantic networks, show that the same mechanism drives the
-growth of both semantic and phonological networks, and demonstrate that
-these effects hold cross-linguistically.
+Children tend to learn first the words that are highly connected in the
+lexical network (i.e., words that are connected to a variety of other
+words). The process by which connectivity in both the phonological and
+semantic netwoks come to influence word learning is still not very well
+understood. One view suggests that learning is driven primarily by
+\emph{internal} connectivity in the child's available lexicon. Another
+view suggests that \emph{external} connectivity in the learning
+environment is what makes words salient and readily learned. The present
+study tests both scenarios systematically in both the phonological and
+the the semantic domains, and across 8 languages. We generate the
+results obtained by Hills et al. (2009) with English semantic networks,
+and show that external connectivity in the learning environment, rather
+than internal connectivity, drives growth of both semantic and
+phonological networks. Finally, we demonstrate that these effects hold
+cross-linguistically.
 
 \textbf{Keywords:}
-keywords: semantic network, phonological network, word learning,
-semantic
+semantic network, phonological network, word learning
 \end{abstract}
@@
 
-A crucial question in language development is to understand why children
-learn some words at an earlier age than others. Previous studies
-documented various word properties that influence the age of
-acquisition. For example, it was shown that, within a lexical category,
-words that are more frequent in child-directed speech are acquired
-earlier (Goodman, Dale, \& Li, 2008). Other predictors include word
-length, the mean length of utterances in which the word occurs, and how
-concrete the word is (see Braginsky, Yurovsky, Marchman, \& Frank,
-2016). Besides these word-level properties, researchers found that the
-lexical structure (that is, the network that specifies how words relate
-to each other) also influences the learning process. For instance,
-children tend to produce first the words that have higher neighborhood
-density (i.g., high connectivity in the network) both at the
-phonological and the semantic level (Stokes, 2010; Storkel, 2009).
-However, it is still not very well understood \emph{why} connectivity in
-the lexical structure influences learning. Steyvers \& Tenenbaum (2005)
-suggested that this effect is nothing but the consequence of how these
-structures get constructed in the child's mind. According to this
-explanation (known as Preferential Attachment), highly connected words
-in the child's lexicon tend to ``attract'' more words over time, in a
-rich-get-richer scenario. Nonetheless, Hills, Maouene, Maouene, Sheya,
-\& Smith (2009) found that what biases the learning is not the
-connectivity in the child's internal lexicon but the connectivity in the
-learning environment.
+What factors shape vocabulary learning over the course of early
+childhood? To investigate this question, scientists have adopted
+multiple research strategies, from controlled laboratory experiments to
+corpus analysis. One strategy consists in documenting the timeline of
+words' acquisition, and studying the properies that make words easy or
+hard to learn. For example, within a lexical category, words that are
+more frequent in child-directed speech are acquired earlier (J. C.
+Goodman, Dale, \& Li, 2008). Other factors include word length, the mean
+length of utterances in which the word occurs, and how concrete the word
+is (see Braginsky, Yurovsky, Marchman, \& Frank, 2016).
 
-These analyses, however, focused on growth in semantic networks only. A
-recent study by Stella, Beckage, \& Brede (2017) analysed both semantic
-and phonological connectivity, but assumed only one growth model
-(preferential acquisition). More importantly, almost all available
-studies are limited in their generality because they focus almost
-exlusively on English data. The novely of this study is that it
-investigtes, for the first time, whether phonological networks grow by
-preferential attachement or preferential acquisition. It also provides a
-systematic comparision between network growth scenarios in both the
-phonological and the semantic domains and assess their relative
-contribution to the learning process. Moreover, it tests the generality
-of the findings across eight languages.
+Besides these word-level properties, researchers found that the lexical
+structure (that is, how words relate to each other) also influences the
+age of acquisition of words. The lexical structure is best characterized
+in terms of a network where each node represents a word in the
+vocabulary, and each link between two nodes represents a relationship
+between the corresponding pair of words. Previous studies investigated
+early vocabulary networks based on different word relations such as
+shared semantic features, target-cue relationship in free association
+norms, co-occurrence in child directed speech, and phonological
+similarity. These studies found that children tend to produce earlier
+the words that have higher neighborhood density (i.g., high connectivity
+in the network) both at the phonological and the semantic level
+(Beckage, Smith, \& Hills, 2011; Engelthaler \& Hills, 2017; Hills,
+Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya, \&
+Smith, 2009; Stella, Beckage, \& Brede, 2017; Stokes, 2010; Storkel,
+2009).
+
+A crucial question that naturally emerges from these analyses is how
+does network connectivity influence word learning? Steyvers \& Tenenbaum
+(2005) suggested that the effect of connectivity is the consequence of
+how the lexical network gets constructed in the child's mind. According
+to this explanation, known as Preferential Attachment (PAT), highly
+connected words in the child's lexicon tend to ``attract'' more words
+over time, in a rich-get-richer scenario (Barabasi \& Albert, 1999). In
+other words, what predicts word learning is \emph{internal} connectivity
+in the child's early lexicon. In contrast, Hills et al. (2009) found
+that what biases the learning is not the connectivity in the child's
+internal lexicon but, rather, \emph{external} connectivity in the
+learning environment. They called this alternative explanation
+Preferential Acquisition (PAC). Figure \ref{fig:growth} shows an
+illustration of both growth scenarios with the same simplified network.
+
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/growth-1}
+
+}
+
+\caption{\label{fig:growth}Illustration of the two growth models with the same network.
+Filled circles (I1-I4) represent known words (internal lexicon), and empty circles (E1 and E2) represent words that have not been learned yet (external lexicon).
+Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
+For PAT, each candidate node is characterized with the average degree (i.e., number of links) of the existing nodes that it would attach to.
+Thus, according to PAT, the node E1 is more likely to enter the lexicon first.
+For PAC, each candidate node is characterized with its degree in the entire network.
+According th PAC, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
+\end{figure}
+\end{CodeChunk}
+
+Studies that investigted lexical network growth focused on semantic
+networks using English data only (Hills et al., 2010, 2009; Steyvers \&
+Tenenbaum, 2005). The novelty of the current study is that it
+investigates whether phonological networks, like semantic networks, grow
+by PAC, or if they rather grow by PAT. It also provides a systematic
+comparision of network growth scenarios in both the phonological and the
+semantic domains and assesses their relative contribution to the
+learning process. Moreover, it tests the generality of the findings
+across eight languages.
 
@@
 used, the procedure we followed to construct both semantic and
-phonological networks, and the network growth scenarios we tested. Next,
-we show the results of the various analyses we conducted comparing
-network growth scenarios across languages. Then we compare the overall
-contribution of the networks in the learning process relative to other
-known predictors of age of acquisition (frequency and length). Finally
-we discuss the major results in relation to known experimental facts in
-language development.
+phonological networks. Next, we show the results of the various analyses
+we conducted comparing network growth scenarios across languages. Then
+we test the overall contribution of the networks in the learning process
+relative to other known predictors of age of acquisition (frequency and
+length). Finally we discuss the major results in relation to known
+experimental facts in language development.
 
@@
 developmental data of the MacArthur-Bates Communicative Development
-Inventory (CDI). The latter consists of parent report vocabulary
-checklists. We used the \emph{Words and Sentence} version which contains
-the productive vocabulary of toddlers (age varied between 16 to 35
-months). We included words that were produced by at least 50\% of
-children, and we considered that these words were learned at the month
-when this percentage was reached (Goodman et al., 2008). Moreover,
-following previous studies (Hills et al., 2009; e.g., Storkel, 2009), we
-restricted the analysis to the category of nouns, since there are known
+Inventory (CDI), a parent report vocabulary checklist. We used the
+\emph{Words and Sentence} version of the CDI which contains the
+productive vocabulary of toddlers (age varied between 16 to 36 months).
+Following previous studies (Hills et al., 2009; e.g., Storkel, 2009), we
+restricted our analysis to the category of nouns, since there are known
 discrepancies between the learning of nouns, predicates, and function
-words (e.g., Braginsky et al., 2016). We obtained these nouns in eight
-languages: Croatian, Danish, English, Italian, Norwegian, Russian,
-Spanish, and Turkish. We used the subset of nouns that had entries in
-the Florida Association Norms (see below). Since these norms are
-available only in English, we mapped words onto translation equivalents
-across CDI forms. This allowed us to use the English association norms
-across languages. Table \ref{tab:stats} gives an overview of the data
-used. The translation of non-English words is still an ongoing process.
-Note, however, that all languages have at least 60\% of nouns
-translated.
+words (e.g., Braginsky et al., 2016). The age of acquisition was defined
+by the month at which a word was produced by at least 50\% of children
+(J. C. Goodman et al., 2008).
+
+We obtained these nouns in eight languages: Croatian, Danish, English,
+Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of
+nouns that had entries in the Florida Association Norms (see below).
+Since these norms are available only in English, we used the translation
+of non-English words provided by Braginsky et al. (2016). This allowed
+us to use the English association norms across languages. Table
+\ref{tab:stats} gives an overview of the data used. The translation of
+non-English words is still an ongoing process. Note, however, that all
+languages have at least 60\% of nouns translated.
 
@@
 \caption{\label{tab:stats}Total number of productive nouns in the CDI (left).
-We used a subset of these nouns that have available English translations (middle), as well as entries in the Free Association Norms (right).}
+We used a subset of these nouns that had available English translations (middle).
+The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).}
 \end{table}
@@
 
-We used as index of semantic relatedness the Florida Free Association
+We used as an index of semantic relatedness the Florida Free Association
 Norms (Nelson, McEvoy, \& Schreiber, 1998). This dataset was collected
@@
 Following Hills et al. (2009), we used as a proxy for the learning
-environment, the network constructed using the full CDI data in each
-language (e.g., in English this corresponds to the network by 30
-months).
-
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/pred_ind_img-1}
-
-}
-
-\caption{\label{fig:pred_ind}Evaluation of individual network growth models using both  one-sample t-test over the z-score distribution of learned words (dotted), and model fitting (solid).
-Each dot represents, in the first case, the mean of the z-score distribution of the learned words with ranges representing 95\% confidence interval, and in the second case, the mean of the posterior distribution of the model's parameter, with ranges reppresenting 95\% credible intervals (computed using the highest density intervals).}\label{fig:pred_ind_img}
-\end{figure*}
-\end{CodeChunk}
+environment, the network constructed using the full set of nouns in the
+CDI data in each language (e.g., in English this corresponds to the
+network by 30 months).
 
@@
 substitutions) required to change one string into another. We generated
-approximate IPA forms from the orthographic transcription, across
-languages, using the open source text-to-speech software
-\textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.}. In
-previous studies, two nodes were linked if they had an edit distance of
-1 (Stokes, 2010; Storkel, 2009). However, in these previous studies the
-network was built using an adult vocabulary. Here, similar to the
+approximate International Phonetic Alphabet (IPA) trnascriptions from
+the orthographic transcription, across languages, using the open source
+text-to-speech software
+\textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.}
+
+In previous studies, two nodes were linked if they had an edit distance
+of 1 (Stokes, 2010; Storkel, 2009). However, in these previous studies
+the network was built using an adult vocabulary. Here, similar to the
 approximation we made for the semantic network, we used the full set of
@@
 
-\subsection{Network growth}\label{network-growth}
-
-We tested two network growth scenarios discussed in Hills et al. (2009).
-The first one was \emph{Preferential Attachment} (PAT). According to
-this mechanism, the network structure of known words predicts what words
-will be learned next. A word is more likely to be learned if it is
-linked to one of the highly connected nodes in this internal network.
-The second mechanism was \emph{Preferential Acquisition} (PAC). In this
-model, what predicts what word will enter the lexicon is not
-connectivity in the internal network, but connectivity in the learning
-environment. Figure \ref{fig:growth} shows an illustration of both
-growth scenarios with the same simplified network. For PAT, each
-candidate node was characterized with the average degree of the existing
-nodes that it would attach to. Thus, according to PAT, the node N1 is
-more likely to enter the lexicon first. For PAC, each candidate node was
-characterized with its degree in the entire network. According th PAC,
-the node N3 is more likely to enter the lexicon first.
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/growth-1}
-
-}
-
-\caption{\label{fig:growth}Illustration of the two growth models with the same network.
-Filled circles (A to D) represent known words, and empty circles (N1 to N3) represent words that have not been learned yet.
-Back lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant (from Hills et al.
-2009).}\label{fig:growth}
-\end{figure}
-\end{CodeChunk}
-
 \section{Analysis}\label{analysis}
 
-\subsection{Connectivity vs.~Age of
-acquisition}\label{connectivity-vs.age-of-acquisition}
-
-Preferential attachment and preferential acquisition provide different
-generative scenarios for the same end-state. The latter is defined here
-as the network corresponding to the oldest age for which we have CDI
-data. However in both cases, it is predicted that nodes with the higher
-degrees in this end-state are learned earlier than nodes with the lower
-degrees. Figure \ref{fig:data_all} shows how the age of acquisition for
-each word varies as a function of its degree (or indegree for the
-semantic network) in the end-state network. In order to compare this
-correlation across languages, the predictor (i.e., the degree) was
-centered and scaled. The plot shows a negative correlation between the
-month of acquisition and the degree (with the exception of the Russian
-semantic network), indicating that nouns with higher degrees are
-generally learned earlier.
+We start by examining how connectivity in the global netowrk influences
+the age of acqusition. Regardless of the growth mechanism that might
+have given rise to this netowrk (i.e., PAC or PAT), we expect nodes with
+the higher degrees in this network to be learned earlier than nodes with
+the lower degrees. The network was constructed using nouns at the oldest
+age for which we have CDI data. Figure \ref{fig:data_all} shows how the
+age of acquisition for each word varies as a function of its degree (or
+indegree for the semantic network). For ease of visual comparison, the
+predictor (i.e., the degree) was centered and scaled across languages.
+The plots show, overall, a negative correlation between the month of
+acquisition and the degree, indicating that nouns with higher degrees
+are generally learned earlier.
 
@@
 
-{\centering \includegraphics{figs/pred_comb_img-1}
+{\centering \includegraphics{figs/pred_ind_img-1}
 
@@
 
-\caption{\label{fig:pred_comb_img}Estimates of the growth models' parameters in each language.
-Dots represent the means of the posteriori distribution of the parameters, and ranges represent 95\% credible intervals (computed using the highest density intervals).
-}\label{fig:pred_comb_img}
+\caption{\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid).
+Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\% credible intervals (computed using the highest density intervals).}\label{fig:pred_ind_img}
 \end{figure*}
@@
 
-Following Hills et al. (2009), we evaluated the growth models in two
-separate ways. The first evaluation consists in determining, in each
-month, the model-dependent growth value distribution of all words that
-could possibly be learned at this month, and then computing the z-score
-of each learned word with respect to this distribution. For each model,
-we tested if the distribution constituted by the z-scores of all learned
-words was different from zero, using a one-sample t-test. The results
-are shown in Figure \ref{fig:pred_ind}.
+\subsubsection{How does each growth scenario predict noun
+development?}\label{how-does-each-growth-scenario-predict-noun-development}
 
-The second evaluation consists in fitting an explicit model to the data.
-The purpose of this second evaluation is, first, to validate the
-findings obtained with the one-sample t-test, and second, to determine
-(in a next step) the relative contribution of each network growth
-scenario (PAT vs.~PAC) across domains (phonological vs.~semantic).
-
-We proceeded as follows. We calculated the probability that a word
-\(w_i\), with a growth value \(d_i\) would enter the lexicon at a given
-month, using a softmax function:
+To test the network growth scenarios, we fit different growth models to
+the data. We proceeded as follows. We calculated the probability that a
+word \(w_i\), with a growth value \(d_i\) would enter the lexicon at a
+given month, using a softmax function:
 
@@
 Where \(\beta\) is the fitting parameter. A positive value of \(\beta\)
-means that words with higher groth values \(d_i\) are acquired first,
+means that words with higher growth values \(d_i\) are acquired first,
 and a negative value means that words with lower growth values are
-acquired first. The normalization included words that were not yet
-learned at the month the word at hand was acquired. We estimated the
-parameter \(\beta\) using a Bayesian approach. We started with a uniform
+acquired first. As explained in Figure \ref{fig:growth}, each candidate
+word \(w_i\) is characterized with a growth values \(d_i\) that depends
+on the growth scenario tested. The normalization includes all words that
+could be learned at that month.
+
+We estimated the parameter \(\beta\) using a Bayesian approach. The
+inference was performed using the probabilisitic programming language
+WebPPL (N. Goodman \& Stuhlmüller, 2014). We started with a uniform
 distribution, and at each month, we computed the likelihood function
@@
 
+Besides fitting a growth model to the data, we conducted another
+evaluation. This second evaluation consists in determining, in each
+month, the model-dependent growth value distribution of all words that
+could possibly be learned at this month, and then computing the z-score
+of each learned word with respect to this distribution. For each model,
+we tested if the distribution constituted by the z-scores of all learned
+words was different from zero, using a one-sample t-test.
+
 The results from both evaluations were very similar and lead essentially
-to the same conclusions. For the semantic networks, the results
-replicate Hills et al.'s finding in English, which was that the semantic
-network grows by PAC, not by PAT. Moreover, it generalizes this finding
-to all other languages (with the exception of Russian). For the
-phonological network, the results show that, generally speaking, PAC
-fits the developmental trajectory better than PAT in all languages. We
-note however that PAT, though weaker, fares better for the phonological
-networks than it does for the semantic networks. In the former, it
-predicts part of the growth process in some languages such as Croatian,
-English, Norwegian and Russian. In the latter, it is rather universally
-unpredictive.
+to the same
+conclusions\footnote{we do not show here the resuts of the second evaluation because they were redundant with the results of the first evaluation}.
+For the semantic network, the results replicate Hills et al.'s finding
+in English, which was that the semantic network grows by PAC, not by
+PAT. Moreover, it generalizes this finding to all other languages (with
+the exception of Russian). For the phonological network, the results
+show that, generally speaking, PAC again fits the developmental
+trajectory better than PAT. We note however that PAT, though weaker,
+fares better for the phonological networks (where it predicts part of
+the growth process in some languages such as Croatian, English,
+Norwegian and Russian) than it does for the semantic networks (where it
+is rather universally unpredictive).
+
+\subsubsection{What is the relative contribution of each growth
+model?}\label{what-is-the-relative-contribution-of-each-growth-model}
 
@@
 This was done through adding more fitting parameters to the model, that
-is, by substituting \(\beta d_i\) in equation (1) with:
+is, by substituting \(\beta d_i\) in formula (1) with:
 \[\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}\]
@@
 PhonoPAC. Using the same fitting technique, we obtained the values shown
-in Figure \ref{fig:pred_comb_img}. In term of growth scenarios, we found
-that PAC dominates the learning. In particular, though we found
-previously that phonological PAT predicted part of the learning in some
-languages when tested individually, here PAT appears to lose its
-predictive power when pitted against phonological PAC. In terms of
-domain (phonological vs.~semantic), both phonological and semantic
-networks appear to contribute to learning, although the phonological
-network appears to be stronger and more reliable across languages. In
-summary, the findings show that both semantic and phonological networks
-grow primarily through preferential acquisition, and that, generally
-speaking, semantic and phonological networks both contribute to the
-learning process.
+in Figure \ref{fig:pred_ind}. In term of growth scenarios, we found that
+PAC dominates the learning. In particular, though we found previously
+that phonological PAT predicted part of the learning in some languages
+when tested individually, here PAT appears to lose its predictive power
+when pitted against phonological PAC. In terms of domain, both
+phonological and semantic networks appear to contribute to learning,
+although the phonological network appears to be stronger and more
+reliable across languages. In summary, the findings show that both
+semantic and phonological networks grow primarily by PAC, and that,
+generally speaking, semantic and phonological networks both contribute
+to the learning process.
 
@@
 
-\subsection{The big picture: comparison to other known predictors of age
-of
-acquisition}\label{the-big-picture-comparison-to-other-known-predictors-of-age-of-acquisition}
+\subsection{Comparison to other known predictors of age of
+acquisition}\label{comparison-to-other-known-predictors-of-age-of-acquisition}
 
@@
 other factors. The first one is word frequency, a well studied factor
-shown to predict the age of acquisition in a reliable fashion (e.g.
-Goodman et al., 2008). The second factor is word length because it
+shown to predict the age of acquisition in a reliable fashion (e.g. J.
+C. Goodman et al., 2008). The second factor is word length, which
 correlates with phonological connectivity (Pisoni, Nusbaum, Luce, \&
@@
 Since PAT was uninformative, we dropped it from this analysis. Thus, we
-no longer needed to to fit the growth model month-by-month as in the
+no longer needed to fit the growth model month-by-month as in the
 previous section. In fact, word utilities in the case of PAC are fixed,
@@
 as daddy). For word length, we used our generated IPA transcription.
-This allowed us to get a more accurate estimate of word length across
-languages than the number of characters in the orthographic
-transcription.
 
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/regressions_all_img-1}
-
-}
-
-\caption{\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined model.
-Ranges indicate 95\% confidence intervals.
-Fade color indicates estimates of PAC predictors in a model that does not include frequency and length as covariates.}\label{fig:regressions_all_img}
-\end{figure}
-\end{CodeChunk}
-
-We conducted two analyses. On the one had, we fit a linear regression
-for each language, and on the other hand, we fit a linear mixed-effect
-to all the data pooled across languages, with language as a random
-effect. Figure \ref{fig:regressions_img} shows the coefficient estimate
-for each predictor in each language, and figure
-\ref{fig:regressions_all_img} shows the coefficient estimates for all
-languages combined (all predictors were centered and scaled). The
-findings were as follows. Overall, frequency is the most reliable
-predictor of age of acquisition. Word length predicts part of learning
-in some languages such as Croatian and Norwegian, but not in others
-(including English). It remains, however, a significant predictor in the
-global model. As for the factors of interest, i.e., semantic and
-phonological connectivities, we also found cross-linguistic differences.
-The phonological connectivity contributes to learning in languages such
-as Croatian, English and Russian, whereas semantic connectivity
-contributes to learning in Turkish, Spanish and to some extent in
-Croatian, but interestingly not in
-English\footnote{Semantic connectivity does not explain variance in English data beyond that explained by frequency and length.
+We conducted two analyses. We fit a linear regression for each language,
+and we fit a linear mixed-effect to all the data pooled across
+languages, with language as a random effect. Figure
+\ref{fig:regressions_img} shows the coefficient estimate for each
+predictor in each language, and figure \ref{fig:regressions_all_img}
+shows the coefficient estimates for all languages combined (all
+predictors were centered and scaled). The findings were as follows.
+Overall, frequency is the largest and most consistent predictor of age
+of acquisition. Word length predicts learning in some languages such as
+Croatian and Norwegian, but not in others (including English). It
+remains, however, a significant predictor in the global model. As for
+the factors of interest, i.e., semantic and phonological connectivity,
+we also found cross-linguistic differences. The phonological
+connectivity contributes to learning in languages such as Croatian,
+English and Russian, whereas semantic connectivity contributes to
+learning in Turkish, Spanish and to some extent in Croatian, but
+interestingly not in
+English\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
 This contrasts with the original finding in Hills et al.
 2009.
-However, in this previous studiy, semantic connectivity was not tested in a model that included both frequency and length as covariates.
-Morever, our sample size is bigger.}.
+However, in this previous study, semantic connectivity was not tested in a model that included both frequency and length as covariates.
+Another important difference is the number of words tested.
+Our study uses a larger set of nouns.}.
 Despite this cross-linguistic variation, both phonological and semantic
@@
 frequency and length), the effect of word connectivity shows a
-cross-linguistic variation, predicting part of learning in some
-languages, but not in others. Despite this coross-lingusitic variation,
-both phonological and semantic connectivity contribute to the overall
+cross-linguistic variation, predicting learning in some languages, but
+not in others. Despite this cross-lingusitic variation, both
+phonological and semantic connectivity contribute to the overall
 learning (when data is pooled across languages).
+
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/regressions_all_img-1}
+
+}
+
+\caption{\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined model pooling across languages .
+Ranges indicate 95\% confidence intervals.
+Fade color indicates estimates of PAC predictors in a model that does not include frequency and length as covariates.}\label{fig:regressions_all_img}
+\end{figure}
+\end{CodeChunk}
 
@@
 that have high phonological and semantic similarity with a variety of
-other words in the learning environment, not in the available lexicon.
-This suggests that children are sensitive to connectivity even without
-having first acquired the connected words! How can children indirectly
-detect highly connected words, and why would such words be more readily
-learned? In the semantic case, free association can be predicted through
-the patterns of word co-occurrence (Griffiths, Steyvers, \& Tenenbaum,
-2007), meaning that highly connected words tend to be the words that
-co-occur with many other words in various contexts. One possibility,
-suggested by Hills, Maouene, Riordan, \& Smith (2010), is that the
-referents of such words are more easily disambiguated as demonstrated,
-for instance, by cross-situational learning experiments (Smith \& Yu,
-2008). In the phonological case, connectivity is inherently correlated
-with phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999).
-That is, highly connected words tend to be made of frequent sound
-sequences, and vice versa. We know even infant (whose vocabulary is
+other words in the learning environment, not in the child's available
+lexicon. This suggests that children are sensitive to connectivity even
+without having first acquired the connected words. How can children
+indirectly detect highly connected words, and why would such words be
+more readily learned? In the semantic case, free association can be
+predicted through the patterns of word co-occurrence (Griffiths,
+Steyvers, \& Tenenbaum, 2007), meaning that highly connected words tend
+to be the words that co-occur with many other words in various contexts.
+One possibility, suggested by Hills et al. (2010), is that the referents
+of such words are more easily disambiguated from other potential
+referents. Such effect was demonstrated by cross-situational learning
+experiments (Smith \& Yu, 2008). In the phonological case, connectivity
+is inherently correlated with phonotactic probability (Vitevitch, Luce,
+Pisoni, \& Auer, 1999). That is, highly connected words tend to be made
+of frequent sound sequences. We know even infant (whose vocabulary is
 still very rudimentary) develop a sensitivity for high frequency sound
-sequences in the ambient native language (Jusczyk, Luce, \&
-Charles-Luce, 1994). Interestingly, it was shown that phonotactic
-probability facilitates learning and recognition of novel words in
-toddlers and preschoolers (MacRoy-Higgins, Shafer, Schwartz, \& Marton,
-2014; Storkel, 2001). Thus, children's ability to keep track of
-co-occurrence statistics (both at the semantic and phonological level)
-might explain their apparent sensitivity and preference for high
-connectivity in the lexical network.
+sequences in the ambient language (Jusczyk, Luce, \& Charles-Luce,
+1994). Interestingly, it was shown that phonotactic probability
+facilitates learning and recognition of novel words in toddlers and
+preschoolers (MacRoy-Higgins, Shafer, Schwartz, \& Marton, 2014;
+Storkel, 2001). Thus, children's ability to keep track of co-occurrence
+statistics (both at the semantic and phonological level) might explain
+their sensitivity and preference for highly connected words in the
+learning envirnoment.
 
@@
 using similar datasets. For instance, we used normative age of
-acquisition. However, individual children may not follow a unique
-learning trajectory. The use of longitudinal data would allow us to
-assess how the aggregate behavior relates to individual trajectories
-(e.g., typical vs.~late talkers, Beckage, Smith, \& Hills, 2011).
-Moreover, the results obtained in this study provide correlational but
-not causal evidence. Thus, conclusion drawn from our network analysis
-would require parallel evidence, especially through controlled
-behavioral experiments.
+acquisition. However, individual children may follow different learning
+trajectories. The use of longitudinal data would allow us to assess how
+the aggregate behavior relates to these individual trajectories (e.g.,
+typical vs.~late talkers, Beckage et al., 2011). Moreover, the results
+obtained in this study provide correlational but not causal evidence.
+Thus, conclusions drawn from our network analysis would require parallel
+evidence, especially from controlled behavioral experiments.
+
+\vspace{1em}
+
+\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}}
+\vspace{1em}
 
@@
 \hypertarget{refs}{}
+\hypertarget{ref-barabasi99}{}
+Barabasi, A.-L., \& Albert, R. (1999). Emergence of scaling in random
+networks. \emph{Science}, \emph{286}(5439), 509--512.
+
 \hypertarget{ref-beckage2011}{}
@@
 
+\hypertarget{ref-engelthaler2017}{}
+Engelthaler, T., \& Hills, T. T. (2017). Feature biases in early word
+learning: Network distinctiveness predicts age of acquisition.
+\emph{Cognitive Science}, \emph{41}, 120--140.
+
 \hypertarget{ref-frank2017}{}
@@
 Language}, \emph{35}(3), 515--531.
+
+\hypertarget{ref-dippl}{}
+Goodman, N., \& Stuhlmüller, A. (2014). The Design and Implementation of
+Probabilistic Programming Languages. \url{http://dippl.org}.
 

### 2018-01-25 Main.Rmd
cogsci up-date and packrat
changes in CogSci manuscript

@@
 
+Here do the power-law analysis and the log-log plots
+
+```{r}
+#make a loop
+degreeDist <- data.frame(matrix(ncol = 4, nrow = 0))
+x <- c("x", "y", "dimension", "language")
+colnames(degreeDist) <- x
+
+for (i in language_dict$language_name) {
+  #Select data for the language
+  data_lang <- data_first_month %>%
+    filter(language == i) %>%
+    select(language, PAC_assoc, PAC_phono_t2) %>%
+    rename(Sem = PAC_assoc, Phono = PAC_phono_t2) %>%
+    filter (!is.na(Sem),!is.na(Phono))
+
+  #Do the transfomation
+  semList <- data_lang$Sem[data_lang$Sem != 0]
+  sem_pl = displ$new(semList)
+  sem_est = estimate_xmin(sem_pl)
+  sem_pl$setXmin(sem_est)
+  sem_dist = plot(sem_pl) %>%
+    mutate(dimension='Sem', language  =  i)
+
+  phonoList <- data_lang$Phono[data_lang$Phono != 0]
+  phono_pl = displ$new(phonoList)
+  phono_est = estimate_xmin(phono_pl)
+  phono_pl$setXmin(phono_est)
+  phono_dist = plot(phono_pl) %>%
+    mutate(dimension='Phono', language = i)
+
+  dist_lang <- bind_rows(sem_dist, phono_dist)
+
+  degreeDist <- bind_rows(degreeDist, dist_lang)
+
+}
+
+feather::write_feather(degreeDist, "saved_data/degreeDist.feather")
+degreeDist <- feather::read_feather("saved_data/degreeDist.feather")
+
+#plot cumulative distributions
+ggplot(data = degreeDist,  aes(x=x, y=y, col=dimension))+
+  facet_grid(. ~ language)+#, scales = "free") +
+  geom_point(#aes(colour = lexical_class),
+    #colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  scale_y_log10() + scale_x_log10() +
+  theme(aspect.ratio = 1)
+  #scale_x_continuous(limits=c(-2,5))+
+  #geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
+  #scale_colour_solarized(name = "")
+
+```
+
 Here do the statistics
@@
 
-Prepare data for age of acqusition analysis (regressions)
+Prepare data for age of acquisition analysis (regressions)
 
@@
 
+individ <- individual_both %>%
+
 ```

### 2018-01-25 cogsci/cogsci.Rmd
changes in CogSci manuscript

@@
 abstract:
-    "Children tend to learn first the words that are highly connected in the lexical network (i.e., words that are connected to a variety of other words).
-The process by which connectivity in both the phonological and semantic netwoks come to influence word learning is still not very well understood.
-One view suggests that learning is driven primarily by *internal* connectivity in the child's available lexicon.
-Another view suggests that *external* connectivity in the learning environment is what makes words salient and readily learned.
-The present study tests both scenarios systematically in both the phonological and the the semantic domains, and across 8 languages.
-We generate the results obtained by Hills et al.
-(2009) with English semantic networks, and show that external connectivity in the learning environment, rather than internal connectivity, drives growth of both semantic and phonological networks.
-Finally, we demonstrate that these effects hold cross-linguistically."
+
+    "Children tend to produce first the words that are connected to a variety of other words along both the phonological and the semantic dimensions.
+Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.
+One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's ealy lexicon attract similar words.
+Another view suggests that learning is driven, not by highly connected words in the early internal lexicon, but by highly connected word in the external learning environment.
+The present study tests both scenarios systematically in both the phonological and the semantic domains, and across 8 languages.
+We show that external connectivity in the learning environment drives growth in both the semantic and the phonological networks, and that this pattern is consistent cross-linguistically.
+The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment."
 
 keywords:
-    "semantic network, phonological network, word learning"
+    "semantic network, phonological network, network growth, mechanism of word learning"
 
@@
 
+<!-- Children tend to learn some words typically at an earlier age than others.
+Researchers have documented many word properties that influence the order of acquisition of words.
+This paper investigates strcutural properties that characterize how words are related to each other in the lexicon.
+-->
 ```{r global_options, include=FALSE}
@@
 To investigate this question, scientists have adopted multiple research strategies, from controlled laboratory experiments to corpus analysis.
-One strategy consists in documenting the timeline of words' acquisition, and studying the properies that make words easy or hard to learn.
+One strategy consists in documenting the timeline of words' acquisition, and studying the properties that make words easy or hard to learn.
 For example, within a lexical category, words that are more frequent in child-directed speech are acquired earlier [@goodman2008].
@@
 
-Studies that investigted lexical network growth focused on semantic networks using English data only [@steyvers2005; @hills2009; @hills2010].
+Studies that investigated lexical network growth focused on semantic networks using English data only [@steyvers2005; @hills2009; @hills2010].
 The novelty of the current study is that it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT.
-It also provides a systematic comparision of network growth scenarios in both the phonological and the semantic domains and assesses their relative contribution to the learning process.
+It also provides a systematic comparison of network growth scenarios in  the phonological and the semantic domains and assesses their relative contribution to the learning process.
 Moreover, it tests the generality of the findings across eight languages.
@@
 Then we test the overall contribution of the networks in the learning process relative to other known predictors of age of acquisition (frequency and length).
-Finally we discuss the major results in relation to known experimental facts in language development.
+Finally we discuss the major results in relation to known experimental facts in language development, and we speculate about the potential learning mechanism that might drive early vocabulary learning.
 
@@
   theme_bw()+
+  #theme_bw()+
   theme(aspect.ratio = 0.7, 
@@
 
+```{r }
+
+#Import data from saved
+degreeDist <- feather::read_feather("../saved_data/degreeDist.feather")
+
+plot_dist <- ggplot(data = degreeDist,  aes(x=x, y=y, col=dimension))+
+  facet_grid(. ~ language)+
+  geom_point(size = 0.5, alpha = 0.5) +
+  scale_y_log10() + scale_x_log10() +
+  theme_bw()+
+  theme(aspect.ratio = 1)+
+  xlab("degree") +ylab("probability")
+
+ggsave("figs/degreeDist.png", plot = plot_dist, width = 7, height = 3)
+
+```
+
+```{r degree_distribution, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
+A perfect power law distribution should appear as a straight line in this graph."}
+plot_dist
+#img <- png::readPNG("figs/data_all.png")
+#grid::grid.raster(img)
+
+```
+
 # Networks
-
 ## Data
-
 We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist.
 We used the *Words and Sentence* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months).
-Following previous studies [e.g., @storkel2009; @hills2009], we restricted our analysis to the category of nouns, since there are known discrepancies between the learning of nouns, predicates, and function words [e.g., @braginsky2016].
+Following previous studies [e.g., @storkel2009; @hills2009], we restricted our analysis to the category of nouns.
 The age of acquisition was defined by the month at which a word was produced by at least 50% of children [@goodman2008].
@@
 
-With this data, we constructed both semantic and phonological networks.
-
 ## Semantic networks
@@
 Each node was characterized by its "indegree", which represents the number of links for which the word was the target.
+To model growth from month to month, we constructed a different network at each month, made of words that have been learned at that month.
 Following @hills2009, we used as a proxy for the learning environment, the network constructed using the full set of nouns in the CDI data in each language (e.g., in English this corresponds to the network by 30 months).
@@
 The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.
-We generated approximate International Phonetic Alphabet (IPA) trnascriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).**
+We generated approximate International Phonetic Alphabet (IPA) transcriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).**
 
@@
 Each node was characterized with its degree, i.e., the number of links it shares with other words.
+<!-- Moreover, and in order to model growth from month to month, we constructed a different network at each month, made of words that have been learned at that month.
+-->
 
@@
 
-We start by examining how connectivity in the global netowrk influences the age of acqusition.
-Regardless of the growth mechanism that might have given rise to this netowrk (i.e., PAC or PAT), we expect nodes with the higher degrees in this network to be learned earlier than nodes with the lower degrees.
-The network was constructed using nouns at the oldest age for which we have CDI data.
+## Preliminary analysis
+We start by examining how connectivity in the global network influences the age of acquisition.
+Regardless of the growth mechanism that might have given rise to this network (i.e., PAC or PAT), we expect nodes with the higher degrees in this network to be learned earlier than nodes with the lower degrees.
+The global network was constructed using nouns at the oldest age for which we have CDI data.
 Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network).
@@
 
+We also analysed the global network degree distribution.
+PAT is known to generate networks with a power-law degree distribution [@barabasi99].
+Thus, if the networks display this property, it means that PAT cannot be ruled out *a priori* as a potential growth mechanism.
+In contrast, if there is strong evidence against a power law distribution, then PAT (but not PAC) can be ruled out.
+The distributions are shown in Figure \ref{fig:degree_distribution}.
+Overall, the results do not provide strong evidence against a power-law distribution.
+Moreover, the degree to which the distribution approximates a power law varies across dimension and languages.
+For a more conclusive test, we fit explicit growth models to the data (next section).
 <!--
@@
 As explained in Figure \ref{fig:growth}, each candidate word $w_i$ is characterized with a growth values $d_i$ that depends on the growth scenario tested.
+In PAT, the growth value of a given word is equal to the average degree of the existing nodes that it would attach to.
+In PAC, the growth value of a word is equal to its degree in the entire network.
 The normalization includes all words that could be learned at that month.
@@
 We estimated the parameter $\beta$ using a Bayesian approach.
-The inference was performed using the probabilisitic programming language  WebPPL [@dippl].
+The inference was performed using the probabilistic programming language  WebPPL [@dippl].
 We started with a uniform distribution, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been actually learned at that month (using formula 1).
@@
 
-The results from both evaluations were very similar and lead essentially to the same conclusions\footnote{we do not show here the resuts of the second evaluation because they were redundant with the results of the first evaluation}.
+The results from both evaluations were very similar and lead essentially to the same conclusions\footnote{we do not show here the results of the second evaluation because they were redundant with the results of the first evaluation}.
 For the semantic network, the results replicate Hills et al.'s finding in English, which was that the semantic network grows by PAC, not by PAT.
@@
 @goodman2008].
-The second factor is word length, which correlates with phonological connectivity [@pisoni1985].
+The second factor is word length, which correlates with phonological connectivity.
+<!-- [@pisoni1985].-->
 
@@
 These findings generalize well across languages.
-Moreoever, both semantic and phonological connectivity in the learning environment (i.e., PAC) predict growth in a consistent way across many languages.
+Moreover, both semantic and phonological connectivity in the learning environment (i.e., PAC) predict growth in a consistent way across many languages.
 However, when pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting learning in some languages, but not in others.
-Despite this cross-lingusitic variation, both phonological and semantic connectivity contribute to the overall learning (when data is pooled across languages).
+Despite this cross-linguistic variation, both phonological and semantic connectivity contribute to the overall learning (when data is pooled across languages).
 
@@
 Such effect was demonstrated by cross-situational learning experiments [@smith2008].
+
 In the phonological case, connectivity is inherently correlated with phonotactic probability [@vitevitch1999].
@@
 Interestingly, it was shown that phonotactic probability facilitates learning and recognition of novel words in toddlers and preschoolers [@storkel2001;  @higgins2014].
-Thus, children's ability to keep track of co-occurrence statistics (both at the semantic and phonological level) might explain their sensitivity and preference for highly connected words in the learning envirnoment.
+Thus, children's ability to keep track of co-occurrence statistics (both at the semantic and phonological level) might explain their sensitivity and preference for highly connected words in the learning environment.
 
 Finally, this study shares a number of limitations with previous studies using similar datasets.
-For instance, we used normative age of acquisition.
+<!--For instance, we used normative age of acquisition.
 However, individual children may follow different learning trajectories.
@@
 late talkers, @beckage2011].
-Moreover, the results obtained in this study provide correlational but not causal evidence.
-Thus, conclusions drawn from our network analysis would require parallel evidence, especially from controlled behavioral experiments.
+Moreover,--> In particular, the results provide correlational but not causal evidence.
+Thus, the conclusions of this study  require parallel evidence, especially from controlled behavioral experiments.
 

### 2018-01-25 cogsci/cogsci.tex
changes in CogSci manuscript

@@
 \begin{abstract}
-Children tend to learn first the words that are highly connected in the
-lexical network (i.e., words that are connected to a variety of other
-words). The process by which connectivity in both the phonological and
-semantic netwoks come to influence word learning is still not very well
-understood. One view suggests that learning is driven primarily by
-\emph{internal} connectivity in the child's available lexicon. Another
-view suggests that \emph{external} connectivity in the learning
-environment is what makes words salient and readily learned. The present
-study tests both scenarios systematically in both the phonological and
-the the semantic domains, and across 8 languages. We generate the
-results obtained by Hills et al. (2009) with English semantic networks,
-and show that external connectivity in the learning environment, rather
-than internal connectivity, drives growth of both semantic and
-phonological networks. Finally, we demonstrate that these effects hold
-cross-linguistically.
+Children tend to produce first the words that are connected to a variety
+of other words along both the phonological and the semantic dimensions.
+Though this connectivity effect has been extensively documented, little
+is known about the underlying developmental mechanism. One view suggests
+that learning is primarily driven by a network growth model where highly
+connected words in the child's ealy lexicon attract similar words.
+Another view suggests that learning is driven, not by highly connected
+words in the early internal lexicon, but by highly connected word in the
+external learning environment. The present study tests both scenarios
+systematically in both the phonological and the semantic domains, and
+across 8 languages. We show that external connectivity in the learning
+environment drives growth in both the semantic and the phonological
+networks, and that this pattern is consistent cross-linguistically. The
+findings suggest a word learning mechanism where children harness their
+statistical learning abilities to (indirectly) detect and learn highly
+connected words in the learning environment.
 
 \textbf{Keywords:}
-semantic network, phonological network, word learning
+semantic network, phonological network, network growth, mechanism of
+word learning
 \end{abstract}
@@
 corpus analysis. One strategy consists in documenting the timeline of
-words' acquisition, and studying the properies that make words easy or
+words' acquisition, and studying the properties that make words easy or
 hard to learn. For example, within a lexical category, words that are
@@
 
-Studies that investigted lexical network growth focused on semantic
+Studies that investigated lexical network growth focused on semantic
 networks using English data only (Hills et al., 2010, 2009; Steyvers \&
@@
 by PAC, or if they rather grow by PAT. It also provides a systematic
-comparision of network growth scenarios in both the phonological and the
+comparison of network growth scenarios in the phonological and the
 semantic domains and assesses their relative contribution to the
@@
 length). Finally we discuss the major results in relation to known
-experimental facts in language development.
+experimental facts in language development, and we speculate about the
+potential learning mechanism that might drive early vocabulary learning.
 
@@
 
+\begin{CodeChunk}
+\begin{figure*}[h]
+
+{\centering \includegraphics{figs/degree_distribution-1}
+
+}
+
+\caption{\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
+A perfect power law distribution should appear as a straight line in this graph.}\label{fig:degree_distribution}
+\end{figure*}
+\end{CodeChunk}
+
 \section{Networks}\label{networks}
@@
 Following previous studies (Hills et al., 2009; e.g., Storkel, 2009), we
-restricted our analysis to the category of nouns, since there are known
-discrepancies between the learning of nouns, predicates, and function
-words (e.g., Braginsky et al., 2016). The age of acquisition was defined
-by the month at which a word was produced by at least 50\% of children
-(J. C. Goodman et al., 2008).
+restricted our analysis to the category of nouns. The age of acquisition
+was defined by the month at which a word was produced by at least 50\%
+of children (J. C. Goodman et al., 2008).
 
@@
 
-With this data, we constructed both semantic and phonological networks.
-
 \subsection{Semantic networks}\label{semantic-networks}
@@
 which represents the number of links for which the word was the target.
+To model growth from month to month, we constructed a different network
+at each month, made of words that have been learned at that month.
 Following Hills et al. (2009), we used as a proxy for the learning
@@
 substitutions) required to change one string into another. We generated
-approximate International Phonetic Alphabet (IPA) trnascriptions from
+approximate International Phonetic Alphabet (IPA) transcriptions from
 the orthographic transcription, across languages, using the open source
@@
 
-We start by examining how connectivity in the global netowrk influences
-the age of acqusition. Regardless of the growth mechanism that might
-have given rise to this netowrk (i.e., PAC or PAT), we expect nodes with
+\subsection{Preliminary analysis}\label{preliminary-analysis}
+
+We start by examining how connectivity in the global network influences
+the age of acquisition. Regardless of the growth mechanism that might
+have given rise to this network (i.e., PAC or PAT), we expect nodes with
 the higher degrees in this network to be learned earlier than nodes with
-the lower degrees. The network was constructed using nouns at the oldest
-age for which we have CDI data. Figure \ref{fig:data_all} shows how the
-age of acquisition for each word varies as a function of its degree (or
-indegree for the semantic network). For ease of visual comparison, the
-predictor (i.e., the degree) was centered and scaled across languages.
-The plots show, overall, a negative correlation between the month of
-acquisition and the degree, indicating that nouns with higher degrees
-are generally learned earlier.
+the lower degrees. The global network was constructed using nouns at the
+oldest age for which we have CDI data. Figure \ref{fig:data_all} shows
+how the age of acquisition for each word varies as a function of its
+degree (or indegree for the semantic network). For ease of visual
+comparison, the predictor (i.e., the degree) was centered and scaled
+across languages. The plots show, overall, a negative correlation
+between the month of acquisition and the degree, indicating that nouns
+with higher degrees are generally learned earlier.
+
+We also analysed the global network degree distribution. PAT is known to
+generate networks with a power-law degree distribution (Barabasi \&
+Albert, 1999). Thus, if the networks display this property, it means
+that PAT cannot be ruled out \emph{a priori} as a potential growth
+mechanism. In contrast, if there is strong evidence against a power law
+distribution, then PAT (but not PAC) can be ruled out. The distributions
+are shown in Figure \ref{fig:degree_distribution}. Overall, the results
+do not provide strong evidence against a power-law distribution.
+Moreover, the degree to which the distribution approximates a power law
+varies across dimension and languages. For a more conclusive test, we
+fit explicit growth models to the data (next section).
 
@@
 word \(w_i\) is characterized with a growth values \(d_i\) that depends
-on the growth scenario tested. The normalization includes all words that
-could be learned at that month.
+on the growth scenario tested. In PAT, the growth value of a given word
+is equal to the average degree of the existing nodes that it would
+attach to. In PAC, the growth value of a word is equal to its degree in
+the entire network. The normalization includes all words that could be
+learned at that month.
 
 We estimated the parameter \(\beta\) using a Bayesian approach. The
-inference was performed using the probabilisitic programming language
+inference was performed using the probabilistic programming language
 WebPPL (N. Goodman \& Stuhlmüller, 2014). We started with a uniform
@@
 to the same
-conclusions\footnote{we do not show here the resuts of the second evaluation because they were redundant with the results of the first evaluation}.
+conclusions\footnote{we do not show here the results of the second evaluation because they were redundant with the results of the first evaluation}.
 For the semantic network, the results replicate Hills et al.'s finding
@@
 C. Goodman et al., 2008). The second factor is word length, which
-correlates with phonological connectivity (Pisoni, Nusbaum, Luce, \&
-Slowiaczek, 1985).
+correlates with phonological connectivity.
 
@@
 were pitted against each other in the same model. These findings
-generalize well across languages. Moreoever, both semantic and
+generalize well across languages. Moreover, both semantic and
 phonological connectivity in the learning environment (i.e., PAC)
@@
 cross-linguistic variation, predicting learning in some languages, but
-not in others. Despite this cross-lingusitic variation, both
+not in others. Despite this cross-linguistic variation, both
 phonological and semantic connectivity contribute to the overall
@@
 referents. Such effect was demonstrated by cross-situational learning
-experiments (Smith \& Yu, 2008). In the phonological case, connectivity
-is inherently correlated with phonotactic probability (Vitevitch, Luce,
-Pisoni, \& Auer, 1999). That is, highly connected words tend to be made
-of frequent sound sequences. We know even infant (whose vocabulary is
-still very rudimentary) develop a sensitivity for high frequency sound
-sequences in the ambient language (Jusczyk, Luce, \& Charles-Luce,
-1994). Interestingly, it was shown that phonotactic probability
-facilitates learning and recognition of novel words in toddlers and
-preschoolers (MacRoy-Higgins, Shafer, Schwartz, \& Marton, 2014;
-Storkel, 2001). Thus, children's ability to keep track of co-occurrence
-statistics (both at the semantic and phonological level) might explain
-their sensitivity and preference for highly connected words in the
-learning envirnoment.
+experiments (Smith \& Yu, 2008).
+
+In the phonological case, connectivity is inherently correlated with
+phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
+is, highly connected words tend to be made of frequent sound sequences.
+We know even infant (whose vocabulary is still very rudimentary) develop
+a sensitivity for high frequency sound sequences in the ambient language
+(Jusczyk, Luce, \& Charles-Luce, 1994). Interestingly, it was shown that
+phonotactic probability facilitates learning and recognition of novel
+words in toddlers and preschoolers (MacRoy-Higgins, Shafer, Schwartz, \&
+Marton, 2014; Storkel, 2001). Thus, children's ability to keep track of
+co-occurrence statistics (both at the semantic and phonological level)
+might explain their sensitivity and preference for highly connected
+words in the learning environment.
 
 Finally, this study shares a number of limitations with previous studies
-using similar datasets. For instance, we used normative age of
-acquisition. However, individual children may follow different learning
-trajectories. The use of longitudinal data would allow us to assess how
-the aggregate behavior relates to these individual trajectories (e.g.,
-typical vs.~late talkers, Beckage et al., 2011). Moreover, the results
-obtained in this study provide correlational but not causal evidence.
-Thus, conclusions drawn from our network analysis would require parallel
-evidence, especially from controlled behavioral experiments.
+using similar datasets. In particular, the results provide correlational
+but not causal evidence. Thus, the conclusions of this study require
+parallel evidence, especially from controlled behavioral experiments.
 
@@
 
-\hypertarget{ref-pisoni1985}{}
-Pisoni, D. B., Nusbaum, H. C., Luce, P. A., \& Slowiaczek, L. M. (1985).
-Speech perception, word recognition and the structure of the lexicon.
-\emph{Speech Communication}, \emph{4}(1), 75--95.
-
 \hypertarget{ref-smith2008}{}

### 2018-01-25 cogsci/cogsci.Rmd
modif in Cogci

@@
 
-A crucial question that naturally emerges from these analyses is how does network connectivity influence word learning?
+While most studies focued on the static properties of the lexical network, a few have proposed to account for the underlying developmental process.
 @steyvers2005 suggested that the effect of connectivity is the consequence of how the lexical network gets constructed in the child's mind.
@@
 In other words, what predicts word learning is *internal* connectivity in the child's early lexicon.
-In contrast, @hills2009 found that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment.
+In contrast, @hills2009 suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment.
 They called this alternative explanation Preferential Acquisition (PAC).
@@
 The novelty of the current study is that it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT.
-It also provides a systematic comparison of network growth scenarios in  the phonological and the semantic domains and assesses their relative contribution to the learning process.
+It also provides a systematic comparison of both network growth scenarios in the phonological and the semantic domains and assesses their relative contribution to the learning process.
 Moreover, it tests the generality of the findings across eight languages.
@@
 
-```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the end-state network as predicted by the degree in this network.
+```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
 Results are shown in each language for the phonological network (top) and the semantic network (bottom).
@@
   theme_bw()+
-  theme(aspect.ratio = 1)+
+  theme(aspect.ratio = 0.7)+
   xlab("degree") +ylab("probability")
@@
 PAT is known to generate networks with a power-law degree distribution [@barabasi99].
-Thus, if the networks display this property, it means that PAT cannot be ruled out *a priori* as a potential growth mechanism.
-In contrast, if there is strong evidence against a power law distribution, then PAT (but not PAC) can be ruled out.
-The distributions are shown in Figure \ref{fig:degree_distribution}.
-Overall, the results do not provide strong evidence against a power-law distribution.
-Moreover, the degree to which the distribution approximates a power law varies across dimension and languages.
-For a more conclusive test, we fit explicit growth models to the data (next section).
+If the networks display this property, this fact would strongly suggests a PAT-like generative process.
+<!--cannot be ruled out *a priori* as a potential growth mechanism.
+In contrast, if there is strong evidence against a power law distribution, then PAT (but not PAC) can be ruled out--> The results are shown in Figure \ref{fig:degree_distribution}.
+Overall, the extent to which the degree distribution approximates a power law varies across dimensions and languages.
+For a more direct test of the developmental process, we fit explicit growth models to the data (see next section).
 <!--
@@
 A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first.
-As explained in Figure \ref{fig:growth}, each candidate word $w_i$ is characterized with a growth values $d_i$ that depends on the growth scenario tested.
+As explained in Figure \ref{fig:growth}, each candidate word $w_i$ is characterized with a growth value $d_i$ that depends on the growth scenario tested.
 In PAT, the growth value of a given word is equal to the average degree of the existing nodes that it would attach to.
@@
 In term of growth scenarios, we found that PAC dominates the learning.
-In particular, though we found previously that phonological PAT predicted part of the learning in some languages when tested individually, here PAT appears to lose its predictive power when pitted against phonological PAC.
-In terms of domain, both phonological and semantic networks appear to contribute to learning, although the phonological network appears to be stronger and more reliable across languages.
+<!--In particular, though we found previously that phonological PAT predicted part of the learning in some languages when tested individually, here PAT appears to lose its predictive power when pitted against phonological PAC--> In terms of domain, both phonological and semantic networks appear to contribute to the lexical growth, but the phonological network appears to be stronger and more consistent across languages.
 In summary, the findings show that both semantic and phonological networks grow primarily by PAC, and that, generally speaking, semantic and phonological networks both contribute to the learning process.
@@
 Thus, we no longer needed to fit the growth model month-by-month as in the previous section.
-In fact, word utilities in the case of PAC are fixed, they do not depend on previously learned words.
+In fact, word utilities (i.e., growth values) in the case of PAC are fixed, they do not depend on previously learned words.
 A more direct way to assess and compare the contribution of PAC in relation to other factors is through conducting linear regressions, where connectivity in the learning environment (at both the phonological and semantic level), frequency and length predict the age of acquisition.
@@
 However, in this previous study, semantic connectivity was not tested in a model that included both frequency and length as covariates.
-Another important difference is the number of words tested.
-Our study uses a larger set of nouns.}.
+Another important difference is the number of words tested: our study uses a larger set of nouns.}.
 Despite this cross-linguistic variation, both phonological and semantic connectivity remain significant predictors in the global model.
@@
 
-Finally, this study shares a number of limitations with previous studies using similar datasets.
+Finally, this study shares a number of limitations with previous studies using similar research strategy and dataset.
 <!--For instance, we used normative age of acquisition.

### 2018-01-25 cogsci/cogsci.tex
modif in Cogci

@@
 
-A crucial question that naturally emerges from these analyses is how
-does network connectivity influence word learning? Steyvers \& Tenenbaum
-(2005) suggested that the effect of connectivity is the consequence of
-how the lexical network gets constructed in the child's mind. According
-to this explanation, known as Preferential Attachment (PAT), highly
-connected words in the child's lexicon tend to ``attract'' more words
-over time, in a rich-get-richer scenario (Barabasi \& Albert, 1999). In
-other words, what predicts word learning is \emph{internal} connectivity
-in the child's early lexicon. In contrast, Hills et al. (2009) found
-that what biases the learning is not the connectivity in the child's
-internal lexicon but, rather, \emph{external} connectivity in the
-learning environment. They called this alternative explanation
-Preferential Acquisition (PAC). Figure \ref{fig:growth} shows an
-illustration of both growth scenarios with the same simplified network.
+While most studies focued on the static properties of the lexical
+network, a few have proposed to account for the underlying developmental
+process. Steyvers \& Tenenbaum (2005) suggested that the effect of
+connectivity is the consequence of how the lexical network gets
+constructed in the child's mind. According to this explanation, known as
+Preferential Attachment (PAT), highly connected words in the child's
+lexicon tend to ``attract'' more words over time, in a rich-get-richer
+scenario (Barabasi \& Albert, 1999). In other words, what predicts word
+learning is \emph{internal} connectivity in the child's early lexicon.
+In contrast, Hills et al. (2009) suggested that what biases the learning
+is not the connectivity in the child's internal lexicon but, rather,
+\emph{external} connectivity in the learning environment. They called
+this alternative explanation Preferential Acquisition (PAC). Figure
+\ref{fig:growth} shows an illustration of both growth scenarios with the
+same simplified network.
 
@@
 by PAC, or if they rather grow by PAT. It also provides a systematic
-comparison of network growth scenarios in the phonological and the
+comparison of both network growth scenarios in the phonological and the
 semantic domains and assesses their relative contribution to the
@@
 
-\caption{\label{fig:data_all}Age of acquisition in the end-state network as predicted by the degree in this network.
+\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
 Results are shown in each language for the phonological network (top) and the semantic network (bottom).
@@
 generate networks with a power-law degree distribution (Barabasi \&
-Albert, 1999). Thus, if the networks display this property, it means
-that PAT cannot be ruled out \emph{a priori} as a potential growth
-mechanism. In contrast, if there is strong evidence against a power law
-distribution, then PAT (but not PAC) can be ruled out. The distributions
-are shown in Figure \ref{fig:degree_distribution}. Overall, the results
-do not provide strong evidence against a power-law distribution.
-Moreover, the degree to which the distribution approximates a power law
-varies across dimension and languages. For a more conclusive test, we
-fit explicit growth models to the data (next section).
+Albert, 1999). If the networks display this property, this fact would
+strongly suggests a PAT-like generative process. The results are shown
+in Figure \ref{fig:degree_distribution}. Overall, the extent to which
+the degree distribution approximates a power law varies across
+dimensions and languages. For a more direct test of the developmental
+process, we fit explicit growth models to the data (see next section).
 
@@
 acquired first. As explained in Figure \ref{fig:growth}, each candidate
-word \(w_i\) is characterized with a growth values \(d_i\) that depends
+word \(w_i\) is characterized with a growth value \(d_i\) that depends
 on the growth scenario tested. In PAT, the growth value of a given word
@@
 in Figure \ref{fig:pred_ind}. In term of growth scenarios, we found that
-PAC dominates the learning. In particular, though we found previously
-that phonological PAT predicted part of the learning in some languages
-when tested individually, here PAT appears to lose its predictive power
-when pitted against phonological PAC. In terms of domain, both
-phonological and semantic networks appear to contribute to learning,
-although the phonological network appears to be stronger and more
-reliable across languages. In summary, the findings show that both
-semantic and phonological networks grow primarily by PAC, and that,
-generally speaking, semantic and phonological networks both contribute
-to the learning process.
+PAC dominates the learning. In terms of domain, both phonological and
+semantic networks appear to contribute to the lexical growth, but the
+phonological network appears to be stronger and more consistent across
+languages. In summary, the findings show that both semantic and
+phonological networks grow primarily by PAC, and that, generally
+speaking, semantic and phonological networks both contribute to the
+learning process.
 
@@
 no longer needed to fit the growth model month-by-month as in the
-previous section. In fact, word utilities in the case of PAC are fixed,
-they do not depend on previously learned words. A more direct way to
-assess and compare the contribution of PAC in relation to other factors
-is through conducting linear regressions, where connectivity in the
-learning environment (at both the phonological and semantic level),
-frequency and length predict the age of acquisition.
+previous section. In fact, word utilities (i.e., growth values) in the
+case of PAC are fixed, they do not depend on previously learned words. A
+more direct way to assess and compare the contribution of PAC in
+relation to other factors is through conducting linear regressions,
+where connectivity in the learning environment (at both the phonological
+and semantic level), frequency and length predict the age of
+acquisition.
 
@@
 However, in this previous study, semantic connectivity was not tested in a model that included both frequency and length as covariates.
-Another important difference is the number of words tested.
-Our study uses a larger set of nouns.}.
+Another important difference is the number of words tested: our study uses a larger set of nouns.}.
 Despite this cross-linguistic variation, both phonological and semantic
@@
 Finally, this study shares a number of limitations with previous studies
-using similar datasets. In particular, the results provide correlational
-but not causal evidence. Thus, the conclusions of this study require
-parallel evidence, especially from controlled behavioral experiments.
+using similar research strategy and dataset. In particular, the results
+provide correlational but not causal evidence. Thus, the conclusions of
+this study require parallel evidence, especially from controlled
+behavioral experiments.
 

### 2018-01-30 cogsci/cogsci.Rmd
modif to cogsci draft

@@
 ---
-title: "Word Learning as Network Growth: a Cross-linguistic Analysis"
+title: "Word Learning as Network Growth: A Cross-linguistic Analysis"
 
@@
 document-params: "10pt, letterpaper"
+
+header-includes:
+   - \usepackage[subtle]{savetrees}
 
@@
 
-    "Children tend to produce first the words that are connected to a variety of other words along both the phonological and the semantic dimensions.
+    "Children tend to produce words earlier when they are connected to other words along both the phonological and semantic dimensions.
 Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.
 One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's ealy lexicon attract similar words.
-Another view suggests that learning is driven, not by highly connected words in the early internal lexicon, but by highly connected word in the external learning environment.
+Another view suggests that learning is driven, not by highly connected words in the early internal lexicon, but by words that are highly connected in the external learning environment.
 The present study tests both scenarios systematically in both the phonological and the semantic domains, and across 8 languages.
@@
 
-<!-- Children tend to learn some words typically at an earlier age than others.
-Researchers have documented many word properties that influence the order of acquisition of words.
-This paper investigates strcutural properties that characterize how words are related to each other in the lexicon.
--->
 ```{r global_options, include=FALSE}
@@
 library(ggplot2)
+library(ggthemes)
 library(xtable)
@@
 What factors shape vocabulary learning over the course of early childhood?
-To investigate this question, scientists have adopted multiple research strategies, from controlled laboratory experiments to corpus analysis.
+To investigate this question, scientists have adopted multiple research strategies, from conducting controlled laboratory experiments [e.g.
+@markman90] to analysing dense corpora capturing language learning in context [e.g., @roy2015].
 One strategy consists in documenting the timeline of words' acquisition, and studying the properties that make words easy or hard to learn.
 For example, within a lexical category, words that are more frequent in child-directed speech are acquired earlier [@goodman2008].
-Other factors include word length, the mean length of utterances in which the word occurs, and how concrete the word is [see @braginsky2016].
+Other factors include word length, the mean length of utterances in which the word occurs, and concreteness [see @braginsky2016].
 
-Besides these word-level properties, researchers found that the lexical structure (that is, how words relate to each other) also influences the age of acquisition of words.
+Besides these word-level properties, the lexical structure (that is, how words relate to each other) also influences the age of acquisition of words.
 The lexical structure is best characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words.
-Previous studies investigated early vocabulary networks based on different word relations such as shared semantic features, target-cue relationship in free association norms, co-occurrence in child directed speech, and phonological similarity.
-These studies found that children tend to produce earlier the words that have higher neighborhood density (i.g., high connectivity in the network) both at the phonological and the semantic level [@stokes2010; @storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017; @beckage2011].
+Previous studies investigated early vocabulary networks based on different word relations such as shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological similarity.
+These studies have found that children tend to produce earlier the words that have higher neighborhood density (i.e., high connectivity in the network) both at the phonological and the semantic level [@stokes2010; @storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017; @beckage2011].
 
-While most studies focued on the static properties of the lexical network, a few have proposed to account for the underlying developmental process.
+While most studies focused on the static properties of the lexical network, a few have investigated the underlying developmental process.
 @steyvers2005 suggested that the effect of connectivity is the consequence of how the lexical network gets constructed in the child's mind.
 According to this explanation, known as Preferential Attachment (PAT), highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99].
-In other words, what predicts word learning is *internal* connectivity in the child's early lexicon.
+In other words, what predicts word learning is the *internal* connectivity in the child's early lexicon.
 In contrast, @hills2009 suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment.
@@
 Figure \ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network.
+These two proposals represent two divergent ideas about the role of lexical networks in acquisition.
+On the PAT proposal, network structure is a causal factor in early word learning; in contrast, on the PAC approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguisitc input (see discussion).
 
-```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Illustration of the two growth models with the same network.
-Filled circles (I1-I4) represent known words (internal lexicon), and empty circles (E1 and E2) represent words that have not been learned yet (external lexicon).
+```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Filled circles (I1-I4) represent known words (internal lexicon), and empty circles (E1 and E2) represent words that have not been learned yet (external lexicon).
 Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
@@
 
-Studies that investigated lexical network growth focused on semantic networks using English data only [@steyvers2005; @hills2009; @hills2010].
+Studies that investigate lexical network growth have focused on semantic networks using English data [@steyvers2005; @hills2009; @hills2010].
 The novelty of the current study is that it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT.
@@
 
-The paper is organized as follows.
+<!--The paper is organized as follows.
 First, we describe the dataset we used, the procedure we followed to construct both semantic and phonological networks.
@@
 Then we test the overall contribution of the networks in the learning process relative to other known predictors of age of acquisition (frequency and length).
-Finally we discuss the major results in relation to known experimental facts in language development, and we speculate about the potential learning mechanism that might drive early vocabulary learning.
+Finally we discuss the major results in relation to known experimental facts in language development, and we speculate about the potential learning mechanism that might drive early vocabulary learning.-->
 
@@
   scale_colour_solarized(name = "") +
-  theme_bw()+
+  theme_few()+
   #theme_bw()+
@@
   scale_y_log10() + scale_x_log10() +
-  theme_bw()+
+  theme_few()+
   theme(aspect.ratio = 0.7)+
@@
 We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist.
+Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94].
 We used the *Words and Sentence* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months).
@@
 We used the subset of nouns that had entries in the Florida Association Norms (see below).
-Since these norms are available only in English, we used the translation of non-English words provided by @braginsky2016.
-This allowed us to use the English association norms across languages.
+Since these norms are available only in English, we used the hand-checked translation equivalents provided by Braginsky by @braginsky2016, allowing us to use the English association norms across languages.
 Table \ref{tab:stats} gives an overview of the data used.
-The translation of non-English words is still an ongoing process.
+Translation equivalents were originally constructed for a subset of words appearing on the toddler CDI form (the subset is labeled *Words and Gestures*), and so not all words are currently available.
 Note, however, that all languages have at least 60% of nouns translated.
@@
 tab <- xtable::xtable(statistics,
-                      caption = "\\label{tab:stats}Total number of productive nouns in the CDI (left).
-We used a subset of these nouns that had available English translations (middle).
+                      caption = "\\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left).
+We included in our study the subset of these nouns that had available English translations (middle).
 The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).")
@@
 
-We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998].
+@hills2009, we used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998].
 This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target).
@@
 To model growth from month to month, we constructed a different network at each month, made of words that have been learned at that month.
-Following @hills2009, we used as a proxy for the learning environment, the network constructed using the full set of nouns in the CDI data in each language (e.g., in English this corresponds to the network by 30 months).
 
@@
 
-We used as a measure of phonological relatedness between two nodes the Levenshtein (edit) distance between their phonological forms.
+We generated approximate International Phonetic Alphabet (IPA) transcriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein (edit) distance as a measure of phonological relatedness between two nodes.
 The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.
-We generated approximate International Phonetic Alphabet (IPA) transcriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).**
 
@@
 However, in these previous studies the network was built using an adult vocabulary.
-Here, similar to the approximation we made for the semantic network, we used the full set of nouns in the CDI data as a proxy for phonological connectivity in the learning environment.
-However, since the children's vocabulary contains very few word pairs with an edit distance of 1, the resulting network was too sparse and uninformative.
-Thus, we increased the threshold from 1 to 2, that is, two node were related if their edit distance was equal to 1 or 2.
+However, since the children's vocabulary contains very few word pairs with an edit distance of 1, the resulting networks were too sparse and uninformative.
+Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.
 Each node was characterized with its degree, i.e., the number of links it shares with other words.
-<!-- Moreover, and in order to model growth from month to month, we constructed a different network at each month, made of words that have been learned at that month.
--->
 
@@
 
-## Preliminary analysis
-We start by examining how connectivity in the global network influences the age of acquisition.
-Regardless of the growth mechanism that might have given rise to this network (i.e., PAC or PAT), we expect nodes with the higher degrees in this network to be learned earlier than nodes with the lower degrees.
-The global network was constructed using nouns at the oldest age for which we have CDI data.
-Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network).
+## Static properties of the global network
+
+We start by analysing word connectivity in the global (static) network.
+We constructed this network using nouns at the oldest age for which we have CDI data (e.g., in English this corresponds to the network by 30 months).
+This global netowrk is the end-state towards which both PAT and PAC should converge by the last month of learning.
+Morover, following @hills2009, we used this end-state netowrk as a proxy for the external connectivity in the learning environment.
+Below we analyse properties of this global networks that are relevant to PAT and/or PAC.
+
+###Connectivity predicts the age of acquisition
+
+Connectivity in the global network is directly related to PAC as it represents the explicit criterion PAC uses to determine what words should be learned first (Figure \ref{fig:growth}).
+Therefore, a direct consequence of a PAC-like growth scenario is a correlation betweeen connectivity in the global network and the age of acquisition.\footnote{Note that this correlation is also compatible with PAT, even if this growth scenario does not rely explicity on external connectivity.
+Indeed, from a PAT perspective, higher connectivity in the global network is caused by earlier learning, i.e., some words end up being highly connected in the global network precisely because they happen to be acquired earlier (and therefore have a higher chance of forming more links over time).} Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its connectivity/degree (or indegree for the semantic network).
 For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages.
@@
 
-We also analysed the global network degree distribution.
-PAT is known to generate networks with a power-law degree distribution [@barabasi99].
-If the networks display this property, this fact would strongly suggests a PAT-like generative process.
-<!--cannot be ruled out *a priori* as a potential growth mechanism.
-In contrast, if there is strong evidence against a power law distribution, then PAT (but not PAC) can be ruled out--> The results are shown in Figure \ref{fig:degree_distribution}.
-Overall, the extent to which the degree distribution approximates a power law varies across dimensions and languages.
-For a more direct test of the developmental process, we fit explicit growth models to the data (see next section).
+###Power law degree distribution?
+We also analysed the global network's degree distribution.
+This property is particularly relevant to PAT as this growth scenario is known to generate networks with a power-law degree distribution [@barabasi99].
+If the network displays this property, this fact would strongly suggests a PAT-like generative process.
+Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for PAT.
+The results are shown in Figure \ref{fig:degree_distribution}.
+Overall, we did not find consistent evidence for a power law distribution: the extent to which the degree distribution approximates a power law varies across dimensions and languages.
+
+For a more direct test of the developmental process, we fit explicit growth models to the data (next section).
 <!--
@@
 \end{equation}
-Where $\beta$ is the fitting parameter.
-A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first.
-As explained in Figure \ref{fig:growth}, each candidate word $w_i$ is characterized with a growth value $d_i$ that depends on the growth scenario tested.
-In PAT, the growth value of a given word is equal to the average degree of the existing nodes that it would attach to.
-In PAC, the growth value of a word is equal to its degree in the entire network.
+
+\noindent where $\beta$ is a fitted parameter that captures the magnitude of the relationship between network parameters and growth (analogous to a regression coefficient).
+A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first (see Figure \ref{fig:growth} for illustrations of growth scenarios, and how a word's growth value $d_i$ is defined in each of these scenarios).
 The normalization includes all words that could be learned at that month.
@@
 The inference was performed using the probabilistic programming language  WebPPL [@dippl].
-We started with a uniform distribution, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been actually learned at that month (using formula 1).
-We ended up with a posterior distribution of $\beta$, which we summarized in Figure \ref{fig:pred_ind}.
+We defined a uniform prior over $\beta$, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been actually learned at that month (using formula 1).
+Markov chain monte carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \ref{fig:pred_ind}.
 
 Besides fitting a growth model to the data, we conducted another evaluation.
-This second evaluation consists in determining, in each month, the model-dependent growth value distribution of all words that could possibly be learned at this month, and then computing the z-score of each learned word with respect to this distribution.
-For each model, we tested if the distribution constituted by the z-scores of all learned words was different from zero, using a one-sample t-test.
+This second evaluation consists in determining, in each month, the growth value distribution of all words that could possibly be learned at this month, and then computing the z-score of each learned word with respect to this distribution.
+For each growth scenario, we tested if the distribution constituted by the z-scores of all learned words was different from zero, using a one-sample t-test.
 
-The results from both evaluations were very similar and lead essentially to the same conclusions\footnote{we do not show here the results of the second evaluation because they were redundant with the results of the first evaluation}.
-For the semantic network, the results replicate Hills et al.'s finding in English, which was that the semantic network grows by PAC, not by PAT.
-Moreover, it generalizes this finding to all other languages (with the exception of Russian).
-For the phonological network, the results show that, generally speaking, PAC again fits the developmental trajectory better than PAT.
+The results from both evaluations were very similar and lead essentially to the same conclusions.\footnote{we do not show here the results of the second evaluation because they were redundant with the results of the first evaluation} For the semantic networks, the results replicate Hills et al.'s finding in English, which was that the semantic network grows by PAC, not by PAT.
+Moreover, this finding held in seven of the eight languages we examined.
+The PAC model also fit better than PAT for phonological networks.
 We note however that PAT, though weaker, fares  better for the phonological networks (where it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian) than it does for the semantic networks (where it is rather universally unpredictive).
@@
 Using the same fitting technique, we obtained the values shown in Figure \ref{fig:pred_ind}.
-In term of growth scenarios, we found that PAC dominates the learning.
-<!--In particular, though we found previously that phonological PAT predicted part of the learning in some languages when tested individually, here PAT appears to lose its predictive power when pitted against phonological PAC--> In terms of domain, both phonological and semantic networks appear to contribute to the lexical growth, but the phonological network appears to be stronger and more consistent across languages.
-In summary, the findings show that both semantic and phonological networks grow primarily by PAC, and that, generally speaking, semantic and phonological networks both contribute to the learning process.
+PAC dominates the learning.
+Both phonological and semantic networks contribute to lexical growth, but the phonological network appears to be stronger and more consistent across languages.
+In summary, the findings show that both semantic and phonological networks contribute to the learning process, and that they both grow primarily by PAC, relying on the external connectivity in the learning environment, rather than the internal connectivity in the acquired lexicon.
 
@@
 However, we know that other factors influence learning as well [e.g., @braginsky2016].
-In what follows, we will investigate how semantic and phonological connectivity interact with two other factors.
+Next we investigated how semantic and phonological connectivity interact with two other factors.
 The first one is word frequency, a well studied factor shown to predict the age of acquisition in a reliable fashion [e.g.
@@
 In fact, word utilities (i.e., growth values) in the case of PAC are fixed, they do not depend on previously learned words.
-A more direct way to assess and compare the contribution of PAC in relation to other factors is through conducting linear regressions, where connectivity in the learning environment (at both the phonological and semantic level), frequency and length predict the age of acquisition.
+A more direct way to assess and compare the contribution of PAC in relation to other word-level factors is through conducting linear regressions, where connectivity in the learning environment (at both the phonological and semantic level), frequency and length predict the age of acquisition.
 
-We used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language.
+We used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language (note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children).
 For each word, counts included words that shared the same stem  (e.g., cats counts as cat), or words that were synonymous (e.g.
@@
 We fit a linear regression for each language, and we fit a linear mixed-effect to all the data pooled across languages, with language as a random effect.
-Figure \ref{fig:regressions_img} shows the coefficient estimate for each predictor in each language, and figure \ref{fig:regressions_all_img} shows the coefficient estimates for all languages combined (all predictors were centered and scaled).
+Figure \ref{fig:regressions_img} shows the coefficient estimate for each predictor in each language, and Figure \ref{fig:regressions_all_img} shows the coefficient estimates for all languages combined (all predictors were centered and scaled).
 The findings were as follows.
-Overall, frequency is the largest and most consistent predictor of age of acquisition.
+Overall, frequency is the largest and most consistent predictor of age of acquisition, replicating results for nouns across a variety of analyses [@goodman2008; @braginsky2016; @roy2015].
 Word length predicts learning in some languages such as Croatian and Norwegian, but not in others (including English).
@@
 As for the factors of interest, i.e., semantic and phonological connectivity, we also found cross-linguistic differences.
-The phonological connectivity contributes to learning in languages such as Croatian, English and Russian, whereas semantic connectivity contributes to learning in Turkish, Spanish and to some extent in Croatian, but interestingly not in English\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
+The phonological connectivity contributes to learning in languages such as Croatian, English and Russian, whereas semantic connectivity contributes to learning in Turkish, Spanish and to some extent in Croatian, but interestingly not in English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
 This contrasts with the original finding in Hills et al.
 2009.
-However, in this previous study, semantic connectivity was not tested in a model that included both frequency and length as covariates.
-Another important difference is the number of words tested: our study uses a larger set of nouns.}.
-Despite this cross-linguistic variation, both phonological and semantic connectivity remain significant predictors in the global model.
+However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates.
+Another important difference is the number of words tested: our study uses a larger set of nouns.} Despite this cross-linguistic variation, both phonological and semantic connectivity remain significant predictors in the global model.
 
@@
 The present study provided a comprehensive analysis of how lexical connectivity influences the age of acquisition of nouns in toddlers.
-We compared two network growth scenarios and assessed the relative contribution of phonological and semantic information in 8 languages.
+We compared two network growth scenarios and assessed their relative contributions of phonological vs.
+semantic networks across eight languages.
+One scenario, PAT, described a "rich get richer" network growth model in which the structure of the learner's internal network determines future growth; the other, PAC, described a model in which the external, global environmental network structure determines learners' growth patterns.
 Part of the findings largely replicate the results obtained in @hills2009, i.e., semantic networks (based on free associations) grow by preferential acquisition, not by preferential attachment.
@@
 
-```{r regressions_all_img, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, fig.cap = "\\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined model pooling across languages .
+```{r regressions_all_img, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, fig.cap = "\\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect.
 Ranges indicate 95\\% confidence intervals.
-Fade color indicates estimates of PAC predictors in a model that does not include frequency and length as covariates."}
+Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates."}
 
@@
 
-A major results of the study is that children start by learning words that have high phonological and semantic similarity with a variety of other words in the learning environment, not in the child's available lexicon.
+One important result of the study is that children start by learning words that have high phonological and semantic similarity with a variety of other words in the learning environment, not in the child's available lexicon.
 This suggests that children are sensitive to connectivity even without having first acquired the connected words.
 How can children indirectly detect highly connected words, and why would such words be more readily learned?
+
 In the semantic case, free association can be predicted through the patterns of word co-occurrence [@griffiths07], meaning that highly connected words tend to be the words that co-occur with many other words in various contexts.
-One possibility, suggested by @hills2010, is that the referents of such words are more easily disambiguated from other potential referents.
-Such effect was demonstrated by cross-situational learning experiments [@smith2008].
+One possibility, suggested by @hills2010, is that the referents of such words are more easily disambiguated from other potential referents (because their presence in mulitiple contexts provides more diambiguating statisitcs about their true referents).
+[@smith2008] showed that children can disambiguate the words' referents based on such cross-situational statisitics [@smith2008].
 
@@
 That is, highly connected words tend to be made of frequent sound sequences.
-We know even infant (whose vocabulary is still very rudimentary) develop a sensitivity for high frequency sound sequences in the ambient language [@jusczyk1994].
-Interestingly, it was shown that phonotactic probability facilitates learning and recognition of novel words in toddlers and preschoolers [@storkel2001;  @higgins2014].
-Thus, children's ability to keep track of co-occurrence statistics (both at the semantic and phonological level) might explain their sensitivity and preference for highly connected words in the learning environment.
+Even infants (whose vocabulary is still very rudimentary) show a sensitivity for high frequency sound sequences in the ambient language [@jusczyk1994].
+Moreover, it was shown that phonotactic probability facilitates learning and recognition of novel words in toddlers and preschoolers [@storkel2001;  @higgins2014].
+In other words, children's sensitivity to local phonotactic regularities might lead them to learn higher-probability words more easily.
+This learning effect in turn would lead to an observed pattern of growth that would appear to follow the PAC growth model even though learners themselves would only be tracking local statistics.
 
-Finally, this study shares a number of limitations with previous studies using similar research strategy and dataset.
-<!--For instance, we used normative age of acquisition.
+Finally, while validating previous results using network growth models, our study suggests that these correlational patterns may emerge from the operation of simpler mechanisms.
+One question for future experimental work is whether such patterns of growth can be produced in controlled behavioral experiments.
+<!--Finally, this study shares a number of limitations with previous studies using similar research strategy and dataset.For instance, we used normative age of acquisition.
 However, individual children may follow different learning trajectories.
@@
 late talkers, @beckage2011].
-Moreover,--> In particular, the results provide correlational but not causal evidence.
+Moreover,In particular, the results provide correlational but not causal evidence.
 Thus, the conclusions of this study  require parallel evidence, especially from controlled behavioral experiments.
+-->
 

### 2018-01-30 cogsci/cogsci.tex
modif to cogsci draft

@@
 
-\title{Word Learning as Network Growth: a Cross-linguistic Analysis}
+\title{Word Learning as Network Growth: A Cross-linguistic Analysis}
+
+\usepackage[subtle]{savetrees}
 
@@
 \begin{abstract}
-Children tend to produce first the words that are connected to a variety
-of other words along both the phonological and the semantic dimensions.
-Though this connectivity effect has been extensively documented, little
-is known about the underlying developmental mechanism. One view suggests
-that learning is primarily driven by a network growth model where highly
+Children tend to produce words earlier when they are connected to other
+words along both the phonological and semantic dimensions. Though this
+connectivity effect has been extensively documented, little is known
+about the underlying developmental mechanism. One view suggests that
+learning is primarily driven by a network growth model where highly
 connected words in the child's ealy lexicon attract similar words.
 Another view suggests that learning is driven, not by highly connected
-words in the early internal lexicon, but by highly connected word in the
-external learning environment. The present study tests both scenarios
-systematically in both the phonological and the semantic domains, and
-across 8 languages. We show that external connectivity in the learning
-environment drives growth in both the semantic and the phonological
-networks, and that this pattern is consistent cross-linguistically. The
-findings suggest a word learning mechanism where children harness their
-statistical learning abilities to (indirectly) detect and learn highly
-connected words in the learning environment.
+words in the early internal lexicon, but by words that are highly
+connected in the external learning environment. The present study tests
+both scenarios systematically in both the phonological and the semantic
+domains, and across 8 languages. We show that external connectivity in
+the learning environment drives growth in both the semantic and the
+phonological networks, and that this pattern is consistent
+cross-linguistically. The findings suggest a word learning mechanism
+where children harness their statistical learning abilities to
+(indirectly) detect and learn highly connected words in the learning
+environment.
 
@@
 childhood? To investigate this question, scientists have adopted
-multiple research strategies, from controlled laboratory experiments to
-corpus analysis. One strategy consists in documenting the timeline of
-words' acquisition, and studying the properties that make words easy or
-hard to learn. For example, within a lexical category, words that are
-more frequent in child-directed speech are acquired earlier (J. C.
-Goodman, Dale, \& Li, 2008). Other factors include word length, the mean
-length of utterances in which the word occurs, and how concrete the word
-is (see Braginsky, Yurovsky, Marchman, \& Frank, 2016).
+multiple research strategies, from conducting controlled laboratory
+experiments (e.g. Markman, 1990) to analysing dense corpora capturing
+language learning in context (e.g., B. C. Roy, Frank, DeCamp, Miller, \&
+Roy, 2015). One strategy consists in documenting the timeline of words'
+acquisition, and studying the properties that make words easy or hard to
+learn. For example, within a lexical category, words that are more
+frequent in child-directed speech are acquired earlier (J. C. Goodman,
+Dale, \& Li, 2008). Other factors include word length, the mean length
+of utterances in which the word occurs, and concreteness (see Braginsky,
+Yurovsky, Marchman, \& Frank, 2016).
 
-Besides these word-level properties, researchers found that the lexical
-structure (that is, how words relate to each other) also influences the
-age of acquisition of words. The lexical structure is best characterized
-in terms of a network where each node represents a word in the
-vocabulary, and each link between two nodes represents a relationship
-between the corresponding pair of words. Previous studies investigated
-early vocabulary networks based on different word relations such as
-shared semantic features, target-cue relationship in free association
-norms, co-occurrence in child directed speech, and phonological
-similarity. These studies found that children tend to produce earlier
-the words that have higher neighborhood density (i.g., high connectivity
-in the network) both at the phonological and the semantic level
-(Beckage, Smith, \& Hills, 2011; Engelthaler \& Hills, 2017; Hills,
-Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya, \&
-Smith, 2009; Stella, Beckage, \& Brede, 2017; Stokes, 2010; Storkel,
-2009).
+Besides these word-level properties, the lexical structure (that is, how
+words relate to each other) also influences the age of acquisition of
+words. The lexical structure is best characterized in terms of a network
+where each node represents a word in the vocabulary, and each link
+between two nodes represents a relationship between the corresponding
+pair of words. Previous studies investigated early vocabulary networks
+based on different word relations such as shared semantic features,
+target-cue relationships in free association norms, co-occurrence in
+child directed speech, and phonological similarity. These studies have
+found that children tend to produce earlier the words that have higher
+neighborhood density (i.e., high connectivity in the network) both at
+the phonological and the semantic level (Beckage, Smith, \& Hills, 2011;
+Engelthaler \& Hills, 2017; Hills, Maouene, Riordan, \& Smith, 2010;
+Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Stella, Beckage, \&
+Brede, 2017; Stokes, 2010; Storkel, 2009).
 
-While most studies focued on the static properties of the lexical
-network, a few have proposed to account for the underlying developmental
-process. Steyvers \& Tenenbaum (2005) suggested that the effect of
-connectivity is the consequence of how the lexical network gets
-constructed in the child's mind. According to this explanation, known as
-Preferential Attachment (PAT), highly connected words in the child's
-lexicon tend to ``attract'' more words over time, in a rich-get-richer
-scenario (Barabasi \& Albert, 1999). In other words, what predicts word
-learning is \emph{internal} connectivity in the child's early lexicon.
-In contrast, Hills et al. (2009) suggested that what biases the learning
-is not the connectivity in the child's internal lexicon but, rather,
+While most studies focused on the static properties of the lexical
+network, a few have investigated the underlying developmental process.
+Steyvers \& Tenenbaum (2005) suggested that the effect of connectivity
+is the consequence of how the lexical network gets constructed in the
+child's mind. According to this explanation, known as Preferential
+Attachment (PAT), highly connected words in the child's lexicon tend to
+``attract'' more words over time, in a rich-get-richer scenario
+(Barabasi \& Albert, 1999). In other words, what predicts word learning
+is the \emph{internal} connectivity in the child's early lexicon. In
+contrast, Hills et al. (2009) suggested that what biases the learning is
+not the connectivity in the child's internal lexicon but, rather,
 \emph{external} connectivity in the learning environment. They called
@@
 \ref{fig:growth} shows an illustration of both growth scenarios with the
-same simplified network.
+same simplified network. These two proposals represent two divergent
+ideas about the role of lexical networks in acquisition. On the PAT
+proposal, network structure is a causal factor in early word learning;
+in contrast, on the PAC approach, network structure is not internally
+represented and, therefore, might be an epiphenomenon of the statistics
+of the linguisitc input (see discussion).
 
@@
 
-\caption{\label{fig:growth}Illustration of the two growth models with the same network.
-Filled circles (I1-I4) represent known words (internal lexicon), and empty circles (E1 and E2) represent words that have not been learned yet (external lexicon).
+\caption{\label{fig:growth}Filled circles (I1-I4) represent known words (internal lexicon), and empty circles (E1 and E2) represent words that have not been learned yet (external lexicon).
 Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
@@
 
-Studies that investigated lexical network growth focused on semantic
-networks using English data only (Hills et al., 2010, 2009; Steyvers \&
+Studies that investigate lexical network growth have focused on semantic
+networks using English data (Hills et al., 2010, 2009; Steyvers \&
 Tenenbaum, 2005). The novelty of the current study is that it
@@
 across eight languages.
-
-The paper is organized as follows. First, we describe the dataset we
-used, the procedure we followed to construct both semantic and
-phonological networks. Next, we show the results of the various analyses
-we conducted comparing network growth scenarios across languages. Then
-we test the overall contribution of the networks in the learning process
-relative to other known predictors of age of acquisition (frequency and
-length). Finally we discuss the major results in relation to known
-experimental facts in language development, and we speculate about the
-potential learning mechanism that might drive early vocabulary learning.
 
@@
 developmental data of the MacArthur-Bates Communicative Development
-Inventory (CDI), a parent report vocabulary checklist. We used the
+Inventory (CDI), a parent report vocabulary checklist. Parent report is
+a reliable and valid measure of children's vocabulary that allows for
+the cost-effective collection of datasets large enough to test
+network-based models of acquisition (Fenson et al., 1994). We used the
 \emph{Words and Sentence} version of the CDI which contains the
@@
 nouns that had entries in the Florida Association Norms (see below).
-Since these norms are available only in English, we used the translation
-of non-English words provided by Braginsky et al. (2016). This allowed
-us to use the English association norms across languages. Table
-\ref{tab:stats} gives an overview of the data used. The translation of
-non-English words is still an ongoing process. Note, however, that all
-languages have at least 60\% of nouns translated.
+Since these norms are available only in English, we used the
+hand-checked translation equivalents provided by Braginsky by Braginsky
+et al. (2016), allowing us to use the English association norms across
+languages. Table \ref{tab:stats} gives an overview of the data used.
+Translation equivalents were originally constructed for a subset of
+words appearing on the toddler CDI form (the subset is labeled
+\emph{Words and Gestures}), and so not all words are currently
+available. Note, however, that all languages have at least 60\% of nouns
+translated.
 
@@
 \end{tabular}
-\caption{\label{tab:stats}Total number of productive nouns in the CDI (left).
-We used a subset of these nouns that had available English translations (middle).
+\caption{\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left).
+We included in our study the subset of these nouns that had available English translations (middle).
 The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).}
@@
 
-We used as an index of semantic relatedness the Florida Free Association
-Norms (Nelson, McEvoy, \& Schreiber, 1998). This dataset was collected
-by giving adult participants a word (the cue), and asking them to write
-the first word that comes to mind (the target). For example, when given
-the word ``ball'', they might answer with the word ``game''. A pair of
-nodes were connected by a directed link from the cue to the target if
-there was a cue-target relationship between these nodes in the
-association norms. Each node was characterized by its ``indegree'',
-which represents the number of links for which the word was the target.
-To model growth from month to month, we constructed a different network
-at each month, made of words that have been learned at that month.
-Following Hills et al. (2009), we used as a proxy for the learning
-environment, the network constructed using the full set of nouns in the
-CDI data in each language (e.g., in English this corresponds to the
-network by 30 months).
+Hills et al. (2009), we used as an index of semantic relatedness the
+Florida Free Association Norms (Nelson, McEvoy, \& Schreiber, 1998).
+This dataset was collected by giving adult participants a word (the
+cue), and asking them to write the first word that comes to mind (the
+target). For example, when given the word ``ball'', they might answer
+with the word ``game''. A pair of nodes were connected by a directed
+link from the cue to the target if there was a cue-target relationship
+between these nodes in the association norms. Each node was
+characterized by its ``indegree'', which represents the number of links
+for which the word was the target. To model growth from month to month,
+we constructed a different network at each month, made of words that
+have been learned at that month.
 
@@
 
-We used as a measure of phonological relatedness between two nodes the
-Levenshtein (edit) distance between their phonological forms. The
-measure counts the minimum number of operations (insertions, deletions,
-substitutions) required to change one string into another. We generated
-approximate International Phonetic Alphabet (IPA) transcriptions from
-the orthographic transcription, across languages, using the open source
-text-to-speech software
-\textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.}
+We generated approximate International Phonetic Alphabet (IPA)
+transcriptions from the orthographic transcription, across languages,
+using the open source text-to-speech software
+\textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.} We used
+the Levenshtein (edit) distance as a measure of phonological relatedness
+between two nodes. The measure counts the minimum number of operations
+(insertions, deletions, substitutions) required to change one string
+into another.
 
@@
 of 1 (Stokes, 2010; Storkel, 2009). However, in these previous studies
-the network was built using an adult vocabulary. Here, similar to the
-approximation we made for the semantic network, we used the full set of
-nouns in the CDI data as a proxy for phonological connectivity in the
-learning environment. However, since the children's vocabulary contains
-very few word pairs with an edit distance of 1, the resulting network
-was too sparse and uninformative. Thus, we increased the threshold from
-1 to 2, that is, two node were related if their edit distance was equal
-to 1 or 2. Each node was characterized with its degree, i.e., the number
-of links it shares with other words.
+the network was built using an adult vocabulary. However, since the
+children's vocabulary contains very few word pairs with an edit distance
+of 1, the resulting networks were too sparse and uninformative. Thus, we
+increased the threshold from 1 to 2, that is, two nodes were related if
+their edit distance was equal to 1 or 2. Each node was characterized
+with its degree, i.e., the number of links it shares with other words.
 
@@
 
-\subsection{Preliminary analysis}\label{preliminary-analysis}
+\subsection{Static properties of the global
+network}\label{static-properties-of-the-global-network}
 
-We start by examining how connectivity in the global network influences
-the age of acquisition. Regardless of the growth mechanism that might
-have given rise to this network (i.e., PAC or PAT), we expect nodes with
-the higher degrees in this network to be learned earlier than nodes with
-the lower degrees. The global network was constructed using nouns at the
-oldest age for which we have CDI data. Figure \ref{fig:data_all} shows
-how the age of acquisition for each word varies as a function of its
-degree (or indegree for the semantic network). For ease of visual
-comparison, the predictor (i.e., the degree) was centered and scaled
-across languages. The plots show, overall, a negative correlation
-between the month of acquisition and the degree, indicating that nouns
-with higher degrees are generally learned earlier.
+We start by analysing word connectivity in the global (static) network.
+We constructed this network using nouns at the oldest age for which we
+have CDI data (e.g., in English this corresponds to the network by 30
+months). This global netowrk is the end-state towards which both PAT and
+PAC should converge by the last month of learning. Morover, following
+Hills et al. (2009), we used this end-state netowrk as a proxy for the
+external connectivity in the learning environment. Below we analyse
+properties of this global networks that are relevant to PAT and/or PAC.
 
-We also analysed the global network degree distribution. PAT is known to
+\subsubsection{Connectivity predicts the age of
+acquisition}\label{connectivity-predicts-the-age-of-acquisition}
+
+Connectivity in the global network is directly related to PAC as it
+represents the explicit criterion PAC uses to determine what words
+should be learned first (Figure \ref{fig:growth}). Therefore, a direct
+consequence of a PAC-like growth scenario is a correlation betweeen
+connectivity in the global network and the age of
+acquisition.\footnote{Note that this correlation is also compatible with PAT, even if this growth scenario does not rely explicity on external connectivity.
+Indeed, from a PAT perspective, higher connectivity in the global network is caused by earlier learning, i.e., some words end up being highly connected in the global network precisely because they happen to be acquired earlier (and therefore have a higher chance of forming more links over time).}
+Figure \ref{fig:data_all} shows how the age of acquisition for each word
+varies as a function of its connectivity/degree (or indegree for the
+semantic network). For ease of visual comparison, the predictor (i.e.,
+the degree) was centered and scaled across languages. The plots show,
+overall, a negative correlation between the month of acquisition and the
+degree, indicating that nouns with higher degrees are generally learned
+earlier.
+
+\subsubsection{Power law degree
+distribution?}\label{power-law-degree-distribution}
+
+We also analysed the global network's degree distribution. This property
+is particularly relevant to PAT as this growth scenario is known to
 generate networks with a power-law degree distribution (Barabasi \&
-Albert, 1999). If the networks display this property, this fact would
-strongly suggests a PAT-like generative process. The results are shown
-in Figure \ref{fig:degree_distribution}. Overall, the extent to which
-the degree distribution approximates a power law varies across
-dimensions and languages. For a more direct test of the developmental
-process, we fit explicit growth models to the data (see next section).
+Albert, 1999). If the network displays this property, this fact would
+strongly suggests a PAT-like generative process. Conversely, if the
+degree distribution does not follow a power law, this fact would weaken
+the case for PAT. The results are shown in Figure
+\ref{fig:degree_distribution}. Overall, we did not find consistent
+evidence for a power law distribution: the extent to which the degree
+distribution approximates a power law varies across dimensions and
+languages.
+
+For a more direct test of the developmental process, we fit explicit
+growth models to the data (next section).
 
@@
 
-Where \(\beta\) is the fitting parameter. A positive value of \(\beta\)
+\noindent where \(\beta\) is a fitted parameter that captures the
+magnitude of the relationship between network parameters and growth
+(analogous to a regression coefficient). A positive value of \(\beta\)
 means that words with higher growth values \(d_i\) are acquired first,
 and a negative value means that words with lower growth values are
-acquired first. As explained in Figure \ref{fig:growth}, each candidate
-word \(w_i\) is characterized with a growth value \(d_i\) that depends
-on the growth scenario tested. In PAT, the growth value of a given word
-is equal to the average degree of the existing nodes that it would
-attach to. In PAC, the growth value of a word is equal to its degree in
-the entire network. The normalization includes all words that could be
+acquired first (see Figure \ref{fig:growth} for illustrations of growth
+scenarios, and how a word's growth value \(d_i\) is defined in each of
+these scenarios). The normalization includes all words that could be
 learned at that month.
@@
 inference was performed using the probabilistic programming language
-WebPPL (N. Goodman \& Stuhlmüller, 2014). We started with a uniform
-distribution, and at each month, we computed the likelihood function
+WebPPL (N. Goodman \& Stuhlmüller, 2014). We defined a uniform prior
+over \(\beta\), and at each month, we computed the likelihood function
 over words that could possibly enter the lexicon at that month, fit to
 the words that have been actually learned at that month (using formula
-1). We ended up with a posterior distribution of \(\beta\), which we
-summarized in Figure \ref{fig:pred_ind}.
+1). Markov chain monte carlo sampling resulted in a posterior
+distribution over \(\beta\), which we summarized in Figure
+\ref{fig:pred_ind}.
 
@@
 evaluation. This second evaluation consists in determining, in each
-month, the model-dependent growth value distribution of all words that
-could possibly be learned at this month, and then computing the z-score
-of each learned word with respect to this distribution. For each model,
-we tested if the distribution constituted by the z-scores of all learned
+month, the growth value distribution of all words that could possibly be
+learned at this month, and then computing the z-score of each learned
+word with respect to this distribution. For each growth scenario, we
+tested if the distribution constituted by the z-scores of all learned
 words was different from zero, using a one-sample t-test.
@@
 to the same
-conclusions\footnote{we do not show here the results of the second evaluation because they were redundant with the results of the first evaluation}.
-For the semantic network, the results replicate Hills et al.'s finding
+conclusions.\footnote{we do not show here the results of the second evaluation because they were redundant with the results of the first evaluation}
+For the semantic networks, the results replicate Hills et al.'s finding
 in English, which was that the semantic network grows by PAC, not by
-PAT. Moreover, it generalizes this finding to all other languages (with
-the exception of Russian). For the phonological network, the results
-show that, generally speaking, PAC again fits the developmental
-trajectory better than PAT. We note however that PAT, though weaker,
-fares better for the phonological networks (where it predicts part of
-the growth process in some languages such as Croatian, English,
-Norwegian and Russian) than it does for the semantic networks (where it
-is rather universally unpredictive).
+PAT. Moreover, this finding held in seven of the eight languages we
+examined. The PAC model also fit better than PAT for phonological
+networks. We note however that PAT, though weaker, fares better for the
+phonological networks (where it predicts part of the growth process in
+some languages such as Croatian, English, Norwegian and Russian) than it
+does for the semantic networks (where it is rather universally
+unpredictive).
 
@@
 PhonoPAC. Using the same fitting technique, we obtained the values shown
-in Figure \ref{fig:pred_ind}. In term of growth scenarios, we found that
-PAC dominates the learning. In terms of domain, both phonological and
-semantic networks appear to contribute to the lexical growth, but the
+in Figure \ref{fig:pred_ind}. PAC dominates the learning. Both
+phonological and semantic networks contribute to lexical growth, but the
 phonological network appears to be stronger and more consistent across
 languages. In summary, the findings show that both semantic and
-phonological networks grow primarily by PAC, and that, generally
-speaking, semantic and phonological networks both contribute to the
-learning process.
+phonological networks contribute to the learning process, and that they
+both grow primarily by PAC, relying on the external connectivity in the
+learning environment, rather than the internal connectivity in the
+acquired lexicon.
 
@@
 across languages. However, we know that other factors influence learning
-as well (e.g., Braginsky et al., 2016). In what follows, we will
-investigate how semantic and phonological connectivity interact with two
-other factors. The first one is word frequency, a well studied factor
-shown to predict the age of acquisition in a reliable fashion (e.g. J.
-C. Goodman et al., 2008). The second factor is word length, which
-correlates with phonological connectivity.
+as well (e.g., Braginsky et al., 2016). Next we investigated how
+semantic and phonological connectivity interact with two other factors.
+The first one is word frequency, a well studied factor shown to predict
+the age of acquisition in a reliable fashion (e.g. J. C. Goodman et al.,
+2008). The second factor is word length, which correlates with
+phonological connectivity.
 
@@
 more direct way to assess and compare the contribution of PAC in
-relation to other factors is through conducting linear regressions,
-where connectivity in the learning environment (at both the phonological
-and semantic level), frequency and length predict the age of
-acquisition.
+relation to other word-level factors is through conducting linear
+regressions, where connectivity in the learning environment (at both the
+phonological and semantic level), frequency and length predict the age
+of acquisition.
 
 We used the frequency estimates from Braginsky et al. (2016) where
-unigram counts were derived based on CHILDES corpora in each language.
-For each word, counts included words that shared the same stem (e.g.,
-cats counts as cat), or words that were synonymous (e.g.~father counts
-as daddy). For word length, we used our generated IPA transcription.
+unigram counts were derived based on CHILDES corpora in each language
+(note that these frequency counts are based on transcripts from
+independent sets of children and represent a general estimate of
+environmental frequency across children). For each word, counts included
+words that shared the same stem (e.g., cats counts as cat), or words
+that were synonymous (e.g.~father counts as daddy). For word length, we
+used our generated IPA transcription.
 
@@
 \ref{fig:regressions_img} shows the coefficient estimate for each
-predictor in each language, and figure \ref{fig:regressions_all_img}
+predictor in each language, and Figure \ref{fig:regressions_all_img}
 shows the coefficient estimates for all languages combined (all
@@
 Overall, frequency is the largest and most consistent predictor of age
-of acquisition. Word length predicts learning in some languages such as
+of acquisition, replicating results for nouns across a variety of
+analyses (Braginsky et al., 2016; J. C. Goodman et al., 2008; B. C. Roy
+et al., 2015). Word length predicts learning in some languages such as
 Croatian and Norwegian, but not in others (including English). It
@@
 interestingly not in
-English\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
+English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
 This contrasts with the original finding in Hills et al.
 2009.
-However, in this previous study, semantic connectivity was not tested in a model that included both frequency and length as covariates.
-Another important difference is the number of words tested: our study uses a larger set of nouns.}.
+However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates.
+Another important difference is the number of words tested: our study uses a larger set of nouns.}
 Despite this cross-linguistic variation, both phonological and semantic
@@
 connectivity influences the age of acquisition of nouns in toddlers. We
-compared two network growth scenarios and assessed the relative
-contribution of phonological and semantic information in 8 languages.
+compared two network growth scenarios and assessed their relative
+contributions and the relative contributions of phonological
+vs.~semantic networks across eight languages. One scenario, PAT,
+described a ``rich get richer'' network growth model in which the
+structure of the learner's internal network determines future growth;
+the other, PAC, described a model in which the external, global
+environmental network structure determines learners' growth patterns.
 Part of the findings largely replicate the results obtained in Hills et
@@
 
-\caption{\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined model pooling across languages .
+\caption{\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect.
 Ranges indicate 95\% confidence intervals.
-Fade color indicates estimates of PAC predictors in a model that does not include frequency and length as covariates.}\label{fig:regressions_all_img}
+Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates.}\label{fig:regressions_all_img}
 \end{figure}
@@
 
-A major results of the study is that children start by learning words
-that have high phonological and semantic similarity with a variety of
-other words in the learning environment, not in the child's available
+One important result of the study is that children start by learning
+words that have high phonological and semantic similarity with a variety
+of other words in the learning environment, not in the child's available
 lexicon. This suggests that children are sensitive to connectivity even
@@
 indirectly detect highly connected words, and why would such words be
-more readily learned? In the semantic case, free association can be
-predicted through the patterns of word co-occurrence (Griffiths,
-Steyvers, \& Tenenbaum, 2007), meaning that highly connected words tend
-to be the words that co-occur with many other words in various contexts.
-One possibility, suggested by Hills et al. (2010), is that the referents
-of such words are more easily disambiguated from other potential
-referents. Such effect was demonstrated by cross-situational learning
-experiments (Smith \& Yu, 2008).
+more readily learned?
+
+In the semantic case, free association can be predicted through the
+patterns of word co-occurrence (Griffiths, Steyvers, \& Tenenbaum,
+2007), meaning that highly connected words tend to be the words that
+co-occur with many other words in various contexts. One possibility,
+suggested by Hills et al. (2010), is that the referents of such words
+are more easily disambiguated from other potential referents (because
+their presence in mulitiple contexts provides more diambiguating
+statisitcs about their true referents). (Smith \& Yu, 2008) showed that
+children can disambiguate the words' referents based on such
+cross-situational statisitics (Smith \& Yu, 2008).
 
@@
 is, highly connected words tend to be made of frequent sound sequences.
-We know even infant (whose vocabulary is still very rudimentary) develop
-a sensitivity for high frequency sound sequences in the ambient language
-(Jusczyk, Luce, \& Charles-Luce, 1994). Interestingly, it was shown that
+Even infants (whose vocabulary is still very rudimentary) show a
+sensitivity for high frequency sound sequences in the ambient language
+(Jusczyk, Luce, \& Charles-Luce, 1994). Moreover, it was shown that
 phonotactic probability facilitates learning and recognition of novel
 words in toddlers and preschoolers (MacRoy-Higgins, Shafer, Schwartz, \&
-Marton, 2014; Storkel, 2001). Thus, children's ability to keep track of
-co-occurrence statistics (both at the semantic and phonological level)
-might explain their sensitivity and preference for highly connected
-words in the learning environment.
+Marton, 2014; Storkel, 2001). In other words, children's sensitivity to
+local phonotactic regularities might lead them to learn
+higher-probability words more easily. This learning effect in turn would
+lead to an observed pattern of growth that would appear to follow the
+PAC growth model even though learners themselves would only be tracking
+local statistics.
 
-Finally, this study shares a number of limitations with previous studies
-using similar research strategy and dataset. In particular, the results
-provide correlational but not causal evidence. Thus, the conclusions of
-this study require parallel evidence, especially from controlled
+Finally, while validating previous results using network growth models,
+our study suggests that these correlational patterns may emerge from the
+operation of simpler mechanisms. One question for future experimental
+work is whether such patterns of growth can be produced in controlled
 behavioral experiments.
@@
 \emph{Cognitive Science}, \emph{41}, 120--140.
+
+\hypertarget{ref-fenson94}{}
+Fenson, L., Dale, P. S., Reznick, J. S., Bates, E., Thal, D. J.,
+Pethick, S. J., \ldots{} Stiles, J. (1994). Variability in early
+communicative development. \emph{Monographs of the Society for Research
+in Child Development}, \emph{59}(5), i--185.
 
@@
 
+\hypertarget{ref-markman90}{}
+Markman, E. M. (1990). Constraints children place on word meanings.
+\emph{Cognitive Science}, \emph{14}(1), 57--77.
+
 \hypertarget{ref-nelson1998}{}
@@
 Retrieved from \url{http://w3.usf.edu/FreeAssociation/}
+
+\hypertarget{ref-roy2015}{}
+Roy, B. C., Frank, M. C., DeCamp, P., Miller, M., \& Roy, D. (2015).
+Predicting the birth of a spoken word. \emph{Proceedings of the National
+Academy of Sciences}, \emph{112}(41), 12663--12668.
+\url{http://doi.org/10.1073/pnas.1419773112}
 

### 2018-01-31 Main.Rmd
modif cogsci draft

@@
 ```{r}
-#make a loop
+#Data for plot
 degreeDist <- data.frame(matrix(ncol = 4, nrow = 0))
-x <- c("x", "y", "dimension", "language")
-colnames(degreeDist) <- x
+dist_names <- c("x", "y", "dimension", "language")
+colnames(degreeDist) <- dist_names
+
+#Parameters and test
+degreeTest <- data.frame(matrix(ncol = 5, nrow = 0))
+test_names <- c("xMin", "alpha", "pVal", "dimension","language")
+colnames(degreeTest) <- test_names
 
@@
 
-  #Do the transfomation
+  #fit and derive parameters for power law
   semList <- data_lang$Sem[data_lang$Sem != 0]
@@
     mutate(dimension='Sem', language  =  i)
+
+  #bootstrap to get p-value
+  sem_boot = bootstrap_p(sem_pl, no_of_sims=1000, threads=2)
+
+  sem_test <- data.frame(as.numeric(sem_pl$xmin), as.numeric(sem_pl$pars), as.numeric(sem_boot$p), 'Sem', i)
+  colnames(sem_test) <- test_names
 
@@
 
+  phono_boot = bootstrap_p(phono_pl, no_of_sims=1000, threads=2)
+
+  phono_test <- data.frame(as.numeric(phono_pl$xmin), as.numeric(phono_pl$pars), as.numeric(phono_boot$p), 'Phono', i)
+  colnames(phono_test) <- test_names
+
   dist_lang <- bind_rows(sem_dist, phono_dist)
+  test_lang <- bind_rows(sem_test, phono_test)
 
   degreeDist <- bind_rows(degreeDist, dist_lang) 
+  degreeTest <- bind_rows(degreeTest, test_lang)
 
@@
 
-feather::write_feather(degreeDist, "saved_data/degreeDist.feather")
+#feather::write_feather(degreeDist, "saved_data/degreeDist.feather")
 degreeDist <- feather::read_feather("saved_data/degreeDist.feather")
+
+feather::write_feather(degreeTest, "saved_data/degreeTest.feather")
+degreeTest <- feather::read_feather("saved_data/degreeTest.feather")
 

### 2018-01-31 cogsci/cogsci.Rmd
modif cogsci draft

@@
 
-    "Children tend to produce words earlier when they are connected to other words along both the phonological and semantic dimensions.
+    "Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions.
 Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.
-One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's ealy lexicon attract similar words.
-Another view suggests that learning is driven, not by highly connected words in the early internal lexicon, but by words that are highly connected in the external learning environment.
+One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words.
+Another view suggests that learning is driven  by highly connected word in the external learning environment instead of highly connected words in the early internal lexicon.
 The present study tests both scenarios systematically in both the phonological and the semantic domains, and across 8 languages.
@@
 Previous studies investigated early vocabulary networks based on different word relations such as shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological similarity.
-These studies have found that children tend to produce earlier the words that have higher neighborhood density (i.e., high connectivity in the network) both at the phonological and the semantic level [@stokes2010; @storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017; @beckage2011].
+These studies have found that children tend to produce earlier the words that have higher neighborhood density (i.e., high connectivity in the network) both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017].
 
@@
 These two proposals represent two divergent ideas about the role of lexical networks in acquisition.
-On the PAT proposal, network structure is a causal factor in early word learning; in contrast, on the PAC approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguisitc input (see discussion).
+On the PAT proposal, network structure is a causal factor in early word learning; in contrast, on the PAC approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguistic input (see discussion).
 
-```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Filled circles (I1-I4) represent known words (internal lexicon), and empty circles (E1 and E2) represent words that have not been learned yet (external lexicon).
+```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Illustration of the growth scenarios.
+Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
 Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
-For PAT, each candidate node is characterized with the average degree (i.e., number of links) of the existing nodes that it would attach to.
+For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
 Thus, according to PAT, the node E1 is more likely to enter the lexicon first.
-For PAC, each candidate node is characterized with its degree in the entire network.
-According th PAC, the node E2 is more likely to enter the lexicon first."}
+For PAC, the utility of a candidate node is its degree in the entire network.
+According to PAC, the node E2 is more likely to enter the lexicon first."}
 
@@
 Studies that investigate lexical network growth have focused on semantic networks using English data [@steyvers2005; @hills2009; @hills2010].
-The novelty of the current study is that it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT.
-It also provides a systematic comparison of both network growth scenarios in the phonological and the semantic domains and assesses their relative contribution to the learning process.
-Moreover, it tests the generality of the findings across eight languages.
-
-<!--The paper is organized as follows.
-First, we describe the dataset we used, the procedure we followed to construct both semantic and phonological networks.
-Next, we show the results of the various analyses we conducted comparing network growth scenarios across languages.
-Then we test the overall contribution of the networks in the learning process relative to other known predictors of age of acquisition (frequency and length).
-Finally we discuss the major results in relation to known experimental facts in language development, and we speculate about the potential learning mechanism that might drive early vocabulary learning.-->
+The novelty of the current study is threefold:  First, it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT.
+Second, it provides a systematic comparison of both network growth scenarios in the phonological and the semantic domains and assesses their relative contribution to the learning process.
+Third, it tests the generality of the findings across eight languages.
 
@@
     size = 0.5, alpha = 0.5) +
+  geom_abline(slope = -1)+
   coord_cartesian(xlim=c(-1,5))+
@@
 ```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
-Results are shown in each language for the phonological network (top) and the semantic network (bottom).
+Results are shown in each language for phonological and semantic networks.
 Each point is a word, with lines indicating linear model fits."}
@@
   theme_few()+
-  theme(aspect.ratio = 0.7)+
+  theme(aspect.ratio = 0.7,  text = element_text(size=9))+
   xlab("degree") +ylab("probability")
@@
 ```{r degree_distribution, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
-A perfect power law distribution should appear as a straight line in this graph."}
+A perfect power-law distribution should appear as a straight line in this graph."}
 plot_dist
@@
 We used the *Words and Sentence* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months).
-Following previous studies [e.g., @storkel2009; @hills2009], we restricted our analysis to the category of nouns.
-The age of acquisition was defined by the month at which a word was produced by at least 50% of children [@goodman2008].
+Following previous studies [@storkel2009; @hills2009], we restricted our analysis to the category of nouns.
+We defined the age of acquisition of a given word by the month at which this word was produced by at least 50% of children [@goodman2008].
+We excluded nouns that have not been learned (according to this criterion) by the last month for which we have CDI data.
 
@@
 We used the subset of nouns that had entries in the Florida Association Norms (see below).
-Since these norms are available only in English, we used the hand-checked translation equivalents provided by Braginsky by @braginsky2016, allowing us to use the English association norms across languages.
+Since these norms are available only in English, we used the hand-checked translation equivalents provided by @braginsky2016, allowing us to use the English association norms across languages.
 Table \ref{tab:stats} gives an overview of the data used.
-Translation equivalents were originally constructed for a subset of words appearing on the toddler CDI form (the subset is labeled *Words and Gestures*), and so not all words are currently available.
+Translation equivalents were originally constructed for a subset of words appearing on the toddler CDI form, and so not all words are currently available.
 Note, however, that all languages have at least 60% of nouns translated.
@@
 
-@hills2009, we used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998].
+We constructed the semantic networks following the procedure outlined in @hills2009.
+We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998].
 This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target).
@@
 A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms.
-Each node was characterized by its "indegree", which represents the number of links for which the word was the target.
-To model growth from month to month, we constructed a different network at each month, made of words that have been learned at that month.
+The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target.
+To model growth from month to month, we constructed a different network at each month, made of the words that have been acquired at that month.
 
@@
 
-We generated approximate International Phonetic Alphabet (IPA) transcriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein (edit) distance as a measure of phonological relatedness between two nodes.
+We generated approximate International Phonetic Alphabet (IPA) transcriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes.
 The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.
 
-In previous studies, two nodes were linked if they had an edit distance of 1 [@stokes2010; @storkel2009].
+In previous studies, two nodes were linked if they had an edit distance of 1 [e.g., @storkel2009].
 However, in these previous studies the network was built using an adult vocabulary.
@@
 Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.
-Each node was characterized with its degree, i.e., the number of links it shares with other words.
+The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
 
@@
 We constructed this network using nouns at the oldest age for which we have CDI data (e.g., in English this corresponds to the network by 30 months).
-This global netowrk is the end-state towards which both PAT and PAC should converge by the last month of learning.
-Morover, following @hills2009, we used this end-state netowrk as a proxy for the external connectivity in the learning environment.
+This global network is the end-state towards which both PAT and PAC should converge by the last month of learning.
+Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment.
 Below we analyse properties of this global networks that are relevant to PAT and/or PAC.
@@
 Connectivity in the global network is directly related to PAC as it represents the explicit criterion PAC uses to determine what words should be learned first (Figure \ref{fig:growth}).
-Therefore, a direct consequence of a PAC-like growth scenario is a correlation betweeen connectivity in the global network and the age of acquisition.\footnote{Note that this correlation is also compatible with PAT, even if this growth scenario does not rely explicity on external connectivity.
-Indeed, from a PAT perspective, higher connectivity in the global network is caused by earlier learning, i.e., some words end up being highly connected in the global network precisely because they happen to be acquired earlier (and therefore have a higher chance of forming more links over time).} Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its connectivity/degree (or indegree for the semantic network).
+Therefore, a direct consequence of a PAC-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{Note that this correlation is also compatible with PAT, even if this growth scenario does not rely explicitly on external connectivity.
+Indeed, from a PAT perspective, higher connectivity in the global network is caused by earlier learning, i.e., some words end up being highly connected in the global network precisely because they happen to be acquired earlier (and therefore have a higher chance of forming more links over time).} Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network).
 For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages.
@@
 
-###Power law degree distribution?
+###Power-law degree distribution?
 We also analysed the global network's degree distribution.
-This property is particularly relevant to PAT as this growth scenario is known to generate networks with a power-law degree distribution [@barabasi99].
-If the network displays this property, this fact would strongly suggests a PAT-like generative process.
+This property is particularly relevant to PAT as this growth scenario is known to generate networks with a power-law degree distribution [i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$, @barabasi99].
+If the network displays this property, this fact would suggests a PAT-like generative process.
 Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for PAT.
-The results are shown in Figure \ref{fig:degree_distribution}.
-Overall, we did not find consistent evidence for a power law distribution: the extent to which the degree distribution approximates a power law varies across dimensions and languages.
+The log-log plots are shown in Figure \ref{fig:degree_distribution}.
+We fit a discrete power law to each empirical degree distribution following the procedure outlined in @clauset09 and using the related R package [poweRlaw, @gillespie15].
+In brief, the analysis consists in two steps.
+First, we derive the optimal cut-off, $k_{min}$, above which the distribution is more likely to follow a power law\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}, and we estimate the corresponding scaling parameter $\alpha$.
+Second we calculate the goodness-to-fit, which results in a $p$-value quantifying the plausibility of the model.
+Overall, we did not find strong evidence against a power-law distribution: the $p$-value was generally above 0.1, except for the Italian phonological network where we  obtained  $p < 0.05$ (suggesting that the power law can be ruled out in this particular case).
 
-For a more direct test of the developmental process, we fit explicit growth models to the data (next section).
+In sum, the static properties of the global network do not provide conclusive evidence in favor or against any of the growth scenarios in question.
+For a more direct test of the developmental process, we need to fit explicit growth models to the data.
 <!--
@@
   scale_colour_solarized() +
-  theme_bw()+
-  theme(aspect.ratio = 0.7)
+  theme_few()+
+  theme(aspect.ratio = 0.7, axis.text.x = element_text(size=8))
 
@@
 ```{r pred_ind_img, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3.5, fig.align = "center", fig.cap = "\\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid).
-Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\\% credible intervals (computed using the highest density intervals)."}
+Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\\% credible intervals (computed using the highest density intervals).
+Positive values mean that learning proceeds according to the predictions of the growth scenario.
+Negative values mean that learning proceeds in opposition to the predictions of the growth scenario."}
 
@@
 To test the network growth scenarios, we fit different growth models to the data.
-We proceeded as follows.
 We calculated the probability that a word $w_i$, with a growth value $d_i$ would enter the lexicon at a given month, using a softmax function:
@@
 \noindent where $\beta$ is a fitted parameter that captures the magnitude of the relationship between network parameters and growth (analogous to a regression coefficient).
-A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first (see Figure \ref{fig:growth} for illustrations of growth scenarios, and how a word's growth value $d_i$ is defined in each of these scenarios).
+A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first (see Figure \ref{fig:growth} for an illustration of how growth values $d_i$ are defined in each growth scenario).
 The normalization includes all words that could be learned at that month.
@@
 The inference was performed using the probabilistic programming language  WebPPL [@dippl].
-We defined a uniform prior over $\beta$, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been actually learned at that month (using formula 1).
-Markov chain monte carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \ref{fig:pred_ind}.
+We defined a uniform prior over $\beta$, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using formula 1).
+Markov Chain Monte Carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \ref{fig:pred_ind}.
 
-Besides fitting a growth model to the data, we conducted another evaluation.
+Besides fitting a growth model to the data, we conducted a separate evaluation.
 This second evaluation consists in determining, in each month, the growth value distribution of all words that could possibly be learned at this month, and then computing the z-score of each learned word with respect to this distribution.
@@
 As a next step, we analysed their relative contribution to the learning process.
-This was done through adding more fitting parameters to the model, that is, by substituting $\beta d_i$ in formula (1) with: $$\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}$$ where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and PhonoPAC.
+This was done through adding more fitted parameters to the model, that is, by substituting $\beta d_i$ in formula (1) with: $$\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}$$ where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and PhonoPAC.
 Using the same fitting technique, we obtained the values shown in Figure \ref{fig:pred_ind}.
@@
   scale_colour_solarized() +
-  theme_bw()+
+  theme_few()+
   theme(aspect.ratio = 0.7)
@@
 
-```{r regressions_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:regressions_img}Estimates of predictor coefficients by language.
-Values above 0 indicate a positive relationship (e.g.
-longer words tend to have a higher AoA), while values below 0 indicate a negative relationship (e.g.
-words with higher frequency tend to have a lower AoA).
-Ranges indicate 95\\% confidence intervals."}
+```{r regressions_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:regressions_img}Estimates of predictor coefficients by language, with ranges indicating 95\\% confidence intervals.
+Positive values indicate a positive relationship (e.g.
+longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
+words with higher frequency tend to have a lower AoA)."}
 
@@
 
-We saw that the way semantic and phonological information is structured in the learning environment (i.e., PAC) contribute to noun learning across languages.
+We saw that the way semantic and phonological information is structured in the learning environment (i.e., PAC) contributes to noun learning across languages.
 However, we know that other factors influence learning as well [e.g., @braginsky2016].
@@
 
-Since PAT was uninformative, we dropped it from this analysis.
-Thus, we no longer needed to fit the growth model month-by-month as in the previous section.
-In fact, word utilities (i.e., growth values) in the case of PAC are fixed, they do not depend on previously learned words.
-A more direct way to assess and compare the contribution of PAC in relation to other word-level factors is through conducting linear regressions, where connectivity in the learning environment (at both the phonological and semantic level), frequency and length predict the age of acquisition.
+Since PAT was uninformative, we dropped it from this analysis, keeping only PAC.
+This simplified the model because we no longer needed to fit growth month-by-month.\footnote{This was a requirement only for PAT whose utilities varied from month to month, depending on previously learned words.} A more direct way to assess and compare the contribution of PAC in relation to other word-level factors is through conducting linear regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.
 
-We used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language (note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children).
-For each word, counts included words that shared the same stem  (e.g., cats counts as cat), or words that were synonymous (e.g.
+We used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children} For each word, counts included words that shared the same stem  (e.g., cats counts as cat), or words that were synonymous (e.g.
 father counts as daddy).
@@
 We conducted two analyses.
-We fit a linear regression for each language, and we fit a linear mixed-effect to all the data pooled across languages, with language as a random effect.
+We fit a linear regression for each language, and we fit a linear mixed-effect model to all the data pooled across languages, with language as a random effect.
 Figure \ref{fig:regressions_img} shows the coefficient estimate for each predictor in each language, and Figure \ref{fig:regressions_all_img} shows the coefficient estimates for all languages combined (all predictors were centered and scaled).
@@
 As for the factors of interest, i.e., semantic and phonological connectivity, we also found cross-linguistic differences.
-The phonological connectivity contributes to learning in languages such as Croatian, English and Russian, whereas semantic connectivity contributes to learning in Turkish, Spanish and to some extent in Croatian, but interestingly not in English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
+Phonological connectivity contributes to learning in languages such as Croatian, English and Russian, whereas semantic connectivity contributes to learning in Turkish, Spanish and to some extent in Croatian, but not in English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
 This contrasts with the original finding in Hills et al.
@@
 The present study provided a comprehensive analysis of how lexical connectivity influences the age of acquisition of nouns in toddlers.
-We compared two network growth scenarios and assessed their relative contributions of phonological vs.
-semantic networks across eight languages.
+We compared two network growth scenarios and assessed their relative contributions across eight languages.
 One scenario, PAT, described a "rich get richer" network growth model in which the structure of the learner's internal network determines future growth; the other, PAC, described a model in which the external, global environmental network structure determines learners' growth patterns.
-Part of the findings largely replicate the results obtained in @hills2009, i.e., semantic networks (based on free associations) grow by preferential acquisition, not by preferential attachment.
-Another finding was that phonological networks also grow primarily by preferential acquisition, especially when both scenarios (PAT and PAC) were pitted against each other in the same model.
+Part of the findings largely replicates the results obtained in @hills2009, i.e., semantic networks (based on free associations) grow by preferential acquisition, not by preferential attachment.
+A novel finding was that phonological networks also grow primarily by preferential acquisition, especially when both scenarios (PAT and PAC) were pitted against each other in the same model.
 These findings generalize well across languages.
 Moreover, both semantic and phonological connectivity in the learning environment (i.e., PAC) predict growth in a consistent way across many languages.
-However, when pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting learning in some languages, but not in others.
+Nevertheless, when pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting learning in some languages, but not in others.
 Despite this cross-linguistic variation, both phonological and semantic connectivity contribute to the overall learning (when data is pooled across languages).
@@
 
-One important result of the study is that children start by learning words that have high phonological and semantic similarity with a variety of other words in the learning environment, not in the child's available lexicon.
+One important result of the study is that children start by learning words that have high phonological and semantic similarity to a variety of other words in the learning environment, not in the child's available lexicon.
 This suggests that children are sensitive to connectivity even without having first acquired the connected words.
@@
 In the semantic case, free association can be predicted through the patterns of word co-occurrence [@griffiths07], meaning that highly connected words tend to be the words that co-occur with many other words in various contexts.
-One possibility, suggested by @hills2010, is that the referents of such words are more easily disambiguated from other potential referents (because their presence in mulitiple contexts provides more diambiguating statisitcs about their true referents).
-[@smith2008] showed that children can disambiguate the words' referents based on such cross-situational statisitics [@smith2008].
+One possibility, suggested by @hills2010, is that the referents of such words are more easily disambiguated from other potential referents because their presence in multiple contexts provides more cross-situational, disambiguating statistics about their true referents [@smith2008].
 
@@
 Even infants (whose vocabulary is still very rudimentary) show a sensitivity for high frequency sound sequences in the ambient language [@jusczyk1994].
-Moreover, it was shown that phonotactic probability facilitates learning and recognition of novel words in toddlers and preschoolers [@storkel2001;  @higgins2014].
+Moreover, phonotactic probability facilitates learning and recognition [e.g., @storkel2001].
 In other words, children's sensitivity to local phonotactic regularities might lead them to learn higher-probability words more easily.
-This learning effect in turn would lead to an observed pattern of growth that would appear to follow the PAC growth model even though learners themselves would only be tracking local statistics.
+This learning effect, in turn, would lead to an observed pattern of growth that would appear to follow the PAC growth model even though learners themselves would only be tracking local statistics.
 
-Finally, while validating previous results using network growth models, our study suggests that these correlational patterns may emerge from the operation of simpler mechanisms.
+Finally, while validating previous results using network growth models, our study suggests that these correlational patterns may emerge from the operation of simpler mechanisms in both the semantic and phonological domains.
 One question for future experimental work is whether such patterns of growth can be produced in controlled behavioral experiments.
@@
 
-This work was supported by a post-doctoral grant from the Fyssen Foundation.
+This work was supported by a post-doctoral grant from the Fyssen Foundation, NSF #1528526, and NSF #1659585.
 

### 2018-01-31 cogsci/cogsci.tex
modif cogsci draft

@@
 \begin{abstract}
-Children tend to produce words earlier when they are connected to other
-words along both the phonological and semantic dimensions. Though this
-connectivity effect has been extensively documented, little is known
-about the underlying developmental mechanism. One view suggests that
-learning is primarily driven by a network growth model where highly
-connected words in the child's ealy lexicon attract similar words.
-Another view suggests that learning is driven, not by highly connected
-words in the early internal lexicon, but by words that are highly
-connected in the external learning environment. The present study tests
-both scenarios systematically in both the phonological and the semantic
-domains, and across 8 languages. We show that external connectivity in
-the learning environment drives growth in both the semantic and the
-phonological networks, and that this pattern is consistent
-cross-linguistically. The findings suggest a word learning mechanism
-where children harness their statistical learning abilities to
+Children tend to produce words earlier when they are connected to a
+variety of other words along both the phonological and semantic
+dimensions. Though this connectivity effect has been extensively
+documented, little is known about the underlying developmental
+mechanism. One view suggests that learning is primarily driven by a
+network growth model where highly connected words in the child's early
+lexicon attract similar words. Another view suggests that learning is
+driven by highly connected word in the external learning environment
+instead of highly connected words in the early internal lexicon. The
+present study tests both scenarios systematically in both the
+phonological and the semantic domains, and across 8 languages. We show
+that external connectivity in the learning environment drives growth in
+both the semantic and the phonological networks, and that this pattern
+is consistent cross-linguistically. The findings suggest a word learning
+mechanism where children harness their statistical learning abilities to
 (indirectly) detect and learn highly connected words in the learning
@@
 neighborhood density (i.e., high connectivity in the network) both at
-the phonological and the semantic level (Beckage, Smith, \& Hills, 2011;
-Engelthaler \& Hills, 2017; Hills, Maouene, Riordan, \& Smith, 2010;
-Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Stella, Beckage, \&
-Brede, 2017; Stokes, 2010; Storkel, 2009).
+the phonological and the semantic level (Engelthaler \& Hills, 2017;
+Hills, Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya,
+\& Smith, 2009; Stella, Beckage, \& Brede, 2017; Storkel, 2009).
 
@@
 represented and, therefore, might be an epiphenomenon of the statistics
-of the linguisitc input (see discussion).
+of the linguistic input (see discussion).
 
@@
 
-\caption{\label{fig:growth}Filled circles (I1-I4) represent known words (internal lexicon), and empty circles (E1 and E2) represent words that have not been learned yet (external lexicon).
+\caption{\label{fig:growth}Illustration of the growth scenarios.
+Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
 Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
-For PAT, each candidate node is characterized with the average degree (i.e., number of links) of the existing nodes that it would attach to.
+For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
 Thus, according to PAT, the node E1 is more likely to enter the lexicon first.
-For PAC, each candidate node is characterized with its degree in the entire network.
-According th PAC, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
+For PAC, the utility of a candidate node is its degree in the entire network.
+According to PAC, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
 \end{figure}
@@
 networks using English data (Hills et al., 2010, 2009; Steyvers \&
-Tenenbaum, 2005). The novelty of the current study is that it
-investigates whether phonological networks, like semantic networks, grow
-by PAC, or if they rather grow by PAT. It also provides a systematic
-comparison of both network growth scenarios in the phonological and the
-semantic domains and assesses their relative contribution to the
-learning process. Moreover, it tests the generality of the findings
-across eight languages.
+Tenenbaum, 2005). The novelty of the current study is threefold: First,
+it investigates whether phonological networks, like semantic networks,
+grow by PAC, or if they rather grow by PAT. Second, it provides a
+systematic comparison of both network growth scenarios in the
+phonological and the semantic domains and assesses their relative
+contribution to the learning process. Third, it tests the generality of
+the findings across eight languages.
 
@@
 \caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
-Results are shown in each language for the phonological network (top) and the semantic network (bottom).
+Results are shown in each language for phonological and semantic networks.
 Each point is a word, with lines indicating linear model fits.}\label{fig:all_data}
@@
 \caption{\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
-A perfect power law distribution should appear as a straight line in this graph.}\label{fig:degree_distribution}
+A perfect power-law distribution should appear as a straight line in this graph.}\label{fig:degree_distribution}
 \end{figure*}
@@
 productive vocabulary of toddlers (age varied between 16 to 36 months).
-Following previous studies (Hills et al., 2009; e.g., Storkel, 2009), we
-restricted our analysis to the category of nouns. The age of acquisition
-was defined by the month at which a word was produced by at least 50\%
-of children (J. C. Goodman et al., 2008).
+Following previous studies (Hills et al., 2009; Storkel, 2009), we
+restricted our analysis to the category of nouns. We defined the age of
+acquisition of a given word by the month at which this word was produced
+by at least 50\% of children (J. C. Goodman et al., 2008). We excluded
+nouns that have not been learned (according to this criterion) by the
+last month for which we have CDI data.
 
@@
 Since these norms are available only in English, we used the
-hand-checked translation equivalents provided by Braginsky by Braginsky
-et al. (2016), allowing us to use the English association norms across
+hand-checked translation equivalents provided by Braginsky et al.
+(2016), allowing us to use the English association norms across
 languages. Table \ref{tab:stats} gives an overview of the data used.
 Translation equivalents were originally constructed for a subset of
-words appearing on the toddler CDI form (the subset is labeled
-\emph{Words and Gestures}), and so not all words are currently
-available. Note, however, that all languages have at least 60\% of nouns
-translated.
+words appearing on the toddler CDI form, and so not all words are
+currently available. Note, however, that all languages have at least
+60\% of nouns translated.
 
@@
 
-Hills et al. (2009), we used as an index of semantic relatedness the
+We constructed the semantic networks following the procedure outlined in
+Hills et al. (2009). We used as an index of semantic relatedness the
 Florida Free Association Norms (Nelson, McEvoy, \& Schreiber, 1998).
@@
 link from the cue to the target if there was a cue-target relationship
-between these nodes in the association norms. Each node was
-characterized by its ``indegree'', which represents the number of links
+between these nodes in the association norms. The connectivity of a
+given node was characterized by its \emph{indegree}: the number of links
 for which the word was the target. To model growth from month to month,
-we constructed a different network at each month, made of words that
-have been learned at that month.
+we constructed a different network at each month, made of the words that
+have been acquired at that month.
 
@@
 \textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.} We used
-the Levenshtein (edit) distance as a measure of phonological relatedness
-between two nodes. The measure counts the minimum number of operations
-(insertions, deletions, substitutions) required to change one string
-into another.
+the Levenshtein distance (also known as edit distance) as a measure of
+phonological relatedness between two nodes. The measure counts the
+minimum number of operations (insertions, deletions, substitutions)
+required to change one string into another.
 
 In previous studies, two nodes were linked if they had an edit distance
-of 1 (Stokes, 2010; Storkel, 2009). However, in these previous studies
-the network was built using an adult vocabulary. However, since the
+of 1 (e.g., Storkel, 2009). However, in these previous studies the
+network was built using an adult vocabulary. However, since the
 children's vocabulary contains very few word pairs with an edit distance
@@
 increased the threshold from 1 to 2, that is, two nodes were related if
-their edit distance was equal to 1 or 2. Each node was characterized
-with its degree, i.e., the number of links it shares with other words.
+their edit distance was equal to 1 or 2. The connectivity of a given
+node was characterized with its \emph{degree}: the number of links it
+shares with other words.
 
@@
 have CDI data (e.g., in English this corresponds to the network by 30
-months). This global netowrk is the end-state towards which both PAT and
-PAC should converge by the last month of learning. Morover, following
-Hills et al. (2009), we used this end-state netowrk as a proxy for the
+months). This global network is the end-state towards which both PAT and
+PAC should converge by the last month of learning. Moreover, following
+Hills et al. (2009), we used this end-state network as a proxy for the
 external connectivity in the learning environment. Below we analyse
@@
 should be learned first (Figure \ref{fig:growth}). Therefore, a direct
-consequence of a PAC-like growth scenario is a correlation betweeen
+consequence of a PAC-like growth scenario is a correlation between
 connectivity in the global network and the age of
-acquisition.\footnote{Note that this correlation is also compatible with PAT, even if this growth scenario does not rely explicity on external connectivity.
+acquisition.\footnote{Note that this correlation is also compatible with PAT, even if this growth scenario does not rely explicitly on external connectivity.
 Indeed, from a PAT perspective, higher connectivity in the global network is caused by earlier learning, i.e., some words end up being highly connected in the global network precisely because they happen to be acquired earlier (and therefore have a higher chance of forming more links over time).}
 Figure \ref{fig:data_all} shows how the age of acquisition for each word
-varies as a function of its connectivity/degree (or indegree for the
-semantic network). For ease of visual comparison, the predictor (i.e.,
-the degree) was centered and scaled across languages. The plots show,
+varies as a function of its degree (or indegree for the semantic
+network). For ease of visual comparison, the predictor (i.e., the
+degree) was centered and scaled across languages. The plots show,
 overall, a negative correlation between the month of acquisition and the
@@
 
-\subsubsection{Power law degree
+\subsubsection{Power-law degree
 distribution?}\label{power-law-degree-distribution}
@@
 is particularly relevant to PAT as this growth scenario is known to
-generate networks with a power-law degree distribution (Barabasi \&
-Albert, 1999). If the network displays this property, this fact would
-strongly suggests a PAT-like generative process. Conversely, if the
-degree distribution does not follow a power law, this fact would weaken
-the case for PAT. The results are shown in Figure
-\ref{fig:degree_distribution}. Overall, we did not find consistent
-evidence for a power law distribution: the extent to which the degree
-distribution approximates a power law varies across dimensions and
-languages.
+generate networks with a power-law degree distribution (i.e., a
+distribution of the form \(p(k) \propto \frac{1}{k^{\alpha}}\), Barabasi
+\& Albert, 1999). If the network displays this property, this fact would
+suggests a PAT-like generative process. Conversely, if the degree
+distribution does not follow a power law, this fact would weaken the
+case for PAT. The log-log plots are shown in Figure
+\ref{fig:degree_distribution}. We fit a discrete power law to each
+empirical degree distribution following the procedure outlined in
+Clauset, Shalizi, \& Newman (2009) and using the related R package
+(poweRlaw, Gillespie, 2015). In brief, the analysis consists in two
+steps. First, we derive the optimal cut-off, \(k_{min}\), above which
+the distribution is more likely to follow a power
+law\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.},
+and we estimate the corresponding scaling parameter \(\alpha\). Second
+we calculate the goodness-to-fit, which results in a \(p\)-value
+quantifying the plausibility of the model. Overall, we did not find
+strong evidence against a power-law distribution: the \(p\)-value was
+generally above 0.1, except for the Italian phonological network where
+we obtained \(p < 0.05\) (suggesting that the power law can be ruled out
+in this particular case).
 
-For a more direct test of the developmental process, we fit explicit
-growth models to the data (next section).
+In sum, the static properties of the global network do not provide
+conclusive evidence in favor or against any of the growth scenarios in
+question. For a more direct test of the developmental process, we need
+to fit explicit growth models to the data.
 
@@
 \caption{\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid).
-Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\% credible intervals (computed using the highest density intervals).}\label{fig:pred_ind_img}
+Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\% credible intervals (computed using the highest density intervals).
+Positive values mean that learning proceeds according to the predictions of the growth scenario.
+Negative values mean that learning proceeds in opposition to the predictions of the growth scenario.}\label{fig:pred_ind_img}
 \end{figure*}
@@
 To test the network growth scenarios, we fit different growth models to
-the data. We proceeded as follows. We calculated the probability that a
-word \(w_i\), with a growth value \(d_i\) would enter the lexicon at a
-given month, using a softmax function:
+the data. We calculated the probability that a word \(w_i\), with a
+growth value \(d_i\) would enter the lexicon at a given month, using a
+softmax function:
 
@@
 and a negative value means that words with lower growth values are
-acquired first (see Figure \ref{fig:growth} for illustrations of growth
-scenarios, and how a word's growth value \(d_i\) is defined in each of
-these scenarios). The normalization includes all words that could be
-learned at that month.
+acquired first (see Figure \ref{fig:growth} for an illustration of how
+growth values \(d_i\) are defined in each growth scenario). The
+normalization includes all words that could be learned at that month.
 
@@
 over words that could possibly enter the lexicon at that month, fit to
-the words that have been actually learned at that month (using formula
-1). Markov chain monte carlo sampling resulted in a posterior
-distribution over \(\beta\), which we summarized in Figure
-\ref{fig:pred_ind}.
+the words that have been learned at that month (using formula 1). Markov
+Chain Monte Carlo sampling resulted in a posterior distribution over
+\(\beta\), which we summarized in Figure \ref{fig:pred_ind}.
 
-Besides fitting a growth model to the data, we conducted another
+Besides fitting a growth model to the data, we conducted a separate
 evaluation. This second evaluation consists in determining, in each
@@
 step, we analysed their relative contribution to the learning process.
-This was done through adding more fitting parameters to the model, that
+This was done through adding more fitted parameters to the model, that
 is, by substituting \(\beta d_i\) in formula (1) with:
@@
 
-\caption{\label{fig:regressions_img}Estimates of predictor coefficients by language.
-Values above 0 indicate a positive relationship (e.g.
-longer words tend to have a higher AoA), while values below 0 indicate a negative relationship (e.g.
-words with higher frequency tend to have a lower AoA).
-Ranges indicate 95\% confidence intervals.}\label{fig:regressions_img}
+\caption{\label{fig:regressions_img}Estimates of predictor coefficients by language, with ranges indicating 95\% confidence intervals.
+Positive values indicate a positive relationship (e.g.
+longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
+words with higher frequency tend to have a lower AoA).}\label{fig:regressions_img}
 \end{figure*}
@@
 We saw that the way semantic and phonological information is structured
-in the learning environment (i.e., PAC) contribute to noun learning
+in the learning environment (i.e., PAC) contributes to noun learning
 across languages. However, we know that other factors influence learning
@@
 
-Since PAT was uninformative, we dropped it from this analysis. Thus, we
-no longer needed to fit the growth model month-by-month as in the
-previous section. In fact, word utilities (i.e., growth values) in the
-case of PAC are fixed, they do not depend on previously learned words. A
-more direct way to assess and compare the contribution of PAC in
+Since PAT was uninformative, we dropped it from this analysis, keeping
+only PAC. This simplified the model because we no longer needed to fit
+growth
+month-by-month.\footnote{This was a requirement only for PAT whose utilities varied from month to month, depending on previously learned words.}
+A more direct way to assess and compare the contribution of PAC in
 relation to other word-level factors is through conducting linear
-regressions, where connectivity in the learning environment (at both the
-phonological and semantic level), frequency and length predict the age
-of acquisition.
+regressions, where connectivity in the learning environment, frequency
+and length predict the age of acquisition.
 
 We used the frequency estimates from Braginsky et al. (2016) where
-unigram counts were derived based on CHILDES corpora in each language
-(note that these frequency counts are based on transcripts from
-independent sets of children and represent a general estimate of
-environmental frequency across children). For each word, counts included
-words that shared the same stem (e.g., cats counts as cat), or words
-that were synonymous (e.g.~father counts as daddy). For word length, we
-used our generated IPA transcription.
+unigram counts were derived based on CHILDES corpora in each
+language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children}
+For each word, counts included words that shared the same stem (e.g.,
+cats counts as cat), or words that were synonymous (e.g.~father counts
+as daddy). For word length, we used our generated IPA transcription.
 
 We conducted two analyses. We fit a linear regression for each language,
-and we fit a linear mixed-effect to all the data pooled across
+and we fit a linear mixed-effect model to all the data pooled across
 languages, with language as a random effect. Figure
@@
 the factors of interest, i.e., semantic and phonological connectivity,
-we also found cross-linguistic differences. The phonological
-connectivity contributes to learning in languages such as Croatian,
-English and Russian, whereas semantic connectivity contributes to
-learning in Turkish, Spanish and to some extent in Croatian, but
-interestingly not in
+we also found cross-linguistic differences. Phonological connectivity
+contributes to learning in languages such as Croatian, English and
+Russian, whereas semantic connectivity contributes to learning in
+Turkish, Spanish and to some extent in Croatian, but not in
 English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
@@
 compared two network growth scenarios and assessed their relative
-contributions and the relative contributions of phonological
-vs.~semantic networks across eight languages. One scenario, PAT,
-described a ``rich get richer'' network growth model in which the
-structure of the learner's internal network determines future growth;
-the other, PAC, described a model in which the external, global
-environmental network structure determines learners' growth patterns.
-Part of the findings largely replicate the results obtained in Hills et
-al. (2009), i.e., semantic networks (based on free associations) grow by
-preferential acquisition, not by preferential attachment. Another
-finding was that phonological networks also grow primarily by
-preferential acquisition, especially when both scenarios (PAT and PAC)
-were pitted against each other in the same model. These findings
-generalize well across languages. Moreover, both semantic and
-phonological connectivity in the learning environment (i.e., PAC)
-predict growth in a consistent way across many languages. However, when
-pitted against other known predictors of age of acquisition (word
-frequency and length), the effect of word connectivity shows a
-cross-linguistic variation, predicting learning in some languages, but
-not in others. Despite this cross-linguistic variation, both
-phonological and semantic connectivity contribute to the overall
-learning (when data is pooled across languages).
+contributions across eight languages. One scenario, PAT, described a
+``rich get richer'' network growth model in which the structure of the
+learner's internal network determines future growth; the other, PAC,
+described a model in which the external, global environmental network
+structure determines learners' growth patterns. Part of the findings
+largely replicates the results obtained in Hills et al. (2009), i.e.,
+semantic networks (based on free associations) grow by preferential
+acquisition, not by preferential attachment. A novel finding was that
+phonological networks also grow primarily by preferential acquisition,
+especially when both scenarios (PAT and PAC) were pitted against each
+other in the same model. These findings generalize well across
+languages. Moreover, both semantic and phonological connectivity in the
+learning environment (i.e., PAC) predict growth in a consistent way
+across many languages. Nevertheless, when pitted against other known
+predictors of age of acquisition (word frequency and length), the effect
+of word connectivity shows a cross-linguistic variation, predicting
+learning in some languages, but not in others. Despite this
+cross-linguistic variation, both phonological and semantic connectivity
+contribute to the overall learning (when data is pooled across
+languages).
 
@@
 One important result of the study is that children start by learning
-words that have high phonological and semantic similarity with a variety
+words that have high phonological and semantic similarity to a variety
 of other words in the learning environment, not in the child's available
@@
 suggested by Hills et al. (2010), is that the referents of such words
-are more easily disambiguated from other potential referents (because
-their presence in mulitiple contexts provides more diambiguating
-statisitcs about their true referents). (Smith \& Yu, 2008) showed that
-children can disambiguate the words' referents based on such
-cross-situational statisitics (Smith \& Yu, 2008).
+are more easily disambiguated from other potential referents because
+their presence in multiple contexts provides more cross-situational,
+disambiguating statistics about their true referents (Smith \& Yu,
+2008).
 
@@
 sensitivity for high frequency sound sequences in the ambient language
-(Jusczyk, Luce, \& Charles-Luce, 1994). Moreover, it was shown that
-phonotactic probability facilitates learning and recognition of novel
-words in toddlers and preschoolers (MacRoy-Higgins, Shafer, Schwartz, \&
-Marton, 2014; Storkel, 2001). In other words, children's sensitivity to
-local phonotactic regularities might lead them to learn
-higher-probability words more easily. This learning effect in turn would
-lead to an observed pattern of growth that would appear to follow the
-PAC growth model even though learners themselves would only be tracking
-local statistics.
+(Jusczyk, Luce, \& Charles-Luce, 1994). Moreover, phonotactic
+probability facilitates learning and recognition (e.g., Storkel, 2001).
+In other words, children's sensitivity to local phonotactic regularities
+might lead them to learn higher-probability words more easily. This
+learning effect, in turn, would lead to an observed pattern of growth
+that would appear to follow the PAC growth model even though learners
+themselves would only be tracking local statistics.
 
@@
 our study suggests that these correlational patterns may emerge from the
-operation of simpler mechanisms. One question for future experimental
-work is whether such patterns of growth can be produced in controlled
-behavioral experiments.
+operation of simpler mechanisms in both the semantic and phonological
+domains. One question for future experimental work is whether such
+patterns of growth can be produced in controlled behavioral experiments.
 
@@
 This work was supported by a post-doctoral grant from the Fyssen
-Foundation.
+Foundation, NSF \#1528526, and NSF \#1659585.
 
@@
 
-\hypertarget{ref-beckage2011}{}
-Beckage, N. M., Smith, L., \& Hills, T. T. (2011). Small worlds and
-semantic network growth in typical and late talkers. \emph{PLOS ONE},
-\emph{6}(5), 1--6.
-
 \hypertarget{ref-braginsky2016}{}
@@
 the Cognitive Science Society}.
+
+\hypertarget{ref-clauset09}{}
+Clauset, A., Shalizi, C. R., \& Newman, M. E. J. (2009). Power-law
+distributions in empirical data. \emph{SIAM Review}, \emph{51}(4),
+661--703.
 
@@
 \emph{Journal of Child Language}, \emph{44}(3), 677--694.
+
+\hypertarget{ref-gillespie15}{}
+Gillespie, C. S. (2015). Fitting heavy tailed distributions: The
+poweRlaw package. \emph{Journal of Statistical Software}, \emph{64}(2),
+1--16. Retrieved from \url{http://www.jstatsoft.org/v64/i02/}
 
@@
 
-\hypertarget{ref-higgins2014}{}
-MacRoy-Higgins, M., Shafer, V. L., Schwartz, R. G., \& Marton, K.
-(2014). The influence of phonotactic probability on word recognition in
-toddlers. \emph{Child Language Teaching and Therapy}, \emph{30}(1),
-117--130.
-
 \hypertarget{ref-markman90}{}
@@
 
-\hypertarget{ref-stokes2010}{}
-Stokes, S. F. (2010). Neighborhood density and word frequency predict
-vocabulary size in toddlers. \emph{Journal of Speech, Language, and
-Hearing Research}, \emph{53}(3), 670--683.
-
 \hypertarget{ref-storkel2001}{}

### 2018-02-01 cogsci/cogsci.Rmd
final modif on cogsci

@@
 One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words.
-Another view suggests that learning is driven  by highly connected word in the external learning environment instead of highly connected words in the early internal lexicon.
-The present study tests both scenarios systematically in both the phonological and the semantic domains, and across 8 languages.
+Another view suggests that learning is driven  by highly connected words in the external learning environment instead of highly connected words in the early internal lexicon.
+The present study tests both scenarios systematically in both the phonological and semantic domains, and across 8 languages.
 We show that external connectivity in the learning environment drives growth in both the semantic and the phonological networks, and that this pattern is consistent cross-linguistically.
@@
 To investigate this question, scientists have adopted multiple research strategies, from conducting controlled laboratory experiments [e.g.
-@markman90] to analysing dense corpora capturing language learning in context [e.g., @roy2015].
+@markman90] to analyzing dense corpora capturing language learning in context [e.g., @roy2015].
 One strategy consists in documenting the timeline of words' acquisition, and studying the properties that make words easy or hard to learn.
@@
 The lexical structure is best characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words.
-Previous studies investigated early vocabulary networks based on different word relations such as shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological similarity.
-These studies have found that children tend to produce earlier the words that have higher neighborhood density (i.e., high connectivity in the network) both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017].
+Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological similarity.
+These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017].
 
-While most studies focused on the static properties of the lexical network, a few have investigated the underlying developmental process.
-@steyvers2005 suggested that the effect of connectivity is the consequence of how the lexical network gets constructed in the child's mind.
+While most studies have focused on the static properties of the lexical network, a few have investigated the underlying developmental process.
+In particular, @steyvers2005 suggested that the observed effects of connectivity are the consequence of how the lexical network gets constructed in the child's mind.
 According to this explanation, known as Preferential Attachment (PAT), highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99].
@@
 These two proposals represent two divergent ideas about the role of lexical networks in acquisition.
-On the PAT proposal, network structure is a causal factor in early word learning; in contrast, on the PAC approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguistic input (see discussion).
+On the PAT proposal, network structure is a causal factor in early word learning; in contrast, on the PAC approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguistic input.
 
@@
 #Import data from saved
-degreeDist <- feather::read_feather("../saved_data/degreeDist.feather")
+degreeDist <- feather::read_feather("../saved_data/degreeDist.feather") %>%
+  dplyr::rename(Dimension = dimension)
 
-plot_dist <- ggplot(data = degreeDist,  aes(x=x, y=y, col=dimension))+
+plot_dist <- ggplot(data = degreeDist,  aes(x=x, y=y, col=Dimension))+
   facet_grid(. ~ language)+
@@
 Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94].
-We used the *Words and Sentence* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months).
-Following previous studies [@storkel2009; @hills2009], we restricted our analysis to the category of nouns.
-We defined the age of acquisition of a given word by the month at which this word was produced by at least 50% of children [@goodman2008].
-We excluded nouns that have not been learned (according to this criterion) by the last month for which we have CDI data.
+We used the *Words and Sentences* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months).
+Following previous studies [@storkel2009; @hills2009], we restricted our analysis to nouns.
+We defined the age of acquisition of a given word by the month at which this word was produced by at least 50% of children [@goodman2008], and we excluded nouns that have not been learned (according to this criterion) by the last month for which we have CDI data.
 
@@
 
-We constructed the semantic networks following the procedure outlined in @hills2009.
+We constructed semantic networks following the procedure outlined in @hills2009.
 We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998].
@@
 The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target.
-To model growth from month to month, we constructed a different network at each month, made of the words that have been acquired at that month.
+To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.
 
@@
 However, in these previous studies the network was built using an adult vocabulary.
-However, since the children's vocabulary contains very few word pairs with an edit distance of 1, the resulting networks were too sparse and uninformative.
+In the current study, however, network growth models are based on the children's early vocabulary which contains very few word pairs with an edit distance of 1.
+When using this threshold, the resulting networks were too sparse and uninformative.
 Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.
@@
 
-We start by analysing word connectivity in the global (static) network.
-We constructed this network using nouns at the oldest age for which we have CDI data (e.g., in English this corresponds to the network by 30 months).
+We start by analyzing word connectivity in the global (static) network.
+We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds to the network by 30 months).
 This global network is the end-state towards which both PAT and PAC should converge by the last month of learning.
 Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment.
-Below we analyse properties of this global networks that are relevant to PAT and/or PAC.
+Below we analyze properties of this global networks that are relevant to PAC and/or PAT.
 
@@
 Connectivity in the global network is directly related to PAC as it represents the explicit criterion PAC uses to determine what words should be learned first (Figure \ref{fig:growth}).
-Therefore, a direct consequence of a PAC-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{Note that this correlation is also compatible with PAT, even if this growth scenario does not rely explicitly on external connectivity.
-Indeed, from a PAT perspective, higher connectivity in the global network is caused by earlier learning, i.e., some words end up being highly connected in the global network precisely because they happen to be acquired earlier (and therefore have a higher chance of forming more links over time).} Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network).
+Therefore, a direct consequence of a PAC-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed.
+Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around.
+Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network).
 For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages.
@@
 ###Power-law degree distribution?
-We also analysed the global network's degree distribution.
-This property is particularly relevant to PAT as this growth scenario is known to generate networks with a power-law degree distribution [i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$, @barabasi99].
-If the network displays this property, this fact would suggests a PAT-like generative process.
+We also analyzed the global network's degree distribution.
+The shape of this distribution is particularly relevant to PAT as this growth scenario is known to generate networks with a power-law degree distribution [i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$, @barabasi99].
+If the network displays this property, this fact would suggest a PAT-like generative process.
 Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for PAT.
 The log-log plots are shown in Figure \ref{fig:degree_distribution}.
-We fit a discrete power law to each empirical degree distribution following the procedure outlined in @clauset09 and using the related R package [poweRlaw, @gillespie15].
-In brief, the analysis consists in two steps.
-First, we derive the optimal cut-off, $k_{min}$, above which the distribution is more likely to follow a power law\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}, and we estimate the corresponding scaling parameter $\alpha$.
-Second we calculate the goodness-to-fit, which results in a $p$-value quantifying the plausibility of the model.
-Overall, we did not find strong evidence against a power-law distribution: the $p$-value was generally above 0.1, except for the Italian phonological network where we  obtained  $p < 0.05$ (suggesting that the power law can be ruled out in this particular case).
+We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using the related R package [poweRlaw, @gillespie15].
+In brief, the analysis consisted in two steps.
+First, we derived the optimal cut-off, $k_{min}$, above which the distribution is more likely to follow a power law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter $\alpha$.
+Second we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model.
+Overall, we could not reject the null hypothesis of a power-law distribution: the $p$-value was generally above 0.1, except for the Italian phonological network where we obtained  $p < 0.05$, suggesting that the power law can be ruled out in this particular case.
 
-In sum, the static properties of the global network do not provide conclusive evidence in favor or against any of the growth scenarios in question.
-For a more direct test of the developmental process, we need to fit explicit growth models to the data.
+In sum, the static properties of the global network are *a priori* compatible with both PAT and PAC.
+In order to decide between these two developmental scenarios, we need to fit explicit growth models to the data.
 <!--
@@
 
-Besides fitting a growth model to the data, we conducted a separate evaluation.
+<!--Besides fitting a growth model to the data, we conducted a separate evaluation.
 This second evaluation consists in determining, in each month, the growth value distribution of all words that could possibly be learned at this month, and then computing the z-score of each learned word with respect to this distribution.
-For each growth scenario, we tested if the distribution constituted by the z-scores of all learned words was different from zero, using a one-sample t-test.
+For each growth scenario, we tested if the distribution constituted by the z-scores of all learned words was different from zero, using a one-sample t-test.-->
 
-The results from both evaluations were very similar and lead essentially to the same conclusions.\footnote{we do not show here the results of the second evaluation because they were redundant with the results of the first evaluation} For the semantic networks, the results replicate Hills et al.'s finding in English, which was that the semantic network grows by PAC, not by PAT.
-Moreover, this finding held in seven of the eight languages we examined.
-The PAC model also fit better than PAT for phonological networks.
+<!--The results from both evaluations were very similar and lead essentially to the same conclusions.\footnote{We do not show here the results of the second evaluation because they were redundant with the results of the first evaluation}-->For the semantic networks, the results replicate Hills et al.'s finding in English, which is that the semantic network grows by PAC, not by PAT.
+Moreover, this finding holds in seven of the eight languages we examined.\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
+However, our findings do not support this assumption as the effects were generally similar in magnitude cross-linguistically.} The PAC model also fits better than PAT for phonological networks.
 We note however that PAT, though weaker, fares  better for the phonological networks (where it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian) than it does for the semantic networks (where it is rather universally unpredictive).
@@
 Above we evaluated the network growth scenarios individually.
-As a next step, we analysed their relative contribution to the learning process.
+As a next step, we analyzed their relative contribution to the learning process.
 This was done through adding more fitted parameters to the model, that is, by substituting $\beta d_i$ in formula (1) with: $$\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}$$ where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and PhonoPAC.
@@
 
-## Comparison to other known predictors of age of acquisition
+## Comparison to other predictors of age of acquisition
 
@@
 Since PAT was uninformative, we dropped it from this analysis, keeping only PAC.
-This simplified the model because we no longer needed to fit growth month-by-month.\footnote{This was a requirement only for PAT whose utilities varied from month to month, depending on previously learned words.} A more direct way to assess and compare the contribution of PAC in relation to other word-level factors is through conducting linear regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.
+This simplified the model because we no longer needed to fit growth month-by-month.\footnote{This was a requirement only for PAT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.} A more direct way to assess and compare the contribution of PAC in relation to other word-level factors is through conducting linear regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.
 
-We used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children} For each word, counts included words that shared the same stem  (e.g., cats counts as cat), or words that were synonymous (e.g.
-father counts as daddy).
-For word length, we used our generated IPA transcription.
+We used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.} For each word, counts included words that shared the same stem  (e.g., "cats" counts as "cat"), or words that were synonymous (e.g.
+"father" counts as "daddy").
+For word length, we counted the number of phonemes in our generated IPA transcription.
 
@@
 However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates.
-Another important difference is the number of words tested: our study uses a larger set of nouns.} Despite this cross-linguistic variation, both phonological and semantic connectivity remain significant predictors in the global model.
+Another important difference is the number of words tested: Our study uses a larger set of nouns.} Despite these cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.
 
@@
 We compared two network growth scenarios and assessed their relative contributions across eight languages.
-One scenario, PAT, described a "rich get richer" network growth model in which the structure of the learner's internal network determines future growth; the other, PAC, described a model in which the external, global environmental network structure determines learners' growth patterns.
-Part of the findings largely replicates the results obtained in @hills2009, i.e., semantic networks (based on free associations) grow by preferential acquisition, not by preferential attachment.
-A novel finding was that phonological networks also grow primarily by preferential acquisition, especially when both scenarios (PAT and PAC) were pitted against each other in the same model.
+One scenario, PAT, described a rich-get-richer network growth model in which the structure of the learner's internal network determines future growth; the other, PAC, described a model in which the external, global environmental network structure determines learners' growth patterns.
+Our findings largely replicate the results obtained by @hills2009: Semantic networks grow by preferential acquisition, not by preferential attachment.
+A novel finding is that phonological networks also grow primarily by preferential acquisition.
+Moreover, both semantic and phonological connectivity in the learning environment predict growth.
 These findings generalize well across languages.
-Moreover, both semantic and phonological connectivity in the learning environment (i.e., PAC) predict growth in a consistent way across many languages.
-Nevertheless, when pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting learning in some languages, but not in others.
-Despite this cross-linguistic variation, both phonological and semantic connectivity contribute to the overall learning (when data is pooled across languages).
+When pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting learning in some languages, but not in others.
+Nevertheless, this cross-linguistic variability is to be taken with a grain of salt as it might be exaggerated in our study by the limited and partially-overlapping sample of nouns for each language.
+In fact, both phonological and semantic connectivity are significant predictors when data are pooled across languages.
 
@@
 
-One important result of the study is that children start by learning words that have high phonological and semantic similarity to a variety of other words in the learning environment, not in the child's available lexicon.
-This suggests that children are sensitive to connectivity even without having first acquired the connected words.
+Children start by learning words that have high semantic and phonological similarity to a variety of other words in the learning environment, not in the child's available lexicon.
+This result suggests that children are sensitive to connectivity even without having first acquired the connected words.
 How can children indirectly detect highly connected words, and why would such words be more readily learned?
 
-In the semantic case, free association can be predicted through the patterns of word co-occurrence [@griffiths07], meaning that highly connected words tend to be the words that co-occur with many other words in various contexts.
-One possibility, suggested by @hills2010, is that the referents of such words are more easily disambiguated from other potential referents because their presence in multiple contexts provides more cross-situational, disambiguating statistics about their true referents [@smith2008].
+In the semantic case, the networks are based on free association norms.
+These associations can be derived from the patterns of word-word co-occurrence [e.g., @griffiths07], i.e., two words are associated if they co-occur in many different contexts.
+In a network structure, highly connected words would be the words that co-occur with many other words in various contexts.
+Why would such words be easier to learn?
+One possibility, suggested by @hills2010, is that the referents of these words are more easily disambiguated from other potential referents because their presence in multiple contexts provides more cross-situational, disambiguating statistics about their true referents [@smith2008].
 
@@
 That is, highly connected words tend to be made of frequent sound sequences.
-Even infants (whose vocabulary is still very rudimentary) show a sensitivity for high frequency sound sequences in the ambient language [@jusczyk1994].
+Even infants show a sensitivity for high frequency sound sequences in the ambient language [@jusczyk1994].
 Moreover, phonotactic probability facilitates learning and recognition [e.g., @storkel2001].

### 2018-02-01 cogsci/cogsci.tex
final modif on cogsci

@@
 lexicon attract similar words. Another view suggests that learning is
-driven by highly connected word in the external learning environment
+driven by highly connected words in the external learning environment
 instead of highly connected words in the early internal lexicon. The
 present study tests both scenarios systematically in both the
-phonological and the semantic domains, and across 8 languages. We show
-that external connectivity in the learning environment drives growth in
-both the semantic and the phonological networks, and that this pattern
-is consistent cross-linguistically. The findings suggest a word learning
+phonological and semantic domains, and across 8 languages. We show that
+external connectivity in the learning environment drives growth in both
+the semantic and the phonological networks, and that this pattern is
+consistent cross-linguistically. The findings suggest a word learning
 mechanism where children harness their statistical learning abilities to
@@
 multiple research strategies, from conducting controlled laboratory
-experiments (e.g. Markman, 1990) to analysing dense corpora capturing
+experiments (e.g. Markman, 1990) to analyzing dense corpora capturing
 language learning in context (e.g., B. C. Roy, Frank, DeCamp, Miller, \&
@@
 between two nodes represents a relationship between the corresponding
-pair of words. Previous studies investigated early vocabulary networks
-based on different word relations such as shared semantic features,
-target-cue relationships in free association norms, co-occurrence in
-child directed speech, and phonological similarity. These studies have
-found that children tend to produce earlier the words that have higher
-neighborhood density (i.e., high connectivity in the network) both at
-the phonological and the semantic level (Engelthaler \& Hills, 2017;
-Hills, Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya,
-\& Smith, 2009; Stella, Beckage, \& Brede, 2017; Storkel, 2009).
+pair of words. Previous studies have investigated early vocabulary
+structure by constructing networks using a variety of word-word
+relations including shared semantic features, target-cue relationships
+in free association norms, co-occurrence in child directed speech, and
+phonological similarity. These studies have found that children tend to
+produce words that have higher neighborhood density (i.e., high
+connectivity in the network) earlier, both at the phonological and the
+semantic level (Engelthaler \& Hills, 2017; Hills, Maouene, Riordan, \&
+Smith, 2010; Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Stella,
+Beckage, \& Brede, 2017; Storkel, 2009).
 
-While most studies focused on the static properties of the lexical
+While most studies have focused on the static properties of the lexical
 network, a few have investigated the underlying developmental process.
-Steyvers \& Tenenbaum (2005) suggested that the effect of connectivity
-is the consequence of how the lexical network gets constructed in the
-child's mind. According to this explanation, known as Preferential
-Attachment (PAT), highly connected words in the child's lexicon tend to
-``attract'' more words over time, in a rich-get-richer scenario
-(Barabasi \& Albert, 1999). In other words, what predicts word learning
-is the \emph{internal} connectivity in the child's early lexicon. In
-contrast, Hills et al. (2009) suggested that what biases the learning is
-not the connectivity in the child's internal lexicon but, rather,
-\emph{external} connectivity in the learning environment. They called
-this alternative explanation Preferential Acquisition (PAC). Figure
-\ref{fig:growth} shows an illustration of both growth scenarios with the
-same simplified network. These two proposals represent two divergent
-ideas about the role of lexical networks in acquisition. On the PAT
-proposal, network structure is a causal factor in early word learning;
-in contrast, on the PAC approach, network structure is not internally
-represented and, therefore, might be an epiphenomenon of the statistics
-of the linguistic input (see discussion).
+In particular, Steyvers \& Tenenbaum (2005) suggested that the observed
+effects of connectivity are the consequence of how the lexical network
+gets constructed in the child's mind. According to this explanation,
+known as Preferential Attachment (PAT), highly connected words in the
+child's lexicon tend to ``attract'' more words over time, in a
+rich-get-richer scenario (Barabasi \& Albert, 1999). In other words,
+what predicts word learning is the \emph{internal} connectivity in the
+child's early lexicon. In contrast, Hills et al. (2009) suggested that
+what biases the learning is not the connectivity in the child's internal
+lexicon but, rather, \emph{external} connectivity in the learning
+environment. They called this alternative explanation Preferential
+Acquisition (PAC). Figure \ref{fig:growth} shows an illustration of both
+growth scenarios with the same simplified network. These two proposals
+represent two divergent ideas about the role of lexical networks in
+acquisition. On the PAT proposal, network structure is a causal factor
+in early word learning; in contrast, on the PAC approach, network
+structure is not internally represented and, therefore, might be an
+epiphenomenon of the statistics of the linguistic input.
 
@@
 network-based models of acquisition (Fenson et al., 1994). We used the
-\emph{Words and Sentence} version of the CDI which contains the
+\emph{Words and Sentences} version of the CDI which contains the
 productive vocabulary of toddlers (age varied between 16 to 36 months).
 Following previous studies (Hills et al., 2009; Storkel, 2009), we
-restricted our analysis to the category of nouns. We defined the age of
-acquisition of a given word by the month at which this word was produced
-by at least 50\% of children (J. C. Goodman et al., 2008). We excluded
-nouns that have not been learned (according to this criterion) by the
-last month for which we have CDI data.
+restricted our analysis to nouns. We defined the age of acquisition of a
+given word by the month at which this word was produced by at least 50\%
+of children (J. C. Goodman et al., 2008), and we excluded nouns that
+have not been learned (according to this criterion) by the last month
+for which we have CDI data.
 
@@
 
-We constructed the semantic networks following the procedure outlined in
+We constructed semantic networks following the procedure outlined in
 Hills et al. (2009). We used as an index of semantic relatedness the
@@
 for which the word was the target. To model growth from month to month,
-we constructed a different network at each month, made of the words that
-have been acquired at that month.
+we constructed a different network at each month, based on the words
+that have been acquired by that month.
 
@@
 of 1 (e.g., Storkel, 2009). However, in these previous studies the
-network was built using an adult vocabulary. However, since the
-children's vocabulary contains very few word pairs with an edit distance
-of 1, the resulting networks were too sparse and uninformative. Thus, we
-increased the threshold from 1 to 2, that is, two nodes were related if
-their edit distance was equal to 1 or 2. The connectivity of a given
-node was characterized with its \emph{degree}: the number of links it
-shares with other words.
+network was built using an adult vocabulary. In the current study,
+however, network growth models are based on the children's early
+vocabulary which contains very few word pairs with an edit distance of
+1. When using this threshold, the resulting networks were too sparse and
+uninformative. Thus, we increased the threshold from 1 to 2, that is,
+two nodes were related if their edit distance was equal to 1 or 2. The
+connectivity of a given node was characterized with its \emph{degree}:
+the number of links it shares with other words.
 
@@
 
-We start by analysing word connectivity in the global (static) network.
-We constructed this network using nouns at the oldest age for which we
-have CDI data (e.g., in English this corresponds to the network by 30
-months). This global network is the end-state towards which both PAT and
-PAC should converge by the last month of learning. Moreover, following
-Hills et al. (2009), we used this end-state network as a proxy for the
-external connectivity in the learning environment. Below we analyse
-properties of this global networks that are relevant to PAT and/or PAC.
+We start by analyzing word connectivity in the global (static) network.
+We constructed this network using nouns learned by the oldest age for
+which we have CDI data (e.g., in English this corresponds to the network
+by 30 months). This global network is the end-state towards which both
+PAT and PAC should converge by the last month of learning. Moreover,
+following Hills et al. (2009), we used this end-state network as a proxy
+for the external connectivity in the learning environment. Below we
+analyze properties of this global networks that are relevant to PAC
+and/or PAT.
 
@@
 connectivity in the global network and the age of
-acquisition.\footnote{Note that this correlation is also compatible with PAT, even if this growth scenario does not rely explicitly on external connectivity.
-Indeed, from a PAT perspective, higher connectivity in the global network is caused by earlier learning, i.e., some words end up being highly connected in the global network precisely because they happen to be acquired earlier (and therefore have a higher chance of forming more links over time).}
+acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed.
+Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around.
+Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.}
 Figure \ref{fig:data_all} shows how the age of acquisition for each word
@@
 
-We also analysed the global network's degree distribution. This property
-is particularly relevant to PAT as this growth scenario is known to
-generate networks with a power-law degree distribution (i.e., a
-distribution of the form \(p(k) \propto \frac{1}{k^{\alpha}}\), Barabasi
-\& Albert, 1999). If the network displays this property, this fact would
-suggests a PAT-like generative process. Conversely, if the degree
-distribution does not follow a power law, this fact would weaken the
-case for PAT. The log-log plots are shown in Figure
-\ref{fig:degree_distribution}. We fit a discrete power law to each
-empirical degree distribution following the procedure outlined in
-Clauset, Shalizi, \& Newman (2009) and using the related R package
-(poweRlaw, Gillespie, 2015). In brief, the analysis consists in two
-steps. First, we derive the optimal cut-off, \(k_{min}\), above which
-the distribution is more likely to follow a power
-law\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.},
+We also analyzed the global network's degree distribution. The shape of
+this distribution is particularly relevant to PAT as this growth
+scenario is known to generate networks with a power-law degree
+distribution (i.e., a distribution of the form
+\(p(k) \propto \frac{1}{k^{\alpha}}\), Barabasi \& Albert, 1999). If the
+network displays this property, this fact would suggest a PAT-like
+generative process. Conversely, if the degree distribution does not
+follow a power law, this fact would weaken the case for PAT. The log-log
+plots are shown in Figure \ref{fig:degree_distribution}. We fit a power
+law to each empirical degree distribution following the procedure
+outlined in Clauset, Shalizi, \& Newman (2009) and using the related R
+package (poweRlaw, Gillespie, 2015). In brief, the analysis consisted in
+two steps. First, we derived the optimal cut-off, \(k_{min}\), above
+which the distribution is more likely to follow a power
+law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}
 and we estimate the corresponding scaling parameter \(\alpha\). Second
-we calculate the goodness-to-fit, which results in a \(p\)-value
-quantifying the plausibility of the model. Overall, we did not find
-strong evidence against a power-law distribution: the \(p\)-value was
+we calculated the goodness-to-fit, which resulted in a \(p\)-value
+quantifying the plausibility of the model. Overall, we could not reject
+the null hypothesis of a power-law distribution: the \(p\)-value was
 generally above 0.1, except for the Italian phonological network where
-we obtained \(p < 0.05\) (suggesting that the power law can be ruled out
-in this particular case).
+we obtained \(p < 0.05\), suggesting that the power law can be ruled out
+in this particular case.
 
-In sum, the static properties of the global network do not provide
-conclusive evidence in favor or against any of the growth scenarios in
-question. For a more direct test of the developmental process, we need
-to fit explicit growth models to the data.
+In sum, the static properties of the global network are \emph{a priori}
+compatible with both PAT and PAC. In order to decide between these two
+developmental scenarios, we need to fit explicit growth models to the
+data.
 
@@
 inference was performed using the probabilistic programming language
-WebPPL (N. Goodman \& Stuhlmüller, 2014). We defined a uniform prior
+WebPPL (N. Goodman \& Stuhlmuller, 2014). We defined a uniform prior
 over \(\beta\), and at each month, we computed the likelihood function
@@
 
-Besides fitting a growth model to the data, we conducted a separate
-evaluation. This second evaluation consists in determining, in each
-month, the growth value distribution of all words that could possibly be
-learned at this month, and then computing the z-score of each learned
-word with respect to this distribution. For each growth scenario, we
-tested if the distribution constituted by the z-scores of all learned
-words was different from zero, using a one-sample t-test.
-
-The results from both evaluations were very similar and lead essentially
-to the same
-conclusions.\footnote{we do not show here the results of the second evaluation because they were redundant with the results of the first evaluation}
 For the semantic networks, the results replicate Hills et al.'s finding
-in English, which was that the semantic network grows by PAC, not by
-PAT. Moreover, this finding held in seven of the eight languages we
-examined. The PAC model also fit better than PAT for phonological
-networks. We note however that PAT, though weaker, fares better for the
-phonological networks (where it predicts part of the growth process in
-some languages such as Croatian, English, Norwegian and Russian) than it
-does for the semantic networks (where it is rather universally
-unpredictive).
+in English, which is that the semantic network grows by PAC, not by PAT.
+Moreover, this finding holds in seven of the eight languages we
+examined.\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
+However, our findings do not support this assumption as the effects were generally similar in magnitude cross-linguistically.}
+The PAC model also fits better than PAT for phonological networks. We
+note however that PAT, though weaker, fares better for the phonological
+networks (where it predicts part of the growth process in some languages
+such as Croatian, English, Norwegian and Russian) than it does for the
+semantic networks (where it is rather universally unpredictive).
 
@@
 Above we evaluated the network growth scenarios individually. As a next
-step, we analysed their relative contribution to the learning process.
+step, we analyzed their relative contribution to the learning process.
 This was done through adding more fitted parameters to the model, that
@@
 
-\subsection{Comparison to other known predictors of age of
-acquisition}\label{comparison-to-other-known-predictors-of-age-of-acquisition}
+\subsection{Comparison to other predictors of age of
+acquisition}\label{comparison-to-other-predictors-of-age-of-acquisition}
 
@@
 growth
-month-by-month.\footnote{This was a requirement only for PAT whose utilities varied from month to month, depending on previously learned words.}
+month-by-month.\footnote{This was a requirement only for PAT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.}
 A more direct way to assess and compare the contribution of PAC in
@@
 unigram counts were derived based on CHILDES corpora in each
-language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children}
+language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.}
 For each word, counts included words that shared the same stem (e.g.,
-cats counts as cat), or words that were synonymous (e.g.~father counts
-as daddy). For word length, we used our generated IPA transcription.
+``cats'' counts as ``cat''), or words that were synonymous (e.g.
+``father'' counts as ``daddy''). For word length, we counted the number
+of phonemes in our generated IPA transcription.
 
@@
 However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates.
-Another important difference is the number of words tested: our study uses a larger set of nouns.}
-Despite this cross-linguistic variation, both phonological and semantic
-connectivity remain significant predictors in the global model.
+Another important difference is the number of words tested: Our study uses a larger set of nouns.}
+Despite these cross-linguistic differences, both phonological and
+semantic connectivity are significant predictors in the combined model.
 
@@
 contributions across eight languages. One scenario, PAT, described a
-``rich get richer'' network growth model in which the structure of the
+rich-get-richer network growth model in which the structure of the
 learner's internal network determines future growth; the other, PAC,
 described a model in which the external, global environmental network
-structure determines learners' growth patterns. Part of the findings
-largely replicates the results obtained in Hills et al. (2009), i.e.,
-semantic networks (based on free associations) grow by preferential
-acquisition, not by preferential attachment. A novel finding was that
-phonological networks also grow primarily by preferential acquisition,
-especially when both scenarios (PAT and PAC) were pitted against each
-other in the same model. These findings generalize well across
-languages. Moreover, both semantic and phonological connectivity in the
-learning environment (i.e., PAC) predict growth in a consistent way
-across many languages. Nevertheless, when pitted against other known
+structure determines learners' growth patterns. Our findings largely
+replicate the results obtained by Hills et al. (2009): Semantic networks
+grow by preferential acquisition, not by preferential attachment. A
+novel finding is that phonological networks also grow primarily by
+preferential acquisition. Moreover, both semantic and phonological
+connectivity in the learning environment predict growth. These findings
+generalize well across languages. When pitted against other known
 predictors of age of acquisition (word frequency and length), the effect
 of word connectivity shows a cross-linguistic variation, predicting
-learning in some languages, but not in others. Despite this
-cross-linguistic variation, both phonological and semantic connectivity
-contribute to the overall learning (when data is pooled across
-languages).
+learning in some languages, but not in others. Nevertheless, this
+cross-linguistic variability is to be taken with a grain of salt as it
+might be exaggerated in our study by the limited and
+partially-overlapping sample of nouns for each language. In fact, both
+phonological and semantic connectivity are significant predictors when
+data are pooled across languages.
 
@@
 
-One important result of the study is that children start by learning
-words that have high phonological and semantic similarity to a variety
-of other words in the learning environment, not in the child's available
-lexicon. This suggests that children are sensitive to connectivity even
-without having first acquired the connected words. How can children
-indirectly detect highly connected words, and why would such words be
-more readily learned?
+Children start by learning words that have high semantic and
+phonological similarity to a variety of other words in the learning
+environment, not in the child's available lexicon. This result suggests
+that children are sensitive to connectivity even without having first
+acquired the connected words. How can children indirectly detect highly
+connected words, and why would such words be more readily learned?
 
-In the semantic case, free association can be predicted through the
-patterns of word co-occurrence (Griffiths, Steyvers, \& Tenenbaum,
-2007), meaning that highly connected words tend to be the words that
-co-occur with many other words in various contexts. One possibility,
-suggested by Hills et al. (2010), is that the referents of such words
-are more easily disambiguated from other potential referents because
-their presence in multiple contexts provides more cross-situational,
-disambiguating statistics about their true referents (Smith \& Yu,
-2008).
+In the semantic case, the networks are based on free association norms.
+These associations can be derived from the patterns of word-word
+co-occurrence (e.g., Griffiths, Steyvers, \& Tenenbaum, 2007), i.e., two
+words are associated if they co-occur in many different contexts. In a
+network structure, highly connected words would be the words that
+co-occur with many other words in various contexts. Why would such words
+be easier to learn? One possibility, suggested by Hills et al. (2010),
+is that the referents of these words are more easily disambiguated from
+other potential referents because their presence in multiple contexts
+provides more cross-situational, disambiguating statistics about their
+true referents (Smith \& Yu, 2008).
 
@@
 is, highly connected words tend to be made of frequent sound sequences.
-Even infants (whose vocabulary is still very rudimentary) show a
-sensitivity for high frequency sound sequences in the ambient language
-(Jusczyk, Luce, \& Charles-Luce, 1994). Moreover, phonotactic
-probability facilitates learning and recognition (e.g., Storkel, 2001).
-In other words, children's sensitivity to local phonotactic regularities
-might lead them to learn higher-probability words more easily. This
-learning effect, in turn, would lead to an observed pattern of growth
-that would appear to follow the PAC growth model even though learners
-themselves would only be tracking local statistics.
+Even infants show a sensitivity for high frequency sound sequences in
+the ambient language (Jusczyk, Luce, \& Charles-Luce, 1994). Moreover,
+phonotactic probability facilitates learning and recognition (e.g.,
+Storkel, 2001). In other words, children's sensitivity to local
+phonotactic regularities might lead them to learn higher-probability
+words more easily. This learning effect, in turn, would lead to an
+observed pattern of growth that would appear to follow the PAC growth
+model even though learners themselves would only be tracking local
+statistics.
 
@@
 \hypertarget{ref-dippl}{}
-Goodman, N., \& Stuhlmüller, A. (2014). The Design and Implementation of
+Goodman, N., \& Stuhlmuller, A. (2014). The Design and Implementation of
 Probabilistic Programming Languages. \url{http://dippl.org}.
@@
 Academy of Sciences}, \emph{112}(41), 12663--12668.
-\url{http://doi.org/10.1073/pnas.1419773112}
 

### 2018-07-06 cogsci/cogsci.Rmd
journal version

@@
 In the semantic case, the networks are based on free association norms.
-These associations can be derived from the patterns of word-word co-occurrence [e.g., @griffiths07], i.e., two words are associated if they co-occur in many different contexts.
+These associations can be (partly) derived from the patterns of word-word co-occurrence [e.g., @griffiths07], i.e., two words are associated if they co-occur in many different contexts.
 In a network structure, highly connected words would be the words that co-occur with many other words in various contexts.

### 2018-07-06 cogsci/cogsci.tex
journal version

@@
 In the semantic case, the networks are based on free association norms.
-These associations can be derived from the patterns of word-word
-co-occurrence (e.g., Griffiths, Steyvers, \& Tenenbaum, 2007), i.e., two
-words are associated if they co-occur in many different contexts. In a
-network structure, highly connected words would be the words that
-co-occur with many other words in various contexts. Why would such words
-be easier to learn? One possibility, suggested by Hills et al. (2010),
-is that the referents of these words are more easily disambiguated from
-other potential referents because their presence in multiple contexts
-provides more cross-situational, disambiguating statistics about their
-true referents (Smith \& Yu, 2008).
+These associations can be (partly) derived from the patterns of
+word-word co-occurrence (e.g., Griffiths, Steyvers, \& Tenenbaum, 2007),
+i.e., two words are associated if they co-occur in many different
+contexts. In a network structure, highly connected words would be the
+words that co-occur with many other words in various contexts. Why would
+such words be easier to learn? One possibility, suggested by Hills et
+al. (2010), is that the referents of these words are more easily
+disambiguated from other potential referents because their presence in
+multiple contexts provides more cross-situational, disambiguating
+statistics about their true referents (Smith \& Yu, 2008).
 

### 2018-07-06 journal/ms.Rmd
journal version

--- 2018-07-06 cogsci/cogsci.Rmd
@@
 ---
-title: "Word Learning as Network Growth: A Cross-linguistic Analysis"
+title             : "Word Learning as Network Growth: A Cross-linguistic Analysis"
+shorttitle        : "Word Learning as Network Growth"
+#numbersections: true
 
-bibliography: library.bib
-csl: apa6.csl
-document-params: "10pt, letterpaper"
+author: 
+  - name          : "Abdellah Fourtassi"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Postal address"
+    email         : "afourtas@stanford.edu"
 
-header-includes:
-   - \usepackage[subtle]{savetrees}
+  - name          : "Yuan Bian"
+    affiliation   : "2"
+    email         : "ybian.uiuc@gmail.com"
 
-author-information: > 
-    \author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University
-    \And {\large \bf Yuan Bian} \\ \texttt{ybian.uiuc@gmail.com} \\ Department of Psychology \\ University of Illinois
-    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
+  - name          : "Michael C. Frank"
+    affiliation   : "1"
+    email         : "mcfrank@stanford.edu"
 
-abstract:
+affiliation:
+  - id            : "1"
+    institution   : "Department of Psychology, Stanford University"
 
-    "Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions.
+  - id            : "2"
+    institution   : "Department of Psychology, University of Illinois"
+
+author_note: |
+
+  Abdellah Fourtassi
+
+  Department of Psychology
+
+  Stanford University
+
+  50 Serra Mall
+
+  Jordan Hall, Building 420
+
+  Stanford, CA 94301
+
+abstract: |
+
+ Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions.
 Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.
@@
 We show that external connectivity in the learning environment drives growth in both the semantic and the phonological networks, and that this pattern is consistent cross-linguistically.
-The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment."
+The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment.
 
-keywords:
-    "semantic network, phonological network, network growth, mechanism of word learning"
+keywords          : "Language understanding; audio-visual processing; word learning; speech perception; computational modeling."
 
-output: cogsci2016::cogsci_paper
+header-includes:
+   #- \usepackage{bibentry}
+   - \usepackage[sortcites=false,sorting=none]{biblatex}
+
+bibliography      : ["references.bib"]
+
+figsintext        : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+lineno            : yes
+
+lang              : "english"
+class             : "man"
+output            : papaja::apa6_pdf
+
+citation_package: biblatex
+
 ---
 
-```{r global_options, include=FALSE}
-rm(list=ls())
-
-#knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
-#                      echo=F, warning=F, cache=F, message=F, sanitize = T)
-
-knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=F, message=F, sanitize = T)
-
+```{r}
+knitr::opts_chunk$set(echo=F, warning=F, cache=F, message=F, sanitize = T)
 ```
 
-```{r, libraries}
-library(png)
-library(grid)
+```{r load_packages, include = FALSE}
+library(papaja)
+library(readr)
+library(tidyr)
 library(ggplot2)
+library(cowplot)
+library(knitr)
+library(boot)
+library(dplyr)
+library(langcog)
 library(ggthemes)
-library(xtable)
-options(xtable.comment = FALSE)
-library(purrr)
-library(readr)
-library(ggplot2)
-library(langcog)
-library(boot)
-#library(lazyeval)
-library(dplyr)
-library(tidyr)
-library(wordbankr)
-library(directlabels)
-#library(scales)
-library(stringr)
-library(lmtest)
-library(rwebppl)
-library(jsonlite)
-library(nlme)
-library(feather)
 library(broom)
 library(HDInterval)
-library(BBmisc)
+#library("knitcitations")
+#cleanbib()
+#options("citation_format" = "pandoc")
 ```
 
-# Introduction
+#Introduction
 
@@
 They called this alternative explanation Preferential Acquisition (PAC).
-Figure \ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network.
+Figure\ \@ref(fig:growth) shows an illustration of both growth scenarios with the same simplified network.
 These two proposals represent two divergent ideas about the role of lexical networks in acquisition.
@@
 
-```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Illustration of the growth scenarios.
+```{r growth, fig.cap = "Illustration of the growth scenarios.
 Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
@@
 For PAC, the utility of a candidate node is its degree in the entire network.
-According to PAC, the node E2 is more likely to enter the lexicon first."}
-
-img <- png::readPNG("figs/growth2.png")
-grid::grid.raster(img)
-
+According to PAC, the node E2 is more likely to enter the lexicon first.", fig.align = "center", out.width = "400px"}
+knitr::include_graphics("figs/growth2.png")
 ```
@@
 Third, it tests the generality of the findings across eight languages.
-
-```{r }
-
-#Import data from saved
-data_all_scaled <- feather::read_feather("../saved_data/data_all_scaled.feather")
-
-#tidy data
-data_long <- data_all_scaled %>%
-  gather(predictor, value, length:freq_mika)
-
-data_long <- data_long %>%
-  #filter(predictor %in% c("PAC_assoc", "PAC_phono_t2", "freq_mika", "length")) %>%
-  filter(predictor %in% c("PAC_assoc", "PAC_phono_t2"))
-
-data_long$predictor <- mapValues(data_long$predictor, 
-                                 from = c("PAC_assoc", "PAC_phono_t2"), 
-                                 to = c("Sem.", "Phono."))
-
-#Compute the correlations 
-correlations <-  data_long %>%
-  group_by(language, predictor) %>%
-  dplyr::summarise(cor = round(cor(AoA, value), 2))
-
-plot_data_all <- ggplot(data_long, aes(x=value, y=AoA))+
-  facet_grid(predictor ~ language)+#, scales = "free") +
-  geom_jitter(#aes(colour = lexical_class),
-    colour = solarized_palette(1),
-    size = 0.5, alpha = 0.5) +
-  geom_abline(slope = -1)+
-  coord_cartesian(xlim=c(-1,5))+
-  #scale_x_continuous(limits=c(-2,5))+
-  scale_y_continuous(breaks =c(15,25,35))+
-  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
-  scale_colour_solarized(name = "") +
-  theme_few()+
-  #theme_bw()+
-  theme(aspect.ratio = 0.7, 
-        plot.margin=grid::unit(c(0,0,0,0), "mm")
-        )+
-  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
-  xlab("degree z-score") +ylab("AoA")
-
-ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)
-
-```
-
-```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
-Results are shown in each language for phonological and semantic networks.
-Each point is a word, with lines indicating linear model fits."}
-plot_data_all
-#img <- png::readPNG("figs/data_all.png")
-#grid::grid.raster(img)
-
-```
-
-```{r }
-
-#Import data from saved
-degreeDist <- feather::read_feather("../saved_data/degreeDist.feather") %>%
-  dplyr::rename(Dimension = dimension)
-
-plot_dist <- ggplot(data = degreeDist,  aes(x=x, y=y, col=Dimension))+
-  facet_grid(. ~ language)+
-  geom_point(size = 0.5, alpha = 0.5) +
-  scale_y_log10() + scale_x_log10() +
-  theme_few()+
-  theme(aspect.ratio = 0.7,  text = element_text(size=9))+
-  xlab("degree") +ylab("probability")
-
-ggsave("figs/degreeDist.png", plot = plot_dist, width = 7, height = 3)
-
-```
-
-```{r degree_distribution, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
-A perfect power-law distribution should appear as a straight line in this graph."}
-plot_dist
-#img <- png::readPNG("figs/data_all.png")
-#grid::grid.raster(img)
-
-```
 
@@
 Since these norms are available only in English, we used the hand-checked translation equivalents provided by @braginsky2016, allowing us to use the English association norms across languages.
-Table \ref{tab:stats} gives an overview of the data used.
+Table \@ref(tab:stats) gives an overview of the data used.
 Translation equivalents were originally constructed for a subset of words appearing on the toddler CDI form, and so not all words are currently available.
@@
 
-## Semantic networks
+# Semantic networks
 
@@
 
-<!--## Network growth
-
-We tested two network growth scenarios discussed in @hills2009.
-The first one was *Preferential Attachment* (PAT).
-According to this mechanism, the network structure of known words predicts what words will be learned next.
-A word is more likely to be learned if it is linked to one of the highly connected nodes in this internal network.
-The second mechanism was *Preferential Acquisition* (PAC).
-In this model, what predicts what word will enter the lexicon is not connectivity in the internal network, but connectivity in the learning environment.
-Figure \ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network.
-For PAT, each candidate node was characterized with the average degree of the existing nodes that it would attach to.
-Thus, according to PAT, the node N1 is more likely to enter the lexicon first.
-For PAC, each candidate node was characterized with its degree in the entire network.
-According th PAC, the node N3 is more likely to enter the lexicon first.
-
--->
-
 # Analysis
@@
 
+```{r}
+#Import data from saved
+data_all <- feather::read_feather("../saved_data/data_static_scaled.feather")
+
+data_long <- data_all %>%
+  rename(Sem = sem_deg, Phono=phono_deg) %>%
+  gather(predictor, value, Sem:frequency) %>%
+  filter(predictor == "Sem" | predictor == "Phono")
+
+correlations <- data_long %>%
+  group_by(measure, language, predictor) %>%
+  summarise(cor = round(cor(aoa, value), 2))
+
+plot_correlation_prod <- ggplot(subset(data_long, measure == "produces"), aes(x=value, y=aoa))+
+  facet_grid(predictor ~ language)+#, scales = "free") +
+  geom_jitter(#aes(colour = lexical_class),
+    colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  geom_abline(slope = -1)+
+  coord_cartesian(xlim=c(-1,5))+
+  #scale_x_continuous(limits=c(-2,5))+
+  scale_y_continuous(breaks =c(15,25,35))+
+  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
+  scale_colour_solarized(name = "") +
+  theme_few()+
+  #theme_bw()+
+  theme(aspect.ratio = 0.7, 
+        plot.margin=grid::unit(c(0,0,0,0), "mm")
+        )+
+  geom_text(data=subset(correlations, measure=="produces"), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
+  xlab("degree z-score") +ylab("Age")
+
+plot_correlation_comp <- ggplot(subset(data_long, measure == "understands"), aes(x=value, y=aoa))+
+  facet_grid(predictor ~ language)+#, scales = "free") +
+  geom_jitter(#aes(colour = lexical_class),
+    colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  geom_abline(slope = -1)+
+  coord_cartesian(xlim=c(-1,5))+
+  #scale_x_continuous(limits=c(-2,5))+
+  scale_y_continuous(breaks =c(15,25,35))+
+  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
+  scale_colour_solarized(name = "") +
+  theme_few()+
+  #theme_bw()+
+  theme(aspect.ratio = 0.7, 
+        plot.margin=grid::unit(c(0,0,0,0), "mm")
+        )+
+  geom_text(data=subset(correlations, measure=="understands"), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
+  xlab("degree z-score") +ylab("Age")
+
+#ggsave("figs/plot_correlation_prod.pdf", plot = plot_correlation_prod, width = 10, height = 3)
+#ggsave("figs/plot_correlation_comp.pdf", plot = plot_correlation_comp, width = 10, height = 3)
+```
+
+```{r corrAll, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Age of production (A) and comprehension (B) in the global network as predicted by the degree in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits."}
+
+plot_grid(plot_correlation_prod , NULL, plot_correlation_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+```
+
 ###Connectivity predicts the age of acquisition
 
-Connectivity in the global network is directly related to PAC as it represents the explicit criterion PAC uses to determine what words should be learned first (Figure \ref{fig:growth}).
+Connectivity in the global network is directly related to PAC as it represents the explicit criterion PAC uses to determine what words should be learned first (Figure \@ref(fig:growth)).
 Therefore, a direct consequence of a PAC-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed.
 Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around.
-Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network).
+Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \@ref(fig:corrAll) shows how the age of production (A) and comprehension (B) for each word varies as a function of its degree (or indegree for the semantic network).
 For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages.
 The plots show, overall, a negative correlation between the month of acquisition and the degree, indicating that nouns with higher degrees are generally learned earlier.
+
+```{r}
+
+degree_dist <- feather::read_feather("../saved_data/degree_dist.feather") %>%
+  mutate(data=ifelse(measure=='produces', 'Prod.', 'Comp.'))
+
+plot_degree <- ggplot(data = degree_dist,  aes(x=x, y=y, col=dimension))+
+  facet_grid(data ~ language)+#, scales = "free") +
+  geom_point(#aes(colour = lexical_class),
+    #colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  scale_y_log10() + scale_x_log10() +
+  theme(aspect.ratio = 1) +
+  theme_few()+
+  theme(aspect.ratio = 0.7)+
+  xlab("Degree") +ylab("Prob.")
+
+ggsave("figs/plot_degree.pdf", plot = plot_degree, width = 10, height = 3)
+```
+
+```{r degreeDist, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
+The figure shows the results for both production and comprehension data.
+A perfect power-law distribution should appear as a straight line in this graph."}
+
+knitr::include_graphics("figs/plot_degree.pdf")
+
+```
 
@@
 Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for PAT.
-The log-log plots are shown in Figure \ref{fig:degree_distribution}.
+The log-log plots are shown in Figure \@ref(fig:degreeDist).
 We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using the related R package [poweRlaw, @gillespie15].
@@
 Second we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model.
-Overall, we could not reject the null hypothesis of a power-law distribution: the $p$-value was generally above 0.1, except for the Italian phonological network where we obtained  $p < 0.05$, suggesting that the power law can be ruled out in this particular case.
+The results are shown in Appendix 1, table XX.
+Overall, we could not reject the null hypothesis of a power-law distribution: the $p$-value was generally above 0.1.
 
@@
 In order to decide between these two developmental scenarios, we need to fit explicit growth models to the data.
-<!--
-```{r }
 
-#Import data from saved
-post_combined <- feather::read_feather("../saved_data/combined_net.feather")
+```{r}
 
-pred_comb <- ggplot(post_combined, aes(x = model, y = mean)) +
-  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, y = mean, col = model), size=0.3)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  coord_flip() +
-  facet_wrap(~language, ncol=4)  +
-  guides(colour=FALSE)+
-  scale_colour_solarized() +
-  theme_bw()+
-  theme(aspect.ratio = 0.7)
+growth_preds <- feather::read_feather("../saved_data/growth_preds.feather")
 
-ggsave("figs/pred_comb.png", plot = pred_comb, width = 8, height = 4)
-```
-
-```{r pred_comb_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:pred_comb_img}Estimates of the growth models' parameters in each language.
-Dots represent the means of the posteriori distribution of the parameters, and ranges represent 95\\% credible intervals (computed using the highest density intervals).
-"}
-pred_comb
-#img <- png::readPNG("figs/pred_comb.png")
-#grid::grid.raster(img)
-```
--->
-
-```{r }
-
-#Import data from saved
-individual <- feather::read_feather("../saved_data/individual_both.feather") %>%
-  filter(Evaluation =='Fit') %>%
-  select(-Evaluation) %>%
-  mutate(Test = 'Individual')
-
-combined <- feather::read_feather("../saved_data/combined_net.feather") %>%
-  dplyr::rename(lower = hdi_lower,
-                upper = hdi_upper) %>%
-  mutate(Test = 'Combined')
-
-growth_all <- bind_rows(individual, combined)
-
-pred_ind <- ggplot(growth_all, aes(x = model , y = mean)) +
-  geom_pointrange(aes(ymin = lower, ymax = upper, col = model, linetype=Test),
+plot_growth_preds_prod <- ggplot(subset(growth_preds, measure == "produces"), aes(x = model , y = mean)) +
+  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
                   position = position_dodge(width = .5),
@@
   coord_flip() +
-  facet_wrap(~language, ncol=4)  +
+  facet_wrap( ~ language, ncol=5) +
   guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
@@
   theme_few()+
-  theme(aspect.ratio = 0.7, axis.text.x = element_text(size=8))
+  theme(aspect.ratio = 0.7)
 
-ggsave("figs/pred_ind.png", plot = pred_ind, width = 8, height = 4)
+plot_growth_preds_comp <- ggplot(subset(growth_preds, measure == "understands"), aes(x = model , y = mean)) +
+  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  coord_flip() +
+  facet_wrap( ~ language, ncol=5) +
+  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
+  scale_colour_solarized() +
+  theme_few()+
+  theme(aspect.ratio = 0.7)
+
+#ggsave("figs/plot_growth_preds_prod.pdf", plot = plot_growth_preds_prod, width = 10, height = 4)
+#ggsave("figs/plot_growth_preds_comp.pdf", plot = plot_growth_preds_comp, width = 10, height = 4)
 
@@
 
-```{r pred_ind_img, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3.5, fig.align = "center", fig.cap = "\\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid).
+```{r growthPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Evaluation of network growth scenarios, for both A) production and B) comprehension.
+We plot values when predictors are evaluted individually (dotted), and when combined in the same growth model (solid).
 Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\\% credible intervals (computed using the highest density intervals).
@@
 
-pred_ind
+legend <- get_legend(plot_growth_preds_prod)
 
-#img <- png::readPNG("figs/pred_ind.png")
-#grid::grid.raster(img)
+plot_noLegend <- plot_grid(plot_growth_preds_prod + theme(legend.position="none"), NULL, plot_growth_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))
+
+#knitr::include_graphics("figs/plot_growth_preds_prod.pdf")
+
 ```
@@
 \noindent where $\beta$ is a fitted parameter that captures the magnitude of the relationship between network parameters and growth (analogous to a regression coefficient).
-A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first (see Figure \ref{fig:growth} for an illustration of how growth values $d_i$ are defined in each growth scenario).
+A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first (see Figure \@ref(fig:growth) for an illustration of how growth values $d_i$ are defined in each growth scenario).
 The normalization includes all words that could be learned at that month.
@@
 We defined a uniform prior over $\beta$, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using formula 1).
-Markov Chain Monte Carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \ref{fig:pred_ind}.
+Markov Chain Monte Carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \@ref(fig:growthPred).
 
-<!--Besides fitting a growth model to the data, we conducted a separate evaluation.
-This second evaluation consists in determining, in each month, the growth value distribution of all words that could possibly be learned at this month, and then computing the z-score of each learned word with respect to this distribution.
-For each growth scenario, we tested if the distribution constituted by the z-scores of all learned words was different from zero, using a one-sample t-test.-->
-
-<!--The results from both evaluations were very similar and lead essentially to the same conclusions.\footnote{We do not show here the results of the second evaluation because they were redundant with the results of the first evaluation}-->For the semantic networks, the results replicate Hills et al.'s finding in English, which is that the semantic network grows by PAC, not by PAT.
+For the semantic networks, the results replicate Hills et al.'s finding in English, which is that the semantic network grows by PAC, not by PAT.
 Moreover, this finding holds in seven of the eight languages we examined.\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
@@
 We note however that PAT, though weaker, fares  better for the phonological networks (where it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian) than it does for the semantic networks (where it is rather universally unpredictive).
+
+```{r}
+static_preds <- feather::read_feather("../saved_data/static_preds.feather")
+
+plot_static_preds_prod <- ggplot(subset(static_preds, measure =="produces"), aes(x = predictor, y = estimate)) +
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test), 
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  facet_wrap(~language, ncol=5)  +
+  coord_flip() +
+  guides(colour=FALSE)+
+  scale_colour_solarized() +
+  theme_few()+
+  theme(aspect.ratio = 0.7)
+
+plot_static_preds_comp <- ggplot(subset(static_preds, measure =="understands"), aes(x = predictor, y = estimate)) +
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  facet_wrap(~language, ncol=5)  +
+  coord_flip() +
+  guides(colour=FALSE)+
+  scale_colour_solarized() +
+  theme_few()+
+  theme(aspect.ratio = 0.7)
+
+```
+
+```{r staticPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of predictor coefficients by language in production (A) and comprehension (B), with ranges indicating 95\\% confidence intervals.
+Positive values indicate a positive relationship (e.g.
+longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
+words with higher frequency tend to have a lower AoA)."}
+
+legend <- get_legend(plot_static_preds_prod)
+
+plot_noLegend <- plot_grid(plot_static_preds_prod + theme(legend.position="none"), NULL, plot_static_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))
+
+#plot_static_preds_prod
+
+```
 
@@
 
-```{r }
+```{r}
+static_preds_all <- feather::read_feather("../saved_data/static_preds_all.feather")
 
-#Import data from saved
-regressions <- feather::read_feather("../saved_data/regressions_bis.feather")
-
-pred_regressions <- ggplot(regressions, aes(x = predictor, y = estimate)) +
-  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor), size=0.3)+
+plot_static_preds_all <- ggplot(static_preds_all, aes(x = predictor, y = Estimate)) +
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = Estimate, col = predictor, linetype=Test),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
   geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  facet_wrap(~language, ncol=4)  +
+  facet_wrap(~measure)  +
   coord_flip() +
@@
 
-ggsave("figs/pred_regressions.png", plot = pred_regressions, width = 8, height = 4)
+ggsave("figs/plot_static_preds_all.pdf", plot = plot_static_preds_all, width = 6, height = 3)
+
 ```
 
-```{r regressions_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:regressions_img}Estimates of predictor coefficients by language, with ranges indicating 95\\% confidence intervals.
-Positive values indicate a positive relationship (e.g.
-longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
-words with higher frequency tend to have a lower AoA)."}
+```{r staticAll, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect for both production and comprehension.
+Ranges indicate 95\\% confidence intervals.
+Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates."}
 
-pred_regressions
+knitr::include_graphics("figs/plot_static_preds_all.pdf")
 
-#img <- png::readPNG("figs/pred_regressions.png")
-#grid::grid.raster(img)
 ```
@@
 The second factor is word length, which correlates with phonological connectivity.
-<!-- [@pisoni1985].-->
 
@@
 We fit a linear regression for each language, and we fit a linear mixed-effect model to all the data pooled across languages, with language as a random effect.
-Figure \ref{fig:regressions_img} shows the coefficient estimate for each predictor in each language, and Figure \ref{fig:regressions_all_img} shows the coefficient estimates for all languages combined (all predictors were centered and scaled).
+Figure \@ref(fig:staticPred) shows the coefficient estimate for each predictor in each language for production and comprehension data.
+Figure \@ref(fig:staticAll) shows the coefficient estimates for all languages combined (all predictors were centered and scaled).
 The findings were as follows.
@@
 Another important difference is the number of words tested: Our study uses a larger set of nouns.} Despite these cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.
+
+## Does the network's effect change with age?
+
+As a final analysis, we examined  whether the effect of semantic and phnonological networks change over development. @braginsky2016 found that
 
@@
 In fact, both phonological and semantic connectivity are significant predictors when data are pooled across languages.
-
-```{r }
-
-#Import data from saved
-regression_all <- feather::read_feather("../saved_data/regression_all_bis.feather")
-regression_all_noCov <- feather::read_feather("../saved_data/regression_all_bis_noCov.feather")
-
-pred_regression_all <- ggplot(regression_all, aes(x = predictor, y = estimate)) +
-  geom_pointrange(aes(ymin = lower, ymax = upper, col = predictor), size=0.3)+
-  geom_pointrange(data=regression_all_noCov,
-                  aes(ymin = lower, ymax = upper, col = predictor),
-                  position = position_dodge(width = .3),
-                  linetype=1,
-                  size = 0.7,
-                  fatten = 1.5,
-                  alpha = 0.3)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  coord_flip() +
-  guides(colour=FALSE)+
-  scale_colour_solarized() +
-  theme_few()+
-  theme(aspect.ratio = 0.7)
-
-ggsave("figs/pred_regression_all.png", plot = pred_regression_all, width = 4, height = 2)
-```
-
-```{r regressions_all_img, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, fig.cap = "\\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect.
-Ranges indicate 95\\% confidence intervals.
-Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates."}
-
-pred_regression_all
-
-#img <- png::readPNG("figs/pred_regression_all.png")
-#grid::grid.raster(img)
-```
 
@@
 
-\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}} \vspace{1em}
+\vspace{1em} \fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}} \vspace{1em}
 
 # Acknowledgements
+This work was supported by a post-doctoral grant from the Fyssen Foundation.
 
-This work was supported by a post-doctoral grant from the Fyssen Foundation, NSF #1528526, and NSF #1659585.
+# Disclosure statement
+None of the authors have any financial interest or a conflict of interest regarding this work and this submission.
+
+# Appendix 1: Power law model
+
+```{r powerLaw2, results="asis", echo=FALSE}
+
+powerL <- feather::read_feather("../saved_data/degree_test.feather") %>%
+  rename(Kmin = xMin) %>%
+  rename(pValue = pVal)
+
+powerProd <- powerL %>%
+  dplyr::filter(measure == 'produces') %>%
+  select(-measure)
+
+powerComp <- powerL %>%
+  dplyr::filter(measure == 'understands') %>%
+  select(-measure)
+
+#rownames(statistics) <- NULL
+
+tabProd <- xtable::xtable(powerProd,
+                      caption = "Results of fitting a power law model to the degree distribution in each model for production data.
+Kmin is the optimal degree cut-off, alpha is the scaling parameter, and pValue is the probability that quantifies the plausibility of the power law hypothesis.
+If pValue is close to 1, the power law model cannot be rejected as a plausible fit for the data.
+If, instead, pValue is small (e.g., p < 0.05) then the null hypothesis of a power law model can be rejected.")
+
+tabComp <- xtable::xtable(powerComp,
+                      caption = "Results of fitting a power law model to the degree distribution in each model for comprehension data.
+Kmin is the optimal degree cut-off, alpha is the scaling parameter, and pValue is the probability that quantifies the plausibility of the power law hypothesis.
+If pValue is close to 1, the power law model cannot be rejected as a plausible fit for the data.
+If, instead, pValue is small (e.g., p < 0.05) then the null hypothesis of a power law model can be rejected.")
+
+print(tabProd, type="latex", comment = F, table.placement = "H")
+print(tabComp, type="latex", comment = F, table.placement = "H")
+```
 
 # References
-
-```{r}
-# References will be generated automatically by Pandoc and included here.
-# The following code is some latex to format the bibliography. Do not remove it.
+```{r create_r-references}
+r_refs(file = "references.bib")
 ```
 
-\setlength{\parindent}{-0.1in} 
-\setlength{\leftskip}{0.125in}
-\noindent
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}

### 2018-07-06 journal/ms.tex
journal version

--- 2018-07-06 cogsci/cogsci.tex
@@
-% Template for Cogsci submission with R Markdown
+\documentclass[english,floatsintext,man]{apa6}
 
-% Stuff changed from original Markdown PLOS Template
-\documentclass[10pt, letterpaper]{article}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+    \usepackage{xltxtra,xunicode}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
+  \newcommand{\euro}{€}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
 
-\usepackage{cogsci}
-\usepackage{pslatex}
-\usepackage{float}
-\usepackage{caption}
+% Table formatting
+\usepackage{longtable, booktabs}
+\usepackage{lscape}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
 
-% amsmath package, useful for mathematical formulas
-\usepackage{amsmath}
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
 
-% amssymb package, useful for mathematical symbols
-\usepackage{amssymb}
+\newenvironment{lltable}
+  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
+  {\end{ThreePartTable}\end{center}\end{landscape}}
 
-% hyperref package, useful for hyperlinks
-\usepackage{hyperref}
+% The following enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand\getlongtablewidth{%
+ \begingroup
+  \ifcsname LT@\roman{LT@tables}\endcsname
+  \global\longtablewidth=0pt
+  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
+  \@nameuse{LT@\roman{LT@tables}}%
+  \fi
+\endgroup}
 
-% graphicx package, useful for including eps and pdf graphics
-% include graphics with the command \includegraphics
-\usepackage{graphicx}
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \usepackage[unicode=true]{hyperref}
+\fi
+\hypersetup{breaklinks=true,
+            pdfauthor={},
+            pdftitle={Word Learning as Network Growth: A Cross-linguistic Analysis},
+            colorlinks=true,
+            citecolor=blue,
+            urlcolor=blue,
+            linkcolor=black,
+            pdfborder={0 0 0}}
+\urlstyle{same}  % don't use monospace font for urls
 
-% Sweave(-like)
-\usepackage{fancyvrb}
-\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
-\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
-\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
-\newenvironment{Schunk}{}{}
-\DefineVerbatimEnvironment{Code}{Verbatim}{}
-\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
-\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
-\newenvironment{CodeChunk}{}{}
+\setlength{\parindent}{0pt}
+%\setlength{\parskip}{0pt plus 0pt minus 0pt}
 
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
 
-\usepackage{color}
+\ifxetex
+  \usepackage{polyglossia}
+  \setmainlanguage{}
+\else
+  \usepackage[english]{babel}
+\fi
 
-% Use doublespacing - comment out for single spacing
-%\usepackage{setspace}
-%\doublespacing
+% Manuscript styling
+\captionsetup{font=singlespacing,justification=justified}
+\usepackage{csquotes}
+\usepackage{upgreek}
 
-% % Text layout
-% \topmargin 0.0cm
-% \oddsidemargin 0.5cm
-% \evensidemargin 0.5cm
-% \textwidth 16cm
-% \textheight 21cm
+ % Line numbering
+  \usepackage{lineno}
+  \linenumbers
 
+\usepackage{tikz} % Variable definition to generate author note
+
+% fix for \tightlist problem in pandoc 1.14
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+% Essential manuscript parts
   \title{Word Learning as Network Growth: A Cross-linguistic Analysis}
 
-\usepackage[subtle]{savetrees}
+  \shorttitle{Word Learning as Network Growth}
 
-\author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Yuan Bian} \\ \texttt{ybian.uiuc@gmail.com} \\ Department of Psychology \\ University of Illinois \And {\large \bf Michael C.
-Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
+  \author{Abdellah Fourtassi\textsuperscript{1}, Yuan Bian\textsuperscript{2}, \& Michael C. Frank\textsuperscript{1}}
 
-\begin{document}
+  % \def\affdep{{"", "", ""}}%
+  % \def\affcity{{"", "", ""}}%
 
-\maketitle
+  \affiliation{
+    \vspace{0.5cm}
+          \textsuperscript{1} Department of Psychology, Stanford University\\
+          \textsuperscript{2} Department of Psychology, University of Illinois  }
 
-\begin{abstract}
-Children tend to produce words earlier when they are connected to a
+  \authornote{
+    Abdellah Fourtassi
+
+    Department of Psychology
+
+    Stanford University
+
+    50 Serra Mall
+
+    Jordan Hall, Building 420
+
+    Stanford, CA 94301
+
+    Correspondence concerning this article should be addressed to Abdellah
+    Fourtassi, Postal address. E-mail:
+    \href{mailto:afourtas@stanford.edu}{\nolinkurl{afourtas@stanford.edu}}
+  }
+
+  \abstract{Children tend to produce words earlier when they are connected to a
 variety of other words along both the phonological and semantic
@@
 (indirectly) detect and learn highly connected words in the learning
-environment.
+environment.}
+  \keywords{Language understanding; audio-visual processing; word learning; speech
+perception; computational modeling. \\
 
-\textbf{Keywords:}
-semantic network, phonological network, network growth, mechanism of
-word learning
-\end{abstract}
+  }
+
+  \usepackage[sortcites=false,sorting=none]{biblatex}
+
+\usepackage{amsthm}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newtheorem{corollary}{Corollary}
+\newtheorem{proposition}{Proposition}
+\theoremstyle{definition}
+\newtheorem{example}{Example}
+\theoremstyle{definition}
+\newtheorem{exercise}{Exercise}
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
+\newtheorem*{solution}{Solution}
+\begin{document}
+
+\maketitle
+
+\setcounter{secnumdepth}{0}
 
@@
 network, a few have investigated the underlying developmental process.
-In particular, Steyvers \& Tenenbaum (2005) suggested that the observed
+In particular, Steyvers and Tenenbaum (2005) suggested that the observed
 effects of connectivity are the consequence of how the lexical network
@@
 known as Preferential Attachment (PAT), highly connected words in the
-child's lexicon tend to ``attract'' more words over time, in a
+child's lexicon tend to \enquote{attract} more words over time, in a
 rich-get-richer scenario (Barabasi \& Albert, 1999). In other words,
@@
 environment. They called this alternative explanation Preferential
-Acquisition (PAC). Figure \ref{fig:growth} shows an illustration of both
+Acquisition (PAC). Figure~\ref{fig:growth} shows an illustration of both
 growth scenarios with the same simplified network. These two proposals
@@
 
-\begin{CodeChunk}
-\begin{figure}[H]
+\begin{figure}
 
-{\centering \includegraphics{figs/growth-1}
+{\centering \includegraphics[width=400px]{figs/growth2}
 
@@
 
-\caption{\label{fig:growth}Illustration of the growth scenarios.
+\caption{Illustration of the growth scenarios.
 Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
@@
 \end{figure}
-\end{CodeChunk}
 
@@
 the findings across eight languages.
-
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/all_data-1}
-
-}
-
-\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
-Results are shown in each language for phonological and semantic networks.
-Each point is a word, with lines indicating linear model fits.}\label{fig:all_data}
-\end{figure*}
-\end{CodeChunk}
-
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/degree_distribution-1}
-
-}
-
-\caption{\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
-A perfect power-law distribution should appear as a straight line in this graph.}\label{fig:degree_distribution}
-\end{figure*}
-\end{CodeChunk}
 
@@
 
-\subsection{Semantic networks}\label{semantic-networks}
+\section{Semantic networks}\label{semantic-networks}
 
@@
 cue), and asking them to write the first word that comes to mind (the
-target). For example, when given the word ``ball'', they might answer
-with the word ``game''. A pair of nodes were connected by a directed
-link from the cue to the target if there was a cue-target relationship
-between these nodes in the association norms. The connectivity of a
-given node was characterized by its \emph{indegree}: the number of links
-for which the word was the target. To model growth from month to month,
-we constructed a different network at each month, based on the words
-that have been acquired by that month.
+target). For example, when given the word \enquote{ball}, they might
+answer with the word \enquote{game}. A pair of nodes were connected by a
+directed link from the cue to the target if there was a cue-target
+relationship between these nodes in the association norms. The
+connectivity of a given node was characterized by its \emph{indegree}:
+the number of links for which the word was the target. To model growth
+from month to month, we constructed a different network at each month,
+based on the words that have been acquired by that month.
 
@@
 
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrAll-1} \caption{Age of production (A) and comprehension (B) in the global network as predicted by the degree in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits.}\label{fig:corrAll}
+\end{figure}
+
 \subsubsection{Connectivity predicts the age of
@@
 Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.}
-Figure \ref{fig:data_all} shows how the age of acquisition for each word
-varies as a function of its degree (or indegree for the semantic
-network). For ease of visual comparison, the predictor (i.e., the
-degree) was centered and scaled across languages. The plots show,
-overall, a negative correlation between the month of acquisition and the
-degree, indicating that nouns with higher degrees are generally learned
-earlier.
+Figure \ref{fig:corrAll} shows how the age of production (A) and
+comprehension (B) for each word varies as a function of its degree (or
+indegree for the semantic network). For ease of visual comparison, the
+predictor (i.e., the degree) was centered and scaled across languages.
+The plots show, overall, a negative correlation between the month of
+acquisition and the degree, indicating that nouns with higher degrees
+are generally learned earlier.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{figs/plot_degree} \caption{Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
+The figure shows the results for both production and comprehension data.
+A perfect power-law distribution should appear as a straight line in this graph.}\label{fig:degreeDist}
+\end{figure}
 
@@
 follow a power law, this fact would weaken the case for PAT. The log-log
-plots are shown in Figure \ref{fig:degree_distribution}. We fit a power
-law to each empirical degree distribution following the procedure
-outlined in Clauset, Shalizi, \& Newman (2009) and using the related R
-package (poweRlaw, Gillespie, 2015). In brief, the analysis consisted in
-two steps. First, we derived the optimal cut-off, \(k_{min}\), above
-which the distribution is more likely to follow a power
+plots are shown in Figure \ref{fig:degreeDist}. We fit a power law to
+each empirical degree distribution following the procedure outlined in
+Clauset, Shalizi, and Newman (2009) and using the related R package
+(poweRlaw, Gillespie, 2015). In brief, the analysis consisted in two
+steps. First, we derived the optimal cut-off, \(k_{min}\), above which
+the distribution is more likely to follow a power
 law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}
@@
 we calculated the goodness-to-fit, which resulted in a \(p\)-value
-quantifying the plausibility of the model. Overall, we could not reject
-the null hypothesis of a power-law distribution: the \(p\)-value was
-generally above 0.1, except for the Italian phonological network where
-we obtained \(p < 0.05\), suggesting that the power law can be ruled out
-in this particular case.
+quantifying the plausibility of the model. The results are shown in
+Appendix 1, table XX. Overall, we could not reject the null hypothesis
+of a power-law distribution: the \(p\)-value was generally above 0.1.
 
@@
 
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/pred_ind_img-1}
-
-}
-
-\caption{\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid).
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/growthPred-1} \caption{Evaluation of network growth scenarios, for both A) production and B) comprehension.
+We plot values when predictors are evaluted individually (dotted), and when combined in the same growth model (solid).
 Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\% credible intervals (computed using the highest density intervals).
 Positive values mean that learning proceeds according to the predictions of the growth scenario.
-Negative values mean that learning proceeds in opposition to the predictions of the growth scenario.}\label{fig:pred_ind_img}
-\end{figure*}
-\end{CodeChunk}
+Negative values mean that learning proceeds in opposition to the predictions of the growth scenario.}\label{fig:growthPred}
+\end{figure}
 
@@
 Chain Monte Carlo sampling resulted in a posterior distribution over
-\(\beta\), which we summarized in Figure \ref{fig:pred_ind}.
+\(\beta\), which we summarized in Figure \ref{fig:growthPred}.
 
@@
 semantic networks (where it is rather universally unpredictive).
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPred-1} \caption{Estimates of predictor coefficients by language in production (A) and comprehension (B), with ranges indicating 95\% confidence intervals.
+Positive values indicate a positive relationship (e.g.
+longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
+words with higher frequency tend to have a lower AoA).}\label{fig:staticPred}
+\end{figure}
 
@@
 
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/regressions_img-1}
-
-}
-
-\caption{\label{fig:regressions_img}Estimates of predictor coefficients by language, with ranges indicating 95\% confidence intervals.
-Positive values indicate a positive relationship (e.g.
-longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
-words with higher frequency tend to have a lower AoA).}\label{fig:regressions_img}
-\end{figure*}
-\end{CodeChunk}
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{figs/plot_static_preds_all} \caption{Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect for both production and comprehension.
+Ranges indicate 95\% confidence intervals.
+Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates.}\label{fig:staticAll}
+\end{figure}
 
@@
 For each word, counts included words that shared the same stem (e.g.,
-``cats'' counts as ``cat''), or words that were synonymous (e.g.
-``father'' counts as ``daddy''). For word length, we counted the number
-of phonemes in our generated IPA transcription.
+\enquote{cats} counts as \enquote{cat}), or words that were synonymous
+(e.g. \enquote{father} counts as \enquote{daddy}). For word length, we
+counted the number of phonemes in our generated IPA transcription.
 
@@
 and we fit a linear mixed-effect model to all the data pooled across
-languages, with language as a random effect. Figure
-\ref{fig:regressions_img} shows the coefficient estimate for each
-predictor in each language, and Figure \ref{fig:regressions_all_img}
-shows the coefficient estimates for all languages combined (all
-predictors were centered and scaled). The findings were as follows.
-Overall, frequency is the largest and most consistent predictor of age
-of acquisition, replicating results for nouns across a variety of
-analyses (Braginsky et al., 2016; J. C. Goodman et al., 2008; B. C. Roy
-et al., 2015). Word length predicts learning in some languages such as
-Croatian and Norwegian, but not in others (including English). It
-remains, however, a significant predictor in the global model. As for
-the factors of interest, i.e., semantic and phonological connectivity,
-we also found cross-linguistic differences. Phonological connectivity
-contributes to learning in languages such as Croatian, English and
-Russian, whereas semantic connectivity contributes to learning in
-Turkish, Spanish and to some extent in Croatian, but not in
+languages, with language as a random effect. Figure \ref{fig:staticPred}
+shows the coefficient estimate for each predictor in each language for
+production and comprehension data. Figure \ref{fig:staticAll} shows the
+coefficient estimates for all languages combined (all predictors were
+centered and scaled). The findings were as follows. Overall, frequency
+is the largest and most consistent predictor of age of acquisition,
+replicating results for nouns across a variety of analyses (Braginsky et
+al., 2016; J. C. Goodman et al., 2008; B. C. Roy et al., 2015). Word
+length predicts learning in some languages such as Croatian and
+Norwegian, but not in others (including English). It remains, however, a
+significant predictor in the global model. As for the factors of
+interest, i.e., semantic and phonological connectivity, we also found
+cross-linguistic differences. Phonological connectivity contributes to
+learning in languages such as Croatian, English and Russian, whereas
+semantic connectivity contributes to learning in Turkish, Spanish and to
+some extent in Croatian, but not in
 English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
@@
 data are pooled across languages.
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/regressions_all_img-1}
-
-}
-
-\caption{\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect.
-Ranges indicate 95\% confidence intervals.
-Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates.}\label{fig:regressions_all_img}
-\end{figure}
-\end{CodeChunk}
 
@@
 
-\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}}
+\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/WordRec}}}
 \vspace{1em}
@@
 This work was supported by a post-doctoral grant from the Fyssen
-Foundation, NSF \#1528526, and NSF \#1659585.
+Foundation.
+
+\section{Disclosure statement}\label{disclosure-statement}
+
+None of the authors have any financial interest or a conflict of
+interest regarding this work and this submission.
+
+\section{Appendix 1: Power law model}\label{appendix-1-power-law-model}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{rrrrll}
+  \hline
+ & Kmin & alpha & pValue & dimension & language \\ 
+  \hline
+1 & 4.00 & 2.55 & 0.88 & Sem & Croatian \\ 
+  2 & 4.00 & 2.18 & 0.12 & Phono & Croatian \\ 
+  3 & 4.00 & 2.38 & 0.00 & Sem & Danish \\ 
+  4 & 11.00 & 4.55 & 0.86 & Phono & Danish \\ 
+  5 & 5.00 & 2.66 & 0.13 & Sem & English \\ 
+  6 & 20.00 & 9.14 & 0.51 & Phono & English \\ 
+  7 & 8.00 & 2.81 & 0.13 & Sem & French \\ 
+  8 & 20.00 & 3.75 & 0.11 & Phono & French \\ 
+  9 & 4.00 & 2.93 & 0.61 & Sem & Italian \\ 
+  10 & 9.00 & 9.45 & 0.78 & Phono & Italian \\ 
+  11 & 5.00 & 2.88 & 0.20 & Sem & Norwegian \\ 
+  12 & 15.00 & 6.28 & 0.74 & Phono & Norwegian \\ 
+  13 & 24.00 & 5.61 & 0.72 & Sem & Russian \\ 
+  14 & 8.00 & 4.20 & 0.54 & Phono & Russian \\ 
+  15 & 4.00 & 2.98 & 0.46 & Sem & Spanish \\ 
+  16 & 13.00 & 8.75 & 0.74 & Phono & Spanish \\ 
+  17 & 4.00 & 2.49 & 0.17 & Sem & Swedish \\ 
+  18 & 11.00 & 4.68 & 0.10 & Phono & Swedish \\ 
+  19 & 4.00 & 2.87 & 0.93 & Sem & Turkish \\ 
+  20 & 8.00 & 3.26 & 0.38 & Phono & Turkish \\ 
+   \hline
+\end{tabular}
+\caption{Results of fitting a power law model to the degree distribution in each model for production data.
+Kmin is the optimal degree cut-off, alpha is the scaling parameter, and pValue is the probability that quantifies the plausibility of the power law hypothesis.
+If pValue is close to 1, the power law model cannot be rejected as a plausible fit for the data.
+If, instead, pValue is small (e.g., p < 0.05) then the null hypothesis of a power law model can be rejected.}
+\end{table}\begin{table}[H]
+\centering
+\begin{tabular}{rrrrll}
+  \hline
+ & Kmin & alpha & pValue & dimension & language \\ 
+  \hline
+1 & 5.00 & 2.67 & 0.90 & Sem & Croatian \\ 
+  2 & 2.00 & 2.06 & 0.02 & Phono & Croatian \\ 
+  3 & 4.00 & 2.39 & 0.01 & Sem & Danish \\ 
+  4 & 5.00 & 2.98 & 0.14 & Phono & Danish \\ 
+  5 & 4.00 & 2.64 & 0.77 & Sem & English \\ 
+  6 & 13.00 & 5.16 & 0.23 & Phono & English \\ 
+  7 & 4.00 & 2.63 & 0.33 & Sem & French \\ 
+  8 & 18.00 & 5.58 & 0.34 & Phono & French \\ 
+  9 & 4.00 & 2.88 & 0.69 & Sem & Italian \\ 
+  10 & 8.00 & 10.27 & 0.91 & Phono & Italian \\ 
+  11 & 5.00 & 2.87 & 0.43 & Sem & Norwegian \\ 
+  12 & 13.00 & 7.65 & 0.44 & Phono & Norwegian \\ 
+  13 & 8.00 & 3.91 & 0.95 & Sem & Russian \\ 
+  14 & 5.00 & 3.97 & 0.85 & Phono & Russian \\ 
+  15 & 5.00 & 3.11 & 0.55 & Sem & Spanish \\ 
+  16 & 5.00 & 3.01 & 0.09 & Phono & Spanish \\ 
+  17 & 5.00 & 2.81 & 0.71 & Sem & Swedish \\ 
+  18 & 9.00 & 6.75 & 0.10 & Phono & Swedish \\ 
+  19 & 4.00 & 3.13 & 0.89 & Sem & Turkish \\ 
+  20 & 9.00 & 5.73 & 0.96 & Phono & Turkish \\ 
+   \hline
+\end{tabular}
+\caption{Results of fitting a power law model to the degree distribution in each model for comprehension data.
+Kmin is the optimal degree cut-off, alpha is the scaling parameter, and pValue is the probability that quantifies the plausibility of the power law hypothesis.
+If pValue is close to 1, the power law model cannot be rejected as a plausible fit for the data.
+If, instead, pValue is small (e.g., p < 0.05) then the null hypothesis of a power law model can be rejected.}
+\end{table}
 
@@
 
-\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent
+\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
 
@@
 \hypertarget{ref-nelson1998}{}
-Nelson, D. L., McEvoy, C. L., \& Schreiber, T. A. (1998). The University
-of South Florida word association, rhyme, and word fragment norms.
-Retrieved from \url{http://w3.usf.edu/FreeAssociation/}
+Nelson, D. L., McEvoy, C. L., \& Schreiber, T. A. (1998). \emph{The
+University of South Florida word association, rhyme, and word fragment
+norms}. Retrieved from \url{http://w3.usf.edu/FreeAssociation/}
 

### 2018-07-06 main_analyses.Rmd
journal version

Libraries
```{r}
  library(broom)
  library(purrr)
  library(readr)
  library(ggplot2)
  library(dplyr)
  library(tidyr)
  library(wordbankr)
  library(stringr)
  library(feather)
  library(lme4)
  library(boot)
  library(langcog)
  library(ggthemes)
  library(nlme)
  library(rwebppl)
  library(jsonlite)
  library(Hmisc)
  library(poweRlaw)
  library(HDInterval)
```

Import helper functions and probabilstic models

```{r}
#Load helper functions
source(paste(getwd(),"/helper_functions/all_helper.r",sep = ""), chdir = T)

#Load probabilsitic models
source(paste(getwd(),"/models/all_models.r",sep = ""), chdir = T)

```

Load data and pre-process
```{r}

languages = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish")

admins <- get_administration_data() %>%
  select(data_id, age, language, form) %>%
  filter(language %in% languages)

items <- get_item_data() %>%
  filter(type == "word", lexical_class == "nouns") %>%
  filter(language %in% languages)

items_by_inst <- split(items, paste(items$language, items$form, sep = "_"))

get_inst_data <- function(inst_items) {
  inst_lang <- unique(inst_items$language)
  inst_form <- unique(inst_items$form)
  inst_admins <- filter(admins, language == inst_lang, form == inst_form)
  get_instrument_data(language = inst_lang ,
                      form = inst_form,
                      administrations = inst_admins,
                      items = inst_items$item_id,
                      iteminfo = inst_items
                      ) %>%
    filter(!is.na(age)) %>%
    mutate(produces = !is.na(value) & value == "produces",
           understands = !is.na(value) & (value == "understands" | value == "produces")) %>%
    select(-value) %>%
    gather(measure, value, produces, understands) %>%
    filter((measure == "understands" & form == "WG") | (measure == "produces" & form == "WS") ) %>%
    mutate(language = inst_lang,
           form = inst_form)

}

data_raw <- map(items_by_inst, get_inst_data)

data_all <- bind_rows(data_raw) %>%
  rename(item = num_item_id) %>%
  group_by(language, form, measure,
             lexical_category, lexical_class, uni_lemma,  item, definition, 
             age) %>%
  summarise(num_true = sum(value, na.rm = TRUE),
              num_false = n() - num_true,
              prop = mean(value, na.rm = TRUE))

#feather::write_feather(data_all, "saved_data/data_all.feather")

#I am taking out measure to keep only produce
data_all <- feather::read_feather("saved_data/all_data.feather")

data_all$language <- plyr::mapvalues(data_all$language, 
                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))

```

Compute Age of Acqusition (AoA) of words

```{r}

fit_inst_measure_uni <- function(inst_measure_uni_data) {
  ages <- min(inst_measure_uni_data$age):max(inst_measure_uni_data$age)
  model <- glm(cbind(num_true, num_false) ~ age, family = "binomial",
               data = inst_measure_uni_data)
  fit <- predict(model, newdata = data.frame(age = ages), se.fit = TRUE)
  aoa <- -model$coefficients[["(Intercept)"]] / model$coefficients[["age"]]
  constants <- inst_measure_uni_data %>%
    ungroup()%>%
    select(language, form, measure, lexical_category, lexical_class, uni_lemma, item, definition) %>%
    distinct()

  props <- inst_measure_uni_data %>%
    ungroup() %>%
    select(age, prop)

  data.frame(age = ages,
             fit_prop = inv.logit(fit$fit),
             fit_se = fit$se.fit,
             aoa = aoa, language = constants$language,
             form = constants$form,
             measure = constants$measure,
             uni_lemma = constants$uni_lemma,
             item = constants$item,
             definition = constants$definition) %>%
    left_join(props)
}

list_by_item <- data_all %>%
  # make this filtering at the beginning, not here
  split(paste(.$language, .$form, .$measure, .$item))

data_aoa <- map(list_by_item, fit_inst_measure_uni) %>%
  bind_rows()

data_aoa <- data_aoa %>%
  select(language, form, measure, uni_lemma, item, definition, aoa) %>%
  distinct()

#feather::write_feather(data_aoa, "saved_data/data_aoa.feather")

#I am taking out measure to keep only produce
#data_aoa2 <- feather::read_feather("saved_data/aoa_data.feather") %>%
#  rename(definition = defintion) %>%
#  select(language, form, measure, uni_lemma, item, definition, aoa) %>%
#  distinct()

```

Compute the growth data structue (based on AoA data)

```{r}

#make a growth dataframe
make_data_growth <- function(word_aoa) {

  measure <- unique(word_aoa$measure)
  lang <- unique(word_aoa$language)

  ages<- (word_aoa %>%
    arrange(age) %>%
    group_by(age) %>%
    summarise(n = n()))$age

  df <- data.frame()
  for (i in ages) {
    rem_words <- word_aoa %>% filter(age >= i)
    rem_lemma <- c(rem_words$uni_lemma)
    rem_def <- c(rem_words$definition)
    rem_item<- c(rem_words$item)
    corr_age <- rep(i, times = length(rem_lemma))
    curr_df <- data.frame(corr_age, rem_item, rem_lemma, rem_def)
    df <- rbind(df, curr_df)
  }  
  df <- df %>% rename(uni_lemma = rem_lemma, definition=rem_def, item=rem_item)%>%
    left_join(word_aoa %>% select(item, age)) %>%
    mutate(learned = as.numeric(age == corr_age)) %>%
    select(corr_age, item, definition, uni_lemma,learned) %>%
    rename(age = corr_age) %>%
    arrange(age, item) %>%
    mutate(language = lang,
           measure = measure)
  return(df)
}

aoa_by_measure_lang <- data_aoa %>%
  mutate(age = round(aoa)) %>%
  select(-form, -aoa) %>%
  split(paste(.$language, .$measure))

data_growth <- map(aoa_by_measure_lang, make_data_growth) %>%
  bind_rows()

#Save at this point
#feather::write_feather(data_growth, "saved_data/data_growth.feather")
#data_growth <- feather::read_feather("saved_data/data_growth.feather") 
```

Construct the netwroks and derive the dynamic predictors: PAC and PAT
```{r}

#I should here define the set of words that will be used in the network construction
#Here I chose to use the full data for the phono netwotk and filter later for the unilemmas only, thus the utility will be more precise for the resulting subset

words_growth <- data_growth %>%
  #filter(!is.na(uni_lemma)) %>% #only keep unilemmas that intersect with free association data
  dplyr::filter(aoa > 5)

growth_by_meas <- words_growth %>%
  split(paste(.$measure))

growth_by_meas_lang <- words_growth %>%
  split(paste(.$measure, .$language))

#Semantic netwrok 
##################

sem_net_fun  <- function (growth_meas_lang){

  first_age<- growth_meas_lang$age[1]

  lemma_list<- growth_meas_lang %>%
      trim_all_unilemma() %>%
      filter(age==first_age) %>%
      select(item, uni_lemma)

assoc_pairs<- make_assoc_pairs(lemma_list = lemma_list)

assoc_PAC<- PAC_generator(vocab_age = growth_meas_lang, word_pairs = assoc_pairs) %>% 
      rename(PAC_assoc = value) %>% select(-definition, -uni_lemma)

 assoc_PAT<- PAT_generator(vocab_age = growth_meas_lang, word_pairs = assoc_pairs) %>% 
      rename(PAT_assoc = value) %>% select(-definition, -uni_lemma)

 sem_growth <- growth_meas_lang %>%
   left_join(assoc_PAC) %>%
   left_join(assoc_PAT)

 return(sem_growth)

}

sem_red <-  map(growth_by_meas_lang, sem_net_fun) %>%
  bind_rows()

#Save 
#feather::write_feather(sem_red, "saved_data/sem_red.feather")
#sem_red <- feather::read_feather("saved_data/sem_red.feather")

#Phonological Networks
######################

phono_net_fun <- function (growth_meas_lang) {

  lang <- unique(growth_meas_lang$language)
  #meas <- unique(growth_meas_lang$measure)

  first_age<- growth_meas_lang$age[1]

  def_list<- growth_meas_lang %>%
      trim_all_definition() %>% 
      filter(age==first_age) %>%
      select(item, definition)

  phono_pairs<- make_IPA_pairs(def_list = def_list, lang = lang)

  #Threshold the phonetic distance (we take t=2, becuase t=1 is too sparse) 
  threshold <- 2

  phono_PAC <- PAC_generator(vocab_age = growth_meas_lang, word_pairs = phono_pairs %>% IPA_threshold(threshold)) %>% 
      rename(PAC_phono_t2 = value) %>% select(-definition, -uni_lemma)

  phono_PAT <- PAT_generator(vocab_age = growth_meas_lang, word_pairs = phono_pairs %>% IPA_threshold(threshold)) %>% 
      rename(PAT_phono_t2 = value) %>% select(-definition, -uni_lemma)

  phono_growth <- growth_meas_lang %>%
   left_join(phono_PAC) %>%
   left_join(phono_PAT)

}

phono_red <-  map(growth_by_meas_lang, phono_net_fun) %>%
  bind_rows()

#feather::write_feather(phono_red, "saved_data/phono_red.feather")
#phono_red <- feather::read_feather("saved_data/phono_red.feather")

#Combine data 
data_growth_net <- words_growth %>%
  left_join(sem_red) %>%
  left_join(phono_red)

```

Compute other static predictors (frequency and length) besides PAC

```{r}

data_static <- data_growth_net %>%
  distinct(measure, language, uni_lemma, definition, item, PAC_assoc, PAC_phono) %>%
  rename(sem_deg = PAC_assoc, 
         phono_deg =  PAC_phono)

#Word length

words_len <- data_static %>%
  trim_all_definition() %>%
  rowwise() %>%
  mutate(IPA=Speak(lang = language, word = definition)) %>%
  trim_IPA_completely() %>%
  mutate(length = str_count(IPA)) %>%
  select(-definition, -uni_lemma, -sem_deg, -phono_deg)

#Word frequency: we use frequency values derived from Childes (from Mika e al. 2016)

load("saved_data/uni_joined.RData")

frequency_mika <- uni_joined %>%
  filter(lexical_classes =='nouns') %>%
  distinct(language, uni_lemma, frequency) %>%
  mutate(lang_temp = ifelse(language == "French (Quebec)", "French (Quebecois)", language)) %>%
  select(-language) %>%
  rename(language = lang_temp)

words_freq <- data_static %>%
  left_join(frequency_mika) %>%
  select(-definition, -uni_lemma, -sem_deg, -phono_deg)

aoa_items <- data_aoa %>%
  select(language, measure, item, aoa) # Here I should round the AoA?

#Combine predictors

data_static_pred  <- data_static %>%
  left_join(words_len) %>%
  left_join(words_freq) %>%
  left_join(aoa_items) #%>%
  #select(-definition, -uni_lemma)

#Use feather here
################

#Combine with full proportion-based data  (for the second regression which fit the entire production curve)

data_static_pred$language <- plyr::mapvalues(data_static_pred$language, 
                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))

data_static_prop$language <- plyr::mapvalues(data_static_prop$language, 
                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))

data_static_prop <- data_all %>%
  left_join(data_static_pred) 
```

## Correlations

Correlatinon degree/AoA using unilemmas

```{r}
#Sem_deg is defined over unilemmas,  phono_deg is defined over definitions, and AoA is defined over items 
#For a given defintion we can have more than one item (polysemy), for one unilemma we can have more than one definiton (if the semantic distinction is not very important), or we might have 0 unilemma (if the meaning of the defintion is not part of the main cross-lingusitc lemmas)
#The following analyses predict try to predict the items' AoA. I keep duplicated values of the predictors for different items (when they have the same defintions and/or unilemma) since I consider that this is the actual (albeit braod) information brough by the precitors

#Restrict analysis to unilemmas (i.e., definitons which have translations in English). This allows us to comapre various predictors on the same set of data
unilemmas <- data_static_pred %>%
  select(-IPA) %>%
  filter(!is.na(uni_lemma)) %>% 
  filter(!is.na(sem_deg)) %>% #only keep unilemmas that intersect with free association data 
  filter(aoa > 5) #These AoA are  artifact of the glm fitting (likely due to very few data point, I need to check these)

#Impute missing values and center/scale
uni_scale <- unilemmas %>%
  group_by(measure, language) %>%
  mutate_at(c('sem_deg', 'phono_deg', 'length', 'frequency'), funs(as.numeric(Hmisc::impute(.)))) %>%
  mutate_at(c('sem_deg', 'phono_deg', 'length', 'frequency'), funs(as.numeric(scale(.))))

feather::write_feather(uni_scale, "saved_data/data_static_scaled.feather")
#phono_red <- feather::read_feather("saved_data/phono_red.feather")

data_long <- uni_scale %>%
  gather(predictor, value, sem_deg:frequency) %>%
  filter(predictor == "sem_deg" | predictor == "phono_deg")

correlations <- data_long %>%
  group_by(measure, language, predictor) %>%
  summarise(cor = round(cor(aoa, value), 2))

#Reproduce the first analyses of correlation, (degree distribution later), then regressions both language specific and aggragate, 
#Then go to the intercation based regression, and aggregate, show that there is no significant interaction with age. And also show

```

Production

```{r fig.width=10, fig.height=5}
plot_correlation_prod <- ggplot(subset(data_long, measure == "produces"), aes(x=value, y=aoa))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="produces"), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("AoA")

plot_correlation_prod

```

Comprehension
```{r fig.width=10, fig.height=5}
plot_correlation_comp <- ggplot(subset(data_long, measure == "understands"), aes(x=value, y=aoa))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="understands"), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("AoA")

plot_correlation_comp

```

##Static netwrok properties

### Degree distribution
Import the analysese from cogsci paper

```{r}

#function that takes data growth and does power law analyses

#Data for plot
degreeDist <- data.frame(matrix(ncol = 5, nrow = 0))
dist_names <- c("x", "y", "dimension", "language", "measure")
colnames(degreeDist) <- dist_names

#Parameters and test
degreeTest <- data.frame(matrix(ncol = 6, nrow = 0))
test_names <- c("xMin", "alpha", "pVal", "dimension","language", "measure")
colnames(degreeTest) <- test_names

powerLaw_fun <- function(data_growth_meas_lang, analysis){

  lang <- unique(data_growth_meas_lang$language)
  meas <- unique(data_growth_meas_lang$measure)

  data_meas_lang <- data_growth_meas_lang %>%
    select(measure, language, sem_deg, phono_deg) %>%
    dplyr::rename(Sem = sem_deg, Phono = phono_deg) %>%
    dplyr::filter (!is.na(Sem),!is.na(Phono))

  ##Semantic network

  #fit and derive parameters for power law
  semList <- data_meas_lang$Sem[data_meas_lang$Sem != 0]
  sem_pl = displ$new(semList)
  sem_est = estimate_xmin(sem_pl)
  sem_pl$setXmin(sem_est)
  sem_dist = plot(sem_pl) %>%
    mutate(dimension='Sem', language  =  lang, measure = meas)

  #bootstrap to get p-value
  sem_boot = bootstrap_p(sem_pl, no_of_sims=1000, threads=2)

  sem_test <- data.frame(as.numeric(sem_pl$xmin), as.numeric(sem_pl$pars), as.numeric(sem_boot$p), 'Sem', lang, meas)
  colnames(sem_test) <- test_names

  ##Phonological network

  #fit and derive parameters for power law
  phonoList <- data_meas_lang$Phono[data_meas_lang$Phono != 0]
  phono_pl = displ$new(phonoList)
  phono_est = estimate_xmin(phono_pl)
  phono_pl$setXmin(phono_est)
  phono_dist = plot(phono_pl) %>%
    mutate(dimension='Phono', language = lang, measure = meas)

  #bootstrap to get p-value
  phono_boot = bootstrap_p(phono_pl, no_of_sims=1000, threads=2)

  phono_test <- data.frame(as.numeric(phono_pl$xmin), as.numeric(phono_pl$pars), as.numeric(phono_boot$p), 'Phono', lang, meas)
  colnames(phono_test) <- test_names

  dist_meas_lang <- bind_rows(sem_dist, phono_dist)
  test_meas_lang <- bind_rows(sem_test, phono_test)

  #return(dist_meas_lang)

  if (analysis == 'distribution') {

    return(dist_meas_lang)

  } else if (analysis == 'test') {

    return(test_meas_lang)

  } else {

    print("Please specify the analysis type ('distribution' or 'test')")

  }

}

#Split by measure and language

data_by_meas_lang <- unilemmas %>%
  split(paste(.$measure, .$language))

degree_dist  <- map2(data_by_meas_lang, 'distribution', powerLaw_fun) %>%
  bind_rows()

feather::write_feather(degree_dist, "saved_data/degree_dist.feather")

degree_test  <- map2(data_by_meas_lang, 'test' , powerLaw_fun) %>%
  bind_rows()

feather::write_feather(degreeDist, "saved_data/degree_dist.feather")
degree_dist <- feather::read_feather("saved_data/degree_dist.feather")

feather::write_feather(degree_test, "saved_data/degree_test.feather")
degree_test <- feather::read_feather("saved_data/degree_test.feather")

#plot cumulative distributions
ggplot(data = degree_dist,  aes(x=x, y=y, col=dimension))+
  facet_grid(measure ~ language)+#, scales = "free") +
  geom_point(#aes(colour = lexical_class),
    #colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  scale_y_log10() + scale_x_log10() +
  theme(aspect.ratio = 1)
  #scale_x_continuous(limits=c(-2,5))+
  #geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  #scale_colour_solarized(name = "")

```

### Small world properties

Use igraph to derive small world properties

For each netwrok, compute:
-Clustering coefficient 
-Shortest path length 
what we want: Compared to an equivalent random network, we want a balance between local processing (high clustering coefficient) and global integration (small short path length)

## Growth mechanisms

PreProcessing growth data strcutire for network growth models

```{r}

#Filtering 
data_growth_pred <- data_growth_net %>%
  filter(!is.na(uni_lemma)) %>% #use only words with english translation 
  filter(!is.na(PAC_assoc)) %>% # keep unilemma whcih intersect with free association data
  filter(!is.na(PAC_phono_t2)) # In case a word is not trnascribed phonologically (there should not be any)

  # replace NA in PAT with O (NA is when the utility cannot be computed, e.g., a candidate word is not linked to any previousely learned word, as opposed to being linked to a previously learned word with a degree=0)

data_growth_pred$PAT_assoc[is.na(data_growth_pred$PAT_assoc)] <- 0
data_growth_pred$PAT_phono_t2[is.na(data_growth_pred$PAT_phono_t2)] <- 0

#Scale predictors

data_growth_pred$language <- plyr::mapvalues(data_growth_pred$language, 
                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))

data_growth_pred <- data_growth_pred %>%
  group_by(measure, language) %>%
  mutate_at(c('PAC_assoc', 'PAT_assoc', 'PAC_phono_t2', 'PAT_phono_t2'), funs(as.numeric(scale(.)))) %>%
  select(-definition) #removing defintions because they cause JSon parser to fail in rWebppl (especially the (') in French)

```

Here we train the probabilistic models

```{r}
#Define the models

#Load probabilsitic models
source(paste(getwd(),"/models/all_models.r",sep = ""), chdir = T)

#Isolateed predictors
model_semPAT <-  paste(helper, sem_PAT, optimize, sep = '\n')
model_semPAC <-  paste(helper, sem_PAC, optimize, sep = '\n')
model_phonoPAT <-  paste(helper, phono_PAT, optimize, sep = '\n')
model_phonoPAC <-  paste(helper, phono_PAC, optimize, sep = '\n')

#Combined predictors
model_semPAC_phonoPAC_semPAT_phonoPAT <-  paste(helper, semPAC_phonoPAC_semPAT_phonoPAT, optimize, sep = '\n')

#Make a list of theses models
model_list = list(model_semPAT, model_semPAC, model_phonoPAT, model_phonoPAC,
                  model_semPAC_phonoPAC_semPAT_phonoPAT
                  )

model_name=c('semPAT', 'semPAC', 'phonoPAT', 'phonoPAC',
                                        'model_semPAC_phonoPAC_semPAT_phonoPAT')

```

Compute posteriors
```{r}

#Function that computes the posterior

posterior_fun <- function(data_growth_meas_lang) {

  lang <- unique(data_growth_meas_lang$language)
  meas <- unique(data_growth_meas_lang$measure)

  posteriors_lang <- vector("list", length = length(model_list))

  for (i in 1:length(model_list)) {

    posterior_model <- NULL
    print(model_name[[i]]) 
    print(meas)
    print(lang)

    while (typeof(posterior_model)=="NULL") {
      posterior_model <- webppl(model_list[[i]],
                                data = data_growth_meas_lang,
                                data_var = "data",
                                inference_opts = list(
                                  method = "MCMC",
                                  samples = 1000, 
                                  burn = 500),
                                model_var = "AOA",
                                output_format = "webppl")
    }

    posteriors_lang[[i]] <- posterior_model %>%
      mutate(measure = meas,
             language = lang,
             model_name = model_name[i])
  }

  return(bind_rows(posteriors_lang))

}

#Split by measure and language

data_growth_by_meas_lang <- data_growth_pred %>%
  split(paste(.$measure, .$language))

posterior <- map(data_growth_by_meas_lang, posterior_fun) %>%
  bind_rows()

feather::write_feather(posterior, "saved_data/posterior.feather")
posterior <- feather::read_feather("saved_data/posterior.feather")

```

Extact coefficients from the posterior

```{r}

param <- posterior %>%
  select(starts_with("value.parameters"), measure, language, model_name) %>%
  gather(alpha, value, value.parameters.alpha1:value.parameters.alpha6) %>%
  mutate(alpha = gsub("value.parameters.", "", alpha)) %>%
  dplyr::filter(alpha != "alpha5",
         alpha != "alpha6") %>%
  rename(model = model_name)

#feather::write_feather(param, "saved_data/param.feather")
#param <- feather::read_feather("saved_data/param.feather")

param_summary <- param %>%
  group_by(measure, language, model, alpha) %>%
  summarise(mean = mean(value),
            median = median(value),
            quantile_lower = quantile(value, c(0.025, 0.975))["2.5%"],
            quantile_upper = quantile(value, c(0.025, 0.975))["97.5%"],
            hdi_lower = hdi(value)['lower'],
            hdi_upper = hdi(value)['upper']
  )

param_summary_ind <- param_summary %>%
  dplyr::filter(model != "model_semPAC_phonoPAC_semPAT_phonoPAT",
         alpha == "alpha1") %>%
  mutate(Test = 'Individual') %>%
  select(-alpha)

param_summary_com <- param_summary %>%
  ungroup() %>%
  dplyr::filter(model == "model_semPAC_phonoPAC_semPAT_phonoPAT") %>%
  select(-model) %>%
  rename(model = alpha) %>%
  mutate(Test = 'Combined')

param_summary_com$model <- plyr::mapvalues(param_summary_com$model, 
                                 from = c("alpha1", "alpha2","alpha3","alpha4"), 
                                 to = c("semPAC", "phonoPAC", "semPAT", "phonoPAT"))

param_summary_all <- param_summary_ind %>%
  bind_rows(param_summary_com)

feather::write_feather(param_summary_all, "saved_data/growth_preds.feather")
param_summary_all <- feather::read_feather("saved_data/growth_preds.feather")

```

Plot growth data (production)

```{r fig.width=5, fig.height=2}
ggplot(subset(param_summary_all, measure == "produces"), aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

```

Plot growth data (comprehension)

```{r fig.width=5, fig.height=2}
ggplot(subset(param_summary_all, measure == "understands"), aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

```

## Compare PAC to other predictors of AoA

```{r}

sem_formula <- as.formula("aoa ~ sem_deg")
phono_formula <- as.formula("aoa ~ phono_deg")
all_formula <- as.formula("aoa ~ frequency + length + sem_deg + phono_deg")

formulas <- list(sem_formula,  phono_formula, all_formula)

coefs_all <- data.frame()

for (formula in formulas){

#Model
model_reg <- function(data) {
   lm(formula, data = data)
}

#CI
ci_reg <- function(data) {
   confint(lm(formula, data = data))
 }

reg <- uni_scale %>%
  group_by(measure, language) %>%
  nest() %>%
  mutate(model = map(data, model_reg)) %>%
  mutate(conf = map(data, ci_reg))

coefs_form <- reg %>%
  mutate(coefs = map(model, broom::tidy)) %>%
  mutate(ci = map(conf, broom::tidy)) %>%
  select(measure, language, coefs, ci) %>%
  unnest() %>%
  select(-.rownames) %>%
  dplyr::filter(term != "(Intercept)") %>%
  rename(predictor = term) %>%
  mutate(Test = ifelse(toString(formula[3])=='frequency + length + sem_deg + phono_deg', 'Combined', 'Individual'))

 coefs_all <- bind_rows(coefs_all, coefs_form)

}

feather::write_feather(coefs_all, "saved_data/static_preds.feather")
coefs_all <- feather::read_feather("saved_data/static_preds.feather")

```

Plot for production
```{r}
plot_reg_prod <- ggplot(subset(coefs_all, measure =="produces"), aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test), 
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~language, ncol=4)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

plot_reg_prod

```

Plot for comprehension
```{r}
plot_reg_comp <- ggplot(subset(coefs_all, measure =="understands"), aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+

  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~language, ncol=4)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

plot_reg_comp

```

Regression for data aggregated across all languages

```{r}

#Regression with all predictors and language as a random effect
#reg_agg <- lme(aoa ~ frequency + length + sem_deg + phono_deg , random=~1|language,  data= uni_scale)

sem_formula <- as.formula("aoa ~ sem_deg + (1 | language)")
phono_formula <- as.formula("aoa ~ phono_deg + (1 | language)")
all_formula <- as.formula("aoa ~ frequency + length + sem_deg + phono_deg + (1 | language)")

formulas <- list(sem_formula,  phono_formula, all_formula)

coefs_agg_all <- data.frame()

for (formula in formulas){

reg_agg_prod <- lmer(formula,  data= subset(uni_scale, measure == "produces"))
reg_agg_comp <- lmer(formula,  data= subset(uni_scale, measure == "understands"))

#Extract coeficnet and confidence intervals
coef_agg_fun <- function (model, meas_name) {
conf <- confint(model, method ="Wald") 
conf <- data.frame(predictor = row.names(conf), conf) %>%
  dplyr::filter(!(predictor %in% c('.sig01', '.sigma', '(Intercept)')))

coef <- coef(summary(model))
data.frame(predictor = row.names(coef), coef) %>%
  dplyr::filter(predictor !='(Intercept)') %>%
  left_join(conf) %>%
  mutate(measure = meas_name)
}

coef_agg_prod <- coef_agg_fun(reg_agg_prod, 'production')
coef_agg_comp <- coef_agg_fun(reg_agg_comp, 'comprehension')

coef_agg_form <- coef_agg_prod %>%
  bind_rows(coef_agg_comp) %>%
  mutate(Test = ifelse(toString(formula[3])=='frequency + length + sem_deg + phono_deg + (1 | language)', 'Combined', 'Individual'))

 coefs_agg_all <- bind_rows(coefs_agg_all, coef_agg_form)

}

feather::write_feather(coefs_agg_all, "saved_data/static_preds_all.feather")
coefs_agg_all <- feather::read_feather("saved_data/static_preds_all.feather")

plot_agg <- ggplot(coefs_agg_all, aes(x = predictor, y = Estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = Estimate, col = predictor, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~measure)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

plot_agg

```
# Supplementary material

## Interaction with age

To examine interaction with age, we need to predict curve of acquisition instead of just AoA 
```{r}
#Start with reproducing Mika's analysis

predictors <- c("sem_deg", "phono_deg", "length", "frequency")
#predictors <- c("frequency", "length")
###Do we want to separate by 'form'? let's omit 'form' for now and focus on priduction (the case of understading is more problematic)

cols <- c("language", "measure", "uni_lemma", "lexical_class", "lexical_class", "defintion", "age",
          "num_true", "num_false", "prop", predictors)

load("saved_data/uni_joined.RData")
uni_joined$language <- plyr::mapvalues(uni_joined$language, 
                                 from = c("Croatian","Danish","English (American)", "French (Quebec)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))

uni_joined <- uni_joined %>%
  dplyr::filter(lexical_classes =='nouns') %>%
  rename(length = num_phons)

#Impute and scale (it's also good to have a sense of the missing data)
#uni_model_data <- uni_joined %>%
#  dplyr::filter(lexical_classes =='nouns') %>%
uni_model_data <- data_static_prop %>%
  #filter(language =="English (American)") %>%
  dplyr::filter(!is.na(uni_lemma)) %>% 
  #filter(!is.na(sem_deg)) %>% #only keep unilemmas that intersect with free association data 
  dplyr::filter(aoa > 5) %>%
  #group_by(language, measure) %>%
  group_by(measure, language) %>%
  mutate_at(vars(!!predictors), funs(as.numeric(Hmisc::impute(.)))) %>% #To fill NA 
  mutate(unscaled_age = age) %>%
  mutate_at(vars(c(!!predictors, "age")), funs(as.numeric(scale(.)))) %>%# Center and scale predictors 
  ungroup()

```

Interaction with age
```{r}
#This works for each language separately,

lang_model_fun <- function(lang, lang_data) {
   print(sprintf("Fitting glmer for %s...", lang))
   interaction_formula <- as.formula(
     #sprintf("prop ~ (age | item) +  %s",
     sprintf("cbind(num_true, num_false) ~ (age | uni_lemma) +  %s",
             paste(sprintf("age * %s", predictors), collapse = " + "))
   )

   glmer(interaction_formula, family = "binomial", data = lang_data, 
         control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e7))
         )

}

lang_models <- uni_model_data %>%
  group_by(measure, language) %>%
  nest() %>%
  mutate(model = map2(language, data, lang_model_fun))# %>%
  #mutate(conf = map2(language, data, lang_coef_fun))

all_model_fun <- function(data) {
   interaction_formula <- as.formula(
     sprintf("cbind(num_true, num_false) ~ (age | item) + (sem_deg + phono_deg + length + frequency | language) + %s",
             paste(sprintf("age * %s", predictors), collapse = " + "))
   )

   glmer(interaction_formula, family = "binomial", data = data, 
         control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e7))
         )

}

all_model <- uni_model_data %>%
  group_by(measure) %>%
  nest() %>%
  mutate(model = map(data, all_model_fun))#

all_coefs_net <- all_model %>%
  mutate(coefs = map(model, broom::tidy)) %>%
  #mutate(ci = map(conf, broom::tidy)) %>%
  select(measure, coefs) %>%
  unnest() %>%
  dplyr::filter(term != "(Intercept)", term != "age", group == 'fixed') %>%
  mutate(interaction = ifelse(grepl(":", term), "interaction with age",
                                "main effect"),
           term = gsub("age:", "", term)) %>%
  rename(predictor = term) %>%
  mutate(ci_low = estimate-1.96*std.error,
         ci_up = estimate+1.96*std.error)

lang_coefs_net <- lang_models %>%
  mutate(coefs = map(model, broom::tidy)) %>%
  #mutate(ci = map(conf, broom::tidy)) %>%
  select(measure, language, coefs) %>%
  unnest() %>%
  dplyr::filter(term != "(Intercept)", term != "age", group == 'fixed') %>%
  mutate(interaction = ifelse(grepl(":", term), "interaction with age",
                                "main effect"),
           term = gsub("age:", "", term)) %>%
  rename(predictor = term) %>%
  mutate(ci_low = estimate-1.96*std.error,
         ci_up = estimate+1.96*std.error)

mean_coefs <- lang_coefs_net %>%
  group_by(predictor, measure, interaction) %>%
  summarise(mean = mean(estimate))

```

```{r}
ggplot(lang_coefs_net, aes(x = estimate, y = predictor)) +
  #facet_grid(measure ~ interaction,  scales="free_x") +
  facet_grid(measure ~ interaction) +
  geom_point(aes(colour = predictor), size = 1, alpha = 0.4) +
  #geom_point(aes(x = mean, colour = predictor), size = 3, data = mean_coefs) +
  geom_point(aes(x = estimate, colour = predictor), size = 3, data = all_coefs_net) +
  geom_vline(xintercept = 0, color = "grey", linetype = "dashed") +
  scale_fill_solarized(guide = FALSE) +
  scale_colour_manual(guide = FALSE,
                      values = rev(solarized_palette(num_coefs))) +
  ylab("") +
  scale_x_continuous(name = "Coefficient estimate")
```

```{r fig.width=5, fig.height=2}
ggplot(data=subset(lang_coefs_net, measure== 'produces'), aes(x = predictor, y = estimate)) +
  facet_grid(~ interaction, scales="free_x") +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_up, col=language), 
                  position = position_dodge(width = .5),
                  size=0.3,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip()

ggplot(data=subset(lang_coefs_net, measure== 'understands'), aes(x = predictor, y = estimate)) +
  facet_grid(~ interaction, scales="free_x") +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_up, col=language), 
                  position = position_dodge(width = .5),
                  size=0.3,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip()

```

### 2018-07-06 helper_functions/all_helper_WG.r

@@ -1,0 +1,8 @@
+source("growth_helper.r")
+source("wb_helper_WG.r")
+source("make_pairs_helper.r")
+source("optims.r")
+source("phono_helper.r")
+source("network_creator.r")
+source("network_tester.r")
+source("stemmer.R")

### 2018-07-06 helper_functions/growth_helper.r

@@ -33,7 +33,7 @@ PAT_generator<-function(vocab_age, word_pairs){
       link_to_exist<-(word_pairs %>% filter(pair==j, item %in% exist_words, link==1))$item
       PAT_value<-sem_acq %>%
         filter(item %in% link_to_exist)
-      vocab_age$value[row_n]<- mean(PAT_value$value)
+      vocab_age$value[row_n]<- mean(PAT_value$value) #here the "mean" is the crucial thing
       row_n<-row_n+1
     }
   }
@@ -86,7 +86,11 @@ PAT_nt_generator<-function(vocab_age, word_pairs){
 ######################################################################################################################
 
 PAC_generator<- function(vocab_age, word_pairs){
+  
+  #This condition is what reduces the number of words, keeping only items that are in the list of pairs
+  #To be kept in the list of pairs, a word has to appear as a cue or as target in the free associations  
   vocab_age<- vocab_age %>% filter((item %in% word_pairs$item) | (item %in% word_pairs$pair) )
+  
   word_pairs<- word_pairs %>% filter(item %in% vocab_age$item, pair %in% vocab_age$item)
   
   item_value<- word_pairs %>% 

### 2018-07-06 helper_functions/make_pairs_helper.r

@@ -124,11 +124,11 @@ make_assoc_pairs <- function(lemma_list) {
   cue_target<- read.csv("in_files/association_cue_target.csv", as.is = T)
   # filter until words in lemma_list remain
   lemma_list<- lemma_list %>% filter((uni_lemma %in% cue_target$cue) | (uni_lemma %in% cue_target$target))
-  lemma<- lemma_list$uni_lemma
+  lemma<- lemma_list$uni_lemma #here maybe use uniqu
   cue_target<- cue_target %>% 
     filter(cue %in% lemma, 
-           target %in% lemma, 
-           normed=="YES") %>% 
+           target %in% lemma) %>% #, 
+           #normed=="YES") %>%  #Do we need this to be normed? I don't think so
     select(cue, target) %>% 
     mutate(link=1)
   

### 2018-07-06 helper_functions/network_creator.r

@@ -17,8 +17,8 @@ create_combo <- function(languages){
       select(item, definition)
     
     # make pairs of words and show whether they have connection via associative norms
-    assoc_pairs<- make_assoc_pairs(lemma_list = lemma_list)
-    phono_pairs<- make_IPA_pairs(def_list = def_list, lang = lang_name)
+    assoc_pairs<- make_assoc_pairs(lemma_list = lemma_list) # here we used the unilemma
+    phono_pairs<- make_IPA_pairs(def_list = def_list, lang = lang_name) #here we use the defintion
     
     assoc_PAC<- PAC_generator(vocab_age = aoa_frame, word_pairs = assoc_pairs) %>% 
       rename(PAC_assoc = value) %>% select(-definition, -uni_lemma)

### 2018-07-06 helper_functions/phono_helper.r

@@ -1,9 +1,10 @@
 ######################################################################################################
 # Espeak function
 Speak<- function(lang, word){
-  langs<- c("English (British)","English (American)", "Spanish", "Croatian", 
-            "Italian", "Danish", "Norwegian", "Turkish", "Slovak", "Swedish", "Russian", "German")
-  abbr <- c("en-rp", "en-us", "es", "hr", "it", "da", "no", "tr","sk", "sv","ru","de")
+  langs<- c("English (British)","English (American)", "English (Australian)", "Spanish (European)", "Spanish (Mexican)",  "Croatian", 
+            "Italian", "Danish", "Norwegian", "Turkish", "Slovak", "Swedish", "Russian", "German", "French (French)",
+            "French (Quebecois)", "Portuguese (European)", "Czech", "Greek (Cypriot)","Latvian" )
+  abbr <- c("en-rp", "en-us", "en", "es", "es", "hr", "it", "da", "no", "tr","sk", "sv","ru","de", "fr", "fr", "pt-pt","cs", "el", "lv")
   lang_abbr<- abbr[which(langs==lang)]
   IPA<- system(paste("espeak -q -v ", lang_abbr, " --ipa ", "\"", word, "\"",sep=""), intern=T)
   return(IPA)

### 2018-07-06 helper_functions/wb_helper_WG.r

@@ -1,0 +1,383 @@
+# This file contains functions used to get item data, admin data, etc. , and generate dataframes for analysis
+import_all_library<- function(){
+  library(tidyr)
+  library(purrr)
+  library(readr)
+  library(ggplot2)
+  library(langcog)
+  library(boot)
+  library(lazyeval)
+  library(dplyr)
+  library(wordbankr)
+  library(directlabels)
+  library(scales)
+  library(stringr)
+  library(lmtest)
+}
+######################################################################################################################
+get_lang_item_data <- function(lang, lang_form = "WG", lex_class = "nouns") {
+
+  item_data <- get_item_data(language = lang, form = lang_form) %>%
+    select(num_item_id, definition, type, lexical_class, uni_lemma) %>%
+    filter(type == "word", lexical_class == lex_class) %>%
+    rename(item = num_item_id)
+  
+  #Initialize every item as NA (NOT yet learnt)
+  lang_item <- item_data %>%
+    select(item, definition, uni_lemma) %>%
+    mutate(age = NA)
+  
+  return(lang_item)
+}
+
+######################################################################################################################
+# get only "useful" admin data (where comprehension is not NA)
+get_lang_admin_data <- function(lang, lang_form = "WG") {
+  #get the kids' data_id from every age
+  admin_data <- get_administration_data() %>%
+    filter(form == lang_form, !is.na(comprehension), language == lang) %>%
+    select(data_id, age) %>%
+    arrange(age)
+  
+  return(admin_data)
+}
+
+######################################################################################################################
+# See how many kids we have in every age
+get_kids_by_age <- function(admin_data) {
+  #get number of kids by age
+  nkids_by_age <- admin_data %>%
+    group_by(age) %>%
+    summarise(n = n())
+  return(nkids_by_age)
+}
+
+######################################################################################################################
+#get "produces" instrument data 
+get_lang_instr_data <- function(lang, lang_form = "WG") {
+  instr_data <- get_instrument_data(instrument_language = lang,
+                                    instrument_form = lang_form) %>%
+    filter(value == "understands") %>%
+    arrange(num_item_id) %>%
+    rename(item = num_item_id)
+  
+  return(instr_data)
+}
+
+######################################################################################################################
[…]

### 2018-07-06 models/helpers.R

@@ -13,46 +13,46 @@ var itemData = _.where(data, itemInfo)
 //prepare data for a dictionary with the utilies (freq, length, Sem_PAC, Phono_PAC)
 
 //frequency
-var value_freq  =  map(function(single){
-return _.object([single.definition], [single.freq_mika])
-}, itemData)
+//var value_freq  =  map(function(single){
+//return _.object([single.item], [single.freq])
+//}, itemData)
 
 //Length 
-var value_len  =  map(function(single){
-return _.object([single.definition], [single.length])
-}, itemData)
+//var value_len  =  map(function(single){
+//return _.object([single.item], [single.length])
+//}, itemData)
 
 //Sem PAC
 var value_PAC_assoc  =  map(function(single){
-return _.object([single.definition], [single.PAC_assoc])
+return _.object([single.item], [single.PAC_assoc])
 }, itemData)
 
 //Sem PAT
 var value_PAT_assoc  =  map(function(single){
-return _.object([single.definition], [single.PAT_assoc])
+return _.object([single.item], [single.PAT_assoc])
 }, itemData)
 
 //Phono PAC t2
 var value_PAC_phono  =  map(function(single){
-return _.object([single.definition], [single.PAC_phono_t2])
+return _.object([single.item], [single.PAC_phono_t2])
 }, itemData)
 
 //Phono PAT t2
 var value_PAT_phono  =  map(function(single){
-return _.object([single.definition], [single.PAT_phono_t2])
+return _.object([single.item], [single.PAT_phono_t2])
 }, itemData)
 
 //Also prepare data for a dictionary with "definitions" as keys and boolean "learned" as values
 var learned_pair = map(function(single){
-return _.object([single.definition], [single.learned])
+return _.object([single.item], [single.learned])
 }, itemData)
 
-//now get the "defintions"
-var word = map(function(w){_.keys(w)[0]}, value_freq)
+//now get the items
+var word = map(function(w){_.keys(w)[0]}, value_PAC_assoc)
 
 //get the utilities scores
-var util_freq = map(function(w){w[_.keys(w)[0]]}, value_freq)
-var util_len = map(function(w){w[_.keys(w)[0]]}, value_len)
[…]

### 2018-10-16 journal/ms.Rmd
new journal

@@
   gather(predictor, value, Sem:frequency) %>%
-  filter(predictor == "Sem" | predictor == "Phono")
+  dplyr::filter(predictor == "Sem" | predictor == "Phono")
 
@@
 
-plot_correlation_comp <- ggplot(subset(data_long, measure == "understands"), aes(x=value, y=aoa))+
+plot_correlation_comp <- ggplot(subset(data_long, measure == "understands" & aoa < 35), aes(x=value, y=aoa))+
   facet_grid(predictor ~ language)+#, scales = "free") +
@@
         )+
-  geom_text(data=subset(correlations, measure=="understands"), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
+  geom_text(data=subset(correlations, measure=="understands"), aes(label=paste("r=", cor, sep="")), x=3.5, y=25, size=2, fontface = "bold")+
   xlab("degree z-score") +ylab("Age")
@@
 
+<!--
+
 ```{r}
@@
 
-plot_growth_preds_prod <- ggplot(subset(growth_preds, measure == "produces"), aes(x = model , y = mean)) +
-  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
+plot_growth_preds_prod <- ggplot(subset(growth_preds, measure == "produces" & Test=='Individual'), aes(x = model , y = mean)) +
+  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
+  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
                   position = position_dodge(width = .5),
@@
   theme_few()+
-  theme(aspect.ratio = 0.7)
+  theme(aspect.ratio = 0.7) + #,+
+        #axis.text.x = element_text(size=7.5, angle=45)) +
+  scale_y_continuous(breaks =c(0,0.2))
+  #scale_y_discrete(breaks =NULL)
 
-plot_growth_preds_comp <- ggplot(subset(growth_preds, measure == "understands"), aes(x = model , y = mean)) +
-  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
+plot_growth_preds_comp <- ggplot(subset(growth_preds, measure == "understands" & Test=='Individual'), aes(x = model , y = mean)) +
+  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
+  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
                   position = position_dodge(width = .5),
@@
   theme_few()+
-  theme(aspect.ratio = 0.7)
+  theme(aspect.ratio = 0.7) +
+  scale_y_continuous(breaks =c(0,0.2))
 
@@
 
-```{r growthPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Evaluation of network growth scenarios, for both A) production and B) comprehension.
-We plot values when predictors are evaluted individually (dotted), and when combined in the same growth model (solid).
-Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\\% credible intervals (computed using the highest density intervals).
-Positive values mean that learning proceeds according to the predictions of the growth scenario.
-Negative values mean that learning proceeds in opposition to the predictions of the growth scenario."}
+-->
 
-legend <- get_legend(plot_growth_preds_prod)
+```{r}
+##Test
+growth_preds <- feather::read_feather("../saved_data/growth_preds.feather")
 
-plot_noLegend <- plot_grid(plot_growth_preds_prod + theme(legend.position="none"), NULL, plot_growth_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+growth_preds$model <- plyr::mapvalues(growth_preds$model, 
+                                 from = c("semPAC","semPAT","phonoPAC", "phonoPAT"), 
+                                 to = c("semEXT","semINT","phonoEXT", "phonoINT"))
 
-plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))
+growth_preds$measure <- plyr::mapvalues(growth_preds$measure, 
+                                 from = c("produces","understands"), 
+                                 to = c("production","comprehension"))
+
+plot_growth_preds <- ggplot(subset(growth_preds, Test=='Individual'), aes(x = model , y = mean)) +
+  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=measure),
+  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  coord_flip() +
+  facet_wrap( ~ language, ncol=5) +
+  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
+  scale_colour_solarized() +
+  theme_few()+
+  theme(aspect.ratio = 0.7) + #,+
+        #axis.text.x = element_text(size=7.5, angle=45)) +
+  scale_y_continuous(breaks =c(0,0.2))  +
+  #scale_y_discrete(breaks =NULL)
+  ylab("Estimate") +xlab("Mechanism")
+
+#plot_growth_preds
+```
+
+```{r growthPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Evaluation of growth scenarios (EXT: externally-driven, INT: internally-driven) for both semantic and phonological networks.
+Each point represents the mean of the posterior distribution of the growth parameter, with ranges representing 95\\% credible intervals.
+Positive values mean that learning proceeds according to the predictions of the growth scenario, whereas negative values mean that learning proceeds in opposition to the predictions of the growth scenario."}
+
+#legend <- get_legend(plot_growth_preds_prod)
+
+#plot_noLegend <- plot_grid(plot_growth_preds_prod + theme(legend.position="none"), NULL, plot_growth_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+#plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))
+
+#plot_noLegend <- plot_grid(plot_growth_preds_prod, NULL, plot_growth_preds_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+#plot_grid(plot_noLegend)
 
 #knitr::include_graphics("figs/plot_growth_preds_prod.pdf")
+
+plot_growth_preds
 
@@
 ```{r}
+##Test
 static_preds <- feather::read_feather("../saved_data/static_preds.feather")
 
-plot_static_preds_prod <- ggplot(subset(static_preds, measure =="produces"), aes(x = predictor, y = estimate)) +
-  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test), 
+static_preds$predictor <- plyr::mapvalues(static_preds$predictor, 
+                                 from = c("sem_deg","phono_deg","frequency", "length"), 
+                                 to = c("semEXT","phonoEXT", "frequency", "length"))
+
+static_preds$measure <- plyr::mapvalues(static_preds$measure, 
+                                 from = c("produces","understands"), 
+                                 to = c("production","comprehension"))
+
+plot_static_preds <- ggplot(subset(static_preds, Test=='Combined'), aes(x = predictor , y = estimate)) +
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., col = predictor, linetype=measure),
+  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  coord_flip() +
+  facet_wrap( ~ language, ncol=5) +
+  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
+  scale_colour_solarized() +
+  theme_few()+
+  theme(aspect.ratio = 0.7) + #,+
+        #axis.text.x = element_text(size=7.5, angle=45)) +
+  scale_y_continuous(breaks =c(0,0.2))  +
+  #scale_y_discrete(breaks =NULL)
+  ylab("Estimate") +xlab("Mechanism")
+
+plot_static_preds
+
+```
+<!--
+```{r}
+static_preds <- feather::read_feather("../saved_data/static_preds.feather")
+
+plot_static_preds_prod <- ggplot(subset(static_preds, measure =="produces" & Test =="Combined"), aes(x = predictor, y = estimate)) +
+  #geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test), 
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor),
                   position = position_dodge(width = .5),
@@
 
-plot_static_preds_comp <- ggplot(subset(static_preds, measure =="understands"), aes(x = predictor, y = estimate)) +
-  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test),
+plot_static_preds_comp <- ggplot(subset(static_preds, measure =="understands" & Test =="Combined"), aes(x = predictor, y = estimate)) +
+  #geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test),
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor),
                   position = position_dodge(width = .5),
@@
 ```
+-->
 
-```{r staticPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of predictor coefficients by language in production (A) and comprehension (B), with ranges indicating 95\\% confidence intervals.
+```{r staticPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined regression model.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\\% confidence intervals.
 Positive values indicate a positive relationship (e.g.
@@
 
-legend <- get_legend(plot_static_preds_prod)
+#legend <- get_legend(plot_static_preds_prod)
 
-plot_noLegend <- plot_grid(plot_static_preds_prod + theme(legend.position="none"), NULL, plot_static_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+#plot_noLegend <- plot_grid(plot_static_preds_prod + theme(legend.position="none"), NULL, plot_static_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
 
-plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))
+#plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))
 
-#plot_static_preds_prod
+#plot_noLegend <- plot_grid(plot_static_preds_prod, NULL, plot_static_preds_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+#plot_grid(plot_noLegend)
+
+plot_static_preds
 
@@
 
+<!--
 ### What is the relative contribution of each growth model?
@@
 static_preds_all <- feather::read_feather("../saved_data/static_preds_all.feather")
+
+static_preds_all$predictor <- plyr::mapvalues(static_preds_all$predictor, 
+                                 from = c("sem_deg","phono_deg","frequency", "length"), 
+                                 to = c("semEXT","phonoEXT","frequency", "length"))
 
@@
 ```
+
+-->
 
@@
 Another important difference is the number of words tested: Our study uses a larger set of nouns.} Despite these cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.
-
-## Does the network's effect change with age?
-
-As a final analysis, we examined  whether the effect of semantic and phnonological networks change over development. @braginsky2016 found that
 

### 2018-10-16 journal/ms.tex
new journal

@@
 
+  \usepackage{graphicx}
+  \makeatletter
+  \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+  \def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+  \makeatother
+  % Scale images if necessary, so that they will not overflow the page
+  % margins by default, and it is still possible to overwrite the defaults
+  % using explicit options in \includegraphics[width, height, ...]{}
+  \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 \ifxetex
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/growthPred-1} \caption{Evaluation of network growth scenarios, for both A) production and B) comprehension.
-We plot values when predictors are evaluted individually (dotted), and when combined in the same growth model (solid).
-Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\% credible intervals (computed using the highest density intervals).
-Positive values mean that learning proceeds according to the predictions of the growth scenario.
-Negative values mean that learning proceeds in opposition to the predictions of the growth scenario.}\label{fig:growthPred}
+\includegraphics[width=\textwidth]{ms_files/figure-latex/growthPred-1} \caption{Evaluation of growth scenarios (EXT: externally-driven, INT: internally-driven) for both semantic and phonological networks.
+Each point represents the mean of the posterior distribution of the growth parameter, with ranges representing 95\% credible intervals.
+Positive values mean that learning proceeds according to the predictions of the growth scenario, whereas negative values mean that learning proceeds in opposition to the predictions of the growth scenario.}\label{fig:growthPred}
 \end{figure}
@@
 
+\includegraphics{ms_files/figure-latex/unnamed-chunk-6-1.pdf}
+
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPred-1} \caption{Estimates of predictor coefficients by language in production (A) and comprehension (B), with ranges indicating 95\% confidence intervals.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPred-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined regression model.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\% confidence intervals.
 Positive values indicate a positive relationship (e.g.
@@
 words with higher frequency tend to have a lower AoA).}\label{fig:staticPred}
-\end{figure}
-
-\subsubsection{What is the relative contribution of each growth
-model?}\label{what-is-the-relative-contribution-of-each-growth-model}
-
-Above we evaluated the network growth scenarios individually. As a next
-step, we analyzed their relative contribution to the learning process.
-This was done through adding more fitted parameters to the model, that
-is, by substituting \(\beta d_i\) in formula (1) with:
-\[\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}\]
-where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and
-PhonoPAC. Using the same fitting technique, we obtained the values shown
-in Figure \ref{fig:pred_ind}. PAC dominates the learning. Both
-phonological and semantic networks contribute to lexical growth, but the
-phonological network appears to be stronger and more consistent across
-languages. In summary, the findings show that both semantic and
-phonological networks contribute to the learning process, and that they
-both grow primarily by PAC, relying on the external connectivity in the
-learning environment, rather than the internal connectivity in the
-acquired lexicon.
-
-\begin{figure}[!h]
-\includegraphics[width=\textwidth]{figs/plot_static_preds_all} \caption{Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect for both production and comprehension.
-Ranges indicate 95\% confidence intervals.
-Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates.}\label{fig:staticAll}
 \end{figure}
@@
 
-\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/WordRec}}}
+\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}}
 \vspace{1em}

### 2018-10-16 main_analyses.Rmd
new journal

@@
 #feather::write_feather(data_growth, "saved_data/data_growth.feather")
-#data_growth <- feather::read_feather("saved_data/data_growth.feather") 
+data_growth <- feather::read_feather("saved_data/data_growth.feather") 
 ```

### 2018-10-16 helper_functions/growth_helper.r

@@ -3,6 +3,7 @@
 # column name: 
 # item, item.definition, pair, pair.definition, link
 
+
 PAT_generator<-function(vocab_age, word_pairs){
   vocab_age<-vocab_age %>%
     filter(item %in% word_pairs$item) %>%
@@ -13,7 +14,7 @@ PAT_generator<-function(vocab_age, word_pairs){
     summarise(n=n()))$age
   ages<- all_ages[2:length(all_ages)]
   for (i in ages){
-    #current items in this age
+    #current items in this age 
     curr_items<- (vocab_age %>%
                     filter(age==i) %>%
                     select(item))$item
@@ -30,6 +31,8 @@ PAT_generator<-function(vocab_age, word_pairs){
     row_n<-which(vocab_age$age==i & vocab_age$item==curr_items[1])
     for (j in curr_items){
       #calculating d
+      
+      #here determine the nodes to which candidate word "j" is related
       link_to_exist<-(word_pairs %>% filter(pair==j, item %in% exist_words, link==1))$item
       PAT_value<-sem_acq %>%
         filter(item %in% link_to_exist)

### 2018-10-16 helper_functions/make_pairs_helper.r

@@ -138,7 +138,10 @@ make_assoc_pairs <- function(lemma_list) {
   
   #make a association network dataframe with item number
   #rename stuffs so it could conform to the format PAT_generator needs
-  #item corresponds to target ;  pair corresponds to cue
+  
+  #item corresponds to target ;  pair corresponds to cue: 
+  #it is important to keep that in mind becuase later will compute 'incoming' degree:
+  #for each item (target), we will sum the pairs (cues)
   assoc_link <- assoc_table %>%
     rename(pair.definition = cue) %>%
     left_join(lemma_list, c("pair.definition" = "uni_lemma")) %>%

### 2018-10-23 journal/ms.Rmd
journal

@@
 Besides these word-level properties, the lexical structure (that is, how words relate to each other) also influences the age of acquisition of words.
-The lexical structure is best characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words.
+The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words (Collins and Loftus, 1975).
 Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological similarity.
-These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017].
+These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017] add Beckage, 2011 and other people...
 
@@
 In particular, @steyvers2005 suggested that the observed effects of connectivity are the consequence of how the lexical network gets constructed in the child's mind.
-According to this explanation, known as Preferential Attachment (PAT), highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99].
+According to this explanation, known as Preferential Attachment, highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99].
 In other words, what predicts word learning is the *internal* connectivity in the child's early lexicon.
 In contrast, @hills2009 suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment.
-They called this alternative explanation Preferential Acquisition (PAC).
+They called this alternative explanation Preferential Acquisition.
+For clarity of reading, we will rename these scenarios in a ways that reflects how their modes of operation contrast with each other.
+We will call preferential attachment the Internally-driven mechanism (INT), and preferential acquisition the Externally-driven mechanism (EXT).
 Figure\ \@ref(fig:growth) shows an illustration of both growth scenarios with the same simplified network.
 These two proposals represent two divergent ideas about the role of lexical networks in acquisition.
-On the PAT proposal, network structure is a causal factor in early word learning; in contrast, on the PAC approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguistic input.
+On the INT proposal, network structure is a causal factor in early word learning; in contrast, on the EXT approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguistic input.
 
-```{r growth, fig.cap = "Illustration of the growth scenarios.
-Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
+```{r growth, fig.cap = "Illustration of the two growth scenarios.
+Filled circles (I1-I4) represent known words (Internal), and empty circles (E1 and E2) represent words that have not been learned yet (External).
 Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
-For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
-Thus, according to PAT, the node E1 is more likely to enter the lexicon first.
-For PAC, the utility of a candidate node is its degree in the entire network.
-According to PAC, the node E2 is more likely to enter the lexicon first.", fig.align = "center", out.width = "400px"}
+For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
+Thus, according to INT, the node E1 is more likely to enter the lexicon first.
+For EXT, the utility of a candidate node is its degree in the entire network.
+According to EXT, the node E2 is more likely to enter the lexicon first.", fig.align = "center", out.width = "400px"}
 knitr::include_graphics("figs/growth2.png")
@@
 
-Studies that investigate lexical network growth have focused on semantic networks using English data [@steyvers2005; @hills2009; @hills2010].
+@hills2009 found that early networks do not grow through INT as was originally hypothesised by @steyvers2005, but rather through EXT.
+This finding, though potentially very profound, has only been estabished in the special case of networks that are 1) based on semantic associations, 2) use data from English-learning children, and 3) consider word production as a measure of acqusition.
+Thus, it could be that the result depends on the domain, culture or/and the measure.
+In this work, we test the generality of the finding along these three dimesnions.
+
+First, we investigte the mechanism that underlies the growth of phonological networks.
+Previous studies have analyzed various strcutural properties of adults phonological networks, and found that some of these properties influence the language processes of word recognition and production as well as language-related memory processes (Vitevitch, 2008; Luce & Pisoni, 1998; Chan & Vitevitch, 2009; Chan & Vitevitch,2010; Vitevitch, Chan, and Roodenrys, 2012; Castro et al.
+2018).
+More relvant to our study is the research that investigates learning in children, and in particualr the finding that words' connectivity in a phonological network is negatively correlated with their age of learning in children (Stokes 2004; Storkel, 2004, 2009).
+In other words, the finding suggests that words learned earlier tend to sound similar to many other words than a word learned later in life.
+This finding is similar to semantics however, does not address the question of the learning mechanism.
+In fact, as with semantic networks, the fact that the connectivity in the end-state network predicts AoA can be the outcome of both the internallay- and externally-driven mechanisms (Hills et al.
+2009).
+
+Second, we test how the proposed growth mechanims predict word comprehension as compared to production.
+These two measures differ in their assessment of vocabulary composition (e.g., Benedict, 1979).
+Testing both measures is critical as it allows us to investigate the extent to which the mechanism  is infleunced by production constraints (i.e., how difficult a word is to say) as compared to comprehension constraints (i.e., how difficult it is to store or access).
+If there is consistency across both measures, this would suggest that the growth mechanism captures learning patterns beyond these specific constraints.
+
+Finally, we use developmental data of children in 10 cultures.
+Such cross-linguistic comparison is crucial to test what growth mechanism is cognitively universal and is used by all children, and what mechansism is specific to some patterns of learning that emerge due to the particulars of a given language or culture (Bates & MacWhinney, 1987; Slobin, 1985).
+More precisely, we test whether Hill's finding with English-learning data generalize to other languages, and we test whether this generalization holds for both the semantic and phonological networks, and for both the comprehension and production data.
+
+we test the growth mechanim in the phonological domain.
+Although previous results showed that ...
+(Storkel,), the growth mechanim has never been tested.
+The outcome could enrich the debate as to whether children first learn the words that  (Here I should read the Dautrich paper).
+Second, we use developmental data collected from children in 10 cultures.
+Third, we compare results  using production and comprehension as measures of acuquition.
+
+Why phonological domain is important
+Why languages are important
+Why comprehension is important
+
+whether phonological networks, like semantic networks, grow by , or if they rather grow by P
+
+Studies that investigate lexical network growth have focused on semantic networks using the English vocabulary and development data based on word production. In particualr,
+
+However, the lexicon is not only strctured semantically
+
+Our work expands this previous research in three ways: 1) we test whether
+
 The novelty of the current study is threefold:  First, it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT.
@@
 
-plot_static_preds
-
 ```
@@
 
+-->
+
 ```{r}
@@
 
-```{r staticAll, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect for both production and comprehension.
+```{r staticAll, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect.
+Results are shown for both production and comprehension data.
 Ranges indicate 95\\% confidence intervals.
-Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates."}
+Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect."}
 
@@
 ```
-
--->
 

### 2018-10-23 journal/ms.tex
journal

@@
 
-  \usepackage{graphicx}
-  \makeatletter
-  \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-  \def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-  \makeatother
-  % Scale images if necessary, so that they will not overflow the page
-  % margins by default, and it is still possible to overwrite the defaults
-  % using explicit options in \includegraphics[width, height, ...]{}
-  \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 \ifxetex
@@
 words relate to each other) also influences the age of acquisition of
-words. The lexical structure is best characterized in terms of a network
+words. The lexical structure can be characterized in terms of a network
 where each node represents a word in the vocabulary, and each link
 between two nodes represents a relationship between the corresponding
-pair of words. Previous studies have investigated early vocabulary
-structure by constructing networks using a variety of word-word
-relations including shared semantic features, target-cue relationships
-in free association norms, co-occurrence in child directed speech, and
-phonological similarity. These studies have found that children tend to
-produce words that have higher neighborhood density (i.e., high
-connectivity in the network) earlier, both at the phonological and the
-semantic level (Engelthaler \& Hills, 2017; Hills, Maouene, Riordan, \&
-Smith, 2010; Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Stella,
-Beckage, \& Brede, 2017; Storkel, 2009).
+pair of words (Collins and Loftus, 1975). Previous studies have
+investigated early vocabulary structure by constructing networks using a
+variety of word-word relations including shared semantic features,
+target-cue relationships in free association norms, co-occurrence in
+child directed speech, and phonological similarity. These studies have
+found that children tend to produce words that have higher neighborhood
+density (i.e., high connectivity in the network) earlier, both at the
+phonological and the semantic level (Engelthaler \& Hills, 2017; Hills,
+Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya, \&
+Smith, 2009; Stella, Beckage, \& Brede, 2017; Storkel, 2009) add
+Beckage, 2011 and other people\ldots{}
 
@@
 gets constructed in the child's mind. According to this explanation,
-known as Preferential Attachment (PAT), highly connected words in the
-child's lexicon tend to \enquote{attract} more words over time, in a
+known as Preferential Attachment, highly connected words in the child's
+lexicon tend to \enquote{attract} more words over time, in a
 rich-get-richer scenario (Barabasi \& Albert, 1999). In other words,
@@
 environment. They called this alternative explanation Preferential
-Acquisition (PAC). Figure~\ref{fig:growth} shows an illustration of both
+Acquisition. For clarity of reading, we will rename these scenarios in a
+ways that reflects how their modes of operation contrast with each
+other. We will call preferential attachment the Internally-driven
+mechanism (INT), and preferential acquisition the Externally-driven
+mechanism (EXT). Figure~\ref{fig:growth} shows an illustration of both
 growth scenarios with the same simplified network. These two proposals
 represent two divergent ideas about the role of lexical networks in
-acquisition. On the PAT proposal, network structure is a causal factor
-in early word learning; in contrast, on the PAC approach, network
+acquisition. On the INT proposal, network structure is a causal factor
+in early word learning; in contrast, on the EXT approach, network
 structure is not internally represented and, therefore, might be an
@@
 
-\caption{Illustration of the growth scenarios.
-Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
+\caption{Illustration of the two growth scenarios.
+Filled circles (I1-I4) represent known words (Internal), and empty circles (E1 and E2) represent words that have not been learned yet (External).
 Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
-For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
-Thus, according to PAT, the node E1 is more likely to enter the lexicon first.
-For PAC, the utility of a candidate node is its degree in the entire network.
-According to PAC, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
+For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
+Thus, according to INT, the node E1 is more likely to enter the lexicon first.
+For EXT, the utility of a candidate node is its degree in the entire network.
+According to EXT, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
 \end{figure}
 
+Hills et al. (2009) found that early networks do not grow through INT as
+was originally hypothesised by Steyvers and Tenenbaum (2005), but rather
+through EXT. This finding, though potentially very profound, has only
+been estabished in the special case of networks that are 1) based on
+semantic associations, 2) use data from English-learning children, and
+3) consider word production as a measure of acqusition. Thus, it could
+be that the result depends on the domain, culture or/and the measure. In
+this work, we test the generality of the finding along these three
+dimesnions.
+
+First, we investigte the mechanism that underlies the growth of
+phonological networks. Previous studies have analyzed various strcutural
+properties of adults phonological networks, and found that some of these
+properties influence the language processes of word recognition and
+production as well as language-related memory processes (Vitevitch,
+2008; Luce \& Pisoni, 1998; Chan \& Vitevitch, 2009; Chan \&
+Vitevitch,2010; Vitevitch, Chan, and Roodenrys, 2012; Castro et al.
+2018). More relvant to our study is the research that investigates
+learning in children, and in particualr the finding that words'
+connectivity in a phonological network is negatively correlated with
+their age of learning in children (Stokes 2004; Storkel, 2004, 2009). In
+other words, the finding suggests that words learned earlier tend to
+sound similar to many other words than a word learned later in life.
+This finding however, does not address the question of the learning
+mechanism. In fact, as with semantic networks, the fact that the
+connectivity in the end-state network predicts AoA can be the outcome of
+both the internallay- and externally-driven mechanisms (Hills et al.
+2009).
+
+Second, we test how the proposed growth mechanims predict word
+comprehension as compared to production. These two measures differ in
+their assessment of vocabulary composition (e.g., Benedict, 1979).
+Testing both measures is critical as it allows us to investigate the
+extent to which the mechanism is infleunced by production constraints
+(i.e., how difficult a word is to say) as compared to comprehension
+constraints (i.e., how difficult it is to store or access). If there is
+consistency across both measures, this would suggest that the growth
+mechanism captures learning patterns beyond these specific constraints.
+
+Finally, we use developmental data of children in 10 cultures. Such
+cross-linguistic comparison is crucial to test what growth mechanism is
+cognitively universal and is used by all children, and what mechansism
+is specific to some patterns of learning that emerge due to the
+particulars of a given language or culture (Bates \& MacWhinney, 1987;
+Slobin, 1985). More precisely, we test whether Hill's finding with
+English-learning data generalize to other languages, and we test whether
+this generalization holds for both the semantic and phonological
+networks, and for both the comprehension and production data.
+
+we test the growth mechanim in the phonological domain. Although
+previous results showed that \ldots{} (Storkel,), the growth mechanim
+has never been tested. The outcome could enrich the debate as to whether
+children first learn the words that (Here I should read the Dautrich
+paper). Second, we use developmental data collected from children in 10
+cultures. Third, we compare results using production and comprehension
+as measures of acuquition.
+
+Why phonological domain is important Why languages are important Why
+comprehension is important
+
+whether phonological networks, like semantic networks, grow by , or if
+they rather grow by P
+
 Studies that investigate lexical network growth have focused on semantic
-networks using English data (Hills et al., 2010, 2009; Steyvers \&
-Tenenbaum, 2005). The novelty of the current study is threefold: First,
-it investigates whether phonological networks, like semantic networks,
-grow by PAC, or if they rather grow by PAT. Second, it provides a
-systematic comparison of both network growth scenarios in the
-phonological and the semantic domains and assesses their relative
-contribution to the learning process. Third, it tests the generality of
-the findings across eight languages.
+networks using the English vocabulary and development data based on word
+production. In particualr,
+
+However, the lexicon is not only strctured semantically
+
+Our work expands this previous research in three ways: 1) we test
+whether
+
+The novelty of the current study is threefold: First, it investigates
+whether phonological networks, like semantic networks, grow by PAC, or
+if they rather grow by PAT. Second, it provides a systematic comparison
+of both network growth scenarios in the phonological and the semantic
+domains and assesses their relative contribution to the learning
+process. Third, it tests the generality of the findings across eight
+languages.
 
@@
 
-\includegraphics{ms_files/figure-latex/unnamed-chunk-6-1.pdf}
-
 \begin{figure}[!h]
@@
 words with higher frequency tend to have a lower AoA).}\label{fig:staticPred}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{figs/plot_static_preds_all} \caption{Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\% confidence intervals.
+Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAll}
 \end{figure}

### 2018-10-26 journal/ms.Rmd
journal

--- 2018-10-16 journal/ms.Rmd
@@
 Besides these word-level properties, the lexical structure (that is, how words relate to each other) also influences the age of acquisition of words.
-The lexical structure is best characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words.
+The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words (e.g., Collins and Loftus, 1975).
 Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological similarity.
-These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017].
+These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017] add Beckage, 2011 and other people...
 
@@
 In particular, @steyvers2005 suggested that the observed effects of connectivity are the consequence of how the lexical network gets constructed in the child's mind.
-According to this explanation, known as Preferential Attachment (PAT), highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99].
+According to this explanation, known as Preferential Attachment, highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99].
 In other words, what predicts word learning is the *internal* connectivity in the child's early lexicon.
 In contrast, @hills2009 suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment.
-They called this alternative explanation Preferential Acquisition (PAC).
+They called this alternative explanation Preferential Acquisition.
+For clarity of reading, we will call preferential attachment the Internally-driven mechanism (INT), and preferential acquisition the Externally-driven mechanism (EXT).
 Figure\ \@ref(fig:growth) shows an illustration of both growth scenarios with the same simplified network.
 These two proposals represent two divergent ideas about the role of lexical networks in acquisition.
-On the PAT proposal, network structure is a causal factor in early word learning; in contrast, on the PAC approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguistic input.
+On the INT proposal, network structure is a causal factor in early word learning; in contrast, on the EXT approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguistic input.
 
-```{r growth, fig.cap = "Illustration of the growth scenarios.
-Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
+```{r growth, fig.cap = "Illustration of the two growth scenarios.
+Filled circles (I1-I4) represent known words (Internal), and empty circles (E1 and E2) represent words that have not been learned yet (External).
 Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
-For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
-Thus, according to PAT, the node E1 is more likely to enter the lexicon first.
-For PAC, the utility of a candidate node is its degree in the entire network.
-According to PAC, the node E2 is more likely to enter the lexicon first.", fig.align = "center", out.width = "400px"}
+For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
+Thus, according to INT, the node E1 is more likely to enter the lexicon first.
+For EXT, the utility of a candidate node is its degree in the entire network.
+According to EXT, the node E2 is more likely to enter the lexicon first.", fig.align = "center", out.width = "400px"}
 knitr::include_graphics("figs/growth2.png")
@@
 
-Studies that investigate lexical network growth have focused on semantic networks using English data [@steyvers2005; @hills2009; @hills2010].
-The novelty of the current study is threefold:  First, it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT.
-Second, it provides a systematic comparison of both network growth scenarios in the phonological and the semantic domains and assesses their relative contribution to the learning process.
-Third, it tests the generality of the findings across eight languages.
+@hills2009 found that early lexical networks do not grow through INT as was originally hypothesised by @steyvers2005, but rather through EXT.
+This finding, though potentially very profound, has only been estabished in the special case of networks that are based on 1) semantic associations,  2) word production as a measure of acquisition, and 2) data from English-learning children, only.
+The extent to which this result depends on the domain, the measure and culture/languagae is still unclear.
+In this work, we test the generality of the finding along these three dimesnions.
+
+First, we study the phonological network in addition to the semantic network.
+These two networks represent different ways the mental lexicon is strcutured.
+In particular, words that are neighbors in the semantic network (e.g., "cat", "dog") are not necessarily neighbors in the phonological network, and vice versa.
+Does the phonological network also influence word learning?
+Previous work did find an effect of words' connectivity in the phonological network on their age of learning (Storkel, 2004, 2009; Stokes 2014).
+In other words, words learned earlier in life tend to sound similar to many other words than a word learned later in life.
+However, as mentioned above, this finding did not examine the underlying learning mechanism.\footnote{In particular, this finding is compatible with both INT and EXT.} Here, we investigate whether phonological networks, like semantic networks, grow through EXT, or if they rather grow via INT (Figure\ \@ref(fig:growth)).
+<!--
+The phonological strcuture influence word processing in adults (Vitevitch, 2008;  Chan & Vitevitch, 2009; Chan & Vitevitch,2010; Vitevitch, Chan, and Roodenrys, 2012; Castro et al.
+2018).
+Here we test whether the mechanism of networtk growth in the phonological domains mirrors the mechanism found in the semantic domains.
+-->
+
+Second, we study vocabularies measured using both comprehension and production.
+Previous studies have found differences between these vocabularies in terms of their content and rate of acquistion (Benedict, 1979; Fensen et al.
+1993).
+These differences can be due to the fact that comprehension and production do not share the same contraints.
+For instance, whereas comprehension depends on the ease with which words are stored and accessed, production depends additionally on the ease with witch words are articuated (e.g., shorter words are produced earlier, Braginsky et al.
+2016).
+By including comprehension-based vocabularies in our analysis, we assess the extent to which the network growth mechanisms capture general learning patterns beyond the specific constraints of production.
+
+Finally, we use developmental data in 10 languages.
+Lexical networks can show more or less cross-lingustic variability along both the semantic and phonological domains (Youn et al.
+2015; Arbesman et al.
+2009).\footnote{The difference is more obvious in the phonolgical case where the network strcuture––and the distribution of word connectivity––can a priori change from language to language depending on various languisitc conventions.} Besides, cultures might differ in the way caregivers guide the chidlren's learning patterns or in the way the adults' linguistic input is organized (Kuhl et al., 1997; Cristia et al.
+2017), and this difference could influecne the learning mechanism.
+Thus, Cross-linguistic comparison is crucial to test what mechanism is cognitively universal and is used by all children, and what mechansism is specific to some patterns of learning that emerge due to the particulars of a given language or culture (Bates & MacWhinney, 1987; Slobin, 1985).
+
+HERE ORGANIZATION OF THE PAPER
 
 # Networks
+
 ## Data
+
 We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist.
 Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94].
-We used the *Words and Sentences* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months).
-Following previous studies [@storkel2009; @hills2009], we restricted our analysis to nouns.
-We defined the age of acquisition of a given word by the month at which this word was produced by at least 50% of children [@goodman2008], and we excluded nouns that have not been learned (according to this criterion) by the last month for which we have CDI data.
+When filling out a CDI form, caregivers are either invited to indicate whether their child “understands” (comprehension) or “understands and says” (production) for each of about 400 words.
+For youner chidlren (between 8 and 18 months), both comprehension and production are queried, whereas for oder chidlren (between 16 to 36 months) only production is queried.
+We use data from younger chidlren to test comprehension and data from older chidlren to test production.
+Following previous studies [@storkel2009; @hills2009], we restrict our analysis to nouns.
+Table \@ref(tab:stats) gives an overview of the data source.
 
-We obtained these nouns in eight languages: Croatian, Danish, English, Italian, Norwegian, Russian, Spanish, and Turkish.
+## Age of acquisition
+For each word in CDI data, we compute the proportion of children who understand or produce the word at each month.
+Then we fit a logistic curve to these proportions and determined when the curve crosses 0.5, i.e., the age at which at lest 50% of chidlren know the word.
+We take this point in time to be each word’s age of acquisition [@goodman2008] and Braginsky.
+
+<!--We obtained these nouns in ten languages: Croatian, Danish, English, French, Italian, Norwegian, Russian, Spanish, Swedish, and Turkish.
 We used the subset of nouns that had entries in the Florida Association Norms (see below).
@@
 Table \@ref(tab:stats) gives an overview of the data used.
-Translation equivalents were originally constructed for a subset of words appearing on the toddler CDI form, and so not all words are currently available.
-Note, however, that all languages have at least 60% of nouns translated.
+-->
 
@@
 
-# Semantic networks
+## Semantic networks
 
-We constructed semantic networks following the procedure outlined in @hills2009.
+We constructed semantic networks for English data following the procedure outlined in @hills2009.
 We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998].
@@
 
+Free Association norms are available only in English.
+We used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across languages.
+Note that this does not necessarily mean that the resulting networks will be the same across languages, or that these networks will grow similarly.
+Though using the same association data acoss langauges assumes that the semantic similarity measure is universal (which is a reasonable approximation, Youn et al.
+2015), the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possbility different learing strategies.
+
 ## Phonological networks
 
-We generated approximate International Phonetic Alphabet (IPA) transcriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes.
+To construct phonological networks we first mapped the orthogrphic transcrition of words to their International Phonetic Alphabet (IPA) transcriptions, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes.
 The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.
@@
 We start by analyzing word connectivity in the global (static) network.
-We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds to the network by 30 months).
-This global network is the end-state towards which both PAT and PAC should converge by the last month of learning.
+We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds, in comprehension, to the network by 18 months, and in production, to the network by 30 months).
+This global network is the end-state towards which both INT and EXT converge by the last month of learning.
 Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment.
-Below we analyze properties of this global networks that are relevant to PAC and/or PAT.
+Below we analyze properties of this global networks that are relevant to INT and/or EXT.
 
@@
 
-Connectivity in the global network is directly related to PAC as it represents the explicit criterion PAC uses to determine what words should be learned first (Figure \@ref(fig:growth)).
-Therefore, a direct consequence of a PAC-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed.
+Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \@ref(fig:growth)).
+Therefore, a direct consequence of a EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with INT, although the causality is reversed.
 Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around.
-Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \@ref(fig:corrAll) shows how the age of production (A) and comprehension (B) for each word varies as a function of its degree (or indegree for the semantic network).
+Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \@ref(fig:corrAll) shows how the age of production (A) and comprehension (B) for each word varies as a function of its degree (or indegree for the semantic networks).
 For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages.
 The plots show, overall, a negative correlation between the month of acquisition and the degree, indicating that nouns with higher degrees are generally learned earlier.
+HERE MENTION THE AVERAGE VALUE OF THE CORRELATIONS
 
@@
 
-###Power-law degree distribution?
+###Power-law degree distribution
+
 We also analyzed the global network's degree distribution.
-The shape of this distribution is particularly relevant to PAT as this growth scenario is known to generate networks with a power-law degree distribution [i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$, @barabasi99].
-If the network displays this property, this fact would suggest a PAT-like generative process.
-Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for PAT.
+The shape of this distribution is particularly relevant to INT as this growth scenario is known to generate networks with a power-law degree distribution [i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$, @barabasi99].
+If the network displays this property, this fact would suggest a INT-like generative process.
+Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for INT.
 The log-log plots are shown in Figure \@ref(fig:degreeDist).
 We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using the related R package [poweRlaw, @gillespie15].
+
 In brief, the analysis consisted in two steps.
@@
 Second we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model.
-The results are shown in Appendix 1, table XX.
+
+The results are shown in table XX.
 Overall, we could not reject the null hypothesis of a power-law distribution: the $p$-value was generally above 0.1.
+Also talk about the fact that the power law is truncated.
 
-In sum, the static properties of the global network are *a priori* compatible with both PAT and PAC.
+In sum, the static properties of the global network are *a priori* compatible with both INT and EXT.
 In order to decide between these two developmental scenarios, we need to fit explicit growth models to the data.
@@
 
-For the semantic networks, the results replicate Hills et al.'s finding in English, which is that the semantic network grows by PAC, not by PAT.
-Moreover, this finding holds in seven of the eight languages we examined.\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
-However, our findings do not support this assumption as the effects were generally similar in magnitude cross-linguistically.} The PAC model also fits better than PAT for phonological networks.
-We note however that PAT, though weaker, fares  better for the phonological networks (where it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian) than it does for the semantic networks (where it is rather universally unpredictive).
+The results replicate Hills et al.'s finding regarding the semantic netowrk in English and prouction data, which is that this network grows by EXT, not by INT.
+Besides, this finding generalize to comprehension, and holds overall across languages.
+One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
+However, our findings do not support this assumption, rather it supports our intial approximation, albeit a posteriori, about the unversisality of the semantic similarity measure.
+In the phonological domain, the EXT model also fits better the data than INT for both production and comprehension.
+Similar to the sematic domain, the findings generalize well cross-linguistically.
 
@@
   ylab("Estimate") +xlab("Mechanism")
-
-plot_static_preds
 
@@
 
--->
-
 ## Comparison to other predictors of age of acquisition
 
-We saw that the way semantic and phonological information is structured in the learning environment (i.e., PAC) contributes to noun learning across languages.
+We saw that the way semantic and phonological information is structured in the learning environment (i.e., EXT) contributes to noun learning across languages.
 However, we know that other factors influence learning as well [e.g., @braginsky2016].
@@
 @goodman2008].
-The second factor is word length, which correlates with phonological connectivity.
+The second factor is word length, which correlates with phonological connectivity: Shorter words are more likely to have higher connectivity (Pisoni et al., 1985; Vitevitch and Rodriguez, 2004), and thus it critical to test if phonological connectivity plays a role in learning above and beyond word length.
 
-Since PAT was uninformative, we dropped it from this analysis, keeping only PAC.
-This simplified the model because we no longer needed to fit growth month-by-month.\footnote{This was a requirement only for PAT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.} A more direct way to assess and compare the contribution of PAC in relation to other word-level factors is through conducting linear regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.
+Since the previous section showed that INT was uninformative, we dropped it from this analysis, keeping only EXT.
+This simplified the model because we no longer needed to fit growth month-by-month.The latter was a requirement only for INT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.
+A more direct way to assess and compare the contribution of EXT in relation to other word-level factors is through conducting linear regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.
 
-We used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.} For each word, counts included words that shared the same stem  (e.g., "cats" counts as "cat"), or words that were synonymous (e.g.
+For word length, we counted the number of phonemes in our generated IPA transcription.
+For word frequency, we used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language (MacWhinney, 2000).
+For each word, counts included words that shared the same stem  (e.g., "cats" counts as "cat"), or words that were synonymous (e.g.
 "father" counts as "daddy").
-For word length, we counted the number of phonemes in our generated IPA transcription.
+Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.
+The use of an independent dataset is warraned because it uses large samples to average out the difference between children (see Goodman et al.
+2008).
 
@@
 Figure \@ref(fig:staticAll) shows the coefficient estimates for all languages combined (all predictors were centered and scaled).
-The findings were as follows.
-Overall, frequency is the largest and most consistent predictor of age of acquisition, replicating results for nouns across a variety of analyses [@goodman2008; @braginsky2016; @roy2015].
-Word length predicts learning in some languages such as Croatian and Norwegian, but not in others (including English).
-It remains, however, a significant predictor in the global model.
-As for the factors of interest, i.e., semantic and phonological connectivity, we also found cross-linguistic differences.
-Phonological connectivity contributes to learning in languages such as Croatian, English and Russian, whereas semantic connectivity contributes to learning in Turkish, Spanish and to some extent in Croatian, but not in English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
-This contrasts with the original finding in Hills et al.
-2009.
+
+The findings for the new predictors were as follows.
+Overall, frequency is the largest and most consistent predictor of age of acquisition in both comprehension and production data and across languages, endorsing results for nouns across a variety of analyses [@goodman2008; @braginsky2016; @roy2015].
+Word length is more predictive for production than comprehension (and this difference is very clear in the global model), replicating previous work (Braginsky et al., under review).
+Thus, word length seems to reflect the effects of production constraints rather than than comprehension constraints (i.e., long words are harder to pronounce than short words, but maybe not more difficult to store or access).
+
+As for the factors of interest, i.e., semantic and phonological connectivity, we found cross-linguistic differences.
+Phonological connectivity contributes to learning in some languages but not in other.
+In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
+This contrasts with the original finding in @hills2009.
 However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates.
-Another important difference is the number of words tested: Our study uses a larger set of nouns.} Despite these cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.
+Another important difference is the number of words tested: Our study uses a larger set of nouns.
+That said, and despite these cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.
 
@@
 
-The present study provided a comprehensive analysis of how lexical connectivity influences the age of acquisition of nouns in toddlers.
-We compared two network growth scenarios and assessed their relative contributions across eight languages.
-One scenario, PAT, described a rich-get-richer network growth model in which the structure of the learner's internal network determines future growth; the other, PAC, described a model in which the external, global environmental network structure determines learners' growth patterns.
-Our findings largely replicate the results obtained by @hills2009: Semantic networks grow by preferential acquisition, not by preferential attachment.
-A novel finding is that phonological networks also grow primarily by preferential acquisition.
-Moreover, both semantic and phonological connectivity in the learning environment predict growth.
-These findings generalize well across languages.
-When pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting learning in some languages, but not in others.
-Nevertheless, this cross-linguistic variability is to be taken with a grain of salt as it might be exaggerated in our study by the limited and partially-overlapping sample of nouns for each language.
+This study provided an analysis of network growth during development.
+We compared the two major network growth scenarios desribed in the pioneering work of @hills2009.
+The first scenario, INT (orignially called Preferentailly Attachement), described a rich-get-richer network growth model in which the current structure of the learner's internal network determines future growth; the other, EXT (orignially called Preferentailly Acquisition) described a model in which the external, global environmental network structure determines learners' growth patterns.
+Previous word in this line of research (e.g., @hills2009; @hills2010; Sailor 2013) has been limited in its scope: It focused on semantic networks, while relying only on words' production as a mesure of their acquisition, and using almost exclusively developmental data from English-learning children.
+This study test the generality previous findings first by investigting phonological networks together with semantic networks, second by adopting both production and comprehension as measures of learing, and crucially, by comparing the findings across 10 languages.
+
+We found that the orginal findings reported in @hills2009 generalize well across all these dimensions.
+First, just like semantic networks, phonological networks grow via the externally-driven scenrio (EXT), not by the internally-driven mechanism (INT).
+Besides, both semantic and phonological networks contribute to the learning process above and beyond other known predcitors of word learning such as frequency and word length.
+Second, comprehension-based vocabularies grow in a way similar to production-based vocabularies [HERE ADD MORE NUANCE?].
+Finally, the findings were overall similar across the 10 languages we tested.
+Although we find some cross-lingusitic variation when semantic and phonological networks were pitted against frequency and length, this variability is to be taken with a grain of salt as it might be exaggerated in our study by the limited and partially-overlapping sample of nouns for each language.
 In fact, both phonological and semantic connectivity are significant predictors when data are pooled across languages.
 
-Children start by learning words that have high semantic and phonological similarity to a variety of other words in the learning environment, not in the child's available lexicon.
-This result suggests that children are sensitive to connectivity even without having first acquired the connected words.
-How can children indirectly detect highly connected words, and why would such words be more readily learned?
+These findings corroborate the hypothesis that children start by learning words that have high similarity to a variety of other words in the learning environment, not in the child's available lexicon.
+This means, strikingly, that children are sensitive to highly connected words although they do not initially have access to the full network.
+This remarks begs the following question: What mechanism could allow children to tease apart highly connected words from low connected words?
+Besides, why would highly connected words be easier to learn?
 
-In the semantic case, the networks are based on free association norms.
-These associations can be (partly) derived from the patterns of word-word co-occurrence [e.g., @griffiths07], i.e., two words are associated if they co-occur in many different contexts.
-In a network structure, highly connected words would be the words that co-occur with many other words in various contexts.
-Why would such words be easier to learn?
-One possibility, suggested by @hills2010, is that the referents of these words are more easily disambiguated from other potential referents because their presence in multiple contexts provides more cross-situational, disambiguating statistics about their true referents [@smith2008].
+One possbility is that children rely on their statistical learning abilities.
+For example, in the semantic domain, children might be using a mechanism akin to cross-situational learning to pick up the meanings of some words, especially concrete nouns [@smith2008], and such learning would resemble the growth scenario described by EXT.
+Indeed, since free association is related to contextual co-occurrence (Griffiths et al., Fourtassi and Dupoux, 2013), highly connected words will tend to occur in a variety of speech and referential contexts.
+This fact makes such a word easier to learn  only because it has more referential disambiguating cues across learning contexts, and crucially, even without knowing the entire set of words with witch it occurs (hence the similarity with EXT).
+This possibility is supported by the finding that nouns' diverstiy of occurrence in child directed speech predicts their age of learing (@hills2010).
 
-In the phonological case, connectivity is inherently correlated with phonotactic probability [@vitevitch1999].
+In the phonological case, network growth according to EXT is also compatible with a scenario whereby children are tracking lwo level statistical patterns, e.g., high probability sound sequences.
+Indeed, connectivity in the phonological network is inherently correlated with phonotactic probability [@vitevitch1999].
 That is, highly connected words tend to be made of frequent sound sequences.
-Even infants show a sensitivity for high frequency sound sequences in the ambient language [@jusczyk1994].
-Moreover, phonotactic probability facilitates learning and recognition [e.g., @storkel2001].
-In other words, children's sensitivity to local phonotactic regularities might lead them to learn higher-probability words more easily.
-This learning effect, in turn, would lead to an observed pattern of growth that would appear to follow the PAC growth model even though learners themselves would only be tracking local statistics.
+Children are sensitive to local phonotactic regularities [@jusczyk1994] and this sensitivity might lead them to learn higher-probability words more easily [e.g., @storkel2001].
+This explanation is supported by computational simualtions that shows how learning general phonotactics patterns create ``well-worn paths'' which allow for the representation of several distinct but phonologically neighboring words (Dell et al; 1993; Tavac et al.
+2017).
 
-Finally, while validating previous results using network growth models, our study suggests that these correlational patterns may emerge from the operation of simpler mechanisms in both the semantic and phonological domains.
+Besides using their own statitistical learning skills, children could also benefit from the the way their caregivers speak.
+Perhaps the cargivers put more emphasis on the words that are highly connected in _their_ mature lexical network.
+This emphasis would guide children to learn first these highly connected words even though children do not have access to the distribution of words' connectivity in the final network.
+Investigting this possibility would require further research on caregiver-child interaction (MacWhinney, 2014; Roy et al.
+2015), examining what words are introduced over development and the extent to which children's uptake is infuence by this input (Clark 2007;  Hoff and Naigles, 2002; Hurtado et al., 2008).
+
+This work shares a number of limitations with previous studies using similar research strategy and datasets (e.g., Hills et al.
+2009; 2010).
+Chief among these limitations is the fact that the age of word acquisition is computed using different children at different ages (due to the fact that avialable CDI data is mainly cross-sectional).
+Althoug this measure has proven highly consistent (Fensen et al.
+1993), it lead us to focus on studying the learning mechanism of the "average" child.
+Individual trajectories, however, could show different learning patterns.
+For example, using longitudinal data @beckage2011 found differences between typical and late talkers in terms of the semantic network structure.
+Besides, although our study endorses the externally-driven account of network growth, this does not mean individual children never use some variant of the internally-driven mechanism.
+For instance, some children develop "islands of expertise", that is, well organized knowledge about a certain topic (e.g., birds or dinosaurs).
+This prior knowledge enables these children to learn new related words more easily (e.g., Chi and Koeske, 1983).
+
+To conclude, our work validates previous results in early network development, and suggests that the advantage of highly connected words words may emerge, at least in the early stages of word learning, from the operation of simpler mechanisms in both the semantic and phonological domains.
+One question for future experimental work is whether such correlational patterns of growth can be produced in controlled behavioral experiments.
+
+<!--Finally, while validating previous results using network growth models, our study suggests that these correlational patterns may emerge from the operation of simpler mechanisms in both the semantic and phonological domains.
 One question for future experimental work is whether such patterns of growth can be produced in controlled behavioral experiments.
-<!--Finally, this study shares a number of limitations with previous studies using similar research strategy and dataset.For instance, we used normative age of acquisition.
-However, individual children may follow different learning trajectories.
-The use of longitudinal data would allow us to assess how the aggregate behavior relates to these individual trajectories [e.g., typical vs.
-late talkers, @beckage2011].
-Moreover,In particular, the results provide correlational but not causal evidence.
-Thus, the conclusions of this study  require parallel evidence, especially from controlled behavioral experiments.
+In particular, the results provide correlational but not causal evidence. Thus, the conclusions of this study  require parallel evidence, especially from controlled behavioral experiments.
 -->

### 2018-10-26 journal/ms.tex
journal

@@
 between two nodes represents a relationship between the corresponding
-pair of words (Collins and Loftus, 1975). Previous studies have
+pair of words (e.g., Collins and Loftus, 1975). Previous studies have
 investigated early vocabulary structure by constructing networks using a
@@
 environment. They called this alternative explanation Preferential
-Acquisition. For clarity of reading, we will rename these scenarios in a
-ways that reflects how their modes of operation contrast with each
-other. We will call preferential attachment the Internally-driven
-mechanism (INT), and preferential acquisition the Externally-driven
-mechanism (EXT). Figure~\ref{fig:growth} shows an illustration of both
-growth scenarios with the same simplified network. These two proposals
-represent two divergent ideas about the role of lexical networks in
-acquisition. On the INT proposal, network structure is a causal factor
-in early word learning; in contrast, on the EXT approach, network
-structure is not internally represented and, therefore, might be an
-epiphenomenon of the statistics of the linguistic input.
+Acquisition. For clarity of reading, we will call preferential
+attachment the Internally-driven mechanism (INT), and preferential
+acquisition the Externally-driven mechanism (EXT).
+Figure~\ref{fig:growth} shows an illustration of both growth scenarios
+with the same simplified network. These two proposals represent two
+divergent ideas about the role of lexical networks in acquisition. On
+the INT proposal, network structure is a causal factor in early word
+learning; in contrast, on the EXT approach, network structure is not
+internally represented and, therefore, might be an epiphenomenon of the
+statistics of the linguistic input.
 
@@
 
-Hills et al. (2009) found that early networks do not grow through INT as
-was originally hypothesised by Steyvers and Tenenbaum (2005), but rather
-through EXT. This finding, though potentially very profound, has only
-been estabished in the special case of networks that are 1) based on
-semantic associations, 2) use data from English-learning children, and
-3) consider word production as a measure of acqusition. Thus, it could
-be that the result depends on the domain, culture or/and the measure. In
-this work, we test the generality of the finding along these three
-dimesnions.
+Hills et al. (2009) found that early lexical networks do not grow
+through INT as was originally hypothesised by Steyvers and Tenenbaum
+(2005), but rather through EXT. This finding, though potentially very
+profound, has only been estabished in the special case of networks that
+are based on 1) semantic associations, 2) word production as a measure
+of acquisition, and 2) data from English-learning children, only. The
+extent to which this result depends on the domain, the measure and
+culture/languagae is still unclear. In this work, we test the generality
+of the finding along these three dimesnions.
 
-First, we investigte the mechanism that underlies the growth of
-phonological networks. Previous studies have analyzed various strcutural
-properties of adults phonological networks, and found that some of these
-properties influence the language processes of word recognition and
-production as well as language-related memory processes (Vitevitch,
-2008; Luce \& Pisoni, 1998; Chan \& Vitevitch, 2009; Chan \&
-Vitevitch,2010; Vitevitch, Chan, and Roodenrys, 2012; Castro et al.
-2018). More relvant to our study is the research that investigates
-learning in children, and in particualr the finding that words'
-connectivity in a phonological network is negatively correlated with
-their age of learning in children (Stokes 2004; Storkel, 2004, 2009). In
-other words, the finding suggests that words learned earlier tend to
-sound similar to many other words than a word learned later in life.
-This finding however, does not address the question of the learning
-mechanism. In fact, as with semantic networks, the fact that the
-connectivity in the end-state network predicts AoA can be the outcome of
-both the internallay- and externally-driven mechanisms (Hills et al.
-2009).
+First, we study the phonological network in addition to the semantic
+network. These two networks represent different ways the mental lexicon
+is strcutured. In particular, words that are neighbors in the semantic
+network (e.g., \enquote{cat}, \enquote{dog}) are not necessarily
+neighbors in the phonological network, and vice versa. Does the
+phonological network also influence word learning? Previous work did
+find an effect of words' connectivity in the phonological network on
+their age of learning (Storkel, 2004, 2009; Stokes 2014). In other
+words, words learned earlier in life tend to sound similar to many other
+words than a word learned later in life. However, as mentioned above,
+this finding did not examine the underlying learning
+mechanism.\footnote{In particular, this finding is compatible with both INT and EXT.}
+Here, we investigate whether phonological networks, like semantic
+networks, grow through EXT, or if they rather grow via INT
+(Figure~\ref{fig:growth}).
 
-Second, we test how the proposed growth mechanims predict word
-comprehension as compared to production. These two measures differ in
-their assessment of vocabulary composition (e.g., Benedict, 1979).
-Testing both measures is critical as it allows us to investigate the
-extent to which the mechanism is infleunced by production constraints
-(i.e., how difficult a word is to say) as compared to comprehension
-constraints (i.e., how difficult it is to store or access). If there is
-consistency across both measures, this would suggest that the growth
-mechanism captures learning patterns beyond these specific constraints.
+Second, we study vocabularies measured using both comprehension and
+production. Previous studies have found differences between these
+vocabularies in terms of their content and rate of acquistion (Benedict,
+1979; Fensen et al. 1993). These differences can be due to the fact that
+comprehension and production do not share the same contraints. For
+instance, whereas comprehension depends on the ease with which words are
+stored and accessed, production depends additionally on the ease with
+witch words are articuated (e.g., shorter words are produced earlier,
+Braginsky et al. 2016). By including comprehension-based vocabularies in
+our analysis, we assess the extent to which the network growth
+mechanisms capture general learning patterns beyond the specific
+constraints of production.
 
-Finally, we use developmental data of children in 10 cultures. Such
-cross-linguistic comparison is crucial to test what growth mechanism is
+Finally, we use developmental data in 10 languages. Lexical networks can
+show more or less cross-lingustic variability along both the semantic
+and phonological domains (Youn et al. 2015; Arbesman et al.
+2009).\footnote{The difference is more obvious in the phonolgical case where the network strcuture––and the distribution of word connectivity––can a priori change from language to language depending on various languisitc conventions.}
+Besides, cultures might differ in the way caregivers guide the
+chidlren's learning patterns or in the way the adults' linguistic input
+is organized (Kuhl et al., 1997; Cristia et al. 2017), and this
+difference could influecne the learning mechanism. Thus,
+Cross-linguistic comparison is crucial to test what mechanism is
 cognitively universal and is used by all children, and what mechansism
@@
 particulars of a given language or culture (Bates \& MacWhinney, 1987;
-Slobin, 1985). More precisely, we test whether Hill's finding with
-English-learning data generalize to other languages, and we test whether
-this generalization holds for both the semantic and phonological
-networks, and for both the comprehension and production data.
+Slobin, 1985).
 
-we test the growth mechanim in the phonological domain. Although
-previous results showed that \ldots{} (Storkel,), the growth mechanim
-has never been tested. The outcome could enrich the debate as to whether
-children first learn the words that (Here I should read the Dautrich
-paper). Second, we use developmental data collected from children in 10
-cultures. Third, we compare results using production and comprehension
-as measures of acuquition.
-
-Why phonological domain is important Why languages are important Why
-comprehension is important
-
-whether phonological networks, like semantic networks, grow by , or if
-they rather grow by P
-
-Studies that investigate lexical network growth have focused on semantic
-networks using the English vocabulary and development data based on word
-production. In particualr,
-
-However, the lexicon is not only strctured semantically
-
-Our work expands this previous research in three ways: 1) we test
-whether
-
-The novelty of the current study is threefold: First, it investigates
-whether phonological networks, like semantic networks, grow by PAC, or
-if they rather grow by PAT. Second, it provides a systematic comparison
-of both network growth scenarios in the phonological and the semantic
-domains and assesses their relative contribution to the learning
-process. Third, it tests the generality of the findings across eight
-languages.
+HERE ORGANIZATION OF THE PAPER
 
@@
 the cost-effective collection of datasets large enough to test
-network-based models of acquisition (Fenson et al., 1994). We used the
-\emph{Words and Sentences} version of the CDI which contains the
-productive vocabulary of toddlers (age varied between 16 to 36 months).
-Following previous studies (Hills et al., 2009; Storkel, 2009), we
-restricted our analysis to nouns. We defined the age of acquisition of a
-given word by the month at which this word was produced by at least 50\%
-of children (J. C. Goodman et al., 2008), and we excluded nouns that
-have not been learned (according to this criterion) by the last month
-for which we have CDI data.
+network-based models of acquisition (Fenson et al., 1994). When filling
+out a CDI form, caregivers are either invited to indicate whether their
+child \enquote{understands} (comprehension) or \enquote{understands and
+says} (production) for each of about 400 words. For youner chidlren
+(between 8 and 18 months), both comprehension and production are
+queried, whereas for oder chidlren (between 16 to 36 months) only
+production is queried. We use data from younger chidlren to test
+comprehension and data from older chidlren to test production. Following
+previous studies (Hills et al., 2009; Storkel, 2009), we restrict our
+analysis to nouns. Table \ref{tab:stats} gives an overview of the data
+source.
 
-We obtained these nouns in eight languages: Croatian, Danish, English,
-Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of
-nouns that had entries in the Florida Association Norms (see below).
-Since these norms are available only in English, we used the
-hand-checked translation equivalents provided by Braginsky et al.
-(2016), allowing us to use the English association norms across
-languages. Table \ref{tab:stats} gives an overview of the data used.
-Translation equivalents were originally constructed for a subset of
-words appearing on the toddler CDI form, and so not all words are
-currently available. Note, however, that all languages have at least
-60\% of nouns translated.
+\subsection{Age of acquisition}\label{age-of-acquisition}
+
+For each word in CDI data, we compute the proportion of children who
+understand or produce the word at each month. Then we fit a logistic
+curve to these proportions and determined when the curve crosses 0.5,
+i.e., the age at which at lest 50\% of chidlren know the word. We take
+this point in time to be each word's age of acquisition (J. C. Goodman
+et al., 2008) and Braginsky.
 
@@
 
-\section{Semantic networks}\label{semantic-networks}
+\subsection{Semantic networks}\label{semantic-networks}
 
-We constructed semantic networks following the procedure outlined in
-Hills et al. (2009). We used as an index of semantic relatedness the
-Florida Free Association Norms (Nelson, McEvoy, \& Schreiber, 1998).
-This dataset was collected by giving adult participants a word (the
-cue), and asking them to write the first word that comes to mind (the
-target). For example, when given the word \enquote{ball}, they might
-answer with the word \enquote{game}. A pair of nodes were connected by a
-directed link from the cue to the target if there was a cue-target
-relationship between these nodes in the association norms. The
-connectivity of a given node was characterized by its \emph{indegree}:
-the number of links for which the word was the target. To model growth
-from month to month, we constructed a different network at each month,
-based on the words that have been acquired by that month.
+We constructed semantic networks for English data following the
+procedure outlined in Hills et al. (2009). We used as an index of
+semantic relatedness the Florida Free Association Norms (Nelson, McEvoy,
+\& Schreiber, 1998). This dataset was collected by giving adult
+participants a word (the cue), and asking them to write the first word
+that comes to mind (the target). For example, when given the word
+\enquote{ball}, they might answer with the word \enquote{game}. A pair
+of nodes were connected by a directed link from the cue to the target if
+there was a cue-target relationship between these nodes in the
+association norms. The connectivity of a given node was characterized by
+its \emph{indegree}: the number of links for which the word was the
+target. To model growth from month to month, we constructed a different
+network at each month, based on the words that have been acquired by
+that month.
+
+Free Association norms are available only in English. We used the
+hand-checked translation equivalents available in Wordbank, which
+allowed us to use the English association norms across languages. Note
+that this does not necessarily mean that the resulting networks will be
+the same across languages, or that these networks will grow similarly.
+Though using the same association data acoss langauges assumes that the
+semantic similarity measure is universal (which is a reasonable
+approximation, Youn et al. 2015), the set of words acquired by children
+as well as the timeline of this acquisition can still vary from language
+to language leading to possbility different learing strategies.
 
@@
 
-We generated approximate International Phonetic Alphabet (IPA)
-transcriptions from the orthographic transcription, across languages,
-using the open source text-to-speech software
-\textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.} We used
-the Levenshtein distance (also known as edit distance) as a measure of
-phonological relatedness between two nodes. The measure counts the
-minimum number of operations (insertions, deletions, substitutions)
-required to change one string into another.
+To construct phonological networks we first mapped the orthogrphic
+transcrition of words to their International Phonetic Alphabet (IPA)
+transcriptions, across languages, using the open source text-to-speech
+software \textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.}
+We used the Levenshtein distance (also known as edit distance) as a
+measure of phonological relatedness between two nodes. The measure
+counts the minimum number of operations (insertions, deletions,
+substitutions) required to change one string into another.
 
@@
 We constructed this network using nouns learned by the oldest age for
-which we have CDI data (e.g., in English this corresponds to the network
-by 30 months). This global network is the end-state towards which both
-PAT and PAC should converge by the last month of learning. Moreover,
+which we have CDI data (e.g., in English this corresponds, in
+comprehension, to the network by 18 months, and in production, to the
+network by 30 months). This global network is the end-state towards
+which both INT and EXT converge by the last month of learning. Moreover,
 following Hills et al. (2009), we used this end-state network as a proxy
 for the external connectivity in the learning environment. Below we
-analyze properties of this global networks that are relevant to PAC
-and/or PAT.
+analyze properties of this global networks that are relevant to INT
+and/or EXT.
 
@@
 
-Connectivity in the global network is directly related to PAC as it
-represents the explicit criterion PAC uses to determine what words
-should be learned first (Figure \ref{fig:growth}). Therefore, a direct
-consequence of a PAC-like growth scenario is a correlation between
-connectivity in the global network and the age of
-acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed.
+Connectivity in the global network is directly related to EXT as it
+represents the explicit criterion this growth scenario uses to determine
+what words should be learned first (Figure \ref{fig:growth}). Therefore,
+a direct consequence of a EXT-like growth scenario is a correlation
+between connectivity in the global network and the age of
+acquisition.\footnote{This correlation is also compatible with INT, although the causality is reversed.
 Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around.
@@
 comprehension (B) for each word varies as a function of its degree (or
-indegree for the semantic network). For ease of visual comparison, the
+indegree for the semantic networks). For ease of visual comparison, the
 predictor (i.e., the degree) was centered and scaled across languages.
@@
 acquisition and the degree, indicating that nouns with higher degrees
-are generally learned earlier.
+are generally learned earlier. HERE MENTION THE AVERAGE VALUE OF THE
+CORRELATIONS
 
@@
 \subsubsection{Power-law degree
-distribution?}\label{power-law-degree-distribution}
+distribution}\label{power-law-degree-distribution}
 
 We also analyzed the global network's degree distribution. The shape of
-this distribution is particularly relevant to PAT as this growth
+this distribution is particularly relevant to INT as this growth
 scenario is known to generate networks with a power-law degree
@@
 \(p(k) \propto \frac{1}{k^{\alpha}}\), Barabasi \& Albert, 1999). If the
-network displays this property, this fact would suggest a PAT-like
+network displays this property, this fact would suggest a INT-like
 generative process. Conversely, if the degree distribution does not
-follow a power law, this fact would weaken the case for PAT. The log-log
+follow a power law, this fact would weaken the case for INT. The log-log
 plots are shown in Figure \ref{fig:degreeDist}. We fit a power law to
@@
 Clauset, Shalizi, and Newman (2009) and using the related R package
-(poweRlaw, Gillespie, 2015). In brief, the analysis consisted in two
-steps. First, we derived the optimal cut-off, \(k_{min}\), above which
-the distribution is more likely to follow a power
+(poweRlaw, Gillespie, 2015).
+
+In brief, the analysis consisted in two steps. First, we derived the
+optimal cut-off, \(k_{min}\), above which the distribution is more
+likely to follow a power
 law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}
@@
 we calculated the goodness-to-fit, which resulted in a \(p\)-value
-quantifying the plausibility of the model. The results are shown in
-Appendix 1, table XX. Overall, we could not reject the null hypothesis
-of a power-law distribution: the \(p\)-value was generally above 0.1.
+quantifying the plausibility of the model.
+
+The results are shown in table XX. Overall, we could not reject the null
+hypothesis of a power-law distribution: the \(p\)-value was generally
+above 0.1. Also talk about the fact that the power law is truncated.
 
 In sum, the static properties of the global network are \emph{a priori}
-compatible with both PAT and PAC. In order to decide between these two
+compatible with both INT and EXT. In order to decide between these two
 developmental scenarios, we need to fit explicit growth models to the
@@
 
-For the semantic networks, the results replicate Hills et al.'s finding
-in English, which is that the semantic network grows by PAC, not by PAT.
-Moreover, this finding holds in seven of the eight languages we
-examined.\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
-However, our findings do not support this assumption as the effects were generally similar in magnitude cross-linguistically.}
-The PAC model also fits better than PAT for phonological networks. We
-note however that PAT, though weaker, fares better for the phonological
-networks (where it predicts part of the growth process in some languages
-such as Croatian, English, Norwegian and Russian) than it does for the
-semantic networks (where it is rather universally unpredictive).
+The results replicate Hills et al.'s finding regarding the semantic
+netowrk in English and prouction data, which is that this network grows
+by EXT, not by INT. Besides, this finding generalize to comprehension,
+and holds overall across languages. One could imagine that the fact of
+using English free association norms cross-linguistically would decrease
+the effect of non-English semantic networks because of possible cultural
+differences. However, our findings do not support this assumption,
+rather it supports our intial approximation, albeit a posteriori, about
+the unversisality of the semantic similarity measure. In the
+phonological domain, the EXT model also fits better the data than INT
+for both production and comprehension. Similar to the sematic domain,
+the findings generalize well cross-linguistically.
 
@@
 We saw that the way semantic and phonological information is structured
-in the learning environment (i.e., PAC) contributes to noun learning
+in the learning environment (i.e., EXT) contributes to noun learning
 across languages. However, we know that other factors influence learning
@@
 2008). The second factor is word length, which correlates with
-phonological connectivity.
+phonological connectivity: Shorter words are more likely to have higher
+connectivity (Pisoni et al., 1985; Vitevitch and Rodriguez, 2004), and
+thus it critical to test if phonological connectivity plays a role in
+learning above and beyond word length.
 
-Since PAT was uninformative, we dropped it from this analysis, keeping
-only PAC. This simplified the model because we no longer needed to fit
-growth
-month-by-month.\footnote{This was a requirement only for PAT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.}
-A more direct way to assess and compare the contribution of PAC in
-relation to other word-level factors is through conducting linear
+Since the previous section showed that INT was uninformative, we dropped
+it from this analysis, keeping only EXT. This simplified the model
+because we no longer needed to fit growth month-by-month.The latter was
+a requirement only for INT where the words' utilities varied from month
+to month, depending on how connectivity changed in the growing internal
+network. A more direct way to assess and compare the contribution of EXT
+in relation to other word-level factors is through conducting linear
 regressions, where connectivity in the learning environment, frequency
@@
 
-We used the frequency estimates from Braginsky et al. (2016) where
-unigram counts were derived based on CHILDES corpora in each
-language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.}
-For each word, counts included words that shared the same stem (e.g.,
-\enquote{cats} counts as \enquote{cat}), or words that were synonymous
-(e.g. \enquote{father} counts as \enquote{daddy}). For word length, we
-counted the number of phonemes in our generated IPA transcription.
+For word length, we counted the number of phonemes in our generated IPA
+transcription. For word frequency, we used the frequency estimates from
+Braginsky et al. (2016) where unigram counts were derived based on
+CHILDES corpora in each language (MacWhinney, 2000). For each word,
+counts included words that shared the same stem (e.g., \enquote{cats}
+counts as \enquote{cat}), or words that were synonymous (e.g.
+\enquote{father} counts as \enquote{daddy}). Note that these frequency
+counts are based on transcripts from independent sets of children and
+represent a general estimate of environmental frequency across children.
+The use of an independent dataset is warraned because it uses large
+samples to average out the difference between children (see Goodman et
+al. 2008).
 
@@
 coefficient estimates for all languages combined (all predictors were
-centered and scaled). The findings were as follows. Overall, frequency
-is the largest and most consistent predictor of age of acquisition,
-replicating results for nouns across a variety of analyses (Braginsky et
-al., 2016; J. C. Goodman et al., 2008; B. C. Roy et al., 2015). Word
-length predicts learning in some languages such as Croatian and
-Norwegian, but not in others (including English). It remains, however, a
-significant predictor in the global model. As for the factors of
-interest, i.e., semantic and phonological connectivity, we also found
-cross-linguistic differences. Phonological connectivity contributes to
-learning in languages such as Croatian, English and Russian, whereas
-semantic connectivity contributes to learning in Turkish, Spanish and to
-some extent in Croatian, but not in
-English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
-This contrasts with the original finding in Hills et al.
-2009.
-However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates.
-Another important difference is the number of words tested: Our study uses a larger set of nouns.}
-Despite these cross-linguistic differences, both phonological and
-semantic connectivity are significant predictors in the combined model.
+centered and scaled).
+
+The findings for the new predictors were as follows. Overall, frequency
+is the largest and most consistent predictor of age of acquisition in
+both comprehension and production data and across languages, endorsing
+results for nouns across a variety of analyses (Braginsky et al., 2016;
+J. C. Goodman et al., 2008; B. C. Roy et al., 2015). Word length is more
+predictive for production than comprehension (and this difference is
+very clear in the global model), replicating previous work (Braginsky et
+al., under review). Thus, word length seems to reflect the effects of
+production constraints rather than than comprehension constraints (i.e.,
+long words are harder to pronounce than short words, but maybe not more
+difficult to store or access).
+
+As for the factors of interest, i.e., semantic and phonological
+connectivity, we found cross-linguistic differences. Phonological
+connectivity contributes to learning in some languages but not in other.
+In particular, semantic connectivity does not explain variance in
+English data beyond that explained by phonological connectivity,
+frequency and length. This contrasts with the original finding in Hills
+et al. (2009). However, in this previous study, semantic connectivity
+was not tested in a model that included frequency, length and
+phonological connectivity as covariates. Another important difference is
+the number of words tested: Our study uses a larger set of nouns. That
+said, and despite these cross-linguistic differences, both phonological
+and semantic connectivity are significant predictors in the combined
+model.
 
@@
 
-The present study provided a comprehensive analysis of how lexical
-connectivity influences the age of acquisition of nouns in toddlers. We
-compared two network growth scenarios and assessed their relative
-contributions across eight languages. One scenario, PAT, described a
-rich-get-richer network growth model in which the structure of the
-learner's internal network determines future growth; the other, PAC,
-described a model in which the external, global environmental network
-structure determines learners' growth patterns. Our findings largely
-replicate the results obtained by Hills et al. (2009): Semantic networks
-grow by preferential acquisition, not by preferential attachment. A
-novel finding is that phonological networks also grow primarily by
-preferential acquisition. Moreover, both semantic and phonological
-connectivity in the learning environment predict growth. These findings
-generalize well across languages. When pitted against other known
-predictors of age of acquisition (word frequency and length), the effect
-of word connectivity shows a cross-linguistic variation, predicting
-learning in some languages, but not in others. Nevertheless, this
-cross-linguistic variability is to be taken with a grain of salt as it
+This study provided an analysis of network growth during development. We
+compared the two major network growth scenarios desribed in the
+pioneering work of Hills et al. (2009). The first scenario, INT
+(orignially called Preferentailly Attachement), described a
+rich-get-richer network growth model in which the current structure of
+the learner's internal network determines future growth; the other, EXT
+(orignially called Preferentailly Acquisition) described a model in
+which the external, global environmental network structure determines
+learners' growth patterns. Previous word in this line of research (e.g.,
+Hills et al. (2009); Hills et al. (2010); Sailor 2013) has been limited
+in its scope: It focused on semantic networks, while relying only on
+words' production as a mesure of their acquisition, and using almost
+exclusively developmental data from English-learning children. This
+study test the generality previous findings first by investigting
+phonological networks together with semantic networks, second by
+adopting both production and comprehension as measures of learing, and
+crucially, by comparing the findings across 10 languages.
+
+We found that the orginal findings reported in Hills et al. (2009)
+generalize well across all these dimensions. First, just like semantic
+networks, phonological networks grow via the externally-driven scenrio
+(EXT), not by the internally-driven mechanism (INT). Besides, both
+semantic and phonological networks contribute to the learning process
+above and beyond other known predcitors of word learning such as
+frequency and word length. Second, comprehension-based vocabularies grow
+in a way similar to production-based vocabularies {[}HERE ADD MORE
+NUANCE?{]}. Finally, the findings were overall similar across the 10
+languages we tested. Although we find some cross-lingusitic variation
+when semantic and phonological networks were pitted against frequency
+and length, this variability is to be taken with a grain of salt as it
 might be exaggerated in our study by the limited and
@@
 
-Children start by learning words that have high semantic and
-phonological similarity to a variety of other words in the learning
-environment, not in the child's available lexicon. This result suggests
-that children are sensitive to connectivity even without having first
-acquired the connected words. How can children indirectly detect highly
-connected words, and why would such words be more readily learned?
+These findings corroborate the hypothesis that children start by
+learning words that have high similarity to a variety of other words in
+the learning environment, not in the child's available lexicon. This
+means, strikingly, that children are sensitive to highly connected words
+although they do not initially have access to the full network. This
+remarks begs the following question: What mechanism could allow children
+to tease apart highly connected words from low connected words? Besides,
+why would highly connected words be easier to learn?
 
-In the semantic case, the networks are based on free association norms.
-These associations can be (partly) derived from the patterns of
-word-word co-occurrence (e.g., Griffiths, Steyvers, \& Tenenbaum, 2007),
-i.e., two words are associated if they co-occur in many different
-contexts. In a network structure, highly connected words would be the
-words that co-occur with many other words in various contexts. Why would
-such words be easier to learn? One possibility, suggested by Hills et
-al. (2010), is that the referents of these words are more easily
-disambiguated from other potential referents because their presence in
-multiple contexts provides more cross-situational, disambiguating
-statistics about their true referents (Smith \& Yu, 2008).
+One possbility is that children rely on their statistical learning
+abilities. For example, in the semantic domain, children might be using
+a mechanism akin to cross-situational learning to pick up the meanings
+of some words, especially concrete nouns (Smith \& Yu, 2008), and such
+learning would resemble the growth scenario described by EXT. Indeed,
+since free association is related to contextual co-occurrence (Griffiths
+et al., Fourtassi and Dupoux, 2013), highly connected words will tend to
+occur in a variety of speech and referential contexts. This fact makes
+such a word easier to learn only because it has more referential
+disambiguating cues across learning contexts, and crucially, even
+without knowing the entire set of words with witch it occurs (hence the
+similarity with EXT). This possibility is supported by the finding that
+nouns' diverstiy of occurrence in child directed speech predicts their
+age of learing (Hills et al. (2010)).
 
-In the phonological case, connectivity is inherently correlated with
+In the phonological case, network growth according to EXT is also
+compatible with a scenario whereby children are tracking lwo level
+statistical patterns, e.g., high probability sound sequences. Indeed,
+connectivity in the phonological network is inherently correlated with
 phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
 is, highly connected words tend to be made of frequent sound sequences.
-Even infants show a sensitivity for high frequency sound sequences in
-the ambient language (Jusczyk, Luce, \& Charles-Luce, 1994). Moreover,
-phonotactic probability facilitates learning and recognition (e.g.,
-Storkel, 2001). In other words, children's sensitivity to local
-phonotactic regularities might lead them to learn higher-probability
-words more easily. This learning effect, in turn, would lead to an
-observed pattern of growth that would appear to follow the PAC growth
-model even though learners themselves would only be tracking local
-statistics.
+Children are sensitive to local phonotactic regularities (Jusczyk, Luce,
+\& Charles-Luce, 1994) and this sensitivity might lead them to learn
+higher-probability words more easily (e.g., Storkel, 2001). This
+explanation is supported by computational simualtions that shows how
+learning general phonotactics patterns create ``well-worn paths'' which
+allow for the representation of several distinct but phonologically
+neighboring words (Dell et al; 1993; Tavac et al. 2017).
 
-Finally, while validating previous results using network growth models,
-our study suggests that these correlational patterns may emerge from the
-operation of simpler mechanisms in both the semantic and phonological
-domains. One question for future experimental work is whether such
-patterns of growth can be produced in controlled behavioral experiments.
+Besides using their own statitistical learning skills, children could
+also benefit from the the way their caregivers speak. Perhaps the
+cargivers put more emphasis on the words that are highly connected in
+\emph{their} mature lexical network. This emphasis would guide children
+to learn first these highly connected words even though children do not
+have access to the distribution of words' connectivity in the final
+network. Investigting this possibility would require further research on
+caregiver-child interaction (MacWhinney, 2014; Roy et al. 2015),
+examining what words are introduced over development and the extent to
+which children's uptake is infuence by this input (Clark 2007; Hoff and
+Naigles, 2002; Hurtado et al., 2008).
+
+This work shares a number of limitations with previous studies using
+similar research strategy and datasets (e.g., Hills et al. 2009; 2010).
+Chief among these limitations is the fact that the age of word
+acquisition is computed using different children at different ages (due
+to the fact that avialable CDI data is mainly cross-sectional). Althoug
+this measure has proven highly consistent (Fensen et al. 1993), it lead
+us to focus on studying the learning mechanism of the \enquote{average}
+child. Individual trajectories, however, could show different learning
+patterns. For example, using longitudinal data Beckage, Smith, and Hills
+(2011) found differences between typical and late talkers in terms of
+the semantic network structure. Besides, although our study endorses the
+externally-driven account of network growth, this does not mean
+individual children never use some variant of the internally-driven
+mechanism. For instance, some children develop \enquote{islands of
+expertise}, that is, well organized knowledge about a certain topic
+(e.g., birds or dinosaurs). This prior knowledge enables these children
+to learn new related words more easily (e.g., Chi and Koeske, 1983).
+
+To conclude, our work validates previous results in early network
+development, and suggests that the advantage of highly connected words
+words may emerge, at least in the early stages of word learning, from
+the operation of simpler mechanisms in both the semantic and
+phonological domains. One question for future experimental work is
+whether such correlational patterns of growth can be produced in
+controlled behavioral experiments.
 
@@
 
+\hypertarget{ref-beckage2011}{}
+Beckage, N. M., Smith, L., \& Hills, T. T. (2011). Small worlds and
+semantic network growth in typical and late talkers. \emph{PLOS ONE},
+\emph{6}(5), 1--6.
+
 \hypertarget{ref-braginsky2016}{}
@@
 Probabilistic Programming Languages. \url{http://dippl.org}.
-
-\hypertarget{ref-griffiths07}{}
-Griffiths, T. L., Steyvers, M., \& Tenenbaum, J. B. (2007). Topics in
-semantic representation. \emph{Psychological Review}, \emph{114}(2),
-2007.
 

### 2018-10-30 journal/ms.Rmd
journal

@@
 Another view suggests that learning is driven  by highly connected words in the external learning environment instead of highly connected words in the early internal lexicon.
-The present study tests both scenarios systematically in both the phonological and semantic domains, and across 8 languages.
-We show that external connectivity in the learning environment drives growth in both the semantic and the phonological networks, and that this pattern is consistent cross-linguistically.
+The present study tests both scenarios systematically in both the phonological and semantic domains across 10 languages.
+We show that external connectivity in the learning environment drives growth in both production- and comprehension-based vocabularies.
 The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment.
@@
 library(HDInterval)
+library(kableExtra)
 #library("knitcitations")
@@
 The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words (e.g., Collins and Loftus, 1975).
-Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological similarity.
-These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017] add Beckage, 2011 and other people...
+Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological relatedness.
+These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @stella2017; @carlson2014].
 
@@
 ```{r growth, fig.cap = "Illustration of the two growth scenarios.
-Filled circles (I1-I4) represent known words (Internal), and empty circles (E1 and E2) represent words that have not been learned yet (External).
-Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
+Filled grey circles represent known words (Internal) at a certain point in time.
+The empty, numbered circles represent words that have not yet been learned (External) and which are candidates to enter the lexicon next.
+The identity of the word that is going to be learned depends on the growth scenario.
+Here the squares indicate the node that drives growth in each scenario and the hand pointer indicates which word is likely to be learned.
 For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
-Thus, according to INT, the node E1 is more likely to enter the lexicon first.
+Thus, according to INT, the node 1 is more likely to enter the lexicon.
 For EXT, the utility of a candidate node is its degree in the entire network.
-According to EXT, the node E2 is more likely to enter the lexicon first.", fig.align = "center", out.width = "400px"}
-knitr::include_graphics("figs/growth2.png")
+According to EXT, the node 2 is more likely to enter the lexicon next.", fig.align = "center", out.width = "300px"}
+knitr::include_graphics("figs/growth3.png")
 ```
@@
 @hills2009 found that early lexical networks do not grow through INT as was originally hypothesised by @steyvers2005, but rather through EXT.
-This finding, though potentially very profound, has only been estabished in the special case of networks that are based on 1) semantic associations,  2) word production as a measure of acquisition, and 2) data from English-learning children, only.
-The extent to which this result depends on the domain, the measure and culture/languagae is still unclear.
-In this work, we test the generality of the finding along these three dimesnions.
+This finding, though potentially very profound, has only been established in the special case of networks that are based on 1) semantic associations,  2) production-based vocabularies, and 2) data from English-learning children, only.
+The extent to which this result depends on the domain, the measure and culture/language is still unclear.
+In this work, we test the generality of the finding along these three dimensions.
 
 First, we study the phonological network in addition to the semantic network.
-These two networks represent different ways the mental lexicon is strcutured.
+These two networks represent different ways the mental lexicon is structured.
 In particular, words that are neighbors in the semantic network (e.g., "cat", "dog") are not necessarily neighbors in the phonological network, and vice versa.
 Does the phonological network also influence word learning?
-Previous work did find an effect of words' connectivity in the phonological network on their age of learning (Storkel, 2004, 2009; Stokes 2014).
+Previous work did find an effect of words' connectivity in the phonological network on their age of learning [@storkel2009; @stella2017; @carlson2014].
 In other words, words learned earlier in life tend to sound similar to many other words than a word learned later in life.
-However, as mentioned above, this finding did not examine the underlying learning mechanism.\footnote{In particular, this finding is compatible with both INT and EXT.} Here, we investigate whether phonological networks, like semantic networks, grow through EXT, or if they rather grow via INT (Figure\ \@ref(fig:growth)).
+However, this finding is compatible with both INT and EXT, and previous studies did not explicitly compare these two mechanisms.
+Here, we investigate whether phonological networks, like semantic networks, grow through EXT, or if they rather grow via INT (Figure\ \@ref(fig:growth)).
 <!--
@@
 Second, we study vocabularies measured using both comprehension and production.
-Previous studies have found differences between these vocabularies in terms of their content and rate of acquistion (Benedict, 1979; Fensen et al.
-1993).
-These differences can be due to the fact that comprehension and production do not share the same contraints.
-For instance, whereas comprehension depends on the ease with which words are stored and accessed, production depends additionally on the ease with witch words are articuated (e.g., shorter words are produced earlier, Braginsky et al.
-2016).
-By including comprehension-based vocabularies in our analysis, we assess the extent to which the network growth mechanisms capture general learning patterns beyond the specific constraints of production.
+Previous studies have found differences between these vocabularies in terms of their content and rate of acquisition [@benedict1979; @fenson94].
+These differences may reflect the fact that comprehension and production do not share the same constraints.
+For instance, whereas comprehension depends on the ease with which words are stored and accessed, production depends, additionally, on the ease with which words are articulated, e.g., shorter words are produced earlier [@braginsky2016].
+By investigating comprehension-based vocabularies, we assess the extent to which the network growth mechanism captures general learning patterns beyond the specific constraints of production.
 
 Finally, we use developmental data in 10 languages.
-Lexical networks can show more or less cross-lingustic variability along both the semantic and phonological domains (Youn et al.
-2015; Arbesman et al.
-2009).\footnote{The difference is more obvious in the phonolgical case where the network strcuture––and the distribution of word connectivity––can a priori change from language to language depending on various languisitc conventions.} Besides, cultures might differ in the way caregivers guide the chidlren's learning patterns or in the way the adults' linguistic input is organized (Kuhl et al., 1997; Cristia et al.
-2017), and this difference could influecne the learning mechanism.
-Thus, Cross-linguistic comparison is crucial to test what mechanism is cognitively universal and is used by all children, and what mechansism is specific to some patterns of learning that emerge due to the particulars of a given language or culture (Bates & MacWhinney, 1987; Slobin, 1985).
+Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains [@youn2016; @arbesman2010].\footnote{The difference is more obvious in the phonological case where the network structure––and the distribution of word connectivity––can a priori change from language to language depending on various languistic conventions.} Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the chidlren's learning strategy.
+Thus, Cross-linguistic comparison is crucial to test what mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014].
 
-HERE ORGANIZATION OF THE PAPER
+The paper is organized as follows.
+First, we describe the datasets we used and explain how we constructed the networks.
+Second, we analyze static properties of words' connectivity in these networks (correlation with AoA and shape of the distribution) and we explain how these properties infom hypotheses about network growth.
+Next, we explicitly fit the two hypothesized growth mechanisms to the data.
+We investigate the extent to which the results obtained in @hills2009 generalize to phonological networks and comprehension-based vocabularies, and whether this generalization holds cross-linguistically.
 
@@
 Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94].
-When filling out a CDI form, caregivers are either invited to indicate whether their child “understands” (comprehension) or “understands and says” (production) for each of about 400 words.
-For youner chidlren (between 8 and 18 months), both comprehension and production are queried, whereas for oder chidlren (between 16 to 36 months) only production is queried.
-We use data from younger chidlren to test comprehension and data from older chidlren to test production.
+When filling out a CDI form, caregivers are either invited to indicate whether their child "understands" (comprehension) or "understands and says" (production) each of about 400-700 words.
+For younger children (e.g., 8 to 18 months in the English data), both comprehension and production are queried, whereas for older children (16 to 36 months) only production is queried.
+We use data from younger children to test comprehension and data from older children to test production across 10 languages.
 Following previous studies [@storkel2009; @hills2009], we restrict our analysis to nouns.
-Table \@ref(tab:stats) gives an overview of the data source.
+Table \@ref(tab:stats) gives an overview of the data.
 
 ## Age of acquisition
-For each word in CDI data, we compute the proportion of children who understand or produce the word at each month.
-Then we fit a logistic curve to these proportions and determined when the curve crosses 0.5, i.e., the age at which at lest 50% of chidlren know the word.
-We take this point in time to be each word’s age of acquisition [@goodman2008] and Braginsky.
-
+For each word in the CDI data, we compute the proportion of children who understand or produce the word at each month.
+Then we fit a logistic curve to these proportions and determined when the curve crosses 0.5, i.e., the age at which at least 50% of children know the word.
+We take this point in time to be each word’s age of acquisition [@goodman2008; @braginsky2016].
 <!--We obtained these nouns in ten languages: Croatian, Danish, English, French, Italian, Norwegian, Russian, Spanish, Swedish, and Turkish.
@@
 
-statistics <- feather::read_feather("../saved_data/statistics.feather") 
-rownames(statistics) <- NULL
+statistics <- feather::read_feather("../saved_data/stats_new.feather") 
+#rownames(statistics) <- NULL
 
-tab <- xtable::xtable(statistics,
-                      caption = "\\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left).
-We included in our study the subset of these nouns that had available English translations (middle).
-The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).")
+kable(statistics, format = "latex", escape = FALSE, booktabs = TRUE,
+      linesep = "", format.args = list(big.mark = ","),
+      caption = "Statistics for data from Wordbank.",
+      col.names = c("Language",  "Nouns", "Ages", "Nouns", "Ages")) %>%
+  add_header_above(c("", "Comprehension" = 2, "Production" = 2)) %>%
+  column_spec(1, bold = TRUE) %>%
+  kable_styling(position = "center")
 
-print(tab, type="latex", comment = F, table.placement = "H")
-
-#print(statistics, type="latex", comment = F, table.placement = "H")
 ```
@@
 
-We constructed semantic networks for English data following the procedure outlined in @hills2009.
+We constructed semantic networks for English data following the procedure outlined in @hills2009, as follows.
 We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998].
@@
 
-Free Association norms are available only in English.
-We used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across languages.
-Note that this does not necessarily mean that the resulting networks will be the same across languages, or that these networks will grow similarly.
-Though using the same association data acoss langauges assumes that the semantic similarity measure is universal (which is a reasonable approximation, Youn et al.
-2015), the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possbility different learing strategies.
+Since  the free association norms are available only in English, we used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across languages.
+Using the same association data across languages does not necessarily mean that the resulting networks will be the same across languages, or that these networks will grow similarly.
+Indeed, though this approximation assumes that the semantic similarity measure is universal––which is a reasonable assumption (e.g., Youn et al.
+2015), the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possibility different learning strategies.
 
@@
 
-To construct phonological networks we first mapped the orthogrphic transcrition of words to their International Phonetic Alphabet (IPA) transcriptions, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes.
+To construct phonological networks we first mapped the orthographic transcription of words to their International Phonetic Alphabet (IPA) transcriptions in each language, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes.
 The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.
 
-In previous studies, two nodes were linked if they had an edit distance of 1 [e.g., @storkel2009].
-However, in these previous studies the network was built using an adult vocabulary.
-In the current study, however, network growth models are based on the children's early vocabulary which contains very few word pairs with an edit distance of 1.
-When using this threshold, the resulting networks were too sparse and uninformative.
-Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.
-The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
+In previous studies, two nodes were linked if they had an edit distance of 1 [@storkel2009; @carlson2014; @stella2017].
+However, these studies reported a contribution of phonological networks to word learning when these networks were built using a rich adult vocabulary.
+However, since the focus of the current study is on the mechanism of growth, the networks should be based on the children's early vocabulary which, nevertheless, contains very few word pairs with an edit distance of 1.
+Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold.
+In both cases, the results were weaker that those done with a threshold of 2.} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
 
@@
 Below we analyze properties of this global networks that are relevant to INT and/or EXT.
+In order to compare various predictors on the same data, we restrict the analysis to the subset of nouns for which we had both semantic and phonological information in each language.
 
@@
   summarise(cor = round(cor(aoa, value), 2))
+
+corrAve <- correlations %>%
+  group_by(measure, predictor) %>%
+  summarise(ave = mean(cor),
+            sd = sd(cor))
+
+#Average values of the correlation 
+pp_ave=corrAve$ave[which(corrAve$measure == "produces" & corrAve$predictor == "Phono")]
+ps_ave=corrAve$ave[which(corrAve$measure == "produces" & corrAve$predictor == "Sem")]
+cp_ave=corrAve$ave[which(corrAve$measure == "understands" & corrAve$predictor == "Phono")]
+cs_ave=corrAve$ave[which(corrAve$measure == "understands" & corrAve$predictor == "Sem")]
+
+#Sd of the ave 
+pp_sd=corrAve$sd[which(corrAve$measure == "produces" & corrAve$predictor == "Phono")]
+ps_sd=corrAve$sd[which(corrAve$measure == "produces" & corrAve$predictor == "Sem")]
+cp_sd=corrAve$sd[which(corrAve$measure == "understands" & corrAve$predictor == "Phono")]
+cs_sd=corrAve$sd[which(corrAve$measure == "understands" & corrAve$predictor == "Sem")]
 
@@
 
-```{r corrAll, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Age of production (A) and comprehension (B) in the global network as predicted by the degree in this network.
+```{r corrAll, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Age of production (A) and comprehension (B) in the global network as predicted by the degree (i.e., connectivity) in this network.
 Results are shown in each language for phonological and semantic networks.
-Each point is a word, with lines indicating linear model fits."}
+Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.", fig.width=8, fig.height=4}
 
@@
 Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \@ref(fig:growth)).
-Therefore, a direct consequence of a EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with INT, although the causality is reversed.
+Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with INT, although the causality is reversed.
 Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around.
-Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \@ref(fig:corrAll) shows how the age of production (A) and comprehension (B) for each word varies as a function of its degree (or indegree for the semantic networks).
+Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \@ref(fig:corrAll) shows how the age of production and comprehension for each word varies as a function of its degree (or indegree for the semantic networks) as well as the correlation values.
 For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages.
-The plots show, overall, a negative correlation between the month of acquisition and the degree, indicating that nouns with higher degrees are generally learned earlier.
-HERE MENTION THE AVERAGE VALUE OF THE CORRELATIONS
+
+The plots show, overall, a negative correlation between the month of acquisition and the degree.
+In production data, the average correlation across languages was `r ps_ave` (SD=`r ps_sd`) for the semantic networks and `r pp_ave` (SD=`r pp_sd`) for the phonological networks.
+In comprehension data, the average correlation was `r cs_ave` (SD=`r cs_sd`) for the semantic networks and `r cp_ave` (SD=`r cp_sd`) for the phonological networks.
+These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English (e.g., Storkel 2004, 2009; Hills et al.
+2009) and extending these findings to ten different languages (with few exceptions) in both production- and comprehension-based vocabularies.
 
@@
 The figure shows the results for both production and comprehension data.
-A perfect power-law distribution should appear as a straight line in this graph."}
+A perfect power-law distribution should appear as a straight line in this graph.",  fig.width=10, fig.height=2}
 
-knitr::include_graphics("figs/plot_degree.pdf")
-
+#knitr::include_graphics("figs/plot_degree.pdf")
+plot_degree
 ```
@@
 We also analyzed the global network's degree distribution.
-The shape of this distribution is particularly relevant to INT as this growth scenario is known to generate networks with a power-law degree distribution [i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$, @barabasi99].
-If the network displays this property, this fact would suggest a INT-like generative process.
+The shape of this distribution is particularly relevant to INT as this growth scenario is known to generate networks with a power-law degree distribution, i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$ [@barabasi99].
+If the network displays this property, this fact would suggest an INT-like generative process.
 Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for INT.
 The log-log plots are shown in Figure \@ref(fig:degreeDist).
-We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using the related R package [poweRlaw, @gillespie15].
+We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using a related R package [poweRlaw, @gillespie15].
+
+```{r powerLawData, results="asis", echo=FALSE}
+
+powerL <- feather::read_feather("../saved_data/degree_test.feather") %>%
+  rename(Kmin = xMin) %>%
+  rename(pValue = pVal) %>%
+  rename(domain = dimension) %>%
+  mutate(alpha_r = round(alpha, digits = 2),
+         pValue_r = round(pValue, digits = 3)) %>%
+  select(Kmin, domain, language, measure, alpha_r, pValue_r)
+
+powerProd <- powerL %>%
+  dplyr::filter(measure == 'produces') %>%
+  select(-measure) %>%
+  group_by(language, domain) %>%
+  nest() %>%
+  spread(domain, data) %>%
+  unnest(.sep = "_")
+
+powerComp <- powerL %>%
+  dplyr::filter(measure == 'understands') %>%
+  select(-measure) %>%
+  group_by(language, domain) %>%
+  nest() %>%
+  spread(domain, data) %>%
+  unnest(.sep = "_")
+
+#rownames(statistics) <- NULL 
+```
+
+```{r powerLawProd, results="asis", echo=FALSE}
+
+kable(powerProd, format = "latex", escape = FALSE, booktabs = TRUE,
+      linesep = "", format.args = list(big.mark = ","),
+      caption = "Results of fitting a power law model to the degree (i.e., connectivity) distribution in each model for production data.
+Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis.
+If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.",
+      col.names = c("Language",  "cut-off", "alpha", "p-value", "cut-off", "alpha", "p-value")) %>%
+  add_header_above(c("", "Phono." = 3, "Sem." = 3)) %>%
+  column_spec(1, bold = TRUE) %>%
+  kable_styling(position = "center")
+```
+
+```{r powerLawComp, results="asis", echo=FALSE}
+
+kable(powerComp, format = "latex", escape = FALSE, booktabs = TRUE,
+      linesep = "", format.args = list(big.mark = ","),
+      caption = "Results of fitting a power law model to the degree distribution in each model for comprehension data.
+Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis.
+If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.",
+      col.names = c("Language",  "cut-off", "alpha", "p-value", "cut-off", "alpha", "p-value")) %>%
+  add_header_above(c("", "Phono." = 3, "Sem." = 3)) %>%
+  column_spec(1, bold = TRUE) %>%
+  kable_styling(position = "center")
+
+```
 
@@
 Second we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model.
+The results are shown in Table \@ref(tab:powerLawProd) for production data, and in Table \@ref(tab:powerLawComp) for comprehension data.
 
-The results are shown in table XX.
-Overall, we could not reject the null hypothesis of a power-law distribution: the $p$-value was generally above 0.1.
-Also talk about the fact that the power law is truncated.
+Overall, we could not reject the null hypothesis of a power-law distribution: The $p$-value was generally above 0.1 in almost all languages for both production and comprehension.
+That said, phonological networks had relatively larger cut-offs than semantic networks.
+As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks ––as well as the observed cross-linguistic variability in the value of the cut-offs–– may reflect the various constraints that exist on word formation such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words.
+Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law.
 
@@
 Each point represents the mean of the posterior distribution of the growth parameter, with ranges representing 95\\% credible intervals.
-Positive values mean that learning proceeds according to the predictions of the growth scenario, whereas negative values mean that learning proceeds in opposition to the predictions of the growth scenario."}
+Positive values mean that learning proceeds according to the predictions of the growth scenario, whereas negative values mean that learning proceeds in opposition to the predictions of the growth scenario.", fig.width=8, fig.height=3}
 
@@
 
-### How does each growth scenario predict noun development?
-
-To test the network growth scenarios, we fit different growth models to the data.
-We calculated the probability that a word $w_i$, with a growth value $d_i$ would enter the lexicon at a given month, using a softmax function:
+To test the network growth scenarios, we fit two growth models to the data.
+We calculated the probability that a word $w_i$, with a utility value $u_i$ would enter the lexicon at a given month, using a softmax function:
 \begin{equation}
- p(w_i)= \frac{e^{\beta d_i}}{\sum_j e^{\beta d_j} }
+ p(w_i)= \frac{e^{\beta u_i}}{\sum_j e^{\beta u_j} }
 \end{equation}
@@
 \noindent where $\beta$ is a fitted parameter that captures the magnitude of the relationship between network parameters and growth (analogous to a regression coefficient).
-A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first (see Figure \@ref(fig:growth) for an illustration of how growth values $d_i$ are defined in each growth scenario).
+A positive value of $\beta$ means that words with higher utility values $u_i$ are acquired first, and a negative value means that words with lower utility values are acquired first (see Figure \@ref(fig:growth) for an illustration of how utilities values $u_i$ are defined in each growth scenario).
 The normalization includes all words that could be learned at that month.
@@
 
-The results replicate Hills et al.'s finding regarding the semantic netowrk in English and prouction data, which is that this network grows by EXT, not by INT.
-Besides, this finding generalize to comprehension, and holds overall across languages.
-One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
-However, our findings do not support this assumption, rather it supports our intial approximation, albeit a posteriori, about the unversisality of the semantic similarity measure.
-In the phonological domain, the EXT model also fits better the data than INT for both production and comprehension.
-Similar to the sematic domain, the findings generalize well cross-linguistically.
+First, the results replicate Hills et al.'s original finding regarding the semantic network in English and production data, which is that this network grows by EXT, not by INT.
+Second, our results show that, generally speaing, this finding generalizes to comprehension, and holds across languages.
+This generalization was obtained in both the semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
+However, our findings do not support this assumption, rather it supports our initial approximation about the universality of the semantic similarity measure.} and phonological domains.
 
@@
         #axis.text.x = element_text(size=7.5, angle=45)) +
-  scale_y_continuous(breaks =c(0,0.2))  +
+  scale_y_continuous(breaks =c(-1,0,1))  +
   #scale_y_discrete(breaks =NULL)
@@
 
-```{r staticPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined regression model.
+```{r staticPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression model in each language.
 Results are shown for both production and comprehension data.
@@
 longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
-words with higher frequency tend to have a lower AoA)."}
+words with higher frequency tend to have a lower AoA).", fig.width=8, fig.height=3}
 
@@
 Ranges indicate 95\\% confidence intervals.
-Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect."}
+Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.", fig.width=6, fig.height=2.5}
 
-knitr::include_graphics("figs/plot_static_preds_all.pdf")
+plot_static_preds_all
 
@@
 
-We saw that the way semantic and phonological information is structured in the learning environment (i.e., EXT) contributes to noun learning across languages.
+Above we showed that the way semantic and phonological information is structured in the learning environment contributes to noun learning (via EXT) across languages.
 However, we know that other factors influence learning as well [e.g., @braginsky2016].
@@
 @goodman2008].
-The second factor is word length, which correlates with phonological connectivity: Shorter words are more likely to have higher connectivity (Pisoni et al., 1985; Vitevitch and Rodriguez, 2004), and thus it critical to test if phonological connectivity plays a role in learning above and beyond word length.
+The second factor is word length, which was shown to correlate with phonological connectivity: Shorter words are more likely to have higher connectivity (Pisoni et al., 1985; Vitevitch and Rodriguez, 2004).
 
-Since the previous section showed that INT was uninformative, we dropped it from this analysis, keeping only EXT.
-This simplified the model because we no longer needed to fit growth month-by-month.The latter was a requirement only for INT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.
+Since we found INT to be uninformative, we dropped it from this analysis, keeping only EXT.
+This simplified the model because we no longer needed to fit growth month-by-month.
+The latter was a requirement only for INT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.
 A more direct way to assess and compare the contribution of EXT in relation to other word-level factors is through conducting linear regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.
@@
 "father" counts as "daddy").
-Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.
-The use of an independent dataset is warraned because it uses large samples to average out the difference between children (see Goodman et al.
+Although these frequency counts use transcripts from independent sets of children, they are based on large samples, and this allows us to average out possible differences between children and the specificities of their input (see Goodman et al.
 2008).
@@
 Word length is more predictive for production than comprehension (and this difference is very clear in the global model), replicating previous work (Braginsky et al., under review).
-Thus, word length seems to reflect the effects of production constraints rather than than comprehension constraints (i.e., long words are harder to pronounce than short words, but maybe not more difficult to store or access).
+Thus, word length seems to reflect the effects of production's constraints rather than than comprehension's constraints, i.e., longer words are harder to articulate but they may not be significantly more difficult to store and access.
 
 As for the factors of interest, i.e., semantic and phonological connectivity, we found cross-linguistic differences.
-Phonological connectivity contributes to learning in some languages but not in other.
+Connectivity contributes to learning in some languages but not in other.
 In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
@@
 Another important difference is the number of words tested: Our study uses a larger set of nouns.
-That said, and despite these cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.
+That said, and despite these apparent cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.
 
@@
 This study provided an analysis of network growth during development.
-We compared the two major network growth scenarios desribed in the pioneering work of @hills2009.
-The first scenario, INT (orignially called Preferentailly Attachement), described a rich-get-richer network growth model in which the current structure of the learner's internal network determines future growth; the other, EXT (orignially called Preferentailly Acquisition) described a model in which the external, global environmental network structure determines learners' growth patterns.
-Previous word in this line of research (e.g., @hills2009; @hills2010; Sailor 2013) has been limited in its scope: It focused on semantic networks, while relying only on words' production as a mesure of their acquisition, and using almost exclusively developmental data from English-learning children.
-This study test the generality previous findings first by investigting phonological networks together with semantic networks, second by adopting both production and comprehension as measures of learing, and crucially, by comparing the findings across 10 languages.
+We compared two network growth scenarios described in the pioneering work of @steyvers2005 and @hills2009.
+The first scenario, INT (originally called Preferential Attachment), described a rich-get-richer network growth model in which the current structure of the learner's internal network determines future growth; the other, EXT (originally called Preferential Acquisition) described a model in which the external, global environmental network structure determines learners' growth patterns.
+These two mechanisms represent two fundamentally different accounts of lexical growth: one suggests that future word knowledge is primarily shaped by the children’s past knowledge and its organization, whereas the other suggests that learning is shaped, rather, by salient properties in the input regardless of how past knowledge is organized.
 
-We found that the orginal findings reported in @hills2009 generalize well across all these dimensions.
-First, just like semantic networks, phonological networks grow via the externally-driven scenrio (EXT), not by the internally-driven mechanism (INT).
-Besides, both semantic and phonological networks contribute to the learning process above and beyond other known predcitors of word learning such as frequency and word length.
-Second, comprehension-based vocabularies grow in a way similar to production-based vocabularies [HERE ADD MORE NUANCE?].
-Finally, the findings were overall similar across the 10 languages we tested.
-Although we find some cross-lingusitic variation when semantic and phonological networks were pitted against frequency and length, this variability is to be taken with a grain of salt as it might be exaggerated in our study by the limited and partially-overlapping sample of nouns for each language.
-In fact, both phonological and semantic connectivity are significant predictors when data are pooled across languages.
+Previous work [@hills2009; @hills2010] has been limited in its scope: It focused primarily on semantic networks, production-based vocabularies, and developmental data from English-learning children.
+The present study tested the generality of previous findings by 1) investigating phonological networks together with semantic networks, 2) testing both comprehension- and production-based vocabularies, and 3) comparing the results across 10 languages.
+
+We found that the original findings reported in @hills2009 generalize well across all these dimensions.
+First, just like semantic networks, phonological networks grow via the externally-driven scenario (EXT), not by the internally-driven mechanism (INT).
+Second, comprehension-based vocabularies grow in a way similar to production-based vocabularies.
+Finally, the findings were, overall, similar across the 10 languages we tested.
+Although we find some cross-linguistic variation when semantic and phonological networks were pitted against frequency and length, this variability is to be taken with a grain of salt as it might be exaggerated in our study by the limited and partially-overlapping sample of nouns for each language.
+In fact, both phonological and semantic connectivity are significant predictors above and beyond frequency and length when data are pooled across languages.
 
@@
 This means, strikingly, that children are sensitive to highly connected words although they do not initially have access to the full network.
-This remarks begs the following question: What mechanism could allow children to tease apart highly connected words from low connected words?
+This finding raises some important questions.
+What mechanism allows children to distinguish highly connected words from other words?
 Besides, why would highly connected words be easier to learn?
 
-One possbility is that children rely on their statistical learning abilities.
+One possibility is that children rely on their statistical learning abilities.
 For example, in the semantic domain, children might be using a mechanism akin to cross-situational learning to pick up the meanings of some words, especially concrete nouns [@smith2008], and such learning would resemble the growth scenario described by EXT.
-Indeed, since free association is related to contextual co-occurrence (Griffiths et al., Fourtassi and Dupoux, 2013), highly connected words will tend to occur in a variety of speech and referential contexts.
-This fact makes such a word easier to learn  only because it has more referential disambiguating cues across learning contexts, and crucially, even without knowing the entire set of words with witch it occurs (hence the similarity with EXT).
-This possibility is supported by the finding that nouns' diverstiy of occurrence in child directed speech predicts their age of learing (@hills2010).
+Indeed, since free association is related to contextual co-occurrence (Griffiths et al., 2007), highly connected words will tend to occur in a variety of speech and referential contexts.
+This fact makes such words easier to learnonly because they have more referential disambiguating cues across learning contexts, and crucially, even without knowing the entire set of words with witch they occurs (hence the similarity with EXT).
+This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@hills2010].
 
@@
 Children are sensitive to local phonotactic regularities [@jusczyk1994] and this sensitivity might lead them to learn higher-probability words more easily [e.g., @storkel2001].
-This explanation is supported by computational simualtions that shows how learning general phonotactics patterns create ``well-worn paths'' which allow for the representation of several distinct but phonologically neighboring words (Dell et al; 1993; Tavac et al.
+This explanation is supported by computational simulations that shows how learning general phonotactics patterns create ``well-worn paths'' which allow the models to represent several distinct but phonologically neighboring words (Dell et al; 1993; Takac et al.
 2017).
 
-Besides using their own statitistical learning skills, children could also benefit from the the way their caregivers speak.
-Perhaps the cargivers put more emphasis on the words that are highly connected in _their_ mature lexical network.
+Besides using their own statistical learning skills, children could also benefit from the way their caregivers speak.
+Perhaps the caregivers put more emphasis on the words that are highly connected in _their_ mature lexical network.
 This emphasis would guide children to learn first these highly connected words even though children do not have access to the distribution of words' connectivity in the final network.
-Investigting this possibility would require further research on caregiver-child interaction (MacWhinney, 2014; Roy et al.
-2015), examining what words are introduced over development and the extent to which children's uptake is infuence by this input (Clark 2007;  Hoff and Naigles, 2002; Hurtado et al., 2008).
+Investigating this possibility would require further research on caregiver-child interaction [@macwhinney2014; @roy2015], examining what words are introduced over development and the extent to which children's uptake is influenced by this input (Clark 2007;  Hoff and Naigles, 2002; Hurtado et al., 2008).
 
@@
 2009; 2010).
-Chief among these limitations is the fact that the age of word acquisition is computed using different children at different ages (due to the fact that avialable CDI data is mainly cross-sectional).
-Althoug this measure has proven highly consistent (Fensen et al.
-1993), it lead us to focus on studying the learning mechanism of the "average" child.
+Chief among these limitations is the fact that the age of word acquisition is computed using different children at different ages (due to the fact that available CDI data is mainly cross-sectional).
+Although this measure has proven highly consistent (Fensen et al.
+1994), it lead us to focus on studying the learning mechanism of the "average" child.
 Individual trajectories, however, could show different learning patterns.
 For example, using longitudinal data @beckage2011 found differences between typical and late talkers in terms of the semantic network structure.
-Besides, although our study endorses the externally-driven account of network growth, this does not mean individual children never use some variant of the internally-driven mechanism.
-For instance, some children develop "islands of expertise", that is, well organized knowledge about a certain topic (e.g., birds or dinosaurs).
+Besides, although our study endorses the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT (Beckage and Colunga, under review).
+For example, some children develop "islands of expertise", that is, well organized knowledge about a certain topic (e.g., birds or dinosaurs).
 This prior knowledge enables these children to learn new related words more easily (e.g., Chi and Koeske, 1983).
 
-To conclude, our work validates previous results in early network development, and suggests that the advantage of highly connected words words may emerge, at least in the early stages of word learning, from the operation of simpler mechanisms in both the semantic and phonological domains.
+To conclude, our work validates and generalizes previous results in early network development.
+It suggests that the advantage of highly connected words may result, at least in the early stages of word learning, from the operation of simpler mechanisms in both the semantic and phonological domains.
 One question for future experimental work is whether such correlational patterns of growth can be produced in controlled behavioral experiments.
@@
 
-# Appendix 1: Power law model
-
-```{r powerLaw2, results="asis", echo=FALSE}
-
-powerL <- feather::read_feather("../saved_data/degree_test.feather") %>%
-  rename(Kmin = xMin) %>%
-  rename(pValue = pVal)
-
-powerProd <- powerL %>%
-  dplyr::filter(measure == 'produces') %>%
-  select(-measure)
-
-powerComp <- powerL %>%
-  dplyr::filter(measure == 'understands') %>%
-  select(-measure)
-
-#rownames(statistics) <- NULL
-
-tabProd <- xtable::xtable(powerProd,
-                      caption = "Results of fitting a power law model to the degree distribution in each model for production data.
-Kmin is the optimal degree cut-off, alpha is the scaling parameter, and pValue is the probability that quantifies the plausibility of the power law hypothesis.
-If pValue is close to 1, the power law model cannot be rejected as a plausible fit for the data.
-If, instead, pValue is small (e.g., p < 0.05) then the null hypothesis of a power law model can be rejected.")
-
-tabComp <- xtable::xtable(powerComp,
-                      caption = "Results of fitting a power law model to the degree distribution in each model for comprehension data.
-Kmin is the optimal degree cut-off, alpha is the scaling parameter, and pValue is the probability that quantifies the plausibility of the power law hypothesis.
-If pValue is close to 1, the power law model cannot be rejected as a plausible fit for the data.
-If, instead, pValue is small (e.g., p < 0.05) then the null hypothesis of a power law model can be rejected.")
-
-print(tabProd, type="latex", comment = F, table.placement = "H")
-print(tabComp, type="latex", comment = F, table.placement = "H")
-```
-
 # References

### 2018-10-30 journal/ms.tex
journal

@@
 present study tests both scenarios systematically in both the
-phonological and semantic domains, and across 8 languages. We show that
+phonological and semantic domains across 10 languages. We show that
 external connectivity in the learning environment drives growth in both
-the semantic and the phonological networks, and that this pattern is
-consistent cross-linguistically. The findings suggest a word learning
-mechanism where children harness their statistical learning abilities to
-(indirectly) detect and learn highly connected words in the learning
-environment.}
+production- and comprehension-based vocabularies. The findings suggest a
+word learning mechanism where children harness their statistical
+learning abilities to (indirectly) detect and learn highly connected
+words in the learning environment.}
   \keywords{Language understanding; audio-visual processing; word learning; speech
@@
 target-cue relationships in free association norms, co-occurrence in
-child directed speech, and phonological similarity. These studies have
+child directed speech, and phonological relatedness. These studies have
 found that children tend to produce words that have higher neighborhood
 density (i.e., high connectivity in the network) earlier, both at the
-phonological and the semantic level (Engelthaler \& Hills, 2017; Hills,
-Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya, \&
-Smith, 2009; Stella, Beckage, \& Brede, 2017; Storkel, 2009) add
-Beckage, 2011 and other people\ldots{}
+phonological and the semantic level (Carlson, Sonderegger, \& Bane,
+2014; Hills, Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene,
+Sheya, \& Smith, 2009; Stella, Beckage, \& Brede, 2017; Storkel, 2009).
 
@@
 
-{\centering \includegraphics[width=400px]{figs/growth2}
+{\centering \includegraphics[width=300px]{figs/growth3}
 
@@
 \caption{Illustration of the two growth scenarios.
-Filled circles (I1-I4) represent known words (Internal), and empty circles (E1 and E2) represent words that have not been learned yet (External).
-Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
+Filled grey circles represent known words (Internal) at a certain point in time.
+The empty, numbered circles represent words that have not yet been learned (External) and which are candidates to enter the lexicon next.
+The identity of the word that is going to be learned depends on the growth scenario.
+Here the squares indicate the node that drives growth in each scenario and the hand pointer indicates which word is likely to be learned.
 For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
-Thus, according to INT, the node E1 is more likely to enter the lexicon first.
+Thus, according to INT, the node 1 is more likely to enter the lexicon.
 For EXT, the utility of a candidate node is its degree in the entire network.
-According to EXT, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
+According to EXT, the node 2 is more likely to enter the lexicon next.}\label{fig:growth}
 \end{figure}
@@
 (2005), but rather through EXT. This finding, though potentially very
-profound, has only been estabished in the special case of networks that
-are based on 1) semantic associations, 2) word production as a measure
-of acquisition, and 2) data from English-learning children, only. The
-extent to which this result depends on the domain, the measure and
-culture/languagae is still unclear. In this work, we test the generality
-of the finding along these three dimesnions.
+profound, has only been established in the special case of networks that
+are based on 1) semantic associations, 2) production-based vocabularies,
+and 2) data from English-learning children, only. The extent to which
+this result depends on the domain, the measure and culture/language is
+still unclear. In this work, we test the generality of the finding along
+these three dimensions.
 
@@
 network. These two networks represent different ways the mental lexicon
-is strcutured. In particular, words that are neighbors in the semantic
+is structured. In particular, words that are neighbors in the semantic
 network (e.g., \enquote{cat}, \enquote{dog}) are not necessarily
@@
 find an effect of words' connectivity in the phonological network on
-their age of learning (Storkel, 2004, 2009; Stokes 2014). In other
-words, words learned earlier in life tend to sound similar to many other
-words than a word learned later in life. However, as mentioned above,
-this finding did not examine the underlying learning
-mechanism.\footnote{In particular, this finding is compatible with both INT and EXT.}
-Here, we investigate whether phonological networks, like semantic
-networks, grow through EXT, or if they rather grow via INT
-(Figure~\ref{fig:growth}).
+their age of learning (Carlson et al., 2014; Stella et al., 2017;
+Storkel, 2009). In other words, words learned earlier in life tend to
+sound similar to many other words than a word learned later in life.
+However, this finding is compatible with both INT and EXT, and previous
+studies did not explicitly compare these two mechanisms. Here, we
+investigate whether phonological networks, like semantic networks, grow
+through EXT, or if they rather grow via INT (Figure~\ref{fig:growth}).
 
@@
 production. Previous studies have found differences between these
-vocabularies in terms of their content and rate of acquistion (Benedict,
-1979; Fensen et al. 1993). These differences can be due to the fact that
-comprehension and production do not share the same contraints. For
-instance, whereas comprehension depends on the ease with which words are
-stored and accessed, production depends additionally on the ease with
-witch words are articuated (e.g., shorter words are produced earlier,
-Braginsky et al. 2016). By including comprehension-based vocabularies in
-our analysis, we assess the extent to which the network growth
-mechanisms capture general learning patterns beyond the specific
-constraints of production.
+vocabularies in terms of their content and rate of acquisition
+(Benedict, 1979; Fenson et al., 1994). These differences may reflect the
+fact that comprehension and production do not share the same
+constraints. For instance, whereas comprehension depends on the ease
+with which words are stored and accessed, production depends,
+additionally, on the ease with which words are articulated, e.g.,
+shorter words are produced earlier (Braginsky et al., 2016). By
+investigating comprehension-based vocabularies, we assess the extent to
+which the network growth mechanism captures general learning patterns
+beyond the specific constraints of production.
 
 Finally, we use developmental data in 10 languages. Lexical networks can
-show more or less cross-lingustic variability along both the semantic
-and phonological domains (Youn et al. 2015; Arbesman et al.
-2009).\footnote{The difference is more obvious in the phonolgical case where the network strcuture––and the distribution of word connectivity––can a priori change from language to language depending on various languisitc conventions.}
-Besides, cultures might differ in the way caregivers guide the
-chidlren's learning patterns or in the way the adults' linguistic input
-is organized (Kuhl et al., 1997; Cristia et al. 2017), and this
-difference could influecne the learning mechanism. Thus,
-Cross-linguistic comparison is crucial to test what mechanism is
-cognitively universal and is used by all children, and what mechansism
-is specific to some patterns of learning that emerge due to the
-particulars of a given language or culture (Bates \& MacWhinney, 1987;
-Slobin, 1985).
+show more or less cross-linguistic variability along both the semantic
+and phonological domains (Arbesman, Strogatz, \& Vitevitch, 2010; Youn
+et al.,
+2016).\footnote{The difference is more obvious in the phonological case where the network structure––and the distribution of word connectivity––can a priori change from language to language depending on various languistic conventions.}
+Besides, cultures might differ in the way caregivers talk to children
+(Cristia, Dupoux, Gurven, \& Stieglitz, 2017; Kuhl et al., 1997), and
+this difference in the input could influence the chidlren's learning
+strategy. Thus, Cross-linguistic comparison is crucial to test what
+mechanism is cognitively universal and is used by all children, and what
+mechanism is specific to some patterns of learning that emerge due to
+the particulars of a given language or culture (Bates \& MacWhinney,
+1987; Slobin, 2014).
 
-HERE ORGANIZATION OF THE PAPER
+The paper is organized as follows. First, we describe the datasets we
+used and explain how we constructed the networks. Second, we analyze
+static properties of words' connectivity in these networks (correlation
+with AoA and shape of the distribution) and we explain how these
+properties infom hypotheses about network growth. Next, we explicitly
+fit the two hypothesized growth mechanisms to the data. We investigate
+the extent to which the results obtained in Hills et al. (2009)
+generalize to phonological networks and comprehension-based
+vocabularies, and whether this generalization holds
+cross-linguistically.
 
@@
 child \enquote{understands} (comprehension) or \enquote{understands and
-says} (production) for each of about 400 words. For youner chidlren
-(between 8 and 18 months), both comprehension and production are
-queried, whereas for oder chidlren (between 16 to 36 months) only
-production is queried. We use data from younger chidlren to test
-comprehension and data from older chidlren to test production. Following
-previous studies (Hills et al., 2009; Storkel, 2009), we restrict our
-analysis to nouns. Table \ref{tab:stats} gives an overview of the data
-source.
+says} (production) each of about 400-700 words. For younger children
+(e.g., 8 to 18 months in the English data), both comprehension and
+production are queried, whereas for older children (16 to 36 months)
+only production is queried. We use data from younger children to test
+comprehension and data from older children to test production across 10
+languages. Following previous studies (Hills et al., 2009; Storkel,
+2009), we restrict our analysis to nouns. Table \ref{tab:stats} gives an
+overview of the data.
 
@@
 
-For each word in CDI data, we compute the proportion of children who
+For each word in the CDI data, we compute the proportion of children who
 understand or produce the word at each month. Then we fit a logistic
 curve to these proportions and determined when the curve crosses 0.5,
-i.e., the age at which at lest 50\% of chidlren know the word. We take
-this point in time to be each word's age of acquisition (J. C. Goodman
-et al., 2008) and Braginsky.
+i.e., the age at which at least 50\% of children know the word. We take
+this point in time to be each word's age of acquisition (Braginsky et
+al., 2016; J. C. Goodman et al., 2008).
 
-\begin{table}[H]
+\begin{table}
+
+\caption{\label{tab:stats}Statistics for data from Wordbank.}
 \centering
-\begin{tabular}{rlrrr}
-  \hline
- & language & total & translated & normed \\ 
-  \hline
-1 & Croatian & 253 & 177 & 170 \\ 
-  2 & Danish & 295 & 198 & 187 \\ 
-  3 & English & 296 & 296 & 274 \\ 
-  4 & Italian & 311 & 203 & 194 \\ 
-  5 & Norwegian & 305 & 193 & 186 \\ 
-  6 & Russian & 311 & 311 & 285 \\ 
-  7 & Spanish & 240 & 173 & 163 \\ 
-  8 & Turkish & 293 & 175 & 164 \\ 
-   \hline
+\begin{tabular}[t]{>{\bfseries}lrlrl}
+\toprule
+\multicolumn{1}{c}{} & \multicolumn{2}{c}{Comprehension} & \multicolumn{2}{c}{Production} \\
+\cmidrule(l{2pt}r{2pt}){2-3} \cmidrule(l{2pt}r{2pt}){4-5}
+Language & Nouns & Ages & Nouns & Ages\\
+\midrule
+Croatian & 209 & 8-16 & 312 & 16-30\\
+Danish & 200 & 8-20 & 316 & 16-36\\
+English & 209 & 8-18 & 312 & 16-30\\
+French & 197 & 8-16 & 307 & 16-30\\
+Italian & 209 & 7-24 & 312 & 18-36\\
+Norwegian & 193 & 8-20 & 316 & 16-36\\
+Russian & 207 & 8-18 & 314 & 18-36\\
+Spanish & 208 & 8-18 & 312 & 16-30\\
+Swedish & 205 & 8-16 & 339 & 16-28\\
+Turkish & 180 & 8-16 & 297 & 16-36\\
+\bottomrule
 \end{tabular}
-\caption{\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left).
-We included in our study the subset of these nouns that had available English translations (middle).
-The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).}
 \end{table}
@@
 We constructed semantic networks for English data following the
-procedure outlined in Hills et al. (2009). We used as an index of
-semantic relatedness the Florida Free Association Norms (Nelson, McEvoy,
-\& Schreiber, 1998). This dataset was collected by giving adult
-participants a word (the cue), and asking them to write the first word
-that comes to mind (the target). For example, when given the word
-\enquote{ball}, they might answer with the word \enquote{game}. A pair
-of nodes were connected by a directed link from the cue to the target if
-there was a cue-target relationship between these nodes in the
+procedure outlined in Hills et al. (2009), as follows. We used as an
+index of semantic relatedness the Florida Free Association Norms
+(Nelson, McEvoy, \& Schreiber, 1998). This dataset was collected by
+giving adult participants a word (the cue), and asking them to write the
+first word that comes to mind (the target). For example, when given the
+word \enquote{ball}, they might answer with the word \enquote{game}. A
+pair of nodes were connected by a directed link from the cue to the
+target if there was a cue-target relationship between these nodes in the
 association norms. The connectivity of a given node was characterized by
@@
 
-Free Association norms are available only in English. We used the
-hand-checked translation equivalents available in Wordbank, which
-allowed us to use the English association norms across languages. Note
-that this does not necessarily mean that the resulting networks will be
-the same across languages, or that these networks will grow similarly.
-Though using the same association data acoss langauges assumes that the
-semantic similarity measure is universal (which is a reasonable
-approximation, Youn et al. 2015), the set of words acquired by children
-as well as the timeline of this acquisition can still vary from language
-to language leading to possbility different learing strategies.
+Since the free association norms are available only in English, we used
+the hand-checked translation equivalents available in Wordbank, which
+allowed us to use the English association norms across languages. Using
+the same association data across languages does not necessarily mean
+that the resulting networks will be the same across languages, or that
+these networks will grow similarly. Indeed, though this approximation
+assumes that the semantic similarity measure is universal----which is a
+reasonable assumption (e.g., Youn et al. 2015), the set of words
+acquired by children as well as the timeline of this acquisition can
+still vary from language to language leading to possibility different
+learning strategies.
 
@@
 
-To construct phonological networks we first mapped the orthogrphic
-transcrition of words to their International Phonetic Alphabet (IPA)
-transcriptions, across languages, using the open source text-to-speech
+To construct phonological networks we first mapped the orthographic
+transcription of words to their International Phonetic Alphabet (IPA)
+transcriptions in each language, using the open source text-to-speech
 software \textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.}
@@
 In previous studies, two nodes were linked if they had an edit distance
-of 1 (e.g., Storkel, 2009). However, in these previous studies the
-network was built using an adult vocabulary. In the current study,
-however, network growth models are based on the children's early
-vocabulary which contains very few word pairs with an edit distance of
-1. When using this threshold, the resulting networks were too sparse and
-uninformative. Thus, we increased the threshold from 1 to 2, that is,
-two nodes were related if their edit distance was equal to 1 or 2. The
-connectivity of a given node was characterized with its \emph{degree}:
-the number of links it shares with other words.
+of 1 (Carlson et al., 2014; Stella et al., 2017; Storkel, 2009).
+However, these studies reported a contribution of phonological networks
+to word learning when these networks were built using a rich adult
+vocabulary. However, since the focus of the current study is on the
+mechanism of growth, the networks should be based on the children's
+early vocabulary which, nevertheless, contains very few word pairs with
+an edit distance of 1. Thus, we increased the threshold from 1 to 2,
+that is, two nodes were related if their edit distance was equal to 1 or
+2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold.
+In both cases, the results were weaker that those done with a threshold of 2.}
+The connectivity of a given node was characterized with its
+\emph{degree}: the number of links it shares with other words.
 
@@
 analyze properties of this global networks that are relevant to INT
-and/or EXT.
+and/or EXT. In order to compare various predictors on the same data, we
+restrict the analysis to the subset of nouns for which we had both
+semantic and phonological information in each language.
 
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/corrAll-1} \caption{Age of production (A) and comprehension (B) in the global network as predicted by the degree in this network.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrAll-1} \caption{Age of production (A) and comprehension (B) in the global network as predicted by the degree (i.e., connectivity) in this network.
 Results are shown in each language for phonological and semantic networks.
-Each point is a word, with lines indicating linear model fits.}\label{fig:corrAll}
+Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrAll}
 \end{figure}
@@
 what words should be learned first (Figure \ref{fig:growth}). Therefore,
-a direct consequence of a EXT-like growth scenario is a correlation
+a direct consequence of an EXT-like growth scenario is a correlation
 between connectivity in the global network and the age of
@@
 Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.}
-Figure \ref{fig:corrAll} shows how the age of production (A) and
-comprehension (B) for each word varies as a function of its degree (or
-indegree for the semantic networks). For ease of visual comparison, the
-predictor (i.e., the degree) was centered and scaled across languages.
+Figure \ref{fig:corrAll} shows how the age of production and
+comprehension for each word varies as a function of its degree (or
+indegree for the semantic networks) as well as the correlation values.
+For ease of visual comparison, the predictor (i.e., the degree) was
+centered and scaled across languages.
+
 The plots show, overall, a negative correlation between the month of
-acquisition and the degree, indicating that nouns with higher degrees
-are generally learned earlier. HERE MENTION THE AVERAGE VALUE OF THE
-CORRELATIONS
+acquisition and the degree. In production data, the average correlation
+across languages was -0.24 (SD=0.10) for the semantic networks and -0.30
+(SD=0.05) for the phonological networks. In comprehension data, the
+average correlation was -0.21 (SD=0.08) for the semantic networks and
+-0.21 (SD=0.07) for the phonological networks. These results indicate
+that nouns with higher degrees are generally learned earlier, thus
+replicating previous findings in English (e.g., Storkel 2004, 2009;
+Hills et al. 2009) and extending these findings to ten different
+languages (with few exceptions) in both production- and
+comprehension-based vocabularies.
 
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{figs/plot_degree} \caption{Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/degreeDist-1} \caption{Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
 The figure shows the results for both production and comprehension data.
@@
 scenario is known to generate networks with a power-law degree
-distribution (i.e., a distribution of the form
-\(p(k) \propto \frac{1}{k^{\alpha}}\), Barabasi \& Albert, 1999). If the
-network displays this property, this fact would suggest a INT-like
+distribution, i.e., a distribution of the form
+\(p(k) \propto \frac{1}{k^{\alpha}}\) (Barabasi \& Albert, 1999). If the
+network displays this property, this fact would suggest an INT-like
 generative process. Conversely, if the degree distribution does not
@@
 each empirical degree distribution following the procedure outlined in
-Clauset, Shalizi, and Newman (2009) and using the related R package
+Clauset, Shalizi, and Newman (2009) and using a related R package
 (poweRlaw, Gillespie, 2015).
+
+\begin{table}
+
+\caption{\label{tab:powerLawProd}Results of fitting a power law model to the degree (i.e., connectivity) distribution in each model for production data.
+Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis.
+If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.}
+\centering
+\begin{tabular}[t]{>{\bfseries}lrrrrrr}
+\toprule
+\multicolumn{1}{c}{} & \multicolumn{3}{c}{Phono.} & \multicolumn{3}{c}{Sem.} \\
+\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
+Language & cut-off & alpha & p-value & cut-off & alpha & p-value\\
+\midrule
+Croatian & 4 & 2.18 & 0.123 & 4 & 2.55 & 0.881\\
+Danish & 11 & 4.55 & 0.858 & 4 & 2.38 & 0.001\\
+English & 20 & 9.14 & 0.511 & 5 & 2.66 & 0.132\\
+French & 20 & 3.75 & 0.112 & 8 & 2.81 & 0.133\\
+Italian & 9 & 9.45 & 0.780 & 4 & 2.93 & 0.608\\
+Norwegian & 15 & 6.28 & 0.744 & 5 & 2.88 & 0.201\\
+Russian & 8 & 4.20 & 0.541 & 24 & 5.61 & 0.723\\
+Spanish & 13 & 8.75 & 0.736 & 4 & 2.98 & 0.460\\
+Swedish & 11 & 4.68 & 0.103 & 4 & 2.49 & 0.171\\
+Turkish & 8 & 3.26 & 0.375 & 4 & 2.87 & 0.925\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:powerLawComp}Results of fitting a power law model to the degree distribution in each model for comprehension data.
+Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis.
+If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.}
+\centering
+\begin{tabular}[t]{>{\bfseries}lrrrrrr}
+\toprule
+\multicolumn{1}{c}{} & \multicolumn{3}{c}{Phono.} & \multicolumn{3}{c}{Sem.} \\
+\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
+Language & cut-off & alpha & p-value & cut-off & alpha & p-value\\
+\midrule
+Croatian & 2 & 2.06 & 0.020 & 5 & 2.67 & 0.895\\
+Danish & 5 & 2.98 & 0.136 & 4 & 2.39 & 0.005\\
+English & 13 & 5.16 & 0.235 & 4 & 2.64 & 0.765\\
+French & 18 & 5.58 & 0.336 & 4 & 2.63 & 0.330\\
+Italian & 8 & 10.27 & 0.909 & 4 & 2.88 & 0.688\\
+Norwegian & 13 & 7.65 & 0.440 & 5 & 2.87 & 0.433\\
+Russian & 5 & 3.97 & 0.854 & 8 & 3.91 & 0.952\\
+Spanish & 5 & 3.01 & 0.085 & 5 & 3.11 & 0.552\\
+Swedish & 9 & 6.75 & 0.102 & 5 & 2.81 & 0.713\\
+Turkish & 9 & 5.73 & 0.958 & 4 & 3.13 & 0.887\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 we calculated the goodness-to-fit, which resulted in a \(p\)-value
-quantifying the plausibility of the model.
+quantifying the plausibility of the model. The results are shown in
+Table \ref{tab:powerLawProd} for production data, and in Table
+\ref{tab:powerLawComp} for comprehension data.
 
-The results are shown in table XX. Overall, we could not reject the null
-hypothesis of a power-law distribution: the \(p\)-value was generally
-above 0.1. Also talk about the fact that the power law is truncated.
+Overall, we could not reject the null hypothesis of a power-law
+distribution: The \(p\)-value was generally above 0.1 in almost all
+languages for both production and comprehension. That said, phonological
+networks had relatively larger cut-offs than semantic networks. As was
+suggested by Arbesman et al. (2010), these \enquote{truncated}
+power-laws in phonological networks ----as well as the observed
+cross-linguistic variability in the value of the cut-offs---- may
+reflect the various constraints that exist on word formation such as the
+number of phonemes in the language, the phonotactics (i.e., the way
+sound sequences are arranged in words), and the length of words. Such
+constraints may limit the number of words that are phonologically
+similar, thus leading to distributions which decay faster than a
+non-truncated power law.
 
@@
 
-\subsubsection{How does each growth scenario predict noun
-development?}\label{how-does-each-growth-scenario-predict-noun-development}
-
-To test the network growth scenarios, we fit different growth models to
-the data. We calculated the probability that a word \(w_i\), with a
-growth value \(d_i\) would enter the lexicon at a given month, using a
-softmax function:
+To test the network growth scenarios, we fit two growth models to the
+data. We calculated the probability that a word \(w_i\), with a utility
+value \(u_i\) would enter the lexicon at a given month, using a softmax
+function:
 
 \begin{equation}
- p(w_i)= \frac{e^{\beta d_i}}{\sum_j e^{\beta d_j} }
+ p(w_i)= \frac{e^{\beta u_i}}{\sum_j e^{\beta u_j} }
 \end{equation}
@@
 (analogous to a regression coefficient). A positive value of \(\beta\)
-means that words with higher growth values \(d_i\) are acquired first,
-and a negative value means that words with lower growth values are
+means that words with higher utility values \(u_i\) are acquired first,
+and a negative value means that words with lower utility values are
 acquired first (see Figure \ref{fig:growth} for an illustration of how
-growth values \(d_i\) are defined in each growth scenario). The
+utilities values \(u_i\) are defined in each growth scenario). The
 normalization includes all words that could be learned at that month.
@@
 
-The results replicate Hills et al.'s finding regarding the semantic
-netowrk in English and prouction data, which is that this network grows
-by EXT, not by INT. Besides, this finding generalize to comprehension,
-and holds overall across languages. One could imagine that the fact of
-using English free association norms cross-linguistically would decrease
-the effect of non-English semantic networks because of possible cultural
-differences. However, our findings do not support this assumption,
-rather it supports our intial approximation, albeit a posteriori, about
-the unversisality of the semantic similarity measure. In the
-phonological domain, the EXT model also fits better the data than INT
-for both production and comprehension. Similar to the sematic domain,
-the findings generalize well cross-linguistically.
+First, the results replicate Hills et al.'s original finding regarding
+the semantic network in English and production data, which is that this
+network grows by EXT, not by INT. Second, our results show that,
+generally speaing, this finding generalizes to comprehension, and holds
+across languages. This generalization was obtained in both the
+semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
+However, our findings do not support this assumption, rather it supports our initial approximation about the universality of the semantic similarity measure.}
+and phonological domains.
 
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPred-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined regression model.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPred-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression model in each language.
 Results are shown for both production and comprehension data.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{figs/plot_static_preds_all} \caption{Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAll-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect.
 Results are shown for both production and comprehension data.
@@
 
-We saw that the way semantic and phonological information is structured
-in the learning environment (i.e., EXT) contributes to noun learning
-across languages. However, we know that other factors influence learning
-as well (e.g., Braginsky et al., 2016). Next we investigated how
-semantic and phonological connectivity interact with two other factors.
-The first one is word frequency, a well studied factor shown to predict
-the age of acquisition in a reliable fashion (e.g. J. C. Goodman et al.,
-2008). The second factor is word length, which correlates with
-phonological connectivity: Shorter words are more likely to have higher
-connectivity (Pisoni et al., 1985; Vitevitch and Rodriguez, 2004), and
-thus it critical to test if phonological connectivity plays a role in
-learning above and beyond word length.
+Above we showed that the way semantic and phonological information is
+structured in the learning environment contributes to noun learning (via
+EXT) across languages. However, we know that other factors influence
+learning as well (e.g., Braginsky et al., 2016). Next we investigated
+how semantic and phonological connectivity interact with two other
+factors. The first one is word frequency, a well studied factor shown to
+predict the age of acquisition in a reliable fashion (e.g. J. C. Goodman
+et al., 2008). The second factor is word length, which was shown to
+correlate with phonological connectivity: Shorter words are more likely
+to have higher connectivity (Pisoni et al., 1985; Vitevitch and
+Rodriguez, 2004).
 
-Since the previous section showed that INT was uninformative, we dropped
-it from this analysis, keeping only EXT. This simplified the model
-because we no longer needed to fit growth month-by-month.The latter was
-a requirement only for INT where the words' utilities varied from month
-to month, depending on how connectivity changed in the growing internal
-network. A more direct way to assess and compare the contribution of EXT
-in relation to other word-level factors is through conducting linear
+Since we found INT to be uninformative, we dropped it from this
+analysis, keeping only EXT. This simplified the model because we no
+longer needed to fit growth month-by-month. The latter was a requirement
+only for INT where the words' utilities varied from month to month,
+depending on how connectivity changed in the growing internal network. A
+more direct way to assess and compare the contribution of EXT in
+relation to other word-level factors is through conducting linear
 regressions, where connectivity in the learning environment, frequency
@@
 counts as \enquote{cat}), or words that were synonymous (e.g.
-\enquote{father} counts as \enquote{daddy}). Note that these frequency
-counts are based on transcripts from independent sets of children and
-represent a general estimate of environmental frequency across children.
-The use of an independent dataset is warraned because it uses large
-samples to average out the difference between children (see Goodman et
+\enquote{father} counts as \enquote{daddy}). Although these frequency
+counts use transcripts from independent sets of children, they are based
+on large samples, and this allows us to average out possible differences
+between children and the specificities of their input (see Goodman et
 al. 2008).
@@
 al., under review). Thus, word length seems to reflect the effects of
-production constraints rather than than comprehension constraints (i.e.,
-long words are harder to pronounce than short words, but maybe not more
-difficult to store or access).
+production's constraints rather than than comprehension's constraints,
+i.e., longer words are harder to articulate but they may not be
+significantly more difficult to store and access.
 
 As for the factors of interest, i.e., semantic and phonological
-connectivity, we found cross-linguistic differences. Phonological
-connectivity contributes to learning in some languages but not in other.
-In particular, semantic connectivity does not explain variance in
-English data beyond that explained by phonological connectivity,
-frequency and length. This contrasts with the original finding in Hills
-et al. (2009). However, in this previous study, semantic connectivity
-was not tested in a model that included frequency, length and
-phonological connectivity as covariates. Another important difference is
-the number of words tested: Our study uses a larger set of nouns. That
-said, and despite these cross-linguistic differences, both phonological
-and semantic connectivity are significant predictors in the combined
-model.
+connectivity, we found cross-linguistic differences. Connectivity
+contributes to learning in some languages but not in other. In
+particular, semantic connectivity does not explain variance in English
+data beyond that explained by phonological connectivity, frequency and
+length. This contrasts with the original finding in Hills et al. (2009).
+However, in this previous study, semantic connectivity was not tested in
+a model that included frequency, length and phonological connectivity as
+covariates. Another important difference is the number of words tested:
+Our study uses a larger set of nouns. That said, and despite these
+apparent cross-linguistic differences, both phonological and semantic
+connectivity are significant predictors in the combined model.
 
@@
 This study provided an analysis of network growth during development. We
-compared the two major network growth scenarios desribed in the
-pioneering work of Hills et al. (2009). The first scenario, INT
-(orignially called Preferentailly Attachement), described a
+compared two network growth scenarios described in the pioneering work
+of Steyvers and Tenenbaum (2005) and Hills et al. (2009). The first
+scenario, INT (originally called Preferential Attachment), described a
 rich-get-richer network growth model in which the current structure of
 the learner's internal network determines future growth; the other, EXT
-(orignially called Preferentailly Acquisition) described a model in
-which the external, global environmental network structure determines
-learners' growth patterns. Previous word in this line of research (e.g.,
-Hills et al. (2009); Hills et al. (2010); Sailor 2013) has been limited
-in its scope: It focused on semantic networks, while relying only on
-words' production as a mesure of their acquisition, and using almost
-exclusively developmental data from English-learning children. This
-study test the generality previous findings first by investigting
-phonological networks together with semantic networks, second by
-adopting both production and comprehension as measures of learing, and
-crucially, by comparing the findings across 10 languages.
+(originally called Preferential Acquisition) described a model in which
+the external, global environmental network structure determines
+learners' growth patterns. These two mechanisms represent two
+fundamentally different accounts of lexical growth: one suggests that
+future word knowledge is primarily shaped by the children's past
+knowledge and its organization, whereas the other suggests that learning
+is shaped, rather, by salient properties in the input regardless of how
+past knowledge is organized.
 
-We found that the orginal findings reported in Hills et al. (2009)
+Previous work (Hills et al., 2010, 2009) has been limited in its scope:
+It focused primarily on semantic networks, production-based
+vocabularies, and developmental data from English-learning children. The
+present study tested the generality of previous findings by 1)
+investigating phonological networks together with semantic networks, 2)
+testing both comprehension- and production-based vocabularies, and 3)
+comparing the results across 10 languages.
+
+We found that the original findings reported in Hills et al. (2009)
 generalize well across all these dimensions. First, just like semantic
-networks, phonological networks grow via the externally-driven scenrio
-(EXT), not by the internally-driven mechanism (INT). Besides, both
-semantic and phonological networks contribute to the learning process
-above and beyond other known predcitors of word learning such as
-frequency and word length. Second, comprehension-based vocabularies grow
-in a way similar to production-based vocabularies {[}HERE ADD MORE
-NUANCE?{]}. Finally, the findings were overall similar across the 10
-languages we tested. Although we find some cross-lingusitic variation
-when semantic and phonological networks were pitted against frequency
-and length, this variability is to be taken with a grain of salt as it
-might be exaggerated in our study by the limited and
-partially-overlapping sample of nouns for each language. In fact, both
-phonological and semantic connectivity are significant predictors when
-data are pooled across languages.
+networks, phonological networks grow via the externally-driven scenario
+(EXT), not by the internally-driven mechanism (INT). Second,
+comprehension-based vocabularies grow in a way similar to
+production-based vocabularies. Finally, the findings were, overall,
+similar across the 10 languages we tested. Although we find some
+cross-linguistic variation when semantic and phonological networks were
+pitted against frequency and length, this variability is to be taken
+with a grain of salt as it might be exaggerated in our study by the
+limited and partially-overlapping sample of nouns for each language. In
+fact, both phonological and semantic connectivity are significant
+predictors above and beyond frequency and length when data are pooled
+across languages.
 
@@
 although they do not initially have access to the full network. This
-remarks begs the following question: What mechanism could allow children
-to tease apart highly connected words from low connected words? Besides,
-why would highly connected words be easier to learn?
+finding raises some important questions. What mechanism allows children
+to distinguish highly connected words from other words? Besides, why
+would highly connected words be easier to learn?
 
-One possbility is that children rely on their statistical learning
+One possibility is that children rely on their statistical learning
 abilities. For example, in the semantic domain, children might be using
@@
 since free association is related to contextual co-occurrence (Griffiths
-et al., Fourtassi and Dupoux, 2013), highly connected words will tend to
-occur in a variety of speech and referential contexts. This fact makes
-such a word easier to learn only because it has more referential
-disambiguating cues across learning contexts, and crucially, even
-without knowing the entire set of words with witch it occurs (hence the
-similarity with EXT). This possibility is supported by the finding that
-nouns' diverstiy of occurrence in child directed speech predicts their
-age of learing (Hills et al. (2010)).
+et al., 2007), highly connected words will tend to occur in a variety of
+speech and referential contexts. This fact makes such words easier to
+learnonly because they have more referential disambiguating cues across
+learning contexts, and crucially, even without knowing the entire set of
+words with witch they occurs (hence the similarity with EXT). This
+possibility is supported by the finding that words' diversity of
+occurrence in child directed speech predicts their age of learning
+(Hills et al., 2010).
 
@@
 connectivity in the phonological network is inherently correlated with
-phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
-is, highly connected words tend to be made of frequent sound sequences.
-Children are sensitive to local phonotactic regularities (Jusczyk, Luce,
-\& Charles-Luce, 1994) and this sensitivity might lead them to learn
-higher-probability words more easily (e.g., Storkel, 2001). This
-explanation is supported by computational simualtions that shows how
-learning general phonotactics patterns create ``well-worn paths'' which
-allow for the representation of several distinct but phonologically
-neighboring words (Dell et al; 1993; Tavac et al. 2017).
+phonotactic probability (M. S. Vitevitch, Luce, Pisoni, \& Auer, 1999).
+That is, highly connected words tend to be made of frequent sound
+sequences. Children are sensitive to local phonotactic regularities
+(Jusczyk, Luce, \& Charles-Luce, 1994) and this sensitivity might lead
+them to learn higher-probability words more easily (e.g., Storkel,
+2001). This explanation is supported by computational simulations that
+shows how learning general phonotactics patterns create ``well-worn
+paths'' which allow the models to represent several distinct but
+phonologically neighboring words (Dell et al; 1993; Takac et al. 2017).
 
-Besides using their own statitistical learning skills, children could
-also benefit from the the way their caregivers speak. Perhaps the
-cargivers put more emphasis on the words that are highly connected in
-\emph{their} mature lexical network. This emphasis would guide children
-to learn first these highly connected words even though children do not
-have access to the distribution of words' connectivity in the final
-network. Investigting this possibility would require further research on
-caregiver-child interaction (MacWhinney, 2014; Roy et al. 2015),
+Besides using their own statistical learning skills, children could also
+benefit from the way their caregivers speak. Perhaps the caregivers put
+more emphasis on the words that are highly connected in \emph{their}
+mature lexical network. This emphasis would guide children to learn
+first these highly connected words even though children do not have
+access to the distribution of words' connectivity in the final network.
+Investigating this possibility would require further research on
+caregiver-child interaction (MacWhinney, 2014; B. C. Roy et al., 2015),
 examining what words are introduced over development and the extent to
-which children's uptake is infuence by this input (Clark 2007; Hoff and
-Naigles, 2002; Hurtado et al., 2008).
+which children's uptake is influenced by this input (Clark 2007; Hoff
+and Naigles, 2002; Hurtado et al., 2008).
 
@@
 acquisition is computed using different children at different ages (due
-to the fact that avialable CDI data is mainly cross-sectional). Althoug
-this measure has proven highly consistent (Fensen et al. 1993), it lead
+to the fact that available CDI data is mainly cross-sectional). Although
+this measure has proven highly consistent (Fensen et al. 1994), it lead
 us to focus on studying the learning mechanism of the \enquote{average}
@@
 externally-driven account of network growth, this does not mean
-individual children never use some variant of the internally-driven
-mechanism. For instance, some children develop \enquote{islands of
-expertise}, that is, well organized knowledge about a certain topic
-(e.g., birds or dinosaurs). This prior knowledge enables these children
-to learn new related words more easily (e.g., Chi and Koeske, 1983).
+individual children never use some variant of INT or some combination of
+both INT and EXT (Beckage and Colunga, under review). For example, some
+children develop \enquote{islands of expertise}, that is, well organized
+knowledge about a certain topic (e.g., birds or dinosaurs). This prior
+knowledge enables these children to learn new related words more easily
+(e.g., Chi and Koeske, 1983).
 
-To conclude, our work validates previous results in early network
-development, and suggests that the advantage of highly connected words
-words may emerge, at least in the early stages of word learning, from
-the operation of simpler mechanisms in both the semantic and
-phonological domains. One question for future experimental work is
+To conclude, our work validates and generalizes previous results in
+early network development. It suggests that the advantage of highly
+connected words may result, at least in the early stages of word
+learning, from the operation of simpler mechanisms in both the semantic
+and phonological domains. One question for future experimental work is
 whether such correlational patterns of growth can be produced in
@@
 
-\section{Appendix 1: Power law model}\label{appendix-1-power-law-model}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{rrrrll}
-  \hline
- & Kmin & alpha & pValue & dimension & language \\ 
-  \hline
-1 & 4.00 & 2.55 & 0.88 & Sem & Croatian \\ 
-  2 & 4.00 & 2.18 & 0.12 & Phono & Croatian \\ 
-  3 & 4.00 & 2.38 & 0.00 & Sem & Danish \\ 
-  4 & 11.00 & 4.55 & 0.86 & Phono & Danish \\ 
-  5 & 5.00 & 2.66 & 0.13 & Sem & English \\ 
-  6 & 20.00 & 9.14 & 0.51 & Phono & English \\ 
-  7 & 8.00 & 2.81 & 0.13 & Sem & French \\ 
-  8 & 20.00 & 3.75 & 0.11 & Phono & French \\ 
-  9 & 4.00 & 2.93 & 0.61 & Sem & Italian \\ 
-  10 & 9.00 & 9.45 & 0.78 & Phono & Italian \\ 
-  11 & 5.00 & 2.88 & 0.20 & Sem & Norwegian \\ 
-  12 & 15.00 & 6.28 & 0.74 & Phono & Norwegian \\ 
-  13 & 24.00 & 5.61 & 0.72 & Sem & Russian \\ 
-  14 & 8.00 & 4.20 & 0.54 & Phono & Russian \\ 
-  15 & 4.00 & 2.98 & 0.46 & Sem & Spanish \\ 
-  16 & 13.00 & 8.75 & 0.74 & Phono & Spanish \\ 
-  17 & 4.00 & 2.49 & 0.17 & Sem & Swedish \\ 
-  18 & 11.00 & 4.68 & 0.10 & Phono & Swedish \\ 
-  19 & 4.00 & 2.87 & 0.93 & Sem & Turkish \\ 
-  20 & 8.00 & 3.26 & 0.38 & Phono & Turkish \\ 
-   \hline
-\end{tabular}
-\caption{Results of fitting a power law model to the degree distribution in each model for production data.
-Kmin is the optimal degree cut-off, alpha is the scaling parameter, and pValue is the probability that quantifies the plausibility of the power law hypothesis.
-If pValue is close to 1, the power law model cannot be rejected as a plausible fit for the data.
-If, instead, pValue is small (e.g., p < 0.05) then the null hypothesis of a power law model can be rejected.}
-\end{table}\begin{table}[H]
-\centering
-\begin{tabular}{rrrrll}
-  \hline
- & Kmin & alpha & pValue & dimension & language \\ 
-  \hline
-1 & 5.00 & 2.67 & 0.90 & Sem & Croatian \\ 
-  2 & 2.00 & 2.06 & 0.02 & Phono & Croatian \\ 
-  3 & 4.00 & 2.39 & 0.01 & Sem & Danish \\ 
-  4 & 5.00 & 2.98 & 0.14 & Phono & Danish \\ 
-  5 & 4.00 & 2.64 & 0.77 & Sem & English \\ 
-  6 & 13.00 & 5.16 & 0.23 & Phono & English \\ 
-  7 & 4.00 & 2.63 & 0.33 & Sem & French \\ 
-  8 & 18.00 & 5.58 & 0.34 & Phono & French \\ 
-  9 & 4.00 & 2.88 & 0.69 & Sem & Italian \\ 
-  10 & 8.00 & 10.27 & 0.91 & Phono & Italian \\ 
-  11 & 5.00 & 2.87 & 0.43 & Sem & Norwegian \\ 
-  12 & 13.00 & 7.65 & 0.44 & Phono & Norwegian \\ 
-  13 & 8.00 & 3.91 & 0.95 & Sem & Russian \\ 
-  14 & 5.00 & 3.97 & 0.85 & Phono & Russian \\ 
-  15 & 5.00 & 3.11 & 0.55 & Sem & Spanish \\ 
-  16 & 5.00 & 3.01 & 0.09 & Phono & Spanish \\ 
-  17 & 5.00 & 2.81 & 0.71 & Sem & Swedish \\ 
-  18 & 9.00 & 6.75 & 0.10 & Phono & Swedish \\ 
-  19 & 4.00 & 3.13 & 0.89 & Sem & Turkish \\ 
-  20 & 9.00 & 5.73 & 0.96 & Phono & Turkish \\ 
-   \hline
-\end{tabular}
-\caption{Results of fitting a power law model to the degree distribution in each model for comprehension data.
-Kmin is the optimal degree cut-off, alpha is the scaling parameter, and pValue is the probability that quantifies the plausibility of the power law hypothesis.
-If pValue is close to 1, the power law model cannot be rejected as a plausible fit for the data.
-If, instead, pValue is small (e.g., p < 0.05) then the null hypothesis of a power law model can be rejected.}
-\end{table}
-
 \section{References}\label{references}
@@
 \hypertarget{refs}{}
+\hypertarget{ref-arbesman2010}{}
+Arbesman, S., Strogatz, S. H., \& Vitevitch, M. S. (2010). The structure
+of phonological networks across multiple languages. \emph{International
+Journal of Bifurcation and Chaos}, \emph{20}(03), 679--685.
+
 \hypertarget{ref-barabasi99}{}
@@
 networks. \emph{Science}, \emph{286}(5439), 509--512.
+
+\hypertarget{ref-bates1987}{}
+Bates, E., \& MacWhinney, B. (1987). Competition, variation, and
+language learning. \emph{Mechanisms of Language Acquisition}, 157--193.
 
@@
 \emph{6}(5), 1--6.
+
+\hypertarget{ref-benedict1979}{}
+Benedict, H. (1979). Early lexical development: Comprehension and
+production. \emph{Journal of Child Language}, \emph{6}(2), 183--200.
 
@@
 
+\hypertarget{ref-carlson2014}{}
+Carlson, M. T., Sonderegger, M., \& Bane, M. (2014). How children
+explore the phonological network in child-directed speech: A survival
+analysis of children?s first word productions. \emph{Journal of Memory
+and Language}, \emph{75}, 159--180.
+
 \hypertarget{ref-clauset09}{}
@@
 
-\hypertarget{ref-engelthaler2017}{}
-Engelthaler, T., \& Hills, T. T. (2017). Feature biases in early word
-learning: Network distinctiveness predicts age of acquisition.
-\emph{Cognitive Science}, \emph{41}, 120--140.
+\hypertarget{ref-cristia2017}{}
+Cristia, A., Dupoux, E., Gurven, M., \& Stieglitz, J. (2017).
+Child-directed speech is infrequent in a forager-farmer population: A
+time allocation study. \emph{Child Development}.
 
@@
 communicative development. \emph{Monographs of the Society for Research
-in Child Development}, \emph{59}(5), i--185.
+in Child Development}, \emph{59}(5).
 
@@
 
+\hypertarget{ref-kuhl1997}{}
+Kuhl, P. K., Andruski, J. E., Chistovich, I. A., Chistovich, L. A.,
+Kozhevnikova, E. V., Ryskina, V. L., \ldots{} Lacerda, F. (1997).
+Cross-language analysis of phonetic units in language addressed to
+infants. \emph{Science}, \emph{277}(5326), 684--686.
+
+\hypertarget{ref-macwhinney2014}{}
+MacWhinney, B. (2014). \emph{The childes project: Tools for analyzing
+talk, volume ii: The database}. Psychology Press.
+
 \hypertarget{ref-markman90}{}
@@
 Academy of Sciences}, \emph{112}(41), 12663--12668.
+
+\hypertarget{ref-slobin2014}{}
+Slobin, D. I. (2014). \emph{The crosslinguistic study of language
+acquisition} (Vol. 4). Psychology Press.
 
@@
 
+\hypertarget{ref-youn2016}{}
+Youn, H., Sutton, L., Smith, E., Moore, C., Wilkins, J. F., Maddieson,
+I., \ldots{} Bhattacharya, T. (2016). On the universal structure of
+human lexical semantics. \emph{Proceedings of the National Academy of
+Sciences}, \emph{113}(7), 1766--1771.
+
 \end{document}

### 2018-10-30 main_analyses.Rmd
journal

@@
   library(HDInterval)
+  library(kableExtra)
 ```
@@
 
+Here compute the statistics 
+language, measure, number of nouns, age limits, and number  
+```{r}
+
+mysummary <- data_all %>%
+  group_by(language, measure) %>%
+  summarise(min_age = min(age),
+            max_age = max(age),
+            nouns = n_distinct(item)) %>%
+  mutate(age_range = paste(min_age, max_age, sep = "-")) %>%
+  select(-min_age, -max_age)  %>%
+  group_by(language, measure) %>%
+  nest() %>%
+  spread(measure, data) %>%
+  unnest(.sep = "_") %>%
+  select(language, un = understands_nouns, ua=understands_age_range,
+                   pn = produces_nouns, pa=produces_age_range)
+
+feather::write_feather(mysummary, "saved_data/stats_new.feather")
+
+kable(mysummary, format = "latex", escape = FALSE, booktabs = TRUE,
+      linesep = "", format.args = list(big.mark = ","),
+      caption = "Statistics for data from Wordbank.",
+      col.names = c("Language",  "Nouns", "Ages", "Nouns", "Ages")) %>%
+  add_header_above(c("", "Comprehension" = 2, "Production" = 2)) %>%
+  column_spec(1, bold = TRUE) %>%
+  kable_styling(position = "center")
+
+```
+
 Compute Age of Acqusition (AoA) of words
@@
 
-#I should here define the set of words that will be used in the network construction
-#Here I chose to use the full data for the phono netwotk and filter later for the unilemmas only, thus the utility will be more precise for the resulting subset
+#Here I chose to use the full data for the phono netwotk and filter later for the unilemmas only when doing what?
+the combined regression?, thus the utility will be more precise for the resulting subset
 
@@
   lemma_list<- growth_meas_lang %>%
-      trim_all_unilemma() %>%
+      trim_all_unilemma() %>% #For semantic netowtks only the unilmma
       filter(age==first_age) %>%
@@
 #feather::write_feather(sem_red, "saved_data/sem_red.feather")
-#sem_red <- feather::read_feather("saved_data/sem_red.feather")
+sem_red <- feather::read_feather("saved_data/sem_red.feather")
 
@@
 #feather::write_feather(phono_red, "saved_data/phono_red.feather")
-#phono_red <- feather::read_feather("saved_data/phono_red.feather")
+phono_red <- feather::read_feather("saved_data/phono_red.feather")
 
@@
 
-#Word frequency: we use frequency values derived from Childes (from Mika e al. 2016)
-
+#Word frequency: we use frequency values derived from Cross-lingusitic corpora in CHILDES (from Mika e al. 2016) 
 load("saved_data/uni_joined.RData")
@@
 ```{r}
+
 #Sem_deg is defined over unilemmas,  phono_deg is defined over definitions, and AoA is defined over items 
 #For a given defintion we can have more than one item (polysemy), for one unilemma we can have more than one definiton (if the semantic distinction is not very important), or we might have 0 unilemma (if the meaning of the defintion is not part of the main cross-lingusitc lemmas)
-#The following analyses predict try to predict the items' AoA.
+#The following analyses predict the items' AoA.
 I keep duplicated values of the predictors for different items (when they have the same defintions and/or unilemma) since I consider that this is the actual (albeit braod) information brough by the precitors
@@
 
-### Small world properties
-
-Use igraph to derive small world properties
-
-For each netwrok, compute:
--Clustering coefficient 
--Shortest path length 
-what we want: Compared to an equivalent random network, we want a balance between local processing (high clustering coefficient) and global integration (small short path length)
-
 ## Growth mechanisms
@@
   filter(!is.na(uni_lemma)) %>% #use only words with english translation 
-  filter(!is.na(PAC_assoc)) %>% # keep unilemma whcih intersect with free association data
-  filter(!is.na(PAC_phono_t2)) # In case a word is not trnascribed phonologically (there should not be any)
+  filter(!is.na(PAC_assoc)) %>% # keep unilemma which intersect with free association data
+  filter(!is.na(PAC_phono_t2)) # In case a word is not transcribed phonologically (there should not be any)
 

### 2018-11-12 journal/ms.Rmd
journal corrections

@@
 One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words.
-Another view suggests that learning is driven  by highly connected words in the external learning environment instead of highly connected words in the early internal lexicon.
+Another view suggests that learning is driven  by highly connected words in the external learning environment, instead of highly connected words in the early internal lexicon.
 The present study tests both scenarios systematically in both the phonological and semantic domains across 10 languages.
-We show that external connectivity in the learning environment drives growth in both production- and comprehension-based vocabularies.
-The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment.
+We show that external connectivity in the learning environment drives growth in both production- and comprehension-based vocabularies, even controlling for word frequency and length.
+This pattern of findings suggests a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment.
 
@@
 
-Besides these word-level properties, the lexical structure (that is, how words relate to each other) also influences the age of acquisition of words.
-The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words (e.g., Collins and Loftus, 1975).
+Besides these word-level properties, the structure of the lexicon (that is, how words relate to each other) also predicts the age of acquisition of words.
+The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words [e.g., @collins1975].
 Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological relatedness.
@@
 Figure\ \@ref(fig:growth) shows an illustration of both growth scenarios with the same simplified network.
+
 These two proposals represent two divergent ideas about the role of lexical networks in acquisition.
-On the INT proposal, network structure is a causal factor in early word learning; in contrast, on the EXT approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguistic input.
+On the INT proposal, learning is driven by known words with high connectivity to other known words (Figure 1, left).
+Thus, the network structure is a causal factor in early word learning, that is, children might be relying on the organization of their past knowledge to determine future learning.
+For example, having a rich and organized knowledge about the domain of dinosaurs would facilitate the acquisition of new dinosaur-related words [@chi1983].
+In contrast, on the EXT approach, learning is driven by the connectivity of words that are not known yet (Figure 1, right).
+Thus, the relevant network structure is not internally represented by children, and the related connectivity effect might be an epiphenomenon of some low level properties of the linguistic input.
+For example, highly connected words in the input could be more easily learned because of their contextual diversity [e.g., @smith2008] or because caregivers emphasize such words in child-directed speech [@macwhinney2014].
 
@@
 
-@hills2009 found that early lexical networks do not grow through INT as was originally hypothesised by @steyvers2005, but rather through EXT.
-This finding, though potentially very profound, has only been established in the special case of networks that are based on 1) semantic associations,  2) production-based vocabularies, and 2) data from English-learning children, only.
-The extent to which this result depends on the domain, the measure and culture/language is still unclear.
+@hills2009 investigated the growth of lexico-semantic networks in toddlers and found that growth did not proceed according to INT as was originally hypothesised by @steyvers2005, but rather according to EXT.\footnote{Besides INT and EXT, the authors tested a third mechanism (called the lure of associates) which resembles EXT in that it is driven by the connectivity of external nodes, except that this connectivity is computed with respect to words that are known.
+However, EXT is the externally-driven scenario that best predicted the data in this previous work.} This is a profound finding because it suggests that learning in the early stages is mostly driven by properties of the external input, regardless of how past knowledge is organized.
+However, this work has been done in the special case of networks that are based on 1) semantic associations, 2) production-based vocabularies, and 2) data from English-learning children, only.
+The extent to which this result depends on the domain (e.g., semantic vs.
+phonological connectivity), the vocabulary measure (production vs.
+comprehension) and culture/language is still unclear.
 In this work, we test the generality of the finding along these three dimensions.
@@
 In particular, words that are neighbors in the semantic network (e.g., "cat", "dog") are not necessarily neighbors in the phonological network, and vice versa.
-Does the phonological network also influence word learning?
+Does the phonological network also predict word learning?
 Previous work did find an effect of words' connectivity in the phonological network on their age of learning [@storkel2009; @stella2017; @carlson2014].
 In other words, words learned earlier in life tend to sound similar to many other words than a word learned later in life.
-However, this finding is compatible with both INT and EXT, and previous studies did not explicitly compare these two mechanisms.
+However, this finding is *a priori* compatible with both INT and EXT, and previous studies did not explicitly compare these two mechanisms.
 Here, we investigate whether phonological networks, like semantic networks, grow through EXT, or if they rather grow via INT (Figure\ \@ref(fig:growth)).
@@
 Finally, we use developmental data in 10 languages.
-Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains [@youn2016; @arbesman2010].\footnote{The difference is more obvious in the phonological case where the network structure––and the distribution of word connectivity––can a priori change from language to language depending on various languistic conventions.} Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the chidlren's learning strategy.
+Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains [@youn2016; @arbesman2010].
+Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the children's learning strategy.
 Thus, Cross-linguistic comparison is crucial to test what mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014].
+ <!--
+\footnote{The difference is more obvious in the phonological case where the network structure––and the distribution of word connectivity––can a priori change from language to language depending on various languistic conventions.}
+-->
+
+We test the growth scenarios using parent reports of children vocabularies and their normative age of acquisition [@fenson94].
+Children may vary in their individual learning trajectories, but the aggregate data leads to an average learning pattern which is highly consistent.
+It is this normative trajectory that we model in the current study, following the steps of previous research using similar datasets [@storkel2009; @stella2017; @hills2009; @hills2010; @goodman2008; @braginsky2016]
 
@@
 For younger children (e.g., 8 to 18 months in the English data), both comprehension and production are queried, whereas for older children (16 to 36 months) only production is queried.
-We use data from younger children to test comprehension and data from older children to test production across 10 languages.
+Thus, we use data from younger children to test comprehension and data from older children to test production across 10 languages.
 Following previous studies [@storkel2009; @hills2009], we restrict our analysis to nouns.
@@
       linesep = "", format.args = list(big.mark = ","),
-      caption = "Statistics for data from Wordbank.",
+      caption = "Statistics for dataset we used.",
       col.names = c("Language",  "Nouns", "Ages", "Nouns", "Ages")) %>%
@@
 Using the same association data across languages does not necessarily mean that the resulting networks will be the same across languages, or that these networks will grow similarly.
-Indeed, though this approximation assumes that the semantic similarity measure is universal––which is a reasonable assumption (e.g., Youn et al.
-2015), the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possibility different learning strategies.
+Indeed, though this approximation assumes that the semantic similarity measure is universal––which is a reasonable assumption [e.g., @youn2016], the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possibility different learning strategies.
 
@@
 These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English (e.g., Storkel 2004, 2009; Hills et al.
-2009) and extending these findings to ten different languages (with few exceptions) in both production- and comprehension-based vocabularies.
+2009) and extending these findings to ten different languages, generally, in both production- and comprehension-based vocabularies.
 
@@
 The shape of this distribution is particularly relevant to INT as this growth scenario is known to generate networks with a power-law degree distribution, i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$ [@barabasi99].
-If the network displays this property, this fact would suggest an INT-like generative process.
-Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for INT.
+If the network displays this property, this fact would suggest, but not prove, an INT-like generative process.
+If the degree distribution does not follow a power law, this  would largely weaken the case for INT.
 The log-log plots are shown in Figure \@ref(fig:degreeDist).
@@
 That said, phonological networks had relatively larger cut-offs than semantic networks.
-As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks ––as well as the observed cross-linguistic variability in the value of the cut-offs–– may reflect the various constraints that exist on word formation such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words.
+As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks–as well as the observed cross-linguistic variability in the value of the cut-offs–may reflect the various constraints that exist on word formation such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words.
 Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law.
@@
 First, the results replicate Hills et al.'s original finding regarding the semantic network in English and production data, which is that this network grows by EXT, not by INT.
-Second, our results show that, generally speaing, this finding generalizes to comprehension, and holds across languages.
+Second, our results show that, generally speaking, this finding generalizes to comprehension, and holds across languages.
 This generalization was obtained in both the semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
@@
 @goodman2008].
-The second factor is word length, which was shown to correlate with phonological connectivity: Shorter words are more likely to have higher connectivity (Pisoni et al., 1985; Vitevitch and Rodriguez, 2004).
+The second factor is word length, which was shown to correlate with phonological connectivity: Shorter words are more likely to have higher connectivity [@pisoni1985; @vitevitch2005].
 
@@
 For word length, we counted the number of phonemes in our generated IPA transcription.
-For word frequency, we used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language (MacWhinney, 2000).
+For word frequency, we used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language [@macwhinney2014].
 For each word, counts included words that shared the same stem  (e.g., "cats" counts as "cat"), or words that were synonymous (e.g.
 "father" counts as "daddy").
-Although these frequency counts use transcripts from independent sets of children, they are based on large samples, and this allows us to average out possible differences between children and the specificities of their input (see Goodman et al.
-2008).
+Although these frequency counts use transcripts from independent sets of children, they are based on large samples, and this allows us to average out possible differences between children and the specificities of their input [see @goodman2008].
 
@@
 This contrasts with the original finding in @hills2009.
-However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates.
-Another important difference is the number of words tested: Our study uses a larger set of nouns.
+However, this might be due to our using of a slightly different model (which included word length as a covariate) and a larger dataset.
 That said, and despite these apparent cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.
@@
 The first scenario, INT (originally called Preferential Attachment), described a rich-get-richer network growth model in which the current structure of the learner's internal network determines future growth; the other, EXT (originally called Preferential Acquisition) described a model in which the external, global environmental network structure determines learners' growth patterns.
-These two mechanisms represent two fundamentally different accounts of lexical growth: one suggests that future word knowledge is primarily shaped by the children’s past knowledge and its organization, whereas the other suggests that learning is shaped, rather, by salient properties in the input regardless of how past knowledge is organized.
-
-Previous work [@hills2009; @hills2010] has been limited in its scope: It focused primarily on semantic networks, production-based vocabularies, and developmental data from English-learning children.
-The present study tested the generality of previous findings by 1) investigating phonological networks together with semantic networks, 2) testing both comprehension- and production-based vocabularies, and 3) comparing the results across 10 languages.
+These two mechanisms represent two fundamentally different accounts of lexical growth: One suggests that future word knowledge is primarily shaped by the children’s past knowledge and its organization, whereas the other suggests that learning is shaped, rather, by salient properties in the input regardless of how past knowledge is organized.
+The present study tested the generality of previous findings [@hills2009; @hills2010] by 1) investigating phonological networks together with semantic networks, 2) testing both comprehension- and production-based vocabularies, and 3) comparing the results across 10 languages.
 
@@
 These findings corroborate the hypothesis that children start by learning words that have high similarity to a variety of other words in the learning environment, not in the child's available lexicon.
-This means, strikingly, that children are sensitive to highly connected words although they do not initially have access to the full network.
-This finding raises some important questions.
-What mechanism allows children to distinguish highly connected words from other words?
+This hypothesis implies that children are sensitive to highly connected words although they do not initially have access to the full network, thus raising some important questions: What mechanism allows children to distinguish highly connected words from other words?
 Besides, why would highly connected words be easier to learn?
 
-One possibility is that children rely on their statistical learning abilities.
-For example, in the semantic domain, children might be using a mechanism akin to cross-situational learning to pick up the meanings of some words, especially concrete nouns [@smith2008], and such learning would resemble the growth scenario described by EXT.
-Indeed, since free association is related to contextual co-occurrence (Griffiths et al., 2007), highly connected words will tend to occur in a variety of speech and referential contexts.
-This fact makes such words easier to learnonly because they have more referential disambiguating cues across learning contexts, and crucially, even without knowing the entire set of words with witch they occurs (hence the similarity with EXT).
+One possibility is that these patterns emerge from children’s use of statistical learning abilities [@saffran1996; @aslin2012; @smith2008].
+The term "statistical learning" has been used in the developmental literature to describes the process by which one acquires information about their environment through tracking the frequency distribution of some elements (e.g., words) in different contexts.
+An important property of this kind of learning is that it occurs without explicit instructions and through mere exposure to the input.
+Previous work in the line of research has documented mechanisms which can explain the patterns found in the current study.
+
+For example, in the semantic domain, growth according to EXT can be explained by a mechanism similar to cross-situational learning [@smith2008; @pinker2013; @yurovsky2015].
+According to this mechanism, children track the co-occurrence of concrete nouns with their possible semantic referents.
+The referent of a word heard in only one naming situation can be ambiguous (e.g., when the word "ball" is heard for the first time in the presence of both a ball and a chair), but hearing the same word in a diversity of semantic contexts allows  the learner  to  narrow down the set of possible word-object mappings.
+In our case, free association is related to contextual co-occurrence [@griffiths07], meaning that highly connected words will tend to occur in a variety of speech and referential contexts.
+This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts, and crucially, even without knowing the entire set of words with witch they co-occur (hence the similarity with EXT).
 This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@hills2010].
@@
 That is, highly connected words tend to be made of frequent sound sequences.
-Children are sensitive to local phonotactic regularities [@jusczyk1994] and this sensitivity might lead them to learn higher-probability words more easily [e.g., @storkel2001].
-This explanation is supported by computational simulations that shows how learning general phonotactics patterns create ``well-worn paths'' which allow the models to represent several distinct but phonologically neighboring words (Dell et al; 1993; Takac et al.
-2017).
+Children are sensitive to local phonotactic regularities [@jusczyk1994] and this sensitivity might lead them to learn higher-probability words more easily [@storkel2001].
+This explanation is supported by computational simulations that shows how learning general phonotactics patterns create ``well-worn paths'' which allow the models to represent several distinct but phonologically neighboring words [@dell1993; @takac2017].
 
 Besides using their own statistical learning skills, children could also benefit from the way their caregivers speak.
-Perhaps the caregivers put more emphasis on the words that are highly connected in _their_ mature lexical network.
+Perhaps the caregivers put more emphasis on the words that are highly connected in *their* mature lexical network.
 This emphasis would guide children to learn first these highly connected words even though children do not have access to the distribution of words' connectivity in the final network.
-Investigating this possibility would require further research on caregiver-child interaction [@macwhinney2014; @roy2015], examining what words are introduced over development and the extent to which children's uptake is influenced by this input (Clark 2007;  Hoff and Naigles, 2002; Hurtado et al., 2008).
+Investigating this possibility would require further research on caregiver-child interaction [@macwhinney2014; @roy2015], examining what words are introduced over development and the extent to which children's uptake is influenced by this input [@clark2007; @hoff2002].
 
-This work shares a number of limitations with previous studies using similar research strategy and datasets (e.g., Hills et al.
-2009; 2010).
+This work shares a number of limitations with previous studies using similar research strategy and datasets.
 Chief among these limitations is the fact that the age of word acquisition is computed using different children at different ages (due to the fact that available CDI data is mainly cross-sectional).
-Although this measure has proven highly consistent (Fensen et al.
-1994), it lead us to focus on studying the learning mechanism of the "average" child.
+Although this measure has proven highly consistent [@fenson94], it led us to focus on studying the learning mechanism of the "average" child.
 Individual trajectories, however, could show different learning patterns.
@@
 For example, some children develop "islands of expertise", that is, well organized knowledge about a certain topic (e.g., birds or dinosaurs).
-This prior knowledge enables these children to learn new related words more easily (e.g., Chi and Koeske, 1983).
+This prior knowledge enables these children to learn new related words more easily [e.g., @chi1983].
 

### 2018-11-12 journal/ms.tex
journal corrections

@@
 lexicon attract similar words. Another view suggests that learning is
-driven by highly connected words in the external learning environment
+driven by highly connected words in the external learning environment,
 instead of highly connected words in the early internal lexicon. The
@@
 external connectivity in the learning environment drives growth in both
-production- and comprehension-based vocabularies. The findings suggest a
-word learning mechanism where children harness their statistical
-learning abilities to (indirectly) detect and learn highly connected
-words in the learning environment.}
+production- and comprehension-based vocabularies, even controlling for
+word frequency and length. This pattern of findings suggests a word
+learning mechanism where children harness their statistical learning
+abilities to (indirectly) detect and learn highly connected words in the
+learning environment.}
   \keywords{Language understanding; audio-visual processing; word learning; speech
@@
 
-Besides these word-level properties, the lexical structure (that is, how
-words relate to each other) also influences the age of acquisition of
-words. The lexical structure can be characterized in terms of a network
-where each node represents a word in the vocabulary, and each link
-between two nodes represents a relationship between the corresponding
-pair of words (e.g., Collins and Loftus, 1975). Previous studies have
-investigated early vocabulary structure by constructing networks using a
-variety of word-word relations including shared semantic features,
-target-cue relationships in free association norms, co-occurrence in
-child directed speech, and phonological relatedness. These studies have
-found that children tend to produce words that have higher neighborhood
-density (i.e., high connectivity in the network) earlier, both at the
-phonological and the semantic level (Carlson, Sonderegger, \& Bane,
-2014; Hills, Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene,
-Sheya, \& Smith, 2009; Stella, Beckage, \& Brede, 2017; Storkel, 2009).
+Besides these word-level properties, the structure of the lexicon (that
+is, how words relate to each other) also predicts the age of acquisition
+of words. The lexical structure can be characterized in terms of a
+network where each node represents a word in the vocabulary, and each
+link between two nodes represents a relationship between the
+corresponding pair of words (e.g., Collins \& Loftus, 1975). Previous
+studies have investigated early vocabulary structure by constructing
+networks using a variety of word-word relations including shared
+semantic features, target-cue relationships in free association norms,
+co-occurrence in child directed speech, and phonological relatedness.
+These studies have found that children tend to produce words that have
+higher neighborhood density (i.e., high connectivity in the network)
+earlier, both at the phonological and the semantic level (Carlson,
+Sonderegger, \& Bane, 2014; Hills, Maouene, Riordan, \& Smith, 2010;
+Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Stella, Beckage, \&
+Brede, 2017; Storkel, 2009).
 
@@
 Figure~\ref{fig:growth} shows an illustration of both growth scenarios
-with the same simplified network. These two proposals represent two
-divergent ideas about the role of lexical networks in acquisition. On
-the INT proposal, network structure is a causal factor in early word
-learning; in contrast, on the EXT approach, network structure is not
-internally represented and, therefore, might be an epiphenomenon of the
-statistics of the linguistic input.
+with the same simplified network.
+
+These two proposals represent two divergent ideas about the role of
+lexical networks in acquisition. On the INT proposal, learning is driven
+by known words with high connectivity to other known words (Figure 1,
+left). Thus, the network structure is a causal factor in early word
+learning, that is, children might be relying on the organization of
+their past knowledge to determine future learning. For example, having a
+rich and organized knowledge about the domain of dinosaurs would
+facilitate the acquisition of new dinosaur-related words (Chi \& Koeske,
+1983). In contrast, on the EXT approach, learning is driven by the
+connectivity of words that are not known yet (Figure 1, right). Thus,
+the relevant network structure is not internally represented by
+children, and the related connectivity effect might be an epiphenomenon
+of some low level properties of the linguistic input. For example,
+highly connected words in the input could be more easily learned because
+of their contextual diversity (e.g., Smith \& Yu, 2008) or because
+caregivers emphasize such words in child-directed speech (MacWhinney,
+2014).
 
@@
 
-Hills et al. (2009) found that early lexical networks do not grow
-through INT as was originally hypothesised by Steyvers and Tenenbaum
-(2005), but rather through EXT. This finding, though potentially very
-profound, has only been established in the special case of networks that
-are based on 1) semantic associations, 2) production-based vocabularies,
-and 2) data from English-learning children, only. The extent to which
-this result depends on the domain, the measure and culture/language is
-still unclear. In this work, we test the generality of the finding along
-these three dimensions.
+Hills et al. (2009) investigated the growth of lexico-semantic networks
+in toddlers and found that growth did not proceed according to INT as
+was originally hypothesised by Steyvers and Tenenbaum (2005), but rather
+according to
+EXT.\footnote{Besides INT and EXT, the authors tested a third mechanism (called the lure of associates) which resembles EXT in that it is driven by the connectivity of external nodes, except that this connectivity is computed with respect to words that are known.
+However, EXT is the externally-driven scenario that best predicted the data in this previous work.}
+This is a profound finding because it suggests that learning in the
+early stages is mostly driven by properties of the external input,
+regardless of how past knowledge is organized. However, this work has
+been done in the special case of networks that are based on 1) semantic
+associations, 2) production-based vocabularies, and 2) data from
+English-learning children, only. The extent to which this result depends
+on the domain (e.g., semantic vs.~phonological connectivity), the
+vocabulary measure (production vs.~comprehension) and culture/language
+is still unclear. In this work, we test the generality of the finding
+along these three dimensions.
 
@@
 neighbors in the phonological network, and vice versa. Does the
-phonological network also influence word learning? Previous work did
-find an effect of words' connectivity in the phonological network on
-their age of learning (Carlson et al., 2014; Stella et al., 2017;
-Storkel, 2009). In other words, words learned earlier in life tend to
-sound similar to many other words than a word learned later in life.
-However, this finding is compatible with both INT and EXT, and previous
-studies did not explicitly compare these two mechanisms. Here, we
-investigate whether phonological networks, like semantic networks, grow
-through EXT, or if they rather grow via INT (Figure~\ref{fig:growth}).
+phonological network also predict word learning? Previous work did find
+an effect of words' connectivity in the phonological network on their
+age of learning (Carlson et al., 2014; Stella et al., 2017; Storkel,
+2009). In other words, words learned earlier in life tend to sound
+similar to many other words than a word learned later in life. However,
+this finding is \emph{a priori} compatible with both INT and EXT, and
+previous studies did not explicitly compare these two mechanisms. Here,
+we investigate whether phonological networks, like semantic networks,
+grow through EXT, or if they rather grow via INT
+(Figure~\ref{fig:growth}).
 
@@
 and phonological domains (Arbesman, Strogatz, \& Vitevitch, 2010; Youn
-et al.,
-2016).\footnote{The difference is more obvious in the phonological case where the network structure––and the distribution of word connectivity––can a priori change from language to language depending on various languistic conventions.}
-Besides, cultures might differ in the way caregivers talk to children
-(Cristia, Dupoux, Gurven, \& Stieglitz, 2017; Kuhl et al., 1997), and
-this difference in the input could influence the chidlren's learning
-strategy. Thus, Cross-linguistic comparison is crucial to test what
-mechanism is cognitively universal and is used by all children, and what
-mechanism is specific to some patterns of learning that emerge due to
-the particulars of a given language or culture (Bates \& MacWhinney,
+et al., 2016). Besides, cultures might differ in the way caregivers talk
+to children (Cristia, Dupoux, Gurven, \& Stieglitz, 2017; Kuhl et al.,
+1997), and this difference in the input could influence the children's
+learning strategy. Thus, Cross-linguistic comparison is crucial to test
+what mechanism is cognitively universal and is used by all children, and
+what mechanism is specific to some patterns of learning that emerge due
+to the particulars of a given language or culture (Bates \& MacWhinney,
 1987; Slobin, 2014).
+
+We test the growth scenarios using parent reports of children
+vocabularies and their normative age of acquisition (Fenson et al.,
+1994). Children may vary in their individual learning trajectories, but
+the aggregate data leads to an average learning pattern which is highly
+consistent. It is this normative trajectory that we model in the current
+study, following the steps of previous research using similar datasets
+(Braginsky et al., 2016; J. C. Goodman et al., 2008; Hills et al., 2010,
+2009; Stella et al., 2017; Storkel, 2009)
 
@@
 production are queried, whereas for older children (16 to 36 months)
-only production is queried. We use data from younger children to test
-comprehension and data from older children to test production across 10
-languages. Following previous studies (Hills et al., 2009; Storkel,
-2009), we restrict our analysis to nouns. Table \ref{tab:stats} gives an
-overview of the data.
+only production is queried. Thus, we use data from younger children to
+test comprehension and data from older children to test production
+across 10 languages. Following previous studies (Hills et al., 2009;
+Storkel, 2009), we restrict our analysis to nouns. Table \ref{tab:stats}
+gives an overview of the data.
 
@@
 
-\caption{\label{tab:stats}Statistics for data from Wordbank.}
+\caption{\label{tab:stats}Statistics for dataset we used.}
 \centering
@@
 assumes that the semantic similarity measure is universal----which is a
-reasonable assumption (e.g., Youn et al. 2015), the set of words
+reasonable assumption (e.g., Youn et al., 2016), the set of words
 acquired by children as well as the timeline of this acquisition can
@@
 Hills et al. 2009) and extending these findings to ten different
-languages (with few exceptions) in both production- and
-comprehension-based vocabularies.
+languages, generally, in both production- and comprehension-based
+vocabularies.
 
@@
 \(p(k) \propto \frac{1}{k^{\alpha}}\) (Barabasi \& Albert, 1999). If the
-network displays this property, this fact would suggest an INT-like
-generative process. Conversely, if the degree distribution does not
-follow a power law, this fact would weaken the case for INT. The log-log
-plots are shown in Figure \ref{fig:degreeDist}. We fit a power law to
-each empirical degree distribution following the procedure outlined in
-Clauset, Shalizi, and Newman (2009) and using a related R package
-(poweRlaw, Gillespie, 2015).
+network displays this property, this fact would suggest, but not prove,
+an INT-like generative process. If the degree distribution does not
+follow a power law, this would largely weaken the case for INT. The
+log-log plots are shown in Figure \ref{fig:degreeDist}. We fit a power
+law to each empirical degree distribution following the procedure
+outlined in Clauset, Shalizi, and Newman (2009) and using a related R
+package (poweRlaw, Gillespie, 2015).
 
@@
 suggested by Arbesman et al. (2010), these \enquote{truncated}
-power-laws in phonological networks ----as well as the observed
-cross-linguistic variability in the value of the cut-offs---- may
-reflect the various constraints that exist on word formation such as the
-number of phonemes in the language, the phonotactics (i.e., the way
-sound sequences are arranged in words), and the length of words. Such
+power-laws in phonological networks--as well as the observed
+cross-linguistic variability in the value of the cut-offs--may reflect
+the various constraints that exist on word formation such as the number
+of phonemes in the language, the phonotactics (i.e., the way sound
+sequences are arranged in words), and the length of words. Such
 constraints may limit the number of words that are phonologically
@@
 network grows by EXT, not by INT. Second, our results show that,
-generally speaing, this finding generalizes to comprehension, and holds
+generally speaking, this finding generalizes to comprehension, and holds
 across languages. This generalization was obtained in both the
@@
 correlate with phonological connectivity: Shorter words are more likely
-to have higher connectivity (Pisoni et al., 1985; Vitevitch and
-Rodriguez, 2004).
+to have higher connectivity (Pisoni, Nusbaum, Luce, \& Slowiaczek, 1985;
+Vitevitch \& Rodríguez, 2005).
 
@@
 Braginsky et al. (2016) where unigram counts were derived based on
-CHILDES corpora in each language (MacWhinney, 2000). For each word,
+CHILDES corpora in each language (MacWhinney, 2014). For each word,
 counts included words that shared the same stem (e.g., \enquote{cats}
@@
 on large samples, and this allows us to average out possible differences
-between children and the specificities of their input (see Goodman et
-al. 2008).
+between children and the specificities of their input (see J. C. Goodman
+et al., 2008).
 
@@
 length. This contrasts with the original finding in Hills et al. (2009).
-However, in this previous study, semantic connectivity was not tested in
-a model that included frequency, length and phonological connectivity as
-covariates. Another important difference is the number of words tested:
-Our study uses a larger set of nouns. That said, and despite these
-apparent cross-linguistic differences, both phonological and semantic
-connectivity are significant predictors in the combined model.
+However, this might be due to our using of a slightly different model
+(which included word length as a covariate) and a larger dataset. That
+said, and despite these apparent cross-linguistic differences, both
+phonological and semantic connectivity are significant predictors in the
+combined model.
 
@@
 learners' growth patterns. These two mechanisms represent two
-fundamentally different accounts of lexical growth: one suggests that
+fundamentally different accounts of lexical growth: One suggests that
 future word knowledge is primarily shaped by the children's past
@@
 is shaped, rather, by salient properties in the input regardless of how
-past knowledge is organized.
-
-Previous work (Hills et al., 2010, 2009) has been limited in its scope:
-It focused primarily on semantic networks, production-based
-vocabularies, and developmental data from English-learning children. The
-present study tested the generality of previous findings by 1)
-investigating phonological networks together with semantic networks, 2)
-testing both comprehension- and production-based vocabularies, and 3)
-comparing the results across 10 languages.
+past knowledge is organized. The present study tested the generality of
+previous findings (Hills et al., 2010, 2009) by 1) investigating
+phonological networks together with semantic networks, 2) testing both
+comprehension- and production-based vocabularies, and 3) comparing the
+results across 10 languages.
 
@@
 the learning environment, not in the child's available lexicon. This
-means, strikingly, that children are sensitive to highly connected words
-although they do not initially have access to the full network. This
-finding raises some important questions. What mechanism allows children
-to distinguish highly connected words from other words? Besides, why
-would highly connected words be easier to learn?
-
-One possibility is that children rely on their statistical learning
-abilities. For example, in the semantic domain, children might be using
-a mechanism akin to cross-situational learning to pick up the meanings
-of some words, especially concrete nouns (Smith \& Yu, 2008), and such
-learning would resemble the growth scenario described by EXT. Indeed,
-since free association is related to contextual co-occurrence (Griffiths
-et al., 2007), highly connected words will tend to occur in a variety of
-speech and referential contexts. This fact makes such words easier to
-learnonly because they have more referential disambiguating cues across
-learning contexts, and crucially, even without knowing the entire set of
-words with witch they occurs (hence the similarity with EXT). This
-possibility is supported by the finding that words' diversity of
-occurrence in child directed speech predicts their age of learning
-(Hills et al., 2010).
+hypothesis implies that children are sensitive to highly connected words
+although they do not initially have access to the full network, thus
+raising some important questions: What mechanism allows children to
+distinguish highly connected words from other words? Besides, why would
+highly connected words be easier to learn?
+
+One possibility is that these patterns emerge from children's use of
+statistical learning abilities (Aslin \& Newport, 2012; Saffran, Aslin,
+\& Newport, 1996; Smith \& Yu, 2008). The term \enquote{statistical
+learning} has been used in the developmental literature to describes the
+process by which one acquires information about their environment
+through keeping track of the frequency distribution of some elements
+(e.g., words) in different contexts. An important property of this kind
+of learning is that it occurs without explicit instructions and through
+mere exposure to the input. Previous work in the line of research has
+documented mechanisms which can explain the patterns found in the
+current study.
+
+For example, in the semantic domain, growth according to EXT can be
+explained by a mechanism similar to cross-situational learning (Pinker,
+2013; Smith \& Yu, 2008; Yurovsky \& Frank, 2015). According to this
+mechanism, children track the co-occurrence of concrete nouns with their
+possible semantic referents. The referent of a word heard in only one
+naming situation can be ambiguous (e.g., when the word \enquote{ball} is
+heard for the first time in the presence of both a ball and a chair),
+but hearing the same word in a diversity of semantic contexts allows the
+learner to narrow down the set of possible word-object mappings. In our
+case, free association is related to contextual co-occurrence
+(Griffiths, Steyvers, \& Tenenbaum, 2007), meaning that highly connected
+words will tend to occur in a variety of speech and referential
+contexts. This fact makes such words easier to learn because they have
+more referential disambiguating cues across learning contexts, and
+crucially, even without knowing the entire set of words with witch they
+co-occur (hence the similarity with EXT). This possibility is supported
+by the finding that words' diversity of occurrence in child directed
+speech predicts their age of learning (Hills et al., 2010).
 
@@
 (Jusczyk, Luce, \& Charles-Luce, 1994) and this sensitivity might lead
-them to learn higher-probability words more easily (e.g., Storkel,
-2001). This explanation is supported by computational simulations that
-shows how learning general phonotactics patterns create ``well-worn
-paths'' which allow the models to represent several distinct but
-phonologically neighboring words (Dell et al; 1993; Takac et al. 2017).
+them to learn higher-probability words more easily (Storkel, 2001). This
+explanation is supported by computational simulations that shows how
+learning general phonotactics patterns create ``well-worn paths'' which
+allow the models to represent several distinct but phonologically
+neighboring words (Dell, Juliano, \& Govindjee, 1993; Takac, Knott, \&
+Stokes, 2017).
 
@@
 examining what words are introduced over development and the extent to
-which children's uptake is influenced by this input (Clark 2007; Hoff
-and Naigles, 2002; Hurtado et al., 2008).
+which children's uptake is influenced by this input (Clark, 2007; Hoff
+\& Naigles, 2002).
 
 This work shares a number of limitations with previous studies using
-similar research strategy and datasets (e.g., Hills et al. 2009; 2010).
-Chief among these limitations is the fact that the age of word
-acquisition is computed using different children at different ages (due
-to the fact that available CDI data is mainly cross-sectional). Although
-this measure has proven highly consistent (Fensen et al. 1994), it lead
-us to focus on studying the learning mechanism of the \enquote{average}
-child. Individual trajectories, however, could show different learning
-patterns. For example, using longitudinal data Beckage, Smith, and Hills
-(2011) found differences between typical and late talkers in terms of
-the semantic network structure. Besides, although our study endorses the
+similar research strategy and datasets. Chief among these limitations is
+the fact that the age of word acquisition is computed using different
+children at different ages (due to the fact that available CDI data is
+mainly cross-sectional). Although this measure has proven highly
+consistent (Fenson et al., 1994), it led us to focus on studying the
+learning mechanism of the \enquote{average} child. Individual
+trajectories, however, could show different learning patterns. For
+example, using longitudinal data Beckage, Smith, and Hills (2011) found
+differences between typical and late talkers in terms of the semantic
+network structure. Besides, although our study endorses the
 externally-driven account of network growth, this does not mean
@@
 knowledge enables these children to learn new related words more easily
-(e.g., Chi and Koeske, 1983).
+(e.g., Chi \& Koeske, 1983).
 
@@
 
+\hypertarget{ref-aslin2012}{}
+Aslin, R. N., \& Newport, E. L. (2012). Statistical learning: From
+acquiring specific items to forming general rules. \emph{Current
+Directions in Psychological Science}, \emph{21}(3).
+
 \hypertarget{ref-barabasi99}{}
@@
 
+\hypertarget{ref-chi1983}{}
+Chi, M. T., \& Koeske, R. D. (1983). Network representation of a child's
+dinosaur knowledge. \emph{Developmental Psychology}, \emph{19}(1).
+
+\hypertarget{ref-clark2007}{}
+Clark, E. V. (2007). Young children's uptake of new words in
+conversation. \emph{Language in Society}, \emph{36}(2).
+
 \hypertarget{ref-clauset09}{}
@@
 
+\hypertarget{ref-collins1975}{}
+Collins, A. M., \& Loftus, E. F. (1975). A spreading-activation theory
+of semantic processing. \emph{Psychological Review}, \emph{82}(6).
+
 \hypertarget{ref-cristia2017}{}
@@
 time allocation study. \emph{Child Development}.
+
+\hypertarget{ref-dell1993}{}
+Dell, G. S., Juliano, C., \& Govindjee, A. (1993). Structure and content
+in language production: A theory of frame constraints in phonological
+speech errors. \emph{Cognitive Science}, \emph{17}(2), 149--195.
 
@@
 
+\hypertarget{ref-griffiths07}{}
+Griffiths, T. L., Steyvers, M., \& Tenenbaum, J. B. (2007). Topics in
+semantic representation. \emph{Psychological Review}, \emph{114}(2),
+2007.
+
 \hypertarget{ref-hills2010}{}
@@
 
+\hypertarget{ref-hoff2002}{}
+Hoff, E., \& Naigles, L. (2002). How children use input to acquire a
+lexicon. \emph{Child Development}, \emph{73}(2).
+
 \hypertarget{ref-jusczyk1994}{}
@@
 
+\hypertarget{ref-pinker2013}{}
+Pinker, S. (2013). \emph{Learnability and cognition: The acquisition of
+argument structure}. MIT press.
+
+\hypertarget{ref-pisoni1985}{}
+Pisoni, D. B., Nusbaum, H. C., Luce, P. A., \& Slowiaczek, L. M. (1985).
+Speech perception, word recognition and the structure of the lexicon.
+\emph{Speech Communication}, \emph{4}(1), 75--95.
+
 \hypertarget{ref-roy2015}{}
@@
 
+\hypertarget{ref-saffran1996}{}
+Saffran, J. R., Aslin, R. N., \& Newport, E. L. (1996). Statistical
+learning by 8-month-old infants. \emph{Science}, \emph{274}(5294),
+1926--1928.
+
 \hypertarget{ref-slobin2014}{}
@@
 mappings via cross-situational statistics. \emph{Cognition},
-\emph{106}(3), 1558--1568.
+\emph{106}(3).
 
@@
 infants. \emph{Journal of Child Language}, \emph{36}(2), 29--321.
+
+\hypertarget{ref-takac2017}{}
+Takac, M., Knott, A., \& Stokes, S. (2017). What can neighbourhood
+density effects tell us about word learning? Insights from a
+connectionist model of vocabulary development. \emph{Journal of Child
+Language}, \emph{44}(2).
+
+\hypertarget{ref-vitevitch2005}{}
+Vitevitch, M. S., \& Rodríguez, E. (2005). Neighborhood density effects
+in spoken word recognition in spanish. \emph{Journal of Multilingual
+Communication Disorders}, \emph{3}(1).
 
@@
 
+\hypertarget{ref-yurovsky2015}{}
+Yurovsky, D., \& Frank, M. C. (2015). An integrative account of
+constraints on cross-situational learning. \emph{Cognition}, \emph{145}.
+
 \end{document}

### 2018-11-12 journal/ms.Rmd
final journal draft

@@
 We show that external connectivity in the learning environment drives growth in both production- and comprehension-based vocabularies, even controlling for word frequency and length.
-This pattern of findings suggests a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment.
+This pattern of findings suggests a word learning mechanism where children harness their statistical learning abilities to detect and learn highly connected words in the learning environment.
 
@@
 For example, within a lexical category, words that are more frequent in child-directed speech are acquired earlier [@goodman2008].
-Other factors include word length, the mean length of utterances in which the word occurs, and concreteness [see @braginsky2016].
+Other factors include word length and the mean length of utterances in which the word occurs [e.g., @braginsky2016; @swingley2018].
 
-Besides these word-level properties, the structure of the lexicon (that is, how words relate to each other) also predicts the age of acquisition of words.
+Besides these word-level properties, the structure of the lexicon (that is, how words relate to one another) also predicts the Age of Acquisition (AoA) of words.
 The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words [e.g., @collins1975].
-Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological relatedness.
-These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @stella2017; @carlson2014].
+Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features [@mcrae2005], target-cue relationships in free association norms [@nelson1998], co-occurrence in child directed speech [@macwhinney2014], and phonological relatedness [@vitevitch2008].
+These studies have generally found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @stella2017; @carlson2014].
 
@@
 On the INT proposal, learning is driven by known words with high connectivity to other known words (Figure 1, left).
-Thus, the network structure is a causal factor in early word learning, that is, children might be relying on the organization of their past knowledge to determine future learning.
+Thus, the network structure is a causal factor in early word learning, that is, children rely on the organization of their past knowledge to determine future learning.
 For example, having a rich and organized knowledge about the domain of dinosaurs would facilitate the acquisition of new dinosaur-related words [@chi1983].
 In contrast, on the EXT approach, learning is driven by the connectivity of words that are not known yet (Figure 1, right).
-Thus, the relevant network structure is not internally represented by children, and the related connectivity effect might be an epiphenomenon of some low level properties of the linguistic input.
+Thus, the relevant network structure is not internally represented by children, and the observed connectivity effect might be an epiphenomenon of some properties of the linguistic input.
 For example, highly connected words in the input could be more easily learned because of their contextual diversity [e.g., @smith2008] or because caregivers emphasize such words in child-directed speech [@macwhinney2014].
@@
 However, EXT is the externally-driven scenario that best predicted the data in this previous work.} This is a profound finding because it suggests that learning in the early stages is mostly driven by properties of the external input, regardless of how past knowledge is organized.
-However, this work has been done in the special case of networks that are based on 1) semantic associations, 2) production-based vocabularies, and 2) data from English-learning children, only.
+However, this work has been done in the special case of networks that are based on 1) semantic associations, 2) production-based vocabularies, and 3) data from English-learning children, only.
 The extent to which this result depends on the domain (e.g., semantic vs.
@@
 First, we study the phonological network in addition to the semantic network.
-These two networks represent different ways the mental lexicon is structured.
+These two networks represent different ways the mental lexicon is structured [@beckage2016].
 In particular, words that are neighbors in the semantic network (e.g., "cat", "dog") are not necessarily neighbors in the phonological network, and vice versa.
@@
 Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains [@youn2016; @arbesman2010].
-Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the children's learning strategy.
-Thus, Cross-linguistic comparison is crucial to test what mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014].
+Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the way in which the children's networks grow.
+Thus, Cross-linguistic comparison is crucial to test what growth mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014].
  <!--
@@
 Children may vary in their individual learning trajectories, but the aggregate data leads to an average learning pattern which is highly consistent.
-It is this normative trajectory that we model in the current study, following the steps of previous research using similar datasets [@storkel2009; @stella2017; @hills2009; @hills2010; @goodman2008; @braginsky2016]
+It is this normative trajectory that we model in the current study, following in this regard the steps of previous research using similar datasets [@storkel2009; @stella2017; @hills2009; @hills2010; @goodman2008; @braginsky2016]
 
@@
 First, we describe the datasets we used and explain how we constructed the networks.
-Second, we analyze static properties of words' connectivity in these networks (correlation with AoA and shape of the distribution) and we explain how these properties infom hypotheses about network growth.
+Second, we analyze static properties of words' connectivity in these networks (correlation with age of acquisition and shape of the distribution) and we explain how these properties infom hypotheses about network growth.
 Next, we explicitly fit the two hypothesized growth mechanisms to the data.
@@
 For younger children (e.g., 8 to 18 months in the English data), both comprehension and production are queried, whereas for older children (16 to 36 months) only production is queried.
-Thus, we use data from younger children to test comprehension and data from older children to test production across 10 languages.
+Due to these limitations, we use data from younger children to test comprehension and data from older children to test production.
 Following previous studies [@storkel2009; @hills2009], we restrict our analysis to nouns.
-Table \@ref(tab:stats) gives an overview of the data.
+Table \@ref(tab:stats) gives an overview of the data we used.
 
@@
       linesep = "", format.args = list(big.mark = ","),
-      caption = "Statistics for dataset we used.",
+      caption = "Statistics for the dataset we used.",
       col.names = c("Language",  "Nouns", "Ages", "Nouns", "Ages")) %>%
@@
 
-Since  the free association norms are available only in English, we used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across languages.
-Using the same association data across languages does not necessarily mean that the resulting networks will be the same across languages, or that these networks will grow similarly.
-Indeed, though this approximation assumes that the semantic similarity measure is universal––which is a reasonable assumption [e.g., @youn2016], the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possibility different learning strategies.
+Since  the free association norms are available only in English, we used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across 10 languages.
+Using the same association data across languages does not necessarily lead to similar networks.
+Indeed, though this approximation assumes that the semantic similarity measure is universal–which is a reasonable approximation [e.g., @youn2016], the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possibility different learning strategies.
 
@@
 In previous studies, two nodes were linked if they had an edit distance of 1 [@storkel2009; @carlson2014; @stella2017].
-However, these studies reported a contribution of phonological networks to word learning when these networks were built using a rich adult vocabulary.
-However, since the focus of the current study is on the mechanism of growth, the networks should be based on the children's early vocabulary which, nevertheless, contains very few word pairs with an edit distance of 1.
+However, these studies reported a contribution of phonological connectivity to word learning when networks were built using a rich adult vocabulary.
+Since the focus of the current study is on the mechanism of growth, the networks should be based on the children's early vocabulary.
+The latter, nevertheless, contains very few word pairs with an edit distance of 1.
 Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold.
-In both cases, the results were weaker that those done with a threshold of 2.} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
+In both cases, the results were weaker that those obtained with a threshold of 2.} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
 
@@
 Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment.
-Below we analyze properties of this global networks that are relevant to INT and/or EXT.
+Below we analyze properties of this global networks that may a priori hint at an INT- or EXT-like growth.
 In order to compare various predictors on the same data, we restrict the analysis to the subset of nouns for which we had both semantic and phonological information in each language.
@@
 Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \@ref(fig:growth)).
-Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with INT, although the causality is reversed.
-Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around.
-Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \@ref(fig:corrAll) shows how the age of production and comprehension for each word varies as a function of its degree (or indegree for the semantic networks) as well as the correlation values.
+Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.
+This correlation is also compatible with INT, although the causality is reversed: higher connectivity in the global network is caused by earlier learning, not the other way around.
+Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.
+Thus, the correlates between connectivity in the end-state network and AoA is an important blusprint of both EXT and INT.
+If there is no such correlation, neither growth scenarios can be posited as a learning mechanism.
+
+Figure \@ref(fig:corrAll) shows how the age of production and comprehension for each word varies as a function of its degree (or indegree for the semantic networks) as well as the correlation values.
 For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages.
-
 The plots show, overall, a negative correlation between the month of acquisition and the degree.
@@
 These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English (e.g., Storkel 2004, 2009; Hills et al.
-2009) and extending these findings to ten different languages, generally, in both production- and comprehension-based vocabularies.
+2009) and extending these findings to 10 different languages, generally, in both production- and comprehension-based vocabularies.
 
@@
 The shape of this distribution is particularly relevant to INT as this growth scenario is known to generate networks with a power-law degree distribution, i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$ [@barabasi99].
-If the network displays this property, this fact would suggest, but not prove, an INT-like generative process.
-If the degree distribution does not follow a power law, this  would largely weaken the case for INT.
+If the end-state network displays this property, this fact would suggest, but not prove, an INT-like generative process.
+If, however, the degree distribution is very different from a power law, this would significantly weaken the case for INT.
 The log-log plots are shown in Figure \@ref(fig:degreeDist).
@@
 That said, phonological networks had relatively larger cut-offs than semantic networks.
-As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks–as well as the observed cross-linguistic variability in the value of the cut-offs–may reflect the various constraints that exist on word formation such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words.
+As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks –as well as the cross-linguistic variability in the value of the cut-offs– may reflect the various constraints that exist on word formation such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words.
 Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law.
 
-In sum, the static properties of the global network are *a priori* compatible with both INT and EXT.
+In sum, the static properties of the end-state network are *a priori* compatible with both INT and EXT.
 In order to decide between these two developmental scenarios, we need to fit explicit growth models to the data.
@@
 
-First, the results replicate Hills et al.'s original finding regarding the semantic network in English and production data, which is that this network grows by EXT, not by INT.
-Second, our results show that, generally speaking, this finding generalizes to comprehension, and holds across languages.
+First, the results replicate Hills et al.'s original finding regarding the semantic network in English and the production-based vocabulary, which is that this network grows by EXT, not by INT.
+Second, our results show that, generally speaking, this finding generalizes to comprehension-based vocabulary, and holds across languages.
 This generalization was obtained in both the semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
@@
 This contrasts with the original finding in @hills2009.
-However, this might be due to our using of a slightly different model (which included word length as a covariate) and a larger dataset.
-That said, and despite these apparent cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.
+However, this might be due to our using a slightly different model (which included word length as a covariate) and a larger dataset.
+That said, and despite these apparent cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model (Figure \@ref(fig:staticAll)).
 
@@
 An important property of this kind of learning is that it occurs without explicit instructions and through mere exposure to the input.
-Previous work in the line of research has documented mechanisms which can explain the patterns found in the current study.
+Previous work in the line of research has documented specific mechanisms which can explain the patterns found in the current study.
 
@@
 The referent of a word heard in only one naming situation can be ambiguous (e.g., when the word "ball" is heard for the first time in the presence of both a ball and a chair), but hearing the same word in a diversity of semantic contexts allows the learner to narrow down the set of possible word-object mappings.
-In our case, free association is related to contextual co-occurrence [@griffiths07], meaning that highly connected words will tend to occur in a variety of speech and referential contexts.
-This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts, and crucially, even without knowing the entire set of words with witch they co-occur (hence the similarity with EXT).
+In our case, free association (used to determine semamtnic network connectivity) is related to contextual co-occurrence [@griffiths07; @fourtassi2013], meaning that highly connected words will tend to occur in a variety of speech and referential contexts.
+This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts.
+Crucially, children can learn these words without knowing the other words with witch they co-occur (hence the similarity with EXT).
 This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@hills2010].
@@
 Children are sensitive to local phonotactic regularities [@jusczyk1994] and this sensitivity might lead them to learn higher-probability words more easily [@storkel2001].
-This explanation is supported by computational simulations that shows how learning general phonotactics patterns create ``well-worn paths'' which allow the models to represent several distinct but phonologically neighboring words [@dell1993; @takac2017].
+This explanation is supported by computational simulations that show how learning general phonotactics patterns create ``well-worn paths'' which allow the models to represent several distinct but phonologically neighboring words [@dell1993; @takac2017].
 
@@
 Although this measure has proven highly consistent [@fenson94], it led us to focus on studying the learning mechanism of the "average" child.
-Individual trajectories, however, could show different learning patterns.
+Individual trajectories, however, could lead to different netwtok strcutures and show different learning patterns.
 For example, using longitudinal data @beckage2011 found differences between typical and late talkers in terms of the semantic network structure.

### 2018-11-12 journal/ms.tex
final journal draft

@@
 learning mechanism where children harness their statistical learning
-abilities to (indirectly) detect and learn highly connected words in the
-learning environment.}
+abilities to detect and learn highly connected words in the learning
+environment.}
   \keywords{Language understanding; audio-visual processing; word learning; speech
@@
 frequent in child-directed speech are acquired earlier (J. C. Goodman,
-Dale, \& Li, 2008). Other factors include word length, the mean length
-of utterances in which the word occurs, and concreteness (see Braginsky,
-Yurovsky, Marchman, \& Frank, 2016).
+Dale, \& Li, 2008). Other factors include word length and the mean
+length of utterances in which the word occurs (e.g., Braginsky,
+Yurovsky, Marchman, \& Frank, 2016; Swingley \& Humphrey, 2018).
 
 Besides these word-level properties, the structure of the lexicon (that
-is, how words relate to each other) also predicts the age of acquisition
-of words. The lexical structure can be characterized in terms of a
-network where each node represents a word in the vocabulary, and each
-link between two nodes represents a relationship between the
-corresponding pair of words (e.g., Collins \& Loftus, 1975). Previous
-studies have investigated early vocabulary structure by constructing
-networks using a variety of word-word relations including shared
-semantic features, target-cue relationships in free association norms,
-co-occurrence in child directed speech, and phonological relatedness.
-These studies have found that children tend to produce words that have
+is, how words relate to one another) also predicts the Age of
+Acquisition (AoA) of words. The lexical structure can be characterized
+in terms of a network where each node represents a word in the
+vocabulary, and each link between two nodes represents a relationship
+between the corresponding pair of words (e.g., Collins \& Loftus, 1975).
+Previous studies have investigated early vocabulary structure by
+constructing networks using a variety of word-word relations including
+shared semantic features (McRae, Cree, Seidenberg, \& McNorgan, 2005),
+target-cue relationships in free association norms (Nelson, McEvoy, \&
+Schreiber, 1998), co-occurrence in child directed speech (MacWhinney,
+2014), and phonological relatedness (Vitevitch, 2008). These studies
+have generally found that children tend to produce words that have
 higher neighborhood density (i.e., high connectivity in the network)
@@
 left). Thus, the network structure is a causal factor in early word
-learning, that is, children might be relying on the organization of
-their past knowledge to determine future learning. For example, having a
-rich and organized knowledge about the domain of dinosaurs would
-facilitate the acquisition of new dinosaur-related words (Chi \& Koeske,
-1983). In contrast, on the EXT approach, learning is driven by the
-connectivity of words that are not known yet (Figure 1, right). Thus,
-the relevant network structure is not internally represented by
-children, and the related connectivity effect might be an epiphenomenon
-of some low level properties of the linguistic input. For example,
-highly connected words in the input could be more easily learned because
-of their contextual diversity (e.g., Smith \& Yu, 2008) or because
-caregivers emphasize such words in child-directed speech (MacWhinney,
-2014).
+learning, that is, children rely on the organization of their past
+knowledge to determine future learning. For example, having a rich and
+organized knowledge about the domain of dinosaurs would facilitate the
+acquisition of new dinosaur-related words (Chi \& Koeske, 1983). In
+contrast, on the EXT approach, learning is driven by the connectivity of
+words that are not known yet (Figure 1, right). Thus, the relevant
+network structure is not internally represented by children, and the
+observed connectivity effect might be an epiphenomenon of some
+properties of the linguistic input. For example, highly connected words
+in the input could be more easily learned because of their contextual
+diversity (e.g., Smith \& Yu, 2008) or because caregivers emphasize such
+words in child-directed speech (MacWhinney, 2014).
 
@@
 been done in the special case of networks that are based on 1) semantic
-associations, 2) production-based vocabularies, and 2) data from
+associations, 2) production-based vocabularies, and 3) data from
 English-learning children, only. The extent to which this result depends
@@
 network. These two networks represent different ways the mental lexicon
-is structured. In particular, words that are neighbors in the semantic
-network (e.g., \enquote{cat}, \enquote{dog}) are not necessarily
-neighbors in the phonological network, and vice versa. Does the
-phonological network also predict word learning? Previous work did find
-an effect of words' connectivity in the phonological network on their
-age of learning (Carlson et al., 2014; Stella et al., 2017; Storkel,
-2009). In other words, words learned earlier in life tend to sound
-similar to many other words than a word learned later in life. However,
-this finding is \emph{a priori} compatible with both INT and EXT, and
-previous studies did not explicitly compare these two mechanisms. Here,
-we investigate whether phonological networks, like semantic networks,
-grow through EXT, or if they rather grow via INT
-(Figure~\ref{fig:growth}).
+is structured (Beckage \& Colunga, 2016). In particular, words that are
+neighbors in the semantic network (e.g., \enquote{cat}, \enquote{dog})
+are not necessarily neighbors in the phonological network, and vice
+versa. Does the phonological network also predict word learning?
+Previous work did find an effect of words' connectivity in the
+phonological network on their age of learning (Carlson et al., 2014;
+Stella et al., 2017; Storkel, 2009). In other words, words learned
+earlier in life tend to sound similar to many other words than a word
+learned later in life. However, this finding is \emph{a priori}
+compatible with both INT and EXT, and previous studies did not
+explicitly compare these two mechanisms. Here, we investigate whether
+phonological networks, like semantic networks, grow through EXT, or if
+they rather grow via INT (Figure~\ref{fig:growth}).
 
@@
 to children (Cristia, Dupoux, Gurven, \& Stieglitz, 2017; Kuhl et al.,
-1997), and this difference in the input could influence the children's
-learning strategy. Thus, Cross-linguistic comparison is crucial to test
-what mechanism is cognitively universal and is used by all children, and
-what mechanism is specific to some patterns of learning that emerge due
-to the particulars of a given language or culture (Bates \& MacWhinney,
-1987; Slobin, 2014).
+1997), and this difference in the input could influence the way in which
+the children's networks grow. Thus, Cross-linguistic comparison is
+crucial to test what growth mechanism is cognitively universal and is
+used by all children, and what mechanism is specific to some patterns of
+learning that emerge due to the particulars of a given language or
+culture (Bates \& MacWhinney, 1987; Slobin, 2014).
 
@@
 consistent. It is this normative trajectory that we model in the current
-study, following the steps of previous research using similar datasets
-(Braginsky et al., 2016; J. C. Goodman et al., 2008; Hills et al., 2010,
-2009; Stella et al., 2017; Storkel, 2009)
+study, following in this regard the steps of previous research using
+similar datasets (Braginsky et al., 2016; J. C. Goodman et al., 2008;
+Hills et al., 2010, 2009; Stella et al., 2017; Storkel, 2009)
 
@@
 static properties of words' connectivity in these networks (correlation
-with AoA and shape of the distribution) and we explain how these
-properties infom hypotheses about network growth. Next, we explicitly
-fit the two hypothesized growth mechanisms to the data. We investigate
-the extent to which the results obtained in Hills et al. (2009)
-generalize to phonological networks and comprehension-based
+with age of acquisition and shape of the distribution) and we explain
+how these properties infom hypotheses about network growth. Next, we
+explicitly fit the two hypothesized growth mechanisms to the data. We
+investigate the extent to which the results obtained in Hills et al.
+(2009) generalize to phonological networks and comprehension-based
 vocabularies, and whether this generalization holds
@@
 production are queried, whereas for older children (16 to 36 months)
-only production is queried. Thus, we use data from younger children to
-test comprehension and data from older children to test production
-across 10 languages. Following previous studies (Hills et al., 2009;
+only production is queried. Due to these limitations, we use data from
+younger children to test comprehension and data from older children to
+test production. Following previous studies (Hills et al., 2009;
 Storkel, 2009), we restrict our analysis to nouns. Table \ref{tab:stats}
-gives an overview of the data.
+gives an overview of the data we used.
 
@@
 
-\caption{\label{tab:stats}Statistics for dataset we used.}
+\caption{\label{tab:stats}Statistics for the dataset we used.}
 \centering
@@
 procedure outlined in Hills et al. (2009), as follows. We used as an
-index of semantic relatedness the Florida Free Association Norms
-(Nelson, McEvoy, \& Schreiber, 1998). This dataset was collected by
-giving adult participants a word (the cue), and asking them to write the
-first word that comes to mind (the target). For example, when given the
-word \enquote{ball}, they might answer with the word \enquote{game}. A
-pair of nodes were connected by a directed link from the cue to the
-target if there was a cue-target relationship between these nodes in the
-association norms. The connectivity of a given node was characterized by
-its \emph{indegree}: the number of links for which the word was the
-target. To model growth from month to month, we constructed a different
-network at each month, based on the words that have been acquired by
-that month.
+index of semantic relatedness the Florida Free Association Norms (Nelson
+et al., 1998). This dataset was collected by giving adult participants a
+word (the cue), and asking them to write the first word that comes to
+mind (the target). For example, when given the word \enquote{ball}, they
+might answer with the word \enquote{game}. A pair of nodes were
+connected by a directed link from the cue to the target if there was a
+cue-target relationship between these nodes in the association norms.
+The connectivity of a given node was characterized by its
+\emph{indegree}: the number of links for which the word was the target.
+To model growth from month to month, we constructed a different network
+at each month, based on the words that have been acquired by that month.
 
@@
 the hand-checked translation equivalents available in Wordbank, which
-allowed us to use the English association norms across languages. Using
-the same association data across languages does not necessarily mean
-that the resulting networks will be the same across languages, or that
-these networks will grow similarly. Indeed, though this approximation
-assumes that the semantic similarity measure is universal----which is a
-reasonable assumption (e.g., Youn et al., 2016), the set of words
-acquired by children as well as the timeline of this acquisition can
-still vary from language to language leading to possibility different
-learning strategies.
+allowed us to use the English association norms across 10 languages.
+Using the same association data across languages does not necessarily
+lead to similar networks. Indeed, though this approximation assumes that
+the semantic similarity measure is universal--which is a reasonable
+approximation (e.g., Youn et al., 2016), the set of words acquired by
+children as well as the timeline of this acquisition can still vary from
+language to language leading to possibility different learning
+strategies.
 
@@
 of 1 (Carlson et al., 2014; Stella et al., 2017; Storkel, 2009).
-However, these studies reported a contribution of phonological networks
-to word learning when these networks were built using a rich adult
-vocabulary. However, since the focus of the current study is on the
+However, these studies reported a contribution of phonological
+connectivity to word learning when networks were built using a rich
+adult vocabulary. Since the focus of the current study is on the
 mechanism of growth, the networks should be based on the children's
-early vocabulary which, nevertheless, contains very few word pairs with
-an edit distance of 1. Thus, we increased the threshold from 1 to 2,
-that is, two nodes were related if their edit distance was equal to 1 or
+early vocabulary. The latter, nevertheless, contains very few word pairs
+with an edit distance of 1. Thus, we increased the threshold from 1 to
+2, that is, two nodes were related if their edit distance was equal to 1
+or
 2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold.
-In both cases, the results were weaker that those done with a threshold of 2.}
+In both cases, the results were weaker that those obtained with a threshold of 2.}
 The connectivity of a given node was characterized with its
@@
 for the external connectivity in the learning environment. Below we
-analyze properties of this global networks that are relevant to INT
-and/or EXT. In order to compare various predictors on the same data, we
-restrict the analysis to the subset of nouns for which we had both
-semantic and phonological information in each language.
+analyze properties of this global networks that may a priori hint at an
+INT- or EXT-like growth. In order to compare various predictors on the
+same data, we restrict the analysis to the subset of nouns for which we
+had both semantic and phonological information in each language.
 
@@
 a direct consequence of an EXT-like growth scenario is a correlation
-between connectivity in the global network and the age of
-acquisition.\footnote{This correlation is also compatible with INT, although the causality is reversed.
-Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around.
-Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.}
+between connectivity in the global network and the age of acquisition.
+This correlation is also compatible with INT, although the causality is
+reversed: higher connectivity in the global network is caused by earlier
+learning, not the other way around. Some words end up being highly
+connected in the global network precisely because they happen to be
+acquired earlier and, therefore, have a higher chance of accumulating
+more links over time. Thus, the correlates between connectivity in the
+end-state network and AoA is an important blusprint of both EXT and INT.
+If there is no such correlation, neither growth scenarios can be posited
+as a learning mechanism.
+
 Figure \ref{fig:corrAll} shows how the age of production and
@@
 For ease of visual comparison, the predictor (i.e., the degree) was
-centered and scaled across languages.
-
-The plots show, overall, a negative correlation between the month of
-acquisition and the degree. In production data, the average correlation
-across languages was -0.24 (SD=0.10) for the semantic networks and -0.30
-(SD=0.05) for the phonological networks. In comprehension data, the
-average correlation was -0.21 (SD=0.08) for the semantic networks and
--0.21 (SD=0.07) for the phonological networks. These results indicate
-that nouns with higher degrees are generally learned earlier, thus
-replicating previous findings in English (e.g., Storkel 2004, 2009;
-Hills et al. 2009) and extending these findings to ten different
-languages, generally, in both production- and comprehension-based
-vocabularies.
+centered and scaled across languages. The plots show, overall, a
+negative correlation between the month of acquisition and the degree. In
+production data, the average correlation across languages was -0.24
+(SD=0.10) for the semantic networks and -0.30 (SD=0.05) for the
+phonological networks. In comprehension data, the average correlation
+was -0.21 (SD=0.08) for the semantic networks and -0.21 (SD=0.07) for
+the phonological networks. These results indicate that nouns with higher
+degrees are generally learned earlier, thus replicating previous
+findings in English (e.g., Storkel 2004, 2009; Hills et al. 2009) and
+extending these findings to 10 different languages, generally, in both
+production- and comprehension-based vocabularies.
 
@@
 \(p(k) \propto \frac{1}{k^{\alpha}}\) (Barabasi \& Albert, 1999). If the
-network displays this property, this fact would suggest, but not prove,
-an INT-like generative process. If the degree distribution does not
-follow a power law, this would largely weaken the case for INT. The
-log-log plots are shown in Figure \ref{fig:degreeDist}. We fit a power
-law to each empirical degree distribution following the procedure
-outlined in Clauset, Shalizi, and Newman (2009) and using a related R
-package (poweRlaw, Gillespie, 2015).
+end-state network displays this property, this fact would suggest, but
+not prove, an INT-like generative process. If, however, the degree
+distribution is very different from a power law, this would
+significantly weaken the case for INT. The log-log plots are shown in
+Figure \ref{fig:degreeDist}. We fit a power law to each empirical degree
+distribution following the procedure outlined in Clauset, Shalizi, and
+Newman (2009) and using a related R package (poweRlaw, Gillespie, 2015).
 
@@
 suggested by Arbesman et al. (2010), these \enquote{truncated}
-power-laws in phonological networks--as well as the observed
-cross-linguistic variability in the value of the cut-offs--may reflect
-the various constraints that exist on word formation such as the number
-of phonemes in the language, the phonotactics (i.e., the way sound
-sequences are arranged in words), and the length of words. Such
-constraints may limit the number of words that are phonologically
-similar, thus leading to distributions which decay faster than a
-non-truncated power law.
-
-In sum, the static properties of the global network are \emph{a priori}
-compatible with both INT and EXT. In order to decide between these two
-developmental scenarios, we need to fit explicit growth models to the
-data.
+power-laws in phonological networks --as well as the cross-linguistic
+variability in the value of the cut-offs-- may reflect the various
+constraints that exist on word formation such as the number of phonemes
+in the language, the phonotactics (i.e., the way sound sequences are
+arranged in words), and the length of words. Such constraints may limit
+the number of words that are phonologically similar, thus leading to
+distributions which decay faster than a non-truncated power law.
+
+In sum, the static properties of the end-state network are \emph{a
+priori} compatible with both INT and EXT. In order to decide between
+these two developmental scenarios, we need to fit explicit growth models
+to the data.
 
@@
 First, the results replicate Hills et al.'s original finding regarding
-the semantic network in English and production data, which is that this
-network grows by EXT, not by INT. Second, our results show that,
-generally speaking, this finding generalizes to comprehension, and holds
-across languages. This generalization was obtained in both the
+the semantic network in English and the production-based vocabulary,
+which is that this network grows by EXT, not by INT. Second, our results
+show that, generally speaking, this finding generalizes to
+comprehension-based vocabulary, and holds across languages. This
+generalization was obtained in both the
 semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
@@
 length. This contrasts with the original finding in Hills et al. (2009).
-However, this might be due to our using of a slightly different model
+However, this might be due to our using a slightly different model
 (which included word length as a covariate) and a larger dataset. That
@@
 phonological and semantic connectivity are significant predictors in the
-combined model.
+combined model (Figure \ref{fig:staticAll}).
 
@@
 process by which one acquires information about their environment
-through keeping track of the frequency distribution of some elements
-(e.g., words) in different contexts. An important property of this kind
-of learning is that it occurs without explicit instructions and through
+through tracking the frequency distribution of some elements (e.g.,
+words) in different contexts. An important property of this kind of
+learning is that it occurs without explicit instructions and through
 mere exposure to the input. Previous work in the line of research has
-documented mechanisms which can explain the patterns found in the
-current study.
+documented specific mechanisms which can explain the patterns found in
+the current study.
 
@@
 learner to narrow down the set of possible word-object mappings. In our
-case, free association is related to contextual co-occurrence
-(Griffiths, Steyvers, \& Tenenbaum, 2007), meaning that highly connected
-words will tend to occur in a variety of speech and referential
-contexts. This fact makes such words easier to learn because they have
-more referential disambiguating cues across learning contexts, and
-crucially, even without knowing the entire set of words with witch they
-co-occur (hence the similarity with EXT). This possibility is supported
-by the finding that words' diversity of occurrence in child directed
-speech predicts their age of learning (Hills et al., 2010).
+case, free association (used to determine semamtnic network
+connectivity) is related to contextual co-occurrence (Fourtassi \&
+Dupoux, 2013; Griffiths, Steyvers, \& Tenenbaum, 2007), meaning that
+highly connected words will tend to occur in a variety of speech and
+referential contexts. This fact makes such words easier to learn because
+they have more referential disambiguating cues across learning contexts.
+Crucially, children can learn these words without knowing the other
+words with witch they co-occur (hence the similarity with EXT). This
+possibility is supported by the finding that words' diversity of
+occurrence in child directed speech predicts their age of learning
+(Hills et al., 2010).
 
@@
 connectivity in the phonological network is inherently correlated with
-phonotactic probability (M. S. Vitevitch, Luce, Pisoni, \& Auer, 1999).
-That is, highly connected words tend to be made of frequent sound
-sequences. Children are sensitive to local phonotactic regularities
-(Jusczyk, Luce, \& Charles-Luce, 1994) and this sensitivity might lead
-them to learn higher-probability words more easily (Storkel, 2001). This
-explanation is supported by computational simulations that shows how
-learning general phonotactics patterns create ``well-worn paths'' which
-allow the models to represent several distinct but phonologically
-neighboring words (Dell, Juliano, \& Govindjee, 1993; Takac, Knott, \&
-Stokes, 2017).
+phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
+is, highly connected words tend to be made of frequent sound sequences.
+Children are sensitive to local phonotactic regularities (Jusczyk, Luce,
+\& Charles-Luce, 1994) and this sensitivity might lead them to learn
+higher-probability words more easily (Storkel, 2001). This explanation
+is supported by computational simulations that show how learning general
+phonotactics patterns create ``well-worn paths'' which allow the models
+to represent several distinct but phonologically neighboring words
+(Dell, Juliano, \& Govindjee, 1993; Takac, Knott, \& Stokes, 2017).
 
@@
 learning mechanism of the \enquote{average} child. Individual
-trajectories, however, could show different learning patterns. For
-example, using longitudinal data Beckage, Smith, and Hills (2011) found
-differences between typical and late talkers in terms of the semantic
-network structure. Besides, although our study endorses the
-externally-driven account of network growth, this does not mean
-individual children never use some variant of INT or some combination of
-both INT and EXT (Beckage and Colunga, under review). For example, some
-children develop \enquote{islands of expertise}, that is, well organized
-knowledge about a certain topic (e.g., birds or dinosaurs). This prior
-knowledge enables these children to learn new related words more easily
-(e.g., Chi \& Koeske, 1983).
+trajectories, however, could lead to different netwtok strcutures and
+show different learning patterns. For example, using longitudinal data
+Beckage, Smith, and Hills (2011) found differences between typical and
+late talkers in terms of the semantic network structure. Besides,
+although our study endorses the externally-driven account of network
+growth, this does not mean individual children never use some variant of
+INT or some combination of both INT and EXT (Beckage and Colunga, under
+review). For example, some children develop \enquote{islands of
+expertise}, that is, well organized knowledge about a certain topic
+(e.g., birds or dinosaurs). This prior knowledge enables these children
+to learn new related words more easily (e.g., Chi \& Koeske, 1983).
 
@@
 
+\hypertarget{ref-beckage2016}{}
+Beckage, N. M., \& Colunga, E. (2016). Language networks as models of
+cognition: Understanding cognition through language. In \emph{Towards a
+theoretical framework for analyzing complex linguistic networks} (pp.
+3--28). Springer.
+
 \hypertarget{ref-beckage2011}{}
@@
 
+\hypertarget{ref-fourtassi2013}{}
+Fourtassi, A., \& Dupoux, E. (2013). A corpus-based evaluation method
+for distributional semantic models. In \emph{51st annual meeting of the
+association for computational linguistics proceedings of the student
+research workshop} (pp. 165--171).
+
 \hypertarget{ref-frank2017}{}
@@
 
+\hypertarget{ref-mcrae2005}{}
+McRae, K., Cree, G. S., Seidenberg, M. S., \& McNorgan, C. (2005).
+Semantic feature production norms for a large set of living and
+nonliving things. \emph{Behavior Research Methods}, \emph{37}(4),
+547--559.
+
 \hypertarget{ref-nelson1998}{}
@@
 infants. \emph{Journal of Child Language}, \emph{36}(2), 29--321.
+
+\hypertarget{ref-swingley2018}{}
+Swingley, D., \& Humphrey, C. (2018). Quantitative linguistic predictors
+of infants? Learning of specific english words. \emph{Child
+Development}, \emph{89}(4), 1247--1267.
 
@@
 
+\hypertarget{ref-vitevitch2008}{}
+Vitevitch, M. S. (2008). What can graph theory tell us about word
+learning and lexical retrieval? \emph{Journal of Speech, Language, and
+Hearing Research}, \emph{51}(2), 408--422.
+
 \hypertarget{ref-vitevitch2005}{}

### 2018-11-13 journal/ms.Rmd
minor corrections

@@
 Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.
-Thus, the correlates between connectivity in the end-state network and AoA is an important blusprint of both EXT and INT.
-If there is no such correlation, neither growth scenarios can be posited as a learning mechanism.
+Thus, the correlation between connectivity in the end-state network and AoA is an important blueprint of both EXT and INT.
+If there is no such correlation, neither growth scenarios can be posited as a possible learning mechanism.
 

### 2018-11-13 journal/ms.tex
minor corrections

@@
 acquired earlier and, therefore, have a higher chance of accumulating
-more links over time. Thus, the correlates between connectivity in the
-end-state network and AoA is an important blusprint of both EXT and INT.
+more links over time. Thus, the correlation between connectivity in the
+end-state network and AoA is an important blueprint of both EXT and INT.
 If there is no such correlation, neither growth scenarios can be posited
-as a learning mechanism.
+as a possible learning mechanism.
 

### 2018-11-13 journal/ms.Rmd
minor corrections

@@
 Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.
-Thus, the correlation between connectivity in the end-state network and AoA is an important blueprint of both EXT and INT.
+Thus, the correlation between connectivity in the end-state network and AoA can result from both EXT and INT.
 If there is no such correlation, neither growth scenarios can be posited as a possible learning mechanism.
@@
 An important property of this kind of learning is that it occurs without explicit instructions and through mere exposure to the input.
-Previous work in the line of research has documented specific mechanisms which can explain the patterns found in the current study.
+Previous work in this line of research has documented specific mechanisms which can explain the patterns found in the current study.
 
@@
 The referent of a word heard in only one naming situation can be ambiguous (e.g., when the word "ball" is heard for the first time in the presence of both a ball and a chair), but hearing the same word in a diversity of semantic contexts allows the learner to narrow down the set of possible word-object mappings.
-In our case, free association (used to determine semamtnic network connectivity) is related to contextual co-occurrence [@griffiths07; @fourtassi2013], meaning that highly connected words will tend to occur in a variety of speech and referential contexts.
+In our case, free association (used to determine semantic network connectivity) is related to contextual co-occurrence [@griffiths07; @fourtassi2013], meaning that highly connected words will tend to occur in a variety of speech and referential contexts.
 This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts.
-Crucially, children can learn these words without knowing the other words with witch they co-occur (hence the similarity with EXT).
+Crucially, children can learn these words without necessarily knowing the meaning of all other words with witch they co-occur (hence the similarity with EXT).
 This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@hills2010].

### 2018-11-13 journal/ms.tex
minor corrections

@@
 more links over time. Thus, the correlation between connectivity in the
-end-state network and AoA is an important blueprint of both EXT and INT.
-If there is no such correlation, neither growth scenarios can be posited
-as a possible learning mechanism.
+end-state network and AoA can result from both EXT and INT. If there is
+no such correlation, neither growth scenarios can be posited as a
+possible learning mechanism.
 
@@
 learning is that it occurs without explicit instructions and through
-mere exposure to the input. Previous work in the line of research has
+mere exposure to the input. Previous work in this line of research has
 documented specific mechanisms which can explain the patterns found in
@@
 learner to narrow down the set of possible word-object mappings. In our
-case, free association (used to determine semamtnic network
-connectivity) is related to contextual co-occurrence (Fourtassi \&
-Dupoux, 2013; Griffiths, Steyvers, \& Tenenbaum, 2007), meaning that
-highly connected words will tend to occur in a variety of speech and
-referential contexts. This fact makes such words easier to learn because
-they have more referential disambiguating cues across learning contexts.
-Crucially, children can learn these words without knowing the other
-words with witch they co-occur (hence the similarity with EXT). This
-possibility is supported by the finding that words' diversity of
-occurrence in child directed speech predicts their age of learning
-(Hills et al., 2010).
+case, free association (used to determine semantic network connectivity)
+is related to contextual co-occurrence (Fourtassi \& Dupoux, 2013;
+Griffiths, Steyvers, \& Tenenbaum, 2007), meaning that highly connected
+words will tend to occur in a variety of speech and referential
+contexts. This fact makes such words easier to learn because they have
+more referential disambiguating cues across learning contexts.
+Crucially, children can learn these words without necessarily knowing
+the meaning of all other words with witch they co-occur (hence the
+similarity with EXT). This possibility is supported by the finding that
+words' diversity of occurrence in child directed speech predicts their
+age of learning (Hills et al., 2010).
 

### 2018-12-02 journal/ms.Rmd
remarks by george

@@
 
- Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions.
+ Children tend to produce words earlier when they are connected to a variety of other words along the phonological and semantic dimensions.
 Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.
-One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words.
+One view suggests that learning is primarily predicted by a network growth model where highly connected words in the child's early lexicon enable learning of similar words.
 Another view suggests that learning is driven  by highly connected words in the external learning environment, instead of highly connected words in the early internal lexicon.
@@
 For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
-Thus, according to INT, the node 1 is more likely to enter the lexicon.
+Thus, according to INT, node 1 is more likely to enter the lexicon.
 For EXT, the utility of a candidate node is its degree in the entire network.
-According to EXT, the node 2 is more likely to enter the lexicon next.", fig.align = "center", out.width = "300px"}
+According to EXT, node 2 is more likely to enter the lexicon next.", fig.align = "center", out.width = "300px"}
 knitr::include_graphics("figs/growth3.png")
@@
 Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the way in which the children's networks grow.
-Thus, Cross-linguistic comparison is crucial to test what growth mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014].
+Thus, cross-linguistic comparison is crucial to test what growth mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014].
  <!--
@@
 Due to these limitations, we use data from younger children to test comprehension and data from older children to test production.
-Following previous studies [@storkel2009; @hills2009], we restrict our analysis to nouns.
+Following previous studies [@storkel2009; @hills2009], we restrict our analysis to the category of nouns.\footnote{This choice was also forced by the fact that the great majority of association data produced by adults–and which we used to build semantic networks–were nouns.}.
 Table \@ref(tab:stats) gives an overview of the data we used.
@@
 A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms.
-The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target.
-To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.
+The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target.\footnote{This choice was based the prior work by @hills2009 stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated for indegree.} To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.
 
@@
 However, these studies reported a contribution of phonological connectivity to word learning when networks were built using a rich adult vocabulary.
-Since the focus of the current study is on the mechanism of growth, the networks should be based on the children's early vocabulary.
-The latter, nevertheless, contains very few word pairs with an edit distance of 1.
+Since the focus of the current study is on the mechanism of growth, the networks should be based on children's early vocabulary.
+The latter, however, contains very few word pairs with an edit distance of 1.
 Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold.
-In both cases, the results were weaker that those obtained with a threshold of 2.} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
+In both cases, the results were weaker than those obtained with a threshold of 2.
+We did not consider the case of a threshold larger than 2 since the pairs will become less and less phonologically related.} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
 
@@
 Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.
-This correlation is also compatible with INT, although the causality is reversed: higher connectivity in the global network is caused by earlier learning, not the other way around.
+This correlation is also necessary to INT, although the causality is reversed: higher connectivity in the global network is caused by earlier learning, not the other way around.
 Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.
 Thus, the correlation between connectivity in the end-state network and AoA can result from both EXT and INT.
-If there is no such correlation, neither growth scenarios can be posited as a possible learning mechanism.
+If there is no such correlation, neither growth scenario can be posited as a possible learning mechanism.
 
@@
 That said, phonological networks had relatively larger cut-offs than semantic networks.
-As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks –as well as the cross-linguistic variability in the value of the cut-offs– may reflect the various constraints that exist on word formation such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words.
+As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks may reflect the various constraints that exist on word formation in the phonological domain such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words.
 Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law.
@@
 Second, our results show that, generally speaking, this finding generalizes to comprehension-based vocabulary, and holds across languages.
-This generalization was obtained in both the semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
-However, our findings do not support this assumption, rather it supports our initial approximation about the universality of the semantic similarity measure.} and phonological domains.
+This generalization was obtained in both the semantic^[One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
+However, our findings do not support this assumption, rather it supports our initial approximation about the universality of the semantic similarity measure.
+That said, this apprimation is not perfect; for example there is evidence that a small part of the variance in free assication data can be explained by phonological similarity [@kachergis2011; @matusevych2018], thus leading to possibly minor cross-linguistic differences.] and phonological domains.
 

### 2018-12-02 journal/ms.tex
remarks by george

@@
   \abstract{Children tend to produce words earlier when they are connected to a
-variety of other words along both the phonological and semantic
-dimensions. Though this connectivity effect has been extensively
-documented, little is known about the underlying developmental
-mechanism. One view suggests that learning is primarily driven by a
-network growth model where highly connected words in the child's early
-lexicon attract similar words. Another view suggests that learning is
-driven by highly connected words in the external learning environment,
-instead of highly connected words in the early internal lexicon. The
-present study tests both scenarios systematically in both the
-phonological and semantic domains across 10 languages. We show that
-external connectivity in the learning environment drives growth in both
-production- and comprehension-based vocabularies, even controlling for
-word frequency and length. This pattern of findings suggests a word
-learning mechanism where children harness their statistical learning
-abilities to detect and learn highly connected words in the learning
-environment.}
+variety of other words along the phonological and semantic dimensions.
+Though this connectivity effect has been extensively documented, little
+is known about the underlying developmental mechanism. One view suggests
+that learning is primarily predicted by a network growth model where
+highly connected words in the child's early lexicon enable learning of
+similar words. Another view suggests that learning is driven by highly
+connected words in the external learning environment, instead of highly
+connected words in the early internal lexicon. The present study tests
+both scenarios systematically in both the phonological and semantic
+domains across 10 languages. We show that external connectivity in the
+learning environment drives growth in both production- and
+comprehension-based vocabularies, even controlling for word frequency
+and length. This pattern of findings suggests a word learning mechanism
+where children harness their statistical learning abilities to detect
+and learn highly connected words in the learning environment.}
   \keywords{Language understanding; audio-visual processing; word learning; speech
@@
 For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
-Thus, according to INT, the node 1 is more likely to enter the lexicon.
+Thus, according to INT, node 1 is more likely to enter the lexicon.
 For EXT, the utility of a candidate node is its degree in the entire network.
-According to EXT, the node 2 is more likely to enter the lexicon next.}\label{fig:growth}
+According to EXT, node 2 is more likely to enter the lexicon next.}\label{fig:growth}
 \end{figure}
@@
 1997), and this difference in the input could influence the way in which
-the children's networks grow. Thus, Cross-linguistic comparison is
+the children's networks grow. Thus, cross-linguistic comparison is
 crucial to test what growth mechanism is cognitively universal and is
@@
 test production. Following previous studies (Hills et al., 2009;
-Storkel, 2009), we restrict our analysis to nouns. Table \ref{tab:stats}
-gives an overview of the data we used.
+Storkel, 2009), we restrict our analysis to the category of
+nouns.\footnote{This choice was also forced by the fact that the great majority of association data produced by adults–and which we used to build semantic networks–were nouns.}.
+Table \ref{tab:stats} gives an overview of the data we used.
 
@@
 The connectivity of a given node was characterized by its
-\emph{indegree}: the number of links for which the word was the target.
+\emph{indegree}: the number of links for which the word was the
+target.\footnote{This choice was based the prior work by @hills2009 stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated for indegree.}
 To model growth from month to month, we constructed a different network
@@
 adult vocabulary. Since the focus of the current study is on the
-mechanism of growth, the networks should be based on the children's
-early vocabulary. The latter, nevertheless, contains very few word pairs
-with an edit distance of 1. Thus, we increased the threshold from 1 to
-2, that is, two nodes were related if their edit distance was equal to 1
-or
+mechanism of growth, the networks should be based on children's early
+vocabulary. The latter, however, contains very few word pairs with an
+edit distance of 1. Thus, we increased the threshold from 1 to 2, that
+is, two nodes were related if their edit distance was equal to 1 or
 2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold.
-In both cases, the results were weaker that those obtained with a threshold of 2.}
+In both cases, the results were weaker than those obtained with a threshold of 2.
+We did not consider the case of a threshold larger than 2 since the pairs will become less and less phonologically related.}
 The connectivity of a given node was characterized with its
@@
 between connectivity in the global network and the age of acquisition.
-This correlation is also compatible with INT, although the causality is
+This correlation is also necessary to INT, although the causality is
 reversed: higher connectivity in the global network is caused by earlier
@@
 end-state network and AoA can result from both EXT and INT. If there is
-no such correlation, neither growth scenarios can be posited as a
+no such correlation, neither growth scenario can be posited as a
 possible learning mechanism.
@@
 suggested by Arbesman et al. (2010), these \enquote{truncated}
-power-laws in phonological networks --as well as the cross-linguistic
-variability in the value of the cut-offs-- may reflect the various
-constraints that exist on word formation such as the number of phonemes
-in the language, the phonotactics (i.e., the way sound sequences are
-arranged in words), and the length of words. Such constraints may limit
-the number of words that are phonologically similar, thus leading to
-distributions which decay faster than a non-truncated power law.
+power-laws in phonological networks may reflect the various constraints
+that exist on word formation in the phonological domain such as the
+number of phonemes in the language, the phonotactics (i.e., the way
+sound sequences are arranged in words), and the length of words. Such
+constraints may limit the number of words that are phonologically
+similar, thus leading to distributions which decay faster than a
+non-truncated power law.
 
@@
 comprehension-based vocabulary, and holds across languages. This
-generalization was obtained in both the
-semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
-However, our findings do not support this assumption, rather it supports our initial approximation about the universality of the semantic similarity measure.}
-and phonological domains.
+generalization was obtained in both the semantic\footnote{One could
+  imagine that the fact of using English free association norms
+  cross-linguistically would decrease the effect of non-English semantic
+  networks because of possible cultural differences. However, our
+  findings do not support this assumption, rather it supports our
+  initial approximation about the universality of the semantic
+  similarity measure. That said, this apprimation is not perfect; there
+  is evidence that a small part of the variance in free assication data
+  can be explained by phonological similarity (Kachergis, Cox, \& Jones,
+  2011; Matusevych \& Stevenson, 2018), thus leading to possibly minor
+  cross-linguistic differences.} and phonological domains.
 
@@
 
+\hypertarget{ref-kachergis2011}{}
+Kachergis, G., Cox, G. E., \& Jones, M. N. (2011). OrBEAGLE: Integrating
+orthography into a holographic model of the lexicon. In
+\emph{International conference on artificial neural networks} (pp.
+307--314). Springer.
+
 \hypertarget{ref-kuhl1997}{}
@@
 
+\hypertarget{ref-matusevych2018}{}
+Matusevych, Y., \& Stevenson, S. (2018). Analyzing and modeling free
+word associations. In \emph{Proceedings of the 40th Annual Conference of
+the Cognitive Science Society}.
+
 \hypertarget{ref-mcrae2005}{}

### 2019-02-05 journal/ms.Rmd
modif journal

@@
 library(cowplot)
+library(ggpubr)
 library(knitr)
@@
 library(dplyr)
+library(gridExtra)
 library(langcog)
@@
 @markman90] to analyzing dense corpora capturing language learning in context [e.g., @roy2015].
-One strategy consists in documenting the timeline of words' acquisition, and studying the properties that make words easy or hard to learn.
-For example, within a lexical category, words that are more frequent in child-directed speech are acquired earlier [@goodman2008].
-Other factors include word length and the mean length of utterances in which the word occurs [e.g., @braginsky2016; @swingley2018].
+One prominent strategy consists in documenting the timeline of words' acquisition, and studying the properties that make words easy or hard to learn [e.g., @goodman2008; @huttenlocher1991].
+For example, @goodman2008 found that, within a lexical category (e.g., nouns), higher parental frequency is associated with earlier learning.
+Researchers have studied the role of several other factors such as word length and the mean length of utterances in which the word occurs [e.g., @braginsky2016; @swingley2018].
 
-Besides these word-level properties, the structure of the lexicon (that is, how words relate to one another) also predicts the Age of Acquisition (AoA) of words.
-The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words [e.g., @collins1975].
+Besides word-level properties, the structure of the lexicon (that is, how words relate to one another) was also found to predict the Age of Acquisition (AoA) of words.
+The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words [e.g., @collins1975; @luce1998].
 Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features [@mcrae2005], target-cue relationships in free association norms [@nelson1998], co-occurrence in child directed speech [@macwhinney2014], and phonological relatedness [@vitevitch2008].
@@
 
+<!-- For example, having a rich and organized knowledge about the domain of dinosaurs would facilitate the acquisition of new dinosaur-related words [@chi1983]. -->
 These two proposals represent two divergent ideas about the role of lexical networks in acquisition.
 On the INT proposal, learning is driven by known words with high connectivity to other known words (Figure 1, left).
-Thus, the network structure is a causal factor in early word learning, that is, children rely on the organization of their past knowledge to determine future learning.
-For example, having a rich and organized knowledge about the domain of dinosaurs would facilitate the acquisition of new dinosaur-related words [@chi1983].
+Thus, the network structure is a causal factor in early word learning, that is, children rely on the organization of their past knowledge to determine future learning [@storkel2009; @altvater2013; @chi1983; @borovsky2016].
 In contrast, on the EXT approach, learning is driven by the connectivity of words that are not known yet (Figure 1, right).
 Thus, the relevant network structure is not internally represented by children, and the observed connectivity effect might be an epiphenomenon of some properties of the linguistic input.
-For example, highly connected words in the input could be more easily learned because of their contextual diversity [e.g., @smith2008] or because caregivers emphasize such words in child-directed speech [@macwhinney2014].
+For example, highly connected words in the input could be more easily learned because of their contextual diversity, allowing for an easier meaning disambiguation [@smith2008; @mcmurray2012; @yurovsky2015].
+Another reason could be that these words are emphasized by the cargivers in their child-directed speech [@huttenlocher1991; @hoff2002; @clark2007].
 
@@
 @hills2009 investigated the growth of lexico-semantic networks in toddlers and found that growth did not proceed according to INT as was originally hypothesised by @steyvers2005, but rather according to EXT.\footnote{Besides INT and EXT, the authors tested a third mechanism (called the lure of associates) which resembles EXT in that it is driven by the connectivity of external nodes, except that this connectivity is computed with respect to words that are known.
-However, EXT is the externally-driven scenario that best predicted the data in this previous work.} This is a profound finding because it suggests that learning in the early stages is mostly driven by properties of the external input, regardless of how past knowledge is organized.
+However, EXT is the externally-driven scenario that best predicted the data in this previous work.} This is an important finding because it suggests that learning in the early stages is mostly driven by properties of the external input, regardless of how past knowledge is organized.
 However, this work has been done in the special case of networks that are based on 1) semantic associations, 2) production-based vocabularies, and 3) data from English-learning children, only.
@@
 
-We test the growth scenarios using parent reports of children vocabularies and their normative age of acquisition [@fenson94].
-Children may vary in their individual learning trajectories, but the aggregate data leads to an average learning pattern which is highly consistent.
-It is this normative trajectory that we model in the current study, following in this regard the steps of previous research using similar datasets [@storkel2009; @stella2017; @hills2009; @hills2010; @goodman2008; @braginsky2016]
+We adopted the following research strategy.
+We used a cross-linguistic dataset of children's vocabulary development [@frank2017; @fenson94], and we studied the timeline of word learning using the normative/average age of acquisition (i.e., the age at which at least 50% of children know a given words).
+Our choice of studying the normative learning trajectory rather than the individual trajectories was motivated by the nature of the dataset used---which is primarily based on cross-sectional studies.
+Children may vary in their individual learning trajectories, but the aggregate data provide highly robust measures of the average learning patterns [@fenson94].
+The use of such measures has lead to important insights on the mechanisms of word learning [@storkel2009; @stella2017; @hills2009; @hills2010; @goodman2008; @braginsky2016].
 
@@
 
-plot_correlation_prod <- ggplot(subset(data_long, measure == "produces"), aes(x=value, y=aoa))+
-  facet_grid(predictor ~ language)+#, scales = "free") +
+plot_correlation_prod_1 <- ggplot(subset(data_long, measure == "produces" & data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), 
+                                  aes(x=value, y=aoa))+
+  facet_grid(language~ predictor)+#, scales = "free") +
   geom_jitter(#aes(colour = lexical_class),
@@
         )+
-  geom_text(data=subset(correlations, measure=="produces"), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
+  geom_text(data=subset(correlations, measure=="produces" & correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
   xlab("degree z-score") +ylab("Age")
 
-plot_correlation_comp <- ggplot(subset(data_long, measure == "understands" & aoa < 35), aes(x=value, y=aoa))+
-  facet_grid(predictor ~ language)+#, scales = "free") +
+plot_correlation_prod_2 <- ggplot(subset(data_long, measure == "produces" & data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
+  facet_grid(language~ predictor)+#, scales = "free") +
   geom_jitter(#aes(colour = lexical_class),
@@
         )+
-  geom_text(data=subset(correlations, measure=="understands"), aes(label=paste("r=", cor, sep="")), x=3.5, y=25, size=2, fontface = "bold")+
+  geom_text(data=subset(correlations, measure=="produces" & correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
   xlab("degree z-score") +ylab("Age")
+
+corr_prod <- cowplot::plot_grid(
+  plot_correlation_prod_1 ,
+  plot_correlation_prod_2 ,
+  nrow = 1#, 
+  #align = 'vh',
+  #hjust = -1
+)
+
+#legend <- cowplot::get_legend(plot_degree_1)
+
+#plot_degree <- cowplot::plot_grid(prow, legend, nrow = 1, rel_widths = c(4, .5))
+
+plot_correlation_comp_1 <- ggplot(subset(data_long, measure == "understands" & aoa < 35 & data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(x=value, y=aoa))+
+  facet_grid(language~ predictor)+#, scales = "free") +
+  geom_jitter(#aes(colour = lexical_class),
+    colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  geom_abline(slope = -1)+
+  coord_cartesian(xlim=c(-1,5))+
+  #scale_x_continuous(limits=c(-2,5))+
+  scale_y_continuous(breaks =c(15,25,35))+
+  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
+  scale_colour_solarized(name = "") +
+  theme_few()+
+  #theme_bw()+
+  theme(aspect.ratio = 0.7, 
+        plot.margin=grid::unit(c(0,0,0,0), "mm")
+        )+
+  geom_text(data=subset(correlations, measure=="understands" & correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=3.5, y=25, size=2, fontface = "bold")+
+  xlab("degree z-score") +ylab("Age")
+
+plot_correlation_comp_2 <- ggplot(subset(data_long, measure == "understands" & aoa < 35 & data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
+  facet_grid(language~ predictor)+#, scales = "free") +
+  geom_jitter(#aes(colour = lexical_class),
+    colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  geom_abline(slope = -1)+
+  coord_cartesian(xlim=c(-1,5))+
+  #scale_x_continuous(limits=c(-2,5))+
+  scale_y_continuous(breaks =c(15,25,35))+
+  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
+  scale_colour_solarized(name = "") +
+  theme_few()+
+  #theme_bw()+
+  theme(aspect.ratio = 0.7, 
+        plot.margin=grid::unit(c(0,0,0,0), "mm")
+        )+
+  geom_text(data=subset(correlations, measure=="understands" & correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=3.5, y=25, size=2, fontface = "bold")+
+  xlab("degree z-score") +ylab("Age")
+
+corr_comp <- cowplot::plot_grid(
+  plot_correlation_comp_1 ,
+  plot_correlation_comp_2 ,
+  nrow = 1#, 
+  #align = 'vh',
+  #hjust = -1
+)
 
@@
 
-```{r corrAll, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Age of production (A) and comprehension (B) in the global network as predicted by the degree (i.e., connectivity) in this network.
+```{r corrProd, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Age of production in the global network as predicted by the degree (i.e., connectivity) in this network.
 Results are shown in each language for phonological and semantic networks.
-Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.", fig.width=8, fig.height=4}
+Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients."}
 
-plot_grid(plot_correlation_prod , NULL, plot_correlation_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+corr_prod
+#plot_grid(plot_correlation_prod , NULL, plot_correlation_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+```
+
+```{r corrComp, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Age of comprehension in the global network as predicted by the degree (i.e., connectivity) in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients."}
+corr_comp
+#plot_grid(plot_correlation_prod , NULL, plot_correlation_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
 
@@
 
-Figure \@ref(fig:corrAll) shows how the age of production and comprehension for each word varies as a function of its degree (or indegree for the semantic networks) as well as the correlation values.
+Figures \@ref(fig:corrProd) and \@ref(fig:corrComp) show how the age of production and comprehension, respectively, correlates with the degree (or indegree for the semantic networks).
 For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages.
@@
 
-plot_degree <- ggplot(data = degree_dist,  aes(x=x, y=y, col=dimension))+
-  facet_grid(data ~ language)+#, scales = "free") +
+plot_degree_1 <- ggplot(data = subset(degree_dist, degree_dist$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')),  
+                        aes(x=x, y=y, col=dimension))+
+  facet_grid( language ~ data)+#, scales = "free") +
   geom_point(#aes(colour = lexical_class),
@@
   scale_y_log10() + scale_x_log10() +
-  theme(aspect.ratio = 1) +
   theme_few()+
-  theme(aspect.ratio = 0.7)+
+  theme(legend.title = element_text(size=11),
+      legend.text=element_text(size=11),
+      axis.text = element_text(size = 8),
+      aspect.ratio = 0.7
+      )+
+  xlab("Degree") +ylab("")
+
+plot_degree_2 <- ggplot(data = subset(degree_dist, degree_dist$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')),  
+                        aes(x=x, y=y, col=dimension))+
+  facet_grid( language ~ data)+#, scales = "free") +
+  geom_point(#aes(colour = lexical_class),
+    #colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  scale_y_log10() + scale_x_log10() +
+  theme_few()+
+  theme(legend.title = element_text(size=11),
+      legend.text=element_text(size=11),
+      axis.text = element_text(size = 8),
+      aspect.ratio = 0.7
+      )+
   xlab("Degree") +ylab("Prob.")
 
-ggsave("figs/plot_degree.pdf", plot = plot_degree, width = 10, height = 3)
+prow <- cowplot::plot_grid(
+  plot_degree_1 + theme(legend.position = "none"),
+  plot_degree_2 + theme(legend.position = "none"),
+  nrow = 1, 
+  align = 'vh',
+  hjust = -1
+)
+legend <- cowplot::get_legend(plot_degree_1)
+
+plot_degree <- cowplot::plot_grid(prow, legend, nrow = 1, rel_widths = c(4, .5))
+
+#plot_degree_2
+#ggarrange(plot_degree_1, plot_degree_2, common.legend = TRUE, legend="bottom")
+#ggsave("figs/plot_degree.png", plot = plot_degree, width = 4, height = 8)
+#legend <- get_legend(plot_degree_1)
+
+#plot_degree <- grid.arrange(
+#  plot_degree_1 + theme(legend.position="none"),
+#  plot_degree_2+  theme(legend.position="none"),
+# legend,
+#  ncol=3)
+
 ```
 
-```{r degreeDist, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
+```{r degreeDist, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
 The figure shows the results for both production and comprehension data.
-A perfect power-law distribution should appear as a straight line in this graph.",  fig.width=10, fig.height=2}
-
+A perfect power-law distribution should appear as a straight line in this graph."}
 #knitr::include_graphics("figs/plot_degree.pdf")
 plot_degree
+
+#img <- png::readPNG("figs/plot_degree.png")
+#grid::grid.raster(img)
 ```
@@
 "father" counts as "daddy").
-Although these frequency counts use transcripts from independent sets of children, they are based on large samples, and this allows us to average out possible differences between children and the specificities of their input [see @goodman2008].
+Although these frequency counts use transcripts from independent sets of children, they are based on large samples, and this allows us to average out possible differences between children and the specificities of their input [see @goodman2008 for a similar research strategy].
 

### 2019-02-05 journal/ms.tex
modif journal

@@
 language learning in context (e.g., B. C. Roy, Frank, DeCamp, Miller, \&
-Roy, 2015). One strategy consists in documenting the timeline of words'
-acquisition, and studying the properties that make words easy or hard to
-learn. For example, within a lexical category, words that are more
-frequent in child-directed speech are acquired earlier (J. C. Goodman,
-Dale, \& Li, 2008). Other factors include word length and the mean
-length of utterances in which the word occurs (e.g., Braginsky,
+Roy, 2015). One prominent strategy consists in documenting the timeline
+of words' acquisition, and studying the properties that make words easy
+or hard to learn (e.g., J. C. Goodman, Dale, \& Li, 2008; Huttenlocher,
+Haight, Bryk, Seltzer, \& Lyons, 1991). For example, J. C. Goodman et
+al. (2008) found that, within a lexical category (e.g., nouns), higher
+parental frequency is associated with earlier learning. Researchers have
+studied the role of several other factors such as word length and the
+mean length of utterances in which the word occurs (e.g., Braginsky,
 Yurovsky, Marchman, \& Frank, 2016; Swingley \& Humphrey, 2018).
 
-Besides these word-level properties, the structure of the lexicon (that
-is, how words relate to one another) also predicts the Age of
+Besides word-level properties, the structure of the lexicon (that is,
+how words relate to one another) was also found to predict the Age of
 Acquisition (AoA) of words. The lexical structure can be characterized
@@
 vocabulary, and each link between two nodes represents a relationship
-between the corresponding pair of words (e.g., Collins \& Loftus, 1975).
-Previous studies have investigated early vocabulary structure by
-constructing networks using a variety of word-word relations including
-shared semantic features (McRae, Cree, Seidenberg, \& McNorgan, 2005),
-target-cue relationships in free association norms (Nelson, McEvoy, \&
-Schreiber, 1998), co-occurrence in child directed speech (MacWhinney,
-2014), and phonological relatedness (Vitevitch, 2008). These studies
-have generally found that children tend to produce words that have
-higher neighborhood density (i.e., high connectivity in the network)
-earlier, both at the phonological and the semantic level (Carlson,
-Sonderegger, \& Bane, 2014; Hills, Maouene, Riordan, \& Smith, 2010;
-Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Stella, Beckage, \&
-Brede, 2017; Storkel, 2009).
+between the corresponding pair of words (e.g., Collins \& Loftus, 1975;
+Luce \& Pisoni, 1998). Previous studies have investigated early
+vocabulary structure by constructing networks using a variety of
+word-word relations including shared semantic features (McRae, Cree,
+Seidenberg, \& McNorgan, 2005), target-cue relationships in free
+association norms (Nelson, McEvoy, \& Schreiber, 1998), co-occurrence in
+child directed speech (MacWhinney, 2014), and phonological relatedness
+(Vitevitch, 2008). These studies have generally found that children tend
+to produce words that have higher neighborhood density (i.e., high
+connectivity in the network) earlier, both at the phonological and the
+semantic level (Carlson, Sonderegger, \& Bane, 2014; Hills, Maouene,
+Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya, \& Smith, 2009;
+Stella, Beckage, \& Brede, 2017; Storkel, 2009).
 
@@
 learning, that is, children rely on the organization of their past
-knowledge to determine future learning. For example, having a rich and
-organized knowledge about the domain of dinosaurs would facilitate the
-acquisition of new dinosaur-related words (Chi \& Koeske, 1983). In
-contrast, on the EXT approach, learning is driven by the connectivity of
-words that are not known yet (Figure 1, right). Thus, the relevant
-network structure is not internally represented by children, and the
-observed connectivity effect might be an epiphenomenon of some
-properties of the linguistic input. For example, highly connected words
-in the input could be more easily learned because of their contextual
-diversity (e.g., Smith \& Yu, 2008) or because caregivers emphasize such
-words in child-directed speech (MacWhinney, 2014).
+knowledge to determine future learning (Altvater-Mackensen \& Mani,
+2013; Borovsky, Ellis, Evans, \& Elman, 2016; Chi \& Koeske, 1983;
+Storkel, 2009). In contrast, on the EXT approach, learning is driven by
+the connectivity of words that are not known yet (Figure 1, right).
+Thus, the relevant network structure is not internally represented by
+children, and the observed connectivity effect might be an epiphenomenon
+of some properties of the linguistic input. For example, highly
+connected words in the input could be more easily learned because of
+their contextual diversity, allowing for an easier meaning
+disambiguation (McMurray, Horst, \& Samuelson, 2012; Smith \& Yu, 2008;
+Yurovsky \& Frank, 2015). Another reason could be that these words are
+emphasized by the cargivers in their child-directed speech (Clark, 2007;
+Hoff \& Naigles, 2002; Huttenlocher et al., 1991).
 
@@
 However, EXT is the externally-driven scenario that best predicted the data in this previous work.}
-This is a profound finding because it suggests that learning in the
+This is an important finding because it suggests that learning in the
 early stages is mostly driven by properties of the external input,
@@
 
-We test the growth scenarios using parent reports of children
-vocabularies and their normative age of acquisition (Fenson et al.,
-1994). Children may vary in their individual learning trajectories, but
-the aggregate data leads to an average learning pattern which is highly
-consistent. It is this normative trajectory that we model in the current
-study, following in this regard the steps of previous research using
-similar datasets (Braginsky et al., 2016; J. C. Goodman et al., 2008;
-Hills et al., 2010, 2009; Stella et al., 2017; Storkel, 2009)
+We adopted the following research strategy. We used a cross-linguistic
+dataset of children's vocabulary development (Fenson et al., 1994;
+Frank, Braginsky, Yurovsky, \& Marchman, 2017), and we studied the
+timeline of word learning using the normative/average age of acquisition
+(i.e., the age at which at least 50\% of children know a given words).
+Our choice of studying the normative learning trajectory rather than the
+individual trajectories was motivated by the nature of the dataset
+used---which is primarily based on cross-sectional studies. Children may
+vary in their individual learning trajectories, but the aggregate data
+provide highly robust measures of the average learning patterns (Fenson
+et al., 1994). The use of such measures has lead to important insights
+on the mechanisms of word learning (Braginsky et al., 2016; J. C.
+Goodman et al., 2008; Hills et al., 2010, 2009; Stella et al., 2017;
+Storkel, 2009).
 
@@
 
-We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
-2017), an open repository aggregating cross-linguistic language
-developmental data of the MacArthur-Bates Communicative Development
-Inventory (CDI), a parent report vocabulary checklist. Parent report is
-a reliable and valid measure of children's vocabulary that allows for
-the cost-effective collection of datasets large enough to test
-network-based models of acquisition (Fenson et al., 1994). When filling
-out a CDI form, caregivers are either invited to indicate whether their
-child \enquote{understands} (comprehension) or \enquote{understands and
-says} (production) each of about 400-700 words. For younger children
-(e.g., 8 to 18 months in the English data), both comprehension and
-production are queried, whereas for older children (16 to 36 months)
-only production is queried. Due to these limitations, we use data from
-younger children to test comprehension and data from older children to
-test production. Following previous studies (Hills et al., 2009;
-Storkel, 2009), we restrict our analysis to the category of
+We used data from Wordbank (Frank et al., 2017), an open repository
+aggregating cross-linguistic language developmental data of the
+MacArthur-Bates Communicative Development Inventory (CDI), a parent
+report vocabulary checklist. Parent report is a reliable and valid
+measure of children's vocabulary that allows for the cost-effective
+collection of datasets large enough to test network-based models of
+acquisition (Fenson et al., 1994). When filling out a CDI form,
+caregivers are either invited to indicate whether their child
+\enquote{understands} (comprehension) or \enquote{understands and says}
+(production) each of about 400-700 words. For younger children (e.g., 8
+to 18 months in the English data), both comprehension and production are
+queried, whereas for older children (16 to 36 months) only production is
+queried. Due to these limitations, we use data from younger children to
+test comprehension and data from older children to test production.
+Following previous studies (Hills et al., 2009; Storkel, 2009), we
+restrict our analysis to the category of
 nouns.\footnote{This choice was also forced by the fact that the great majority of association data produced by adults–and which we used to build semantic networks–were nouns.}.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/corrAll-1} \caption{Age of production (A) and comprehension (B) in the global network as predicted by the degree (i.e., connectivity) in this network.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrProd-1} \caption{Age of production in the global network as predicted by the degree (i.e., connectivity) in this network.
 Results are shown in each language for phonological and semantic networks.
-Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrAll}
+Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrProd}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrComp-1} \caption{Age of comprehension in the global network as predicted by the degree (i.e., connectivity) in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrComp}
 \end{figure}
@@
 
-Figure \ref{fig:corrAll} shows how the age of production and
-comprehension for each word varies as a function of its degree (or
-indegree for the semantic networks) as well as the correlation values.
-For ease of visual comparison, the predictor (i.e., the degree) was
-centered and scaled across languages. The plots show, overall, a
-negative correlation between the month of acquisition and the degree. In
-production data, the average correlation across languages was -0.24
-(SD=0.10) for the semantic networks and -0.30 (SD=0.05) for the
-phonological networks. In comprehension data, the average correlation
-was -0.21 (SD=0.08) for the semantic networks and -0.21 (SD=0.07) for
-the phonological networks. These results indicate that nouns with higher
-degrees are generally learned earlier, thus replicating previous
-findings in English (e.g., Storkel 2004, 2009; Hills et al. 2009) and
-extending these findings to 10 different languages, generally, in both
-production- and comprehension-based vocabularies.
+Figures \ref{fig:corrProd} and \ref{fig:corrComp} show how the age of
+production and comprehension, respectively, correlates with the degree
+(or indegree for the semantic networks). For ease of visual comparison,
+the predictor (i.e., the degree) was centered and scaled across
+languages. The plots show, overall, a negative correlation between the
+month of acquisition and the degree. In production data, the average
+correlation across languages was -0.24 (SD=0.10) for the semantic
+networks and -0.30 (SD=0.05) for the phonological networks. In
+comprehension data, the average correlation was -0.21 (SD=0.08) for the
+semantic networks and -0.21 (SD=0.07) for the phonological networks.
+These results indicate that nouns with higher degrees are generally
+learned earlier, thus replicating previous findings in English (e.g.,
+Storkel 2004, 2009; Hills et al. 2009) and extending these findings to
+10 different languages, generally, in both production- and
+comprehension-based vocabularies.
 
@@
   initial approximation about the universality of the semantic
-  similarity measure. That said, this apprimation is not perfect; there
-  is evidence that a small part of the variance in free assication data
-  can be explained by phonological similarity (Kachergis, Cox, \& Jones,
-  2011; Matusevych \& Stevenson, 2018), thus leading to possibly minor
-  cross-linguistic differences.} and phonological domains.
+  similarity measure. That said, this apprimation is not perfect; for
+  example there is evidence that a small part of the variance in free
+  assication data can be explained by phonological similarity
+  (Kachergis, Cox, \& Jones, 2011; Matusevych \& Stevenson, 2018), thus
+  leading to possibly minor cross-linguistic differences.} and
+phonological domains.
 
@@
 correlate with phonological connectivity: Shorter words are more likely
-to have higher connectivity (Pisoni, Nusbaum, Luce, \& Slowiaczek, 1985;
-Vitevitch \& Rodríguez, 2005).
+to have higher connectivity (D. B. Pisoni, Nusbaum, Luce, \& Slowiaczek,
+1985; Vitevitch \& Rodríguez, 2005).
 
@@
 between children and the specificities of their input (see J. C. Goodman
-et al., 2008).
+et al., 2008 for a similar research strategy).
 
@@
 \hypertarget{refs}{}
+\hypertarget{ref-altvater2013}{}
+Altvater-Mackensen, N., \& Mani, N. (2013). Word-form familiarity
+bootstraps infant speech segmentation. \emph{Developmental Science},
+\emph{16}(6).
+
 \hypertarget{ref-arbesman2010}{}
@@
 
+\hypertarget{ref-borovsky2016}{}
+Borovsky, A., Ellis, E. M., Evans, J. L., \& Elman, J. L. (2016).
+Lexical leverage: Category knowledge boosts real-time novel word
+recognition in 2-year-olds. \emph{Developmental Science}, \emph{19}(6).
+
 \hypertarget{ref-braginsky2016}{}
@@
 
+\hypertarget{ref-huttenlocher1991}{}
+Huttenlocher, J., Haight, W., Bryk, A., Seltzer, M., \& Lyons, T.
+(1991). Early vocabulary growth: Relation to language input and gender.
+\emph{Developmental Psychology}, \emph{27}(2).
+
 \hypertarget{ref-jusczyk1994}{}
@@
 
+\hypertarget{ref-luce1998}{}
+Luce, P. A., \& Pisoni, D. B. (1998). Recognizing spoken words: The
+neighborhood activation model. \emph{Ear and Hearing}, \emph{19}(1).
+
 \hypertarget{ref-macwhinney2014}{}
@@
 the Cognitive Science Society}.
+
+\hypertarget{ref-mcmurray2012}{}
+McMurray, B., Horst, J. S., \& Samuelson, L. K. (2012). Word learning
+emerges from the interaction of online referent selection and slow
+associative learning. \emph{Psychological Review}, \emph{119}.
 

### 2019-02-06 journal/ms.Rmd
second version journal

@@
 ---
-title             : "Word Learning as Network Growth: A Cross-linguistic Analysis"
-shorttitle        : "Word Learning as Network Growth"
+title             : "Noun Learning as Network Growth: A Cross-linguistic Analysis"
+shorttitle        : "Noun Learning as Network Growth"
 #numbersections: true
@@
 
-keywords          : "Language understanding; audio-visual processing; word learning; speech perception; computational modeling."
+keywords          : "Word learning; semantic network; phonological network; network growth; cross-linguistic analysis."
 
@@
 Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features [@mcrae2005], target-cue relationships in free association norms [@nelson1998], co-occurrence in child directed speech [@macwhinney2014], and phonological relatedness [@vitevitch2008].
-These studies have generally found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @stella2017; @carlson2014].
+These studies have generally found that children tend to produce nouns that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @stella2017; @carlson2014].
 
@@
 According to this explanation, known as Preferential Attachment, highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99].
-In other words, what predicts word learning is the *internal* connectivity in the child's early lexicon.
+In other words, what predicts learning is the *internal* connectivity in the child's early lexicon.
 In contrast, @hills2009 suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment.
@@
 On the INT proposal, learning is driven by known words with high connectivity to other known words (Figure 1, left).
-Thus, the network structure is a causal factor in early word learning, that is, children rely on the organization of their past knowledge to determine future learning [@storkel2009; @altvater2013; @chi1983; @borovsky2016].
+Thus, the network structure is a causal factor in word learning, that is, children rely on the organization of their past knowledge to determine future learning [@storkel2009; @altvater2013; @chi1983; @borovsky2016].
 In contrast, on the EXT approach, learning is driven by the connectivity of words that are not known yet (Figure 1, right).
 Thus, the relevant network structure is not internally represented by children, and the observed connectivity effect might be an epiphenomenon of some properties of the linguistic input.
-For example, highly connected words in the input could be more easily learned because of their contextual diversity, allowing for an easier meaning disambiguation [@smith2008; @mcmurray2012; @yurovsky2015].
-Another reason could be that these words are emphasized by the cargivers in their child-directed speech [@huttenlocher1991; @hoff2002; @clark2007].
+For example, highly connected concrete nouns in the input could be more easily learned because of their contextual diversity, allowing for an easier meaning disambiguation [@smith2008; @mcmurray2012; @yurovsky2015].
+Another reason could be that these words are emphasized by the caregivers in their child-directed speech [@huttenlocher1991; @hoff2002; @clark2007].
 
@@
 
-@hills2009 investigated the growth of lexico-semantic networks in toddlers and found that growth did not proceed according to INT as was originally hypothesised by @steyvers2005, but rather according to EXT.\footnote{Besides INT and EXT, the authors tested a third mechanism (called the lure of associates) which resembles EXT in that it is driven by the connectivity of external nodes, except that this connectivity is computed with respect to words that are known.
+@hills2009 investigated the growth of lexico-semantic networks in toddlers and found that growth did not proceed according to INT as was originally hypothesized by @steyvers2005, but rather according to EXT.\footnote{Besides INT and EXT, the authors tested a third mechanism (called the lure of associates) which resembles EXT in that it is driven by the connectivity of external nodes, except that this connectivity is computed with respect to words that are known.
 However, EXT is the externally-driven scenario that best predicted the data in this previous work.} This is an important finding because it suggests that learning in the early stages is mostly driven by properties of the external input, regardless of how past knowledge is organized.
@@
 Does the phonological network also predict word learning?
-Previous work did find an effect of words' connectivity in the phonological network on their age of learning [@storkel2009; @stella2017; @carlson2014].
-In other words, words learned earlier in life tend to sound similar to many other words than a word learned later in life.
+Previous work did find an effect of nouns' connectivity in the phonological network on their age of learning [@storkel2009; @stella2017; @carlson2014].
+In other words, nouns learned earlier in life tend to sound similar to many other nouns than a word learned later in life.
 However, this finding is *a priori* compatible with both INT and EXT, and previous studies did not explicitly compare these two mechanisms.
@@
 Second, we study vocabularies measured using both comprehension and production.
-Previous studies have found differences between these vocabularies in terms of their content and rate of acquisition [@benedict1979; @fenson94].
+Previous studies have found differences between these vocabularies in terms of their content and rate of acquisition [@benedict1979; @fenson94; @bates1995].
 These differences may reflect the fact that comprehension and production do not share the same constraints.
@@
 We adopted the following research strategy.
-We used a cross-linguistic dataset of children's vocabulary development [@frank2017; @fenson94], and we studied the timeline of word learning using the normative/average age of acquisition (i.e., the age at which at least 50% of children know a given words).
+We used a cross-linguistic dataset of children's vocabulary development [@frank2017; @fenson94], and we studied the timeline of noun learning using the normative age of acquisition (i.e., the age at which at least 50% of children know a given words).
 Our choice of studying the normative learning trajectory rather than the individual trajectories was motivated by the nature of the dataset used---which is primarily based on cross-sectional studies.
@@
 First, we describe the datasets we used and explain how we constructed the networks.
-Second, we analyze static properties of words' connectivity in these networks (correlation with age of acquisition and shape of the distribution) and we explain how these properties infom hypotheses about network growth.
+Second, we analyze static properties of words' connectivity in these networks (correlation with age of acquisition and shape of the distribution) and we explain how these properties inform hypotheses about network growth.
 Next, we explicitly fit the two hypothesized growth mechanisms to the data.
@@
 Due to these limitations, we use data from younger children to test comprehension and data from older children to test production.
-Following previous studies [@storkel2009; @hills2009], we restrict our analysis to the category of nouns.\footnote{This choice was also forced by the fact that the great majority of association data produced by adults–and which we used to build semantic networks–were nouns.}.
+In addition, following previous studies [@storkel2009; @hills2009], we restricted our analysis to the category of nouns due to the fact that nouns predominate the early expressive and receptive lexicons [@bates1995].
+Their larger sample size (compared, for example, to verbs or adjectives) is more suited to the network-based analysis of development.
 Table \@ref(tab:stats) gives an overview of the data we used.
+
+<!--
+ Following previous studies [@storkel2009; @hills2009], we restrict our analysis to the category of nouns.
+\footnote{This choice was also forced by the fact that the great majority of association data produced by adults–and which we used to build semantic networks–were nouns.}-->
 
@@
 A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms.
-The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target.\footnote{This choice was based the prior work by @hills2009 stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated for indegree.} To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.
+The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target.\footnote{This choice was based on prior work by Hills et al.
+(2009) stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated with indegree.} To model growth from month to month, we constructed a different network at each month, based on the nouns that have been acquired by that month.
 
@@
 Using the same association data across languages does not necessarily lead to similar networks.
-Indeed, though this approximation assumes that the semantic similarity measure is universal–which is a reasonable approximation [e.g., @youn2016], the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possibility different learning strategies.
+Indeed, though this approximation assumes that the semantic similarity measure is universal---which is a reasonable approximation [e.g., @youn2016]---the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possibility different learning strategies.
 
@@
 
-To construct phonological networks we first mapped the orthographic transcription of words to their International Phonetic Alphabet (IPA) transcriptions in each language, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes.
+To construct phonological networks we first mapped the orthographic transcription of words to their International Phonetic Alphabet (IPA) transcriptions in each language, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/)**.
+This software provides the correct IPA transcription if the word is found in a spelling-to-phonemes dictionary, otherwise it uses  language-specific pronunciation rules to generate an approximate phonetic transcription.
+We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes.
 The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.
@@
 In previous studies, two nodes were linked if they had an edit distance of 1 [@storkel2009; @carlson2014; @stella2017].
-However, these studies reported a contribution of phonological connectivity to word learning when networks were built using a rich adult vocabulary.
+However, these studies reported a contribution of phonological connectivity to noun learning when networks were built using a rich adult vocabulary.
 Since the focus of the current study is on the mechanism of growth, the networks should be based on children's early vocabulary.
-The latter, however, contains very few word pairs with an edit distance of 1.
+The latter, however, contains very few noun pairs with an edit distance of 1.
 Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold.
 In both cases, the results were weaker than those obtained with a threshold of 2.
-We did not consider the case of a threshold larger than 2 since the pairs will become less and less phonologically related.} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
+We did not consider the case of a threshold larger than 2 since many pairs become phonologically unrelated.} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
 
@@
 Below we analyze properties of this global networks that may a priori hint at an INT- or EXT-like growth.
-In order to compare various predictors on the same data, we restrict the analysis to the subset of nouns for which we had both semantic and phonological information in each language.
+In order to compare various predictors on the same data, we restrict the analysis to the subset of nouns for which we had semantic associates in the free association norms.
 
@@
 Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.
-This correlation is also necessary to INT, although the causality is reversed: higher connectivity in the global network is caused by earlier learning, not the other way around.
+This correlation is also necessary to INT, although the causality is reversed: Higher connectivity in the global network is caused by earlier learning, not the other way around.
 Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.
@@
 Figures \@ref(fig:corrProd) and \@ref(fig:corrComp) show how the age of production and comprehension, respectively, correlates with the degree (or indegree for the semantic networks).
-For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages.
+For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled.
 The plots show, overall, a negative correlation between the month of acquisition and the degree.
-In production data, the average correlation across languages was `r ps_ave` (SD=`r ps_sd`) for the semantic networks and `r pp_ave` (SD=`r pp_sd`) for the phonological networks.
-In comprehension data, the average correlation was `r cs_ave` (SD=`r cs_sd`) for the semantic networks and `r cp_ave` (SD=`r cp_sd`) for the phonological networks.
-These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English (e.g., Storkel 2004, 2009; Hills et al.
-2009) and extending these findings to 10 different languages, generally, in both production- and comprehension-based vocabularies.
+In production data, the average correlation across languages was `r ps_ave` ($SD=$`r ps_sd`) for the semantic networks and `r pp_ave` ($SD=$`r pp_sd`) for the phonological networks.
+In comprehension data, the average correlation was `r cs_ave` ($SD=$`r cs_sd`) for the semantic networks and `r cp_ave` ($SD=$`r cp_sd`) for the phonological networks.
+These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English [@storkel2009; @hills2009] and extending these findings to 10 different languages, generally, in both production- and comprehension-based vocabularies.
 
@@
 That said, phonological networks had relatively larger cut-offs than semantic networks.
-As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks may reflect the various constraints that exist on word formation in the phonological domain such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words.
-Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law.
+These "truncated" power-laws  in phonological networks may be due to the constraints that exist on word formation in the phonological domain such as the size of the phonemic inventory, phonotactic rules, and word length.
+Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law [@arbesman2010].
 
@@
 Markov Chain Monte Carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \@ref(fig:growthPred).
-
-First, the results replicate Hills et al.'s original finding regarding the semantic network in English and the production-based vocabulary, which is that this network grows by EXT, not by INT.
-Second, our results show that, generally speaking, this finding generalizes to comprehension-based vocabulary, and holds across languages.
+The results replicate Hills et al.'s original finding regarding the semantic network in English and the production-based vocabulary, which is that this network grows by EXT, not by INT.
+Crucially, our results show that, generally speaking, this finding generalizes to comprehension-based vocabulary, and holds across languages.
 This generalization was obtained in both the semantic^[One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
-However, our findings do not support this assumption, rather it supports our initial approximation about the universality of the semantic similarity measure.
-That said, this apprimation is not perfect; for example there is evidence that a small part of the variance in free assication data can be explained by phonological similarity [@kachergis2011; @matusevych2018], thus leading to possibly minor cross-linguistic differences.] and phonological domains.
+However, our findings do not support this assumption, rather, it supports our initial approximation about the universality of the semantic similarity measure.
+That said, this approximation is not perfect.
+For example there is evidence that a small part of the variance in free association data can be explained by phonological similarity [@kachergis2011; @matusevych2018], thus leading to possibly minor cross-linguistic differences.] and phonological domains.
 
@@
 The latter was a requirement only for INT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.
-A more direct way to assess and compare the contribution of EXT in relation to other word-level factors is through conducting linear regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.
+A more direct way to assess and compare the contribution of EXT in relation to other word-level factors is through conducting regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.
 
@@
 For word frequency, we used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language [@macwhinney2014].
-For each word, counts included words that shared the same stem  (e.g., "cats" counts as "cat"), or words that were synonymous (e.g.
-"father" counts as "daddy").
 Although these frequency counts use transcripts from independent sets of children, they are based on large samples, and this allows us to average out possible differences between children and the specificities of their input [see @goodman2008 for a similar research strategy].
@@
 Word length is more predictive for production than comprehension (and this difference is very clear in the global model), replicating previous work (Braginsky et al., under review).
-Thus, word length seems to reflect the effects of production's constraints rather than than comprehension's constraints, i.e., longer words are harder to articulate but they may not be significantly more difficult to store and access.
+Thus, word length seems to reflect the effects of production's constraints rather than comprehension's constraints, i.e., longer words are harder to articulate but they may not be significantly more difficult to store and access.
 
@@
 In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
-This contrasts with the original finding in @hills2009.
-However, this might be due to our using a slightly different model (which included word length as a covariate) and a larger dataset.
+This finding contrasts with the original finding in @hills2009.
+However, this difference might be due to our using a slightly different model (which included word length as a covariate) and a larger dataset.
 That said, and despite these apparent cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model (Figure \@ref(fig:staticAll)).
@@
 These two mechanisms represent two fundamentally different accounts of lexical growth: One suggests that future word knowledge is primarily shaped by the children’s past knowledge and its organization, whereas the other suggests that learning is shaped, rather, by salient properties in the input regardless of how past knowledge is organized.
-The present study tested the generality of previous findings [@hills2009; @hills2010] by 1) investigating phonological networks together with semantic networks, 2) testing both comprehension- and production-based vocabularies, and 3) comparing the results across 10 languages.
+The present study tested the generality of previous findings by 1) investigating phonological networks together with semantic networks, 2) testing both comprehension- and production-based vocabularies, and 3) comparing the results across 10 languages.
 
@@
 
-For example, in the semantic domain, growth according to EXT can be explained by a mechanism similar to cross-situational learning [@smith2008; @pinker2013; @yurovsky2015].
+For example, in the semantic domain, growth according to EXT can be explained by a mechanism similar to cross-situational learning [@smith2008; @mcmurray2012; @yurovsky2015].
 According to this mechanism, children track the co-occurrence of concrete nouns with their possible semantic referents.
@@
 Crucially, children can learn these words without necessarily knowing the meaning of all other words with witch they co-occur (hence the similarity with EXT).
-This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@hills2010].
+This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@stella2017; @hills2010].
 
-In the phonological case, network growth according to EXT is also compatible with a scenario whereby children are tracking lwo level statistical patterns, e.g., high probability sound sequences.
+In the phonological case, network growth according to EXT is also compatible with a scenario whereby children are tracking low level statistical patterns, e.g., high probability sound sequences.
 Indeed, connectivity in the phonological network is inherently correlated with phonotactic probability [@vitevitch1999].
@@
 Children are sensitive to local phonotactic regularities [@jusczyk1994] and this sensitivity might lead them to learn higher-probability words more easily [@storkel2001].
-This explanation is supported by computational simulations that show how learning general phonotactics patterns create ``well-worn paths'' which allow the models to represent several distinct but phonologically neighboring words [@dell1993; @takac2017].
+This explanation is supported by computational simulations that show how learning general phonotactics patterns create "well-worn paths" which allow the models to represent several distinct but phonologically neighboring words [@dell1993; @takac2017].
 
@@
 This emphasis would guide children to learn first these highly connected words even though children do not have access to the distribution of words' connectivity in the final network.
-Investigating this possibility would require further research on caregiver-child interaction [@macwhinney2014; @roy2015], examining what words are introduced over development and the extent to which children's uptake is influenced by this input [@clark2007; @hoff2002].
+Investigating this possibility would require further research on caregiver-child interaction [@macwhinney2014; @roy2015], examining what words are introduced over development and the extent to which children's uptake is influenced by this input [@huttenlocher1991; @clark2007; @hoff2002].
 
@@
 Chief among these limitations is the fact that the age of word acquisition is computed using different children at different ages (due to the fact that available CDI data is mainly cross-sectional).
-Although this measure has proven highly consistent [@fenson94], it led us to focus on studying the learning mechanism of the "average" child.
-Individual trajectories, however, could lead to different netwtok strcutures and show different learning patterns.
-For example, using longitudinal data @beckage2011 found differences between typical and late talkers in terms of the semantic network structure.
+Such a measure has been shown to be valid and reliable [@fenson94], and has allowed researchers to study important aspects of word learning [@hills2009; @stella2017; @storkel2009; @goodman2008; @braginsky2016 ].
+In our case, the use of cost-effective cross-sectional data has allowed us to leverage large-scale studies across several languages.
+That said, it is important to remember that this type of data can only inform us about the learning trajectory of the "average" child.
+Although our study endorses, overall, the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT (Beckage and Colunga, under review).
+To illustrate, some children develop "islands of expertise", that is, well organized knowledge about a certain topic (e.g., birds or dinosaurs).
+This prior knowledge enables these children to learn new related words more easily [e.g., @chi1983].
+
+<!--Individual trajectories, however, could lead to different network strcutures and show different learning patterns.
+For example, using longitudinal data from English-learning toddlers  @beckage2011 found differences between typical and late talkers in terms of the semantic network structure.
 Besides, although our study endorses the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT (Beckage and Colunga, under review).
@@
 This prior knowledge enables these children to learn new related words more easily [e.g., @chi1983].
+-->
 

### 2019-02-06 journal/ms.tex
second version journal

@@
             pdfauthor={},
-            pdftitle={Word Learning as Network Growth: A Cross-linguistic Analysis},
+            pdftitle={Noun Learning as Network Growth: A Cross-linguistic Analysis},
             colorlinks=true,
@@
 % Essential manuscript parts
-  \title{Word Learning as Network Growth: A Cross-linguistic Analysis}
-
-  \shorttitle{Word Learning as Network Growth}
+  \title{Noun Learning as Network Growth: A Cross-linguistic Analysis}
+
+  \shorttitle{Noun Learning as Network Growth}
 
@@
 and learn highly connected words in the learning environment.}
-  \keywords{Language understanding; audio-visual processing; word learning; speech
-perception; computational modeling. \\
+  \keywords{Word learning; semantic network; phonological network; network growth;
+cross-linguistic analysis. \\
 
@@
 (Vitevitch, 2008). These studies have generally found that children tend
-to produce words that have higher neighborhood density (i.e., high
+to produce nouns that have higher neighborhood density (i.e., high
 connectivity in the network) earlier, both at the phonological and the
@@
 rich-get-richer scenario (Barabasi \& Albert, 1999). In other words,
-what predicts word learning is the \emph{internal} connectivity in the
+what predicts learning is the \emph{internal} connectivity in the
 child's early lexicon. In contrast, Hills et al. (2009) suggested that
@@
 by known words with high connectivity to other known words (Figure 1,
-left). Thus, the network structure is a causal factor in early word
-learning, that is, children rely on the organization of their past
-knowledge to determine future learning (Altvater-Mackensen \& Mani,
-2013; Borovsky, Ellis, Evans, \& Elman, 2016; Chi \& Koeske, 1983;
-Storkel, 2009). In contrast, on the EXT approach, learning is driven by
-the connectivity of words that are not known yet (Figure 1, right).
-Thus, the relevant network structure is not internally represented by
-children, and the observed connectivity effect might be an epiphenomenon
-of some properties of the linguistic input. For example, highly
-connected words in the input could be more easily learned because of
+left). Thus, the network structure is a causal factor in word learning,
+that is, children rely on the organization of their past knowledge to
+determine future learning (Altvater-Mackensen \& Mani, 2013; Borovsky,
+Ellis, Evans, \& Elman, 2016; Chi \& Koeske, 1983; Storkel, 2009). In
+contrast, on the EXT approach, learning is driven by the connectivity of
+words that are not known yet (Figure 1, right). Thus, the relevant
+network structure is not internally represented by children, and the
+observed connectivity effect might be an epiphenomenon of some
+properties of the linguistic input. For example, highly connected
+concrete nouns in the input could be more easily learned because of
 their contextual diversity, allowing for an easier meaning
@@
 Yurovsky \& Frank, 2015). Another reason could be that these words are
-emphasized by the cargivers in their child-directed speech (Clark, 2007;
-Hoff \& Naigles, 2002; Huttenlocher et al., 1991).
+emphasized by the caregivers in their child-directed speech (Clark,
+2007; Hoff \& Naigles, 2002; Huttenlocher et al., 1991).
 
@@
 in toddlers and found that growth did not proceed according to INT as
-was originally hypothesised by Steyvers and Tenenbaum (2005), but rather
+was originally hypothesized by Steyvers and Tenenbaum (2005), but rather
 according to
@@
 versa. Does the phonological network also predict word learning?
-Previous work did find an effect of words' connectivity in the
+Previous work did find an effect of nouns' connectivity in the
 phonological network on their age of learning (Carlson et al., 2014;
-Stella et al., 2017; Storkel, 2009). In other words, words learned
-earlier in life tend to sound similar to many other words than a word
+Stella et al., 2017; Storkel, 2009). In other words, nouns learned
+earlier in life tend to sound similar to many other nouns than a word
 learned later in life. However, this finding is \emph{a priori}
@@
 production. Previous studies have found differences between these
-vocabularies in terms of their content and rate of acquisition
-(Benedict, 1979; Fenson et al., 1994). These differences may reflect the
-fact that comprehension and production do not share the same
-constraints. For instance, whereas comprehension depends on the ease
-with which words are stored and accessed, production depends,
-additionally, on the ease with which words are articulated, e.g.,
-shorter words are produced earlier (Braginsky et al., 2016). By
+vocabularies in terms of their content and rate of acquisition (Bates,
+Dale, \& Thal, 1995; Benedict, 1979; Fenson et al., 1994). These
+differences may reflect the fact that comprehension and production do
+not share the same constraints. For instance, whereas comprehension
+depends on the ease with which words are stored and accessed, production
+depends, additionally, on the ease with which words are articulated,
+e.g., shorter words are produced earlier (Braginsky et al., 2016). By
 investigating comprehension-based vocabularies, we assess the extent to
@@
 Frank, Braginsky, Yurovsky, \& Marchman, 2017), and we studied the
-timeline of word learning using the normative/average age of acquisition
-(i.e., the age at which at least 50\% of children know a given words).
-Our choice of studying the normative learning trajectory rather than the
+timeline of noun learning using the normative age of acquisition (i.e.,
+the age at which at least 50\% of children know a given words). Our
+choice of studying the normative learning trajectory rather than the
 individual trajectories was motivated by the nature of the dataset
@@
 with age of acquisition and shape of the distribution) and we explain
-how these properties infom hypotheses about network growth. Next, we
+how these properties inform hypotheses about network growth. Next, we
 explicitly fit the two hypothesized growth mechanisms to the data. We
@@
 queried. Due to these limitations, we use data from younger children to
-test comprehension and data from older children to test production.
-Following previous studies (Hills et al., 2009; Storkel, 2009), we
-restrict our analysis to the category of
-nouns.\footnote{This choice was also forced by the fact that the great majority of association data produced by adults–and which we used to build semantic networks–were nouns.}.
-Table \ref{tab:stats} gives an overview of the data we used.
+test comprehension and data from older children to test production. In
+addition, following previous studies (Hills et al., 2009; Storkel,
+2009), we restricted our analysis to the category of nouns due to the
+fact that nouns predominate the early expressive and receptive lexicons
+(Bates et al., 1995). Their larger sample size (compared, for example,
+to verbs or adjectives) is more suited to the network-based analysis of
+development. Table \ref{tab:stats} gives an overview of the data we
+used.
 
@@
 \emph{indegree}: the number of links for which the word was the
-target.\footnote{This choice was based the prior work by @hills2009 stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated for indegree.}
+target.\footnote{This choice was based on prior work by Hills et al.
+(2009) stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated with indegree.}
 To model growth from month to month, we constructed a different network
-at each month, based on the words that have been acquired by that month.
+at each month, based on the nouns that have been acquired by that month.
 
@@
 lead to similar networks. Indeed, though this approximation assumes that
-the semantic similarity measure is universal--which is a reasonable
-approximation (e.g., Youn et al., 2016), the set of words acquired by
+the semantic similarity measure is universal---which is a reasonable
+approximation (e.g., Youn et al., 2016)---the set of words acquired by
 children as well as the timeline of this acquisition can still vary from
@@
 transcriptions in each language, using the open source text-to-speech
-software \textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.}
-We used the Levenshtein distance (also known as edit distance) as a
-measure of phonological relatedness between two nodes. The measure
-counts the minimum number of operations (insertions, deletions,
-substitutions) required to change one string into another.
+software \textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}}.
+This software provides the correct IPA transcription if the word is
+found in a spelling-to-phonemes dictionary, otherwise it uses
+language-specific pronunciation rules to generate an approximate
+phonetic transcription. We used the Levenshtein distance (also known as
+edit distance) as a measure of phonological relatedness between two
+nodes. The measure counts the minimum number of operations (insertions,
+deletions, substitutions) required to change one string into another.
 
@@
 However, these studies reported a contribution of phonological
-connectivity to word learning when networks were built using a rich
+connectivity to noun learning when networks were built using a rich
 adult vocabulary. Since the focus of the current study is on the
 mechanism of growth, the networks should be based on children's early
-vocabulary. The latter, however, contains very few word pairs with an
+vocabulary. The latter, however, contains very few noun pairs with an
 edit distance of 1. Thus, we increased the threshold from 1 to 2, that
@@
 In both cases, the results were weaker than those obtained with a threshold of 2.
-We did not consider the case of a threshold larger than 2 since the pairs will become less and less phonologically related.}
+We did not consider the case of a threshold larger than 2 since many pairs become phonologically unrelated.}
 The connectivity of a given node was characterized with its
@@
 same data, we restrict the analysis to the subset of nouns for which we
-had both semantic and phonological information in each language.
+had semantic associates in the free association norms.
 
@@
 This correlation is also necessary to INT, although the causality is
-reversed: higher connectivity in the global network is caused by earlier
+reversed: Higher connectivity in the global network is caused by earlier
 learning, not the other way around. Some words end up being highly
@@
 (or indegree for the semantic networks). For ease of visual comparison,
-the predictor (i.e., the degree) was centered and scaled across
-languages. The plots show, overall, a negative correlation between the
-month of acquisition and the degree. In production data, the average
-correlation across languages was -0.24 (SD=0.10) for the semantic
-networks and -0.30 (SD=0.05) for the phonological networks. In
-comprehension data, the average correlation was -0.21 (SD=0.08) for the
-semantic networks and -0.21 (SD=0.07) for the phonological networks.
-These results indicate that nouns with higher degrees are generally
-learned earlier, thus replicating previous findings in English (e.g.,
-Storkel 2004, 2009; Hills et al. 2009) and extending these findings to
-10 different languages, generally, in both production- and
-comprehension-based vocabularies.
+the predictor (i.e., the degree) was centered and scaled. The plots
+show, overall, a negative correlation between the month of acquisition
+and the degree. In production data, the average correlation across
+languages was -0.24
+(\$SD=\(0.10) for the semantic networks and -0.30 (\)SD=\(0.05) for the phonological networks.
+In comprehension data, the average correlation was -0.21 (\)SD=\(0.08) for the semantic networks and -0.21 (\)SD=\$0.07)
+for the phonological networks. These results indicate that nouns with
+higher degrees are generally learned earlier, thus replicating previous
+findings in English (Hills et al., 2009; Storkel, 2009) and extending
+these findings to 10 different languages, generally, in both production-
+and comprehension-based vocabularies.
 
@@
 languages for both production and comprehension. That said, phonological
-networks had relatively larger cut-offs than semantic networks. As was
-suggested by Arbesman et al. (2010), these \enquote{truncated}
-power-laws in phonological networks may reflect the various constraints
-that exist on word formation in the phonological domain such as the
-number of phonemes in the language, the phonotactics (i.e., the way
-sound sequences are arranged in words), and the length of words. Such
-constraints may limit the number of words that are phonologically
-similar, thus leading to distributions which decay faster than a
-non-truncated power law.
+networks had relatively larger cut-offs than semantic networks. These
+\enquote{truncated} power-laws in phonological networks may be due to
+the constraints that exist on word formation in the phonological domain
+such as the size of the phonemic inventory, phonotactic rules, and word
+length. Such constraints may limit the number of words that are
+phonologically similar, thus leading to distributions which decay faster
+than a non-truncated power law (Arbesman et al., 2010).
 
@@
 Chain Monte Carlo sampling resulted in a posterior distribution over
-\(\beta\), which we summarized in Figure \ref{fig:growthPred}.
-
-First, the results replicate Hills et al.'s original finding regarding
-the semantic network in English and the production-based vocabulary,
-which is that this network grows by EXT, not by INT. Second, our results
-show that, generally speaking, this finding generalizes to
-comprehension-based vocabulary, and holds across languages. This
-generalization was obtained in both the semantic\footnote{One could
-  imagine that the fact of using English free association norms
-  cross-linguistically would decrease the effect of non-English semantic
-  networks because of possible cultural differences. However, our
-  findings do not support this assumption, rather it supports our
-  initial approximation about the universality of the semantic
-  similarity measure. That said, this apprimation is not perfect; for
-  example there is evidence that a small part of the variance in free
-  assication data can be explained by phonological similarity
-  (Kachergis, Cox, \& Jones, 2011; Matusevych \& Stevenson, 2018), thus
-  leading to possibly minor cross-linguistic differences.} and
-phonological domains.
+\(\beta\), which we summarized in Figure \ref{fig:growthPred}. The
+results replicate Hills et al.'s original finding regarding the semantic
+network in English and the production-based vocabulary, which is that
+this network grows by EXT, not by INT. Crucially, our results show that,
+generally speaking, this finding generalizes to comprehension-based
+vocabulary, and holds across languages. This generalization was obtained
+in both the semantic\footnote{One could imagine that the fact of using
+  English free association norms cross-linguistically would decrease the
+  effect of non-English semantic networks because of possible cultural
+  differences. However, our findings do not support this assumption,
+  rather, it supports our initial approximation about the universality
+  of the semantic similarity measure. That said, this approximation is
+  not perfect. For example there is evidence that a small part of the
+  variance in free association data can be explained by phonological
+  similarity (Kachergis, Cox, \& Jones, 2011; Matusevych \& Stevenson,
+  2018), thus leading to possibly minor cross-linguistic differences.}
+and phonological domains.
 
@@
 more direct way to assess and compare the contribution of EXT in
-relation to other word-level factors is through conducting linear
-regressions, where connectivity in the learning environment, frequency
-and length predict the age of acquisition.
+relation to other word-level factors is through conducting regressions,
+where connectivity in the learning environment, frequency and length
+predict the age of acquisition.
 
@@
 Braginsky et al. (2016) where unigram counts were derived based on
-CHILDES corpora in each language (MacWhinney, 2014). For each word,
-counts included words that shared the same stem (e.g., \enquote{cats}
-counts as \enquote{cat}), or words that were synonymous (e.g.
-\enquote{father} counts as \enquote{daddy}). Although these frequency
-counts use transcripts from independent sets of children, they are based
-on large samples, and this allows us to average out possible differences
-between children and the specificities of their input (see J. C. Goodman
-et al., 2008 for a similar research strategy).
+CHILDES corpora in each language (MacWhinney, 2014). Although these
+frequency counts use transcripts from independent sets of children, they
+are based on large samples, and this allows us to average out possible
+differences between children and the specificities of their input (see
+J. C. Goodman et al., 2008 for a similar research strategy).
 
@@
 al., under review). Thus, word length seems to reflect the effects of
-production's constraints rather than than comprehension's constraints,
-i.e., longer words are harder to articulate but they may not be
-significantly more difficult to store and access.
+production's constraints rather than comprehension's constraints, i.e.,
+longer words are harder to articulate but they may not be significantly
+more difficult to store and access.
 
@@
 data beyond that explained by phonological connectivity, frequency and
-length. This contrasts with the original finding in Hills et al. (2009).
-However, this might be due to our using a slightly different model
-(which included word length as a covariate) and a larger dataset. That
-said, and despite these apparent cross-linguistic differences, both
-phonological and semantic connectivity are significant predictors in the
-combined model (Figure \ref{fig:staticAll}).
+length. This finding contrasts with the original finding in Hills et al.
+(2009). However, this difference might be due to our using a slightly
+different model (which included word length as a covariate) and a larger
+dataset. That said, and despite these apparent cross-linguistic
+differences, both phonological and semantic connectivity are significant
+predictors in the combined model (Figure \ref{fig:staticAll}).
 
@@
 past knowledge is organized. The present study tested the generality of
-previous findings (Hills et al., 2010, 2009) by 1) investigating
-phonological networks together with semantic networks, 2) testing both
-comprehension- and production-based vocabularies, and 3) comparing the
-results across 10 languages.
+previous findings by 1) investigating phonological networks together
+with semantic networks, 2) testing both comprehension- and
+production-based vocabularies, and 3) comparing the results across 10
+languages.
 
@@
 For example, in the semantic domain, growth according to EXT can be
-explained by a mechanism similar to cross-situational learning (Pinker,
-2013; Smith \& Yu, 2008; Yurovsky \& Frank, 2015). According to this
-mechanism, children track the co-occurrence of concrete nouns with their
-possible semantic referents. The referent of a word heard in only one
-naming situation can be ambiguous (e.g., when the word \enquote{ball} is
-heard for the first time in the presence of both a ball and a chair),
-but hearing the same word in a diversity of semantic contexts allows the
-learner to narrow down the set of possible word-object mappings. In our
-case, free association (used to determine semantic network connectivity)
-is related to contextual co-occurrence (Fourtassi \& Dupoux, 2013;
-Griffiths, Steyvers, \& Tenenbaum, 2007), meaning that highly connected
-words will tend to occur in a variety of speech and referential
-contexts. This fact makes such words easier to learn because they have
-more referential disambiguating cues across learning contexts.
-Crucially, children can learn these words without necessarily knowing
-the meaning of all other words with witch they co-occur (hence the
-similarity with EXT). This possibility is supported by the finding that
-words' diversity of occurrence in child directed speech predicts their
-age of learning (Hills et al., 2010).
+explained by a mechanism similar to cross-situational learning (McMurray
+et al., 2012; Smith \& Yu, 2008; Yurovsky \& Frank, 2015). According to
+this mechanism, children track the co-occurrence of concrete nouns with
+their possible semantic referents. The referent of a word heard in only
+one naming situation can be ambiguous (e.g., when the word
+\enquote{ball} is heard for the first time in the presence of both a
+ball and a chair), but hearing the same word in a diversity of semantic
+contexts allows the learner to narrow down the set of possible
+word-object mappings. In our case, free association (used to determine
+semantic network connectivity) is related to contextual co-occurrence
+(Fourtassi \& Dupoux, 2013; Griffiths, Steyvers, \& Tenenbaum, 2007),
+meaning that highly connected words will tend to occur in a variety of
+speech and referential contexts. This fact makes such words easier to
+learn because they have more referential disambiguating cues across
+learning contexts. Crucially, children can learn these words without
+necessarily knowing the meaning of all other words with witch they
+co-occur (hence the similarity with EXT). This possibility is supported
+by the finding that words' diversity of occurrence in child directed
+speech predicts their age of learning (Hills et al., 2010; Stella et
+al., 2017).
 
 In the phonological case, network growth according to EXT is also
-compatible with a scenario whereby children are tracking lwo level
+compatible with a scenario whereby children are tracking low level
 statistical patterns, e.g., high probability sound sequences. Indeed,
@@
 is supported by computational simulations that show how learning general
-phonotactics patterns create ``well-worn paths'' which allow the models
-to represent several distinct but phonologically neighboring words
-(Dell, Juliano, \& Govindjee, 1993; Takac, Knott, \& Stokes, 2017).
+phonotactics patterns create \enquote{well-worn paths} which allow the
+models to represent several distinct but phonologically neighboring
+words (Dell, Juliano, \& Govindjee, 1993; Takac, Knott, \& Stokes,
+2017).
 
@@
 which children's uptake is influenced by this input (Clark, 2007; Hoff
-\& Naigles, 2002).
+\& Naigles, 2002; Huttenlocher et al., 1991).
 
@@
 children at different ages (due to the fact that available CDI data is
-mainly cross-sectional). Although this measure has proven highly
-consistent (Fenson et al., 1994), it led us to focus on studying the
-learning mechanism of the \enquote{average} child. Individual
-trajectories, however, could lead to different netwtok strcutures and
-show different learning patterns. For example, using longitudinal data
-Beckage, Smith, and Hills (2011) found differences between typical and
-late talkers in terms of the semantic network structure. Besides,
-although our study endorses the externally-driven account of network
-growth, this does not mean individual children never use some variant of
-INT or some combination of both INT and EXT (Beckage and Colunga, under
-review). For example, some children develop \enquote{islands of
-expertise}, that is, well organized knowledge about a certain topic
-(e.g., birds or dinosaurs). This prior knowledge enables these children
-to learn new related words more easily (e.g., Chi \& Koeske, 1983).
+mainly cross-sectional). Such a measure has been shown to be valid and
+reliable (Fenson et al., 1994), and has allowed researchers to study
+important aspects of word learning (Braginsky et al., 2016 ; J. C.
+Goodman et al., 2008; Hills et al., 2009; Stella et al., 2017; Storkel,
+2009). In our case, the use of cost-effective cross-sectional data has
+allowed us to leverage large-scale studies across several languages.
+That said, it is important to remember that this type of data can only
+inform us about the learning trajectory of the \enquote{average} child.
+Although our study endorses, overall, the externally-driven account of
+network growth, this does not mean individual children never use some
+variant of INT or some combination of both INT and EXT (Beckage and
+Colunga, under review). To illustrate, some children develop
+\enquote{islands of expertise}, that is, well organized knowledge about
+a certain topic (e.g., birds or dinosaurs). This prior knowledge enables
+these children to learn new related words more easily (e.g., Chi \&
+Koeske, 1983).
 
@@
 Bates, E., \& MacWhinney, B. (1987). Competition, variation, and
-language learning. \emph{Mechanisms of Language Acquisition}, 157--193.
+language learning. In B. MacWhinney (Ed.), \emph{Mechanisms of language
+acquisition}. Erlbaum.
+
+\hypertarget{ref-bates1995}{}
+Bates, E., Dale, P. S., \& Thal, D. (1995). Individual differences and
+their implications for theories of language development. In P. Fletcher
+\& B. MacWhinney (Eds.), \emph{The handbook of child language}. Oxford,
+England: Blackwell.
 
@@
 
-\hypertarget{ref-beckage2011}{}
-Beckage, N. M., Smith, L., \& Hills, T. T. (2011). Small worlds and
-semantic network growth in typical and late talkers. \emph{PLOS ONE},
-\emph{6}(5), 1--6.
-
 \hypertarget{ref-benedict1979}{}
@@
 explore the phonological network in child-directed speech: A survival
-analysis of children?s first word productions. \emph{Journal of Memory
+analysis of children's first word productions. \emph{Journal of Memory
 and Language}, \emph{75}, 159--180.
@@
 \hypertarget{ref-macwhinney2014}{}
-MacWhinney, B. (2014). \emph{The childes project: Tools for analyzing
-talk, volume ii: The database}. Psychology Press.
+MacWhinney, B. (2014). \emph{The CHILDES project: Tools for analyzing
+talk, volume ii}. Psychology Press.
 
@@
 
-\hypertarget{ref-pinker2013}{}
-Pinker, S. (2013). \emph{Learnability and cognition: The acquisition of
-argument structure}. MIT press.
-
 \hypertarget{ref-pisoni1985}{}

### 2019-02-06 journal/ms.Rmd
second version journal

@@
 ---
-title             : "Noun Learning as Network Growth: A Cross-linguistic Analysis"
-shorttitle        : "Noun Learning as Network Growth"
+title             : "The growth of children’s semantic and phonological networks: insight from 10 languages"
+shorttitle        : "Lexical Development as Network Growth"
 #numbersections: true
@@
 Below we analyze properties of this global networks that may a priori hint at an INT- or EXT-like growth.
-In order to compare various predictors on the same data, we restrict the analysis to the subset of nouns for which we had semantic associates in the free association norms.
 

### 2019-02-06 journal/ms.tex
second version journal

@@
             pdfauthor={},
-            pdftitle={Noun Learning as Network Growth: A Cross-linguistic Analysis},
+            pdftitle={The growth of children's semantic and phonological networks: insight from 10 languages},
             colorlinks=true,
@@
 % Essential manuscript parts
-  \title{Noun Learning as Network Growth: A Cross-linguistic Analysis}
-
-  \shorttitle{Noun Learning as Network Growth}
+  \title{The growth of children's semantic and phonological networks: insight
+from 10 languages}
+
+  \shorttitle{Lexical Development as Network Growth}
 
@@
 analyze properties of this global networks that may a priori hint at an
-INT- or EXT-like growth. In order to compare various predictors on the
-same data, we restrict the analysis to the subset of nouns for which we
-had semantic associates in the free association norms.
+INT- or EXT-like growth.
 

### 2019-02-06 journal/ms.Rmd
second version journal

@@
 Finally, we use developmental data in 10 languages.
-Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains [@youn2016; @arbesman2010].
+Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains [@youn2016; @arbesman2010;@lupyan2017].
 Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the way in which the children's networks grow.
@@
 The plots show, overall, a negative correlation between the month of acquisition and the degree.
-In production data, the average correlation across languages was `r ps_ave` ($SD=$`r ps_sd`) for the semantic networks and `r pp_ave` ($SD=$`r pp_sd`) for the phonological networks.
-In comprehension data, the average correlation was `r cs_ave` ($SD=$`r cs_sd`) for the semantic networks and `r cp_ave` ($SD=$`r cp_sd`) for the phonological networks.
+In production data, the average correlation across languages was `r ps_ave` ($SD=$ `r ps_sd`) for the semantic networks and `r pp_ave` ($SD=$ `r pp_sd`) for the phonological networks.
+In comprehension data, the average correlation was `r cs_ave` ($SD=$ `r cs_sd`) for the semantic networks and `r cp_ave` ($SD=$ `r cp_sd`) for the phonological networks.
 These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English [@storkel2009; @hills2009] and extending these findings to 10 different languages, generally, in both production- and comprehension-based vocabularies.

### 2019-02-06 journal/ms.tex
second version journal

@@
 show more or less cross-linguistic variability along both the semantic
-and phonological domains (Arbesman, Strogatz, \& Vitevitch, 2010; Youn
-et al., 2016). Besides, cultures might differ in the way caregivers talk
-to children (Cristia, Dupoux, Gurven, \& Stieglitz, 2017; Kuhl et al.,
-1997), and this difference in the input could influence the way in which
-the children's networks grow. Thus, cross-linguistic comparison is
-crucial to test what growth mechanism is cognitively universal and is
-used by all children, and what mechanism is specific to some patterns of
-learning that emerge due to the particulars of a given language or
-culture (Bates \& MacWhinney, 1987; Slobin, 2014).
+and phonological domains (Arbesman, Strogatz, \& Vitevitch, 2010; Lupyan
+\& Lewis, 2017; Youn et al., 2016). Besides, cultures might differ in
+the way caregivers talk to children (Cristia, Dupoux, Gurven, \&
+Stieglitz, 2017; Kuhl et al., 1997), and this difference in the input
+could influence the way in which the children's networks grow. Thus,
+cross-linguistic comparison is crucial to test what growth mechanism is
+cognitively universal and is used by all children, and what mechanism is
+specific to some patterns of learning that emerge due to the particulars
+of a given language or culture (Bates \& MacWhinney, 1987; Slobin,
+2014).
 
@@
 and the degree. In production data, the average correlation across
-languages was -0.24
-(\$SD=\(0.10) for the semantic networks and -0.30 (\)SD=\(0.05) for the phonological networks.
-In comprehension data, the average correlation was -0.21 (\)SD=\(0.08) for the semantic networks and -0.21 (\)SD=\$0.07)
-for the phonological networks. These results indicate that nouns with
-higher degrees are generally learned earlier, thus replicating previous
-findings in English (Hills et al., 2009; Storkel, 2009) and extending
-these findings to 10 different languages, generally, in both production-
-and comprehension-based vocabularies.
+languages was -0.24 (\(SD=\) 0.10) for the semantic networks and -0.30
+(\(SD=\) 0.05) for the phonological networks. In comprehension data, the
+average correlation was -0.21 (\(SD=\) 0.08) for the semantic networks
+and -0.21 (\(SD=\) 0.07) for the phonological networks. These results
+indicate that nouns with higher degrees are generally learned earlier,
+thus replicating previous findings in English (Hills et al., 2009;
+Storkel, 2009) and extending these findings to 10 different languages,
+generally, in both production- and comprehension-based vocabularies.
 
@@
 
+\hypertarget{ref-lupyan2017}{}
+Lupyan, G., \& Lewis, M. (2017). From words-as-mappings to
+words-as-cues: The role of language in semantic knowledge.
+\emph{Language, Cognition and Neuroscience}.
+
 \hypertarget{ref-macwhinney2014}{}
 MacWhinney, B. (2014). \emph{The CHILDES project: Tools for analyzing
-talk, volume ii}. Psychology Press.
+talk, Volume II}. Psychology Press.
 

### 2019-02-12 journal/ms.Rmd
final version

@@
  Children tend to produce words earlier when they are connected to a variety of other words along the phonological and semantic dimensions.
-Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.
-One view suggests that learning is primarily predicted by a network growth model where highly connected words in the child's early lexicon enable learning of similar words.
-Another view suggests that learning is driven by highly connected words in the external learning environment, instead of highly connected words in the early internal lexicon.
+Though these semantic and phonological connectivity effects have been extensively documented, little is known about their underlying developmental mechanism.
+One possibility is that learning is driven by lexical network growth where highly connected words in the child's early lexicon enable learning of similar words.
+Another possibility is that learning is driven by highly connected words in the external learning environment, instead of highly connected words in the early internal lexicon.
 The present study tests both scenarios systematically in both the phonological and semantic domains across 10 languages.
-We show that external connectivity in the learning environment drives growth in both production- and comprehension-based vocabularies, even controlling for word frequency and length.
-This pattern of findings suggests a word learning mechanism where children harness their statistical learning abilities to detect and learn highly connected words in the learning environment.
+We show that phonological and semantic connectivity in the learning environment drives growth in both production- and comprehension-based vocabularies, even controlling for word frequency and length.
+This pattern of findings suggests a word learning process where children harness their statistical learning abilities to detect and learn highly connected words in the learning environment.
 
@@
 For example, @goodman2008 found that, within a lexical category (e.g., nouns), higher parental frequency is associated with earlier learning.
-Researchers have studied the role of several other factors such as word length and the mean length of utterances in which the word occurs [e.g., @braginsky2016; @swingley2018].
+Researchers have studied the role of several other factors such as word length and the mean length of utterances in which the word occurs [e.g., @braginsky; @swingley2018].
 
-Besides word-level properties, the structure of the lexicon (that is, how words relate to one another) was also found to predict the Age of Acquisition (AoA) of words.
+Besides word-level properties, the structure of the lexicon (that is, how words relate to one another) is also linked to the the Age of Acquisition (AoA) of words.
 The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words [e.g., @collins1975; @luce1998].
 Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features [@mcrae2005], target-cue relationships in free association norms [@nelson1998], co-occurrence in child directed speech [@macwhinney2014], and phonological relatedness [@vitevitch2008].
-These studies have generally found that children tend to produce nouns that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @stella2017; @carlson2014].
+These studies have generally found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @stella2017; @carlson2014].
 
@@
 For EXT, the utility of a candidate node is its degree in the entire network.
-According to EXT, node 2 is more likely to enter the lexicon next.", fig.align = "center", out.width = "300px"}
+According to EXT, node 2 is more likely to enter the lexicon next.
+This figure is based on an example from Hills et al (2009).", fig.align = "center", out.width = "300px"}
 knitr::include_graphics("figs/growth3.png")
@@
 However, EXT is the externally-driven scenario that best predicted the data in this previous work.} This is an important finding because it suggests that learning in the early stages is mostly driven by properties of the external input, regardless of how past knowledge is organized.
-However, this work has been done in the special case of networks that are based on 1) semantic associations, 2) production-based vocabularies, and 3) data from English-learning children, only.
+However, this work explored the INT/EXT growth in a special case: networks that were based on 1) semantic associations, 2) production-based vocabularies, and 3) data from English-learning children, only.
 The extent to which this result depends on the domain (e.g., semantic vs.
 phonological connectivity), the vocabulary measure (production vs.
-comprehension) and culture/language is still unclear.
-In this work, we test the generality of the finding along these three dimensions.
+comprehension) and culture/language is thus an open area for investigation [@hills2018].
+In this work, we test the generality of prior findings along these three dimensions.
 
@@
 Does the phonological network also predict word learning?
-Previous work did find an effect of nouns' connectivity in the phonological network on their age of learning [@storkel2009; @stella2017; @carlson2014].
-In other words, nouns learned earlier in life tend to sound similar to many other nouns than a word learned later in life.
+Previous work has found an effect of words' connectivity in the phonological network on their age of learning [@storkel2009; @stella2017; @carlson2014].
+In other words, words learned earlier in life tend to sound similar to many other words than a word learned later in life.
 However, this finding is *a priori* compatible with both INT and EXT, and previous studies did not explicitly compare these two mechanisms.
@@
 These differences may reflect the fact that comprehension and production do not share the same constraints.
-For instance, whereas comprehension depends on the ease with which words are stored and accessed, production depends, additionally, on the ease with which words are articulated, e.g., shorter words are produced earlier [@braginsky2016].
+For instance, whereas comprehension depends on the ease with which words are stored and accessed, production depends, additionally, on the ease with which words are articulated, e.g., shorter words are produced earlier [@braginsky].
 By investigating comprehension-based vocabularies, we assess the extent to which the network growth mechanism captures general learning patterns beyond the specific constraints of production.
@@
 Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the way in which the children's networks grow.
-Thus, cross-linguistic comparison is crucial to test what growth mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014].
+Thus, cross-linguistic comparison is crucial to test the extent to which growth mechanisms are equally engaged across a wider variety of cultures compared with the extent to which the growth mechanisms are specific to patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014].
  <!--
@@
 We adopted the following research strategy.
-We used a cross-linguistic dataset of children's vocabulary development [@frank2017; @fenson94], and we studied the timeline of noun learning using the normative age of acquisition (i.e., the age at which at least 50% of children know a given words).
+We used parent reports on the MacArthur-Bates Communicative Development Inventory and its cross-linguistic adaptations [@frank2017; @fenson94].
+We studied the timeline of word learning using the normative age of acquisition (i.e., the age at which at least 50% of children know a given words).
 Our choice of studying the normative learning trajectory rather than the individual trajectories was motivated by the nature of the dataset used---which is primarily based on cross-sectional studies.
 Children may vary in their individual learning trajectories, but the aggregate data provide highly robust measures of the average learning patterns [@fenson94].
-The use of such measures has lead to important insights on the mechanisms of word learning [@storkel2009; @stella2017; @hills2009; @hills2010; @goodman2008; @braginsky2016].
+The use of such measures has lead to important insights on the mechanisms of word learning [@storkel2009; @stella2017; @hills2009; @hills2010; @goodman2008].
 
@@
 Second, we analyze static properties of words' connectivity in these networks (correlation with age of acquisition and shape of the distribution) and we explain how these properties inform hypotheses about network growth.
-Next, we explicitly fit the two hypothesized growth mechanisms to the data.
+Next, we fit the two hypothesized growth mechanisms to the data.
 We investigate the extent to which the results obtained in @hills2009 generalize to phonological networks and comprehension-based vocabularies, and whether this generalization holds cross-linguistically.
@@
 Then we fit a logistic curve to these proportions and determined when the curve crosses 0.5, i.e., the age at which at least 50% of children know the word.
-We take this point in time to be each word’s age of acquisition [@goodman2008; @braginsky2016].
+We take this point in time to be each word’s age of acquisition [@goodman2008; @braginsky].
 <!--We obtained these nouns in ten languages: Croatian, Danish, English, French, Italian, Norwegian, Russian, Spanish, Swedish, and Turkish.
@@
       caption = "Statistics for the dataset we used.",
-      col.names = c("Language",  "Nouns", "Ages", "Nouns", "Ages")) %>%
-  add_header_above(c("", "Comprehension" = 2, "Production" = 2)) %>%
+      col.names = c("Language",  "Nouns", "Ages", "N", "Nouns", "Ages","N")) %>%
+  add_header_above(c("", "Comprehension" = 3, "Production" = 3)) %>%
   column_spec(1, bold = TRUE) %>%
@@
 Since the free association norms are available only in English, we used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across 10 languages.
-Using the same association data across languages does not necessarily lead to similar networks.
-Indeed, though this approximation assumes that the semantic similarity measure is universal---which is a reasonable approximation [e.g., @youn2016]---the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possibility different learning strategies.
+Semantic associations are not necessarily shared across languages, but we use this technique as a reasonable first approximation.
+In support of this approximation, @youn2016 showed that semantic networks across languages share substantial similarities.
+Furthermore, using the same association data across languages does not necessarily mean that the resulting networks will grow in a similar fashion.
+For instance, the set of words acquired by children as well as the order of word acquisition can vary from language to language leading to possibility different learning strategies.
 
@@
 In both cases, the results were weaker than those obtained with a threshold of 2.
-We did not consider the case of a threshold larger than 2 since many pairs become phonologically unrelated.} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
+We did not consider the case of a threshold larger than 2 since many short pairs appear phonologically unrelated when the edit distance is 3 or more (e.g., "cat"/"dog").} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
 
@@
 Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment.
-Below we analyze properties of this global networks that may a priori hint at an INT- or EXT-like growth.
+Below we analyze properties of these global networks that may a priori hint at an INT- or EXT-like growth.
 
@@
 
-```{r corrProd, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Age of production in the global network as predicted by the degree (i.e., connectivity) in this network.
+```{r corrProd, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network.
 Results are shown in each language for phonological and semantic networks.
@@
 
-```{r corrComp, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Age of comprehension in the global network as predicted by the degree (i.e., connectivity) in this network.
+```{r corrComp, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Comprehension data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network.
 Results are shown in each language for phonological and semantic networks.
@@
 
-Figures \@ref(fig:corrProd) and \@ref(fig:corrComp) show how the age of production and comprehension, respectively, correlates with the degree (or indegree for the semantic networks).
+Figures \@ref(fig:corrProd) and \@ref(fig:corrComp) show how the age of acquisition in production and comprehension, respectively, correlates with the degree (or indegree for the semantic networks).
 For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled.
@@
 The inference was performed using the probabilistic programming language  WebPPL [@dippl].
-We defined a uniform prior over $\beta$, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using formula 1).
+We defined a uniform prior over $\beta$, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using Formula 1).
 Markov Chain Monte Carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \@ref(fig:growthPred).
@@
 This generalization was obtained in both the semantic^[One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
-However, our findings do not support this assumption, rather, it supports our initial approximation about the universality of the semantic similarity measure.
+However, our findings do not support this assumption, rather, it supports our initial approximation about the shared nature of the semantic similarity measure.
 That said, this approximation is not perfect.
@@
 Above we showed that the way semantic and phonological information is structured in the learning environment contributes to noun learning (via EXT) across languages.
-However, we know that other factors influence learning as well [e.g., @braginsky2016].
+However, we know that other factors influence learning as well [e.g., @braginsky].
 Next we investigated how semantic and phonological connectivity interact with two other factors.
@@
 For word length, we counted the number of phonemes in our generated IPA transcription.
-For word frequency, we used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language [@macwhinney2014].
+For word frequency, we used the frequency estimates from @braginsky where unigram counts were derived based on CHILDES corpora in each language [@macwhinney2014].
 Although these frequency counts use transcripts from independent sets of children, they are based on large samples, and this allows us to average out possible differences between children and the specificities of their input [see @goodman2008 for a similar research strategy].
@@
 The findings for the new predictors were as follows.
-Overall, frequency is the largest and most consistent predictor of age of acquisition in both comprehension and production data and across languages, endorsing results for nouns across a variety of analyses [@goodman2008; @braginsky2016; @roy2015].
-Word length is more predictive for production than comprehension (and this difference is very clear in the global model), replicating previous work (Braginsky et al., under review).
+Overall, frequency is the largest and most consistent predictor of age of acquisition in both comprehension and production data and across languages, endorsing results for nouns across a variety of analyses [@goodman2008; @braginsky; @roy2015].
+Word length is more predictive for production than comprehension (and this difference is very clear in the global model), replicating previous work [@braginsky].
 Thus, word length seems to reflect the effects of production's constraints rather than comprehension's constraints, i.e., longer words are harder to articulate but they may not be significantly more difficult to store and access.
@@
 Finally, the findings were, overall, similar across the 10 languages we tested.
-Although we find some cross-linguistic variation when semantic and phonological networks were pitted against frequency and length, this variability is to be taken with a grain of salt as it might be exaggerated in our study by the limited and partially-overlapping sample of nouns for each language.
+Although we find some cross-linguistic variation when semantic and phonological networks were pitted against frequency and length, this variability is to be taken with a grain of salt as it might be exaggerated in our study by several factors such as the limited and partially-overlapping set of nouns for each language, measurement error due to the sample of acquisition data, the sample of frequency data, and the translation of association norms.
 In fact, both phonological and semantic connectivity are significant predictors above and beyond frequency and length when data are pooled across languages.
@@
 
-For example, in the semantic domain, growth according to EXT can be explained by a mechanism similar to cross-situational learning [@smith2008; @mcmurray2012; @yurovsky2015].
+For example, in the semantic domain, growth according to EXT could be explained by a mechanism similar to cross-situational learning [@smith2008; @mcmurray2012; @yurovsky2015].
 According to this mechanism, children track the co-occurrence of concrete nouns with their possible semantic referents.
@@
 This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts.
-Crucially, children can learn these words without necessarily knowing the meaning of all other words with witch they co-occur (hence the similarity with EXT).
+Crucially, children can learn these words without necessarily knowing the meaning of all other words with which they co-occur (hence the similarity with EXT).
 This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@stella2017; @hills2010].
@@
 Chief among these limitations is the fact that the age of word acquisition is computed using different children at different ages (due to the fact that available CDI data is mainly cross-sectional).
-Such a measure has been shown to be valid and reliable [@fenson94], and has allowed researchers to study important aspects of word learning [@hills2009; @stella2017; @storkel2009; @goodman2008; @braginsky2016 ].
+Such a measure has been shown to be valid and reliable [@fenson94], and has allowed researchers to study important aspects of word learning [@hills2009; @stella2017; @storkel2009; @goodman2008; @braginsky].
 In our case, the use of cost-effective cross-sectional data has allowed us to leverage large-scale studies across several languages.
 That said, it is important to remember that this type of data can only inform us about the learning trajectory of the "average" child.
-Although our study endorses, overall, the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT (Beckage and Colunga, under review).
+Although our study endorses, overall, the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT [@beckage].
 To illustrate, some children develop "islands of expertise", that is, well organized knowledge about a certain topic (e.g., birds or dinosaurs).

### 2019-02-12 journal/ms.tex
final version

@@
 variety of other words along the phonological and semantic dimensions.
-Though this connectivity effect has been extensively documented, little
-is known about the underlying developmental mechanism. One view suggests
-that learning is primarily predicted by a network growth model where
-highly connected words in the child's early lexicon enable learning of
-similar words. Another view suggests that learning is driven by highly
-connected words in the external learning environment, instead of highly
-connected words in the early internal lexicon. The present study tests
-both scenarios systematically in both the phonological and semantic
-domains across 10 languages. We show that external connectivity in the
-learning environment drives growth in both production- and
-comprehension-based vocabularies, even controlling for word frequency
-and length. This pattern of findings suggests a word learning mechanism
-where children harness their statistical learning abilities to detect
-and learn highly connected words in the learning environment.}
+Though these semantic and phonological connectivity effects have been
+extensively documented, little is known about their underlying
+developmental mechanism. One possibility is that learning is driven by
+lexical network growth where highly connected words in the child's early
+lexicon enable learning of similar words. Another possibility is that
+learning is driven by highly connected words in the external learning
+environment, instead of highly connected words in the early internal
+lexicon. The present study tests both scenarios systematically in both
+the phonological and semantic domains across 10 languages. We show that
+phonological and semantic connectivity in the learning environment
+drives growth in both production- and comprehension-based vocabularies,
+even controlling for word frequency and length. This pattern of findings
+suggests a word learning process where children harness their
+statistical learning abilities to detect and learn highly connected
+words in the learning environment.}
   \keywords{Word learning; semantic network; phonological network; network growth;
@@
 mean length of utterances in which the word occurs (e.g., Braginsky,
-Yurovsky, Marchman, \& Frank, 2016; Swingley \& Humphrey, 2018).
+Yurovsky, Marchman, \& Frank, in revision; Swingley \& Humphrey, 2018).
 
 Besides word-level properties, the structure of the lexicon (that is,
-how words relate to one another) was also found to predict the Age of
+how words relate to one another) is also linked to the the Age of
 Acquisition (AoA) of words. The lexical structure can be characterized
@@
 (Vitevitch, 2008). These studies have generally found that children tend
-to produce nouns that have higher neighborhood density (i.e., high
+to produce words that have higher neighborhood density (i.e., high
 connectivity in the network) earlier, both at the phonological and the
@@
 For EXT, the utility of a candidate node is its degree in the entire network.
-According to EXT, node 2 is more likely to enter the lexicon next.}\label{fig:growth}
+According to EXT, node 2 is more likely to enter the lexicon next.
+This figure is based on an example from Hills et al (2009).}\label{fig:growth}
 \end{figure}
@@
 early stages is mostly driven by properties of the external input,
-regardless of how past knowledge is organized. However, this work has
-been done in the special case of networks that are based on 1) semantic
-associations, 2) production-based vocabularies, and 3) data from
-English-learning children, only. The extent to which this result depends
-on the domain (e.g., semantic vs.~phonological connectivity), the
-vocabulary measure (production vs.~comprehension) and culture/language
-is still unclear. In this work, we test the generality of the finding
-along these three dimensions.
+regardless of how past knowledge is organized. However, this work
+explored the INT/EXT growth in a special case: networks that were based
+on 1) semantic associations, 2) production-based vocabularies, and 3)
+data from English-learning children, only. The extent to which this
+result depends on the domain (e.g., semantic vs.~phonological
+connectivity), the vocabulary measure (production vs.~comprehension) and
+culture/language is thus an open area for investigation (Hills \& Siew,
+2018). In this work, we test the generality of prior findings along
+these three dimensions.
 
@@
 versa. Does the phonological network also predict word learning?
-Previous work did find an effect of nouns' connectivity in the
+Previous work has found an effect of words' connectivity in the
 phonological network on their age of learning (Carlson et al., 2014;
-Stella et al., 2017; Storkel, 2009). In other words, nouns learned
-earlier in life tend to sound similar to many other nouns than a word
+Stella et al., 2017; Storkel, 2009). In other words, words learned
+earlier in life tend to sound similar to many other words than a word
 learned later in life. However, this finding is \emph{a priori}
@@
 depends, additionally, on the ease with which words are articulated,
-e.g., shorter words are produced earlier (Braginsky et al., 2016). By
-investigating comprehension-based vocabularies, we assess the extent to
-which the network growth mechanism captures general learning patterns
-beyond the specific constraints of production.
+e.g., shorter words are produced earlier (Braginsky et al., in
+revision). By investigating comprehension-based vocabularies, we assess
+the extent to which the network growth mechanism captures general
+learning patterns beyond the specific constraints of production.
 
@@
 could influence the way in which the children's networks grow. Thus,
-cross-linguistic comparison is crucial to test what growth mechanism is
-cognitively universal and is used by all children, and what mechanism is
-specific to some patterns of learning that emerge due to the particulars
-of a given language or culture (Bates \& MacWhinney, 1987; Slobin,
-2014).
-
-We adopted the following research strategy. We used a cross-linguistic
-dataset of children's vocabulary development (Fenson et al., 1994;
-Frank, Braginsky, Yurovsky, \& Marchman, 2017), and we studied the
-timeline of noun learning using the normative age of acquisition (i.e.,
-the age at which at least 50\% of children know a given words). Our
-choice of studying the normative learning trajectory rather than the
-individual trajectories was motivated by the nature of the dataset
-used---which is primarily based on cross-sectional studies. Children may
-vary in their individual learning trajectories, but the aggregate data
-provide highly robust measures of the average learning patterns (Fenson
-et al., 1994). The use of such measures has lead to important insights
-on the mechanisms of word learning (Braginsky et al., 2016; J. C.
-Goodman et al., 2008; Hills et al., 2010, 2009; Stella et al., 2017;
-Storkel, 2009).
+cross-linguistic comparison is crucial to test the extent to which
+growth mechanisms are equally engaged across a wider variety of cultures
+compared with the extent to which the growth mechanisms are specific to
+patterns of learning that emerge due to the particulars of a given
+language or culture (Bates \& MacWhinney, 1987; Slobin, 2014).
+
+We adopted the following research strategy. We used parent reports on
+the MacArthur-Bates Communicative Development Inventory and its
+cross-linguistic adaptations (Fenson et al., 1994; Frank, Braginsky,
+Yurovsky, \& Marchman, 2017). We studied the timeline of word learning
+using the normative age of acquisition (i.e., the age at which at least
+50\% of children know a given words). Our choice of studying the
+normative learning trajectory rather than the individual trajectories
+was motivated by the nature of the dataset used---which is primarily
+based on cross-sectional studies. Children may vary in their individual
+learning trajectories, but the aggregate data provide highly robust
+measures of the average learning patterns (Fenson et al., 1994). The use
+of such measures has lead to important insights on the mechanisms of
+word learning (J. C. Goodman et al., 2008; Hills et al., 2010, 2009;
+Stella et al., 2017; Storkel, 2009).
 
@@
 how these properties inform hypotheses about network growth. Next, we
-explicitly fit the two hypothesized growth mechanisms to the data. We
-investigate the extent to which the results obtained in Hills et al.
-(2009) generalize to phonological networks and comprehension-based
+fit the two hypothesized growth mechanisms to the data. We investigate
+the extent to which the results obtained in Hills et al. (2009)
+generalize to phonological networks and comprehension-based
 vocabularies, and whether this generalization holds
@@
 this point in time to be each word's age of acquisition (Braginsky et
-al., 2016; J. C. Goodman et al., 2008).
+al., in revision; J. C. Goodman et al., 2008).
 
@@
 \centering
-\begin{tabular}[t]{>{\bfseries}lrlrl}
+\begin{tabular}[t]{>{\bfseries}lrlrrlr}
 \toprule
-\multicolumn{1}{c}{} & \multicolumn{2}{c}{Comprehension} & \multicolumn{2}{c}{Production} \\
-\cmidrule(l{2pt}r{2pt}){2-3} \cmidrule(l{2pt}r{2pt}){4-5}
-Language & Nouns & Ages & Nouns & Ages\\
+\multicolumn{1}{c}{} & \multicolumn{3}{c}{Comprehension} & \multicolumn{3}{c}{Production} \\
+\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
+Language & Nouns & Ages & N & Nouns & Ages & N\\
 \midrule
-Croatian & 209 & 8-16 & 312 & 16-30\\
-Danish & 200 & 8-20 & 316 & 16-36\\
-English & 209 & 8-18 & 312 & 16-30\\
-French & 197 & 8-16 & 307 & 16-30\\
-Italian & 209 & 7-24 & 312 & 18-36\\
-Norwegian & 193 & 8-20 & 316 & 16-36\\
-Russian & 207 & 8-18 & 314 & 18-36\\
-Spanish & 208 & 8-18 & 312 & 16-30\\
-Swedish & 205 & 8-16 & 339 & 16-28\\
-Turkish & 180 & 8-16 & 297 & 16-36\\
+Croatian & 209 & 8-16 & 250 & 312 & 16-30 & 377\\
+Danish & 200 & 8-20 & 2,398 & 316 & 16-36 & 3,714\\
+English & 209 & 8-18 & 2,435 & 312 & 16-30 & 5,520\\
+French & 197 & 8-16 & 537 & 307 & 16-30 & 827\\
+Italian & 209 & 7-24 & 648 & 312 & 18-36 & 752\\
+Norwegian & 193 & 8-20 & 2,922 & 316 & 16-36 & 9,303\\
+Russian & 207 & 8-18 & 768 & 314 & 18-36 & 1,037\\
+Spanish & 208 & 8-18 & 788 & 312 & 16-30 & 1,146\\
+Swedish & 205 & 8-16 & 467 & 339 & 16-28 & 900\\
+Turkish & 180 & 8-16 & 1,115 & 297 & 16-36 & 2,422\\
 \bottomrule
@@
 allowed us to use the English association norms across 10 languages.
-Using the same association data across languages does not necessarily
-lead to similar networks. Indeed, though this approximation assumes that
-the semantic similarity measure is universal---which is a reasonable
-approximation (e.g., Youn et al., 2016)---the set of words acquired by
-children as well as the timeline of this acquisition can still vary from
-language to language leading to possibility different learning
-strategies.
+Semantic associations are not necessarily shared across languages, but
+we use this technique as a reasonable first approximation. In support of
+this approximation, Youn et al. (2016) showed that semantic networks
+across languages share substantial similarities. Furthermore, using the
+same association data across languages does not necessarily mean that
+the resulting networks will grow in a similar fashion. For instance, the
+set of words acquired by children as well as the order of word
+acquisition can vary from language to language leading to possibility
+different learning strategies.
 
@@
 In both cases, the results were weaker than those obtained with a threshold of 2.
-We did not consider the case of a threshold larger than 2 since many pairs become phonologically unrelated.}
+We did not consider the case of a threshold larger than 2 since many short pairs appear phonologically unrelated when the edit distance is 3 or more (e.g., "cat"/"dog").}
 The connectivity of a given node was characterized with its
@@
 for the external connectivity in the learning environment. Below we
-analyze properties of this global networks that may a priori hint at an
+analyze properties of these global networks that may a priori hint at an
 INT- or EXT-like growth.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/corrProd-1} \caption{Age of production in the global network as predicted by the degree (i.e., connectivity) in this network.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrProd-1} \caption{Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network.
 Results are shown in each language for phonological and semantic networks.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/corrComp-1} \caption{Age of comprehension in the global network as predicted by the degree (i.e., connectivity) in this network.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrComp-1} \caption{Comprehension data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network.
 Results are shown in each language for phonological and semantic networks.
@@
 Figures \ref{fig:corrProd} and \ref{fig:corrComp} show how the age of
-production and comprehension, respectively, correlates with the degree
-(or indegree for the semantic networks). For ease of visual comparison,
-the predictor (i.e., the degree) was centered and scaled. The plots
-show, overall, a negative correlation between the month of acquisition
-and the degree. In production data, the average correlation across
-languages was -0.24 (\(SD=\) 0.10) for the semantic networks and -0.30
-(\(SD=\) 0.05) for the phonological networks. In comprehension data, the
-average correlation was -0.21 (\(SD=\) 0.08) for the semantic networks
-and -0.21 (\(SD=\) 0.07) for the phonological networks. These results
-indicate that nouns with higher degrees are generally learned earlier,
-thus replicating previous findings in English (Hills et al., 2009;
-Storkel, 2009) and extending these findings to 10 different languages,
-generally, in both production- and comprehension-based vocabularies.
+acquisition in production and comprehension, respectively, correlates
+with the degree (or indegree for the semantic networks). For ease of
+visual comparison, the predictor (i.e., the degree) was centered and
+scaled. The plots show, overall, a negative correlation between the
+month of acquisition and the degree. In production data, the average
+correlation across languages was -0.24 (\(SD=\) 0.10) for the semantic
+networks and -0.30 (\(SD=\) 0.05) for the phonological networks. In
+comprehension data, the average correlation was -0.21 (\(SD=\) 0.08) for
+the semantic networks and -0.21 (\(SD=\) 0.07) for the phonological
+networks. These results indicate that nouns with higher degrees are
+generally learned earlier, thus replicating previous findings in English
+(Hills et al., 2009; Storkel, 2009) and extending these findings to 10
+different languages, generally, in both production- and
+comprehension-based vocabularies.
 
@@
 over words that could possibly enter the lexicon at that month, fit to
-the words that have been learned at that month (using formula 1). Markov
+the words that have been learned at that month (using Formula 1). Markov
 Chain Monte Carlo sampling resulted in a posterior distribution over
@@
   differences. However, our findings do not support this assumption,
-  rather, it supports our initial approximation about the universality
+  rather, it supports our initial approximation about the shared nature
   of the semantic similarity measure. That said, this approximation is
@@
 EXT) across languages. However, we know that other factors influence
-learning as well (e.g., Braginsky et al., 2016). Next we investigated
-how semantic and phonological connectivity interact with two other
-factors. The first one is word frequency, a well studied factor shown to
-predict the age of acquisition in a reliable fashion (e.g. J. C. Goodman
-et al., 2008). The second factor is word length, which was shown to
-correlate with phonological connectivity: Shorter words are more likely
-to have higher connectivity (D. B. Pisoni, Nusbaum, Luce, \& Slowiaczek,
-1985; Vitevitch \& Rodríguez, 2005).
+learning as well (e.g., Braginsky et al., in revision). Next we
+investigated how semantic and phonological connectivity interact with
+two other factors. The first one is word frequency, a well studied
+factor shown to predict the age of acquisition in a reliable fashion
+(e.g. J. C. Goodman et al., 2008). The second factor is word length,
+which was shown to correlate with phonological connectivity: Shorter
+words are more likely to have higher connectivity (Pisoni, Nusbaum,
+Luce, \& Slowiaczek, 1985; Vitevitch \& Rodríguez, 2005).
 
@@
 transcription. For word frequency, we used the frequency estimates from
-Braginsky et al. (2016) where unigram counts were derived based on
-CHILDES corpora in each language (MacWhinney, 2014). Although these
+Braginsky et al. (in revision) where unigram counts were derived based
+on CHILDES corpora in each language (MacWhinney, 2014). Although these
 frequency counts use transcripts from independent sets of children, they
@@
 both comprehension and production data and across languages, endorsing
-results for nouns across a variety of analyses (Braginsky et al., 2016;
-J. C. Goodman et al., 2008; B. C. Roy et al., 2015). Word length is more
-predictive for production than comprehension (and this difference is
-very clear in the global model), replicating previous work (Braginsky et
-al., under review). Thus, word length seems to reflect the effects of
-production's constraints rather than comprehension's constraints, i.e.,
-longer words are harder to articulate but they may not be significantly
-more difficult to store and access.
+results for nouns across a variety of analyses (Braginsky et al., in
+revision; J. C. Goodman et al., 2008; B. C. Roy et al., 2015). Word
+length is more predictive for production than comprehension (and this
+difference is very clear in the global model), replicating previous work
+(Braginsky et al., in revision). Thus, word length seems to reflect the
+effects of production's constraints rather than comprehension's
+constraints, i.e., longer words are harder to articulate but they may
+not be significantly more difficult to store and access.
 
@@
 pitted against frequency and length, this variability is to be taken
-with a grain of salt as it might be exaggerated in our study by the
-limited and partially-overlapping sample of nouns for each language. In
-fact, both phonological and semantic connectivity are significant
+with a grain of salt as it might be exaggerated in our study by several
+factors such as the limited and partially-overlapping set of nouns for
+each language, measurement error due to the sample of acquisition data,
+the sample of frequency data, and the translation of association norms.
+In fact, both phonological and semantic connectivity are significant
 predictors above and beyond frequency and length when data are pooled
@@
 
-For example, in the semantic domain, growth according to EXT can be
+For example, in the semantic domain, growth according to EXT could be
 explained by a mechanism similar to cross-situational learning (McMurray
@@
 learning contexts. Crucially, children can learn these words without
-necessarily knowing the meaning of all other words with witch they
+necessarily knowing the meaning of all other words with which they
 co-occur (hence the similarity with EXT). This possibility is supported
@@
 reliable (Fenson et al., 1994), and has allowed researchers to study
-important aspects of word learning (Braginsky et al., 2016 ; J. C.
+important aspects of word learning (Braginsky et al., in revision; J. C.
 Goodman et al., 2008; Hills et al., 2009; Stella et al., 2017; Storkel,
@@
 network growth, this does not mean individual children never use some
-variant of INT or some combination of both INT and EXT (Beckage and
+variant of INT or some combination of both INT and EXT (Beckage \&
 Colunga, under review). To illustrate, some children develop
@@
 
+\hypertarget{ref-beckage}{}
+Beckage, N. M., \& Colunga, E. (under review). Network growth modeling
+to capture individual lexical learning.
+
 \hypertarget{ref-benedict1979}{}
@@
 
-\hypertarget{ref-braginsky2016}{}
-Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (2016).
-From uh-oh to tomorrow: Predicting age of acquisition for early words
-across languages. In \emph{Proceedings of the 38th Annual Conference of
-the Cognitive Science Society}.
+\hypertarget{ref-braginsky}{}
+Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (in
+revision). Consistency and variability in word learning across
+languages.
 
@@
 
+\hypertarget{ref-hills2018}{}
+Hills, T. T., \& Siew, C. S. (2018). Filling gaps in early word
+learning. \emph{Nature Human Behaviour}, \emph{2}(9).
+
 \hypertarget{ref-hills2010}{}
@@
 Predicting the birth of a spoken word. \emph{Proceedings of the National
-Academy of Sciences}, \emph{112}(41), 12663--12668.
+Academy of Sciences}, \emph{112}(41).
 
@@
 Swingley, D., \& Humphrey, C. (2018). Quantitative linguistic predictors
-of infants? Learning of specific english words. \emph{Child
-Development}, \emph{89}(4), 1247--1267.
+of infants' learning of specific english words. \emph{Child
+Development}, \emph{89}(4).
 

### 2019-09-13 journal/ms.Rmd
revisions

@@
   - id            : "2"
-    institution   : "Department of Psychology, University of Illinois"
+    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
 
@@
 
+# Appendix
+
+## Edit 1
+
+```{r}
+#Import data from saved
+data_all <- feather::read_feather("../saved_data/data_static_scaled_edit1.feather")
+
+data_all$language <- plyr::mapvalues(data_all$language, 
+                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
+                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))
+
+data_long <- data_all %>%
+  rename(Sem = sem_deg, Phono=phono_deg) %>%
+  gather(predictor, value, Sem:frequency) %>%
+  dplyr::filter(predictor == "Phono")
+
+correlations <- data_long %>%
+  group_by(measure, language, predictor) %>%
+  summarise(cor = round(cor(aoa, value), 2))
+
+plot_correlation_1 <- ggplot(subset(data_long, data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), 
+                                  aes(x=value, y=aoa))+
+  facet_grid(language~ measure)+#, scales = "free") +
+  geom_jitter(#aes(colour = lexical_class),
+    colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  geom_abline(slope = -1)+
+  coord_cartesian(xlim=c(-1,5))+
+  #scale_x_continuous(limits=c(-2,5))+
+  scale_y_continuous(breaks =c(15,25,35))+
+  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
+  scale_colour_solarized(name = "") +
+  theme_few()+
+  #theme_bw()+
+  theme(aspect.ratio = 0.7, 
+        plot.margin=grid::unit(c(0,0,0,0), "mm")
+        )+
+  geom_text(data=subset(correlations, correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
+  xlab("degree z-score") +ylab("Age")
+
+plot_correlation_2 <- ggplot(subset(data_long,  data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
+  facet_grid(language~ measure)+#, scales = "free") +
+  geom_jitter(#aes(colour = lexical_class),
+    colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  geom_abline(slope = -1)+
+  coord_cartesian(xlim=c(-1,5))+
+  #scale_x_continuous(limits=c(-2,5))+
+  scale_y_continuous(breaks =c(15,25,35))+
+  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
+  scale_colour_solarized(name = "") +
+  theme_few()+
+  #theme_bw()+
+  theme(aspect.ratio = 0.7, 
+        plot.margin=grid::unit(c(0,0,0,0), "mm")
+        )+
+  geom_text(data=subset(correlations,  correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
+  xlab("degree z-score") +ylab("Age")
+
+corr_plot <- cowplot::plot_grid(
+  plot_correlation_1 ,
+  plot_correlation_2 ,
+  nrow = 1#, 
+  #align = 'vh',
+  #hjust = -1
+)
+
+#legend <- cowplot::get_legend(plot_degree_1)
+
+#plot_degree <- cowplot::plot_grid(prow, legend, nrow = 1, rel_widths = c(4, .5))
+
+#ggsave("figs/plot_correlation_prod.pdf", plot = plot_correlation_prod, width = 10, height = 3)
+#ggsave("figs/plot_correlation_comp.pdf", plot = plot_correlation_comp, width = 10, height = 3)
+```
+
+```{r corrPlot, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients."}
+
+corr_plot
+#plot_grid(plot_correlation_prod , NULL, plot_correlation_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+```
+
+```{r}
+##Test
+static_preds <- feather::read_feather("../saved_data/coefs_all_edit1.feather")
+
+static_preds$predictor <- plyr::mapvalues(static_preds$predictor, 
+                                 from = c("sem_deg","phono_deg","frequency", "length"), 
+                                 to = c("semEXT","phonoEXT", "frequency", "length"))
+
+static_preds$measure <- plyr::mapvalues(static_preds$measure, 
+                                 from = c("produces","understands"), 
+                                 to = c("production","comprehension"))
+
+plot_static_preds_edit1 <- ggplot(subset(static_preds, Test=='Combined'), aes(x = predictor , y = estimate)) +
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., col = predictor, linetype=measure),
+  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  coord_flip() +
+  facet_wrap( ~ language, ncol=5) +
+  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
+  scale_colour_solarized() +
+  theme_few()+
+  theme(aspect.ratio = 0.7) + #,+
+        #axis.text.x = element_text(size=7.5, angle=45)) +
+  scale_y_continuous(breaks =c(-1,0,1))  +
+  #scale_y_discrete(breaks =NULL)
+  ylab("Estimate") +xlab("Mechanism")
+
+```
+
+```{r staticPredEdit1, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression model in each language.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\\% confidence intervals.
+Positive values indicate a positive relationship (e.g.
+longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
+words with higher frequency tend to have a lower AoA).", fig.width=8, fig.height=3}
+
+#legend <- get_legend(plot_static_preds_prod)
+
+#plot_noLegend <- plot_grid(plot_static_preds_prod + theme(legend.position="none"), NULL, plot_static_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+#plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))
+
+#plot_noLegend <- plot_grid(plot_static_preds_prod, NULL, plot_static_preds_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+#plot_grid(plot_noLegend)
+
+plot_static_preds_edit1
+
+```
+
+```{r}
+static_preds_all <- feather::read_feather("../saved_data/static_preds_all_edit1.feather")
+
+static_preds_all$predictor <- plyr::mapvalues(static_preds_all$predictor, 
+                                 from = c("sem_deg","phono_deg","frequency", "length"), 
+                                 to = c("semEXT","phonoEXT","frequency", "length"))
+
+plot_static_preds_all <- ggplot(static_preds_all, aes(x = predictor, y = Estimate)) +
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = Estimate, col = predictor, linetype=Test),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  facet_wrap(~measure)  +
+  coord_flip() +
+  guides(colour=FALSE)+
+  scale_colour_solarized() +
+  theme_few()+
+  theme(aspect.ratio = 0.7)
+
+ggsave("figs/plot_static_preds_all_edit1.pdf", plot = plot_static_preds_all, width = 6, height = 3)
+
+```
+
+```{r staticAllEdit, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\\% confidence intervals.
+Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.", fig.width=6, fig.height=2.5}
+
+plot_static_preds_all
+
+```
+
+## Continuous edit distance
+
+```{r}
+#Import data from saved
+data_all <- feather::read_feather("../saved_data/data_static_scaled_nt.feather")
+
+data_all$language <- plyr::mapvalues(data_all$language, 
+                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
+                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))
+
+data_long <- data_all %>%
+  rename(Sem = sem_deg, Phono=phono_deg) %>%
+  gather(predictor, value, Sem:frequency) %>%
+  dplyr::filter(predictor == "Phono")
+
+correlations <- data_long %>%
+  group_by(measure, language, predictor) %>%
+  summarise(cor = round(cor(aoa, value), 2))
+
+plot_correlation_1 <- ggplot(subset(data_long, data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), 
+                                  aes(x=value, y=aoa))+
+  facet_grid(language~ measure)+#, scales = "free") +
+  geom_jitter(#aes(colour = lexical_class),
+    colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  geom_abline(slope = -1)+
+  #coord_cartesian(xlim=c(-1,5))+
+  #scale_x_continuous(limits=c(-2,5))+
+  scale_y_continuous(breaks =c(15,25,35))+
+  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
+  scale_colour_solarized(name = "") +
+  theme_few()+
+  #theme_bw()+
+  theme(aspect.ratio = 0.7, 
+        plot.margin=grid::unit(c(0,0,0,0), "mm")
+        )+
+  geom_text(data=subset(correlations, correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=1.5, y=35, size=2, fontface = "bold")+
+  xlab("degree z-score") +ylab("Age")
+
+plot_correlation_2 <- ggplot(subset(data_long,  data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
+  facet_grid(language~ measure)+#, scales = "free") +
+  geom_jitter(#aes(colour = lexical_class),
+    colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  geom_abline(slope = -1)+
+  #coord_cartesian(xlim=c(-1,5))+
+  #scale_x_continuous(limits=c(-2,5))+
+  scale_y_continuous(breaks =c(15,25,35))+
+  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
+  scale_colour_solarized(name = "") +
+  theme_few()+
+  #theme_bw()+
+  theme(aspect.ratio = 0.7, 
+        plot.margin=grid::unit(c(0,0,0,0), "mm")
+        )+
+  geom_text(data=subset(correlations,  correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=1.5, y=35, size=2, fontface = "bold")+
+  xlab("degree z-score") +ylab("Age")
+
+corr_plot_nt <- cowplot::plot_grid(
+  plot_correlation_1 ,
+  plot_correlation_2 ,
+  nrow = 1#, 
+  #align = 'vh',
+  #hjust = -1
+)
+
+#legend <- cowplot::get_legend(plot_degree_1)
+
+#plot_degree <- cowplot::plot_grid(prow, legend, nrow = 1, rel_widths = c(4, .5))
+
+#ggsave("figs/plot_correlation_prod.pdf", plot = plot_correlation_prod, width = 10, height = 3)
+#ggsave("figs/plot_correlation_comp.pdf", plot = plot_correlation_comp, width = 10, height = 3)
+```
+
+```{r corrPlotnt, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients."}
+
+corr_plot_nt
+#plot_grid(plot_correlation_prod , NULL, plot_correlation_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+```
+
+```{r}
+##Test
+static_preds <- feather::read_feather("../saved_data/coefs_all_nt.feather")
+
+static_preds$predictor <- plyr::mapvalues(static_preds$predictor, 
+                                 from = c("sem_deg","phono_deg","frequency", "length"), 
+                                 to = c("semEXT","phonoEXT", "frequency", "length"))
+
+static_preds$measure <- plyr::mapvalues(static_preds$measure, 
+                                 from = c("produces","understands"), 
+                                 to = c("production","comprehension"))
+
+plot_static_preds_nt <- ggplot(subset(static_preds, Test=='Combined'), aes(x = predictor , y = estimate)) +
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., col = predictor, linetype=measure),
+  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  coord_flip() +
+  facet_wrap( ~ language, ncol=5) +
+  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
+  scale_colour_solarized() +
+  theme_few()+
+  theme(aspect.ratio = 0.7) + #,+
+        #axis.text.x = element_text(size=7.5, angle=45)) +
+  scale_y_continuous(breaks =c(-1,0,1))  +
+  #scale_y_discrete(breaks =NULL)
+  ylab("Estimate") +xlab("Mechanism")
+
+```
+
+```{r staticPrednt, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression model in each language.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\\% confidence intervals.
+Positive values indicate a positive relationship (e.g.
+longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
+words with higher frequency tend to have a lower AoA).", fig.width=8, fig.height=3}
+
+#legend <- get_legend(plot_static_preds_prod)
+
+#plot_noLegend <- plot_grid(plot_static_preds_prod + theme(legend.position="none"), NULL, plot_static_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+#plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))
+
+#plot_noLegend <- plot_grid(plot_static_preds_prod, NULL, plot_static_preds_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+#plot_grid(plot_noLegend)
+
+plot_static_preds_nt
+
+```
+
+```{r}
+static_preds_all <- feather::read_feather("../saved_data/static_preds_all_nt.feather")
+
+static_preds_all$predictor <- plyr::mapvalues(static_preds_all$predictor, 
+                                 from = c("sem_deg","phono_deg","frequency", "length"), 
+                                 to = c("semEXT","phonoEXT","frequency", "length"))
+
+plot_static_preds_all_nt <- ggplot(static_preds_all, aes(x = predictor, y = Estimate)) +
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = Estimate, col = predictor, linetype=Test),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  facet_wrap(~measure)  +
+  coord_flip() +
+  guides(colour=FALSE)+
+  scale_colour_solarized() +
+  theme_few()+
+  theme(aspect.ratio = 0.7)
+
+ggsave("figs/plot_static_preds_all_nt.pdf", plot = plot_static_preds_all_nt, width = 6, height = 3)
+
+```
+
+```{r staticAllnt, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\\% confidence intervals.
+Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.", fig.width=6, fig.height=2.5}
+
+plot_static_preds_all_nt
+
+```
+
+Problem of colinearity beteen phono and length, that's why the estimates are noisy
+
+## Phonological compostion across languages
+
+generate pair and edit distance, link=1 and link = 2  
+Transform the pairs into matrices 
+Do pairwise mantel test and draw the distribution
+
 \vspace{1em} \fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}} \vspace{1em}
@@
 # Acknowledgements
-This work was supported by a post-doctoral grant from the Fyssen Foundation.
+This work was supported by a post-doctoral grant from the Fyssen Foundation, NSF #1528526, and NSF #1659585.
 

### 2019-09-13 journal/ms.tex
revisions

@@
           \textsuperscript{1} Department of Psychology, Stanford University\\
-          \textsuperscript{2} Department of Psychology, University of Illinois  }
+          \textsuperscript{2} Department of Brain and Cognitive Sciences, Massachusetts Institute of
+Technology  }
 
@@
 
+\section{Appendix}\label{appendix}
+
+\subsection{Edit 1}\label{edit-1}
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlot-1} \caption{Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlot}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPredEdit1-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression model in each language.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\% confidence intervals.
+Positive values indicate a positive relationship (e.g.
+longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
+words with higher frequency tend to have a lower AoA).}\label{fig:staticPredEdit1}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllEdit-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\% confidence intervals.
+Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAllEdit}
+\end{figure}
+
+\subsection{Continuous edit distance}\label{continuous-edit-distance}
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlotnt-1} \caption{Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlotnt}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPrednt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression model in each language.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\% confidence intervals.
+Positive values indicate a positive relationship (e.g.
+longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
+words with higher frequency tend to have a lower AoA).}\label{fig:staticPrednt}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllnt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\% confidence intervals.
+Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAllnt}
+\end{figure}
+
 \vspace{1em}

### 2019-09-13 main_analyses.Rmd
remarks by george
final version
revisions

@@
 
-data_all$language <- plyr::mapvalues(data_all$language, 
-                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
-                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))
-
 ```
@@
 ```{r}
+
+#Number of children
+
+#Number of children
+n_child <- data_all %>%
+  mutate(sum_child =  num_true+num_false) %>%
+  group_by(language, measure, item) %>%
+  summarise(children = sum(sum_child)) %>%
+  distinct(language, measure, children)
 
@@
             nouns = n_distinct(item)) %>%
+  left_join(n_child) %>%
   mutate(age_range = paste(min_age, max_age, sep = "-")) %>%
@@
   unnest(.sep = "_") %>%
-  select(language, un = understands_nouns, ua=understands_age_range,
-                   pn = produces_nouns, pa=produces_age_range)
+  select(language, un = understands_nouns, ua=understands_age_range, uc= understands_children,
+                   pn = produces_nouns, pa=produces_age_range, pc=produces_children)
 
@@
 
-data_aoa <- data_aoa %>%
+feather::write_feather(data_aoa, "saved_data/data_aoa.feather")
+
+aoa <- feather::read_feather("saved_data/data_aoa.feather")  %>%
   select(language, form, measure, uni_lemma, item, definition, aoa) %>%
   distinct()
-
-#feather::write_feather(data_aoa, "saved_data/data_aoa.feather")
 
@@
 data_growth <- feather::read_feather("saved_data/data_growth.feather")
+
 ```
@@
     #filter(!is.na(uni_lemma)) %>% #only keep unilemmas that intersect with free association data
-  dplyr::filter(aoa > 5)
+  filter(age > 5)
 
@@
 
-  phono_pairs<- make_IPA_pairs(def_list = def_list, lang = lang)
+  phono_pairs<- make_IPA_pairs(def_list = def_list, lang = lang) %>%
+    mutate(language = lang) %>%
 
   #Threshold the phonetic distance (we take t=2, becuase t=1 is too sparse) 
-  threshold <- 2
+  threshold <- 1
 
@@
 
+ # phono_nt_PAC <- PAC_generator(vocab_age = growth_meas_lang, word_pairs = phono_pairs %>% IPA_continuous()) #%>% 
+ #    rename(PAC_phono = value) %>% select(-definition, -uni_lemma)
+
   phono_growth <- growth_meas_lang %>%
+   left_join(phono_nt_PAC) 
    left_join(phono_PAC) %>%
@@
 
-}
-
-phono_red <-  map(growth_by_meas_lang, phono_net_fun) %>%
+  return(phono_growth)
+}
+
+phono_red_nt <-  map(growth_by_meas_lang, phono_net_fun) %>%
   bind_rows()
 
-#feather::write_feather(phono_red, "saved_data/phono_red.feather")
-phono_red <- feather::read_feather("saved_data/phono_red.feather")
+feather::write_feather(phono_red_nt, "saved_data/phono_red_nt.feather")
+
+feather::write_feather(phono_red, "saved_data/phono_red_edit1.feather")
+phono_red <- feather::read_feather("saved_data/phono_red_nt.feather")
 
@@
   left_join(phono_red)
+
+feather::write_feather(data_growth_net, "saved_data/data_growth_net_nt.feather")
+
+```
+
+Here do Mantel tests
+```{r}
+
+phono_net_fun <- function (growth_meas_lang) {
+
+  lang <- unique(growth_meas_lang$language)
+  #meas <- unique(growth_meas_lang$measure)
+
+  first_age<- growth_meas_lang$age[1]
+
+  def_list<- growth_meas_lang %>%
+    filter(!is.na(uni_lemma)) %>%
+    trim_all_definition() %>% 
+    filter(age==first_age) %>%
+    select(item, definition)
+
+  item_unilemma <- growth_meas_lang %>%
+    filter(!is.na(uni_lemma)) %>%
+    select(item, uni_lemma)
+
+  phono_pairs<- make_IPA_pairs(def_list = def_list, lang = lang) %>%
+    mutate(language = lang) %>%
+    left_join(item_unilemma) %>%
+    rename(item0 = item,
+           item = pair,
+           item.uni_lemma = uni_lemma) %>%
+    left_join(item_unilemma) %>%
+    rename(pair.uni_lemma = uni_lemma,
+           pair = item,
+           item = item0)
+
+  return(phono_pairs)
+}
+
+#Ici mantel test
+phono_pairs_all <- map(growth_by_meas_lang, phono_net_fun) %>%
+  bind_rows()
+
+feather::write_feather(phono_pairs_all, "saved_data/phono_pairs_all.feather")
+
+phono_pairs_dist <- phono_pairs_all %>%
+  mutate(link1 = as.numeric(dist<=1)) %>%
+  mutate(link2 = as.numeric(dist<=2)) %>%
+  mutate(link_cont = ifelse(dist==0, 1, 1/dist))
+
+#Pairwise comparision: each time, take the overlap and do the test
+
+data_prod <- data_aoa %>%
+  filter(measure =='produces')
+
+data_by_lang <- split(phono_pairs_dist$language)
+
+pair_data <- function(lang1){
+
+  pair_cor_data <- function (lang2){
+
+  lang1_unilemmas <- unique(lang1$uni_lemma)
+  lang2_unilemmas <- unique(lang2$uni_lemma)
+  uni_intersect <-  intersect(lang1_unilemmas, lang2_unilemmas)
+
+  data_lang1 <- lang1 %>%
+    filter(!is.na(uni_lemma),
+           uni_lemma %in% uni_intersect) %>%
+    select(uni_lemma, aoa) %>%
+    group_by(uni_lemma) %>%
+    summarise(aoa1=mean(aoa))
+
+  data_lang2 <- lang2 %>%
+    filter(!is.na(uni_lemma),
+           uni_lemma %in% uni_intersect) %>%
+    select(uni_lemma, aoa) %>%
+    group_by(uni_lemma) %>%
+    summarise(aoa2=mean(aoa))
+
+  both <- data_lang1 %>%
+    left_join(data_lang2)
+
+  mycorr <- cor.test(rank(both$aoa1), rank(both$aoa2), method = 'kendall')
+  val=mycorr$estimate
+  p=mycorr$p.value
+  language1 = unique(lang1$language) 
+  language2 = unique(lang2$language)
+
+  data.frame(language1=language1, language2=language2, tau=val, sig = p)
+
+}
+  map(data_by_lang, pair_cor_data) %>%
+    bind_rows()
+
+}
 
@@
 
-aoa_items <- data_aoa %>%
+aoa_items <- aoa %>%
   select(language, measure, item, aoa) # Here I should round the AoA?
@@
 
-data_static_prop$language <- plyr::mapvalues(data_static_prop$language, 
-                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
-                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))
-
 data_static_prop <- data_all %>%
   left_join(data_static_pred)
+
 ```
@@
 ```{r}
+
+#data_all$language <- plyr::mapvalues(data_all$language, 
+#                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", #"Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
+#                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", #"Russian", "Spanish", "Swedish", "Turkish"))
 
@@
 
+unilemmas_nt <-unilemmas %>%
+  filter(phono_deg != 'Inf')
+
 #Impute missing values and center/scale
-uni_scale <- unilemmas %>%
+uni_scale <- unilemmas_nt %>%
   group_by(measure, language) %>%
@@
 
-feather::write_feather(uni_scale, "saved_data/data_static_scaled.feather")
+feather::write_feather(uni_scale, "saved_data/data_static_scaled_nt.feather")
 #phono_red <- feather::read_feather("saved_data/phono_red.feather")
@@
 
+```
+
+Here do some analysis
+```{r}
+#Regression with phono (edit=1)
+
+#Regression with phono (1/edit)
 ```
@@
   geom_abline(slope = -1)+
-  coord_cartesian(xlim=c(-1,5))+
+  #coord_cartesian(xlim=c(-1,10))+
   #scale_x_continuous(limits=c(-2,5))+
@@
 
+#data_growth_net <- feather::read_feather("saved_data/data_growth_net.feather")
+data_growth_net_as_ws <- feather::read_feather("../asNet_local/saved_data/data_growth_net_AS_WS.feather")
+
 #Filtering 
@@
 
+#data_growth_pred_as <- feather::read_feather("../asNet_local/saved_data/data_growth_pred_wg_as_test")
+
 ```
@@
 
+   #for (i in 1:1) {
    for (i in 1:length(model_list)) {
@@
                                   method = "MCMC",
-                                  samples = 1000, 
+                                  samples = 500, 
                                   burn = 500),
@@
 
-feather::write_feather(posterior, "saved_data/posterior.feather")
-posterior <- feather::read_feather("saved_data/posterior.feather")
+feather::write_feather(posterior, "saved_data/posterior_as_ws.feather")
+#posterior <- feather::read_feather("saved_data/posterior.feather")
+
+#data_growth_meas_lang <- data_growth_by_meas_lang[[1]]
+
+#posterior_fun(data_test)
 
@@
 
-feather::write_feather(param_summary_all, "saved_data/growth_preds.feather")
-param_summary_all <- feather::read_feather("saved_data/growth_preds.feather")
+#feather::write_feather(param_summary_all, "saved_data/growth_preds.feather")
+#param_summary_all <- feather::read_feather("saved_data/growth_preds.feather")
 
@@
 ```{r fig.width=5, fig.height=2}
-ggplot(subset(param_summary_all, measure == "produces"), aes(x = model , y = mean)) +
+ggplot(subset(param_summary_all, measure == "produces" & Test =="Individual"), aes(x = model , y = mean)) +
+  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  coord_flip() +
+  facet_wrap( ~ language, ncol=5) +
+  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
+  scale_colour_solarized() +
+  theme_bw()+
+  theme(aspect.ratio = 0.7)
+
+```
+
+Plot growth data (comprehension)
+
+```{r fig.width=5, fig.height=2}
+ggplot(subset(param_summary_all, measure == "understands" & Test =="Individual"
+              ), aes(x = model , y = mean)) +
   geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
@@
 
-Plot growth data (comprehension)
-
-```{r fig.width=5, fig.height=2}
-ggplot(subset(param_summary_all, measure == "understands"), aes(x = model , y = mean)) +
-  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
-                  position = position_dodge(width = .5),
-                  size = 0.5,
-                  fatten = 0.5)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  coord_flip() +
-  facet_wrap( ~ language, ncol=5) +
-  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
-  scale_colour_solarized() +
-  theme_bw()+
-  theme(aspect.ratio = 0.7)
-
-```
-
 ## Compare PAC to other predictors of AoA
@@
  }
+
+uni_scale <- feather::read_feather("saved_data/data_static_scaled_nt.feather")
+#uni_scale_edit <- feather::read_feather("saved_data/data_static_scaled_edit1.feather")
 
@@
 
-feather::write_feather(coefs_all, "saved_data/static_preds.feather")
-coefs_all <- feather::read_feather("saved_data/static_preds.feather")
+feather::write_feather(coefs_all, "saved_data/coefs_all_nt.feather")
 
@@
   bind_rows(coef_agg_comp) %>%
-  mutate(Test = ifelse(toString(formula[3])=='frequency + length + sem_deg + phono_deg + (1 | language)', 'Combined', 'Individual'))
+  mutate(Test = ifelse(toString(formula[3])=='frequency + length + sem_deg + head(phono_deg + (1 | language)', 'Combined', 'Individual'))
 
@@
 
-feather::write_feather(coefs_agg_all, "saved_data/static_preds_all.feather")
-coefs_agg_all <- feather::read_feather("saved_data/static_preds_all.feather")
+feather::write_feather(coefs_agg_all, "saved_data/static_preds_all_nt.feather")
+coefs_agg_all <- feather::read_feather("saved_data/static_preds_all_nt.feather")
 

### 2019-09-13 helper_functions/phono_helper.r

@@ -37,4 +37,10 @@ IPA_threshold<- function(IPA_list, threshold){
   return(IPA_list)
 }
 
+IPA_continuous<- function(IPA_list){
+  IPA_list<- IPA_list %>%
+    mutate(link=as.numeric(1/dist))
+  return(IPA_list)
+}
+
 ######################################################################################################

### 2019-09-20 journal/ms.Rmd
revisions

--- 2019-02-12 journal/ms.Rmd
@@
 For example, @goodman2008 found that, within a lexical category (e.g., nouns), higher parental frequency is associated with earlier learning.
-Researchers have studied the role of several other factors such as word length and the mean length of utterances in which the word occurs [e.g., @braginsky; @swingley2018].
+Researchers have studied the role of several other factors such as word length and the mean length of utterances in which the word occurs [e.g., @braginsky2019; @swingley2018].
 
@@
 For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
-Thus, according to INT, node 1 is more likely to enter the lexicon.
+In this simplified example, candidate node 1 would connect to an internal node with 3 connections, thus we have $u_{INT}(node_1)= 3$.
+As for candidate node 2, it would connect to internal nodes that have only one connection each, making an average of 1, i.e., $u_{INT}(node_2)= 1$.
+According to INT, node 1 is more likely to enter the lexicon.
 For EXT, the utility of a candidate node is its degree in the entire network.
-According to EXT, node 2 is more likely to enter the lexicon next.
-This figure is based on an example from Hills et al (2009).", fig.align = "center", out.width = "300px"}
+In our example, candidate node 1 has 2 connections in total whereas candidate node 2 has 5 connections.
+So we have $u_{EXT}(node_1)= 2$ and $u_{EXT}(node_2)= 5$.
+Thus, according to EXT, node 2 is more likely to enter the lexicon next.
+This figure is based on an example from Hills et al.
+(2009).", fig.align = "center", out.width = "300px"}
 knitr::include_graphics("figs/growth3.png")
@@
 These differences may reflect the fact that comprehension and production do not share the same constraints.
-For instance, whereas comprehension depends on the ease with which words are stored and accessed, production depends, additionally, on the ease with which words are articulated, e.g., shorter words are produced earlier [@braginsky].
+For instance, whereas comprehension depends on the ease with which words are stored and accessed, production depends, additionally, on the ease with which words are articulated, e.g., shorter words are produced earlier [@braginsky2019].
 By investigating comprehension-based vocabularies, we assess the extent to which the network growth mechanism captures general learning patterns beyond the specific constraints of production.
@@
 Then we fit a logistic curve to these proportions and determined when the curve crosses 0.5, i.e., the age at which at least 50% of children know the word.
-We take this point in time to be each word’s age of acquisition [@goodman2008; @braginsky].
+We take this point in time to be each word’s age of acquisition [@goodman2008; @braginsky2019].
 <!--We obtained these nouns in ten languages: Croatian, Danish, English, French, Italian, Norwegian, Russian, Spanish, Swedish, and Turkish.
@@
       linesep = "", format.args = list(big.mark = ","),
-      caption = "Statistics for the dataset we used.",
+      caption = "Statistics for the dataset we used. The ages are in months.",
       col.names = c("Language",  "Nouns", "Ages", "N", "Nouns", "Ages","N")) %>%
@@
             sd = sd(cor))
+
+cor_phon_len_edit2 <- data_all %>%
+  group_by(language, measure) %>%
+  summarise(phon_len = cor(phono_deg, length)) %>%
+  group_by(measure) %>%
+  summarise(ave = mean(phon_len))
 
@@
   geom_text(data=subset(correlations, measure=="produces" & correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
-  xlab("degree z-score") +ylab("Age")
+  xlab("degree z-score") +ylab("Age (in months)")
 
@@
   geom_text(data=subset(correlations, measure=="produces" & correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
-  xlab("degree z-score") +ylab("Age")
+  xlab("degree z-score") +ylab("Age (in months)")
 
@@
   geom_text(data=subset(correlations, measure=="understands" & correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=3.5, y=25, size=2, fontface = "bold")+
-  xlab("degree z-score") +ylab("Age")
+  xlab("degree z-score") +ylab("Age (in months)")
 
@@
   geom_text(data=subset(correlations, measure=="understands" & correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=3.5, y=25, size=2, fontface = "bold")+
-  xlab("degree z-score") +ylab("Age")
+  xlab("degree z-score") +ylab("Age (in months)")
 
@@
 ##Test
+
+#Colorblind-friendly palette
+cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
 growth_preds <- feather::read_feather("../saved_data/growth_preds.feather")
@@
   facet_wrap( ~ language, ncol=5) +
-  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
-  scale_colour_solarized() +
-  theme_few()+
-  theme(aspect.ratio = 0.7) + #,+
-        #axis.text.x = element_text(size=7.5, angle=45)) +
+  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.5)))+
+  scale_colour_manual(values=cbPalette)+
+  theme_few()+
+  theme(aspect.ratio = 0.7,
+        axis.text = element_text(size=12)) +
   scale_y_continuous(breaks =c(0,0.2))  +
@@
 Each point represents the mean of the posterior distribution of the growth parameter, with ranges representing 95\\% credible intervals.
-Positive values mean that learning proceeds according to the predictions of the growth scenario, whereas negative values mean that learning proceeds in opposition to the predictions of the growth scenario.", fig.width=8, fig.height=3}
+Positive values mean that learning proceeds according to the predictions of the growth scenario, whereas negative values mean that learning proceeds in opposition to the predictions of the growth scenario.", fig.width=10, fig.height=4}
 
@@
 
-plot_growth_preds
+plot_growth_preds + theme(legend.position="bottom")
 
@@
 ##Test
-static_preds <- feather::read_feather("../saved_data/static_preds.feather")
+static_preds <- feather::read_feather("../saved_data/coefs_all.feather")
 
@@
   facet_wrap( ~ language, ncol=5) +
-  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
-  scale_colour_solarized() +
-  theme_few()+
-  theme(aspect.ratio = 0.7) + #,+
-        #axis.text.x = element_text(size=7.5, angle=45)) +
+  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.6)))+
+  scale_colour_manual(values=cbPalette)+
+  theme_few()+
+  theme(aspect.ratio = 0.7,
+        axis.text = element_text(size=12)) +
   scale_y_continuous(breaks =c(-1,0,1))  +
@@
 longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
-words with higher frequency tend to have a lower AoA).", fig.width=8, fig.height=3}
+words with higher frequency tend to have a lower AoA).", fig.width=10, fig.height=4}
 
@@
 
-plot_static_preds
+plot_static_preds + theme(legend.position="bottom")
 
@@
   guides(colour=FALSE)+
-  scale_colour_solarized() +
+  scale_colour_manual(values=cbPalette)+
   theme_few()+
@@
 Above we showed that the way semantic and phonological information is structured in the learning environment contributes to noun learning (via EXT) across languages.
-However, we know that other factors influence learning as well [e.g., @braginsky].
+However, we know that other factors influence learning as well [e.g., @braginsky2019].
 Next we investigated how semantic and phonological connectivity interact with two other factors.
@@
 For word length, we counted the number of phonemes in our generated IPA transcription.
-For word frequency, we used the frequency estimates from @braginsky where unigram counts were derived based on CHILDES corpora in each language [@macwhinney2014].
+For word frequency, we used the frequency estimates from @braginsky2019 where unigram counts were derived based on CHILDES corpora in each language [@macwhinney2014].
 Although these frequency counts use transcripts from independent sets of children, they are based on large samples, and this allows us to average out possible differences between children and the specificities of their input [see @goodman2008 for a similar research strategy].
@@
 The findings for the new predictors were as follows.
-Overall, frequency is the largest and most consistent predictor of age of acquisition in both comprehension and production data and across languages, endorsing results for nouns across a variety of analyses [@goodman2008; @braginsky; @roy2015].
-Word length is more predictive for production than comprehension (and this difference is very clear in the global model), replicating previous work [@braginsky].
+Overall, frequency is the largest and most consistent predictor of age of acquisition in both comprehension and production data and across languages, endorsing results for nouns across a variety of analyses [@goodman2008; @braginsky2019; @roy2015].
+Word length is more predictive for production than comprehension (and this difference is very clear in the global model), replicating previous work [@braginsky2019].
 Thus, word length seems to reflect the effects of production's constraints rather than comprehension's constraints, i.e., longer words are harder to articulate but they may not be significantly more difficult to store and access.
@@
 Children are sensitive to local phonotactic regularities [@jusczyk1994] and this sensitivity might lead them to learn higher-probability words more easily [@storkel2001].
-This explanation is supported by computational simulations that show how learning general phonotactics patterns create "well-worn paths" which allow the models to represent several distinct but phonologically neighboring words [@dell1993; @takac2017].
+This explanation is supported by computational simulations that show how learning general phonotactics patterns create "well-worn paths" which allow the models to represent several distinct but phonologically neighboring words [@dell1993; @takac2017; @siew2013].
+More generally, there is a growing interest in investigating precisely how the local patterns acquired through statistical learning may give rise to the global network orgnization [For a review, see @karuza2016].
 
@@
 
+This study investigated the class of nouns in isolation --- following previous studies investigating the early semantic and phonological network [@hills2009; @storkel2009].
+We could ask if studying one class separtaly is a legitimate research strategy.
+In other words, would word classes (such as nouns, verbs and function words) be acquired relatively differently, or would they interact substantially to the extent that it becomes unreasonable to study each class separately?
+
+We know that different word classes follow different time trajectories.
+For instance, in the early stages of development, nouns tend to be acquired at a higher pace than predicates and function words [@bates1994].
+Research has shown that this difference cannot be trivially attributed to differences in the degree to which these classes are present in the input; if anything, verbs and function words are often more frequent in the input than nouns [e.g., @gentner1982].
+@goodman2008 found an effect of frequency on the age of acquisition within --- not across --- classes.
+Further, a recent work by @braginsky2019 tested a large number of predictors, besides frequency, and found that these predictors do not influence the acquisition of word classes in the same way.
+For example, the acquisition of nouns was found to be most influenced by frequency and concreteness, whereas the acquisition of function words was most influenced by word length.
+
+These patterns support the hypothesis that different word classes have different pathways of learning, thus making it worthwhile to study each class separately.
+This hypothesis, however, does not preclude all sorts of inter-class interaction.
+For example, @dautriche2015 found that the acquisition of similar-sounding words ("bih"-"dih") is easier if these words belong to different syntactic categories (e.g., a noun and a verb).
+
 This work shares a number of limitations with previous studies using similar research strategy and datasets.
 Chief among these limitations is the fact that the age of word acquisition is computed using different children at different ages (due to the fact that available CDI data is mainly cross-sectional).
-Such a measure has been shown to be valid and reliable [@fenson94], and has allowed researchers to study important aspects of word learning [@hills2009; @stella2017; @storkel2009; @goodman2008; @braginsky].
+Such a measure has been shown to be valid and reliable [@fenson94], and has allowed researchers to study important aspects of word learning [@hills2009; @stella2017; @storkel2009; @goodman2008; @braginsky2019].
 In our case, the use of cost-effective cross-sectional data has allowed us to leverage large-scale studies across several languages.
@@
 None of the authors have any financial interest or a conflict of interest regarding this work and this submission.
+
+\clearpage
+
+# Appendix A: Analyses using different phnonological distances
+
+In the methods section, we based the choice of setting the threshold of edit distance at 2 on the fact that the early lexicon is very sparse in terms of phonological neighborhood; the early proposal that set the threshold at 1 (e.g., Vitevitch, 2008) was defined in the context of rather mature, dense lexicon.
+Increasing the threshold from 1 to 2 allows for a more reasonable representation of the similarity space of the early phonological network.
+
+That said, it is useful to include the results obtained with both thresholds.
+In addition, it could be useful to compare the results to the case of weighted networks, i.e., with no thresholding.
+The main analyses for these two cases are shown in what follows.
+In summary, both methods of constructing the phonological networks had issues.
+While the fact of using edit = 1 created sparsity, using weighted networks created colinearity with length.
+
+## Analyses using phonological networks constructed with an edit distance of 1
+
+We show in Figure \@ref(fig:corrPlot) the correlation between the phonological connectivity and age of acquisition in both comprehension and production.
+The sparsity issue, due the low phonological neighborhood in the children's lexicon is apparent: most words had 0 degree and a few had non-zero but small degrees.
+The values of the correlations are much lower than the ones obtained with the threshold of 2.
+
+The next figures show how the phonology-based mechanism of growth (phonoEXT) fares in comaprision to semEXT and other predictors of learing in each language (Figure \@ref(fig:staticPredEdit1) and across all languages (Figure \@ref(fig:staticAllEdit)).
+These figures show that phonoEXT based on edit distance 1 had no noticeable effect on learning.
+
+```{r}
+#Import data from saved
+data_all <- feather::read_feather("../saved_data/data_static_scaled_edit1.feather")
+
+data_all$language <- plyr::mapvalues(data_all$language, 
+                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
+                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))
+
+data_long <- data_all %>%
+  rename(Sem = sem_deg, Phono=phono_deg) %>%
+  gather(predictor, value, Sem:frequency) %>%
+  dplyr::filter(predictor == "Phono")
+
+correlations <- data_long %>%
+  group_by(measure, language, predictor) %>%
+  summarise(cor = round(cor(aoa, value), 2))
+
+plot_correlation_1 <- ggplot(subset(data_long, data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), 
+                                  aes(x=value, y=aoa))+
+  facet_grid(language~ measure)+#, scales = "free") +
+  geom_jitter(#aes(colour = lexical_class),
+    colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  geom_abline(slope = -1)+
+  coord_cartesian(xlim=c(-1,5))+
+  #scale_x_continuous(limits=c(-2,5))+
+  scale_y_continuous(breaks =c(15,25,35))+
+  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
+  scale_colour_solarized(name = "") +
+  theme_few()+
+  #theme_bw()+
+  theme(aspect.ratio = 0.7, 
+        plot.margin=grid::unit(c(0,0,0,0), "mm")
+        )+
+  geom_text(data=subset(correlations, correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
+  xlab("degree z-score") +ylab("Age (in months)")
+
+plot_correlation_2 <- ggplot(subset(data_long,  data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
+  facet_grid(language~ measure)+#, scales = "free") +
+  geom_jitter(#aes(colour = lexical_class),
+    colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  geom_abline(slope = -1)+
+  coord_cartesian(xlim=c(-1,5))+
+  #scale_x_continuous(limits=c(-2,5))+
+  scale_y_continuous(breaks =c(15,25,35))+
+  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
+  scale_colour_solarized(name = "") +
+  theme_few()+
+  #theme_bw()+
+  theme(aspect.ratio = 0.7, 
+        plot.margin=grid::unit(c(0,0,0,0), "mm")
+        )+
+  geom_text(data=subset(correlations,  correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
+  xlab("degree z-score") +ylab("Age (in months)")
+
+corr_plot <- cowplot::plot_grid(
+  plot_correlation_1 ,
+  plot_correlation_2 ,
+  nrow = 1#, 
+  #align = 'vh',
+  #hjust = -1
+)
+
+cor_phon_len_edit1 <- data_all %>%
+  group_by(language, measure) %>%
+  summarise(phon_len = cor(phono_deg, length)) %>%
+  group_by(measure) %>%
+  summarise(ave = mean(phon_len))
+
+#legend <- cowplot::get_legend(plot_degree_1)
+
+#plot_degree <- cowplot::plot_grid(prow, legend, nrow = 1, rel_widths = c(4, .5))
+
+#ggsave("figs/plot_correlation_prod.pdf", plot = plot_correlation_prod, width = 10, height = 3)
+#ggsave("figs/plot_correlation_comp.pdf", plot = plot_correlation_comp, width = 10, height = 3)
+```
+
+```{r corrPlot, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Age of acquistion in both comprehension and production as predicted by the degree (i.e., connectivity) in phonological network, using an edit distance of 1.
+Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients."}
+
+corr_plot
+#plot_grid(plot_correlation_prod , NULL, plot_correlation_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+```
+
+```{r}
+##Test
+static_preds <- feather::read_feather("../saved_data/coefs_all_edit1.feather")
+
+static_preds$predictor <- plyr::mapvalues(static_preds$predictor, 
+                                 from = c("sem_deg","phono_deg","frequency", "length"), 
+                                 to = c("semEXT","phonoEXT", "frequency", "length"))
+
+static_preds$measure <- plyr::mapvalues(static_preds$measure, 
+                                 from = c("produces","understands"), 
+                                 to = c("production","comprehension"))
+
+plot_static_preds_edit1 <- ggplot(subset(static_preds, Test=='Combined'), aes(x = predictor , y = estimate)) +
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., col = predictor, linetype=measure),
+  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  coord_flip() +
+  facet_wrap( ~ language, ncol=5) +
+  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.6)))+
+  scale_colour_manual(values=cbPalette)+ 
+  theme_few()+
+  theme(aspect.ratio = 0.7,
+        axis.text = element_text(size=12))+
+  scale_y_continuous(breaks =c(-1,0,1))  +
+  #scale_y_discrete(breaks =NULL)
+  ylab("Estimate") +xlab("Mechanism")
+
+```
+
+```{r staticPredEdit1, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression model in each language.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\\% confidence intervals.
+Positive values indicate a positive relationship (e.g.
+longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
+words with higher frequency tend to have a lower AoA).", fig.width=10, fig.height=4}
+
+#legend <- get_legend(plot_static_preds_prod)
+
+#plot_noLegend <- plot_grid(plot_static_preds_prod + theme(legend.position="none"), NULL, plot_static_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+#plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))
+
+#plot_noLegend <- plot_grid(plot_static_preds_prod, NULL, plot_static_preds_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+#plot_grid(plot_noLegend)
+
+plot_static_preds_edit1 + theme(legend.position="bottom")
+
+```
+
+```{r}
+static_preds_all <- feather::read_feather("../saved_data/static_preds_all_edit1.feather")
+
+static_preds_all$predictor <- plyr::mapvalues(static_preds_all$predictor, 
+                                 from = c("sem_deg","phono_deg","frequency", "length"), 
+                                 to = c("semEXT","phonoEXT","frequency", "length"))
+
+plot_static_preds_all <- ggplot(static_preds_all, aes(x = predictor, y = Estimate)) +
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = Estimate, col = predictor, linetype=Test),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  facet_wrap(~measure)  +
+  coord_flip() +
+  guides(colour=FALSE)+
+  scale_colour_manual(values=cbPalette) +
+  theme_few()+
+  theme(aspect.ratio = 0.7)
+
+ggsave("figs/plot_static_preds_all_edit1.pdf", plot = plot_static_preds_all, width = 6, height = 3)
+
+```
+
+```{r staticAllEdit, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined model.
+Here the phonologocal networks were based on an edit distance of 1.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\\% confidence intervals.
+Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.", fig.width=6, fig.height=2.5}
+
+plot_static_preds_all
+
+```
+
+## Analyses using wighted phonological networks with no thresholding
+
+```{r}
+#Import data from saved
+data_all <- feather::read_feather("../saved_data/data_static_scaled_nt.feather")
+
+data_all$language <- plyr::mapvalues(data_all$language, 
+                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
+                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))
+
+data_long <- data_all %>%
+  rename(Sem = sem_deg, Phono=phono_deg) %>%
+  gather(predictor, value, Sem:frequency) %>%
+  dplyr::filter(predictor == "Phono")
+
+correlations <- data_long %>%
+  group_by(measure, language, predictor) %>%
+  summarise(cor = round(cor(aoa, value), 2))
+
+plot_correlation_1 <- ggplot(subset(data_long, data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), 
+                                  aes(x=value, y=aoa))+
+  facet_grid(language~ measure)+#, scales = "free") +
+  geom_jitter(#aes(colour = lexical_class),
+    colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  geom_abline(slope = -1)+
+  #coord_cartesian(xlim=c(-1,5))+
+  #scale_x_continuous(limits=c(-2,5))+
+  scale_y_continuous(breaks =c(15,25,35))+
+  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
+  scale_colour_solarized(name = "") +
+  theme_few()+
+  #theme_bw()+
+  theme(aspect.ratio = 0.7, 
+        plot.margin=grid::unit(c(0,0,0,0), "mm")
+        )+
+  geom_text(data=subset(correlations, correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=1.5, y=35, size=2, fontface = "bold")+
+  xlab("degree z-score") +ylab("Age (in months)")
+
+plot_correlation_2 <- ggplot(subset(data_long,  data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
+  facet_grid(language~ measure)+#, scales = "free") +
+  geom_jitter(#aes(colour = lexical_class),
+    colour = solarized_palette(1),
+    size = 0.5, alpha = 0.5) +
+  geom_abline(slope = -1)+
+  #coord_cartesian(xlim=c(-1,5))+
+  #scale_x_continuous(limits=c(-2,5))+
+  scale_y_continuous(breaks =c(15,25,35))+
+  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
+  scale_colour_solarized(name = "") +
+  theme_few()+
+  #theme_bw()+
+  theme(aspect.ratio = 0.7, 
+        plot.margin=grid::unit(c(0,0,0,0), "mm")
+        )+
+  geom_text(data=subset(correlations,  correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=1.5, y=35, size=2, fontface = "bold")+
+  xlab("degree z-score") +ylab("Age (in months)")
+
+corr_plot_nt <- cowplot::plot_grid(
+  plot_correlation_1 ,
+  plot_correlation_2 ,
+  nrow = 1#, 
+  #align = 'vh',
+  #hjust = -1
+)
+
+cor_phon_len_nt <- data_all %>%
+  group_by(language, measure) %>%
+  summarise(phon_len = cor(phono_deg, length)) %>%
+  group_by(measure) %>%
+  summarise(ave = mean(phon_len))
+
+#legend <- cowplot::get_legend(plot_degree_1)
+
+#plot_degree <- cowplot::plot_grid(prow, legend, nrow = 1, rel_widths = c(4, .5))
+
+#ggsave("figs/plot_correlation_prod.pdf", plot = plot_correlation_prod, width = 10, height = 3)
+#ggsave("figs/plot_correlation_comp.pdf", plot = plot_correlation_comp, width = 10, height = 3)
+```
+
+We constructed weighted phonological networks where the edge between a given pair of words $(w_1, w_2)$ was wieghted by $\frac{1}{edit(w_1,w_2)}$.
+The phonological connectivity of a given word $w$ was defined as the sum over all weighted edges with every other word $w_i$ in the network, i.e., $\sum_{i} \frac{1}{edit(w,w_i)}$.
+
+The results were as follows.
+On the one hand, the correlations were generally high and in many cases (especially in the production data), higher than the ones obtained with the thresholds 2 and 1 (Figure \@ref(fig:corrPlotnt)).
+On the other hand, phonoEXT resulted in very noisy estimates when we controlled for frequency and length (Figures \@ref(fig:staticPrednt) and \@ref(fig:staticAllnt)).
+The reason was that the new phonological connectivity was very highly correlated with length.
+The average correlation across languages was $r =$ `r cor_phon_len_nt$ave[cor_phon_len_nt$measure == "produces"]` for production data (compared to `r cor_phon_len_edit1$ave[cor_phon_len_edit1$measure == "produces"]` and `r cor_phon_len_edit2$ave[cor_phon_len_edit2$measure == "produces"]` for the phonological networks with edit = 1 and 2, respectvely).
+This fact lead to a collinearity issue in the regression, making the effect hard to estimate.
+
+```{r corrPlotnt, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients."}
+
+corr_plot_nt
+#plot_grid(plot_correlation_prod , NULL, plot_correlation_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+```
+
+```{r}
+##Test
+static_preds <- feather::read_feather("../saved_data/coefs_all_nt.feather")
+
+static_preds$predictor <- plyr::mapvalues(static_preds$predictor, 
+                                 from = c("sem_deg","phono_deg","frequency", "length"), 
+                                 to = c("semEXT","phonoEXT", "frequency", "length"))
+
+static_preds$measure <- plyr::mapvalues(static_preds$measure, 
+                                 from = c("produces","understands"), 
+                                 to = c("production","comprehension"))
+
+plot_static_preds_nt <- ggplot(subset(static_preds, Test=='Combined'), aes(x = predictor , y = estimate)) +
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., col = predictor, linetype=measure),
+  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  coord_flip() +
+  facet_wrap( ~ language, ncol=5) +
+  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.6)))+
+  scale_colour_manual(values=cbPalette) +
+  theme_few()+
+  theme(aspect.ratio = 0.7,
+        axis.text = element_text(size=12))+
+  scale_y_continuous(breaks =c(-1,0,1))  +
+  #scale_y_discrete(breaks =NULL)
+  ylab("Estimate") +xlab("Mechanism")
+
+```
+
+```{r staticPrednt, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression model in each language.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\\% confidence intervals.
+Positive values indicate a positive relationship (e.g.
+longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
+words with higher frequency tend to have a lower AoA).", fig.width=10, fig.height=4}
+
+#legend <- get_legend(plot_static_preds_prod)
+
+#plot_noLegend <- plot_grid(plot_static_preds_prod + theme(legend.position="none"), NULL, plot_static_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+#plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))
+
+#plot_noLegend <- plot_grid(plot_static_preds_prod, NULL, plot_static_preds_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+#plot_grid(plot_noLegend)
+
+plot_static_preds_nt + theme(legend.position="bottom")
+
+```
+
+```{r}
+static_preds_all <- feather::read_feather("../saved_data/static_preds_all_nt.feather")
+
+static_preds_all$predictor <- plyr::mapvalues(static_preds_all$predictor, 
+                                 from = c("sem_deg","phono_deg","frequency", "length"), 
+                                 to = c("semEXT","phonoEXT","frequency", "length"))
+
+plot_static_preds_all_nt <- ggplot(static_preds_all, aes(x = predictor, y = Estimate)) +
+  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = Estimate, col = predictor, linetype=Test),
+                  position = position_dodge(width = .5),
+                  size = 0.5,
+                  fatten = 0.5)+
+  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
+  facet_wrap(~measure)  +
+  coord_flip() +
+  guides(colour=FALSE)+
+  scale_colour_manual(values=cbPalette)+
+  theme_few()+
+  theme(aspect.ratio = 0.7)
+
+ggsave("figs/plot_static_preds_all_nt.pdf", plot = plot_static_preds_all_nt, width = 6, height = 3)
+
+```
+
+```{r staticAllnt, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined model.
+Here the phonologocal networks were based on weighted edges between words.
+Results are shown for both production and comprehension data.
+Ranges indicate 95\\% confidence intervals.
+Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.", fig.width=6, fig.height=2.5}
+
+plot_static_preds_all_nt
+
+```
+
+\clearpage
+
+# Appendix B: Phonological connectivity across languages
+
+We were interested in investigating if, for a given meaning (e.g., "dog" in English and "chien" in French), phonological connectivity varied across languages.
+For example, if "dog" is highly connected in the English phonological network, will "chien" also be highly connected in the French network, or will these two forms be situated independently in their relative phonological networks?
+
+If the phonological networks are very similar across languages, then network growth in the phonological domain may not be an independent mechanism of acquisition, but rather an epiphenomenon of semantic-based learning.
+If, instead, the phonological connectivity is different from language to language, then this fact would lend support to phonological growth being an independent driving mechanism of early word learning.^[Note that this question can also be answered through the models in Figures 5 and 6 where we test both semantic and phonological connectivities.]
+
+To test this hypothesis, we compute the correlation of the unilemma's phonological connectivity between every pair of languages.
+In Figure \@ref(fig:corrPair), we plot the distribution of the pairwise pearson correlation coefficent.
+Generally speaking, languages are not highly correlated at the phonological level as the distributions peak at low values of r, showing that phonological connectivily is not (at least not fully) determined semantically.
+
+```{r corrPair, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "The distribution of the Pearson correlation coefficents of the unilemma's phonological connectivity between every pair of languages."}
+
+cor_data_t2 <- feather::read_feather("../saved_data/cor_data.feather")  %>%
+  mutate(distance = "edit=2")
+
+cor_data_t1 <- feather::read_feather("../saved_data/cor_data_t1.feather")  %>%
+  mutate(distance = "edit=1")
+
+cor_data_nt <- feather::read_feather("../saved_data/cor_data_nt.feather")  %>%
+  mutate(distance = "1/edit")
+
+cor_data_all <- cor_data_t2 %>%
+  bind_rows(cor_data_t1) %>%
+  bind_rows(cor_data_nt)
+
+ggplot(cor_data_all, 
+      aes(x = tau)) +
+  facet_grid(.~distance) +
+  geom_histogram(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
+                 alpha=0.5,
+                 binwidth=0.1)+
+  #scale_x_log10() +
+  theme_few() + 
+  theme(aspect.ratio = 0.7, legend.title = element_text(size=8)) +  #facet_grid(Segmentation ~ language)+
+  scale_y_continuous(labels = scales::percent)+
+  coord_cartesian(xlim=c(0,1))+
+  xlab("pairwise correlation") +ylab("Count")
+
+#plot_grid(plot_correlation_prod , NULL, plot_correlation_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))
+
+```
+
+\newpage
 

### 2019-09-20 journal/ms.tex
revisions

@@
 mean length of utterances in which the word occurs (e.g., Braginsky,
-Yurovsky, Marchman, \& Frank, in revision; Swingley \& Humphrey, 2018).
+Yurovsky, Marchman, \& Frank, 2019; D. Swingley \& Humphrey, 2018).
 
@@
 For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
-Thus, according to INT, node 1 is more likely to enter the lexicon.
+In this simplified example, candidate node 1 would connect to an internal node with 3 connections, thus we have $u_{INT}(node_1)= 3$.
+As for candidate node 2, it would connect to internal nodes that have only one connection each, making an average of 1, i.e., $u_{INT}(node_2)= 1$.
+According to INT, node 1 is more likely to enter the lexicon.
 For EXT, the utility of a candidate node is its degree in the entire network.
-According to EXT, node 2 is more likely to enter the lexicon next.
-This figure is based on an example from Hills et al (2009).}\label{fig:growth}
+In our example, candidate node 1 has 2 connections in total whereas candidate node 2 has 5 connections.
+So we have $u_{EXT}(node_1)= 2$ and $u_{EXT}(node_2)= 5$.
+Thus, according to EXT, node 2 is more likely to enter the lexicon next.
+This figure is based on an example from Hills et al.
+(2009).}\label{fig:growth}
 \end{figure}
@@
 depends, additionally, on the ease with which words are articulated,
-e.g., shorter words are produced earlier (Braginsky et al., in
-revision). By investigating comprehension-based vocabularies, we assess
-the extent to which the network growth mechanism captures general
-learning patterns beyond the specific constraints of production.
+e.g., shorter words are produced earlier (Braginsky et al., 2019). By
+investigating comprehension-based vocabularies, we assess the extent to
+which the network growth mechanism captures general learning patterns
+beyond the specific constraints of production.
 
@@
 this point in time to be each word's age of acquisition (Braginsky et
-al., in revision; J. C. Goodman et al., 2008).
+al., 2019; J. C. Goodman et al., 2008).
 
@@
 
-\caption{\label{tab:stats}Statistics for the dataset we used.}
+\caption{\label{tab:stats}Statistics for the dataset we used. The ages are in months.}
 \centering
@@
 EXT) across languages. However, we know that other factors influence
-learning as well (e.g., Braginsky et al., in revision). Next we
-investigated how semantic and phonological connectivity interact with
-two other factors. The first one is word frequency, a well studied
-factor shown to predict the age of acquisition in a reliable fashion
-(e.g. J. C. Goodman et al., 2008). The second factor is word length,
-which was shown to correlate with phonological connectivity: Shorter
-words are more likely to have higher connectivity (Pisoni, Nusbaum,
-Luce, \& Slowiaczek, 1985; Vitevitch \& Rodríguez, 2005).
+learning as well (e.g., Braginsky et al., 2019). Next we investigated
+how semantic and phonological connectivity interact with two other
+factors. The first one is word frequency, a well studied factor shown to
+predict the age of acquisition in a reliable fashion (e.g. J. C. Goodman
+et al., 2008). The second factor is word length, which was shown to
+correlate with phonological connectivity: Shorter words are more likely
+to have higher connectivity (Pisoni, Nusbaum, Luce, \& Slowiaczek, 1985;
+Vitevitch \& Rodríguez, 2005).
 
@@
 transcription. For word frequency, we used the frequency estimates from
-Braginsky et al. (in revision) where unigram counts were derived based
-on CHILDES corpora in each language (MacWhinney, 2014). Although these
+Braginsky et al. (2019) where unigram counts were derived based on
+CHILDES corpora in each language (MacWhinney, 2014). Although these
 frequency counts use transcripts from independent sets of children, they
@@
 both comprehension and production data and across languages, endorsing
-results for nouns across a variety of analyses (Braginsky et al., in
-revision; J. C. Goodman et al., 2008; B. C. Roy et al., 2015). Word
-length is more predictive for production than comprehension (and this
-difference is very clear in the global model), replicating previous work
-(Braginsky et al., in revision). Thus, word length seems to reflect the
-effects of production's constraints rather than comprehension's
-constraints, i.e., longer words are harder to articulate but they may
-not be significantly more difficult to store and access.
+results for nouns across a variety of analyses (Braginsky et al., 2019;
+J. C. Goodman et al., 2008; B. C. Roy et al., 2015). Word length is more
+predictive for production than comprehension (and this difference is
+very clear in the global model), replicating previous work (Braginsky et
+al., 2019). Thus, word length seems to reflect the effects of
+production's constraints rather than comprehension's constraints, i.e.,
+longer words are harder to articulate but they may not be significantly
+more difficult to store and access.
 
@@
 models to represent several distinct but phonologically neighboring
-words (Dell, Juliano, \& Govindjee, 1993; Takac, Knott, \& Stokes,
-2017).
+words (Dell, Juliano, \& Govindjee, 1993; Siew, 2013; Takac, Knott, \&
+Stokes, 2017). More generally, there is a growing interest in
+investigating precisely how the local patterns acquired through
+statistical learning may give rise to the global network orgnization
+(For a review, see Karuza, Thompson-Schill, \& Bassett, 2016).
 
@@
 
+This study investigated the class of nouns in isolation --- following
+previous studies investigating the early semantic and phonological
+network (Hills et al., 2009; Storkel, 2009). We could ask if studying
+one class separtaly is a legitimate research strategy. In other words,
+would word classes (such as nouns, verbs and function words) be acquired
+relatively differently, or would they interact substantially to the
+extent that it becomes unreasonable to study each class separately?
+
+We know that different word classes follow different time trajectories.
+For instance, in the early stages of development, nouns tend to be
+acquired at a higher pace than predicates and function words (Bates et
+al., 1994). Research has shown that this difference cannot be trivially
+attributed to differences in the degree to which these classes are
+present in the input; if anything, verbs and function words are often
+more frequent in the input than nouns (e.g., Gentner, 1982). J. C.
+Goodman et al. (2008) found an effect of frequency on the age of
+acquisition within --- not across --- classes. Further, a recent work by
+Braginsky et al. (2019) tested a large number of predictors, besides
+frequency, and found that these predictors do not influence the
+acquisition of word classes in the same way. For example, the
+acquisition of nouns was found to be most influenced by frequency and
+concreteness, whereas the acquisition of function words was most
+influenced by word length.
+
+These patterns support the hypothesis that different word classes have
+different pathways of learning, thus making it worthwhile to study each
+class separately. This hypothesis, however, does not preclude all sorts
+of inter-class interaction. For example, Dautriche, Swingley, and
+Christophe (2015) found that the acquisition of similar-sounding words
+(\enquote{bih}-\enquote{dih}) is easier if these words belong to
+different syntactic categories (e.g., a noun and a verb).
+
 This work shares a number of limitations with previous studies using
@@
 reliable (Fenson et al., 1994), and has allowed researchers to study
-important aspects of word learning (Braginsky et al., in revision; J. C.
+important aspects of word learning (Braginsky et al., 2019; J. C.
 Goodman et al., 2008; Hills et al., 2009; Stella et al., 2017; Storkel,
@@
 
-\section{Appendix}\label{appendix}
-
-\subsection{Edit 1}\label{edit-1}
+\vspace{1em}
+
+\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}}
+\vspace{1em}
+
+\section{Acknowledgements}\label{acknowledgements}
+
+This work was supported by a post-doctoral grant from the Fyssen
+Foundation, NSF \#1528526, and NSF \#1659585.
+
+\section{Disclosure statement}\label{disclosure-statement}
+
+None of the authors have any financial interest or a conflict of
+interest regarding this work and this submission.
+
+\clearpage
+
+\section{Appendix A: Analyses using different phnonological
+distances}\label{appendix-a-analyses-using-different-phnonological-distances}
+
+In the methods section, we based the choice of setting the threshold of
+edit distance at 2 on the fact that the early lexicon is very sparse in
+terms of phonological neighborhood; the early proposal that set the
+threshold at 1 (e.g., Vitevitch, 2008) was defined in the context of
+rather mature, dense lexicon. Increasing the threshold from 1 to 2
+allows for a more reasonable representation of the similarity space of
+the early phonological network.
+
+That said, it is useful to include the results obtained with both
+thresholds. In addition, it could be useful to compare the results to
+the case of weighted networks, i.e., with no thresholding. The main
+analyses for these two cases are shown in what follows. In summary, both
+methods of constructing the phonological networks had issues. While the
+fact of using edit = 1 created sparsity, using weighted networks created
+colinearity with length.
+
+\subsection{Analyses using phonological networks constructed with an
+edit distance of
+1}\label{analyses-using-phonological-networks-constructed-with-an-edit-distance-of-1}
+
+We show in Figure \ref{fig:corrPlot} the correlation between the
+phonological connectivity and age of acquisition in both comprehension
+and production. The sparsity issue, due the low phonological
+neighborhood in the children's lexicon is apparent: most words had 0
+degree and a few had non-zero but small degrees. The values of the
+correlations are much lower than the ones obtained with the threshold of
+2.
+
+The next figures show how the phonology-based mechanism of growth
+(phonoEXT) fares in comaprision to semEXT and other predictors of
+learing in each language (Figure \ref{fig:staticPredEdit1} and across
+all languages (Figure \ref{fig:staticAllEdit}). These figures show that
+phonoEXT based on edit distance 1 had no noticeable effect on learning.
 
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlot-1} \caption{Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network.
-Results are shown in each language for phonological and semantic networks.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlot-1} \caption{Age of acquistion in both comprehension and production as predicted by the degree (i.e., connectivity) in phonological network, using an edit distance of 1.
 Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlot}
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllEdit-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllEdit-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined model.
+Here the phonologocal networks were based on an edit distance of 1.
 Results are shown for both production and comprehension data.
@@
 
-\subsection{Continuous edit distance}\label{continuous-edit-distance}
+\subsection{Analyses using wighted phonological networks with no
+thresholding}\label{analyses-using-wighted-phonological-networks-with-no-thresholding}
+
+We constructed weighted phonological networks where the edge between a
+given pair of words \((w_1, w_2)\) was wieghted by
+\(\frac{1}{edit(w_1,w_2)}\). The phonological connectivity of a given
+word \(w\) was defined as the sum over all weighted edges with every
+other word \(w_i\) in the network, i.e.,
+\(\sum_{i} \frac{1}{edit(w,w_i)}\).
+
+The results were as follows. On the one hand, the correlations were
+generally high and in many cases (especially in the production data),
+higher than the ones obtained with the thresholds 2 and 1 (Figure
+\ref{fig:corrPlotnt}). On the other hand, phonoEXT resulted in very
+noisy estimates when we controlled for frequency and length (Figures
+\ref{fig:staticPrednt} and \ref{fig:staticAllnt}). The reason was that
+the new phonological connectivity was very highly correlated with
+length. The average correlation across languages was \(r =\) -0.95 for
+production data (compared to -0.29 and -0.60 for the phonological
+networks with edit = 1 and 2, respectvely). This fact lead to a
+collinearity issue in the regression, making the effect hard to
+estimate.
 
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllnt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllnt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined model.
+Here the phonologocal networks were based on weighted edges between words.
 Results are shown for both production and comprehension data.
@@
 
-\vspace{1em}
-
-\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}}
-\vspace{1em}
-
-\section{Acknowledgements}\label{acknowledgements}
-
-This work was supported by a post-doctoral grant from the Fyssen
-Foundation, NSF \#1528526, and NSF \#1659585.
-
-\section{Disclosure statement}\label{disclosure-statement}
-
-None of the authors have any financial interest or a conflict of
-interest regarding this work and this submission.
+\clearpage
+
+\section{Appendix B: Phonological connectivity across
+languages}\label{appendix-b-phonological-connectivity-across-languages}
+
+We were interested in investigating if, for a given meaning (e.g.,
+\enquote{dog} in English and \enquote{chien} in French), phonological
+connectivity varied across languages. For example, if \enquote{dog} is
+highly connected in the English phonological network, will
+\enquote{chien} also be highly connected in the French network, or will
+these two forms be situated independently in their relative phonological
+networks?
+
+If the phonological networks are very similar across languages, then
+network growth in the phonological domain may not be an independent
+mechanism of acquisition, but rather an epiphenomenon of semantic-based
+learning. If, instead, the phonological connectivity is different from
+language to language, then this fact would lend support to phonological
+growth being an independent driving mechanism of early word
+learning.\footnote{Note that this question can also be answered through
+  the models in Figures 5 and 6 where we test both semantic and
+  phonological connectivities.}
+
+To test this hypothesis, we compute the correlation of the unilemma's
+phonological connectivity between every pair of languages. In Figure
+\ref{fig:corrPair}, we plot the distribution of the pairwise pearson
+correlation coefficent. Generally speaking, languages are not highly
+correlated at the phonological level as the distributions peak at low
+values of r, showing that phonological connectivily is not (at least not
+fully) determined semantically.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPair-1} \caption{The distribution of the Pearson correlation coefficents of the unilemma's phonological connectivity between every pair of languages.}\label{fig:corrPair}
+\end{figure}
+
+\newpage
 
@@
 
+\hypertarget{ref-bates1994}{}
+Bates, E., Marchman, V., Thal, D., Fenson, L., Dale, P., Reznick, J. S.,
+\ldots{} Hartung, J. (1994). Developmental and stylistic variation in
+the composition of early vocabulary. \emph{Journal of Child Language},
+\emph{21}(1).
+
 \hypertarget{ref-beckage2016}{}
@@
 
-\hypertarget{ref-braginsky}{}
-Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (in
-revision). Consistency and variability in word learning across
-languages.
+\hypertarget{ref-braginsky2019}{}
+Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (2019).
+Consistency and variability in children?s word learning across
+languages. \emph{Open Mind}, \emph{3}.
 
@@
 
+\hypertarget{ref-dautriche2015}{}
+Dautriche, I., Swingley, D., \& Christophe, A. (2015). Learning novel
+phonological neighbors: Syntactic category matters. \emph{Cognition},
+\emph{143}.
+
 \hypertarget{ref-dell1993}{}
@@
 
+\hypertarget{ref-gentner1982}{}
+Gentner, D. (1982). Why nouns are learned before verbs: Linguistic
+relativity versus natural partitioning. \emph{Center for the Study of
+Reading Technical Report}.
+
 \hypertarget{ref-gillespie15}{}
@@
 
+\hypertarget{ref-karuza2016}{}
+Karuza, E. A., Thompson-Schill, S. L., \& Bassett, D. S. (2016). Local
+patterns to global architectures: Influences of network topology on
+human learning. \emph{Trends in Cognitive Sciences}, \emph{20}(8).
+
 \hypertarget{ref-kuhl1997}{}
@@
 
+\hypertarget{ref-siew2013}{}
+Siew, C. S. (2013). Community structure in the phonological network.
+\emph{Frontiers in Psychology}, \emph{4}.
+
 \hypertarget{ref-slobin2014}{}

### 2019-09-20 main_analyses.Rmd
revisions

@@
 
+```{r}
+
+phono_red <- feather::read_feather("saved_data/phono_red_nt.feather")
+
+data_by_lang <- phono_red %>%
+  filter(measure =="produces") %>%
+  split(.$language)
+
+pair_data <- function(lang1){
+
+  pair_cor_data <- function (lang2){
+
+  lang1_unilemmas <- unique(lang1$uni_lemma)
+  lang2_unilemmas <- unique(lang2$uni_lemma)
+
+  uni_intersect <-  intersect(lang1_unilemmas, lang2_unilemmas)
+
+  data_lang1 <- lang1 %>%
+    filter(!is.na(uni_lemma), 
+           !is.na(PAC_phono),
+           PAC_phono != "Inf",
+           uni_lemma %in% uni_intersect) %>%
+    select(uni_lemma, PAC_phono) %>%
+    group_by(uni_lemma) %>%
+    summarise(deg_lang1 = mean(PAC_phono))
+
+  data_lang2 <- lang2 %>%
+    filter(!is.na(uni_lemma), 
+           !is.na(PAC_phono),
+           PAC_phono != "Inf",
+           uni_lemma %in% uni_intersect) %>%
+    select(uni_lemma, PAC_phono) %>%
+    group_by(uni_lemma) %>%
+    summarise(deg_lang2 = mean(PAC_phono_t2))
+
+  both <- data_lang1 %>%
+    left_join(data_lang2)
+
+  mycorr <- cor.test(both$deg_lang1, both$deg_lang2)
+
+  val=mycorr$estimate
+  p=mycorr$p.value
+
+  language1 = unique(lang1$language) 
+  language2 = unique(lang2$language)
+
+  data.frame(language1=language1, language2=language2, tau=val, sig = p)
+
+  }
+  map(data_by_lang, pair_cor_data) %>%
+    bind_rows()
+}
+
+cor_data <- map(data_by_lang, pair_data) %>%
+  bind_rows() %>%
+  filter(language1!=language2) %>%
+  mutate(data="languages")
+
+#feather::write_feather(cor_data, "saved_data/cor_data.feather")
+cor_data <- feather::read_feather("saved_data/cor_data.feather")
+
+```
+
+plots
+```{r}
+
+ggplot(cor_data, 
+      aes(x = tau)) +
+  geom_histogram(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
+                 alpha=0.5,
+                 binwidth=0.1)+
+  #scale_x_log10() +
+  theme_few() + 
+  theme(aspect.ratio = 0.7, legend.title = element_text(size=8)) +  #facet_grid(Segmentation ~ language)+
+  scale_y_continuous(labels = scales::percent)+
+  xlab("pairwise correlation") +ylab("Count")
+
+```
+
 Here do Mantel tests
@@
 
+growth_by_meas_lang <- words_growth %>%
+  split(paste(.$measure, .$language))
+
 phono_net_fun <- function (growth_meas_lang) {
@@
   lang <- unique(growth_meas_lang$language)
-  #meas <- unique(growth_meas_lang$measure)
+  meas <- unique(growth_meas_lang$measure)
 
@@
   phono_pairs<- make_IPA_pairs(def_list = def_list, lang = lang) %>%
-    mutate(language = lang) %>%
+    mutate(language = lang, 
+           measure = meas) %>%
     left_join(item_unilemma) %>%
@@
 
-feather::write_feather(phono_pairs_all, "saved_data/phono_pairs_all.feather")
-
 phono_pairs_dist <- phono_pairs_all %>%
@@
 
+#phono_pairs_wide <- phono_pairs_dist %>%
+ # spread(language, dist)
 #Pairwise comparision: each time, take the overlap and do the test
 
-data_prod <- data_aoa %>%
-  filter(measure =='produces')
-
-data_by_lang <- split(phono_pairs_dist$language)
+phono_pairs_produce <- phono_pairs_dist %>%
+  filter(measure == "produces")
+
+data_by_lang <- phono_pairs_produce %>% 
+  split(.$language)
 
@@
 
-  lang1_unilemmas <- unique(lang1$uni_lemma)
-  lang2_unilemmas <- unique(lang2$uni_lemma)
+  lang1_unilemmas <- unique(lang1$item.uni_lemma)
+  lang2_unilemmas <- unique(lang2$item.uni_lemma)
+
   uni_intersect <-  intersect(lang1_unilemmas, lang2_unilemmas)
@@
   data_lang1 <- lang1 %>%
-    filter(!is.na(uni_lemma),
-           uni_lemma %in% uni_intersect) %>%
-    select(uni_lemma, aoa) %>%
-    group_by(uni_lemma) %>%
-    summarise(aoa1=mean(aoa))
+    filter(item.uni_lemma %in% uni_intersect,
+           pair.uni_lemma %in% uni_intersect) %>%
+    select(item.uni_lemma, pair.uni_lemma, link2) %>%
+    rename(link2_lang1 = link2)
+
+  data_lang2 <- lang2 %>%
+    filter(item.uni_lemma %in% uni_intersect,
+           pair.uni_lemma %in% uni_intersect) %>%
+    select(item.uni_lemma, pair.uni_lemma, link2) %>%
+    rename(link2_lang2 = link2)
+
+  data_both <- data_lang1 %>%
+    left_join(data_lang2)
+
+  #data_mat <- acast(data_both, item.uni_lemma~pair.uni_lemma, value.var="link2_lang1")
+
+  #This too costly computationnally speaking, will try the one-dimentional analysis instead, it should be enough
 
@@
     bind_rows()
-
-}
+}
+
+cor_data <- map(growth_by_meas_lang, pair_data) %>%
+  bind_rows() %>%
+  filter(language1!=language2) %>%
+  mutate(data="languages")
+
+```
+
+Here I will do the analysis for the power law (less computation-costly and more relant to the rest of the analyses)
+
+```{r}
 

### 2019-09-23 journal/ms.Rmd
new version

@@
 @markman90] to analyzing dense corpora capturing language learning in context [e.g., @roy2015].
-One prominent strategy consists in documenting the timeline of words' acquisition, and studying the properties that make words easy or hard to learn [e.g., @goodman2008; @huttenlocher1991].
+One prominent strategy consists in documenting the timeline of words' acquisition and studying the properties that make words easy or hard to learn [e.g., @goodman2008; @huttenlocher1991].
 For example, @goodman2008 found that, within a lexical category (e.g., nouns), higher parental frequency is associated with earlier learning.
@@
 
-Besides word-level properties, the structure of the lexicon (that is, how words relate to one another) is also linked to the the Age of Acquisition (AoA) of words.
+Besides word-level properties, the structure of the lexicon (that is, how words relate to one another) is also linked to the Age of Acquisition (AoA) of words.
 The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words [e.g., @collins1975; @luce1998].
-Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features [@mcrae2005], target-cue relationships in free association norms [@nelson1998], co-occurrence in child directed speech [@macwhinney2014], and phonological relatedness [@vitevitch2008].
+Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features [@mcrae2005], target-cue relationships in free association norms [@nelson1998], co-occurrence in child-directed speech [@macwhinney2014], and phonological relatedness [@vitevitch2008].
 These studies have generally found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @stella2017; @carlson2014].
@@
 Thus, the relevant network structure is not internally represented by children, and the observed connectivity effect might be an epiphenomenon of some properties of the linguistic input.
-For example, highly connected concrete nouns in the input could be more easily learned because of their contextual diversity, allowing for an easier meaning disambiguation [@smith2008; @mcmurray2012; @yurovsky2015].
+For example, highly connected concrete nouns in the input could be more easily learned because of their contextual diversity, allowing for easier meaning disambiguation [@smith2008; @mcmurray2012; @yurovsky2015].
 Another reason could be that these words are emphasized by the caregivers in their child-directed speech [@huttenlocher1991; @hoff2002; @clark2007].
@@
 The identity of the word that is going to be learned depends on the growth scenario.
-Here the squares indicate the node that drives growth in each scenario and the hand pointer indicates which word is likely to be learned.
-For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
-In this simplified example, candidate node 1 would connect to an internal node with 3 connections, thus we have $u_{INT}(node_1)= 3$.
+Here the squares indicate the node that drives growth in each scenario, and the hand pointer indicates which word is likely to be learned.
+For INT, the utility of a candidate external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
+In this simplified example, candidate node 1 would connect to an internal node with 3 connections; thus we have $u_{INT}(node_1)= 3$.
 As for candidate node 2, it would connect to internal nodes that have only one connection each, making an average of 1, i.e., $u_{INT}(node_2)= 1$.
@@
 For EXT, the utility of a candidate node is its degree in the entire network.
-In our example, candidate node 1 has 2 connections in total whereas candidate node 2 has 5 connections.
+In our example, candidate node 1 has 2 connections in total, whereas candidate node 2 has 5 connections.
 So we have $u_{EXT}(node_1)= 2$ and $u_{EXT}(node_2)= 5$.
@@
 These two networks represent different ways the mental lexicon is structured [@beckage2016].
-In particular, words that are neighbors in the semantic network (e.g., "cat", "dog") are not necessarily neighbors in the phonological network, and vice versa.
+In particular, words that are neighbors in the semantic network (e.g., cat, dog) are not necessarily neighbors in the phonological network and vice versa.
 Does the phonological network also predict word learning?
@@
 We used parent reports on the MacArthur-Bates Communicative Development Inventory and its cross-linguistic adaptations [@frank2017; @fenson94].
-We studied the timeline of word learning using the normative age of acquisition (i.e., the age at which at least 50% of children know a given words).
+We studied the timeline of word learning using the normative age of acquisition (i.e., the age at which at least 50% of children know a given word).
 Our choice of studying the normative learning trajectory rather than the individual trajectories was motivated by the nature of the dataset used---which is primarily based on cross-sectional studies.
@@
 First, we describe the datasets we used and explain how we constructed the networks.
-Second, we analyze static properties of words' connectivity in these networks (correlation with age of acquisition and shape of the distribution) and we explain how these properties inform hypotheses about network growth.
+Second, we analyze static properties of words' connectivity in these networks (correlation with age of acquisition and shape of the distribution), and we explain how these properties inform hypotheses about network growth.
 Next, we fit the two hypothesized growth mechanisms to the data.
@@
 This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target).
-For example, when given the word "ball", they might answer with the word "game".
-A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms.
+For example, when given the word "ball," they might answer with the word "game." A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms.
 The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target.\footnote{This choice was based on prior work by Hills et al.
@@
 In support of this approximation, @youn2016 showed that semantic networks across languages share substantial similarities.
-Furthermore, using the same association data across languages does not necessarily mean that the resulting networks will grow in a similar fashion.
-For instance, the set of words acquired by children as well as the order of word acquisition can vary from language to language leading to possibility different learning strategies.
+The fact that semantic associations are assumed to be shared across languages does not mean that the semantic networks will necessarily grow in a similar fashion.
+For instance, the set of words acquired by children as well as the order of word acquisition can vary from language to language leading to possibily different learning strategies.
 
@@
 
-To construct phonological networks we first mapped the orthographic transcription of words to their International Phonetic Alphabet (IPA) transcriptions in each language, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/)**.
+To construct phonological networks we first mapped the orthographic transcription of words to their International Phonetic Alphabet (IPA) transcriptions in each language, using the open-source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/)**.
 This software provides the correct IPA transcription if the word is found in a spelling-to-phonemes dictionary, otherwise it uses  language-specific pronunciation rules to generate an approximate phonetic transcription.
@@
 In previous studies, two nodes were linked if they had an edit distance of 1 [@storkel2009; @carlson2014; @stella2017].
-However, these studies reported a contribution of phonological connectivity to noun learning when networks were built using a rich adult vocabulary.
-Since the focus of the current study is on the mechanism of growth, the networks should be based on children's early vocabulary.
+However, these studies reported a contribution of phonological connectivity to noun learning when networks were built using a dense adult vocabulary.
+Since the focus of the current study is on the mechanism of growth, the networks are based on children's early vocabulary.
 The latter, however, contains very few noun pairs with an edit distance of 1.
-Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold.
-In both cases, the results were weaker than those obtained with a threshold of 2.
+To better represent the similarity space in the phonological domain, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{In Appendix A, we show the main results for phonological networks based on an edit distance of 1.
+We also show the results for phonological networks where the edges between pairs of words were weighted by the inverse of the edit distance.
 We did not consider the case of a threshold larger than 2 since many short pairs appear phonologically unrelated when the edit distance is 3 or more (e.g., "cat"/"dog").} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
@@
 First, we derived the optimal cut-off, $k_{min}$, above which the distribution is more likely to follow a power law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter $\alpha$.
-Second we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model.
+Second, we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model.
 The results are shown in Table \@ref(tab:powerLawProd) for production data, and in Table \@ref(tab:powerLawComp) for comprehension data.
@@
 \noindent where $\beta$ is a fitted parameter that captures the magnitude of the relationship between network parameters and growth (analogous to a regression coefficient).
-A positive value of $\beta$ means that words with higher utility values $u_i$ are acquired first, and a negative value means that words with lower utility values are acquired first (see Figure \@ref(fig:growth) for an illustration of how utilities values $u_i$ are defined in each growth scenario).
+A positive value of $\beta$ means that words with higher utility values $u_i$ are acquired first, and a negative value means that words with lower utility values are acquired first (see Figure \@ref(fig:growth) for an illustration of how utility values $u_i$ are defined in each growth scenario).
 The normalization includes all words that could be learned at that month.
@@
 This generalization was obtained in both the semantic^[One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
-However, our findings do not support this assumption, rather, it supports our initial approximation about the shared nature of the semantic similarity measure.
+However, our findings do not support this assumption; rather, it supports our initial approximation about the shared nature of the semantic similarity measure.
 That said, this approximation is not perfect.
-For example there is evidence that a small part of the variance in free association data can be explained by phonological similarity [@kachergis2011; @matusevych2018], thus leading to possibly minor cross-linguistic differences.] and phonological domains.
+For example, there is evidence that a small part of the variance in free association data can be explained by phonological similarity [@kachergis2011; @matusevych2018], thus leading to possibly minor cross-linguistic differences.] and phonological domains.
 
@@
 However, we know that other factors influence learning as well [e.g., @braginsky2019].
-Next we investigated how semantic and phonological connectivity interact with two other factors.
-The first one is word frequency, a well studied factor shown to predict the age of acquisition in a reliable fashion [e.g.
-@goodman2008].
+Next, we investigated how semantic and phonological connectivity interact with two other factors.
+The first one is word frequency, a well-studied factor shown to predict the age of acquisition in a reliable fashion [e.g., @goodman2008].
 The second factor is word length, which was shown to correlate with phonological connectivity: Shorter words are more likely to have higher connectivity [@pisoni1985; @vitevitch2005].
@@
 The latter was a requirement only for INT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.
-A more direct way to assess and compare the contribution of EXT in relation to other word-level factors is through conducting regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.
+A more direct way to assess and compare the contribution of EXT in relation to other word-level factors is through conducting regressions, where connectivity in the learning environment, frequency, and length predict the age of acquisition.
 
@@
 Crucially, children can learn these words without necessarily knowing the meaning of all other words with which they co-occur (hence the similarity with EXT).
-This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@stella2017; @hills2010].
-
-In the phonological case, network growth according to EXT is also compatible with a scenario whereby children are tracking low level statistical patterns, e.g., high probability sound sequences.
+This possibility is supported by the finding that words' diversity of occurrence in child-directed speech predicts their age of learning [@stella2017; @hills2010].
+
+In the phonological case, network growth according to EXT is also compatible with a scenario whereby children are tracking low-level statistical patterns, e.g., high probability sound sequences.
 Indeed, connectivity in the phonological network is inherently correlated with phonotactic probability [@vitevitch1999].
 That is, highly connected words tend to be made of frequent sound sequences.
-Children are sensitive to local phonotactic regularities [@jusczyk1994] and this sensitivity might lead them to learn higher-probability words more easily [@storkel2001].
+Children are sensitive to local phonotactic regularities [@jusczyk1994], and this sensitivity might lead them to learn higher-probability words more easily [@storkel2001].
 This explanation is supported by computational simulations that show how learning general phonotactics patterns create "well-worn paths" which allow the models to represent several distinct but phonologically neighboring words [@dell1993; @takac2017; @siew2013].
-More generally, there is a growing interest in investigating precisely how the local patterns acquired through statistical learning may give rise to the global network orgnization [For a review, see @karuza2016].
+More generally, there is a growing interest in investigating precisely how the local patterns acquired through statistical learning may give rise to the global network organization [For a review, see @karuza2016].
 
@@
 Perhaps the caregivers put more emphasis on the words that are highly connected in *their* mature lexical network.
-This emphasis would guide children to learn first these highly connected words even though children do not have access to the distribution of words' connectivity in the final network.
+This emphasis would guide children to learn first these highly connected words, even though children do not have access to the distribution of words' connectivity in the final network.
 Investigating this possibility would require further research on caregiver-child interaction [@macwhinney2014; @roy2015], examining what words are introduced over development and the extent to which children's uptake is influenced by this input [@huttenlocher1991; @clark2007; @hoff2002].
@@
 This study investigated the class of nouns in isolation --- following previous studies investigating the early semantic and phonological network [@hills2009; @storkel2009].
-We could ask if studying one class separtaly is a legitimate research strategy.
+We could ask if studying one class separately is a legitimate research strategy.
 In other words, would word classes (such as nouns, verbs and function words) be acquired relatively differently, or would they interact substantially to the extent that it becomes unreasonable to study each class separately?
 
-We know that different word classes follow different time trajectories.
-For instance, in the early stages of development, nouns tend to be acquired at a higher pace than predicates and function words [@bates1994].
+There are many observations that support the hypothesis that different word classes have different pathways of learning, making it worthwhile to study each class separately.
+For instance, different word classes follow different time trajectories: In the early stages of development, nouns tend to be acquired at a higher pace than predicates and function words [@bates1994].
 Research has shown that this difference cannot be trivially attributed to differences in the degree to which these classes are present in the input; if anything, verbs and function words are often more frequent in the input than nouns [e.g., @gentner1982].
 @goodman2008 found an effect of frequency on the age of acquisition within --- not across --- classes.
-Further, a recent work by @braginsky2019 tested a large number of predictors, besides frequency, and found that these predictors do not influence the acquisition of word classes in the same way.
+Further, recent work by @braginsky2019 tested a large number of predictors, besides frequency, and found that these predictors do not influence the acquisition of word classes in the same way.
 For example, the acquisition of nouns was found to be most influenced by frequency and concreteness, whereas the acquisition of function words was most influenced by word length.
-
-These patterns support the hypothesis that different word classes have different pathways of learning, thus making it worthwhile to study each class separately.
-This hypothesis, however, does not preclude all sorts of inter-class interaction.
-For example, @dautriche2015 found that the acquisition of similar-sounding words ("bih"-"dih") is easier if these words belong to different syntactic categories (e.g., a noun and a verb).
 
@@
 Although our study endorses, overall, the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT [@beckage].
-To illustrate, some children develop "islands of expertise", that is, well organized knowledge about a certain topic (e.g., birds or dinosaurs).
+To illustrate, some children develop "islands of expertise," that is, well-organized knowledge about a certain topic (e.g., birds or dinosaurs).
 This prior knowledge enables these children to learn new related words more easily [e.g., @chi1983].
@@
 In summary, both methods of constructing the phonological networks had issues.
-While the fact of using edit = 1 created sparsity, using weighted networks created colinearity with length.
+While the fact of using an edit distance of 1 created sparsity, using weighted networks created collinearity with length in the models.
 
@@
 We show in Figure \@ref(fig:corrPlot) the correlation between the phonological connectivity and age of acquisition in both comprehension and production.
-The sparsity issue, due the low phonological neighborhood in the children's lexicon is apparent: most words had 0 degree and a few had non-zero but small degrees.
+The sparsity issue --- due to the low phonological neighborhood in the children's lexicon --- is apparent: Most words had 0 connectivity, and a few had non-zero but small degrees.
 The values of the correlations are much lower than the ones obtained with the threshold of 2.
 
-The next figures show how the phonology-based mechanism of growth (phonoEXT) fares in comaprision to semEXT and other predictors of learing in each language (Figure \@ref(fig:staticPredEdit1) and across all languages (Figure \@ref(fig:staticAllEdit)).
+The next figures show how the phonology-based mechanism of growth (phonoEXT) fares in comaprison to semEXT and other predictors of learning in each language (Figure \@ref(fig:staticPredEdit1) and across all languages (Figure \@ref(fig:staticAllEdit)).
 These figures show that phonoEXT based on edit distance 1 had no noticeable effect on learning.
@@
 
-```{r corrPlot, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Age of acquistion in both comprehension and production as predicted by the degree (i.e., connectivity) in phonological network, using an edit distance of 1.
+```{r corrPlot, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Age of acquistion in both comprehension and production as predicted by the degree (i.e., connectivity) in the phonological networks, using an edit distance of 1.
 Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients."}
@@
 
-```{r staticPredEdit1, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression model in each language.
-Results are shown for both production and comprehension data.
+```{r staticPredEdit1, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression models.
+The phonologocal networks were based on an edit distance of 1.
 Ranges indicate 95\\% confidence intervals.
@@
 ```{r staticAllEdit, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined model.
-Here the phonologocal networks were based on an edit distance of 1.
-Results are shown for both production and comprehension data.
+The phonologocal networks were based on an edit distance of 1.
 Ranges indicate 95\\% confidence intervals.
@@
 
-## Analyses using wighted phonological networks with no thresholding
+## Analyses using weighted phonological networks with no thresholding
 
@@
 The reason was that the new phonological connectivity was very highly correlated with length.
-The average correlation across languages was $r =$ `r cor_phon_len_nt$ave[cor_phon_len_nt$measure == "produces"]` for production data (compared to `r cor_phon_len_edit1$ave[cor_phon_len_edit1$measure == "produces"]` and `r cor_phon_len_edit2$ave[cor_phon_len_edit2$measure == "produces"]` for the phonological networks with edit = 1 and 2, respectvely).
-This fact lead to a collinearity issue in the regression, making the effect hard to estimate.
-
-```{r corrPlotnt, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network.
-Results are shown in each language for phonological and semantic networks.
+The average correlation across languages was $r =$ `r cor_phon_len_nt$ave[cor_phon_len_nt$measure == "produces"]` for production data (compared to `r cor_phon_len_edit1$ave[cor_phon_len_edit1$measure == "produces"]` and `r cor_phon_len_edit2$ave[cor_phon_len_edit2$measure == "produces"]` for the phonological networks with an edit distance of 1 and 2, respectvely).
+This fact lead to a collinearity issue in the regression, making the effects hard to estimate and interpret.
+
+```{r corrPlotnt, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Age of acquistion in both comprehension and production as predicted by the connectivity in the phonological network, using weighted edges.
 Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients."}
@@
                                  to = c("production","comprehension"))
+
+static_preds$language <- plyr::mapvalues(static_preds$language, 
+                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
+                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))
 
@@
 
-```{r staticPrednt, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression model in each language.
-Results are shown for both production and comprehension data.
+```{r staticPrednt, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression models.
+In the phonological networks, the edges between pairs of words were weighted by the inverse of the edit distance.
 Ranges indicate 95\\% confidence intervals.
-Positive values indicate a positive relationship (e.g.
-longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
-words with higher frequency tend to have a lower AoA).", fig.width=10, fig.height=4}
+Positive values indicate a positive relationship (e.g., longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g., words with higher frequency tend to have a lower AoA).", fig.width=10, fig.height=4}
 
@@
 ```{r staticAllnt, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined model.
-Here the phonologocal networks were based on weighted edges between words.
-Results are shown for both production and comprehension data.
+In the phonological networks, the edges between pairs of words were weighted by the inverse of the edit distance.
 Ranges indicate 95\\% confidence intervals.
@@
 
-If the phonological networks are very similar across languages, then network growth in the phonological domain may not be an independent mechanism of acquisition, but rather an epiphenomenon of semantic-based learning.
-If, instead, the phonological connectivity is different from language to language, then this fact would lend support to phonological growth being an independent driving mechanism of early word learning.^[Note that this question can also be answered through the models in Figures 5 and 6 where we test both semantic and phonological connectivities.]
+If the phonological networks are very similar across languages, then network growth in the phonological domain may be deeply intertwined with growth in the semantic domain, rather than being an independent mechanism of acquisition.
+If, instead, the phonological connectivity is different from language to language, then this fact would lend support to phonological growth being an independent driving mechanism of early word learning.
 
 To test this hypothesis, we compute the correlation of the unilemma's phonological connectivity between every pair of languages.
-In Figure \@ref(fig:corrPair), we plot the distribution of the pairwise pearson correlation coefficent.
-Generally speaking, languages are not highly correlated at the phonological level as the distributions peak at low values of r, showing that phonological connectivily is not (at least not fully) determined semantically.
+In Figure \@ref(fig:corrPair), we plot the distribution of the pairwise Pearson correlation coefficient.
+Generally speaking, languages are not highly correlated at the phonological level as the distributions peak at low values of $r$, showing that phonological connectivity is not (at least not fully) determined semantically.
 

### 2019-09-23 journal/ms.tex
new version

@@
 Roy, 2015). One prominent strategy consists in documenting the timeline
-of words' acquisition, and studying the properties that make words easy
+of words' acquisition and studying the properties that make words easy
 or hard to learn (e.g., J. C. Goodman, Dale, \& Li, 2008; Huttenlocher,
@@
 mean length of utterances in which the word occurs (e.g., Braginsky,
-Yurovsky, Marchman, \& Frank, 2019; D. Swingley \& Humphrey, 2018).
+Yurovsky, Marchman, \& Frank, 2019; Swingley \& Humphrey, 2018).
 
 Besides word-level properties, the structure of the lexicon (that is,
-how words relate to one another) is also linked to the the Age of
+how words relate to one another) is also linked to the Age of
 Acquisition (AoA) of words. The lexical structure can be characterized
@@
 association norms (Nelson, McEvoy, \& Schreiber, 1998), co-occurrence in
-child directed speech (MacWhinney, 2014), and phonological relatedness
+child-directed speech (MacWhinney, 2014), and phonological relatedness
 (Vitevitch, 2008). These studies have generally found that children tend
@@
 concrete nouns in the input could be more easily learned because of
-their contextual diversity, allowing for an easier meaning
-disambiguation (McMurray, Horst, \& Samuelson, 2012; Smith \& Yu, 2008;
-Yurovsky \& Frank, 2015). Another reason could be that these words are
-emphasized by the caregivers in their child-directed speech (Clark,
-2007; Hoff \& Naigles, 2002; Huttenlocher et al., 1991).
+their contextual diversity, allowing for easier meaning disambiguation
+(McMurray, Horst, \& Samuelson, 2012; Smith \& Yu, 2008; Yurovsky \&
+Frank, 2015). Another reason could be that these words are emphasized by
+the caregivers in their child-directed speech (Clark, 2007; Hoff \&
+Naigles, 2002; Huttenlocher et al., 1991).
 
@@
 is structured (Beckage \& Colunga, 2016). In particular, words that are
-neighbors in the semantic network (e.g., \enquote{cat}, \enquote{dog})
-are not necessarily neighbors in the phonological network, and vice
-versa. Does the phonological network also predict word learning?
-Previous work has found an effect of words' connectivity in the
-phonological network on their age of learning (Carlson et al., 2014;
-Stella et al., 2017; Storkel, 2009). In other words, words learned
-earlier in life tend to sound similar to many other words than a word
-learned later in life. However, this finding is \emph{a priori}
-compatible with both INT and EXT, and previous studies did not
-explicitly compare these two mechanisms. Here, we investigate whether
-phonological networks, like semantic networks, grow through EXT, or if
-they rather grow via INT (Figure~\ref{fig:growth}).
+neighbors in the semantic network (e.g., cat, dog) are not necessarily
+neighbors in the phonological network and vice versa. Does the
+phonological network also predict word learning? Previous work has found
+an effect of words' connectivity in the phonological network on their
+age of learning (Carlson et al., 2014; Stella et al., 2017; Storkel,
+2009). In other words, words learned earlier in life tend to sound
+similar to many other words than a word learned later in life. However,
+this finding is \emph{a priori} compatible with both INT and EXT, and
+previous studies did not explicitly compare these two mechanisms. Here,
+we investigate whether phonological networks, like semantic networks,
+grow through EXT, or if they rather grow via INT
+(Figure~\ref{fig:growth}).
 
@@
 using the normative age of acquisition (i.e., the age at which at least
-50\% of children know a given words). Our choice of studying the
+50\% of children know a given word). Our choice of studying the
 normative learning trajectory rather than the individual trajectories
@@
 static properties of words' connectivity in these networks (correlation
-with age of acquisition and shape of the distribution) and we explain
+with age of acquisition and shape of the distribution), and we explain
 how these properties inform hypotheses about network growth. Next, we
@@
 word (the cue), and asking them to write the first word that comes to
-mind (the target). For example, when given the word \enquote{ball}, they
-might answer with the word \enquote{game}. A pair of nodes were
+mind (the target). For example, when given the word \enquote{ball,} they
+might answer with the word \enquote{game.} A pair of nodes were
 connected by a directed link from the cue to the target if there was a
@@
 this approximation, Youn et al. (2016) showed that semantic networks
-across languages share substantial similarities. Furthermore, using the
-same association data across languages does not necessarily mean that
-the resulting networks will grow in a similar fashion. For instance, the
-set of words acquired by children as well as the order of word
-acquisition can vary from language to language leading to possibility
-different learning strategies.
+across languages share substantial similarities. The fact that semantic
+associations are assumed to be shared across languages does not mean
+that the semantic networks will necessarily grow in a similar fashion.
+For instance, the set of words acquired by children as well as the order
+of word acquisition can vary from language to language leading to
+possibily different learning strategies.
 
@@
 transcription of words to their International Phonetic Alphabet (IPA)
-transcriptions in each language, using the open source text-to-speech
+transcriptions in each language, using the open-source text-to-speech
 software \textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}}.
@@
 However, these studies reported a contribution of phonological
-connectivity to noun learning when networks were built using a rich
+connectivity to noun learning when networks were built using a dense
 adult vocabulary. Since the focus of the current study is on the
-mechanism of growth, the networks should be based on children's early
+mechanism of growth, the networks are based on children's early
 vocabulary. The latter, however, contains very few noun pairs with an
-edit distance of 1. Thus, we increased the threshold from 1 to 2, that
-is, two nodes were related if their edit distance was equal to 1 or
-2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold.
-In both cases, the results were weaker than those obtained with a threshold of 2.
+edit distance of 1. To better represent the similarity space in the
+phonological domain, we increased the threshold from 1 to 2, that is,
+two nodes were related if their edit distance was equal to 1 or
+2.\footnote{In Appendix A, we show the main results for phonological networks based on an edit distance of 1.
+We also show the results for phonological networks where the edges between pairs of words were weighted by the inverse of the edit distance.
 We did not consider the case of a threshold larger than 2 since many short pairs appear phonologically unrelated when the edit distance is 3 or more (e.g., "cat"/"dog").}
@@
 law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}
-and we estimate the corresponding scaling parameter \(\alpha\). Second
+and we estimate the corresponding scaling parameter \(\alpha\). Second,
 we calculated the goodness-to-fit, which resulted in a \(p\)-value
@@
 acquired first (see Figure \ref{fig:growth} for an illustration of how
-utilities values \(u_i\) are defined in each growth scenario). The
+utility values \(u_i\) are defined in each growth scenario). The
 normalization includes all words that could be learned at that month.
@@
   effect of non-English semantic networks because of possible cultural
-  differences. However, our findings do not support this assumption,
+  differences. However, our findings do not support this assumption;
   rather, it supports our initial approximation about the shared nature
   of the semantic similarity measure. That said, this approximation is
-  not perfect. For example there is evidence that a small part of the
+  not perfect. For example, there is evidence that a small part of the
   variance in free association data can be explained by phonological
@@
 EXT) across languages. However, we know that other factors influence
-learning as well (e.g., Braginsky et al., 2019). Next we investigated
+learning as well (e.g., Braginsky et al., 2019). Next, we investigated
 how semantic and phonological connectivity interact with two other
-factors. The first one is word frequency, a well studied factor shown to
-predict the age of acquisition in a reliable fashion (e.g. J. C. Goodman
-et al., 2008). The second factor is word length, which was shown to
-correlate with phonological connectivity: Shorter words are more likely
-to have higher connectivity (Pisoni, Nusbaum, Luce, \& Slowiaczek, 1985;
-Vitevitch \& Rodríguez, 2005).
+factors. The first one is word frequency, a well-studied factor shown to
+predict the age of acquisition in a reliable fashion (e.g., J. C.
+Goodman et al., 2008). The second factor is word length, which was shown
+to correlate with phonological connectivity: Shorter words are more
+likely to have higher connectivity (Pisoni, Nusbaum, Luce, \&
+Slowiaczek, 1985; Vitevitch \& Rodríguez, 2005).
 
@@
 relation to other word-level factors is through conducting regressions,
-where connectivity in the learning environment, frequency and length
+where connectivity in the learning environment, frequency, and length
 predict the age of acquisition.
@@
 co-occur (hence the similarity with EXT). This possibility is supported
-by the finding that words' diversity of occurrence in child directed
+by the finding that words' diversity of occurrence in child-directed
 speech predicts their age of learning (Hills et al., 2010; Stella et
@@
 In the phonological case, network growth according to EXT is also
-compatible with a scenario whereby children are tracking low level
+compatible with a scenario whereby children are tracking low-level
 statistical patterns, e.g., high probability sound sequences. Indeed,
@@
 Children are sensitive to local phonotactic regularities (Jusczyk, Luce,
-\& Charles-Luce, 1994) and this sensitivity might lead them to learn
+\& Charles-Luce, 1994), and this sensitivity might lead them to learn
 higher-probability words more easily (Storkel, 2001). This explanation
@@
 investigating precisely how the local patterns acquired through
-statistical learning may give rise to the global network orgnization
+statistical learning may give rise to the global network organization
 (For a review, see Karuza, Thompson-Schill, \& Bassett, 2016).
@@
 mature lexical network. This emphasis would guide children to learn
-first these highly connected words even though children do not have
+first these highly connected words, even though children do not have
 access to the distribution of words' connectivity in the final network.
@@
 network (Hills et al., 2009; Storkel, 2009). We could ask if studying
-one class separtaly is a legitimate research strategy. In other words,
+one class separately is a legitimate research strategy. In other words,
 would word classes (such as nouns, verbs and function words) be acquired
@@
 
-We know that different word classes follow different time trajectories.
-For instance, in the early stages of development, nouns tend to be
-acquired at a higher pace than predicates and function words (Bates et
-al., 1994). Research has shown that this difference cannot be trivially
-attributed to differences in the degree to which these classes are
-present in the input; if anything, verbs and function words are often
-more frequent in the input than nouns (e.g., Gentner, 1982). J. C.
-Goodman et al. (2008) found an effect of frequency on the age of
-acquisition within --- not across --- classes. Further, a recent work by
-Braginsky et al. (2019) tested a large number of predictors, besides
-frequency, and found that these predictors do not influence the
+There are many observations that support the hypothesis that different
+word classes have different pathways of learning, making it worthwhile
+to study each class separately. For instance, different word classes
+follow different time trajectories: In the early stages of development,
+nouns tend to be acquired at a higher pace than predicates and function
+words (Bates et al., 1994). Research has shown that this difference
+cannot be trivially attributed to differences in the degree to which
+these classes are present in the input; if anything, verbs and function
+words are often more frequent in the input than nouns (e.g., Gentner,
+1982). J. C. Goodman et al. (2008) found an effect of frequency on the
+age of acquisition within --- not across --- classes. Further, recent
+work by Braginsky et al. (2019) tested a large number of predictors,
+besides frequency, and found that these predictors do not influence the
 acquisition of word classes in the same way. For example, the
@@
 influenced by word length.
-
-These patterns support the hypothesis that different word classes have
-different pathways of learning, thus making it worthwhile to study each
-class separately. This hypothesis, however, does not preclude all sorts
-of inter-class interaction. For example, Dautriche, Swingley, and
-Christophe (2015) found that the acquisition of similar-sounding words
-(\enquote{bih}-\enquote{dih}) is easier if these words belong to
-different syntactic categories (e.g., a noun and a verb).
 
@@
 Colunga, under review). To illustrate, some children develop
-\enquote{islands of expertise}, that is, well organized knowledge about
+\enquote{islands of expertise,} that is, well-organized knowledge about
 a certain topic (e.g., birds or dinosaurs). This prior knowledge enables
@@
 methods of constructing the phonological networks had issues. While the
-fact of using edit = 1 created sparsity, using weighted networks created
-colinearity with length.
+fact of using an edit distance of 1 created sparsity, using weighted
+networks created collinearity with length in the models.
 
@@
 phonological connectivity and age of acquisition in both comprehension
-and production. The sparsity issue, due the low phonological
-neighborhood in the children's lexicon is apparent: most words had 0
-degree and a few had non-zero but small degrees. The values of the
-correlations are much lower than the ones obtained with the threshold of
-2.
+and production. The sparsity issue --- due to the low phonological
+neighborhood in the children's lexicon --- is apparent: Most words had 0
+connectivity, and a few had non-zero but small degrees. The values of
+the correlations are much lower than the ones obtained with the
+threshold of 2.
 
 The next figures show how the phonology-based mechanism of growth
-(phonoEXT) fares in comaprision to semEXT and other predictors of
-learing in each language (Figure \ref{fig:staticPredEdit1} and across
+(phonoEXT) fares in comaprison to semEXT and other predictors of
+learning in each language (Figure \ref{fig:staticPredEdit1} and across
 all languages (Figure \ref{fig:staticAllEdit}). These figures show that
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlot-1} \caption{Age of acquistion in both comprehension and production as predicted by the degree (i.e., connectivity) in phonological network, using an edit distance of 1.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlot-1} \caption{Age of acquistion in both comprehension and production as predicted by the degree (i.e., connectivity) in the phonological networks, using an edit distance of 1.
 Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlot}
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPredEdit1-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression model in each language.
-Results are shown for both production and comprehension data.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPredEdit1-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression models.
+The phonologocal networks were based on an edit distance of 1.
 Ranges indicate 95\% confidence intervals.
@@
 \includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllEdit-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined model.
-Here the phonologocal networks were based on an edit distance of 1.
-Results are shown for both production and comprehension data.
+The phonologocal networks were based on an edit distance of 1.
 Ranges indicate 95\% confidence intervals.
@@
 
-\subsection{Analyses using wighted phonological networks with no
-thresholding}\label{analyses-using-wighted-phonological-networks-with-no-thresholding}
+\subsection{Analyses using weighted phonological networks with no
+thresholding}\label{analyses-using-weighted-phonological-networks-with-no-thresholding}
 
@@
 production data (compared to -0.29 and -0.60 for the phonological
-networks with edit = 1 and 2, respectvely). This fact lead to a
-collinearity issue in the regression, making the effect hard to
-estimate.
+networks with an edit distance of 1 and 2, respectvely). This fact lead
+to a collinearity issue in the regression, making the effects hard to
+estimate and interpret.
 
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlotnt-1} \caption{Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network.
-Results are shown in each language for phonological and semantic networks.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlotnt-1} \caption{Age of acquistion in both comprehension and production as predicted by the connectivity in the phonological network, using weighted edges.
 Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlotnt}
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPrednt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression model in each language.
-Results are shown for both production and comprehension data.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPrednt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression models.
+In the phonological networks, the edges between pairs of words were weighted by the inverse of the edit distance.
 Ranges indicate 95\% confidence intervals.
-Positive values indicate a positive relationship (e.g.
-longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
-words with higher frequency tend to have a lower AoA).}\label{fig:staticPrednt}
+Positive values indicate a positive relationship (e.g., longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g., words with higher frequency tend to have a lower AoA).}\label{fig:staticPrednt}
 \end{figure}
@@
 \includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllnt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined model.
-Here the phonologocal networks were based on weighted edges between words.
-Results are shown for both production and comprehension data.
+In the phonological networks, the edges between pairs of words were weighted by the inverse of the edit distance.
 Ranges indicate 95\% confidence intervals.
@@
 If the phonological networks are very similar across languages, then
-network growth in the phonological domain may not be an independent
-mechanism of acquisition, but rather an epiphenomenon of semantic-based
-learning. If, instead, the phonological connectivity is different from
-language to language, then this fact would lend support to phonological
-growth being an independent driving mechanism of early word
-learning.\footnote{Note that this question can also be answered through
-  the models in Figures 5 and 6 where we test both semantic and
-  phonological connectivities.}
+network growth in the phonological domain may be deeply intertwined with
+growth in the semantic domain, rather than being an independent
+mechanism of acquisition. If, instead, the phonological connectivity is
+different from language to language, then this fact would lend support
+to phonological growth being an independent driving mechanism of early
+word learning.
 
@@
 phonological connectivity between every pair of languages. In Figure
-\ref{fig:corrPair}, we plot the distribution of the pairwise pearson
-correlation coefficent. Generally speaking, languages are not highly
+\ref{fig:corrPair}, we plot the distribution of the pairwise Pearson
+correlation coefficient. Generally speaking, languages are not highly
 correlated at the phonological level as the distributions peak at low
-values of r, showing that phonological connectivily is not (at least not
-fully) determined semantically.
+values of \(r\), showing that phonological connectivity is not (at least
+not fully) determined semantically.
 
@@
 
-\hypertarget{ref-dautriche2015}{}
-Dautriche, I., Swingley, D., \& Christophe, A. (2015). Learning novel
-phonological neighbors: Syntactic category matters. \emph{Cognition},
-\emph{143}.
-
 \hypertarget{ref-dell1993}{}

### 2020-04-02 journal/ms.Rmd
final revisins

@@
 library(gridExtra)
-library(langcog)
+#library(langcog)
 library(ggthemes)
@@
   geom_jitter(#aes(colour = lexical_class),
-    colour = solarized_palette(1),
+    #colour = solarized_palette(1),
     size = 0.5, alpha = 0.5) +
@@
   nest() %>%
-  spread(domain, data) %>%
-  unnest(.sep = "_")
+  pivot_wider(names_from = domain, values_from = data) %>%
+  #spread(domain, data) %>%
+  unnest(names_sep = "_", cols = c(Phono, Sem))
 
@@
   nest() %>%
-  spread(domain, data) %>%
-  unnest(.sep = "_")
+  pivot_wider(names_from = domain, values_from = data) %>%
+  unnest(names_sep = "_", cols = c(Phono, Sem))
 

### 2020-04-02 journal/ms.tex
final revisins

@@
-\documentclass[english,floatsintext,man]{apa6}
-
+\documentclass[english,,man,floatsintext]{apa6}
+\usepackage{lmodern}
 \usepackage{amssymb,amsmath}
@@
     \usepackage{mathspec}
-    \usepackage{xltxtra,xunicode}
   \else
@@
   \fi
-  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
-  \newcommand{\euro}{€}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
 \fi
@@
 % use microtype if available
-\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={The growth of children's semantic and phonological networks: insight from 10 languages},
+            pdfkeywords={Word learning; semantic network; phonological network; network growth; cross-linguistic analysis.},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\fi
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
+
+  \title{The growth of children's semantic and phonological networks: insight from 10 languages}
+    \author{true \\ true \\ true}
+    \date{}
+
+% Manuscript styling
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
 
 % Table formatting
-\usepackage{longtable, booktabs}
+\usepackage{longtable}
 \usepackage{lscape}
@@
 %   {\end{threeparttable}\end{center}\end{landscape}}
-
-\newenvironment{lltable}
-  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
-  {\end{ThreePartTable}\end{center}\end{landscape}}
-
-% The following enables adjusting longtable caption width to table width
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
+% Enables adjusting longtable caption width to table width
 % Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
@@
 \setlength{\longtablewidth}{1in}
-\newcommand\getlongtablewidth{%
- \begingroup
-  \ifcsname LT@\roman{LT@tables}\endcsname
-  \global\longtablewidth=0pt
-  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
-  \@nameuse{LT@\roman{LT@tables}}%
-  \fi
-\endgroup}
-
-\ifxetex
-  \usepackage[setpagesize=false, % page size defined by xetex
-              unicode=false, % unicode breaks when used with xetex
-              xetex]{hyperref}
-\else
-  \usepackage[unicode=true]{hyperref}
-\fi
-\hypersetup{breaklinks=true,
-            pdfauthor={},
-            pdftitle={The growth of children's semantic and phonological networks: insight from 10 languages},
-            colorlinks=true,
-            citecolor=blue,
-            urlcolor=blue,
-            linkcolor=black,
-            pdfborder={0 0 0}}
-\urlstyle{same}  % don't use monospace font for urls
-
-\setlength{\parindent}{0pt}
-%\setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-
-\ifxetex
-  \usepackage{polyglossia}
-  \setmainlanguage{}
-\else
-  \usepackage[english]{babel}
-\fi
-
-% Manuscript styling
-\captionsetup{font=singlespacing,justification=justified}
-\usepackage{csquotes}
-\usepackage{upgreek}
-
- % Line numbering
-  \usepackage{lineno}
-  \linenumbers
-
-\usepackage{tikz} % Variable definition to generate author note
-
-% fix for \tightlist problem in pandoc 1.14
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% Essential manuscript parts
-  \title{The growth of children's semantic and phonological networks: insight
-from 10 languages}
-
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\makeatother
 \shorttitle{Lexical Development as Network Growth}
-
 \author{Abdellah Fourtassi\textsuperscript{1}, Yuan Bian\textsuperscript{2}, \& Michael C. Frank\textsuperscript{1}}
-
-  % \def\affdep{{"", "", ""}}%
-  % \def\affcity{{"", "", ""}}%
-
 \affiliation{
 \vspace{0.5cm}
-          \textsuperscript{1} Department of Psychology, Stanford University\\
-          \textsuperscript{2} Department of Brain and Cognitive Sciences, Massachusetts Institute of
-Technology  }
-
+\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology}
 \authornote{
@@
 
-    Correspondence concerning this article should be addressed to Abdellah
-    Fourtassi, Postal address. E-mail:
-    \href{mailto:afourtas@stanford.edu}{\nolinkurl{afourtas@stanford.edu}}
+Correspondence concerning this article should be addressed to Abdellah Fourtassi, Postal address. E-mail: afourtas@stanford.edu}
+\keywords{Word learning; semantic network; phonological network; network growth; cross-linguistic analysis.}
+\usepackage{lineno}
+
+\linenumbers
+\usepackage{csquotes}
+\usepackage[sortcites=false,sorting=none]{biblatex}
+
+\abstract{
+Children tend to produce words earlier when they are connected to a variety of other words along the phonological and semantic dimensions.
+Though these semantic and phonological connectivity effects have been extensively documented, little is known about their underlying developmental mechanism.
+One possibility is that learning is driven by lexical network growth where highly connected words in the child's early lexicon enable learning of similar words.
+Another possibility is that learning is driven by highly connected words in the external learning environment, instead of highly connected words in the early internal lexicon.
+The present study tests both scenarios systematically in both the phonological and semantic domains across 10 languages.
+We show that phonological and semantic connectivity in the learning environment drives growth in both production- and comprehension-based vocabularies, even controlling for word frequency and length.
+This pattern of findings suggests a word learning process where children harness their statistical learning abilities to detect and learn highly connected words in the learning environment.
 }
 
-  \abstract{Children tend to produce words earlier when they are connected to a
-variety of other words along the phonological and semantic dimensions.
-Though these semantic and phonological connectivity effects have been
-extensively documented, little is known about their underlying
-developmental mechanism. One possibility is that learning is driven by
-lexical network growth where highly connected words in the child's early
-lexicon enable learning of similar words. Another possibility is that
-learning is driven by highly connected words in the external learning
-environment, instead of highly connected words in the early internal
-lexicon. The present study tests both scenarios systematically in both
-the phonological and semantic domains across 10 languages. We show that
-phonological and semantic connectivity in the learning environment
-drives growth in both production- and comprehension-based vocabularies,
-even controlling for word frequency and length. This pattern of findings
-suggests a word learning process where children harness their
-statistical learning abilities to detect and learn highly connected
-words in the learning environment.}
-  \keywords{Word learning; semantic network; phonological network; network growth;
-cross-linguistic analysis. \\
-
-  }
-
-  \usepackage[sortcites=false,sorting=none]{biblatex}
-
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proposition}{Proposition}
-\theoremstyle{definition}
-\newtheorem{example}{Example}
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
 \begin{document}
-
 \maketitle
 
-\setcounter{secnumdepth}{0}
-
-\section{Introduction}\label{introduction}
-
-What factors shape vocabulary learning over the course of early
-childhood? To investigate this question, scientists have adopted
-multiple research strategies, from conducting controlled laboratory
-experiments (e.g. Markman, 1990) to analyzing dense corpora capturing
-language learning in context (e.g., B. C. Roy, Frank, DeCamp, Miller, \&
-Roy, 2015). One prominent strategy consists in documenting the timeline
-of words' acquisition and studying the properties that make words easy
-or hard to learn (e.g., J. C. Goodman, Dale, \& Li, 2008; Huttenlocher,
-Haight, Bryk, Seltzer, \& Lyons, 1991). For example, J. C. Goodman et
-al. (2008) found that, within a lexical category (e.g., nouns), higher
-parental frequency is associated with earlier learning. Researchers have
-studied the role of several other factors such as word length and the
-mean length of utterances in which the word occurs (e.g., Braginsky,
-Yurovsky, Marchman, \& Frank, 2019; Swingley \& Humphrey, 2018).
-
-Besides word-level properties, the structure of the lexicon (that is,
-how words relate to one another) is also linked to the Age of
-Acquisition (AoA) of words. The lexical structure can be characterized
-in terms of a network where each node represents a word in the
-vocabulary, and each link between two nodes represents a relationship
-between the corresponding pair of words (e.g., Collins \& Loftus, 1975;
-Luce \& Pisoni, 1998). Previous studies have investigated early
-vocabulary structure by constructing networks using a variety of
-word-word relations including shared semantic features (McRae, Cree,
-Seidenberg, \& McNorgan, 2005), target-cue relationships in free
-association norms (Nelson, McEvoy, \& Schreiber, 1998), co-occurrence in
-child-directed speech (MacWhinney, 2014), and phonological relatedness
-(Vitevitch, 2008). These studies have generally found that children tend
-to produce words that have higher neighborhood density (i.e., high
-connectivity in the network) earlier, both at the phonological and the
-semantic level (Carlson, Sonderegger, \& Bane, 2014; Hills, Maouene,
-Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya, \& Smith, 2009;
-Stella, Beckage, \& Brede, 2017; Storkel, 2009).
-
-While most studies have focused on the static properties of the lexical
-network, a few have investigated the underlying developmental process.
-In particular, Steyvers and Tenenbaum (2005) suggested that the observed
-effects of connectivity are the consequence of how the lexical network
-gets constructed in the child's mind. According to this explanation,
-known as Preferential Attachment, highly connected words in the child's
-lexicon tend to \enquote{attract} more words over time, in a
-rich-get-richer scenario (Barabasi \& Albert, 1999). In other words,
-what predicts learning is the \emph{internal} connectivity in the
-child's early lexicon. In contrast, Hills et al. (2009) suggested that
-what biases the learning is not the connectivity in the child's internal
-lexicon but, rather, \emph{external} connectivity in the learning
-environment. They called this alternative explanation Preferential
-Acquisition. For clarity of reading, we will call preferential
-attachment the Internally-driven mechanism (INT), and preferential
-acquisition the Externally-driven mechanism (EXT).
-Figure~\ref{fig:growth} shows an illustration of both growth scenarios
-with the same simplified network.
-
-These two proposals represent two divergent ideas about the role of
-lexical networks in acquisition. On the INT proposal, learning is driven
-by known words with high connectivity to other known words (Figure 1,
-left). Thus, the network structure is a causal factor in word learning,
-that is, children rely on the organization of their past knowledge to
-determine future learning (Altvater-Mackensen \& Mani, 2013; Borovsky,
-Ellis, Evans, \& Elman, 2016; Chi \& Koeske, 1983; Storkel, 2009). In
-contrast, on the EXT approach, learning is driven by the connectivity of
-words that are not known yet (Figure 1, right). Thus, the relevant
-network structure is not internally represented by children, and the
-observed connectivity effect might be an epiphenomenon of some
-properties of the linguistic input. For example, highly connected
-concrete nouns in the input could be more easily learned because of
-their contextual diversity, allowing for easier meaning disambiguation
-(McMurray, Horst, \& Samuelson, 2012; Smith \& Yu, 2008; Yurovsky \&
-Frank, 2015). Another reason could be that these words are emphasized by
-the caregivers in their child-directed speech (Clark, 2007; Hoff \&
-Naigles, 2002; Huttenlocher et al., 1991).
+\#Introduction
+
+What factors shape vocabulary learning over the course of early childhood?
+To investigate this question, scientists have adopted multiple research strategies, from conducting controlled laboratory experiments (e.g.
+Markman, 1990) to analyzing dense corpora capturing language learning in context (e.g., Roy, Frank, DeCamp, Miller, \& Roy, 2015).
+One prominent strategy consists in documenting the timeline of words' acquisition and studying the properties that make words easy or hard to learn (e.g., Goodman, Dale, \& Li, 2008; Huttenlocher, Haight, Bryk, Seltzer, \& Lyons, 1991).
+For example, Goodman et al.
+(2008) found that, within a lexical category (e.g., nouns), higher parental frequency is associated with earlier learning.
+Researchers have studied the role of several other factors such as word length and the mean length of utterances in which the word occurs (e.g., Braginsky, Yurovsky, Marchman, \& Frank, 2019; Swingley \& Humphrey, 2018).
+
+Besides word-level properties, the structure of the lexicon (that is, how words relate to one another) is also linked to the Age of Acquisition (AoA) of words.
+The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words (e.g., Collins \& Loftus, 1975; Luce \& Pisoni, 1998).
+Previous studies have investigated early vocabulary structure by constructing networks using a variety of word-word relations including shared semantic features (McRae, Cree, Seidenberg, \& McNorgan, 2005), target-cue relationships in free association norms (Nelson, McEvoy, \& Schreiber, 1998), co-occurrence in child-directed speech (MacWhinney, 2014), and phonological relatedness (Vitevitch, 2008).
+These studies have generally found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level (Carlson, Sonderegger, \& Bane, 2014; Hills, Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Stella, Beckage, \& Brede, 2017; Storkel, 2009).
+
+While most studies have focused on the static properties of the lexical network, a few have investigated the underlying developmental process.
+In particular, Steyvers \& Tenenbaum (2005) suggested that the observed effects of connectivity are the consequence of how the lexical network gets constructed in the child's mind.
+According to this explanation, known as Preferential Attachment, highly connected words in the child's lexicon tend to \enquote{attract} more words over time, in a rich-get-richer scenario (Barabasi \& Albert, 1999).
+In other words, what predicts learning is the \emph{internal} connectivity in the child's early lexicon.
+In contrast, Hills et al.
+(2009) suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, \emph{external} connectivity in the learning environment.
+They called this alternative explanation Preferential Acquisition.
+For clarity of reading, we will call preferential attachment the Internally-driven mechanism (INT), and preferential acquisition the Externally-driven mechanism (EXT).
+Figure~\ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network.
+
+These two proposals represent two divergent ideas about the role of lexical networks in acquisition.
+On the INT proposal, learning is driven by known words with high connectivity to other known words (Figure 1, left).
+Thus, the network structure is a causal factor in word learning, that is, children rely on the organization of their past knowledge to determine future learning (Altvater-Mackensen \& Mani, 2013; Borovsky, Ellis, Evans, \& Elman, 2016; Chi \& Koeske, 1983; Storkel, 2009).
+In contrast, on the EXT approach, learning is driven by the connectivity of words that are not known yet (Figure 1, right).
+Thus, the relevant network structure is not internally represented by children, and the observed connectivity effect might be an epiphenomenon of some properties of the linguistic input.
+For example, highly connected concrete nouns in the input could be more easily learned because of their contextual diversity, allowing for easier meaning disambiguation (McMurray, Horst, \& Samuelson, 2012; Smith \& Yu, 2008; Yurovsky \& Frank, 2015).
+Another reason could be that these words are emphasized by the caregivers in their child-directed speech (Clark, 2007; Hoff \& Naigles, 2002; Huttenlocher et al., 1991).
 
@@
 
-Hills et al. (2009) investigated the growth of lexico-semantic networks
-in toddlers and found that growth did not proceed according to INT as
-was originally hypothesized by Steyvers and Tenenbaum (2005), but rather
-according to
-EXT.\footnote{Besides INT and EXT, the authors tested a third mechanism (called the lure of associates) which resembles EXT in that it is driven by the connectivity of external nodes, except that this connectivity is computed with respect to words that are known.
-However, EXT is the externally-driven scenario that best predicted the data in this previous work.}
-This is an important finding because it suggests that learning in the
-early stages is mostly driven by properties of the external input,
-regardless of how past knowledge is organized. However, this work
-explored the INT/EXT growth in a special case: networks that were based
-on 1) semantic associations, 2) production-based vocabularies, and 3)
-data from English-learning children, only. The extent to which this
-result depends on the domain (e.g., semantic vs.~phonological
-connectivity), the vocabulary measure (production vs.~comprehension) and
-culture/language is thus an open area for investigation (Hills \& Siew,
-2018). In this work, we test the generality of prior findings along
-these three dimensions.
-
-First, we study the phonological network in addition to the semantic
-network. These two networks represent different ways the mental lexicon
-is structured (Beckage \& Colunga, 2016). In particular, words that are
-neighbors in the semantic network (e.g., cat, dog) are not necessarily
-neighbors in the phonological network and vice versa. Does the
-phonological network also predict word learning? Previous work has found
-an effect of words' connectivity in the phonological network on their
-age of learning (Carlson et al., 2014; Stella et al., 2017; Storkel,
-2009). In other words, words learned earlier in life tend to sound
-similar to many other words than a word learned later in life. However,
-this finding is \emph{a priori} compatible with both INT and EXT, and
-previous studies did not explicitly compare these two mechanisms. Here,
-we investigate whether phonological networks, like semantic networks,
-grow through EXT, or if they rather grow via INT
-(Figure~\ref{fig:growth}).
-
-Second, we study vocabularies measured using both comprehension and
-production. Previous studies have found differences between these
-vocabularies in terms of their content and rate of acquisition (Bates,
-Dale, \& Thal, 1995; Benedict, 1979; Fenson et al., 1994). These
-differences may reflect the fact that comprehension and production do
-not share the same constraints. For instance, whereas comprehension
-depends on the ease with which words are stored and accessed, production
-depends, additionally, on the ease with which words are articulated,
-e.g., shorter words are produced earlier (Braginsky et al., 2019). By
-investigating comprehension-based vocabularies, we assess the extent to
-which the network growth mechanism captures general learning patterns
-beyond the specific constraints of production.
-
-Finally, we use developmental data in 10 languages. Lexical networks can
-show more or less cross-linguistic variability along both the semantic
-and phonological domains (Arbesman, Strogatz, \& Vitevitch, 2010; Lupyan
-\& Lewis, 2017; Youn et al., 2016). Besides, cultures might differ in
-the way caregivers talk to children (Cristia, Dupoux, Gurven, \&
-Stieglitz, 2017; Kuhl et al., 1997), and this difference in the input
-could influence the way in which the children's networks grow. Thus,
-cross-linguistic comparison is crucial to test the extent to which
-growth mechanisms are equally engaged across a wider variety of cultures
-compared with the extent to which the growth mechanisms are specific to
-patterns of learning that emerge due to the particulars of a given
-language or culture (Bates \& MacWhinney, 1987; Slobin, 2014).
-
-We adopted the following research strategy. We used parent reports on
-the MacArthur-Bates Communicative Development Inventory and its
-cross-linguistic adaptations (Fenson et al., 1994; Frank, Braginsky,
-Yurovsky, \& Marchman, 2017). We studied the timeline of word learning
-using the normative age of acquisition (i.e., the age at which at least
-50\% of children know a given word). Our choice of studying the
-normative learning trajectory rather than the individual trajectories
-was motivated by the nature of the dataset used---which is primarily
-based on cross-sectional studies. Children may vary in their individual
-learning trajectories, but the aggregate data provide highly robust
-measures of the average learning patterns (Fenson et al., 1994). The use
-of such measures has lead to important insights on the mechanisms of
-word learning (J. C. Goodman et al., 2008; Hills et al., 2010, 2009;
-Stella et al., 2017; Storkel, 2009).
-
-The paper is organized as follows. First, we describe the datasets we
-used and explain how we constructed the networks. Second, we analyze
-static properties of words' connectivity in these networks (correlation
-with age of acquisition and shape of the distribution), and we explain
-how these properties inform hypotheses about network growth. Next, we
-fit the two hypothesized growth mechanisms to the data. We investigate
-the extent to which the results obtained in Hills et al. (2009)
-generalize to phonological networks and comprehension-based
-vocabularies, and whether this generalization holds
-cross-linguistically.
-
-\section{Networks}\label{networks}
-
-\subsection{Data}\label{data}
-
-We used data from Wordbank (Frank et al., 2017), an open repository
-aggregating cross-linguistic language developmental data of the
-MacArthur-Bates Communicative Development Inventory (CDI), a parent
-report vocabulary checklist. Parent report is a reliable and valid
-measure of children's vocabulary that allows for the cost-effective
-collection of datasets large enough to test network-based models of
-acquisition (Fenson et al., 1994). When filling out a CDI form,
-caregivers are either invited to indicate whether their child
-\enquote{understands} (comprehension) or \enquote{understands and says}
-(production) each of about 400-700 words. For younger children (e.g., 8
-to 18 months in the English data), both comprehension and production are
-queried, whereas for older children (16 to 36 months) only production is
-queried. Due to these limitations, we use data from younger children to
-test comprehension and data from older children to test production. In
-addition, following previous studies (Hills et al., 2009; Storkel,
-2009), we restricted our analysis to the category of nouns due to the
-fact that nouns predominate the early expressive and receptive lexicons
-(Bates et al., 1995). Their larger sample size (compared, for example,
-to verbs or adjectives) is more suited to the network-based analysis of
-development. Table \ref{tab:stats} gives an overview of the data we
-used.
-
-\subsection{Age of acquisition}\label{age-of-acquisition}
-
-For each word in the CDI data, we compute the proportion of children who
-understand or produce the word at each month. Then we fit a logistic
-curve to these proportions and determined when the curve crosses 0.5,
-i.e., the age at which at least 50\% of children know the word. We take
-this point in time to be each word's age of acquisition (Braginsky et
-al., 2019; J. C. Goodman et al., 2008).
+Hills et al.
+(2009) investigated the growth of lexico-semantic networks in toddlers and found that growth did not proceed according to INT as was originally hypothesized by Steyvers \& Tenenbaum (2005), but rather according to EXT.\footnote{Besides INT and EXT, the authors tested a third mechanism (called the lure of associates) which resembles EXT in that it is driven by the connectivity of external nodes, except that this connectivity is computed with respect to words that are known.
+However, EXT is the externally-driven scenario that best predicted the data in this previous work.} This is an important finding because it suggests that learning in the early stages is mostly driven by properties of the external input, regardless of how past knowledge is organized.
+However, this work explored the INT/EXT growth in a special case: networks that were based on 1) semantic associations, 2) production-based vocabularies, and 3) data from English-learning children, only.
+The extent to which this result depends on the domain (e.g., semantic vs.~phonological connectivity), the vocabulary measure (production vs.~comprehension) and culture/language is thus an open area for investigation (Hills \& Siew, 2018).
+In this work, we test the generality of prior findings along these three dimensions.
+
+First, we study the phonological network in addition to the semantic network.
+These two networks represent different ways the mental lexicon is structured (Beckage \& Colunga, 2016).
+In particular, words that are neighbors in the semantic network (e.g., cat, dog) are not necessarily neighbors in the phonological network and vice versa.
+Does the phonological network also predict word learning?
+Previous work has found an effect of words' connectivity in the phonological network on their age of learning (Carlson et al., 2014; Stella et al., 2017; Storkel, 2009).
+In other words, words learned earlier in life tend to sound similar to many other words than a word learned later in life.
+However, this finding is \emph{a priori} compatible with both INT and EXT, and previous studies did not explicitly compare these two mechanisms.
+Here, we investigate whether phonological networks, like semantic networks, grow through EXT, or if they rather grow via INT (Figure~\ref{fig:growth}).
+
+Second, we study vocabularies measured using both comprehension and production.
+Previous studies have found differences between these vocabularies in terms of their content and rate of acquisition (Bates, Dale, \& Thal, 1995; Benedict, 1979; Fenson et al., 1994).
+These differences may reflect the fact that comprehension and production do not share the same constraints.
+For instance, whereas comprehension depends on the ease with which words are stored and accessed, production depends, additionally, on the ease with which words are articulated, e.g., shorter words are produced earlier (Braginsky et al., 2019).
+By investigating comprehension-based vocabularies, we assess the extent to which the network growth mechanism captures general learning patterns beyond the specific constraints of production.
+
+Finally, we use developmental data in 10 languages.
+Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains (Arbesman, Strogatz, \& Vitevitch, 2010; Lupyan \& Lewis, 2017; Youn et al., 2016).
+Besides, cultures might differ in the way caregivers talk to children (Cristia, Dupoux, Gurven, \& Stieglitz, 2017; Kuhl et al., 1997), and this difference in the input could influence the way in which the children's networks grow.
+Thus, cross-linguistic comparison is crucial to test the extent to which growth mechanisms are equally engaged across a wider variety of cultures compared with the extent to which the growth mechanisms are specific to patterns of learning that emerge due to the particulars of a given language or culture (Bates \& MacWhinney, 1987; Slobin, 2014).
+
+We adopted the following research strategy.
+We used parent reports on the MacArthur-Bates Communicative Development Inventory and its cross-linguistic adaptations (Fenson et al., 1994; Frank, Braginsky, Yurovsky, \& Marchman, 2017).
+We studied the timeline of word learning using the normative age of acquisition (i.e., the age at which at least 50\% of children know a given word).
+Our choice of studying the normative learning trajectory rather than the individual trajectories was motivated by the nature of the dataset used---which is primarily based on cross-sectional studies.
+Children may vary in their individual learning trajectories, but the aggregate data provide highly robust measures of the average learning patterns (Fenson et al., 1994).
+The use of such measures has lead to important insights on the mechanisms of word learning (Goodman et al., 2008; Hills et al., 2010, 2009; Stella et al., 2017; Storkel, 2009).
+
+The paper is organized as follows.
+First, we describe the datasets we used and explain how we constructed the networks.
+Second, we analyze static properties of words' connectivity in these networks (correlation with age of acquisition and shape of the distribution), and we explain how these properties inform hypotheses about network growth.
+Next, we fit the two hypothesized growth mechanisms to the data.
+We investigate the extent to which the results obtained in Hills et al.
+(2009) generalize to phonological networks and comprehension-based vocabularies, and whether this generalization holds cross-linguistically.
+
+\hypertarget{networks}{%
+\section{Networks}\label{networks}}
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
+
+We used data from Wordbank (Frank et al., 2017), an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist.
+Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition (Fenson et al., 1994).
+When filling out a CDI form, caregivers are either invited to indicate whether their child \enquote{understands} (comprehension) or \enquote{understands and says} (production) each of about 400-700 words.
+For younger children (e.g., 8 to 18 months in the English data), both comprehension and production are queried, whereas for older children (16 to 36 months) only production is queried.
+Due to these limitations, we use data from younger children to test comprehension and data from older children to test production.
+In addition, following previous studies (Hills et al., 2009; Storkel, 2009), we restricted our analysis to the category of nouns due to the fact that nouns predominate the early expressive and receptive lexicons (Bates et al., 1995).
+Their larger sample size (compared, for example, to verbs or adjectives) is more suited to the network-based analysis of development.
+Table \ref{tab:stats} gives an overview of the data we used.
+
+\hypertarget{age-of-acquisition}{%
+\subsection{Age of acquisition}\label{age-of-acquisition}}
+
+For each word in the CDI data, we compute the proportion of children who understand or produce the word at each month.
+Then we fit a logistic curve to these proportions and determined when the curve crosses 0.5, i.e., the age at which at least 50\% of children know the word.
+We take this point in time to be each word's age of acquisition (Braginsky et al., 2019; Goodman et al., 2008).
 
@@
 \multicolumn{1}{c}{} & \multicolumn{3}{c}{Comprehension} & \multicolumn{3}{c}{Production} \\
-\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
+\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
 Language & Nouns & Ages & N & Nouns & Ages & N\\
@@
 
-\subsection{Semantic networks}\label{semantic-networks}
-
-We constructed semantic networks for English data following the
-procedure outlined in Hills et al. (2009), as follows. We used as an
-index of semantic relatedness the Florida Free Association Norms (Nelson
-et al., 1998). This dataset was collected by giving adult participants a
-word (the cue), and asking them to write the first word that comes to
-mind (the target). For example, when given the word \enquote{ball,} they
-might answer with the word \enquote{game.} A pair of nodes were
-connected by a directed link from the cue to the target if there was a
-cue-target relationship between these nodes in the association norms.
-The connectivity of a given node was characterized by its
-\emph{indegree}: the number of links for which the word was the
-target.\footnote{This choice was based on prior work by Hills et al.
-(2009) stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated with indegree.}
-To model growth from month to month, we constructed a different network
-at each month, based on the nouns that have been acquired by that month.
-
-Since the free association norms are available only in English, we used
-the hand-checked translation equivalents available in Wordbank, which
-allowed us to use the English association norms across 10 languages.
-Semantic associations are not necessarily shared across languages, but
-we use this technique as a reasonable first approximation. In support of
-this approximation, Youn et al. (2016) showed that semantic networks
-across languages share substantial similarities. The fact that semantic
-associations are assumed to be shared across languages does not mean
-that the semantic networks will necessarily grow in a similar fashion.
-For instance, the set of words acquired by children as well as the order
-of word acquisition can vary from language to language leading to
-possibily different learning strategies.
-
-\subsection{Phonological networks}\label{phonological-networks}
-
-To construct phonological networks we first mapped the orthographic
-transcription of words to their International Phonetic Alphabet (IPA)
-transcriptions in each language, using the open-source text-to-speech
-software \textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}}.
-This software provides the correct IPA transcription if the word is
-found in a spelling-to-phonemes dictionary, otherwise it uses
-language-specific pronunciation rules to generate an approximate
-phonetic transcription. We used the Levenshtein distance (also known as
-edit distance) as a measure of phonological relatedness between two
-nodes. The measure counts the minimum number of operations (insertions,
-deletions, substitutions) required to change one string into another.
-
-In previous studies, two nodes were linked if they had an edit distance
-of 1 (Carlson et al., 2014; Stella et al., 2017; Storkel, 2009).
-However, these studies reported a contribution of phonological
-connectivity to noun learning when networks were built using a dense
-adult vocabulary. Since the focus of the current study is on the
-mechanism of growth, the networks are based on children's early
-vocabulary. The latter, however, contains very few noun pairs with an
-edit distance of 1. To better represent the similarity space in the
-phonological domain, we increased the threshold from 1 to 2, that is,
-two nodes were related if their edit distance was equal to 1 or
-2.\footnote{In Appendix A, we show the main results for phonological networks based on an edit distance of 1.
+\hypertarget{semantic-networks}{%
+\subsection{Semantic networks}\label{semantic-networks}}
+
+We constructed semantic networks for English data following the procedure outlined in Hills et al.
+(2009), as follows.
+We used as an index of semantic relatedness the Florida Free Association Norms (Nelson et al., 1998).
+This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target).
+For example, when given the word \enquote{ball,} they might answer with the word \enquote{game.} A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms.
+The connectivity of a given node was characterized by its \emph{indegree}: the number of links for which the word was the target.\footnote{This choice was based on prior work by Hills et al.
+(2009) stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated with indegree.} To model growth from month to month, we constructed a different network at each month, based on the nouns that have been acquired by that month.
+
+Since the free association norms are available only in English, we used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across 10 languages.
+Semantic associations are not necessarily shared across languages, but we use this technique as a reasonable first approximation.
+In support of this approximation, Youn et al.
+(2016) showed that semantic networks across languages share substantial similarities.
+The fact that semantic associations are assumed to be shared across languages does not mean that the semantic networks will necessarily grow in a similar fashion.
+For instance, the set of words acquired by children as well as the order of word acquisition can vary from language to language leading to possibily different learning strategies.
+
+\hypertarget{phonological-networks}{%
+\subsection{Phonological networks}\label{phonological-networks}}
+
+To construct phonological networks we first mapped the orthographic transcription of words to their International Phonetic Alphabet (IPA) transcriptions in each language, using the open-source text-to-speech software \textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}}.
+This software provides the correct IPA transcription if the word is found in a spelling-to-phonemes dictionary, otherwise it uses language-specific pronunciation rules to generate an approximate phonetic transcription.
+We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes.
+The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.
+
+In previous studies, two nodes were linked if they had an edit distance of 1 (Carlson et al., 2014; Stella et al., 2017; Storkel, 2009).
+However, these studies reported a contribution of phonological connectivity to noun learning when networks were built using a dense adult vocabulary.
+Since the focus of the current study is on the mechanism of growth, the networks are based on children's early vocabulary.
+The latter, however, contains very few noun pairs with an edit distance of 1.
+To better represent the similarity space in the phonological domain, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{In Appendix A, we show the main results for phonological networks based on an edit distance of 1.
 We also show the results for phonological networks where the edges between pairs of words were weighted by the inverse of the edit distance.
-We did not consider the case of a threshold larger than 2 since many short pairs appear phonologically unrelated when the edit distance is 3 or more (e.g., "cat"/"dog").}
-The connectivity of a given node was characterized with its
-\emph{degree}: the number of links it shares with other words.
-
-\section{Analysis}\label{analysis}
-
-\subsection{Static properties of the global
-network}\label{static-properties-of-the-global-network}
+We did not consider the case of a threshold larger than 2 since many short pairs appear phonologically unrelated when the edit distance is 3 or more (e.g., "cat"/"dog").} The connectivity of a given node was characterized with its \emph{degree}: the number of links it shares with other words.
+
+\hypertarget{analysis}{%
+\section{Analysis}\label{analysis}}
+
+\hypertarget{static-properties-of-the-global-network}{%
+\subsection{Static properties of the global network}\label{static-properties-of-the-global-network}}
 
 We start by analyzing word connectivity in the global (static) network.
-We constructed this network using nouns learned by the oldest age for
-which we have CDI data (e.g., in English this corresponds, in
-comprehension, to the network by 18 months, and in production, to the
-network by 30 months). This global network is the end-state towards
-which both INT and EXT converge by the last month of learning. Moreover,
-following Hills et al. (2009), we used this end-state network as a proxy
-for the external connectivity in the learning environment. Below we
-analyze properties of these global networks that may a priori hint at an
-INT- or EXT-like growth.
+We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds, in comprehension, to the network by 18 months, and in production, to the network by 30 months).
+This global network is the end-state towards which both INT and EXT converge by the last month of learning.
+Moreover, following Hills et al.
+(2009), we used this end-state network as a proxy for the external connectivity in the learning environment.
+Below we analyze properties of these global networks that may a priori hint at an INT- or EXT-like growth.
 
@@
 
-\subsubsection{Connectivity predicts the age of
-acquisition}\label{connectivity-predicts-the-age-of-acquisition}
-
-Connectivity in the global network is directly related to EXT as it
-represents the explicit criterion this growth scenario uses to determine
-what words should be learned first (Figure \ref{fig:growth}). Therefore,
-a direct consequence of an EXT-like growth scenario is a correlation
-between connectivity in the global network and the age of acquisition.
-This correlation is also necessary to INT, although the causality is
-reversed: Higher connectivity in the global network is caused by earlier
-learning, not the other way around. Some words end up being highly
-connected in the global network precisely because they happen to be
-acquired earlier and, therefore, have a higher chance of accumulating
-more links over time. Thus, the correlation between connectivity in the
-end-state network and AoA can result from both EXT and INT. If there is
-no such correlation, neither growth scenario can be posited as a
-possible learning mechanism.
-
-Figures \ref{fig:corrProd} and \ref{fig:corrComp} show how the age of
-acquisition in production and comprehension, respectively, correlates
-with the degree (or indegree for the semantic networks). For ease of
-visual comparison, the predictor (i.e., the degree) was centered and
-scaled. The plots show, overall, a negative correlation between the
-month of acquisition and the degree. In production data, the average
-correlation across languages was -0.24 (\(SD=\) 0.10) for the semantic
-networks and -0.30 (\(SD=\) 0.05) for the phonological networks. In
-comprehension data, the average correlation was -0.21 (\(SD=\) 0.08) for
-the semantic networks and -0.21 (\(SD=\) 0.07) for the phonological
-networks. These results indicate that nouns with higher degrees are
-generally learned earlier, thus replicating previous findings in English
-(Hills et al., 2009; Storkel, 2009) and extending these findings to 10
-different languages, generally, in both production- and
-comprehension-based vocabularies.
+\#\#\#Connectivity predicts the age of acquisition
+
+Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \ref{fig:growth}).
+Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.
+This correlation is also necessary to INT, although the causality is reversed: Higher connectivity in the global network is caused by earlier learning, not the other way around.
+Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.
+Thus, the correlation between connectivity in the end-state network and AoA can result from both EXT and INT.
+If there is no such correlation, neither growth scenario can be posited as a possible learning mechanism.
+
+Figures \ref{fig:corrProd} and \ref{fig:corrComp} show how the age of acquisition in production and comprehension, respectively, correlates with the degree (or indegree for the semantic networks).
+For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled.
+The plots show, overall, a negative correlation between the month of acquisition and the degree.
+In production data, the average correlation across languages was -0.24 (\(SD=\) 0.10) for the semantic networks and -0.30 (\(SD=\) 0.05) for the phonological networks.
+In comprehension data, the average correlation was -0.21 (\(SD=\) 0.08) for the semantic networks and -0.21 (\(SD=\) 0.07) for the phonological networks.
+These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English (Hills et al., 2009; Storkel, 2009) and extending these findings to 10 different languages, generally, in both production- and comprehension-based vocabularies.
 
@@
 
-\subsubsection{Power-law degree
-distribution}\label{power-law-degree-distribution}
-
-We also analyzed the global network's degree distribution. The shape of
-this distribution is particularly relevant to INT as this growth
-scenario is known to generate networks with a power-law degree
-distribution, i.e., a distribution of the form
-\(p(k) \propto \frac{1}{k^{\alpha}}\) (Barabasi \& Albert, 1999). If the
-end-state network displays this property, this fact would suggest, but
-not prove, an INT-like generative process. If, however, the degree
-distribution is very different from a power law, this would
-significantly weaken the case for INT. The log-log plots are shown in
-Figure \ref{fig:degreeDist}. We fit a power law to each empirical degree
-distribution following the procedure outlined in Clauset, Shalizi, and
-Newman (2009) and using a related R package (poweRlaw, Gillespie, 2015).
+\#\#\#Power-law degree distribution
+
+We also analyzed the global network's degree distribution.
+The shape of this distribution is particularly relevant to INT as this growth scenario is known to generate networks with a power-law degree distribution, i.e., a distribution of the form \(p(k) \propto \frac{1}{k^{\alpha}}\) (Barabasi \& Albert, 1999).
+If the end-state network displays this property, this fact would suggest, but not prove, an INT-like generative process.
+If, however, the degree distribution is very different from a power law, this would significantly weaken the case for INT.
+The log-log plots are shown in Figure \ref{fig:degreeDist}.
+We fit a power law to each empirical degree distribution following the procedure outlined in Clauset, Shalizi, \& Newman (2009) and using a related R package (poweRlaw, Gillespie, 2015).
 
@@
 \multicolumn{1}{c}{} & \multicolumn{3}{c}{Phono.} & \multicolumn{3}{c}{Sem.} \\
-\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
+\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
 Language & cut-off & alpha & p-value & cut-off & alpha & p-value\\
 \midrule
-Croatian & 4 & 2.18 & 0.123 & 4 & 2.55 & 0.881\\
-Danish & 11 & 4.55 & 0.858 & 4 & 2.38 & 0.001\\
-English & 20 & 9.14 & 0.511 & 5 & 2.66 & 0.132\\
-French & 20 & 3.75 & 0.112 & 8 & 2.81 & 0.133\\
-Italian & 9 & 9.45 & 0.780 & 4 & 2.93 & 0.608\\
-Norwegian & 15 & 6.28 & 0.744 & 5 & 2.88 & 0.201\\
-Russian & 8 & 4.20 & 0.541 & 24 & 5.61 & 0.723\\
-Spanish & 13 & 8.75 & 0.736 & 4 & 2.98 & 0.460\\
-Swedish & 11 & 4.68 & 0.103 & 4 & 2.49 & 0.171\\
-Turkish & 8 & 3.26 & 0.375 & 4 & 2.87 & 0.925\\
+Croatian & 4 & 2.55 & 0.881 & 4 & 2.18 & 0.123\\
+Danish & 4 & 2.38 & 0.001 & 11 & 4.55 & 0.858\\
+English & 5 & 2.66 & 0.132 & 20 & 9.14 & 0.511\\
+French & 8 & 2.81 & 0.133 & 20 & 3.75 & 0.112\\
+Italian & 4 & 2.93 & 0.608 & 9 & 9.45 & 0.780\\
+Norwegian & 5 & 2.88 & 0.201 & 15 & 6.28 & 0.744\\
+Russian & 24 & 5.61 & 0.723 & 8 & 4.20 & 0.541\\
+Spanish & 4 & 2.98 & 0.460 & 13 & 8.75 & 0.736\\
+Swedish & 4 & 2.49 & 0.171 & 11 & 4.68 & 0.103\\
+Turkish & 4 & 2.87 & 0.925 & 8 & 3.26 & 0.375\\
 \bottomrule
@@
 \multicolumn{1}{c}{} & \multicolumn{3}{c}{Phono.} & \multicolumn{3}{c}{Sem.} \\
-\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
+\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
 Language & cut-off & alpha & p-value & cut-off & alpha & p-value\\
 \midrule
-Croatian & 2 & 2.06 & 0.020 & 5 & 2.67 & 0.895\\
-Danish & 5 & 2.98 & 0.136 & 4 & 2.39 & 0.005\\
-English & 13 & 5.16 & 0.235 & 4 & 2.64 & 0.765\\
-French & 18 & 5.58 & 0.336 & 4 & 2.63 & 0.330\\
-Italian & 8 & 10.27 & 0.909 & 4 & 2.88 & 0.688\\
-Norwegian & 13 & 7.65 & 0.440 & 5 & 2.87 & 0.433\\
-Russian & 5 & 3.97 & 0.854 & 8 & 3.91 & 0.952\\
-Spanish & 5 & 3.01 & 0.085 & 5 & 3.11 & 0.552\\
-Swedish & 9 & 6.75 & 0.102 & 5 & 2.81 & 0.713\\
-Turkish & 9 & 5.73 & 0.958 & 4 & 3.13 & 0.887\\
+Croatian & 5 & 2.67 & 0.895 & 2 & 2.06 & 0.020\\
+Danish & 4 & 2.39 & 0.005 & 5 & 2.98 & 0.136\\
+English & 4 & 2.64 & 0.765 & 13 & 5.16 & 0.235\\
+French & 4 & 2.63 & 0.330 & 18 & 5.58 & 0.336\\
+Italian & 4 & 2.88 & 0.688 & 8 & 10.27 & 0.909\\
+Norwegian & 5 & 2.87 & 0.433 & 13 & 7.65 & 0.440\\
+Russian & 8 & 3.91 & 0.952 & 5 & 3.97 & 0.854\\
+Spanish & 5 & 3.11 & 0.552 & 5 & 3.01 & 0.085\\
+Swedish & 5 & 2.81 & 0.713 & 9 & 6.75 & 0.102\\
+Turkish & 4 & 3.13 & 0.887 & 9 & 5.73 & 0.958\\
 \bottomrule
@@
 
-In brief, the analysis consisted in two steps. First, we derived the
-optimal cut-off, \(k_{min}\), above which the distribution is more
-likely to follow a power
-law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}
-and we estimate the corresponding scaling parameter \(\alpha\). Second,
-we calculated the goodness-to-fit, which resulted in a \(p\)-value
-quantifying the plausibility of the model. The results are shown in
-Table \ref{tab:powerLawProd} for production data, and in Table
-\ref{tab:powerLawComp} for comprehension data.
-
-Overall, we could not reject the null hypothesis of a power-law
-distribution: The \(p\)-value was generally above 0.1 in almost all
-languages for both production and comprehension. That said, phonological
-networks had relatively larger cut-offs than semantic networks. These
-\enquote{truncated} power-laws in phonological networks may be due to
-the constraints that exist on word formation in the phonological domain
-such as the size of the phonemic inventory, phonotactic rules, and word
-length. Such constraints may limit the number of words that are
-phonologically similar, thus leading to distributions which decay faster
-than a non-truncated power law (Arbesman et al., 2010).
-
-In sum, the static properties of the end-state network are \emph{a
-priori} compatible with both INT and EXT. In order to decide between
-these two developmental scenarios, we need to fit explicit growth models
-to the data.
+In brief, the analysis consisted in two steps.
+First, we derived the optimal cut-off, \(k_{min}\), above which the distribution is more likely to follow a power law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter \(\alpha\).
+Second, we calculated the goodness-to-fit, which resulted in a \(p\)-value quantifying the plausibility of the model.
+The results are shown in Table \ref{tab:powerLawProd} for production data, and in Table \ref{tab:powerLawComp} for comprehension data.
+
+Overall, we could not reject the null hypothesis of a power-law distribution: The \(p\)-value was generally above 0.1 in almost all languages for both production and comprehension.
+That said, phonological networks had relatively larger cut-offs than semantic networks.
+These \enquote{truncated} power-laws in phonological networks may be due to the constraints that exist on word formation in the phonological domain such as the size of the phonemic inventory, phonotactic rules, and word length.
+Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law (Arbesman et al., 2010).
+
+In sum, the static properties of the end-state network are \emph{a priori} compatible with both INT and EXT.
+In order to decide between these two developmental scenarios, we need to fit explicit growth models to the data.
 
@@
 
-\subsection{Network growth models}\label{network-growth-models}
-
-To test the network growth scenarios, we fit two growth models to the
-data. We calculated the probability that a word \(w_i\), with a utility
-value \(u_i\) would enter the lexicon at a given month, using a softmax
-function:
-
+\hypertarget{network-growth-models}{%
+\subsection{Network growth models}\label{network-growth-models}}
+
+To test the network growth scenarios, we fit two growth models to the data.
+We calculated the probability that a word \(w_i\), with a utility value \(u_i\) would enter the lexicon at a given month, using a softmax function:
 \begin{equation}
@@
 
-\noindent where \(\beta\) is a fitted parameter that captures the
-magnitude of the relationship between network parameters and growth
-(analogous to a regression coefficient). A positive value of \(\beta\)
-means that words with higher utility values \(u_i\) are acquired first,
-and a negative value means that words with lower utility values are
-acquired first (see Figure \ref{fig:growth} for an illustration of how
-utility values \(u_i\) are defined in each growth scenario). The
-normalization includes all words that could be learned at that month.
-
-We estimated the parameter \(\beta\) using a Bayesian approach. The
-inference was performed using the probabilistic programming language
-WebPPL (N. Goodman \& Stuhlmuller, 2014). We defined a uniform prior
-over \(\beta\), and at each month, we computed the likelihood function
-over words that could possibly enter the lexicon at that month, fit to
-the words that have been learned at that month (using Formula 1). Markov
-Chain Monte Carlo sampling resulted in a posterior distribution over
-\(\beta\), which we summarized in Figure \ref{fig:growthPred}. The
-results replicate Hills et al.'s original finding regarding the semantic
-network in English and the production-based vocabulary, which is that
-this network grows by EXT, not by INT. Crucially, our results show that,
-generally speaking, this finding generalizes to comprehension-based
-vocabulary, and holds across languages. This generalization was obtained
-in both the semantic\footnote{One could imagine that the fact of using
-  English free association norms cross-linguistically would decrease the
-  effect of non-English semantic networks because of possible cultural
-  differences. However, our findings do not support this assumption;
-  rather, it supports our initial approximation about the shared nature
-  of the semantic similarity measure. That said, this approximation is
-  not perfect. For example, there is evidence that a small part of the
-  variance in free association data can be explained by phonological
-  similarity (Kachergis, Cox, \& Jones, 2011; Matusevych \& Stevenson,
-  2018), thus leading to possibly minor cross-linguistic differences.}
-and phonological domains.
+\noindent where \(\beta\) is a fitted parameter that captures the magnitude of the relationship between network parameters and growth (analogous to a regression coefficient).
+A positive value of \(\beta\) means that words with higher utility values \(u_i\) are acquired first, and a negative value means that words with lower utility values are acquired first (see Figure \ref{fig:growth} for an illustration of how utility values \(u_i\) are defined in each growth scenario).
+The normalization includes all words that could be learned at that month.
+
+We estimated the parameter \(\beta\) using a Bayesian approach.
+The inference was performed using the probabilistic programming language WebPPL (Goodman \& Stuhlmuller, 2014).
+We defined a uniform prior over \(\beta\), and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using Formula 1).
+Markov Chain Monte Carlo sampling resulted in a posterior distribution over \(\beta\), which we summarized in Figure \ref{fig:growthPred}.
+The results replicate Hills et al.'s original finding regarding the semantic network in English and the production-based vocabulary, which is that this network grows by EXT, not by INT.
+Crucially, our results show that, generally speaking, this finding generalizes to comprehension-based vocabulary, and holds across languages.
+This generalization was obtained in both the semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
+However, our findings do not support this assumption; rather, it supports our initial approximation about the shared nature of the semantic similarity measure.
+That said, this approximation is not perfect.
+For example, there is evidence that a small part of the variance in free association data can be explained by phonological similarity (Kachergis, Cox, \& Jones, 2011; Matusevych \& Stevenson, 2018), thus leading to possibly minor cross-linguistic differences.} and phonological domains.
 
@@
 
-\subsection{Comparison to other predictors of age of
-acquisition}\label{comparison-to-other-predictors-of-age-of-acquisition}
-
-Above we showed that the way semantic and phonological information is
-structured in the learning environment contributes to noun learning (via
-EXT) across languages. However, we know that other factors influence
-learning as well (e.g., Braginsky et al., 2019). Next, we investigated
-how semantic and phonological connectivity interact with two other
-factors. The first one is word frequency, a well-studied factor shown to
-predict the age of acquisition in a reliable fashion (e.g., J. C.
-Goodman et al., 2008). The second factor is word length, which was shown
-to correlate with phonological connectivity: Shorter words are more
-likely to have higher connectivity (Pisoni, Nusbaum, Luce, \&
-Slowiaczek, 1985; Vitevitch \& Rodríguez, 2005).
-
-Since we found INT to be uninformative, we dropped it from this
-analysis, keeping only EXT. This simplified the model because we no
-longer needed to fit growth month-by-month. The latter was a requirement
-only for INT where the words' utilities varied from month to month,
-depending on how connectivity changed in the growing internal network. A
-more direct way to assess and compare the contribution of EXT in
-relation to other word-level factors is through conducting regressions,
-where connectivity in the learning environment, frequency, and length
-predict the age of acquisition.
-
-For word length, we counted the number of phonemes in our generated IPA
-transcription. For word frequency, we used the frequency estimates from
-Braginsky et al. (2019) where unigram counts were derived based on
-CHILDES corpora in each language (MacWhinney, 2014). Although these
-frequency counts use transcripts from independent sets of children, they
-are based on large samples, and this allows us to average out possible
-differences between children and the specificities of their input (see
-J. C. Goodman et al., 2008 for a similar research strategy).
-
-We conducted two analyses. We fit a linear regression for each language,
-and we fit a linear mixed-effect model to all the data pooled across
-languages, with language as a random effect. Figure \ref{fig:staticPred}
-shows the coefficient estimate for each predictor in each language for
-production and comprehension data. Figure \ref{fig:staticAll} shows the
-coefficient estimates for all languages combined (all predictors were
-centered and scaled).
-
-The findings for the new predictors were as follows. Overall, frequency
-is the largest and most consistent predictor of age of acquisition in
-both comprehension and production data and across languages, endorsing
-results for nouns across a variety of analyses (Braginsky et al., 2019;
-J. C. Goodman et al., 2008; B. C. Roy et al., 2015). Word length is more
-predictive for production than comprehension (and this difference is
-very clear in the global model), replicating previous work (Braginsky et
-al., 2019). Thus, word length seems to reflect the effects of
-production's constraints rather than comprehension's constraints, i.e.,
-longer words are harder to articulate but they may not be significantly
-more difficult to store and access.
-
-As for the factors of interest, i.e., semantic and phonological
-connectivity, we found cross-linguistic differences. Connectivity
-contributes to learning in some languages but not in other. In
-particular, semantic connectivity does not explain variance in English
-data beyond that explained by phonological connectivity, frequency and
-length. This finding contrasts with the original finding in Hills et al.
-(2009). However, this difference might be due to our using a slightly
-different model (which included word length as a covariate) and a larger
-dataset. That said, and despite these apparent cross-linguistic
-differences, both phonological and semantic connectivity are significant
-predictors in the combined model (Figure \ref{fig:staticAll}).
-
-\section{Discussion}\label{discussion}
-
-This study provided an analysis of network growth during development. We
-compared two network growth scenarios described in the pioneering work
-of Steyvers and Tenenbaum (2005) and Hills et al. (2009). The first
-scenario, INT (originally called Preferential Attachment), described a
-rich-get-richer network growth model in which the current structure of
-the learner's internal network determines future growth; the other, EXT
-(originally called Preferential Acquisition) described a model in which
-the external, global environmental network structure determines
-learners' growth patterns. These two mechanisms represent two
-fundamentally different accounts of lexical growth: One suggests that
-future word knowledge is primarily shaped by the children's past
-knowledge and its organization, whereas the other suggests that learning
-is shaped, rather, by salient properties in the input regardless of how
-past knowledge is organized. The present study tested the generality of
-previous findings by 1) investigating phonological networks together
-with semantic networks, 2) testing both comprehension- and
-production-based vocabularies, and 3) comparing the results across 10
-languages.
-
-We found that the original findings reported in Hills et al. (2009)
-generalize well across all these dimensions. First, just like semantic
-networks, phonological networks grow via the externally-driven scenario
-(EXT), not by the internally-driven mechanism (INT). Second,
-comprehension-based vocabularies grow in a way similar to
-production-based vocabularies. Finally, the findings were, overall,
-similar across the 10 languages we tested. Although we find some
-cross-linguistic variation when semantic and phonological networks were
-pitted against frequency and length, this variability is to be taken
-with a grain of salt as it might be exaggerated in our study by several
-factors such as the limited and partially-overlapping set of nouns for
-each language, measurement error due to the sample of acquisition data,
-the sample of frequency data, and the translation of association norms.
-In fact, both phonological and semantic connectivity are significant
-predictors above and beyond frequency and length when data are pooled
-across languages.
-
-These findings corroborate the hypothesis that children start by
-learning words that have high similarity to a variety of other words in
-the learning environment, not in the child's available lexicon. This
-hypothesis implies that children are sensitive to highly connected words
-although they do not initially have access to the full network, thus
-raising some important questions: What mechanism allows children to
-distinguish highly connected words from other words? Besides, why would
-highly connected words be easier to learn?
-
-One possibility is that these patterns emerge from children's use of
-statistical learning abilities (Aslin \& Newport, 2012; Saffran, Aslin,
-\& Newport, 1996; Smith \& Yu, 2008). The term \enquote{statistical
-learning} has been used in the developmental literature to describes the
-process by which one acquires information about their environment
-through tracking the frequency distribution of some elements (e.g.,
-words) in different contexts. An important property of this kind of
-learning is that it occurs without explicit instructions and through
-mere exposure to the input. Previous work in this line of research has
-documented specific mechanisms which can explain the patterns found in
-the current study.
-
-For example, in the semantic domain, growth according to EXT could be
-explained by a mechanism similar to cross-situational learning (McMurray
-et al., 2012; Smith \& Yu, 2008; Yurovsky \& Frank, 2015). According to
-this mechanism, children track the co-occurrence of concrete nouns with
-their possible semantic referents. The referent of a word heard in only
-one naming situation can be ambiguous (e.g., when the word
-\enquote{ball} is heard for the first time in the presence of both a
-ball and a chair), but hearing the same word in a diversity of semantic
-contexts allows the learner to narrow down the set of possible
-word-object mappings. In our case, free association (used to determine
-semantic network connectivity) is related to contextual co-occurrence
-(Fourtassi \& Dupoux, 2013; Griffiths, Steyvers, \& Tenenbaum, 2007),
-meaning that highly connected words will tend to occur in a variety of
-speech and referential contexts. This fact makes such words easier to
-learn because they have more referential disambiguating cues across
-learning contexts. Crucially, children can learn these words without
-necessarily knowing the meaning of all other words with which they
-co-occur (hence the similarity with EXT). This possibility is supported
-by the finding that words' diversity of occurrence in child-directed
-speech predicts their age of learning (Hills et al., 2010; Stella et
-al., 2017).
-
-In the phonological case, network growth according to EXT is also
-compatible with a scenario whereby children are tracking low-level
-statistical patterns, e.g., high probability sound sequences. Indeed,
-connectivity in the phonological network is inherently correlated with
-phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
-is, highly connected words tend to be made of frequent sound sequences.
-Children are sensitive to local phonotactic regularities (Jusczyk, Luce,
-\& Charles-Luce, 1994), and this sensitivity might lead them to learn
-higher-probability words more easily (Storkel, 2001). This explanation
-is supported by computational simulations that show how learning general
-phonotactics patterns create \enquote{well-worn paths} which allow the
-models to represent several distinct but phonologically neighboring
-words (Dell, Juliano, \& Govindjee, 1993; Siew, 2013; Takac, Knott, \&
-Stokes, 2017). More generally, there is a growing interest in
-investigating precisely how the local patterns acquired through
-statistical learning may give rise to the global network organization
-(For a review, see Karuza, Thompson-Schill, \& Bassett, 2016).
-
-Besides using their own statistical learning skills, children could also
-benefit from the way their caregivers speak. Perhaps the caregivers put
-more emphasis on the words that are highly connected in \emph{their}
-mature lexical network. This emphasis would guide children to learn
-first these highly connected words, even though children do not have
-access to the distribution of words' connectivity in the final network.
-Investigating this possibility would require further research on
-caregiver-child interaction (MacWhinney, 2014; B. C. Roy et al., 2015),
-examining what words are introduced over development and the extent to
-which children's uptake is influenced by this input (Clark, 2007; Hoff
-\& Naigles, 2002; Huttenlocher et al., 1991).
-
-This study investigated the class of nouns in isolation --- following
-previous studies investigating the early semantic and phonological
-network (Hills et al., 2009; Storkel, 2009). We could ask if studying
-one class separately is a legitimate research strategy. In other words,
-would word classes (such as nouns, verbs and function words) be acquired
-relatively differently, or would they interact substantially to the
-extent that it becomes unreasonable to study each class separately?
-
-There are many observations that support the hypothesis that different
-word classes have different pathways of learning, making it worthwhile
-to study each class separately. For instance, different word classes
-follow different time trajectories: In the early stages of development,
-nouns tend to be acquired at a higher pace than predicates and function
-words (Bates et al., 1994). Research has shown that this difference
-cannot be trivially attributed to differences in the degree to which
-these classes are present in the input; if anything, verbs and function
-words are often more frequent in the input than nouns (e.g., Gentner,
-1982). J. C. Goodman et al. (2008) found an effect of frequency on the
-age of acquisition within --- not across --- classes. Further, recent
-work by Braginsky et al. (2019) tested a large number of predictors,
-besides frequency, and found that these predictors do not influence the
-acquisition of word classes in the same way. For example, the
-acquisition of nouns was found to be most influenced by frequency and
-concreteness, whereas the acquisition of function words was most
-influenced by word length.
-
-This work shares a number of limitations with previous studies using
-similar research strategy and datasets. Chief among these limitations is
-the fact that the age of word acquisition is computed using different
-children at different ages (due to the fact that available CDI data is
-mainly cross-sectional). Such a measure has been shown to be valid and
-reliable (Fenson et al., 1994), and has allowed researchers to study
-important aspects of word learning (Braginsky et al., 2019; J. C.
-Goodman et al., 2008; Hills et al., 2009; Stella et al., 2017; Storkel,
-2009). In our case, the use of cost-effective cross-sectional data has
-allowed us to leverage large-scale studies across several languages.
-That said, it is important to remember that this type of data can only
-inform us about the learning trajectory of the \enquote{average} child.
-Although our study endorses, overall, the externally-driven account of
-network growth, this does not mean individual children never use some
-variant of INT or some combination of both INT and EXT (Beckage \&
-Colunga, under review). To illustrate, some children develop
-\enquote{islands of expertise,} that is, well-organized knowledge about
-a certain topic (e.g., birds or dinosaurs). This prior knowledge enables
-these children to learn new related words more easily (e.g., Chi \&
-Koeske, 1983).
-
-To conclude, our work validates and generalizes previous results in
-early network development. It suggests that the advantage of highly
-connected words may result, at least in the early stages of word
-learning, from the operation of simpler mechanisms in both the semantic
-and phonological domains. One question for future experimental work is
-whether such correlational patterns of growth can be produced in
-controlled behavioral experiments.
+\hypertarget{comparison-to-other-predictors-of-age-of-acquisition}{%
+\subsection{Comparison to other predictors of age of acquisition}\label{comparison-to-other-predictors-of-age-of-acquisition}}
+
+Above we showed that the way semantic and phonological information is structured in the learning environment contributes to noun learning (via EXT) across languages.
+However, we know that other factors influence learning as well (e.g., Braginsky et al., 2019).
+Next, we investigated how semantic and phonological connectivity interact with two other factors.
+The first one is word frequency, a well-studied factor shown to predict the age of acquisition in a reliable fashion (e.g., Goodman et al., 2008).
+The second factor is word length, which was shown to correlate with phonological connectivity: Shorter words are more likely to have higher connectivity (Pisoni, Nusbaum, Luce, \& Slowiaczek, 1985; Vitevitch \& Rodrı'guez, 2005).
+
+Since we found INT to be uninformative, we dropped it from this analysis, keeping only EXT.
+This simplified the model because we no longer needed to fit growth month-by-month.
+The latter was a requirement only for INT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.
+A more direct way to assess and compare the contribution of EXT in relation to other word-level factors is through conducting regressions, where connectivity in the learning environment, frequency, and length predict the age of acquisition.
+
+For word length, we counted the number of phonemes in our generated IPA transcription.
+For word frequency, we used the frequency estimates from Braginsky et al.
+(2019) where unigram counts were derived based on CHILDES corpora in each language (MacWhinney, 2014).
+Although these frequency counts use transcripts from independent sets of children, they are based on large samples, and this allows us to average out possible differences between children and the specificities of their input (see Goodman et al., 2008 for a similar research strategy).
+
+We conducted two analyses.
+We fit a linear regression for each language, and we fit a linear mixed-effect model to all the data pooled across languages, with language as a random effect.
+Figure \ref{fig:staticPred} shows the coefficient estimate for each predictor in each language for production and comprehension data.
+Figure \ref{fig:staticAll} shows the coefficient estimates for all languages combined (all predictors were centered and scaled).
+
+The findings for the new predictors were as follows.
+Overall, frequency is the largest and most consistent predictor of age of acquisition in both comprehension and production data and across languages, endorsing results for nouns across a variety of analyses (Braginsky et al., 2019; Goodman et al., 2008; Roy et al., 2015).
+Word length is more predictive for production than comprehension (and this difference is very clear in the global model), replicating previous work (Braginsky et al., 2019).
+Thus, word length seems to reflect the effects of production's constraints rather than comprehension's constraints, i.e., longer words are harder to articulate but they may not be significantly more difficult to store and access.
+
+As for the factors of interest, i.e., semantic and phonological connectivity, we found cross-linguistic differences.
+Connectivity contributes to learning in some languages but not in other.
+In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
+This finding contrasts with the original finding in Hills et al.
+(2009).
+However, this difference might be due to our using a slightly different model (which included word length as a covariate) and a larger dataset.
+That said, and despite these apparent cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model (Figure \ref{fig:staticAll}).
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+This study provided an analysis of network growth during development.
+We compared two network growth scenarios described in the pioneering work of Steyvers \& Tenenbaum (2005) and Hills et al.
+(2009).
+The first scenario, INT (originally called Preferential Attachment), described a rich-get-richer network growth model in which the current structure of the learner's internal network determines future growth; the other, EXT (originally called Preferential Acquisition) described a model in which the external, global environmental network structure determines learners' growth patterns.
+These two mechanisms represent two fundamentally different accounts of lexical growth: One suggests that future word knowledge is primarily shaped by the children's past knowledge and its organization, whereas the other suggests that learning is shaped, rather, by salient properties in the input regardless of how past knowledge is organized.
+The present study tested the generality of previous findings by 1) investigating phonological networks together with semantic networks, 2) testing both comprehension- and production-based vocabularies, and 3) comparing the results across 10 languages.
+
+We found that the original findings reported in Hills et al.
+(2009) generalize well across all these dimensions.
+First, just like semantic networks, phonological networks grow via the externally-driven scenario (EXT), not by the internally-driven mechanism (INT).
+Second, comprehension-based vocabularies grow in a way similar to production-based vocabularies.
+Finally, the findings were, overall, similar across the 10 languages we tested.
+Although we find some cross-linguistic variation when semantic and phonological networks were pitted against frequency and length, this variability is to be taken with a grain of salt as it might be exaggerated in our study by several factors such as the limited and partially-overlapping set of nouns for each language, measurement error due to the sample of acquisition data, the sample of frequency data, and the translation of association norms.
+In fact, both phonological and semantic connectivity are significant predictors above and beyond frequency and length when data are pooled across languages.
+
+These findings corroborate the hypothesis that children start by learning words that have high similarity to a variety of other words in the learning environment, not in the child's available lexicon.
+This hypothesis implies that children are sensitive to highly connected words although they do not initially have access to the full network, thus raising some important questions: What mechanism allows children to distinguish highly connected words from other words?
+Besides, why would highly connected words be easier to learn?
+
+One possibility is that these patterns emerge from children's use of statistical learning abilities (Aslin \& Newport, 2012; Saffran, Aslin, \& Newport, 1996; Smith \& Yu, 2008).
+The term \enquote{statistical learning} has been used in the developmental literature to describes the process by which one acquires information about their environment through tracking the frequency distribution of some elements (e.g., words) in different contexts.
+An important property of this kind of learning is that it occurs without explicit instructions and through mere exposure to the input.
+Previous work in this line of research has documented specific mechanisms which can explain the patterns found in the current study.
+
+For example, in the semantic domain, growth according to EXT could be explained by a mechanism similar to cross-situational learning (McMurray et al., 2012; Smith \& Yu, 2008; Yurovsky \& Frank, 2015).
+According to this mechanism, children track the co-occurrence of concrete nouns with their possible semantic referents.
+The referent of a word heard in only one naming situation can be ambiguous (e.g., when the word \enquote{ball} is heard for the first time in the presence of both a ball and a chair), but hearing the same word in a diversity of semantic contexts allows the learner to narrow down the set of possible word-object mappings.
+In our case, free association (used to determine semantic network connectivity) is related to contextual co-occurrence (Fourtassi \& Dupoux, 2013; Griffiths, Steyvers, \& Tenenbaum, 2007), meaning that highly connected words will tend to occur in a variety of speech and referential contexts.
+This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts.
+Crucially, children can learn these words without necessarily knowing the meaning of all other words with which they co-occur (hence the similarity with EXT).
+This possibility is supported by the finding that words' diversity of occurrence in child-directed speech predicts their age of learning (Hills et al., 2010; Stella et al., 2017).
+
+In the phonological case, network growth according to EXT is also compatible with a scenario whereby children are tracking low-level statistical patterns, e.g., high probability sound sequences.
+Indeed, connectivity in the phonological network is inherently correlated with phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999).
+That is, highly connected words tend to be made of frequent sound sequences.
+Children are sensitive to local phonotactic regularities (Jusczyk, Luce, \& Charles-Luce, 1994), and this sensitivity might lead them to learn higher-probability words more easily (Storkel, 2001).
+This explanation is supported by computational simulations that show how learning general phonotactics patterns create \enquote{well-worn paths} which allow the models to represent several distinct but phonologically neighboring words (Dell, Juliano, \& Govindjee, 1993; Siew, 2013; Takac, Knott, \& Stokes, 2017).
+More generally, there is a growing interest in investigating precisely how the local patterns acquired through statistical learning may give rise to the global network organization (For a review, see Karuza, Thompson-Schill, \& Bassett, 2016).
+
+Besides using their own statistical learning skills, children could also benefit from the way their caregivers speak.
+Perhaps the caregivers put more emphasis on the words that are highly connected in \emph{their} mature lexical network.
+This emphasis would guide children to learn first these highly connected words, even though children do not have access to the distribution of words' connectivity in the final network.
+Investigating this possibility would require further research on caregiver-child interaction (MacWhinney, 2014; Roy et al., 2015), examining what words are introduced over development and the extent to which children's uptake is influenced by this input (Clark, 2007; Hoff \& Naigles, 2002; Huttenlocher et al., 1991).
+
+This study investigated the class of nouns in isolation --- following previous studies investigating the early semantic and phonological network (Hills et al., 2009; Storkel, 2009).
+We could ask if studying one class separately is a legitimate research strategy.
+In other words, would word classes (such as nouns, verbs and function words) be acquired relatively differently, or would they interact substantially to the extent that it becomes unreasonable to study each class separately?
+
+There are many observations that support the hypothesis that different word classes have different pathways of learning, making it worthwhile to study each class separately.
+For instance, different word classes follow different time trajectories: In the early stages of development, nouns tend to be acquired at a higher pace than predicates and function words (Bates et al., 1994).
+Research has shown that this difference cannot be trivially attributed to differences in the degree to which these classes are present in the input; if anything, verbs and function words are often more frequent in the input than nouns (e.g., Gentner, 1982).
+Goodman et al.
+(2008) found an effect of frequency on the age of acquisition within --- not across --- classes.
+Further, recent work by Braginsky et al.
+(2019) tested a large number of predictors, besides frequency, and found that these predictors do not influence the acquisition of word classes in the same way.
+For example, the acquisition of nouns was found to be most influenced by frequency and concreteness, whereas the acquisition of function words was most influenced by word length.
+
+This work shares a number of limitations with previous studies using similar research strategy and datasets.
+Chief among these limitations is the fact that the age of word acquisition is computed using different children at different ages (due to the fact that available CDI data is mainly cross-sectional).
+Such a measure has been shown to be valid and reliable (Fenson et al., 1994), and has allowed researchers to study important aspects of word learning (Braginsky et al., 2019; Goodman et al., 2008; Hills et al., 2009; Stella et al., 2017; Storkel, 2009).
+In our case, the use of cost-effective cross-sectional data has allowed us to leverage large-scale studies across several languages.
+That said, it is important to remember that this type of data can only inform us about the learning trajectory of the \enquote{average} child.
+Although our study endorses, overall, the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT (Beckage \& Colunga, n.d.).
+To illustrate, some children develop \enquote{islands of expertise,} that is, well-organized knowledge about a certain topic (e.g., birds or dinosaurs).
+This prior knowledge enables these children to learn new related words more easily (e.g., Chi \& Koeske, 1983).
+
+To conclude, our work validates and generalizes previous results in early network development.
+It suggests that the advantage of highly connected words may result, at least in the early stages of word learning, from the operation of simpler mechanisms in both the semantic and phonological domains.
+One question for future experimental work is whether such correlational patterns of growth can be produced in controlled behavioral experiments.
 
@@
 
-\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}}
-\vspace{1em}
-
-\section{Acknowledgements}\label{acknowledgements}
-
-This work was supported by a post-doctoral grant from the Fyssen
-Foundation, NSF \#1528526, and NSF \#1659585.
-
-\section{Disclosure statement}\label{disclosure-statement}
-
-None of the authors have any financial interest or a conflict of
-interest regarding this work and this submission.
+\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}} \vspace{1em}
+
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+This work was supported by a post-doctoral grant from the Fyssen Foundation, NSF \#1528526, and NSF \#1659585.
+
+\hypertarget{disclosure-statement}{%
+\section{Disclosure statement}\label{disclosure-statement}}
+
+None of the authors have any financial interest or a conflict of interest regarding this work and this submission.
 
@@
 
-\section{Appendix A: Analyses using different phnonological
-distances}\label{appendix-a-analyses-using-different-phnonological-distances}
-
-In the methods section, we based the choice of setting the threshold of
-edit distance at 2 on the fact that the early lexicon is very sparse in
-terms of phonological neighborhood; the early proposal that set the
-threshold at 1 (e.g., Vitevitch, 2008) was defined in the context of
-rather mature, dense lexicon. Increasing the threshold from 1 to 2
-allows for a more reasonable representation of the similarity space of
-the early phonological network.
-
-That said, it is useful to include the results obtained with both
-thresholds. In addition, it could be useful to compare the results to
-the case of weighted networks, i.e., with no thresholding. The main
-analyses for these two cases are shown in what follows. In summary, both
-methods of constructing the phonological networks had issues. While the
-fact of using an edit distance of 1 created sparsity, using weighted
-networks created collinearity with length in the models.
-
-\subsection{Analyses using phonological networks constructed with an
-edit distance of
-1}\label{analyses-using-phonological-networks-constructed-with-an-edit-distance-of-1}
-
-We show in Figure \ref{fig:corrPlot} the correlation between the
-phonological connectivity and age of acquisition in both comprehension
-and production. The sparsity issue --- due to the low phonological
-neighborhood in the children's lexicon --- is apparent: Most words had 0
-connectivity, and a few had non-zero but small degrees. The values of
-the correlations are much lower than the ones obtained with the
-threshold of 2.
-
-The next figures show how the phonology-based mechanism of growth
-(phonoEXT) fares in comaprison to semEXT and other predictors of
-learning in each language (Figure \ref{fig:staticPredEdit1} and across
-all languages (Figure \ref{fig:staticAllEdit}). These figures show that
-phonoEXT based on edit distance 1 had no noticeable effect on learning.
+\hypertarget{appendix-a-analyses-using-different-phnonological-distances}{%
+\section{Appendix A: Analyses using different phnonological distances}\label{appendix-a-analyses-using-different-phnonological-distances}}
+
+In the methods section, we based the choice of setting the threshold of edit distance at 2 on the fact that the early lexicon is very sparse in terms of phonological neighborhood; the early proposal that set the threshold at 1 (e.g., Vitevitch, 2008) was defined in the context of rather mature, dense lexicon.
+Increasing the threshold from 1 to 2 allows for a more reasonable representation of the similarity space of the early phonological network.
+
+That said, it is useful to include the results obtained with both thresholds.
+In addition, it could be useful to compare the results to the case of weighted networks, i.e., with no thresholding.
+The main analyses for these two cases are shown in what follows.
+In summary, both methods of constructing the phonological networks had issues.
+While the fact of using an edit distance of 1 created sparsity, using weighted networks created collinearity with length in the models.
+
+\hypertarget{analyses-using-phonological-networks-constructed-with-an-edit-distance-of-1}{%
+\subsection{Analyses using phonological networks constructed with an edit distance of 1}\label{analyses-using-phonological-networks-constructed-with-an-edit-distance-of-1}}
+
+We show in Figure \ref{fig:corrPlot} the correlation between the phonological connectivity and age of acquisition in both comprehension and production.
+The sparsity issue --- due to the low phonological neighborhood in the children's lexicon --- is apparent: Most words had 0 connectivity, and a few had non-zero but small degrees.
+The values of the correlations are much lower than the ones obtained with the threshold of 2.
+
+The next figures show how the phonology-based mechanism of growth (phonoEXT) fares in comaprison to semEXT and other predictors of learning in each language (Figure \ref{fig:staticPredEdit1} and across all languages (Figure \ref{fig:staticAllEdit}).
+These figures show that phonoEXT based on edit distance 1 had no noticeable effect on learning.
 
@@
 
-\subsection{Analyses using weighted phonological networks with no
-thresholding}\label{analyses-using-weighted-phonological-networks-with-no-thresholding}
-
-We constructed weighted phonological networks where the edge between a
-given pair of words \((w_1, w_2)\) was wieghted by
-\(\frac{1}{edit(w_1,w_2)}\). The phonological connectivity of a given
-word \(w\) was defined as the sum over all weighted edges with every
-other word \(w_i\) in the network, i.e.,
-\(\sum_{i} \frac{1}{edit(w,w_i)}\).
-
-The results were as follows. On the one hand, the correlations were
-generally high and in many cases (especially in the production data),
-higher than the ones obtained with the thresholds 2 and 1 (Figure
-\ref{fig:corrPlotnt}). On the other hand, phonoEXT resulted in very
-noisy estimates when we controlled for frequency and length (Figures
-\ref{fig:staticPrednt} and \ref{fig:staticAllnt}). The reason was that
-the new phonological connectivity was very highly correlated with
-length. The average correlation across languages was \(r =\) -0.95 for
-production data (compared to -0.29 and -0.60 for the phonological
-networks with an edit distance of 1 and 2, respectvely). This fact lead
-to a collinearity issue in the regression, making the effects hard to
-estimate and interpret.
+\hypertarget{analyses-using-weighted-phonological-networks-with-no-thresholding}{%
+\subsection{Analyses using weighted phonological networks with no thresholding}\label{analyses-using-weighted-phonological-networks-with-no-thresholding}}
+
+We constructed weighted phonological networks where the edge between a given pair of words \((w_1, w_2)\) was wieghted by \(\frac{1}{edit(w_1,w_2)}\).
+The phonological connectivity of a given word \(w\) was defined as the sum over all weighted edges with every other word \(w_i\) in the network, i.e., \(\sum_{i} \frac{1}{edit(w,w_i)}\).
+
+The results were as follows.
+On the one hand, the correlations were generally high and in many cases (especially in the production data), higher than the ones obtained with the thresholds 2 and 1 (Figure \ref{fig:corrPlotnt}).
+On the other hand, phonoEXT resulted in very noisy estimates when we controlled for frequency and length (Figures \ref{fig:staticPrednt} and \ref{fig:staticAllnt}).
+The reason was that the new phonological connectivity was very highly correlated with length.
+The average correlation across languages was \(r =\) -0.95 for production data (compared to -0.29 and -0.60 for the phonological networks with an edit distance of 1 and 2, respectvely).
+This fact lead to a collinearity issue in the regression, making the effects hard to estimate and interpret.
 
@@
 
-\section{Appendix B: Phonological connectivity across
-languages}\label{appendix-b-phonological-connectivity-across-languages}
-
-We were interested in investigating if, for a given meaning (e.g.,
-\enquote{dog} in English and \enquote{chien} in French), phonological
-connectivity varied across languages. For example, if \enquote{dog} is
-highly connected in the English phonological network, will
-\enquote{chien} also be highly connected in the French network, or will
-these two forms be situated independently in their relative phonological
-networks?
-
-If the phonological networks are very similar across languages, then
-network growth in the phonological domain may be deeply intertwined with
-growth in the semantic domain, rather than being an independent
-mechanism of acquisition. If, instead, the phonological connectivity is
-different from language to language, then this fact would lend support
-to phonological growth being an independent driving mechanism of early
-word learning.
-
-To test this hypothesis, we compute the correlation of the unilemma's
-phonological connectivity between every pair of languages. In Figure
-\ref{fig:corrPair}, we plot the distribution of the pairwise Pearson
-correlation coefficient. Generally speaking, languages are not highly
-correlated at the phonological level as the distributions peak at low
-values of \(r\), showing that phonological connectivity is not (at least
-not fully) determined semantically.
+\hypertarget{appendix-b-phonological-connectivity-across-languages}{%
+\section{Appendix B: Phonological connectivity across languages}\label{appendix-b-phonological-connectivity-across-languages}}
+
+We were interested in investigating if, for a given meaning (e.g., \enquote{dog} in English and \enquote{chien} in French), phonological connectivity varied across languages.
+For example, if \enquote{dog} is highly connected in the English phonological network, will \enquote{chien} also be highly connected in the French network, or will these two forms be situated independently in their relative phonological networks?
+
+If the phonological networks are very similar across languages, then network growth in the phonological domain may be deeply intertwined with growth in the semantic domain, rather than being an independent mechanism of acquisition.
+If, instead, the phonological connectivity is different from language to language, then this fact would lend support to phonological growth being an independent driving mechanism of early word learning.
+
+To test this hypothesis, we compute the correlation of the unilemma's phonological connectivity between every pair of languages.
+In Figure \ref{fig:corrPair}, we plot the distribution of the pairwise Pearson correlation coefficient.
+Generally speaking, languages are not highly correlated at the phonological level as the distributions peak at low values of \(r\), showing that phonological connectivity is not (at least not fully) determined semantically.
 
@@
 
-\section{References}\label{references}
-
-\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\hypertarget{ref-altvater2013}{}
-Altvater-Mackensen, N., \& Mani, N. (2013). Word-form familiarity
-bootstraps infant speech segmentation. \emph{Developmental Science},
-\emph{16}(6).
-
-\hypertarget{ref-arbesman2010}{}
-Arbesman, S., Strogatz, S. H., \& Vitevitch, M. S. (2010). The structure
-of phonological networks across multiple languages. \emph{International
-Journal of Bifurcation and Chaos}, \emph{20}(03), 679--685.
-
-\hypertarget{ref-aslin2012}{}
-Aslin, R. N., \& Newport, E. L. (2012). Statistical learning: From
-acquiring specific items to forming general rules. \emph{Current
-Directions in Psychological Science}, \emph{21}(3).
-
-\hypertarget{ref-barabasi99}{}
-Barabasi, A.-L., \& Albert, R. (1999). Emergence of scaling in random
-networks. \emph{Science}, \emph{286}(5439), 509--512.
-
-\hypertarget{ref-bates1987}{}
-Bates, E., \& MacWhinney, B. (1987). Competition, variation, and
-language learning. In B. MacWhinney (Ed.), \emph{Mechanisms of language
-acquisition}. Erlbaum.
-
-\hypertarget{ref-bates1995}{}
-Bates, E., Dale, P. S., \& Thal, D. (1995). Individual differences and
-their implications for theories of language development. In P. Fletcher
-\& B. MacWhinney (Eds.), \emph{The handbook of child language}. Oxford,
-England: Blackwell.
-
-\hypertarget{ref-bates1994}{}
-Bates, E., Marchman, V., Thal, D., Fenson, L., Dale, P., Reznick, J. S.,
-\ldots{} Hartung, J. (1994). Developmental and stylistic variation in
-the composition of early vocabulary. \emph{Journal of Child Language},
-\emph{21}(1).
-
-\hypertarget{ref-beckage2016}{}
-Beckage, N. M., \& Colunga, E. (2016). Language networks as models of
-cognition: Understanding cognition through language. In \emph{Towards a
-theoretical framework for analyzing complex linguistic networks} (pp.
-3--28). Springer.
-
-\hypertarget{ref-beckage}{}
-Beckage, N. M., \& Colunga, E. (under review). Network growth modeling
-to capture individual lexical learning.
-
-\hypertarget{ref-benedict1979}{}
-Benedict, H. (1979). Early lexical development: Comprehension and
-production. \emph{Journal of Child Language}, \emph{6}(2), 183--200.
-
-\hypertarget{ref-borovsky2016}{}
-Borovsky, A., Ellis, E. M., Evans, J. L., \& Elman, J. L. (2016).
-Lexical leverage: Category knowledge boosts real-time novel word
-recognition in 2-year-olds. \emph{Developmental Science}, \emph{19}(6).
-
-\hypertarget{ref-braginsky2019}{}
-Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (2019).
-Consistency and variability in children?s word learning across
-languages. \emph{Open Mind}, \emph{3}.
-
-\hypertarget{ref-carlson2014}{}
-Carlson, M. T., Sonderegger, M., \& Bane, M. (2014). How children
-explore the phonological network in child-directed speech: A survival
-analysis of children's first word productions. \emph{Journal of Memory
-and Language}, \emph{75}, 159--180.
-
-\hypertarget{ref-chi1983}{}
-Chi, M. T., \& Koeske, R. D. (1983). Network representation of a child's
-dinosaur knowledge. \emph{Developmental Psychology}, \emph{19}(1).
-
-\hypertarget{ref-clark2007}{}
-Clark, E. V. (2007). Young children's uptake of new words in
-conversation. \emph{Language in Society}, \emph{36}(2).
-
-\hypertarget{ref-clauset09}{}
-Clauset, A., Shalizi, C. R., \& Newman, M. E. J. (2009). Power-law
-distributions in empirical data. \emph{SIAM Review}, \emph{51}(4),
-661--703.
-
-\hypertarget{ref-collins1975}{}
-Collins, A. M., \& Loftus, E. F. (1975). A spreading-activation theory
-of semantic processing. \emph{Psychological Review}, \emph{82}(6).
-
-\hypertarget{ref-cristia2017}{}
-Cristia, A., Dupoux, E., Gurven, M., \& Stieglitz, J. (2017).
-Child-directed speech is infrequent in a forager-farmer population: A
-time allocation study. \emph{Child Development}.
-
-\hypertarget{ref-dell1993}{}
-Dell, G. S., Juliano, C., \& Govindjee, A. (1993). Structure and content
-in language production: A theory of frame constraints in phonological
-speech errors. \emph{Cognitive Science}, \emph{17}(2), 149--195.
-
-\hypertarget{ref-fenson94}{}
-Fenson, L., Dale, P. S., Reznick, J. S., Bates, E., Thal, D. J.,
-Pethick, S. J., \ldots{} Stiles, J. (1994). Variability in early
-communicative development. \emph{Monographs of the Society for Research
-in Child Development}, \emph{59}(5).
-
-\hypertarget{ref-fourtassi2013}{}
-Fourtassi, A., \& Dupoux, E. (2013). A corpus-based evaluation method
-for distributional semantic models. In \emph{51st annual meeting of the
-association for computational linguistics proceedings of the student
-research workshop} (pp. 165--171).
-
-\hypertarget{ref-frank2017}{}
-Frank, M. C., Braginsky, M., Yurovsky, D., \& Marchman, V. A. (2017).
-Wordbank: An open repository for developmental vocabulary data.
-\emph{Journal of Child Language}, \emph{44}(3), 677--694.
-
-\hypertarget{ref-gentner1982}{}
-Gentner, D. (1982). Why nouns are learned before verbs: Linguistic
-relativity versus natural partitioning. \emph{Center for the Study of
-Reading Technical Report}.
-
-\hypertarget{ref-gillespie15}{}
-Gillespie, C. S. (2015). Fitting heavy tailed distributions: The
-poweRlaw package. \emph{Journal of Statistical Software}, \emph{64}(2),
-1--16. Retrieved from \url{http://www.jstatsoft.org/v64/i02/}
-
-\hypertarget{ref-goodman2008}{}
-Goodman, J. C., Dale, P. S., \& Li, P. (2008). Does frequency count?
-Parental input and the acquisition of vocabulary. \emph{Journal of Child
-Language}, \emph{35}(3), 515--531.
-
-\hypertarget{ref-dippl}{}
-Goodman, N., \& Stuhlmuller, A. (2014). The Design and Implementation of
-Probabilistic Programming Languages. \url{http://dippl.org}.
-
-\hypertarget{ref-griffiths07}{}
-Griffiths, T. L., Steyvers, M., \& Tenenbaum, J. B. (2007). Topics in
-semantic representation. \emph{Psychological Review}, \emph{114}(2),
-2007.
-
-\hypertarget{ref-hills2018}{}
-Hills, T. T., \& Siew, C. S. (2018). Filling gaps in early word
-learning. \emph{Nature Human Behaviour}, \emph{2}(9).
-
-\hypertarget{ref-hills2010}{}
-Hills, T. T., Maouene, J., Riordan, B., \& Smith, L. B. (2010). The
-associative structure of language: Contextual diversity in early word
-learning. \emph{Journal of Memory and Language}, \emph{63}(3), 259--273.
-
-\hypertarget{ref-hills2009}{}
-Hills, T. T., Maouene, M., Maouene, J., Sheya, A., \& Smith, L. (2009).
-Longitudinal analysis of early semantic networks: Preferential
-attachment or preferential acquisition? \emph{Psychological Science},
-\emph{20}(6), 729--739.
-
-\hypertarget{ref-hoff2002}{}
-Hoff, E., \& Naigles, L. (2002). How children use input to acquire a
-lexicon. \emph{Child Development}, \emph{73}(2).
-
-\hypertarget{ref-huttenlocher1991}{}
-Huttenlocher, J., Haight, W., Bryk, A., Seltzer, M., \& Lyons, T.
-(1991). Early vocabulary growth: Relation to language input and gender.
-\emph{Developmental Psychology}, \emph{27}(2).
-
-\hypertarget{ref-jusczyk1994}{}
-Jusczyk, P. W., Luce, P. A., \& Charles-Luce, J. (1994). Infant's
-sensitivity to phonotactic patterns in the native language.
-\emph{Journal of Memory and Language}, \emph{33}(5), 630--645.
-
-\hypertarget{ref-kachergis2011}{}
-Kachergis, G., Cox, G. E., \& Jones, M. N. (2011). OrBEAGLE: Integrating
-orthography into a holographic model of the lexicon. In
-\emph{International conference on artificial neural networks} (pp.
-307--314). Springer.
-
-\hypertarget{ref-karuza2016}{}
-Karuza, E. A., Thompson-Schill, S. L., \& Bassett, D. S. (2016). Local
-patterns to global architectures: Influences of network topology on
-human learning. \emph{Trends in Cognitive Sciences}, \emph{20}(8).
-
-\hypertarget{ref-kuhl1997}{}
-Kuhl, P. K., Andruski, J. E., Chistovich, I. A., Chistovich, L. A.,
-Kozhevnikova, E. V., Ryskina, V. L., \ldots{} Lacerda, F. (1997).
-Cross-language analysis of phonetic units in language addressed to
-infants. \emph{Science}, \emph{277}(5326), 684--686.
-
-\hypertarget{ref-luce1998}{}
-Luce, P. A., \& Pisoni, D. B. (1998). Recognizing spoken words: The
-neighborhood activation model. \emph{Ear and Hearing}, \emph{19}(1).
-
-\hypertarget{ref-lupyan2017}{}
-Lupyan, G., \& Lewis, M. (2017). From words-as-mappings to
-words-as-cues: The role of language in semantic knowledge.
-\emph{Language, Cognition and Neuroscience}.
-
-\hypertarget{ref-macwhinney2014}{}
-MacWhinney, B. (2014). \emph{The CHILDES project: Tools for analyzing
-talk, Volume II}. Psychology Press.
-
-\hypertarget{ref-markman90}{}
-Markman, E. M. (1990). Constraints children place on word meanings.
-\emph{Cognitive Science}, \emph{14}(1), 57--77.
-
-\hypertarget{ref-matusevych2018}{}
-Matusevych, Y., \& Stevenson, S. (2018). Analyzing and modeling free
-word associations. In \emph{Proceedings of the 40th Annual Conference of
-the Cognitive Science Society}.
-
-\hypertarget{ref-mcmurray2012}{}
-McMurray, B., Horst, J. S., \& Samuelson, L. K. (2012). Word learning
-emerges from the interaction of online referent selection and slow
-associative learning. \emph{Psychological Review}, \emph{119}.
-
-\hypertarget{ref-mcrae2005}{}
-McRae, K., Cree, G. S., Seidenberg, M. S., \& McNorgan, C. (2005).
-Semantic feature production norms for a large set of living and
-nonliving things. \emph{Behavior Research Methods}, \emph{37}(4),
-547--559.
-
-\hypertarget{ref-nelson1998}{}
-Nelson, D. L., McEvoy, C. L., \& Schreiber, T. A. (1998). \emph{The
-University of South Florida word association, rhyme, and word fragment
-norms}. Retrieved from \url{http://w3.usf.edu/FreeAssociation/}
-
-\hypertarget{ref-pisoni1985}{}
-Pisoni, D. B., Nusbaum, H. C., Luce, P. A., \& Slowiaczek, L. M. (1985).
-Speech perception, word recognition and the structure of the lexicon.
-\emph{Speech Communication}, \emph{4}(1), 75--95.
-
-\hypertarget{ref-roy2015}{}
-Roy, B. C., Frank, M. C., DeCamp, P., Miller, M., \& Roy, D. (2015).
-Predicting the birth of a spoken word. \emph{Proceedings of the National
-Academy of Sciences}, \emph{112}(41).
-
-\hypertarget{ref-saffran1996}{}
-Saffran, J. R., Aslin, R. N., \& Newport, E. L. (1996). Statistical
-learning by 8-month-old infants. \emph{Science}, \emph{274}(5294),
-1926--1928.
-
-\hypertarget{ref-siew2013}{}
-Siew, C. S. (2013). Community structure in the phonological network.
-\emph{Frontiers in Psychology}, \emph{4}.
-
-\hypertarget{ref-slobin2014}{}
-Slobin, D. I. (2014). \emph{The crosslinguistic study of language
-acquisition} (Vol. 4). Psychology Press.
-
-\hypertarget{ref-smith2008}{}
-Smith, L., \& Yu, C. (2008). Infants rapidly learn word-referent
-mappings via cross-situational statistics. \emph{Cognition},
-\emph{106}(3).
-
-\hypertarget{ref-stella2017}{}
-Stella, M., Beckage, N. M., \& Brede, M. (2017). Multiplex lexical
-networks reveal patterns in early word acquisition in children.
-\emph{Scientific Reports}, \emph{7}.
-
-\hypertarget{ref-steyvers2005}{}
-Steyvers, M., \& Tenenbaum, J. B. (2005). The large-scale structure of
-semantic networks: Statistical analyses and a model of semantic growth.
-\emph{Cognitive Science}, \emph{29}(1), 41--78.
-
-\hypertarget{ref-storkel2001}{}
-Storkel, H. L. (2001). Learning new words: Phonotactic probability in
-language development. \emph{Journal of Speech, Language, and Hearing
-Research}, \emph{44}(6), 1321--1337.
-
-\hypertarget{ref-storkel2009}{}
-Storkel, H. L. (2009). Developmental differences in the effects of
-phonological, lexical and semantic variables on word learning by
-infants. \emph{Journal of Child Language}, \emph{36}(2), 29--321.
-
-\hypertarget{ref-swingley2018}{}
-Swingley, D., \& Humphrey, C. (2018). Quantitative linguistic predictors
-of infants' learning of specific english words. \emph{Child
-Development}, \emph{89}(4).
-
-\hypertarget{ref-takac2017}{}
-Takac, M., Knott, A., \& Stokes, S. (2017). What can neighbourhood
-density effects tell us about word learning? Insights from a
-connectionist model of vocabulary development. \emph{Journal of Child
-Language}, \emph{44}(2).
-
-\hypertarget{ref-vitevitch2008}{}
-Vitevitch, M. S. (2008). What can graph theory tell us about word
-learning and lexical retrieval? \emph{Journal of Speech, Language, and
-Hearing Research}, \emph{51}(2), 408--422.
-
-\hypertarget{ref-vitevitch2005}{}
-Vitevitch, M. S., \& Rodríguez, E. (2005). Neighborhood density effects
-in spoken word recognition in spanish. \emph{Journal of Multilingual
-Communication Disorders}, \emph{3}(1).
-
-\hypertarget{ref-vitevitch1999}{}
-Vitevitch, M. S., Luce, P. A., Pisoni, D. B., \& Auer, E. T. (1999).
-Phonotactics, neighborhood activation, and lexical access for spoken
-words. \emph{Brain and Language}, \emph{68}(1), 306--311.
-
-\hypertarget{ref-youn2016}{}
-Youn, H., Sutton, L., Smith, E., Moore, C., Wilkins, J. F., Maddieson,
-I., \ldots{} Bhattacharya, T. (2016). On the universal structure of
-human lexical semantics. \emph{Proceedings of the National Academy of
-Sciences}, \emph{113}(7), 1766--1771.
-
-\hypertarget{ref-yurovsky2015}{}
-Yurovsky, D., \& Frank, M. C. (2015). An integrative account of
-constraints on cross-situational learning. \emph{Cognition}, \emph{145}.
+\leavevmode\hypertarget{ref-altvater2013}{}%
+Altvater-Mackensen, N., \& Mani, N. (2013). Word-form familiarity bootstraps infant speech segmentation. \emph{Developmental Science}, \emph{16}(6).
+
+\leavevmode\hypertarget{ref-arbesman2010}{}%
+Arbesman, S., Strogatz, S.
+H., \& Vitevitch, M.
+S.
+(2010).
+The structure of phonological networks across multiple languages.
+\emph{International Journal of Bifurcation and Chaos}, \emph{20}(03), 679--685.
+
+\leavevmode\hypertarget{ref-aslin2012}{}%
+Aslin, R. N., \& Newport, E. L. (2012). Statistical learning: From acquiring specific items to forming general rules. \emph{Current Directions in Psychological Science}, \emph{21}(3).
+
+\leavevmode\hypertarget{ref-barabasi99}{}%
+Barabasi, A.-L., \& Albert, R. (1999). Emergence of scaling in random networks. \emph{Science}, \emph{286}(5439), 509--512.
+
+\leavevmode\hypertarget{ref-bates1995}{}%
+Bates, E., Dale, P.
+S., \& Thal, D.
+(1995).
+Individual differences and their implications for theories of language development.
+In P.
+Fletcher \& B.
+MacWhinney (Eds.), \emph{The handbook of child language}.
+Oxford, England: Blackwell.
+
+\leavevmode\hypertarget{ref-bates1987}{}%
+Bates, E., \& MacWhinney, B. (1987). Competition, variation, and language learning. In B. MacWhinney (Ed.), \emph{Mechanisms of language acquisition}. Erlbaum.
+
+\leavevmode\hypertarget{ref-bates1994}{}%
+Bates, E., Marchman, V., Thal, D., Fenson, L., Dale, P., Reznick, J.
+S., \ldots{} Hartung, J.
+(1994).
+Developmental and stylistic variation in the composition of early vocabulary.
+\emph{Journal of Child Language}, \emph{21}(1).
+
+\leavevmode\hypertarget{ref-beckage2016}{}%
+Beckage, N.
+M., \& Colunga, E.
+(2016).
+Language networks as models of cognition: Understanding cognition through language.
+In \emph{Towards a theoretical framework for analyzing complex linguistic networks} (pp.
+3--28).
+Springer.
+
+\leavevmode\hypertarget{ref-beckage}{}%
+Beckage, N. M., \& Colunga, E. (n.d.). Network growth modeling to capture individual lexical learning.
+
+\leavevmode\hypertarget{ref-benedict1979}{}%
+Benedict, H. (1979). Early lexical development: Comprehension and production. \emph{Journal of Child Language}, \emph{6}(2), 183--200.
+
+\leavevmode\hypertarget{ref-borovsky2016}{}%
+Borovsky, A., Ellis, E.
+M., Evans, J.
+L., \& Elman, J.
+L.
+(2016).
+Lexical leverage: Category knowledge boosts real-time novel word recognition in 2-year-olds.
+\emph{Developmental Science}, \emph{19}(6).
+
+\leavevmode\hypertarget{ref-braginsky2019}{}%
+Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (2019). Consistency and variability in children?S word learning across languages. \emph{Open Mind}, \emph{3}.
+
+\leavevmode\hypertarget{ref-carlson2014}{}%
+Carlson, M.
+T., Sonderegger, M., \& Bane, M.
+(2014).
+How children explore the phonological network in child-directed speech: A survival analysis of children's first word productions.
+\emph{Journal of Memory and Language}, \emph{75}, 159--180.
+
+\leavevmode\hypertarget{ref-chi1983}{}%
+Chi, M. T., \& Koeske, R. D. (1983). Network representation of a child's dinosaur knowledge. \emph{Developmental Psychology}, \emph{19}(1).
+
+\leavevmode\hypertarget{ref-clark2007}{}%
+Clark, E. V. (2007). Young children's uptake of new words in conversation. \emph{Language in Society}, \emph{36}(2).
+
+\leavevmode\hypertarget{ref-clauset09}{}%
+Clauset, A., Shalizi, C. R., \& Newman, M. E. J. (2009). Power-law distributions in empirical data. \emph{SIAM Review}, \emph{51}(4), 661--703.
+
+\leavevmode\hypertarget{ref-collins1975}{}%
+Collins, A. M., \& Loftus, E. F. (1975). A spreading-activation theory of semantic processing. \emph{Psychological Review}, \emph{82}(6).
+
+\leavevmode\hypertarget{ref-cristia2017}{}%
+Cristia, A., Dupoux, E., Gurven, M., \& Stieglitz, J. (2017). Child-directed speech is infrequent in a forager-farmer population: A time allocation study. \emph{Child Development}.
+
+\leavevmode\hypertarget{ref-dell1993}{}%
+Dell, G.
+S., Juliano, C., \& Govindjee, A.
+(1993).
+Structure and content in language production: A theory of frame constraints in phonological speech errors.
+\emph{Cognitive Science}, \emph{17}(2), 149--195.
+
+\leavevmode\hypertarget{ref-fenson94}{}%
+Fenson, L., Dale, P.
+S., Reznick, J.
+S., Bates, E., Thal, D.
+J., Pethick, S.
+J., \ldots{} Stiles, J.
+(1994).
+Variability in early communicative development.
+\emph{Monographs of the Society for Research in Child Development}, \emph{59}(5).
+
+\leavevmode\hypertarget{ref-fourtassi2013}{}%
+Fourtassi, A., \& Dupoux, E.
+(2013).
+A corpus-based evaluation method for distributional semantic models.
+In \emph{51st annual meeting of the association for computational linguistics proceedings of the student research workshop} (pp.
+165--171).
+
+\leavevmode\hypertarget{ref-frank2017}{}%
+Frank, M. C., Braginsky, M., Yurovsky, D., \& Marchman, V. A. (2017). Wordbank: An open repository for developmental vocabulary data. \emph{Journal of Child Language}, \emph{44}(3), 677--694.
+
+\leavevmode\hypertarget{ref-gentner1982}{}%
+Gentner, D. (1982). Why nouns are learned before verbs: Linguistic relativity versus natural partitioning. \emph{Center for the Study of Reading Technical Report}.
+
+\leavevmode\hypertarget{ref-gillespie15}{}%
+Gillespie, C. S. (2015). Fitting heavy tailed distributions: The poweRlaw package. \emph{Journal of Statistical Software}, \emph{64}(2), 1--16. Retrieved from \url{http://www.jstatsoft.org/v64/i02/}
+
+\leavevmode\hypertarget{ref-goodman2008}{}%
+Goodman, J. C., Dale, P. S., \& Li, P. (2008). Does frequency count? Parental input and the acquisition of vocabulary. \emph{Journal of Child Language}, \emph{35}(3), 515--531.
+
+\leavevmode\hypertarget{ref-dippl}{}%
+Goodman, N., \& Stuhlmuller, A. (2014). The Design and Implementation of Probabilistic Programming Languages. \url{http://dippl.org}.
+
+\leavevmode\hypertarget{ref-griffiths07}{}%
+Griffiths, T. L., Steyvers, M., \& Tenenbaum, J. B. (2007). Topics in semantic representation. \emph{Psychological Review}, \emph{114}(2), 2007.
+
+\leavevmode\hypertarget{ref-hills2010}{}%
+Hills, T.
+T., Maouene, J., Riordan, B., \& Smith, L.
+B.
+(2010).
+The associative structure of language: Contextual diversity in early word learning.
+\emph{Journal of Memory and Language}, \emph{63}(3), 259--273.
+
+\leavevmode\hypertarget{ref-hills2009}{}%
+Hills, T.
+T., Maouene, M., Maouene, J., Sheya, A., \& Smith, L.
+(2009).
+Longitudinal analysis of early semantic networks: Preferential attachment or preferential acquisition?
+\emph{Psychological Science}, \emph{20}(6), 729--739.
+
+\leavevmode\hypertarget{ref-hills2018}{}%
+Hills, T. T., \& Siew, C. S. (2018). Filling gaps in early word learning. \emph{Nature Human Behaviour}, \emph{2}(9).
+
+\leavevmode\hypertarget{ref-hoff2002}{}%
+Hoff, E., \& Naigles, L. (2002). How children use input to acquire a lexicon. \emph{Child Development}, \emph{73}(2).
+
+\leavevmode\hypertarget{ref-huttenlocher1991}{}%
+Huttenlocher, J., Haight, W., Bryk, A., Seltzer, M., \& Lyons, T. (1991). Early vocabulary growth: Relation to language input and gender. \emph{Developmental Psychology}, \emph{27}(2).
+
+\leavevmode\hypertarget{ref-jusczyk1994}{}%
+Jusczyk, P. W., Luce, P. A., \& Charles-Luce, J. (1994). Infant's sensitivity to phonotactic patterns in the native language. \emph{Journal of Memory and Language}, \emph{33}(5), 630--645.
+
+\leavevmode\hypertarget{ref-kachergis2011}{}%
+Kachergis, G., Cox, G.
+E., \& Jones, M.
+N.
+(2011).
+OrBEAGLE: Integrating orthography into a holographic model of the lexicon.
+In \emph{International conference on artificial neural networks} (pp.
+307--314).
+Springer.
+
+\leavevmode\hypertarget{ref-karuza2016}{}%
+Karuza, E.
+A., Thompson-Schill, S.
+L., \& Bassett, D.
+S.
+(2016).
+Local patterns to global architectures: Influences of network topology on human learning.
+\emph{Trends in Cognitive Sciences}, \emph{20}(8).
+
+\leavevmode\hypertarget{ref-kuhl1997}{}%
+Kuhl, P.
+K., Andruski, J.
+E., Chistovich, I.
+A., Chistovich, L.
+A., Kozhevnikova, E.
+V., Ryskina, V.
+L., \ldots{} Lacerda, F.
+(1997).
+Cross-language analysis of phonetic units in language addressed to infants.
+\emph{Science}, \emph{277}(5326), 684--686.
+
+\leavevmode\hypertarget{ref-luce1998}{}%
+Luce, P. A., \& Pisoni, D. B. (1998). Recognizing spoken words: The neighborhood activation model. \emph{Ear and Hearing}, \emph{19}(1).
+
+\leavevmode\hypertarget{ref-lupyan2017}{}%
+Lupyan, G., \& Lewis, M. (2017). From words-as-mappings to words-as-cues: The role of language in semantic knowledge. \emph{Language, Cognition and Neuroscience}.
+
+\leavevmode\hypertarget{ref-macwhinney2014}{}%
+MacWhinney, B. (2014). \emph{The CHILDES project: Tools for analyzing talk, Volume II}. Psychology Press.
+
+\leavevmode\hypertarget{ref-markman90}{}%
+Markman, E. M. (1990). Constraints children place on word meanings. \emph{Cognitive Science}, \emph{14}(1), 57--77.
+
+\leavevmode\hypertarget{ref-matusevych2018}{}%
+Matusevych, Y., \& Stevenson, S. (2018). Analyzing and modeling free word associations. In \emph{Proceedings of the 40th Annual Conference of the Cognitive Science Society}.
+
+\leavevmode\hypertarget{ref-mcmurray2012}{}%
+McMurray, B., Horst, J. S., \& Samuelson, L. K. (2012). Word learning emerges from the interaction of online referent selection and slow associative learning. \emph{Psychological Review}, \emph{119}.
+
+\leavevmode\hypertarget{ref-mcrae2005}{}%
+McRae, K., Cree, G.
+S., Seidenberg, M.
+S., \& McNorgan, C.
+(2005).
+Semantic feature production norms for a large set of living and nonliving things.
+\emph{Behavior Research Methods}, \emph{37}(4), 547--559.
+
+\leavevmode\hypertarget{ref-nelson1998}{}%
+Nelson, D. L., McEvoy, C. L., \& Schreiber, T. A. (1998). The University of South Florida word association, rhyme, and word fragment norms. Retrieved from \url{http://w3.usf.edu/FreeAssociation/}
+
+\leavevmode\hypertarget{ref-pisoni1985}{}%
+Pisoni, D. B., Nusbaum, H. C., Luce, P. A., \& Slowiaczek, L. M. (1985). Speech perception, word recognition and the structure of the lexicon. \emph{Speech Communication}, \emph{4}(1), 75--95.
+
+\leavevmode\hypertarget{ref-roy2015}{}%
+Roy, B. C., Frank, M. C., DeCamp, P., Miller, M., \& Roy, D. (2015). Predicting the birth of a spoken word. \emph{Proceedings of the National Academy of Sciences}, \emph{112}(41).
+
+\leavevmode\hypertarget{ref-saffran1996}{}%
+Saffran, J. R., Aslin, R. N., \& Newport, E. L. (1996). Statistical learning by 8-month-old infants. \emph{Science}, \emph{274}(5294), 1926--1928.
+
+\leavevmode\hypertarget{ref-siew2013}{}%
+Siew, C. S. (2013). Community structure in the phonological network. \emph{Frontiers in Psychology}, \emph{4}.
+
+\leavevmode\hypertarget{ref-slobin2014}{}%
+Slobin, D. I. (2014). \emph{The crosslinguistic study of language acquisition} (Vol. 4). Psychology Press.
+
+\leavevmode\hypertarget{ref-smith2008}{}%
+Smith, L., \& Yu, C. (2008). Infants rapidly learn word-referent mappings via cross-situational statistics. \emph{Cognition}, \emph{106}(3).
+
+\leavevmode\hypertarget{ref-stella2017}{}%
+Stella, M., Beckage, N. M., \& Brede, M. (2017). Multiplex lexical networks reveal patterns in early word acquisition in children. \emph{Scientific Reports}, \emph{7}.
+
+\leavevmode\hypertarget{ref-steyvers2005}{}%
+Steyvers, M., \& Tenenbaum, J. B. (2005). The large-scale structure of semantic networks: Statistical analyses and a model of semantic growth. \emph{Cognitive Science}, \emph{29}(1), 41--78.
+
+\leavevmode\hypertarget{ref-storkel2001}{}%
+Storkel, H. L. (2001). Learning new words: Phonotactic probability in language development. \emph{Journal of Speech, Language, and Hearing Research}, \emph{44}(6), 1321--1337.
+
+\leavevmode\hypertarget{ref-storkel2009}{}%
+Storkel, H. L. (2009). Developmental differences in the effects of phonological, lexical and semantic variables on word learning by infants. \emph{Journal of Child Language}, \emph{36}(2), 29--321.
+
+\leavevmode\hypertarget{ref-swingley2018}{}%
+Swingley, D., \& Humphrey, C. (2018). Quantitative linguistic predictors of infants' learning of specific english words. \emph{Child Development}, \emph{89}(4).
+
+\leavevmode\hypertarget{ref-takac2017}{}%
+Takac, M., Knott, A., \& Stokes, S.
+(2017).
+What can neighbourhood density effects tell us about word learning?
+Insights from a connectionist model of vocabulary development.
+\emph{Journal of Child Language}, \emph{44}(2).
+
+\leavevmode\hypertarget{ref-vitevitch2008}{}%
+Vitevitch, M. S. (2008). What can graph theory tell us about word learning and lexical retrieval? \emph{Journal of Speech, Language, and Hearing Research}, \emph{51}(2), 408--422.
+
+\leavevmode\hypertarget{ref-vitevitch1999}{}%
+Vitevitch, M. S., Luce, P. A., Pisoni, D. B., \& Auer, E. T. (1999). Phonotactics, neighborhood activation, and lexical access for spoken words. \emph{Brain and Language}, \emph{68}(1), 306--311.
+
+\leavevmode\hypertarget{ref-vitevitch2005}{}%
+Vitevitch, M. S., \& Rodrı'guez, E. (2005). Neighborhood density effects in spoken word recognition in spanish. \emph{Journal of Multilingual Communication Disorders}, \emph{3}(1).
+
+\leavevmode\hypertarget{ref-youn2016}{}%
+Youn, H., Sutton, L., Smith, E., Moore, C., Wilkins, J.
+F., Maddieson, I., \ldots{} Bhattacharya, T.
+(2016).
+On the universal structure of human lexical semantics.
+\emph{Proceedings of the National Academy of Sciences}, \emph{113}(7), 1766--1771.
+
+\leavevmode\hypertarget{ref-yurovsky2015}{}%
+Yurovsky, D., \& Frank, M. C. (2015). An integrative account of constraints on cross-situational learning. \emph{Cognition}, \emph{145}.
+
+\leavevmode\hypertarget{ref-altvater2013}{}%
+Altvater-Mackensen, N., \& Mani, N. (2013). Word-form familiarity bootstraps infant speech segmentation. \emph{Developmental Science}, \emph{16}(6).
+
+\leavevmode\hypertarget{ref-arbesman2010}{}%
+Arbesman, S., Strogatz, S.
+H., \& Vitevitch, M.
+S.
+(2010).
+The structure of phonological networks across multiple languages.
+\emph{International Journal of Bifurcation and Chaos}, \emph{20}(03), 679--685.
+
+\leavevmode\hypertarget{ref-aslin2012}{}%
+Aslin, R. N., \& Newport, E. L. (2012). Statistical learning: From acquiring specific items to forming general rules. \emph{Current Directions in Psychological Science}, \emph{21}(3).
+
+\leavevmode\hypertarget{ref-barabasi99}{}%
+Barabasi, A.-L., \& Albert, R. (1999). Emergence of scaling in random networks. \emph{Science}, \emph{286}(5439), 509--512.
+
+\leavevmode\hypertarget{ref-bates1995}{}%
+Bates, E., Dale, P.
+S., \& Thal, D.
+(1995).
+Individual differences and their implications for theories of language development.
+In P.
+Fletcher \& B.
+MacWhinney (Eds.), \emph{The handbook of child language}.
+Oxford, England: Blackwell.
+
+\leavevmode\hypertarget{ref-bates1987}{}%
+Bates, E., \& MacWhinney, B. (1987). Competition, variation, and language learning. In B. MacWhinney (Ed.), \emph{Mechanisms of language acquisition}. Erlbaum.
+
+\leavevmode\hypertarget{ref-bates1994}{}%
+Bates, E., Marchman, V., Thal, D., Fenson, L., Dale, P., Reznick, J.
+S., \ldots{} Hartung, J.
+(1994).
+Developmental and stylistic variation in the composition of early vocabulary.
+\emph{Journal of Child Language}, \emph{21}(1).
+
+\leavevmode\hypertarget{ref-beckage2016}{}%
+Beckage, N.
+M., \& Colunga, E.
+(2016).
+Language networks as models of cognition: Understanding cognition through language.
+In \emph{Towards a theoretical framework for analyzing complex linguistic networks} (pp.
+3--28).
+Springer.
+
+\leavevmode\hypertarget{ref-beckage}{}%
+Beckage, N. M., \& Colunga, E. (n.d.). Network growth modeling to capture individual lexical learning.
+
+\leavevmode\hypertarget{ref-benedict1979}{}%
+Benedict, H. (1979). Early lexical development: Comprehension and production. \emph{Journal of Child Language}, \emph{6}(2), 183--200.
+
+\leavevmode\hypertarget{ref-borovsky2016}{}%
+Borovsky, A., Ellis, E.
+M., Evans, J.
+L., \& Elman, J.
+L.
+(2016).
+Lexical leverage: Category knowledge boosts real-time novel word recognition in 2-year-olds.
+\emph{Developmental Science}, \emph{19}(6).
+
+\leavevmode\hypertarget{ref-braginsky2019}{}%
+Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (2019). Consistency and variability in children?S word learning across languages. \emph{Open Mind}, \emph{3}.
+
+\leavevmode\hypertarget{ref-carlson2014}{}%
+Carlson, M.
+T., Sonderegger, M., \& Bane, M.
+(2014).
+How children explore the phonological network in child-directed speech: A survival analysis of children's first word productions.
+\emph{Journal of Memory and Language}, \emph{75}, 159--180.
+
+\leavevmode\hypertarget{ref-chi1983}{}%
+Chi, M. T., \& Koeske, R. D. (1983). Network representation of a child's dinosaur knowledge. \emph{Developmental Psychology}, \emph{19}(1).
+
+\leavevmode\hypertarget{ref-clark2007}{}%
+Clark, E. V. (2007). Young children's uptake of new words in conversation. \emph{Language in Society}, \emph{36}(2).
+
+\leavevmode\hypertarget{ref-clauset09}{}%
+Clauset, A., Shalizi, C. R., \& Newman, M. E. J. (2009). Power-law distributions in empirical data. \emph{SIAM Review}, \emph{51}(4), 661--703.
+
+\leavevmode\hypertarget{ref-collins1975}{}%
+Collins, A. M., \& Loftus, E. F. (1975). A spreading-activation theory of semantic processing. \emph{Psychological Review}, \emph{82}(6).
+
+\leavevmode\hypertarget{ref-cristia2017}{}%
+Cristia, A., Dupoux, E., Gurven, M., \& Stieglitz, J. (2017). Child-directed speech is infrequent in a forager-farmer population: A time allocation study. \emph{Child Development}.
+
+\leavevmode\hypertarget{ref-dell1993}{}%
+Dell, G.
+S., Juliano, C., \& Govindjee, A.
+(1993).
+Structure and content in language production: A theory of frame constraints in phonological speech errors.
+\emph{Cognitive Science}, \emph{17}(2), 149--195.
+
+\leavevmode\hypertarget{ref-fenson94}{}%
+Fenson, L., Dale, P.
+S., Reznick, J.
+S., Bates, E., Thal, D.
+J., Pethick, S.
+J., \ldots{} Stiles, J.
+(1994).
+Variability in early communicative development.
+\emph{Monographs of the Society for Research in Child Development}, \emph{59}(5).
+
+\leavevmode\hypertarget{ref-fourtassi2013}{}%
+Fourtassi, A., \& Dupoux, E.
+(2013).
+A corpus-based evaluation method for distributional semantic models.
+In \emph{51st annual meeting of the association for computational linguistics proceedings of the student research workshop} (pp.
+165--171).
+
+\leavevmode\hypertarget{ref-frank2017}{}%
+Frank, M. C., Braginsky, M., Yurovsky, D., \& Marchman, V. A. (2017). Wordbank: An open repository for developmental vocabulary data. \emph{Journal of Child Language}, \emph{44}(3), 677--694.
+
+\leavevmode\hypertarget{ref-gentner1982}{}%
+Gentner, D. (1982). Why nouns are learned before verbs: Linguistic relativity versus natural partitioning. \emph{Center for the Study of Reading Technical Report}.
+
+\leavevmode\hypertarget{ref-gillespie15}{}%
+Gillespie, C. S. (2015). Fitting heavy tailed distributions: The poweRlaw package. \emph{Journal of Statistical Software}, \emph{64}(2), 1--16. Retrieved from \url{http://www.jstatsoft.org/v64/i02/}
+
+\leavevmode\hypertarget{ref-goodman2008}{}%
+Goodman, J. C., Dale, P. S., \& Li, P. (2008). Does frequency count? Parental input and the acquisition of vocabulary. \emph{Journal of Child Language}, \emph{35}(3), 515--531.
+
+\leavevmode\hypertarget{ref-dippl}{}%
+Goodman, N., \& Stuhlmuller, A. (2014). The Design and Implementation of Probabilistic Programming Languages. \url{http://dippl.org}.
+
+\leavevmode\hypertarget{ref-griffiths07}{}%
+Griffiths, T. L., Steyvers, M., \& Tenenbaum, J. B. (2007). Topics in semantic representation. \emph{Psychological Review}, \emph{114}(2), 2007.
+
+\leavevmode\hypertarget{ref-hills2010}{}%
+Hills, T.
+T., Maouene, J., Riordan, B., \& Smith, L.
+B.
+(2010).
+The associative structure of language: Contextual diversity in early word learning.
+\emph{Journal of Memory and Language}, \emph{63}(3), 259--273.
+
+\leavevmode\hypertarget{ref-hills2009}{}%
+Hills, T.
+T., Maouene, M., Maouene, J., Sheya, A., \& Smith, L.
+(2009).
+Longitudinal analysis of early semantic networks: Preferential attachment or preferential acquisition?
+\emph{Psychological Science}, \emph{20}(6), 729--739.
+
+\leavevmode\hypertarget{ref-hills2018}{}%
+Hills, T. T., \& Siew, C. S. (2018). Filling gaps in early word learning. \emph{Nature Human Behaviour}, \emph{2}(9).
+
+\leavevmode\hypertarget{ref-hoff2002}{}%
+Hoff, E., \& Naigles, L. (2002). How children use input to acquire a lexicon. \emph{Child Development}, \emph{73}(2).
+
+\leavevmode\hypertarget{ref-huttenlocher1991}{}%
+Huttenlocher, J., Haight, W., Bryk, A., Seltzer, M., \& Lyons, T. (1991). Early vocabulary growth: Relation to language input and gender. \emph{Developmental Psychology}, \emph{27}(2).
+
+\leavevmode\hypertarget{ref-jusczyk1994}{}%
+Jusczyk, P. W., Luce, P. A., \& Charles-Luce, J. (1994). Infant's sensitivity to phonotactic patterns in the native language. \emph{Journal of Memory and Language}, \emph{33}(5), 630--645.
+
+\leavevmode\hypertarget{ref-kachergis2011}{}%
+Kachergis, G., Cox, G.
+E., \& Jones, M.
+N.
+(2011).
+OrBEAGLE: Integrating orthography into a holographic model of the lexicon.
+In \emph{International conference on artificial neural networks} (pp.
+307--314).
+Springer.
+
+\leavevmode\hypertarget{ref-karuza2016}{}%
+Karuza, E.
+A., Thompson-Schill, S.
+L., \& Bassett, D.
+S.
+(2016).
+Local patterns to global architectures: Influences of network topology on human learning.
+\emph{Trends in Cognitive Sciences}, \emph{20}(8).
+
+\leavevmode\hypertarget{ref-kuhl1997}{}%
+Kuhl, P.
+K., Andruski, J.
+E., Chistovich, I.
+A., Chistovich, L.
+A., Kozhevnikova, E.
+V., Ryskina, V.
+L., \ldots{} Lacerda, F.
+(1997).
+Cross-language analysis of phonetic units in language addressed to infants.
+\emph{Science}, \emph{277}(5326), 684--686.
+
+\leavevmode\hypertarget{ref-luce1998}{}%
+Luce, P. A., \& Pisoni, D. B. (1998). Recognizing spoken words: The neighborhood activation model. \emph{Ear and Hearing}, \emph{19}(1).
+
+\leavevmode\hypertarget{ref-lupyan2017}{}%
+Lupyan, G., \& Lewis, M. (2017). From words-as-mappings to words-as-cues: The role of language in semantic knowledge. \emph{Language, Cognition and Neuroscience}.
+
+\leavevmode\hypertarget{ref-macwhinney2014}{}%
+MacWhinney, B. (2014). \emph{The CHILDES project: Tools for analyzing talk, Volume II}. Psychology Press.
+
+\leavevmode\hypertarget{ref-markman90}{}%
+Markman, E. M. (1990). Constraints children place on word meanings. \emph{Cognitive Science}, \emph{14}(1), 57--77.
+
+\leavevmode\hypertarget{ref-matusevych2018}{}%
+Matusevych, Y., \& Stevenson, S. (2018). Analyzing and modeling free word associations. In \emph{Proceedings of the 40th Annual Conference of the Cognitive Science Society}.
+
+\leavevmode\hypertarget{ref-mcmurray2012}{}%
+McMurray, B., Horst, J. S., \& Samuelson, L. K. (2012). Word learning emerges from the interaction of online referent selection and slow associative learning. \emph{Psychological Review}, \emph{119}.
+
+\leavevmode\hypertarget{ref-mcrae2005}{}%
+McRae, K., Cree, G.
+S., Seidenberg, M.
+S., \& McNorgan, C.
+(2005).
+Semantic feature production norms for a large set of living and nonliving things.
+\emph{Behavior Research Methods}, \emph{37}(4), 547--559.
+
+\leavevmode\hypertarget{ref-nelson1998}{}%
+Nelson, D. L., McEvoy, C. L., \& Schreiber, T. A. (1998). The University of South Florida word association, rhyme, and word fragment norms. Retrieved from \url{http://w3.usf.edu/FreeAssociation/}
+
+\leavevmode\hypertarget{ref-pisoni1985}{}%
+Pisoni, D. B., Nusbaum, H. C., Luce, P. A., \& Slowiaczek, L. M. (1985). Speech perception, word recognition and the structure of the lexicon. \emph{Speech Communication}, \emph{4}(1), 75--95.
+
+\leavevmode\hypertarget{ref-roy2015}{}%
+Roy, B. C., Frank, M. C., DeCamp, P., Miller, M., \& Roy, D. (2015). Predicting the birth of a spoken word. \emph{Proceedings of the National Academy of Sciences}, \emph{112}(41).
+
+\leavevmode\hypertarget{ref-saffran1996}{}%
+Saffran, J. R., Aslin, R. N., \& Newport, E. L. (1996). Statistical learning by 8-month-old infants. \emph{Science}, \emph{274}(5294), 1926--1928.
+
+\leavevmode\hypertarget{ref-siew2013}{}%
+Siew, C. S. (2013). Community structure in the phonological network. \emph{Frontiers in Psychology}, \emph{4}.
+
+\leavevmode\hypertarget{ref-slobin2014}{}%
+Slobin, D. I. (2014). \emph{The crosslinguistic study of language acquisition} (Vol. 4). Psychology Press.
+
+\leavevmode\hypertarget{ref-smith2008}{}%
+Smith, L., \& Yu, C. (2008). Infants rapidly learn word-referent mappings via cross-situational statistics. \emph{Cognition}, \emph{106}(3).
+
+\leavevmode\hypertarget{ref-stella2017}{}%
+Stella, M., Beckage, N. M., \& Brede, M. (2017). Multiplex lexical networks reveal patterns in early word acquisition in children. \emph{Scientific Reports}, \emph{7}.
+
+\leavevmode\hypertarget{ref-steyvers2005}{}%
+Steyvers, M., \& Tenenbaum, J. B. (2005). The large-scale structure of semantic networks: Statistical analyses and a model of semantic growth. \emph{Cognitive Science}, \emph{29}(1), 41--78.
+
+\leavevmode\hypertarget{ref-storkel2001}{}%
+Storkel, H. L. (2001). Learning new words: Phonotactic probability in language development. \emph{Journal of Speech, Language, and Hearing Research}, \emph{44}(6), 1321--1337.
+
+\leavevmode\hypertarget{ref-storkel2009}{}%
+Storkel, H. L. (2009). Developmental differences in the effects of phonological, lexical and semantic variables on word learning by infants. \emph{Journal of Child Language}, \emph{36}(2), 29--321.
+
+\leavevmode\hypertarget{ref-swingley2018}{}%
+Swingley, D., \& Humphrey, C. (2018). Quantitative linguistic predictors of infants' learning of specific english words. \emph{Child Development}, \emph{89}(4).
+
+\leavevmode\hypertarget{ref-takac2017}{}%
+Takac, M., Knott, A., \& Stokes, S.
+(2017).
+What can neighbourhood density effects tell us about word learning?
+Insights from a connectionist model of vocabulary development.
+\emph{Journal of Child Language}, \emph{44}(2).
+
+\leavevmode\hypertarget{ref-vitevitch2008}{}%
+Vitevitch, M. S. (2008). What can graph theory tell us about word learning and lexical retrieval? \emph{Journal of Speech, Language, and Hearing Research}, \emph{51}(2), 408--422.
+
+\leavevmode\hypertarget{ref-vitevitch1999}{}%
+Vitevitch, M. S., Luce, P. A., Pisoni, D. B., \& Auer, E. T. (1999). Phonotactics, neighborhood activation, and lexical access for spoken words. \emph{Brain and Language}, \emph{68}(1), 306--311.
+
+\leavevmode\hypertarget{ref-vitevitch2005}{}%
+Vitevitch, M. S., \& Rodrı'guez, E. (2005). Neighborhood density effects in spoken word recognition in spanish. \emph{Journal of Multilingual Communication Disorders}, \emph{3}(1).
+
+\leavevmode\hypertarget{ref-youn2016}{}%
+Youn, H., Sutton, L., Smith, E., Moore, C., Wilkins, J.
+F., Maddieson, I., \ldots{} Bhattacharya, T.
+(2016).
+On the universal structure of human lexical semantics.
+\emph{Proceedings of the National Academy of Sciences}, \emph{113}(7), 1766--1771.
+
+\leavevmode\hypertarget{ref-yurovsky2015}{}%
+Yurovsky, D., \& Frank, M. C. (2015). An integrative account of constraints on cross-situational learning. \emph{Cognition}, \emph{145}.
 

### 2020-04-02 helper_functions/make_pairs_helper.r

@@ -169,6 +169,7 @@ make_IPA_pairs<- function(def_list, lang){
   only_IPA <- IPA_items %>% select(IPA)
   
   # make word pairs with phonological distance
+  
   IPA_pairs <- expand.grid(only_IPA$IPA, only_IPA$IPA) %>%
     left_join(item_IPA_join, by = c("Var1" = "IPA"))  %>%
     rename(pair = item, pair.definition = Var1) %>%
@@ -179,7 +180,22 @@ make_IPA_pairs<- function(def_list, lang){
     select(item, item.definition, pair, pair.definition, dist) %>%
     filter(item!=pair) %>%
     ungroup()
+  
+  #Here I add the normalized edit distance
+  IPA_pairs_norm <- expand.grid(only_IPA$IPA, only_IPA$IPA) %>%
+    left_join(item_IPA_join, by = c("Var1" = "IPA"))  %>%
+    rename(pair = item, pair.definition = Var1) %>%
+    left_join(item_IPA_join, by = c("Var2" = "IPA")) %>%
+    rename(item.definition = Var2) %>%
+    rowwise() %>%
+    mutate(dist = adist(item.definition, pair.definition)) %>%
+    mutate(len_max = max(str_length(item.definition), str_length(pair.definition))) %>%
+    mutate(dist_norm = dist/len_max) %>%
+    select(item, item.definition, pair, pair.definition, dist, dist_norm) %>%
+    filter(item!=pair) %>%
+    ungroup()
+  
     
-  IPA_pairs
-  return(IPA_pairs)
+  IPA_pairs_norm
+  return(IPA_pairs_norm)
 }

### 2020-04-02 helper_functions/phono_helper.r

@@ -43,4 +43,10 @@ IPA_continuous<- function(IPA_list){
   return(IPA_list)
 }
 
+IPA_continuous_norm<- function(IPA_list){
+  IPA_list<- IPA_list %>%
+    mutate(link=as.numeric(1-dist_norm))
+  return(IPA_list)
+}
+
 ######################################################################################################

### 2020-04-03 journal/ms.Rmd
final revisins

@@
     address       : "Postal address"
-    email         : "afourtas@stanford.edu"
+    email         : "abdellah.fourtassi@gmail.com"
 
@@
     institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
+
+keywords          : "Word learning; semantic network; phonological network; network growth; cross-linguistic analysis."
 
@@
 This pattern of findings suggests a word learning process where children harness their statistical learning abilities to detect and learn highly connected words in the learning environment.
-
-keywords          : "Word learning; semantic network; phonological network; network growth; cross-linguistic analysis."
 
@@
 
-#Introduction
+# Introduction
 
@@
 The fact that semantic associations are assumed to be shared across languages does not mean that the semantic networks will necessarily grow in a similar fashion.
-For instance, the set of words acquired by children as well as the order of word acquisition can vary from language to language leading to possibily different learning strategies.
+For instance, the set of words acquired by children as well as the order of word acquisition can vary from language to language leading to possibly different learning strategies.
 
@@
 To better represent the similarity space in the phonological domain, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{In Appendix A, we show the main results for phonological networks based on an edit distance of 1.
-We also show the results for phonological networks where the edges between pairs of words were weighted by the inverse of the edit distance.
+We also show the results for phonological networks where the edges between pairs of words were weighted by a normalized edit distance.
 We did not consider the case of a threshold larger than 2 since many short pairs appear phonologically unrelated when the edit distance is 3 or more (e.g., "cat"/"dog").} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
@@
   geom_jitter(#aes(colour = lexical_class),
-    #colour = solarized_palette(1),
+    colour = 'dodgerblue3',
     size = 0.5, alpha = 0.5) +
@@
 
-###Connectivity predicts the age of acquisition
+### Connectivity predicts the age of acquisition
 
@@
   geom_point(#aes(colour = lexical_class),
-    #colour = solarized_palette(1),
+    #colour = 'dodgerblue3',
     size = 0.5, alpha = 0.5) +
@@
 
-###Power-law degree distribution
+### Power-law degree distribution
 
@@
       linesep = "", format.args = list(big.mark = ","),
-      caption = "Results of fitting a power law model to the degree (i.e., connectivity) distribution in each model for production data.
-Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis.
+      caption = "Results of fitting a power-law model to the degree (i.e., connectivity) distribution in each model for production data.
+Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power-law hypothesis.
 If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.",
       col.names = c("Language",  "cut-off", "alpha", "p-value", "cut-off", "alpha", "p-value")) %>%
-  add_header_above(c("", "Phono." = 3, "Sem." = 3)) %>%
+  add_header_above(c("", "Sem." = 3, "Phono." = 3)) %>%
   column_spec(1, bold = TRUE) %>%
@@
       linesep = "", format.args = list(big.mark = ","),
-      caption = "Results of fitting a power law model to the degree distribution in each model for comprehension data.
-Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis.
+      caption = "Results of fitting a power-law model to the degree distribution in each model for comprehension data.
+Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power-law hypothesis.
 If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.",
       col.names = c("Language",  "cut-off", "alpha", "p-value", "cut-off", "alpha", "p-value")) %>%
-  add_header_above(c("", "Phono." = 3, "Sem." = 3)) %>%
+  add_header_above(c("", "Sem." = 3, "Phono." = 3)) %>%
   column_spec(1, bold = TRUE) %>%
@@
 In brief, the analysis consisted in two steps.
-First, we derived the optimal cut-off, $k_{min}$, above which the distribution is more likely to follow a power law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter $\alpha$.
+First, we derived the optimal cut-off, $k_{min}$, above which the distribution is more likely to follow a power-law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter $\alpha$.
 Second, we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model.
@@
 These "truncated" power-laws  in phonological networks may be due to the constraints that exist on word formation in the phonological domain such as the size of the phonemic inventory, phonotactic rules, and word length.
-Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law [@arbesman2010].
+Such constraints may limit the number of words that are phonologically similar, thus leading to distributions that decay faster than a non-truncated power law [@arbesman2010].
 
@@
 For example, there is evidence that a small part of the variance in free association data can be explained by phonological similarity [@kachergis2011; @matusevych2018], thus leading to possibly minor cross-linguistic differences.] and phonological domains.
+In Appendix B, we show that the semantic and phonological domains provide largely non-redundant information.
 
@@
 As for the factors of interest, i.e., semantic and phonological connectivity, we found cross-linguistic differences.
-Connectivity contributes to learning in some languages but not in other.
-In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
+Connectivity contributes to learning in some languages but not in others.
+In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency, and length.
 This finding contrasts with the original finding in @hills2009.
@@
 An important property of this kind of learning is that it occurs without explicit instructions and through mere exposure to the input.
-Previous work in this line of research has documented specific mechanisms which can explain the patterns found in the current study.
+Previous work in this line of research has documented specific mechanisms that can explain the patterns found in the current study.
 
@@
 This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts.
-Crucially, children can learn these words without necessarily knowing the meaning of all other words with which they co-occur (hence the similarity with EXT).
+Crucially, children can learn these words without necessarily knowing the meaning of all other words with which they co-occur [@fourtassi2014], hence the similarity with EXT.
 This possibility is supported by the finding that words' diversity of occurrence in child-directed speech predicts their age of learning [@stella2017; @hills2010].
@@
 That said, it is important to remember that this type of data can only inform us about the learning trajectory of the "average" child.
-Although our study endorses, overall, the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT [@beckage].
+Although our study endorses, overall, the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT [@beckage2019].
 To illustrate, some children develop "islands of expertise," that is, well-organized knowledge about a certain topic (e.g., birds or dinosaurs).
@@
 
-# Appendix A: Analyses using different phnonological distances
+# Appendix A: Analyses using different phonological distances
 
@@
 The main analyses for these two cases are shown in what follows.
-In summary, both methods of constructing the phonological networks had issues.
-While the fact of using an edit distance of 1 created sparsity, using weighted networks created collinearity with length in the models.
 
@@
 The sparsity issue --- due to the low phonological neighborhood in the children's lexicon --- is apparent: Most words had 0 connectivity, and a few had non-zero but small degrees.
-The values of the correlations are much lower than the ones obtained with the threshold of 2.
-
-The next figures show how the phonology-based mechanism of growth (phonoEXT) fares in comaprison to semEXT and other predictors of learning in each language (Figure \@ref(fig:staticPredEdit1) and across all languages (Figure \@ref(fig:staticAllEdit)).
+The values of the correlations are much lower than the ones obtained with a threshold of 2.
+
+The next figures show how the phonology-based mechanism of growth (phonoEXT) fares in  comparison to semEXT and other predictors of learning in each language (Figure \@ref(fig:staticPredEdit1)) and across all languages (Figure \@ref(fig:staticAllEdit)).
 These figures show that phonoEXT based on edit distance 1 had no noticeable effect on learning.
@@
 
-```{r corrPlot, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Age of acquistion in both comprehension and production as predicted by the degree (i.e., connectivity) in the phonological networks, using an edit distance of 1.
+```{r corrPlot, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Age of acquisition in both comprehension and production as predicted by the degree (i.e., connectivity) in the phonological networks, using an edit distance of 1.
 Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients."}
@@
 ```{r staticPredEdit1, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression models.
-The phonologocal networks were based on an edit distance of 1.
+The phonological networks were based on an edit distance of 1.
 Ranges indicate 95\\% confidence intervals.
@@
 ```{r staticAllEdit, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined model.
-The phonologocal networks were based on an edit distance of 1.
+The phonological networks were based on an edit distance of 1.
 Ranges indicate 95\\% confidence intervals.
@@
 #Import data from saved
-data_all <- feather::read_feather("../saved_data/data_static_scaled_nt.feather")
+data_all <- feather::read_feather("../saved_data/data_static_scaled_nt_norm.feather")
 
@@
 
-We constructed weighted phonological networks where the edge between a given pair of words $(w_1, w_2)$ was wieghted by $\frac{1}{edit(w_1,w_2)}$.
-The phonological connectivity of a given word $w$ was defined as the sum over all weighted edges with every other word $w_i$ in the network, i.e., $\sum_{i} \frac{1}{edit(w,w_i)}$.
+We constructed weighted phonological networks where the edge between a given pair of words $(w_1, w_2)$ was weighted by a measure of similarity defined as $1-NED(w_1,w_2)$, where $NED(w_1,w_2)$ is the Normalized Edit Distance with values in the range $[0,1]$.
+We obtain $NED(w_1,w_2)$ by dividing the edit distance by the maximum possible distance between the two words, that is, the length of the longer word.
+The phonological connectivity of a given word $w$ was defined as the sum over all weighted edges with every other word $w_i$ in the network, i.e., $\sum_{i} (1-NED(w,w_i))$.
 
 The results were as follows.
-On the one hand, the correlations were generally high and in many cases (especially in the production data), higher than the ones obtained with the thresholds 2 and 1 (Figure \@ref(fig:corrPlotnt)).
-On the other hand, phonoEXT resulted in very noisy estimates when we controlled for frequency and length (Figures \@ref(fig:staticPrednt) and \@ref(fig:staticAllnt)).
-The reason was that the new phonological connectivity was very highly correlated with length.
+The correlations were lower than the ones obtained with the thresholds 2 and 1 (Figure \@ref(fig:corrPlotnt)).
+That sais, we found a (slight) predictive effect of phonoEXT when controlling for frequency and length (Figures \@ref(fig:staticPrednt) and \@ref(fig:staticAllnt)).
+
+<!--The reason was that the new phonological connectivity was very highly correlated with length.
 The average correlation across languages was $r =$ `r cor_phon_len_nt$ave[cor_phon_len_nt$measure == "produces"]` for production data (compared to `r cor_phon_len_edit1$ave[cor_phon_len_edit1$measure == "produces"]` and `r cor_phon_len_edit2$ave[cor_phon_len_edit2$measure == "produces"]` for the phonological networks with an edit distance of 1 and 2, respectvely).
 This fact lead to a collinearity issue in the regression, making the effects hard to estimate and interpret.
-
-```{r corrPlotnt, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Age of acquistion in both comprehension and production as predicted by the connectivity in the phonological network, using weighted edges.
+-->
+
+```{r corrPlotnt, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Age of acquisition in both comprehension and production as predicted by the connectivity in the phonological network, using weighted edges.
 Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients."}
@@
 ##Test
-static_preds <- feather::read_feather("../saved_data/coefs_all_nt.feather")
+static_preds <- feather::read_feather("../saved_data/coefs_all_nt_norm.feather")
 
@@
 ```{r staticPrednt, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression models.
-In the phonological networks, the edges between pairs of words were weighted by the inverse of the edit distance.
+In the phonological networks, the edges between pairs of words were weighted by a normalized edit distance.
 Ranges indicate 95\\% confidence intervals.
@@
 ```{r}
-static_preds_all <- feather::read_feather("../saved_data/static_preds_all_nt.feather")
+static_preds_all <- feather::read_feather("../saved_data/static_preds_all_nt_norm.feather")
 
@@
 
-plot_static_preds_all_nt <- ggplot(static_preds_all, aes(x = predictor, y = Estimate)) +
+plot_static_preds_all_nt_norm <- ggplot(static_preds_all, aes(x = predictor, y = Estimate)) +
   geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = Estimate, col = predictor, linetype=Test),
@@
 
-ggsave("figs/plot_static_preds_all_nt.pdf", plot = plot_static_preds_all_nt, width = 6, height = 3)
+ggsave("figs/plot_static_preds_all_nt_norm.pdf", plot = plot_static_preds_all_nt_norm, width = 6, height = 3)
 
@@
 ```{r staticAllnt, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined model.
-In the phonological networks, the edges between pairs of words were weighted by the inverse of the edit distance.
+In the phonological networks, the edges between pairs of words were weighted by a normalized edit distance.
 Ranges indicate 95\\% confidence intervals.
@@
 
-plot_static_preds_all_nt
+plot_static_preds_all_nt_norm
 
@@
 
-```{r corrPair, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "The distribution of the Pearson correlation coefficents of the unilemma's phonological connectivity between every pair of languages."}
+```{r corrPair, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "The distribution of the Pearson correlation coefficients of the unilemma's phonological connectivity between every pair of languages."}
 

### 2020-04-03 journal/ms.tex
final revisins

@@
 
-Correspondence concerning this article should be addressed to Abdellah Fourtassi, Postal address. E-mail: afourtas@stanford.edu}
+Correspondence concerning this article should be addressed to Abdellah Fourtassi, Postal address. E-mail: abdellah.fourtassi@gmail.com}
 \keywords{Word learning; semantic network; phonological network; network growth; cross-linguistic analysis.}
@@
 
-\#Introduction
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 To better represent the similarity space in the phonological domain, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{In Appendix A, we show the main results for phonological networks based on an edit distance of 1.
-We also show the results for phonological networks where the edges between pairs of words were weighted by the inverse of the edit distance.
+We also show the results for phonological networks where the edges between pairs of words were weighted by a normalized edit distance.
 We did not consider the case of a threshold larger than 2 since many short pairs appear phonologically unrelated when the edit distance is 3 or more (e.g., "cat"/"dog").} The connectivity of a given node was characterized with its \emph{degree}: the number of links it shares with other words.
@@
 
-\#\#\#Connectivity predicts the age of acquisition
+\hypertarget{connectivity-predicts-the-age-of-acquisition}{%
+\subsubsection{Connectivity predicts the age of acquisition}\label{connectivity-predicts-the-age-of-acquisition}}
 
@@
 
-\#\#\#Power-law degree distribution
+\hypertarget{power-law-degree-distribution}{%
+\subsubsection{Power-law degree distribution}\label{power-law-degree-distribution}}
 
@@
 
-\caption{\label{tab:powerLawProd}Results of fitting a power law model to the degree (i.e., connectivity) distribution in each model for production data.
-Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis.
+\caption{\label{tab:powerLawProd}Results of fitting a power-law model to the degree (i.e., connectivity) distribution in each model for production data.
+Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power-law hypothesis.
 If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.}
@@
 \toprule
-\multicolumn{1}{c}{} & \multicolumn{3}{c}{Phono.} & \multicolumn{3}{c}{Sem.} \\
+\multicolumn{1}{c}{} & \multicolumn{3}{c}{Sem.} & \multicolumn{3}{c}{Phono.} \\
 \cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
@@
 
-\caption{\label{tab:powerLawComp}Results of fitting a power law model to the degree distribution in each model for comprehension data.
-Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis.
+\caption{\label{tab:powerLawComp}Results of fitting a power-law model to the degree distribution in each model for comprehension data.
+Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power-law hypothesis.
 If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.}
@@
 In brief, the analysis consisted in two steps.
-First, we derived the optimal cut-off, \(k_{min}\), above which the distribution is more likely to follow a power law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter \(\alpha\).
+First, we derived the optimal cut-off, \(k_{min}\), above which the distribution is more likely to follow a power-law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter \(\alpha\).
 Second, we calculated the goodness-to-fit, which resulted in a \(p\)-value quantifying the plausibility of the model.
@@
 These \enquote{truncated} power-laws in phonological networks may be due to the constraints that exist on word formation in the phonological domain such as the size of the phonemic inventory, phonotactic rules, and word length.
-Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law (Arbesman et al., 2010).
+Such constraints may limit the number of words that are phonologically similar, thus leading to distributions that decay faster than a non-truncated power law (Arbesman et al., 2010).
 
@@
 For example, there is evidence that a small part of the variance in free association data can be explained by phonological similarity (Kachergis, Cox, \& Jones, 2011; Matusevych \& Stevenson, 2018), thus leading to possibly minor cross-linguistic differences.} and phonological domains.
+In Appendix B, we show that the semantic and phonological domains provide largely non-redundant information.
 
@@
 As for the factors of interest, i.e., semantic and phonological connectivity, we found cross-linguistic differences.
-Connectivity contributes to learning in some languages but not in other.
-In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
+Connectivity contributes to learning in some languages but not in others.
+In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency, and length.
 This finding contrasts with the original finding in Hills et al.
@@
 This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts.
-Crucially, children can learn these words without necessarily knowing the meaning of all other words with which they co-occur (hence the similarity with EXT).
+Crucially, children can learn these words without necessarily knowing the meaning of all other words with which they co-occur (Fourtassi, Dunbar, \& Dupoux, 2014), hence the similarity with EXT.
 This possibility is supported by the finding that words' diversity of occurrence in child-directed speech predicts their age of learning (Hills et al., 2010; Stella et al., 2017).
@@
 That said, it is important to remember that this type of data can only inform us about the learning trajectory of the \enquote{average} child.
-Although our study endorses, overall, the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT (Beckage \& Colunga, n.d.).
+Although our study endorses, overall, the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT (Beckage \& Colunga, 2019).
 To illustrate, some children develop \enquote{islands of expertise,} that is, well-organized knowledge about a certain topic (e.g., birds or dinosaurs).
@@
 
-\hypertarget{appendix-a-analyses-using-different-phnonological-distances}{%
-\section{Appendix A: Analyses using different phnonological distances}\label{appendix-a-analyses-using-different-phnonological-distances}}
+\hypertarget{appendix-a-analyses-using-different-phonological-distances}{%
+\section{Appendix A: Analyses using different phonological distances}\label{appendix-a-analyses-using-different-phonological-distances}}
 
@@
 The sparsity issue --- due to the low phonological neighborhood in the children's lexicon --- is apparent: Most words had 0 connectivity, and a few had non-zero but small degrees.
-The values of the correlations are much lower than the ones obtained with the threshold of 2.
-
-The next figures show how the phonology-based mechanism of growth (phonoEXT) fares in comaprison to semEXT and other predictors of learning in each language (Figure \ref{fig:staticPredEdit1} and across all languages (Figure \ref{fig:staticAllEdit}).
+The values of the correlations are much lower than the ones obtained with a threshold of 2.
+
+The next figures show how the phonology-based mechanism of growth (phonoEXT) fares in comparison to semEXT and other predictors of learning in each language (Figure \ref{fig:staticPredEdit1}) and across all languages (Figure \ref{fig:staticAllEdit}).
 These figures show that phonoEXT based on edit distance 1 had no noticeable effect on learning.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlot-1} \caption{Age of acquistion in both comprehension and production as predicted by the degree (i.e., connectivity) in the phonological networks, using an edit distance of 1.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlot-1} \caption{Age of acquisition in both comprehension and production as predicted by the degree (i.e., connectivity) in the phonological networks, using an edit distance of 1.
 Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlot}
@@
 \includegraphics[width=\textwidth]{ms_files/figure-latex/staticPredEdit1-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression models.
-The phonologocal networks were based on an edit distance of 1.
+The phonological networks were based on an edit distance of 1.
 Ranges indicate 95\% confidence intervals.
@@
 \includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllEdit-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined model.
-The phonologocal networks were based on an edit distance of 1.
+The phonological networks were based on an edit distance of 1.
 Ranges indicate 95\% confidence intervals.
@@
 
-We constructed weighted phonological networks where the edge between a given pair of words \((w_1, w_2)\) was wieghted by \(\frac{1}{edit(w_1,w_2)}\).
-The phonological connectivity of a given word \(w\) was defined as the sum over all weighted edges with every other word \(w_i\) in the network, i.e., \(\sum_{i} \frac{1}{edit(w,w_i)}\).
+We constructed weighted phonological networks where the edge between a given pair of words \((w_1, w_2)\) was weighted by a measure of similarity defined as \(1-NED(w_1,w_2)\), where \(NED(w_1,w_2)\) is the Normalized Edit Distance with values in the range \([0,1]\).
+We obtain \(NED(w_1,w_2)\) by dividing the edit distance by the maximum possible distance between the two words, that is, the length of the longer word.
+The phonological connectivity of a given word \(w\) was defined as the sum over all weighted edges with every other word \(w_i\) in the network, i.e., \(\sum_{i} (1-NED(w,w_i))\).
 
 The results were as follows.
-On the one hand, the correlations were generally high and in many cases (especially in the production data), higher than the ones obtained with the thresholds 2 and 1 (Figure \ref{fig:corrPlotnt}).
-On the other hand, phonoEXT resulted in very noisy estimates when we controlled for frequency and length (Figures \ref{fig:staticPrednt} and \ref{fig:staticAllnt}).
-The reason was that the new phonological connectivity was very highly correlated with length.
-The average correlation across languages was \(r =\) -0.95 for production data (compared to -0.29 and -0.60 for the phonological networks with an edit distance of 1 and 2, respectvely).
-This fact lead to a collinearity issue in the regression, making the effects hard to estimate and interpret.
+The correlations were lower than the ones obtained with the thresholds 2 and 1 (Figure \ref{fig:corrPlotnt}).
+That sais, we found a (slight) predictive effect of phonoEXT when controlling for frequency and length (Figures \ref{fig:staticPrednt} and \ref{fig:staticAllnt}).
 
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlotnt-1} \caption{Age of acquistion in both comprehension and production as predicted by the connectivity in the phonological network, using weighted edges.
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlotnt-1} \caption{Age of acquisition in both comprehension and production as predicted by the connectivity in the phonological network, using weighted edges.
 Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlotnt}
@@
 \includegraphics[width=\textwidth]{ms_files/figure-latex/staticPrednt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression models.
-In the phonological networks, the edges between pairs of words were weighted by the inverse of the edit distance.
+In the phonological networks, the edges between pairs of words were weighted by a normalized edit distance.
 Ranges indicate 95\% confidence intervals.
@@
 \includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllnt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined model.
-In the phonological networks, the edges between pairs of words were weighted by the inverse of the edit distance.
+In the phonological networks, the edges between pairs of words were weighted by a normalized edit distance.
 Ranges indicate 95\% confidence intervals.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPair-1} \caption{The distribution of the Pearson correlation coefficents of the unilemma's phonological connectivity between every pair of languages.}\label{fig:corrPair}
+\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPair-1} \caption{The distribution of the Pearson correlation coefficients of the unilemma's phonological connectivity between every pair of languages.}\label{fig:corrPair}
 \end{figure}
@@
 
-\leavevmode\hypertarget{ref-beckage}{}%
-Beckage, N. M., \& Colunga, E. (n.d.). Network growth modeling to capture individual lexical learning.
+\leavevmode\hypertarget{ref-beckage2019}{}%
+Beckage, N. M., \& Colunga, E. (2019). Network growth modeling to capture individual lexical learning. \emph{Complexity}.
 
@@
 \emph{Monographs of the Society for Research in Child Development}, \emph{59}(5).
+
+\leavevmode\hypertarget{ref-fourtassi2014}{}%
+Fourtassi, A., Dunbar, E., \& Dupoux, E. (2014). Self-consistency as an inductive bias in early language acquisition. In \emph{Proceedings of the annual meeting of the cognitive science society}.
 
